### 2020-07-08 main.tex
MDPI template for EIF localisation idea

%  LaTeX support: latex@mdpi.com 
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex]{Definitions/mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, applmech, applnano, applsci, arts, asc, asi, atmosphere, atoms, automation, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomedinformatics, biomimetics, biomolecules, biosensors, bloods, brainsci, breath, buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cyber, dairy, data, dentistry, dermatopathology, designs, diabetology, diagnostics, digital, diseases, diversity, drones, earth, econometrics, ecologies, economies, education, ejbc, ejihpe, electricity, electrochem, electronicmat, electronics, endocrines, energies, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, fuels, futureinternet, futurephys, galaxies, games, gardens, gases, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, hearts, heritage, highthroughput, horticulturae, humanities, hydrogen, hydrology, ijerph, ijfs, ijgi, ijms, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jce, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jne, jnt, jof, joitmc, journalmedia, jpm, jrfm, jsan, land, languages, laws, life, literature, livers, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, ijns, neurosci, neuroglia, nitrogen, notspecified, nutrients, obesities, oceans, ohbm, osteology, optics, organics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, pollutants, polymers, polysaccharides, preprints , proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, religions, remotesensing, reprodmed, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, surfaces, surgeries, suschem, sustainability, world, symmetry, systems, technologies, telecom, test, tourismhosp, toxics, toxins, transplantology, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj, women

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2020}
\copyrightyear{2020}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
%\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% Authors, for metadata in PDF
\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation 3} 
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: Place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: Describe briefly the main methods or treatments applied; (3) Results: Summarize the article's main findings; and (4) Conclusion: Indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}
The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions for authors page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX related questions please contact latex@mdpi.com.
%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision

\section{Introduction}
The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. And now citing a book reference \cite{ref-book}. Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\begin{quote}
This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Subsection}
\unskip
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}[leftmargin=*,labelsep=5.8mm]
\item	First bullet
\item	Second bullet
\item	Third bullet
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
\item	First item 
\item	Second item
\item	Third item
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=2 cm]{Definitions/logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

Text

Text

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

Text

Text

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\textwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\textwidth}{1pt}
%\end{listing}

\subsection{Formatting of Mathematical Components}

This is an example of an equation:

\begin{equation}
a + b = c
\end{equation}
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}
This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}

% Only for the journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & linear dichroism
\end{tabular}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendix
\section{}
\unskip
\subsection{}
The appendix is an optional section that can contain details and data supplemental to the main text. For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data. Mathematical proofs of results not central to the paper can be added as an appendix.

\section{}
All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\externalbibliography{yes}
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book}
Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds ...... are available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2020-07-08 main.tex
Gitignore
Started on structure and intro substructure Current intro substructure is shit - WIP Added ISAS macros and bibtex files

@@
 %=================================================================
-\documentclass[journal,article,submit,moreauthors,pdftex]{Definitions/mdpi}
+\documentclass[sensors,article,submit,moreauthors,pdftex]{Definitions/mdpi}
 
@@
 % Full title of the paper (Capitalized)
-\Title{Title}
+\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Partially Homomorphic Aggregation}
 
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-000-000X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0000-0002-9581-9937} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0001-8996-5738} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0001-9870-2331} % Add \orcidC{} behind the author's name
 
 % Authors, for the paper (add full first names)
-\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}
+\Author{Marko Ristic $^{1}$\orcidA{}, Benjamin Noack $^{1}$\orcidB{} and Uwe D. Hanebeck $^{1,}$*\orcidC{}}
 
 % Authors, for metadata in PDF
-\AuthorNames{Firstname Lastname, Firstname Lastname and Firstname Lastname}
+\AuthorNames{Marko Ristic, Benjamin Noack and Uwe D. Hanebeck}
 
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+\address[1]{%
+$^{1}$ \quad Intelligent Sensor-Actuator-systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany; marko.ristic@kit.edu; noack@kit.edu; uwe.hanebeck@kit.edu}
 
 % Contact information of the corresponding author
-\corres{Correspondence: e-mail@e-mail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+\corres{Correspondence: uwe.hanebeck@kit.edu; Tel.: +49-721-608-43909}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation 3} 
-\secondnote{These authors contributed equally to this work.}
+%\firstnote{Current address: Affiliation 3} 
+%\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
+
+\section{Introduction}
+Introduce localisation, filtering and the need for privacy.
+
+Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs
+
+Explain the additional difficulties with achieving privacy in distributed environments (malicious subsets etc). AO and pWSAO.
+
+Public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.
+
+Differential privacy concerned with hiding individuals in a group but results in noisy results. Also often requires a trusted aggregator, although aggregation methods exist.
+
+Application of partially Homomorphic encryption. Control examples include Alexandru and Farokhi papers, mostly applicable due to distributed aggregation step.
+
+Estimation examples include Filters with a sensor hierarchy and linear models, localisation methods which hide sensor information in a model-free environment but either pay in security or require additional rounds of communication.
+
+Additionally encoding for signal processing is an issue.
+Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers.
+Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication.
+
+Describe Navigator scenario and our contributions
+
+Section Summary
+
+\section{Problem Statement}
+Restate the scenario but more formally.
+
+Exact security guarantees we aim for
+
+Rough computational capabilities expected by parties
+
+Fixed sensor subsets of which only whole subsets can be used at once
+
+\section{Existing Literature}
+
+Details and differences to private localisation methods, aggregation methods, and encoding methods
+
+Model-free localisation examples can include polygon thing, WSN examples which protect against adversaries but don't preserve individual information.
+Importantly model-based filtering and localisation provides accurate estimates and these are not applicable there.
+
+Estimation examples can include Aristov paper (which requires linear model, and a hierarchy of sensors)
+
+Alexandru weighted aggregation requires redistributing keys at every timestep resulting in a costly operations, and a complicated communication protocol.
+
+Encoding of signal processing values for use in encrypted processing should consist of google bignum library and Farokhi qnm encoding
+
+\section{Preliminaries}
+
+\subsection{Integer Encoding for Real Numbers}
+\subsection{Paillier Encryption Scheme}
+\subsection{Joye-Libert Privacy-Preserving Aggregation}
+\subsection{Extended Information Filter}
+
+\section{Private Partially Homomorphic Aggregation}
+\section{Requirements for Measurement Model}
+\section{Localisation Measurement Modification}
+
+\section{Private Localisation with Privacy-Preserving Sensors}
+
+\section{Results}
+\section{Conclusion}
+
+<Rest is template>
+
 \section{How to Use this Template}

### 2020-07-13 main.tex
Added abstract according to my favourite 6 point method Added keywords Continued planning intro/problem/literature sections and orders

@@
 % Full title of the paper (Capitalized)
-\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Partially Homomorphic Aggregation}
+\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: Place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: Describe briefly the main methods or treatments applied; (3) Results: Summarize the article's main findings; and (4) Conclusion: Indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+\abstract{Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
+Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
+Existing secure methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
+We define a novel, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
+The requirements and cryptographic proof are given for the weighted aggregation scheme, and simulations of the private filter are used to evaluate the accuracy and performance of the method.
+Our approach defines a novel, computationally plausible, and private model-based localisation filter with direct application to environments where nodes may not be fully trusted, and data is considered sensitive.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific to the article, yet reasonably common within the subject discipline.)}
+\keyword{Extended Kalman Filter; Secure Localisation; Private Aggregation}
 
@@
 
+Public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.
+
 Explain the additional difficulties with achieving privacy in distributed environments (malicious subsets etc). AO and pWSAO.
-
-Public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.
 
@@
 Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers.
-Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication.
+Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further limits the real number size and increases risk of overflow).
 

### 2020-07-13 main.tex
Changed novel crypto scheme to modified crypto scheme (it's not THAT novel) in abstract Intro will include relevant existing literature as with last paper. Structure has been done in dot points.

@@
 Existing secure methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
-We define a novel, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
+We define a modified, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
 The requirements and cryptographic proof are given for the weighted aggregation scheme, and simulations of the private filter are used to evaluate the accuracy and performance of the method.
@@
 
-Public key cryptography applicability to distributed systems; difference to symmetric schemes. Homomorphic encryption power and use case.
+Methods for introducing security and privacy include differential privacy methods and encryption methods.
+
+Differential privacy involves using statistical noise as security to make individual users' information cannot be deduced.
+Often requires a trusted aggregator, although secure aggregation methods exist.
+always requires noising result such that the final outcome is not exact (a problem in localisation).
+
+Encryption schemes involve formal indistinguishability proofs typically over bit-streams or integers.
+They typically reply on computationally hard problems over bit streams of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
+Continuing, specify public key cryptography applicability to distributed systems; difference to symmetric schemes.
+Homomorphic encryption power and use case.
+
+Model-free localisation using homomorphic encryption examples include polygon thing, WSN examples which protect against adversaries but don't preserve individual information.
+Importantly model-based filtering and localisation provide accurate estimates and these are not applicable there.
+
+Model-based estimation examples can include Aristov paper (which requires a linear model, and a hierarchy of sensors) and Farkhi papers (which includes distribution step)
 
@@
 
-Differential privacy concerned with hiding individuals in a group but results in noisy results. Also often requires a trusted aggregator, although aggregation methods exist.
+pWSAO achieved in Alexandru weighted aggregation, but requires redistributing keys at every timestep resulting in a costly operation, and a complicated communication protocol.
 
-Application of partially Homomorphic encryption. Control examples include Alexandru and Farokhi papers, mostly applicable due to distributed aggregation step.
+In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format.
+Typically unlimited scalar multiplications and additions using a scheme that works over integers does not work on encoded real numbers.
+Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).
 
-Estimation examples include Filters with a sensor hierarchy and linear models, localisation methods which hide sensor information in a model-free environment but either pay in security or require additional rounds of communication.
-
-Additionally encoding for signal processing is an issue.
-Typically unlimited scalar multiplications and additions using a scheme that allows it over integers does not work on encoded real numbers.
-Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further limits the real number size and increases risk of overflow).
-
-Describe Navigator scenario and our contributions
+Briefly describe navigator scenario and our contributions
 
@@
 
+\subsection{Notation}
+Notation
+
 \section{Problem Statement}
+
 Restate the scenario but more formally.
 
-Exact security guarantees we aim for
+Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability)
 
@@
 
-Fixed sensor subsets of which only whole subsets can be used at once
-
-\section{Existing Literature}
-
-Details and differences to private localisation methods, aggregation methods, and encoding methods
-
-Model-free localisation examples can include polygon thing, WSN examples which protect against adversaries but don't preserve individual information.
-Importantly model-based filtering and localisation provides accurate estimates and these are not applicable there.
-
-Estimation examples can include Aristov paper (which requires linear model, and a hierarchy of sensors)
-
-Alexandru weighted aggregation requires redistributing keys at every timestep resulting in a costly operations, and a complicated communication protocol.
-
-Encoding of signal processing values for use in encrypted processing should consist of google bignum library and Farokhi qnm encoding
+Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in high level distributed localisation diagram.
 
@@
 
-\subsection{Integer Encoding for Real Numbers}
 \subsection{Paillier Encryption Scheme}
 \subsection{Joye-Libert Privacy-Preserving Aggregation}
+
+\section{Private Partially Homomorphic Aggregation}
+
+\subsection{Integer Encoding for Real Numbers}
 \subsection{Extended Information Filter}
 
-\section{Private Partially Homomorphic Aggregation}
 \section{Requirements for Measurement Model}
 \section{Localisation Measurement Modification}
+Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
+Give flight navigation as an applicable example with typically high distances.
 

### 2020-07-13 main.tex
Updated rest of paper layout. May need a little more planning.

@@
 
-\section{Preliminaries}
+\section{Private Weighted Aggregation Preliminaries}
 
 \subsection{Paillier Encryption Scheme}
+
 \subsection{Joye-Libert Privacy-Preserving Aggregation}
 
-\section{Private Partially Homomorphic Aggregation}
+% Maybe rename this to Our Scheme or something like that
+\section{Private Weighted Aggregation}
+\subsection{Proof}
+Give the reduction proof here for pWSAO and implicit indistinguishability of weights
+
+\section{Private Localisation Preliminaries}
 
 \subsection{Integer Encoding for Real Numbers}
+
 \subsection{Extended Information Filter}
 
-\section{Requirements for Measurement Model}
-\section{Localisation Measurement Modification}
+\section{Private Localisation with Privacy-Preserving Sensors}
+Explain it in overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors.
+
+\subsection{Requirements for Measurement Model}
+
+\subsection{Localisation Measurement Modification}
+Show here the weighted integrals that give mean and variance of the new noise.
+
 Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
@@
 
-\section{Private Localisation with Privacy-Preserving Sensors}
+\subsection{Expanding Aggregation for Multi-dimensional Inputs}
+Give 1D example that's intuitive (with $a^2b$) and then reduce the equivalent ND case ($A^\top BA$) to a set of weighted sums.
+
+Ensure that timestamps are concatenated with position so that no aggregation values are blinded by the same noise.
+
+% Maybe name the scheme? That would be in the heading here
+\subsection{Algorithm}
+Piece together the whole algorithm here.
 
 \section{Results}
+Decide on what kind of simulations and which plots to make. run times would be nice this time around
+
 \section{Conclusion}

### 2020-07-14 main.tex
Added bib to link with zotero Updated and added more points for paper layout

@@
 Homomorphic encryption power and use case.
+Why FHE isn't used often, why additive partially homomorphic encryption is.
 
@@
 \subsection{Proof}
-Give the reduction proof here for pWSAO and implicit indistinguishability of weights
+Give the reduction proof here for pWSAO and implicit indistinguishability of weights. alternatively sketch it out here and give reduction in appendix.
 
@@
 \subsection{Localisation Measurement Modification}
-Show here the weighted integrals that give mean and variance of the new noise.
+Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.
 
@@
 \section{Conclusion}
+Future work can include hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods.
+Can also consider ways of sending less information form the navigator to the sensors at each time step.
 

### 2020-07-21 main.tex
Added FE and MCFE to introduction Separated introduction from existing literature [structure of first couple sections will still need a look over and confirmation]

@@
 Often requires a trusted aggregator, although secure aggregation methods exist.
-always requires noising result such that the final outcome is not exact (a problem in localisation).
+always requires noising result such that the outcome is not exact (a problem in localisation).
 
-Encryption schemes involve formal indistinguishability proofs typically over bit-streams or integers.
-They typically reply on computationally hard problems over bit streams of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
-Continuing, specify public key cryptography applicability to distributed systems; difference to symmetric schemes.
+Encryption schemes involve formal indistinguishability proofs typically over bits or integers.
+They rely on computationally hard problems involving security parameters of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
+Continuing, explain public-key cryptography applicability to distributed systems; difference to symmetric schemes.
 Homomorphic encryption power and use case.
@@
 
-Model-free localisation using homomorphic encryption examples include polygon thing, WSN examples which protect against adversaries but don't preserve individual information.
-Importantly model-based filtering and localisation provide accurate estimates and these are not applicable there.
+Advancements in function providing encryption schemes such as homomorphic encryption have also led to several other types of schemes which have found uses in signal processing.
+Private aggregation schemes allow the secure computation of the sum of encrypted values originating from different parties, leaking only the final result.
+When considering such multi-party encryption protocols, formal security definitions must now also incorporate the added dangers of colluding malicious parties, and lead to new notions of security.
+For example Aggregator Obliviousness (AO) is typically proven for private aggregation schemes, while alternatives such as Private Weighted Secure Aggregator Obliviousness (pWSAO) exist for other specific use-cases.
+
+Another example of function providing encryption, and a generalisation of private aggregation, is called functional encryption (FE) and its distributed extension, multi-client functional encryption (MCFE), which allow the unencrypted result of an arbitrary function to be computed from encrypted inputs.
+General FE and MCFE are known to be quite computationally expensive (from meeting with ITI and student Johannes - need ref.) but alternatives providing only a subset of possibly computable function exist; for example, inner product encryption.
+
+Several of the aforementioned encryption schemes have found uses in secure localisation, estimation, and control.
+
+\section{Existing Literature}
+
+Model-free localisation using homomorphic encryption examples include polygon thing, WSN examples which protect against adversaries but in the case of the WSN paper.
+don't preserve anchor privacy.
+Importantly, model-based filtering and localisation provide more accurate estimates and these are not applicable there.
 
 Model-based estimation examples can include Aristov paper (which requires a linear model, and a hierarchy of sensors) and Farkhi papers (which includes distribution step)
-
-Explain the additional difficulties with achieving privacy in distributed environments (malicious subsets etc). AO and pWSAO.
 
@@
 
-\subsection{Notation}
+\section{Notation}
 Notation
@@
 
-Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in high level distributed localisation diagram.
+Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram.
 

### 2020-07-21 main.tex
More detailed dot points about security model Fixed English in some parts (still dot points though) specified leakage in localisation from aggregation sum leakage (which is allowed with AO)

@@
 Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
-Existing secure methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
+Secure existing methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
 We define a modified, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
 The requirements and cryptographic proof are given for the weighted aggregation scheme, and simulations of the private filter are used to evaluate the accuracy and performance of the method.
-Our approach defines a novel, computationally plausible, and private model-based localisation filter with direct application to environments where nodes may not be fully trusted, and data is considered sensitive.}
+Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.}
 
@@
 
-\section{Existing Literature}
+\subsection{Relevant Literature on Encrypted Localisation and Estimation}
 
@@
 
-Model-based estimation examples can include Aristov paper (which requires a linear model, and a hierarchy of sensors) and Farkhi papers (which includes distribution step)
+Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only cloud as a service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)
 
@@
 In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format.
-Typically unlimited scalar multiplications and additions using a scheme that works over integers does not work on encoded real numbers.
+As is the case with our proposed localisation method, real number sensor output doesnot trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent.
+Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist.
 Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).
@@
 
-\section{Notation}
+\subsection{Notation}
 Notation
@@
 
-Restate the scenario but more formally.
+Restate the scenario but more formally. Give concrete example - plane and signal towers.
 
-Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability)
+Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
+Note that learning only the sum in aggregation (as is normal in AO) would in this case tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
+
+Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear).
+Justify by saying sensors need to behave for localisation to work in the first place, for example GPS.
+
+Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
+In a wireless setting all sensors would recieve all broadcast weights anyway.
+While special hardware which would support directional broadcasting and recieving could be used to locate sensors individually this is beyond the scope of what is considered in our problem.
+
+Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurment of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measuremments are not known
 
@@
 \section{Private Weighted Aggregation}
+Explain it in overview
+
 \subsection{Proof}
@@
 Explain it in overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors.
+
+Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and meausurement to the navigator.
+This is the reason for the accaptance of this leakage, as we pointed out in the problem statement section.
 

### 2020-07-23 main.tex
Couple more of the points from the ITI meeting added to dot points to make sure they're not forgotten Started trying to make the network/sensor subsets picture in tikz but it's a nightmare. Files remain for the time being

@@
 Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear).
-Justify by saying sensors need to behave for localisation to work in the first place, for example GPS.
+Any largly incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.).
+Justify by saying sensors need to behave for localisation to work in the first place.
 
@@
 
-Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram.
+Fixed sensor subsets of which only whole subsets can be used at once.
+Maybe a picture of what this might look like in a high level distributed localisation diagram.
+Should consider that this subt grouping would also mean the leakage of the average sensor/measurment of each subset not all sensors at once.
+This should be considered when choosing sensor subsets and locations.
 
@@
 \subsection{Localisation Measurement Modification}
-Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.
+Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probably not needed.
 
@@
 Give flight navigation as an applicable example with typically high distances.
+
+Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measumrements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
 
@@
 Piece together the whole algorithm here.
+Give the algorithm as a pseudocode (including encoding and encryption)
 

### 2020-07-24 main.tex
Changes to network tiks, but will remove most likely as it hasn't worked yet. Added dot points for Result plots. These still need to be confirmed

@@
 
+Time results can be captured in one graph.
+Y axis is time, x axis in number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bitsizes (at least 3: 512, 1024, 2048).
+Every data point should be the average over some X number of simulations.
+
+Accuracy plots will describe error due to encoding, number of sensors (more adding may increase error in encoding), and the average distance of the sensors to the navigator.
+All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense).
+
+Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
+
+Plot 2 will plot the RMSE of the average of X runs with different numbers of sensors. A fixed encoding method will be used, and a fixed Paillier bit size.
+
+Plot 3 will plot the RMSE as the average distance of sensors changes.
+Fixed encoding and Paillier bit size.
+Vary between 4 layouts where 4 sensors are either very close to the center (and ground truth, and progressivly further out)
+
+Plot 4 will accompany plot 3 and display the 4 layours (arrow for ground truth and points for the sensors).
+
 \section{Conclusion}
-Future work can include hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods.
-Can also consider ways of sending less information form the navigator to the sensors at each time step.
+Possible future work to consider writing here:
+Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions recieved at sensors.
 

### 2020-08-11 main.tex
Grammarly plugin works again, fixed typos in dot points Removed the network image from before - will need to find easier way to show this, far too complex with tikz

--- 2020-07-21 main.tex
@@
 
-Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only cloud as a service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)
+Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only the cloud-as-a-service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)
 
@@
 In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format.
-As is the case with our proposed localisation method, real number sensor output doesnot trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent.
+As is the case with our proposed localisation method, real number sensor output does not trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent.
 Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist.
@@
 
-Restate the scenario but more formally. Give concrete example - plane and signal towers.
+Restate the scenario but more formally. Give a concrete example - plane and signal towers.
 
 Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
-Note that learning only the sum in aggregation (as is normal in AO) would in this case tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
+Note that learning only the sum in aggregation (as is normal in AO) would, in this case, tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
 
-Passive attacks only from sensors to learn navigator position (Otherwise could do some kind of attack that would send fake measurement and note the change in it's own measurements - possible this would give away average of other sensors' measurements but unclear).
-Justify by saying sensors need to behave for localisation to work in the first place, for example GPS.
+Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear).
+Any largely incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.).
+Justify by saying sensors need to behave for localisation to work in the first place.
 
 Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
-In a wireless setting all sensors would recieve all broadcast weights anyway.
-While special hardware which would support directional broadcasting and recieving could be used to locate sensors individually this is beyond the scope of what is considered in our problem.
+In a wireless setting, all sensors would receive all broadcast weights anyway.
+While special hardware, which may support directional broadcasting or receiving, could be used to locate sensors individually this is beyond the scope of what is considered in our problem.
 
-Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurment of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measuremments are not known
+Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known
 
@@
 
-Fixed sensor subsets of which only whole subsets can be used at once. Maybe a picture of what this might look like in a high level distributed localisation diagram.
+Fixed sensor subsets of which only whole subsets can be used at once.
+Maybe a picture of what this might look like in a high level distributed localisation diagram.
+Should consider that this sub-grouping would also mean the leakage of the average sensor/measurement of each subset not all sensors at once.
+This should be considered when choosing sensor subsets and locations.
 
@@
 \section{Private Weighted Aggregation}
-Explain it in overview
+Explain it in as an overview
 
 \subsection{Proof}
-Give the reduction proof here for pWSAO and implicit indistinguishability of weights. alternatively sketch it out here and give reduction in appendix.
+Give the reduction proof here for pWSAO and implicit indistinguishability of weights. Alternatively, sketch it out here and give reduction proof in the appendix.
 
@@
 \section{Private Localisation with Privacy-Preserving Sensors}
-Explain it in overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors.
+Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
 
-Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and meausurement to the navigator.
-This is the reason for the accaptance of this leakage, as we pointed out in the problem statement section.
+Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator.
+This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.
 
@@
 \subsection{Localisation Measurement Modification}
-Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in appendix section, but probablynot needed.
+Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
 
@@
 
+Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
+
 \subsection{Expanding Aggregation for Multi-dimensional Inputs}
@@
 
-Ensure that timestamps are concatenated with position so that no aggregation values are blinded by the same noise.
+Ensure that timestamps are concatenated with the position so that no aggregation values are blinded by the same noise.
 
@@
 Piece together the whole algorithm here.
+Give the algorithm as pseudocode (including encoding and encryption)
 
@@
 
+Time results can be captured in one graph.
+Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048).
+Every data point should be the average over some X number of simulations.
+
+Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
+All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense).
+
+Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
+
+Plot 2 will plot the RMSE as the average distance of sensors changes.
+Fixed encoding and Paillier bit size.
+Vary between 4 layouts where 4 sensors are either very close to the centre (and ground truth, and progressively further out)
+
+Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).
+
+A well-defined example.
+
 \section{Conclusion}
-Future work can include hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods.
-Can also consider ways of sending less information form the navigator to the sensors at each time step.
+Possible future work to consider writing here:
+Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors.
 

### 2020-08-17 main.tex
Started on writing encryption section. Paillier and Joye-Libert need to be described first. - Enc and Agg in the process of being explained. - Need to simplify/know how to explain why g^m is an easily solvable logarithm (to dow ith n^2) - Need to introduce security of the schemes + random oracle model/normal model

@@
 The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+\usepackage{amsfonts}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 % Contact information of the corresponding author
-\corres{Correspondence: uwe.hanebeck@kit.edu; Tel.: +49-721-608-43909}
+\corres{Correspondence: uwe.hanebeck@kit.edu; Tel.: +49--721--608--43909}
 
@@
 Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
-Secure existing methods fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
-We define a modified, cryptographically secure, weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
-The requirements and cryptographic proof are given for the weighted aggregation scheme, and simulations of the private filter are used to evaluate the accuracy and performance of the method.
+Existing approaches which provide such guarantees, fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
+We define a cryptographically secure weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
+The security requirements, leakage, and cryptographic proof are given for the private filter and weighted aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
 Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.}
@@
 \section{Introduction}
+
+--
+
 Introduce localisation, filtering and the need for privacy.
@@
 \section{Private Weighted Aggregation Preliminaries}
+Our weighted aggregation method relies on the decisional composite residuosity assumption (DCRA) originally defined by Paillier in \cite{paillierPublicKeyCryptosystemsBased1999}.
+The aggregation method can be seen as a combination of the additive homomorphic Paillier encryption scheme, which additionally allows multiplication of an encrypted message with a plaintext value, and the Joye-Libert private stream-aggregation scheme.
+Both of these schemes base their security on the DCRA, and their descriptions are given briefly below before defining our weighted aggregation scheme.
+
+% A number $z$ is said to be an $n$th residue modulo $n^2$ if there exists a number $y \in \mathbb{Z}^{*}_{n^2}$ such that
+% \begin{equation}
+%     z = y^n \pmod{n^2},
+% \end{equation}
+% where $n=pq$ is the product of two large primes. DCRA states that distinguishing an $n$th residue modulo $n^2$ from non $n$th residues is a hard problem, and is shown to be a reduction of the
 
 \subsection{Paillier Encryption Scheme}
+The Paillier encryption scheme is an additively homomorphic encryption scheme which functions over a finite group $\mathbb{G}$, containing
+
+% TODO not true I think - just keep it simple instead - a subgroup where the DCRA holds and is of an unknown order, and another subgroup where discrete logarithms are easily computable.
+
+Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $n=pq$.
+A generator $g$ is also required for encryption, which is often set to $g=n+1$ when $p$ and $q$ are of equal bit length \cite{}.
+The public key is then given by $(n, g)$ and secret key by $(p, q)$.
+
+Encryption of a plaintext message $m \in \mathbb{Z}_n$, producing ciphertext $c \in \mathbb{Z}^{*}_{n^2}$, is computed by
+\begin{equation}
+    c = g^m r^n \pmod{n^2}
+\end{equation}
+for a randomly chosen $r \in \mathbb{Z}_{n}$.
+The $r^n$ term can be considered as the noise which hides the value $g^m \pmod{n^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
+The decryption of a ciphertext is computed by
+\begin{equation}
+    m = \frac{L(c^\lambda\pmod{n^2})}{L(g^\lambda\pmod{n^2})} \pmod{n}
+\end{equation}
+where $\lambda = \operatorfont{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{n}$.
+
+In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
+\begin{align}
+    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\pmod{n^2}) &= m_1+m_2\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\pmod{n^2}) &= m_1+m_2\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\pmod{n^2}) &= m_1m_2\pmod{n}\,.
+\end{align}
+
+The scheme is shown to be indistinguishable under the chosen plaintext attack model (IND-CPA), which is considered the strongest form of security acheivable by a homomorphic encryption scheme \cite{}.
 
 \subsection{Joye-Libert Privacy-Preserving Aggregation}
+The Joye-Libert private stream aggregation scheme allows, at each time-step, encrypted time-series values originating from $N$ different measuring parties, to be summed up and decrypted by an aggregator.
+Time-series values are encrypted by their measuring party's private encryption key, and decrypted by the aggregator using its private key.
+The scheme functions over the same finite group $\mathbb{G}$ as the Paillier encryption scheme above.
+
+A notable difference in key-generation for the aggregation scheme from a public-key scheme such as Paillier's scheme, is the requirement of an offline generation and distribution step by some trusted party.
+Similar to the Paillier scheme, key generation first requires choosing two sufficiently large, equal length, primes $p$ and $q$ and computing $n=pq$.
+In addition to $n$, a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{n^2}$ is defined, and the public key is set to $(n, H)$.
+The private keys are generated by choosing $N$ keys $sk_i,\,i \in \{1,\dots,N\}$ uniformly from $\mathbb{Z}_{n^2}$ and distributing them to all measuring parties, while the last key is set to
+\begin{equation}
+    sk_0 = -\sum^{N}_{i=1}sk_i \pmod{n^2}\,,
+\end{equation}
+and sent to the aggregator.
+
+Encryption of plaintext $m_{i,t} \in \mathbb{Z}_n$ to ciphertext $c_{i,t} \in \mathbb{Z}_{n^2}$ at time $t$ is computed by participant $i$ as
+\begin{equation}
+    c_{i,t} = (n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2}\,,
+\end{equation}
+As with the interpretation of the noise term in the Paillier scheme, here $H(t)^{sk_i}$ can be seen as noise which hides the easily computable discrete logarithm $g^{m_{i,t}} \pmod{n^2}$, where $g=n+1$.
+
+When all encryptions $c_{i,t},\,i \in \{1,\dots,N\}$ are sent to the aggregator, private summation and decryption are computed by the functions
+\begin{equation}
+    c_{t} = H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2}
+\end{equation}
+and
+\begin{equation}
+    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{agg-decryption}
+\end{equation}
+Correctness follows from $\sum^{N}_{i=0}sk_i = 0$, and therefore
+\begin{align}
+    H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} &\equiv H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
+    &\equiv H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
+    &\equiv (n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
+\end{align}
+which results in a solvable discrete logarithm by using \ref{agg-decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.
+
+The aggregation scheme is proven to achieve aggregator obliviousness (AO), which in that no corrupted colluding subset learns anything about the individual messages of the non-corrupted participants, other than the final sum of messages if the aggregator is corrupted, and is proven in the random oracle model.
 
@@
 Explain it in as an overview
+
+% \begin{algorithm}
+%     \caption{Paillier Key Generation}\label{paillier_key_gen}
+%     \begin{algorithmic}[1]
+%         \Procedure{PaillierKeyGen}{$security\_param$}
+%         \State $p,q \gets$ \Call{GeneratePrimes}{$security\_param$}
+%         \State $\lambda \gets$ \Call{lcm}{p,q}
+%         \State $pk \gets (n, n+1)$
+%         \State $sk \gets \lambda$
+%         \State \Return $(pk, sk)$
+%         \EndProcedure
+%     \end{algorithmic}
+% \end{algorithm}
 
@@
 \section{Introduction}
-The introduction should briefly place the study in a broad context and highlight why it is important.
+% The introduction should briefly place the study in a broad context and highlight why it is important.
 It should define the purpose of the work and its significance.
@@
 %=====================================
-%\externalbibliography{yes}
+\externalbibliography{yes}
 %\bibliography{your_external_BibTeX_file}
+\bibliography{BibTeX/PrivateEIFLocalisation}
 
@@
 %=====================================
-\begin{thebibliography}{999}
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book}
-Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-\end{thebibliography}
+% \begin{thebibliography}{999}
+% % Reference 1
+% \bibitem[Author1(year)]{ref-journal}
+% Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
+% % Reference 2
+% \bibitem[Author2(year)]{ref-book}
+% Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
+% \end{thebibliography}
 

### 2020-08-18 main.tex
Switched to automatica template

@@
-%  LaTeX support: latex@mdpi.com 
-%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).
+% autosam.tex
+% Annotated sample file for the preparation of LaTeX files
+% for the final versions of papers submitted to or accepted for 
+% publication in AUTOMATICA.
 
-%=================================================================
-\documentclass[sensors,article,submit,moreauthors,pdftex]{Definitions/mdpi}
+% See also the Information for Authors.
 
-% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'.
-The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}.
-This is especially recommended for submission to arXiv, where line numbers should be removed before posting.
-For preprints.org, the editorial staff will make this change immediately prior to posting.
+% Make sure that the zip file that you send contains all the 
+% files, including the files for the figures and the bib file.
 
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, ai, algorithms, allergies, analytica, animals, antibiotics, antibodies, antioxidants, applmech, applnano, applsci, arts, asc, asi, atmosphere, atoms, automation, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomedinformatics, biomimetics, biomolecules, biosensors, bloods, brainsci, breath, buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, civileng, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, cyber, dairy, data, dentistry, dermatopathology, designs, diabetology, diagnostics, digital, diseases, diversity, drones, earth, econometrics, ecologies, economies, education, ejbc, ejihpe, electricity, electrochem, electronicmat, electronics, endocrines, energies, engproc, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, fuels, futureinternet, futurephys, galaxies, games, gardens, gases, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, hearts, heritage, highthroughput, horticulturae, humanities, hydrogen, hydrology, ijerph, ijfs, ijgi, ijms, ijtpp, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jce, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jne, jnt, jof, joitmc, journalmedia, jpm, jrfm, jsan, land, languages, laws, life, literature, livers, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, ijns, neurosci, neuroglia, nitrogen, notspecified, nutrients, obesities, oceans, ohbm, osteology, optics, organics, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, pollutants, polymers, polysaccharides, preprints , proceedings, processes, prosthesis, proteomes, psych, psychiatryint, publications, quantumrep, quaternary, qubs, radiation, reactions, recycling, religions, remotesensing, reprodmed, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, soilsystems, solids, sports, standards, stats, surfaces, surgeries, suschem, sustainability, world, symmetry, systems, technologies, telecom, test, tourismhosp, toxics, toxins, transplantology, tropicalmed, universe, urbansci, uro, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj, women
+% Output produced with the elsart style file does not imitate the
+% AUTOMATICA style. The style file is generic for all Elsevier
+% journals and the output is laid out for easy copy editing. The
+% final document is produced from the source file in the
+% AUTOMATICA style at Elsevier.
 
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
-% supfile = supplementary materials
+% You may use the style file autart.cls to obtain a two-column 
+% document (see below) that more or less imitates the printed 
+% Automatica style. This may helpful to improve the formatting 
+% of the equations, tables and figures, and also serves to check 
+% whether the paper satisfies the length requirements.
 
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+% Please note: Authors must not create their own macros.
 
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+% For further information regarding the preparation of LaTeX files 
+% for Elsevier, please refer to the "Full Instructions to Authors" 
+% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
+% directory pub/styles, or from the internet (CTAN sites) on
+% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
+% tex-archive/macros/latex/contrib/supported/elsevier.
 
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
+%\documentclass{elsart}               % The use of LaTeX2e is preferred.
 
-%=================================================================
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{xx}
-\issuenum{1}
-\articlenumber{5}
-\pubyear{2020}
-\copyrightyear{2020}
-%\externaleditor{Academic Editor: name}
-\history{Received: date; Accepted: date; Published: date}
-%\updates{yes} % If there is an update available, un-comment this line
+\documentclass[twocolumn]{autart}    % Enable this line and disable the 
+                                     % preceding line to obtain a two-column 
+                                     % document whose style resembles the
+                                     % printed Automatica style.
 
-%% MDPI internal command: uncomment if new journal that already uses continuous page numbers 
-%\continuouspages{yes}
+\usepackage{graphicx}          % Include this line if your 
+                               % document contains figures,
+%\usepackage[dvips]{epsfig}    % or this line, depending on which
+                               % you prefer.
 
-%------------------------------------------------------------------
-% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
-%\pdfoutput=1
-
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx,epstopdf, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, soul, multirow, microtype, tikz, totcount, amsthm, hyphenat, natbib, hyperref, footmisc, url, geometry, newfloat, caption
+% User imported packages
+\usepackage{amsmath}
 \usepackage{amsfonts}
@@
 
-%=================================================================
-%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+\begin{document}
 
-%=================================================================
-% Full title of the paper (Capitalized)
-\Title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation}
+\begin{frontmatter}
+% Running title for regular 
+% papers but only if the title  
+% is over 5 words. Running title 
+% is not shown in output.
+%\runtitle{Insert a suggested running title}
 
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-9581-9937} % Add \orcidA{} behind the author's name
-\newcommand{\orcidauthorB}{0000-0001-8996-5738} % Add \orcidB{} behind the author's name
-\newcommand{\orcidauthorC}{0000-0001-9870-2331} % Add \orcidC{} behind the author's name
+\title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}} % Title, preferably not more than 10 words.
 
-% Authors, for the paper (add full first names)
-\Author{Marko Ristic $^{1}$\orcidA{}, Benjamin Noack $^{1}$\orcidB{} and Uwe D. Hanebeck $^{1,}$*\orcidC{}}
+\thanks[footnoteinfo]{This paper was not presented at any IFAC 
+meeting. Corresponding author Uwe~D.~Hanebeck. Tel. +49--721--608--43909.}
 
-% Authors, for metadata in PDF
-\AuthorNames{Marko Ristic, Benjamin Noack and Uwe D. Hanebeck}
+% Add the 
+% e-mail address 
+% (ead) as shown
+\author[ISAS]{Marko Ristic}\ead{marko.ristic@kit.edu},
+\author[ISAS]{Benjamin Noack}\ead{noack@kit.edu},
+\author[ISAS]{Uwe D. Hanebeck}\ead{uwe.hanebeck@kit.edu}
 
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address[1]{%
-$^{1}$ \quad Intelligent Sensor-Actuator-systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany; marko.ristic@kit.edu; noack@kit.edu; uwe.hanebeck@kit.edu}
+\address[ISAS]{Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}  % Please supply
 
-% Contact information of the corresponding author
-\corres{Correspondence: uwe.hanebeck@kit.edu; Tel.: +49--721--608--43909}
+% Five to ten keywords,  
+% chosen from the IFAC 
+% keyword list or with the 
+% help of the Automatica 
+% keyword wizard
+\begin{keyword}
+System state estimation; Data privacy; Sensor fusion; Kalman filters.
+\end{keyword}
 
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
+\begin{abstract} % Abstract of not more than 200 words.
+Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
 Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
@@
 The security requirements, leakage, and cryptographic proof are given for the private filter and weighted aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
-Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.}
+Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
+\end{abstract}
 
-% Keywords
-\keyword{Extended Kalman Filter; Secure Localisation; Private Aggregation}
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences:
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data:
-%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately.
-If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal.
-In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}
-
-%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
-
-%\setcounter{secnumdepth}{4}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{frontmatter}
 
@@
 \section{Private Weighted Aggregation Preliminaries}
+% TODO define IND-CPA brielfy, AO and our version of AO *HERE* are reffer to it later
+
 Our weighted aggregation method relies on the decisional composite residuosity assumption (DCRA) originally defined by Paillier in \cite{paillierPublicKeyCryptosystemsBased1999}.
@@
 
-<Rest is template>
+%---Rest is template---
 
-\section{How to Use this Template}
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions for authors page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX related questions please contact latex@mdpi.com.
-%The order of the section titles is: Introduction, Materials and Methods, Results, Discussion, Conclusions for these journals: aerospace,algorithms,antibodies,antioxidants,atmosphere,axioms,biomedicines,carbon,crystals,designs,diagnostics,environments,fermentation,fluids,forests,fractalfract,informatics,information,inventions,jfmk,jrfm,lubricants,neonatalscreening,neuroglia,particles,pharmaceutics,polymers,processes,technologies,viruses,vision
+% \section{Introduction}
+% Video, patres conscripti, in me omnium vestrum ora atque oculos esse 
+% conversos, video vos non solunn de vestro ac rei publicae, verum 
+% etiam, si id depulsum sit, de meo periculo esse sollicitos. Est mihi 
+% iucunda in malis et grata in dolore vestra erga me voluntas, sed eam, 
+% per deos inmortales, deponite atque obliti salutis meae de vobis ac 
+% de vestris liberis cogitate. Mihi si haec condicio consulatus data 
+% est, ut omnis acerbitates, onunis dolores cruciatusque perferrem, 
+% feram non solum fortiter, verum etiam lubenter, dum modo meis 
+% laboribus vobis populoque Romano dignitas salusque pariatur.
 
-\section{Introduction}
-% The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-And now citing a book reference \cite{ref-book}.
-Please use the command \citep{ref-journal} for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Languages, Laws, Religions, Risks, Social Sciences.
+% \begin{figure}
+% \begin{center}
+% \includegraphics[height=4cm]{jcaesar.eps}    % The printed column  
+% \caption{Gaius Julius Caesar, 100--44 B.C.}  % width is 8.4 cm.
+% \label{fig1}                                 % Size the figures 
+% \end{center}                                 % accordingly.
+% \end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+% % OR
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\begin{quote}
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\end{quote}
+% %\begin{figure}
+% %\begin{center}
+% %\epsfig{file=jcaesar,width=7cm}
+% %\caption{Gaius Julius Caesar, 100--44 B.C.}
+% %\label{fig1}
+% %\end{center}
+% %\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Subsection}
-\unskip
-\subsubsection{Subsubsection}
+% \subsection{A subsection}
+% Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
+% and philosopher.  A major figure in the last years of the Republic, 
+% he is best known for his orations against Catiline\footnote{
+% This footnote should be very brief.}
+% and for his mastery of Latin prose \cite{Heritage:92}. He was a 
+% contemporary of Julius Caesar (Fig.~\ref{fig1}).
 
-Bulleted lists look like this:
-\begin{itemize}[leftmargin=*,labelsep=5.8mm]
-\item	First bullet
-\item	Second bullet
-\item	Third bullet
-\end{itemize}
+% \section{The argument}
+% Some words might be appropriate describing equation~(\ref{e1}), if 
+% we had but time and space enough.
+% \begin{equation} \label{e1}
+% {{\partial F}\over {\partial t}} =
+% D{{\partial^2 F}\over {\partial x^2}}.
+% \end{equation}
+% See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and 
+% \cite{Pow:85}.
+% This equation goes far beyond the celebrated theorem ascribed to the great
+% Pythagoras by his followers.
+% \begin{thm}
+% The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
+% of the lengths of the other two sides.
+% \end{thm}
+% \section{Epilogue}
+% A word or two to conclude, and this even includes some inline 
+% maths:  $R(x,t)\sim t^{-\beta}g(x/t^\alpha)\exp(-|x|/t^\alpha)$.
 
-Numbered lists can be added as follows:
-\begin{enumerate}[leftmargin=*,labelsep=4.9mm]
-\item	First item 
-\item	Second item
-\item	Third item
-\end{enumerate}
+\begin{ack}                               % Place acknowledgements
+Partially supported by the Roman Senate.  % here.
+\end{ack}
 
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=2 cm]{Definitions/logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-
-Text
-
-Text
-
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g., \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-entry 1		& data			& data\\
-entry 2		& data			& data\\
-\bottomrule
-\end{tabular}
-\end{table}
-
-Text
-
-Text
-
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\textwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\textwidth}{1pt}
-%\end{listing}
-
-\subsection{Formatting of Mathematical Components}
-
-This is an example of an equation:
-
-\begin{equation}
-a + b = c
-\end{equation}
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
-
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
-
-The text continues here. Proofs must be formatted as follows:
-
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Materials and Methods}
-
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
-
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
-
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions}
-
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following are available online at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title.}
-
-% Only for the journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following are available at \linksupplementary{s1}, Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work reported.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflict of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript, or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, or in the decision to publish the results''.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent 
-\begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & linear dichroism
-\end{tabular}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendix
-\section{}
-\unskip
-\subsection{}
-The appendix is an optional section that can contain details and data supplemental to the main text.
-For example, explanations of experimental details that would disrupt the flow of the main text, but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data is shown in the main text can be added here if brief, or as Supplementary data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-\section{}
-All appendix sections must be cited in the main text. In the appendixes, Figures, Tables, etc. should be labeled starting with `A', e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-\externalbibliography{yes}
-%\bibliography{your_external_BibTeX_file}
+\bibliographystyle{plain}        % Include this if you use bibtex 
+                                 % and a bib file to produce the 
+                                 % bibliography (preferred). The
+                                 % correct style is generated by
+                                 % Elsevier at the time of printing.
 \bibliography{BibTeX/PrivateEIFLocalisation}
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-% \begin{thebibliography}{999}
-% % Reference 1
-% \bibitem[Author1(year)]{ref-journal}
-% Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% % Reference 2
-% \bibitem[Author2(year)]{ref-book}
-% Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% \end{thebibliography}
+%\begin{thebibliography}{99}     % Otherwise use the  
+                                 % thebibliography environment.
+                                 % Insert the full references here.
+                                 % See a recent issue of Automatica 
+                                 % for the style.
+%  \bibitem[Heritage, 1992]{Heritage:92}
+%     (1992) {\it The American Heritage. 
+%     Dictionary of the American Language.}
+%     Houghton Mifflin Company.
+%  \bibitem[Able, 1956]{Abl:56}
+%     B.~C.~Able (1956). Nucleic acid content of macroscope. 
+%     {\it Nature 2}, 7--9. 
+%  \bibitem[Able {\em et al.}, 1954]{AbTaRu:54}   
+%     B.~C. Able, R.~A. Tagg, and M.~Rush (1954).
+%     Enzyme-catalyzed cellular transanimations.
+%     In A.~F.~Round, editor, 
+%     {\it Advances in Enzymology Vol. 2} (125--247). 
+%     New York, Academic Press.
+%  \bibitem[R.~Keohane, 1958]{Keo:58}
+%     R.~Keohane (1958).
+%     {\it Power and Interdependence: 
+%     World Politics in Transition.}
+%     Boston, Little, Brown \& Co.
+%  \bibitem[Powers, 1985]{Pow:85}
+%     T.~Powers (1985).
+%     Is there a way out?
+%     {\it Harpers, June 1985}, 35--47.
 
-% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
-For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
+%\end{thebibliography}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-\sampleavailability{Samples of the compounds ...... are available from the authors.}
-
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+\section{A summary of Latin grammar}    % Each appendix must have a short title.
+\section{Some Latin vocabulary}         % Sections and subsections are supported  
+                                        % in the appendices.
 \end{document}

### 2020-08-19 main.tex
Continued on aggregation section Added tikz image to show the aggregation protocol Moved the planned typiing of IND-CPA and AO games to the appendix Added some (to-be-moved later) tikz .tex files in the images folder

@@
 \usepackage{algpseudocode}
+\usepackage{tikz}
+\usepackage{environ}
+\usepackage{layouts}
+
+\makeatletter
+\newsavebox{\measure@tikzpicture}
+\NewEnviron{scaletikzpicturetowidth}[1]{%
+  \def\tikz@width{#1}%
+  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
+  \BODY
+  \end{lrbox}%
+  \pgfmathparse{#1/\wd\measure@tikzpicture}%
+  \edef\tikzscale{\pgfmathresult}%
+  \BODY
+}
+\makeatother
 
@@
 Section Summary
+%In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute the measurement covariance and measurement vector homomorphically at each sensor, and allow the navigator to update their
 
@@
 
-\section{Problem Statement}
+\section{Problem Statement} \label{sec:problem_statement}
 
@@
 
-\section{Private Weighted Aggregation Preliminaries}
-% TODO define IND-CPA brielfy, AO and our version of AO *HERE* are reffer to it later
+\section{Privacy-Preserving Weighted Aggregation}
+For achieveing the goal of private localisation defined in Section \ref{sec:problem_statement} we require a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a privacy-preserving aggregation scheme.
+In our case, weights $\omega_1, \dots , \omega_m$ are encrypted and broadcast by the navigator, linear combinations $\sum^m_{j=1}x_{j,i}^{(t)}\omega_i$ are computed by the sensors $i \in \{1, \dots ,n\}$ at time $t$, and aggregation is computed back at the navigator.
+This has been summarized in Figure \ref{fig:agg_steps}.
+In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute measurement covariances and measurement vectors homomorphically, and update the Extended Information Filter while preserving privacy.
+
+\begin{figure}[htbp]
+\centering
+\vspace{\baselineskip}
+\begin{tikzpicture}[scale=0.75]
+    % Step 1
+    \node at (5,22.5) {1. Broadcast and linear combinations step};
+    % Navigator
+    \node at (1.5,19.25) {\small Navigator};
+    \fill (1.5,18.25) [blue!40] ellipse (0.5 and 0.5);
+    % Sensors
+    \node at (7.75,21.75) {\small Sensor $1$};
+    \fill [red!40] (6.125,19.75) rectangle (9.375,21.25);
+    \node at (7.75,20.5) {\small $\displaystyle y_1 = \sum^m_{i=1}x_{i,1}^{(t)}\omega_i$};
+    \node at (7.75,14.75) {\small Sensor $n$};
+    \fill [red!40] (6.125,15.25) rectangle (9.375,16.75);
+    \node at (7.75,16) {\small $\displaystyle y_n = \sum^m_{i=1}x_{i,n}^{(t)}\omega_i$};
+    \fill [black] (7.75,18.75) circle (0.05);
+    \fill [black] (7.75,17.75) circle (0.05);
+    \fill [black] (7.75,18.25) circle (0.05);
+    % Lines
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18.5) (6,20.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18) (6,16.25)};
+    \node at (4,20.25) {$(\omega_1,\dots ,\omega_m)$};
+    \node at (4,16.25) {$(\omega_1,\dots ,\omega_m)$};
+
+    % Step 2
+    \node at (5,13.25) {2. Aggregation step};
+    % Navigator
+    \node at (3,10.75) {\small Navigator};
+    \fill [blue!40] (0.625,8.75) rectangle (5.375,10.25);
+    \node at (3,9.5) {\small $\displaystyle \sum^{n}_{j=1}\sum^{m}_{i=1} x_{i,j}^{(t)}\omega_i = \sum^n_{i=1}y^{(t)}_{i}$};
+    % Sensors
+    \node at (8.5,12.5) {\small Sensor $1$};
+    \fill  (8.5,7.5) [red!40] ellipse (0.5 and 0.5);
+    \node at (8.5,6.5) {\small Sensor $n$};
+    \fill  (8.5,11.5) [red!40] ellipse (0.5 and 0.5);
+    \fill [black] (8.5,10) circle (0.05);
+    \fill [black] (8.5,9) circle (0.05);
+    \fill [black] (8.5,9.5) circle (0.05);
+    % Lines
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,11.25) (5.5,10)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,7.75) (5.5,9)};
+    \node at (6.5,11.5) {$y_1$};
+    \node at (6.5,7.5) {$y_n$};
+
+    % Bounding rectangles
+    \draw [gray] (0,23.25) rectangle (10,14.25);
+    \draw [gray] (0,14) rectangle (10,5.5);
+\end{tikzpicture}
+\vspace{\baselineskip}
+\caption{Required weighted aggregation scheme}
+\label{fig:agg_steps}
+\end{figure}
+
+The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
+Before defining the desired security of our scheme, we note that it has properties of both an additive homomorphic encryption scheme, and a privacy-preserving aggregation scheme.
+The typical security requirement for a homomorphic encryption scheme is Indistinguishability under the Chosen Plaintext Attack model (IND-CPA) \cite{}.
+Informally, IND-CPA states that an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unkonwn plaintext message when they learn only its encryption.
+The more formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
+Privacy-preserving aggregation, without weights, aims for the security goal of Aggregator Obliviousness (AO) \cite{}.
+AO states that no colluding subset of participants gains any additional information about the aggregation values from the remaining parties, given only their encryption, with the exception of learning only their sum if the aggregator is among the colluding subset.
+The game for AO has been given in Appendix \ref{app:ao}.
+
+Our desired weighted aggregation method has two security goals.
+Firstly, that encrypted values are indistinguishable from random to sensors, and secondly, that individual weighted values remain unknown to the navigator, who learns only the final weighted sum.
+From the definitions above, it is clear that an IND-CPA secure encryption of navigator produced weights is sufficient for the first goal, while the definition of AO needs to be altered to incooporate weights for the second.
+
+Such an altered aggregation games has been defined in \cite{alexandruEncryptedCooperativeControl2019} as private Weighted Sum Aggregator Obliviousness (pWSAO).
+In overview, the game states that given given weights --- not the case, need to define our own slightly different version (but we get to name it something else at least)
+
+and is defined as follows
 
@@
 \begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\pmod{n^2}) &= m_1+m_2\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\pmod{n^2}) &= m_1+m_2\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\pmod{n^2}) &= m_1m_2\pmod{n}\,.
+    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{n^2}) &= m_1m_2\!\pmod{n}\,.
 \end{align}
@@
 \begin{equation}
-    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{agg-decryption}
+    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{eqn:agg_decryption}
 \end{equation}
@@
 \begin{align}
-    H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} &\equiv H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
-    &\equiv H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
-    &\equiv (n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
+    &H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} \\
+    \equiv &H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
+    \equiv &H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
+    \equiv &(n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
 \end{align}
-which results in a solvable discrete logarithm by using \ref{agg-decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.
+which results in a solvable discrete logarithm by using \eqref{eqn:agg_decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.
 
@@
 % Maybe rename this to Our Scheme or something like that
-\section{Private Weighted Aggregation}
+\section{Our Scheme}
 Explain it in as an overview
@@
 
-\section{Private Localisation Preliminaries}
+\section{Private Localisation}
 
@@
 
-\section{Private Localisation with Privacy-Preserving Sensors}
+\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
 Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
@@
 
+% Each appendix must have a short title.
+% Sections and subsections are supported
+% in the appendices.
 \appendix
-\section{A summary of Latin grammar}    % Each appendix must have a short title.
-\section{Some Latin vocabulary}         % Sections and subsections are supported  
-                                        % in the appendices.
+\section{Indistinguishability under the Chosen Plaintext Attack (IND-CPA)} \label{app:ind-cpa}
+\section{Aggregator Obliviousness (AO)} \label{app:ao}
+
 \end{document}

### 2020-08-20 main.tex
Defined encryptino scheme and security game required for our weighted aggregation - still need to make it fit into the section a bit nicer (before and after text needs to be be updated - A couple of the latex font formats are ugly and need to be fixed

@@
 
-%\documentclass{elsart}               % The use of LaTeX2e is preferred.
+% The use of LaTeX2e is preferred.
+%\documentclass{elsart}
 
-\documentclass[twocolumn]{autart}    % Enable this line and disable the 
+% Enable this line and disable the 
 % preceding line to obtain a two-column 
@@
 % printed Automatica style.
+\documentclass[twocolumn]{autart}
 
-\usepackage{graphicx}          % Include this line if your 
+% Include this line if your 
 % document contains figures,
-%\usepackage[dvips]{epsfig}    % or this line, depending on which
+\usepackage{graphicx}
+% or this line, depending on which
 % you prefer.
+%\usepackage[dvips]{epsfig}
 
@@
 \usepackage{amsfonts}
+\usepackage{mathtools}
 \usepackage{algorithm}
@@
 \usepackage{tikz}
-\usepackage{environ}
-\usepackage{layouts}
 
-\makeatletter
-\newsavebox{\measure@tikzpicture}
-\NewEnviron{scaletikzpicturetowidth}[1]{%
-  \def\tikz@width{#1}%
-  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
-  \BODY
-  \end{lrbox}%
-  \pgfmathparse{#1/\wd\measure@tikzpicture}%
-  \edef\tikzscale{\pgfmathresult}%
-  \BODY
-}
-\makeatother
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
 
@@
 
-\title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}} % Title, preferably not more than 10 words.
+% Title, preferably not more than 10 words.
+\title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}}
 
@@
 
-\address[ISAS]{Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}  % Please supply
+% Please supply
+\address[ISAS]{Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
 
@@
 
-\begin{abstract} % Abstract of not more than 200 words.
+% Abstract of not more than 200 words.
+\begin{abstract}
 Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
@@
 For achieveing the goal of private localisation defined in Section \ref{sec:problem_statement} we require a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a privacy-preserving aggregation scheme.
-In our case, weights $\omega_1, \dots , \omega_m$ are encrypted and broadcast by the navigator, linear combinations $\sum^m_{j=1}x_{j,i}^{(t)}\omega_i$ are computed by the sensors $i \in \{1, \dots ,n\}$ at time $t$, and aggregation is computed back at the navigator.
+In our case, at time $t$, weights $\omega_1^{(t)}, \dots , \omega_m^{(t)}$ are encrypted and broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by the sensors $i \in \{1, \dots ,n\}$, and aggregation is computed back at the navigator.
 This has been summarized in Figure \ref{fig:agg_steps}.
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[scale=0.75]
+\begin{tikzpicture}[font=\footnotesize,scale=0.75]
     % Step 1
-    \node at (5,22.5) {1. Broadcast and linear combinations step};
+    \node at (5,22.5) {\small 1. Broadcast and linear combinations step};
     % Navigator
-    \node at (1.5,19.25) {\small Navigator};
-    \fill (1.5,18.25) [blue!40] ellipse (0.5 and 0.5);
+    \node at (1.25,19.25) {Navigator};
+    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
     % Sensors
-    \node at (7.75,21.75) {\small Sensor $1$};
-    \fill [red!40] (6.125,19.75) rectangle (9.375,21.25);
-    \node at (7.75,20.5) {\small $\displaystyle y_1 = \sum^m_{i=1}x_{i,1}^{(t)}\omega_i$};
-    \node at (7.75,14.75) {\small Sensor $n$};
-    \fill [red!40] (6.125,15.25) rectangle (9.375,16.75);
-    \node at (7.75,16) {\small $\displaystyle y_n = \sum^m_{i=1}x_{i,n}^{(t)}\omega_i$};
-    \fill [black] (7.75,18.75) circle (0.05);
-    \fill [black] (7.75,17.75) circle (0.05);
-    \fill [black] (7.75,18.25) circle (0.05);
+    \node at (7.5,21.75) {Sensor $1$};
+    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
+    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
+    \node at (7.5,14.75) {Sensor $n$};
+    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
+    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
+    \fill [black] (7.5,18.75) circle (0.05);
+    \fill [black] (7.5,17.75) circle (0.05);
+    \fill [black] (7.5,18.25) circle (0.05);
     % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18.5) (6,20.25)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(2,18) (6,16.25)};
-    \node at (4,20.25) {$(\omega_1,\dots ,\omega_m)$};
-    \node at (4,16.25) {$(\omega_1,\dots ,\omega_m)$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
+    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
+    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
 
     % Step 2
-    \node at (5,13.25) {2. Aggregation step};
+    \node at (5,13.25) {\small 2. Aggregation step};
     % Navigator
-    \node at (3,10.75) {\small Navigator};
-    \fill [blue!40] (0.625,8.75) rectangle (5.375,10.25);
-    \node at (3,9.5) {\small $\displaystyle \sum^{n}_{j=1}\sum^{m}_{i=1} x_{i,j}^{(t)}\omega_i = \sum^n_{i=1}y^{(t)}_{i}$};
+    \node at (3.25,10.75) {Navigator};
+    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
+    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
     % Sensors
-    \node at (8.5,12.5) {\small Sensor $1$};
-    \fill  (8.5,7.5) [red!40] ellipse (0.5 and 0.5);
-    \node at (8.5,6.5) {\small Sensor $n$};
-    \fill  (8.5,11.5) [red!40] ellipse (0.5 and 0.5);
-    \fill [black] (8.5,10) circle (0.05);
-    \fill [black] (8.5,9) circle (0.05);
-    \fill [black] (8.5,9.5) circle (0.05);
+    \node at (8.75,12.5) {Sensor $1$};
+    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
+    \node at (8.75,6.5) {Sensor $n$};
+    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
+    \fill [black] (8.75,10) circle (0.05);
+    \fill [black] (8.75,9) circle (0.05);
+    \fill [black] (8.75,9.5) circle (0.05);
     % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,11.25) (5.5,10)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8,7.75) (5.5,9)};
-    \node at (6.5,11.5) {$y_1$};
-    \node at (6.5,7.5) {$y_n$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
+    \node at (6.75,11.5) {$y_1^{(t)}$};
+    \node at (6.75,7.5) {$y_n^{(t)}$};
 
@@
 \vspace{\baselineskip}
-\caption{Required weighted aggregation scheme}
+\caption{Required weighted aggregation steps at time $t$}
 \label{fig:agg_steps}
@@
 The typical security requirement for a homomorphic encryption scheme is Indistinguishability under the Chosen Plaintext Attack model (IND-CPA) \cite{}.
-Informally, IND-CPA states that an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unkonwn plaintext message when they learn only its encryption.
-The more formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
+Informally, IND-CPA states that an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
+The formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
 Privacy-preserving aggregation, without weights, aims for the security goal of Aggregator Obliviousness (AO) \cite{}.
-AO states that no colluding subset of participants gains any additional information about the aggregation values from the remaining parties, given only their encryption, with the exception of learning only their sum if the aggregator is among the colluding subset.
-The game for AO has been given in Appendix \ref{app:ao}.
+AO states that no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
+The security game for AO has been given in Appendix \ref{app:ao}.
 
-Our desired weighted aggregation method has two security goals.
-Firstly, that encrypted values are indistinguishable from random to sensors, and secondly, that individual weighted values remain unknown to the navigator, who learns only the final weighted sum.
-From the definitions above, it is clear that an IND-CPA secure encryption of navigator produced weights is sufficient for the first goal, while the definition of AO needs to be altered to incooporate weights for the second.
+The desired security of our weighted encryption scheme has two goals:
 
-Such an altered aggregation games has been defined in \cite{alexandruEncryptedCooperativeControl2019} as private Weighted Sum Aggregator Obliviousness (pWSAO).
-In overview, the game states that given given weights --- not the case, need to define our own slightly different version (but we get to name it something else at least)
+\begin{description}
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j$ from receiving only their encryptions, and encryptions from any previous timesteps.
+    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ and encryptions from any previous timesteps.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
+Note that this implies that $\sum^m_{j=1}x^{(t)}_{1,j}$ may be learned by the colluding subset given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ cannot be learned regardless of weight choice.
+\end{description}
 
-and is defined as follows
+From these definitions it is clear that IND-CPA security of weight encryptions is sufficient for the first requirement, while AO is not sufficient for the second.
+Instead, we give a definition for linear-combination aggregator oblivious Encryption, and the accompanying security game which captures the additional weights, and modified leakage.
+
+\subsection{Linear-Combination Aggregator Oblivious Encryption}
+We define a linear-combination aggregator oblivious encryption scheme as a tuple of the four algorithms $(\operatorfont{Setup}, \operatorfont{Enc}, \operatorfont{CombEnc}, \operatorfont{AggDec})$:
+\begin{description}
+    \item[$\operatorfont{Setup}(\kappa)$] On input of security paramater $\kappa$, generate the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i$, $(1\leq i \leq n)$.
+    \item[$\operatorfont{Enc}(pk_0, sk_0, \omega)$] At time $t$, the aggregator encrypts weight $\omega$ with its public key $pk_0$, and obtains the encryption $\mathcal{E}_{pk_0}(\omega)$.
+    \item[$\operatorfont{CombEnc}(pk_0, sk_i, \mathcal{E}(\omega_1),\dots,\mathcal{E}(\omega_m), x_{i,1},\dots,x_{i,m})$] At time $t$, user $i$ computes the encrypted linear combination $y_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ using its secret key $sk_i$ as $y_i = \operatorfont{CombEnc}(pk_0, sk_i, \mathcal{E}(\omega_1),\dots,\mathcal{E}(\omega_m), x_{i,1},\dots,x_{i,m})$.
+    \item[$\operatorfont{AggDec}(pk_0, sk_0, y_1,\dots,y_n)$] At time $t$, the aggregator computes the aggregation of linear combinations using its private key $sk_0$, as $\sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \operatorfont{AggDec}(pk_0, sk_0, y_1,\dots,y_n)$.
+\end{description}
+
+We define the security notion of Linear-Combination Agregator Obliviousness (LCAO) as the following game between attacker and challenger:
+
+\begin{description}
+    \item[Setup] The challenger runs the $\operatorfont{Setup}$ algorithm and gives $pk_0$ to the attacker
+    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
+    \begin{enumerate}
+        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ for a unique pair $(i,t)$ and is given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and thesecret key $sk_i$.
+        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
+    \end{enumerate} 
+    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $U \subseteq S$ where $S$ is the complete set of users for which no combine queries for time $t^*$ and no compromise queries are made for the duration of the game.
+The attacker then chooses two series of tuples
+    \begin{equation*}
+        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})\,|\,i \in U\rangle
+    \end{equation*}
+    and
+    \begin{equation*}
+        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i,1}',\dots,x_{i,m}')\,|\, i \in U\rangle\,,
+    \end{equation*}
+    and gives them to the challenger. In the case that $0 \in U$ (\textit{i.e.} the aggregator is compromised) and $U = S$, it is additionally required that
+    \begin{equation*}
+        \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}'\omega_j'\,.
+    \end{equation*}
+    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
+    \begin{equation*}
+        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)\,|\,i\in U\rangle
+    \end{equation*}
+    if $b=0$, or 
+    \begin{equation*}
+        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}'\omega_j')\,|\,i\in U\rangle
+    \end{equation*}
+    otherwise.
+    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requiremets in the Challenge stage. That is, $U \subseteq S$.
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
+    \begin{equation*}
+        \operatorfont{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \operatorfont{Pr}[b'=b] - \frac{1}{2}\right\rvert\,.
+    \end{equation*} 
+\end{description}
+
+We say that an encryption scheme meets the security of LCAO if no probabilistic-time adversary has more than negligable advantage in winning this security game.
 
@@
 Both of these schemes base their security on the DCRA, and their descriptions are given briefly below before defining our weighted aggregation scheme.
-
-% A number $z$ is said to be an $n$th residue modulo $n^2$ if there exists a number $y \in \mathbb{Z}^{*}_{n^2}$ such that
-% \begin{equation}
-%     z = y^n \pmod{n^2},
-% \end{equation}
-% where $n=pq$ is the product of two large primes. DCRA states that distinguishing an $n$th residue modulo $n^2$ from non $n$th residues is a hard problem, and is shown to be a reduction of the
 

### 2020-08-21 main.tex
Finished cryptographic requirements and definitions, as well as Paillier and Joy-Libert descriptions Rearranged crypto section to have preliminaries section again - put security notions IND-CPA and AO there, and the Paillier and Joye-Libert schemes Flows much better with introducing our cryptographic problem, and defining LCAO security

@@
 
-\section{Privacy-Preserving Weighted Aggregation}
-For achieveing the goal of private localisation defined in Section \ref{sec:problem_statement} we require a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a privacy-preserving aggregation scheme.
-In our case, at time $t$, weights $\omega_1^{(t)}, \dots , \omega_m^{(t)}$ are encrypted and broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by the sensors $i \in \{1, \dots ,n\}$, and aggregation is computed back at the navigator.
+%  .d8888b.                            888                 8888888b.                  888 d8b
+% d88P  Y88b                           888                 888   Y88b                 888 Y8P
+% 888    888                           888                 888    888                 888
+% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.
+% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
+% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888
+% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888
+%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888
+%                         888 888
+%                    Y8b d88P 888
+%                     "Y88P"  888
+\section{Cryptography Preliminaries}
+When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
+
+% Quickly define homomorphic encryption and private aggregation here??
+
+\subsection{Security Notions}
+The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
+The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{}.
+\begin{definition}
+An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
+
+The formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
+\end{definition}
+Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{}. 
+\begin{definition}
+An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
+
+The formal security game for AO has been given in Appendix \ref{app:ao}.
+\end{definition}
+
+\subsection{Paillier Encryption Scheme}
+The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
+Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
+A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{}.
+The public key is defined by $(N, g)$ and secret key by $(p, q)$.
+
+Encryption of a plaintext message $m \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
+\begin{equation}
+    c = g^m r^N \pmod{N^2}
+\end{equation}
+for a randomly chosen $r \in \mathbb{Z}_{N}$.
+$r^N$ can be considered the noise term which hides the value $g^m \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
+The decryption of a ciphertext is computed by
+\begin{equation}
+    m = \frac{L(c^\lambda\pmod{n^2})}{L(g^\lambda\pmod{n^2})} \pmod{n}
+\end{equation}
+where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{n}$.
+
+In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
+\begin{align}
+    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{n^2}) &= m_1m_2\!\pmod{n}\,.
+\end{align}
+
+\subsection{Joye-Libert Private Aggregation Scheme}
+The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO.
+Similarly to the Paillier scheme, it bases its security on the DCRA.
+A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.
+
+Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
+Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}$ is defined, and the public key is set to $(N, H)$.
+$n$ private keys are generated by choosing $sk_i,\,1\leq i \leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
+\begin{equation}
+    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
+\end{equation}
+and sent to the aggregator.
+
+Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at time $t$ is computed by user $i$ as
+\begin{equation}
+    c^{(t)}_{i} = (N+1)^{m^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
+\end{equation}
+where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{m^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
+
+When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, private summation and decryption are computed by the functions
+\begin{equation}
+    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
+\end{equation}
+and
+\begin{equation}
+    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
+\end{equation}
+Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
+\begin{align*}
+    &H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} \\
+    \equiv &H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
+    \equiv &H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
+    \equiv &(n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
+\end{align*}
+removing all noise terms.
+
+%  .d8888b.                            888                 8888888b.                  888
+% d88P  Y88b                           888                 888   Y88b                 888
+% 888    888                           888                 888    888                 888
+% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  88888b.
+% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d88""88b 888 "88b
+% 888    888 888     888  888 888  888 888   888  888      888        888    888  888 888  888
+% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y88..88P 888 d88P
+%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y88P"  88888P"
+%                         888 888
+%                    Y8b d88P 888
+%                     "Y88P"  888
+\section{Private Linear-Combination Aggregation}
+For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation.
+In the context of navigation, $m$ weights $\omega_1^{(t)}, \dots , \omega_m^{(t)}$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$.
 This has been summarized in Figure \ref{fig:agg_steps}.
-In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute measurement covariances and measurement vectors homomorphically, and update the Extended Information Filter while preserving privacy.
+In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.
 
@@
 \vspace{\baselineskip}
-\caption{Required weighted aggregation steps at time $t$}
+\caption{Required linear-combination aggregation steps at time $t$}
 \label{fig:agg_steps}
@@
 
-The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-Before defining the desired security of our scheme, we note that it has properties of both an additive homomorphic encryption scheme, and a privacy-preserving aggregation scheme.
-The typical security requirement for a homomorphic encryption scheme is Indistinguishability under the Chosen Plaintext Attack model (IND-CPA) \cite{}.
-Informally, IND-CPA states that an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
-The formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
-Privacy-preserving aggregation, without weights, aims for the security goal of Aggregator Obliviousness (AO) \cite{}.
-AO states that no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
-The security game for AO has been given in Appendix \ref{app:ao}.
+To perform the protocol from Figure \ref{fig:agg_steps} in a secure manner, we must first describe the security properties we aim to achieve.
+Broadly speaking, we want a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme.
+That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations.
+This can be summarised by the two informal security notions:
+\begin{description}
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous timesteps, and the ability to encrypt plaintexts of their choice.
+    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous timesteps.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
+Note that this implies that $\sum^m_{j=1}x^{(t)}_{1,j}$ may be learned by the colluding subset given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private.
+\end{description}
 
-The desired security of our weighted encryption scheme has two goals:
+From these definitions, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
+To formalise the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
+
+% 888      .d8888b.        d8888  .d88888b.
+% 888     d88P  Y88b      d88888 d88P" "Y88b
+% 888     888    888     d88P888 888     888
+% 888     888           d88P 888 888     888
+% 888     888          d88P  888 888     888
+% 888     888    888  d88P   888 888     888
+% 888     Y88b  d88P d8888888888 Y88b. .d88P
+% 88888888 "Y8888P" d88P     888  "Y88888P"
+
+\subsection{Linear-Combination Aggregator Oblivious Encryption}
+We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
+For the sake of readbility, we have ommited the time variable $t$ from values $\omega_j$ and $x_{i,j}$.
 
 \begin{description}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j$ from receiving only their encryptions, and encryptions from any previous timesteps.
-    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ and encryptions from any previous timesteps.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
-Note that this implies that $\sum^m_{j=1}x^{(t)}_{1,j}$ may be learned by the colluding subset given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ cannot be learned regardless of weight choice.
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
+    \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j$ using its private key $sk_0$.
 \end{description}
 
-From these definitions it is clear that IND-CPA security of weight encryptions is sufficient for the first requirement, while AO is not sufficient for the second.
-Instead, we give a definition for linear-combination aggregator oblivious Encryption, and the accompanying security game which captures the additional weights, and modified leakage.
-
-\subsection{Linear-Combination Aggregator Oblivious Encryption}
-We define a linear-combination aggregator oblivious encryption scheme as a tuple of the four algorithms $(\operatorfont{Setup}, \operatorfont{Enc}, \operatorfont{CombEnc}, \operatorfont{AggDec})$:
-\begin{description}
-    \item[$\operatorfont{Setup}(\kappa)$] On input of security paramater $\kappa$, generate the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i$, $(1\leq i \leq n)$.
-    \item[$\operatorfont{Enc}(pk_0, sk_0, \omega)$] At time $t$, the aggregator encrypts weight $\omega$ with its public key $pk_0$, and obtains the encryption $\mathcal{E}_{pk_0}(\omega)$.
-    \item[$\operatorfont{CombEnc}(pk_0, sk_i, \mathcal{E}(\omega_1),\dots,\mathcal{E}(\omega_m), x_{i,1},\dots,x_{i,m})$] At time $t$, user $i$ computes the encrypted linear combination $y_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ using its secret key $sk_i$ as $y_i = \operatorfont{CombEnc}(pk_0, sk_i, \mathcal{E}(\omega_1),\dots,\mathcal{E}(\omega_m), x_{i,1},\dots,x_{i,m})$.
-    \item[$\operatorfont{AggDec}(pk_0, sk_0, y_1,\dots,y_n)$] At time $t$, the aggregator computes the aggregation of linear combinations using its private key $sk_0$, as $\sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \operatorfont{AggDec}(pk_0, sk_0, y_1,\dots,y_n)$.
-\end{description}
-
-We define the security notion of Linear-Combination Agregator Obliviousness (LCAO) as the following game between attacker and challenger:
+Next, we formalise the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
 
 \begin{description}
-    \item[Setup] The challenger runs the $\operatorfont{Setup}$ algorithm and gives $pk_0$ to the attacker
+    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $pk_0$ to the attacker
     \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
@@
         \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ for a unique pair $(i,t)$ and is given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and thesecret key $sk_i$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ for a unique pair $(i,t)$ and is given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
@@
     otherwise.
-    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requiremets in the Challenge stage. That is, $U \subseteq S$.
+    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $U \subseteq S$.
     \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
     \begin{equation*}
-        \operatorfont{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \operatorfont{Pr}[b'=b] - \frac{1}{2}\right\rvert\,.
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \mathsf{Pr}[b'=b] - \frac{1}{2}\right\rvert\,.
     \end{equation*} 
@@
 
-We say that an encryption scheme meets the security of LCAO if no probabilistic-time adversary has more than negligable advantage in winning this security game.
+\begin{definition}
+    An encryption scheme meets LCAO security if no probabilistic-time adversary has more than a negligible advantage in winning the above security game.
+\end{definition}
 
-Our weighted aggregation method relies on the decisional composite residuosity assumption (DCRA) originally defined by Paillier in \cite{paillierPublicKeyCryptosystemsBased1999}.
-The aggregation method can be seen as a combination of the additive homomorphic Paillier encryption scheme, which additionally allows multiplication of an encrypted message with a plaintext value, and the Joye-Libert private stream-aggregation scheme.
-Both of these schemes base their security on the DCRA, and their descriptions are given briefly below before defining our weighted aggregation scheme.
+In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
 
-\subsection{Paillier Encryption Scheme}
-The Paillier encryption scheme is an additively homomorphic encryption scheme which functions over a finite group $\mathbb{G}$, containing
+%  .d88888b.                                          888
+% d88P" "Y88b                                         888
+% 888     888                                         888
+% 888     888 888  888 888d888      .d8888b   .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.
+% 888     888 888  888 888P"        88K      d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b
+% 888     888 888  888 888          "Y8888b. 888      888  888 88888888 888  888  888 88888888
+% Y88b. .d88P Y88b 888 888               X88 Y88b.    888  888 Y8b.     888  888  888 Y8b.
+%  "Y88888P"   "Y88888 888           88888P'  "Y8888P 888  888  "Y8888  888  888  888  "Y8888
 
-% TODO not true I think - just keep it simple instead - a subgroup where the DCRA holds and is of an unknown order, and another subgroup where discrete logarithms are easily computable.
-
-Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $n=pq$.
-A generator $g$ is also required for encryption, which is often set to $g=n+1$ when $p$ and $q$ are of equal bit length \cite{}.
-The public key is then given by $(n, g)$ and secret key by $(p, q)$.
-
-Encryption of a plaintext message $m \in \mathbb{Z}_n$, producing ciphertext $c \in \mathbb{Z}^{*}_{n^2}$, is computed by
-\begin{equation}
-    c = g^m r^n \pmod{n^2}
-\end{equation}
-for a randomly chosen $r \in \mathbb{Z}_{n}$.
-The $r^n$ term can be considered as the noise which hides the value $g^m \pmod{n^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
-The decryption of a ciphertext is computed by
-\begin{equation}
-    m = \frac{L(c^\lambda\pmod{n^2})}{L(g^\lambda\pmod{n^2})} \pmod{n}
-\end{equation}
-where $\lambda = \operatorfont{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{n}$.
-
-In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
-\begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{n^2}) &= m_1m_2\!\pmod{n}\,.
-\end{align}
-
-The scheme is shown to be indistinguishable under the chosen plaintext attack model (IND-CPA), which is considered the strongest form of security acheivable by a homomorphic encryption scheme \cite{}.
-
-\subsection{Joye-Libert Privacy-Preserving Aggregation}
-The Joye-Libert private stream aggregation scheme allows, at each time-step, encrypted time-series values originating from $N$ different measuring parties, to be summed up and decrypted by an aggregator.
-Time-series values are encrypted by their measuring party's private encryption key, and decrypted by the aggregator using its private key.
-The scheme functions over the same finite group $\mathbb{G}$ as the Paillier encryption scheme above.
-
-A notable difference in key-generation for the aggregation scheme from a public-key scheme such as Paillier's scheme, is the requirement of an offline generation and distribution step by some trusted party.
-Similar to the Paillier scheme, key generation first requires choosing two sufficiently large, equal length, primes $p$ and $q$ and computing $n=pq$.
-In addition to $n$, a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{n^2}$ is defined, and the public key is set to $(n, H)$.
-The private keys are generated by choosing $N$ keys $sk_i,\,i \in \{1,\dots,N\}$ uniformly from $\mathbb{Z}_{n^2}$ and distributing them to all measuring parties, while the last key is set to
-\begin{equation}
-    sk_0 = -\sum^{N}_{i=1}sk_i \pmod{n^2}\,,
-\end{equation}
-and sent to the aggregator.
-
-Encryption of plaintext $m_{i,t} \in \mathbb{Z}_n$ to ciphertext $c_{i,t} \in \mathbb{Z}_{n^2}$ at time $t$ is computed by participant $i$ as
-\begin{equation}
-    c_{i,t} = (n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2}\,,
-\end{equation}
-As with the interpretation of the noise term in the Paillier scheme, here $H(t)^{sk_i}$ can be seen as noise which hides the easily computable discrete logarithm $g^{m_{i,t}} \pmod{n^2}$, where $g=n+1$.
-
-When all encryptions $c_{i,t},\,i \in \{1,\dots,N\}$ are sent to the aggregator, private summation and decryption are computed by the functions
-\begin{equation}
-    c_{t} = H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2}
-\end{equation}
-and
-\begin{equation}
-    \sum^{N}_{i=1}m_{i,t} = \frac{c_{t}-1}{n}\,. \label{eqn:agg_decryption}
-\end{equation}
-Correctness follows from $\sum^{N}_{i=0}sk_i = 0$, and therefore
-\begin{align}
-    &H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} \\
-    \equiv &H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
-    \equiv &H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
-    \equiv &(n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
-\end{align}
-which results in a solvable discrete logarithm by using \eqref{eqn:agg_decryption}, as defined in \cite{joyeScalableSchemePrivacyPreserving2013}, with no more noise term.
-
-The aggregation scheme is proven to achieve aggregator obliviousness (AO), which in that no corrupted colluding subset learns anything about the individual messages of the non-corrupted participants, other than the final sum of messages if the aggregator is corrupted, and is proven in the random oracle model.
-
-% Maybe rename this to Our Scheme or something like that
 \section{Our Scheme}
-Explain it in as an overview
+%Both scheme base their security on the decisional composite residuosity assumption (DCRA)
+Explain it here
 
@@
 
-\section{Private Localisation}
+\section{Private Localisation Preliminaries}
 

### 2020-08-21 main.tex
Couple small things

@@
 
-The formal security game for IND-CPA has been given in Appendix \ref{app:ind-cpa}.
+The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
 \end{definition}
@@
 \appendix
-\section{Indistinguishability under the Chosen Plaintext Attack (IND-CPA)} \label{app:ind-cpa}
+\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
 \section{Aggregator Obliviousness (AO)} \label{app:ao}

### 2020-08-24 main.tex
Corrected how the restriction on weights was defined - weights must all be the same in queries of the same time step t Added remark which explains the restriction and the meaning behind weights chosen by the aggregator (how this affects the leakage function) Added m and public parameters which will include H to the encryption scheme definition Added the equations for our scheme

@@
 \newtheorem{definition}{Definition}
+
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
 
@@
 \begin{equation}
-    m = \frac{L(c^\lambda\pmod{n^2})}{L(g^\lambda\pmod{n^2})} \pmod{n}
+    m = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
 \end{equation}
-where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{n}$.
+where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.
 
-In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_n$,
+In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
 \begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{n^2}) &= m_1+m_2\!\pmod{n} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{n^2}) &= m_1m_2\!\pmod{n}\,.
+    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,.
 \end{align}
@@
 Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}$ is defined, and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i \leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
+$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
 \begin{equation}
@@
 Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
-\begin{align*}
-    &H(t)^{sk_0}\prod^{N}_{i=1}c_{i,t} \pmod{n^2} \\
-    \equiv &H(t)^{sk_0}\prod^{N}_{i=1}(n+1)^{m_{i,t}} H(t)^{sk_i} \pmod{n^2} \\
-    \equiv &H(t)^{\sum^N_{j=0}sk_j} \prod^{N}_{i=1}g^{m_{i,t}} \pmod{n^2} \\
-    \equiv &(n+1)^{\sum^N_{i=1}m_{i,t}} \pmod{n^2}
-\end{align*}
+\begin{equation*}
+    \begin{split}
+        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
+        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
+        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
+        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
+    \end{split}
+\end{equation*}
 removing all noise terms.
@@
     \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous timesteps.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
-Note that this implies that $\sum^m_{j=1}x^{(t)}_{1,j}$ may be learned by the colluding subset given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{description}
 
-From these definitions, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
+\begin{remark}
+    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
+Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function.
+We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+\end{remark}
+
+From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
 To formalise the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
@@
 \begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
     \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
@@
 \begin{description}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $pk_0$ to the attacker
+    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
     \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
@@
         \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ for a unique pair $(i,t)$ and is given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ such that for any two chosen combine query tuples $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ and $(i',t',\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i',1}',\dots,x_{i',m}')$ the following conditions hold:
+        \begin{equation*}
+            t = t' \implies \mathcal{E}_{pk_0}(\omega_j) = \mathcal{E}_{pk_0}(\omega_j'),\,1\leq j\leq m
+        \end{equation*}
+        and
+        \begin{equation*}
+            i = i' \wedge t = t' \implies x_{i,m} = x_{i',m}',\,1\leq j\leq m\,.
+        \end{equation*}
+        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
@@
 Explain it here
+
+Enccryption: Choose random $r$ and compute
+\begin{equation}
+    \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,,
+\end{equation}
+Combine encryption:
+\begin{equation}
+    \begin{split}
+        y^{(t)}_i &= \mathcal{E}_{pk_0,sk_i}\left(\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j\right) \\
+        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
+        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
+        &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
+        &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2}
+    \end{split}
+\end{equation}
+for a random $r$ (not the same as above)
+
+Aggregation and decryption in two steps. Aggregation:
+\begin{equation}
+    \begin{split}
+        y^{(t)} &= \prod^n_{i=1}y^{(t)}_i \pmod{N^2} \\
+        &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r^N \pmod{N^2} \\
+        &= H(t)^{\sum^n_{i=1}sk_i}\prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}
+    \end{split}
+\end{equation}
+for some $r' \in \mathbb{Z}_N$.
+
+Decryption:
+\begin{equation}
+\sum^{n}_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j = \frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}
+\end{equation}
 

### 2020-08-25 main.tex
Wrote up our scheme, started on proof write up as well Found ERROR in game/proof - with current game cannot A' cannot provide correct queries to C - next need to update LCAO game and add additional query GetWeights - this will fix both the accuracy of the game to the security requirement as well as allow the proof to proceed as planned Added a header comment Found problem with including microtype package - some incompatibility, need to fix at some stage

@@
 \usepackage{tikz}
+%\usepackage{microtype}
 
@@
 %                     "Y88P"  888
-\section{Cryptography Preliminaries}
+\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
 When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
@@
     \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,.
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,. \label{eqn:paillier_hom_mult}
 \end{align}
@@
 Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
-Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}$ is defined, and the public key is set to $(N, H)$.
+Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
 $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
@@
 
-\subsection{Linear-Combination Aggregator Oblivious Encryption}
+\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
 We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
@@
     \begin{equation*}
-        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \mathsf{Pr}[b'=b] - \frac{1}{2}\right\rvert\,.
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
     \end{equation*} 
@@
 \section{Our Scheme}
-%Both scheme base their security on the decisional composite residuosity assumption (DCRA)
-Explain it here
+Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
+As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys.
+Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.
 
-Enccryption: Choose random $r$ and compute
+\begin{description}
+    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
+Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$.
+The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}$.
+
+    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
     \begin{equation}
@@
     \end{equation}
-Combine encryption:
+    for a randomly chosen $r \in \mathbb{Z}_N$.
+
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] The linear combination encryption step at time $t$ is computed as 
+    \begin{equation}
+        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
+    \end{equation}
+    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
+    \begin{equation*}
+        \begin{split}
+             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
+            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
+            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
+            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
+        \end{split}
+    \end{equation*}
+    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
+
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and followed by Paillier decryption
     \begin{equation}
         \begin{split}
-        y^{(t)}_i &= \mathcal{E}_{pk_0,sk_i}\left(\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j\right) \\
-        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
-        &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
-        &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
-        &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2}
+            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
+            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
         \end{split}
     \end{equation}
-for a random $r$ (not the same as above)
+    The correctness of aggregation can be seen from
+    \begin{align*}
+        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
+        \begin{split}
+            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
+            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
+        \end{split}\\
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
+    \end{align*}
+    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
+\end{description}
 
-Aggregation and decryption in two steps. Aggregation:
-\begin{equation}
-    \begin{split}
-        y^{(t)} &= \prod^n_{i=1}y^{(t)}_i \pmod{N^2} \\
-        &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r^N \pmod{N^2} \\
-        &= H(t)^{\sum^n_{i=1}sk_i}\prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N \pmod{N^2} \\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}
-    \end{split}
-\end{equation}
-for some $r' \in \mathbb{Z}_N$.
-
-Decryption:
-\begin{equation}
-\sum^{n}_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j = \frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}
-\end{equation}
-
-% \begin{algorithm}
-%     \caption{Paillier Key Generation}\label{paillier_key_gen}
-%     \begin{algorithmic}[1]
-%         \Procedure{PaillierKeyGen}{$security\_param$}
-%         \State $p,q \gets$ \Call{GeneratePrimes}{$security\_param$}
-%         \State $\lambda \gets$ \Call{lcm}{p,q}
-%         \State $pk \gets (n, n+1)$
-%         \State $sk \gets \lambda$
-%         \State \Return $(pk, sk)$
-%         \EndProcedure
-%     \end{algorithmic}
-% \end{algorithm}
+some summary here
 
 \subsection{Proof}
-Give the reduction proof here for pWSAO and implicit indistinguishability of weights. Alternatively, sketch it out here and give reduction proof in the appendix.
+To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
+From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA.
+We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{} instead.
+
+To show our scheme meets the security notion of LCAO, we prove by contrapositive that given a polynomial-time adversary $\mathcal{A}$ with non-negligible advantage $\mathsf{Adv}^{LCAO}(\mathcal{A})$ against a challenger using our scheme (\textit{i.e.} if we assume our scheme is not LCAO secure) we can construct an adversary $\mathcal{A}'$ with non-negligible advantage $\mathsf{Adv}^{AO}(\mathcal{A}')$ against a challenger using the Joye-Libert private aggregation scheme (\textit{i.e.} then the Joye-Libert scheme is not AO secure).
+As this is a contradiction to the Joye-Libert AO proof in \cite{}, our scheme must meet LCAO security.
+\begin{pf}
+    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}.
+The following is a construction of adversary $\mathcal{A}'$ playing the AO game from Appendix \ref{app:ao} against a challenger $\mathcal{C}$.
+    \begin{description}
+        \item[$\mathsf{Setup}$] $\mathcal{A}'$ receives $N$ and $H$ as public parameters from $\mathcal{C}$, and generates a new key with same size $N'=pq$ and creates aggregator public and private keys $pk_0$, $sk_0$, chooses an $m>1$, and gives $H$, $m$, and $pk_0$ to $\mathcal{A}$
+        \item[$\mathsf{CombEnc}$] When $\mathcal{A}$ makes combine encryption queries $(i, t, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$, $\mathcal{A}'$ uses $sk_0$ to decrypt weights $\omega_1,\dots,\omega_m$ and makes an $\mathsf{Enc}(i, t, \sum^m_{j=1}x_{i,j}\omega_j)$ query to $\mathcal{C}$.
+The received response is of the form $(N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}$, from which $H(t)^{sk_i}$ is recovered by
+        \begin{equation*}
+            H(t)^{sk_i} = (N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}((N+1)^{\sum^m_{j=1}x_{i,j}})^{-1} \pmod{N^2}
+        \end{equation*}
+        where $^-1$ denotes the modular inverse. 
+    \end{description}
+
+    Note that decryption and encryption are polynomial in security parameter and therefore\dots
+\end{pf}
+
+% 888                            8888888b.                  888 d8b
+% 888                            888   Y88b                 888 Y8P
+% 888                            888    888                 888
+% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.
+% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
+% 888     888  888 888           888        888    88888888 888 888 888  888  888
+% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888
+% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888
 
@@
 Give the algorithm as pseudocode (including encoding and encryption)
+
+% \begin{algorithm}
+%     \caption{Paillier Key Generation}\label{paillier_key_gen}
+%     \begin{algorithmic}[1]
+%         \Procedure{PaillierKeyGen}{$security\_param$}
+%         \State $p,q \gets$ \Call{GeneratePrimes}{$security\_param$}
+%         \State $\lambda \gets$ \Call{lcm}{p,q}
+%         \State $pk \gets (n, n+1)$
+%         \State $sk \gets \lambda$
+%         \State \Return $(pk, sk)$
+%         \EndProcedure
+%     \end{algorithmic}
+% \end{algorithm}
 

### 2020-08-26 main.tex
Fixed LCAO game to capture not knowing weights at time t, and consistent weights for all participants at the same time t. Wrote proof showing that if non-negligible adversary exists for LCAO, then the Joye-Libert scheme is not AO secure (which is proven to be the case) - referenced details about AO game and the Joye-Libert scheme that I think weren't made clear enough in it's description - need to update that next

@@
 
-\subsection{Paillier Encryption Scheme}
+\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
 The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
@@
 
-\subsection{Joye-Libert Private Aggregation Scheme}
+\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
 The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO.
@@
 \subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
-We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-For the sake of readbility, we have ommited the time variable $t$ from values $\omega_j$ and $x_{i,j}$.
+We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$, defined as
 
@@
     \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j$ using its private key $sk_0$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{description}
@@
     \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
-    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The three types of actions are:
+    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
     \begin{enumerate}
         \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ such that for any two chosen combine query tuples $(i,t,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})$ and $(i',t',\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i',1}',\dots,x_{i',m}')$ the following conditions hold:
+        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
         \begin{equation*}
-            t = t' \implies \mathcal{E}_{pk_0}(\omega_j) = \mathcal{E}_{pk_0}(\omega_j'),\,1\leq j\leq m
+            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
+        \end{equation*}
+        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
+        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
+    \end{enumerate} 
+    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
+The attacker then chooses two series of tuples
+    \begin{equation*}
+        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
     \end{equation*}
@@
     \begin{equation*}
-            i = i' \wedge t = t' \implies x_{i,m} = x_{i',m}',\,1\leq j\leq m\,.
+        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
     \end{equation*}
-        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
-        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{enumerate} 
-    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $U \subseteq S$ where $S$ is the complete set of users for which no combine queries for time $t^*$ and no compromise queries are made for the duration of the game.
-The attacker then chooses two series of tuples
+    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
     \begin{equation*}
-        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m),x_{i,1},\dots,x_{i,m})\,|\,i \in U\rangle
+        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
     \end{equation*}
-    and
+    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
     \begin{equation*}
-        \langle(i,t^*,\mathcal{E}_{pk_0}(\omega_1'),\dots,\mathcal{E}_{pk_0}(\omega_m'),x_{i,1}',\dots,x_{i,m}')\,|\, i \in U\rangle\,,
+        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
     \end{equation*}
-    and gives them to the challenger. In the case that $0 \in U$ (\textit{i.e.} the aggregator is compromised) and $U = S$, it is additionally required that
-    \begin{equation*}
-        \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}\omega_j = \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}'\omega_j'\,.
-    \end{equation*}
-    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
-    \begin{equation*}
-        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}\omega_j)\,|\,i\in U\rangle
-    \end{equation*}
-    if $b=0$, or 
-    \begin{equation*}
-        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x_{i,j}'\omega_j')\,|\,i\in U\rangle
-    \end{equation*}
-    otherwise.
-    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $U \subseteq S$.
+    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
     \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
@@
 \begin{definition}
-    An encryption scheme meets LCAO security if no probabilistic-time adversary has more than a negligible advantage in winning the above security game.
+    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game.
+Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
 \end{definition}
@@
 
-\section{Our Scheme}
+\section{Our Scheme} \label{sec:our_scheme}
 Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
@@
 
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$] The linear combination encryption step at time $t$ is computed as 
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as
     \begin{equation}
@@
 
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y_1,\dots,y_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and followed by Paillier decryption
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
     \begin{equation}
@@
 From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA.
-We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{} instead.
+We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.
 
-To show our scheme meets the security notion of LCAO, we prove by contrapositive that given a polynomial-time adversary $\mathcal{A}$ with non-negligible advantage $\mathsf{Adv}^{LCAO}(\mathcal{A})$ against a challenger using our scheme (\textit{i.e.} if we assume our scheme is not LCAO secure) we can construct an adversary $\mathcal{A}'$ with non-negligible advantage $\mathsf{Adv}^{AO}(\mathcal{A}')$ against a challenger using the Joye-Libert private aggregation scheme (\textit{i.e.} then the Joye-Libert scheme is not AO secure).
-As this is a contradiction to the Joye-Libert AO proof in \cite{}, our scheme must meet LCAO security.
+To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger using the \textit{Joye-Libert scheme}, such that
+\begin{equation*}
+    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
+\end{equation*}
+for some negligible functions $\eta_1$ and $\eta_2$.
+(\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.
 \begin{pf}
     Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}.
-The following is a construction of adversary $\mathcal{A}'$ playing the AO game from Appendix \ref{app:ao} against a challenger $\mathcal{C}$.
+The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
     \begin{description}
-        \item[$\mathsf{Setup}$] $\mathcal{A}'$ receives $N$ and $H$ as public parameters from $\mathcal{C}$, and generates a new key with same size $N'=pq$ and creates aggregator public and private keys $pk_0$, $sk_0$, chooses an $m>1$, and gives $H$, $m$, and $pk_0$ to $\mathcal{A}$
-        \item[$\mathsf{CombEnc}$] When $\mathcal{A}$ makes combine encryption queries $(i, t, \mathcal{E}_{pk_0}(\omega_1),\dots,\mathcal{E}_{pk_0}(\omega_m), x_{i,1},\dots,x_{i,m})$, $\mathcal{A}'$ uses $sk_0$ to decrypt weights $\omega_1,\dots,\omega_m$ and makes an $\mathsf{Enc}(i, t, \sum^m_{j=1}x_{i,j}\omega_j)$ query to $\mathcal{C}$.
-The received response is of the form $(N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}$, from which $H(t)^{sk_i}$ is recovered by
+        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
+        \item[Queries] Handle queries from $\mathcal{A}$:
+        \begin{description}
+            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
             \begin{equation*}
-            H(t)^{sk_i} = (N+1)^{\sum^m_{j=1}x_{i,j}\omega_j}H(t)^{sk_i}((N+1)^{\sum^m_{j=1}x_{i,j}})^{-1} \pmod{N^2}
+                (N+1)^{(\omega^{(t)}_{j})}r_j^N\pmod{N^2},\,1\leq j\leq m
             \end{equation*}
-        where $^-1$ denotes the modular inverse. 
+            to $\mathcal{A}$.
+            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
+The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
+            \begin{equation*}
+                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N H(t)^{sk_i} \pmod{N^2}
+            \end{equation*}
+            to $\mathcal{A}$.
+            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
+        \end{description}
+        \item[Challenge] When $\mathcal{A}$ submits challenge series
+        \begin{equation*}
+            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
+        \end{equation*}
+        and
+        \begin{equation*}
+            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
+        \end{equation*}
+        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
+        \begin{equation*}
+            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
+        \end{equation*}
+        and
+        \begin{equation*}
+            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
+        \end{equation*}
+        to $\mathcal{C}$. The received response if of the form 
+        \begin{equation*}
+            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
+        \end{equation*}
+        for an unkonwn $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
+        \begin{equation*}
+            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
+        \end{equation*}
+        to $\mathcal{A}$.
+        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
     \end{description}
 
-    Note that decryption and encryption are polynomial in security parameter and therefore\dots
+    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{sec:our_scheme}.
+Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
+That is, there exists a negligible function $\eta$, such that
+    \begin{equation*}
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
+    \end{equation*}
+    for security parameter $\kappa$. \qed
 \end{pf}
@@
 \section{Results}
-Decide on what kind of simulations and which plots to make. run times would be nice this time around
-
 Time results can be captured in one graph.

### 2020-08-26 main.tex
Added a couple of pending references in the encryption preliminaries section

@@
 The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{}.
+The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}.
 \begin{definition}
@@
 \end{definition}
-Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{}. 
+Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
 \begin{definition}
@@
 Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
-A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{}.
+A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}.
 The public key is defined by $(N, g)$ and secret key by $(p, q)$.
@@
             \begin{equation*}
-                (N+1)^{(\omega^{(t)}_{j})}r_j^N\pmod{N^2},\,1\leq j\leq m
+                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
             \end{equation*}
@@
             \begin{equation*}
-                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N H(t)^{sk_i} \pmod{N^2}
+                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
             \end{equation*}
@@
         \begin{equation*}
-            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
+            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
         \end{equation*}

### 2020-08-27 main.tex
Installed new banner plugin and updated banner comments making the subsection comments more identifiable
Clarified that our proof is in the random oracle model since the Joye-Libert one is Referred to multiple noise terms in our scheme (since the noise terms were introduced in the preliminaries section but not referenced) Fixed some inconsistencies in notation

@@
 
+% 
 %  .d8888b.                            888                 8888888b.                  888 d8b               
@@
 %                     "Y88P"  888                                                                           
+%
+
 \section{Cryptography Preliminaries} \label{sec:crypto_prelim}
@@
 
-% Quickly define homomorphic encryption and private aggregation here??
+% 
+%  ######  ########  ######  ##     ## ########  #### ######## ##    ## 
+% ##    ## ##       ##    ## ##     ## ##     ##  ##     ##     ##  ##  
+% ##       ##       ##       ##     ## ##     ##  ##     ##      ####   
+%  ######  ######   ##       ##     ## ########   ##     ##       ##    
+%       ## ##       ##       ##     ## ##   ##    ##     ##       ##    
+% ##    ## ##       ##    ## ##     ## ##    ##   ##     ##       ##    
+%  ######  ########  ######   #######  ##     ## ####    ##       ##    
+%
 
@@
 \end{definition}
+
+% 
+% ########     ###    #### ##       ##       #### ######## ########  
+% ##     ##   ## ##    ##  ##       ##        ##  ##       ##     ## 
+% ##     ##  ##   ##   ##  ##       ##        ##  ##       ##     ## 
+% ########  ##     ##  ##  ##       ##        ##  ######   ########  
+% ##        #########  ##  ##       ##        ##  ##       ##   ##   
+% ##        ##     ##  ##  ##       ##        ##  ##       ##    ##  
+% ##        ##     ## #### ######## ######## #### ######## ##     ## 
+%
 
@@
 \end{align}
+
+% 
+%       ##         ##    ## 
+%       ##          ##  ##  
+%       ##           ####   
+%       ## #######    ##    
+% ##    ##            ##    
+% ##    ##            ##    
+%  ######             ##    
+%
 
@@
 
+% 
 %  .d8888b.                            888                 8888888b.                  888      
@@
 %                     "Y88P"  888                                                              
+%
+
 \section{Private Linear-Combination Aggregation}
 For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation.
-In the context of navigation, $m$ weights $\omega_1^{(t)}, \dots , \omega_m^{(t)}$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$.
+In the context of navigation, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$.
 This has been summarized in Figure \ref{fig:agg_steps}.
-In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.
+In Section \ref{sec:private_localisation} we will show how this protocol can be sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.
 
@@
 
-% 888      .d8888b.        d8888  .d88888b.
-% 888     d88P  Y88b      d88888 d88P" "Y88b
-% 888     888    888     d88P888 888     888
-% 888     888           d88P 888 888     888
-% 888     888          d88P  888 888     888
-% 888     888    888  d88P   888 888     888
-% 888     Y88b  d88P d8888888888 Y88b. .d88P
-% 88888888 "Y8888P" d88P     888  "Y88888P"
+% 
+% ##        ######     ###     #######  
+% ##       ##    ##   ## ##   ##     ## 
+% ##       ##        ##   ##  ##     ## 
+% ##       ##       ##     ## ##     ## 
+% ##       ##       ######### ##     ## 
+% ##       ##    ## ##     ## ##     ## 
+% ########  ######  ##     ##  #######  
+%
 
@@
     \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
     \begin{equation*}
@@
 
-%  .d88888b.                                          888
-% d88P" "Y88b                                         888
-% 888     888                                         888
-% 888     888 888  888 888d888      .d8888b   .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.
-% 888     888 888  888 888P"        88K      d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b
-% 888     888 888  888 888          "Y8888b. 888      888  888 88888888 888  888  888 88888888
-% Y88b. .d88P Y88b 888 888               X88 Y88b.    888  888 Y8b.     888  888  888 Y8b.
-%  "Y88888P"   "Y88888 888           88888P'  "Y8888P 888  888  "Y8888  888  888  888  "Y8888
+% 
+%  .d88888b.                         .d8888b.           888                                      
+% d88P" "Y88b                       d88P  Y88b          888                                      
+% 888     888                       Y88b.               888                                      
+% 888     888 888  888 888d888       "Y888b.    .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.  
+% 888     888 888  888 888P"            "Y88b. d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b 
+% 888     888 888  888 888                "888 888      888  888 88888888 888  888  888 88888888 
+% Y88b. .d88P Y88b 888 888          Y88b  d88P Y88b.    888  888 Y8b.     888  888  888 Y8b.     
+%  "Y88888P"   "Y88888 888           "Y8888P"   "Y8888P 888  888  "Y8888  888  888  888  "Y8888  
+%                                                                                                
+%                                                                                                
+%                                                                                                
+%
 
@@
     for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
+Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
 
@@
 
-some summary here
+% 
+% ########  ########   #######   #######  ######## 
+% ##     ## ##     ## ##     ## ##     ## ##       
+% ##     ## ##     ## ##     ## ##     ## ##       
+% ########  ########  ##     ## ##     ## ######   
+% ##        ##   ##   ##     ## ##     ## ##       
+% ##        ##    ##  ##     ## ##     ## ##       
+% ##        ##     ##  #######   #######  ##       
+%
 
-\subsection{Proof}
+\subsection{Security Proof}
 To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
@@
 (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.
+The function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
 \begin{pf}
@@
         \end{equation*}
-        for an unkonwn $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
+        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
         \begin{equation*}
@@
 
+% 
 % 888                            8888888b.                  888 d8b               
@@
 % 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888 
+%                                                                                 
+%                                                                                 
+%                                                                                 
+%
 

### 2020-08-27 main.tex
Explicitly state that weights and values are integers in our scheme. This will tie in nicer in the real number encoding section Removed some remaining instances of "weighted aggregation" as this has been replaced by linear-combination aggregation throughout - includes updating the paper title, and the abstract

@@
 % Title, preferably not more than 10 words.
-\title{Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}}
+\title{Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}}
 
@@
 Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
-Existing approaches which provide such guarantees, fail to address sensor and navigator privacy in some common model-based non-linear measurement localisation methods forfeiting broad applicability.
-We define a cryptographically secure weighted aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
-The security requirements, leakage, and cryptographic proof are given for the private filter and weighted aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
+Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common, model-based, non-linear measurement, localisation methods and forfeit broad applicability.
+We define a cryptographically secure linear-combination aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
+The security requirements, leakage, and cryptographic proof are given for the private filter and aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
 Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
@@
 \begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2)\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2}\!\pmod{N^2}) &= m_1+m_2\!\pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2}\!\pmod{N^2}) &= m_1m_2\!\pmod{N}\,. \label{eqn:paillier_hom_mult}
+    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \\
+    \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
 \end{align}
@@
 $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
-\begin{equation}
+\begin{equation*}
     sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
-\end{equation}
+\end{equation*}
 and sent to the aggregator.
@@
 
+Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $x^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.
+
 % 
@@
 \subsection{Integer Encoding for Real Numbers}
+Point out the integer range limit introduced by our scheme, $x<N$, for both the weights and the values.
 

### 2020-08-27 main.tex
Fixed typo in LCAO game equation Added appendix description for IND-CPA and AO (included description of public key scheme, and aggregator oblivious scheme)

@@
     \begin{equation*}
-        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
+        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
     \end{equation*}
@@
 \section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
+A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
+\begin{description}
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
+    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
+    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
+\end{description}
+
+The security game between attacker and challenger for IND-CPA is given by
+\begin{description}
+    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public key $pk$ to the attacker
+    \item[Encryptions] The attacker may compute encryptions using the public key $pk$.
+    \item[Challenge] Next, the attacker chooses two values
+    \begin{equation*}
+        x^{(0)} \text{ and } x^{(1)}
+    \end{equation*}
+    and gives them to the challenger. The challenger then chooses a random bit $b \in \{1,0\}$ and returns the encryption
+    \begin{equation*}
+        \mathcal{E}_{pk}(x^{(b)}).
+    \end{equation*}
+    \item[More Encryptions] The attacker can now compute more encryptions with the public key $pk$.
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
+    \begin{equation*}
+        \mathsf{Adv}^{IND-CPA}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
+    \end{equation*} 
+\end{description}
+
 \section{Aggregator Obliviousness (AO)} \label{app:ao}
+An aggregator oblivious encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{AggDec})$, defined as
+\begin{description}
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
+    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At time $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
+\end{description}
+
+The security game between attacker and challenger for AO is given by
+\begin{description}
+    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
+    \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
+    \begin{enumerate}
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_i)$ and $(i',t',x^{\prime(t')}_{i'}$, the following condition holds:
+        \begin{equation*}
+            i = i' \wedge t = t' \implies x^{(t)}_{i} = x^{\prime(t')}_{i'}\,.
+        \end{equation*}
+        They are given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
+        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
+    \end{enumerate} 
+    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
+The attacker then chooses two series of tuples
+    \begin{equation*}
+        \langle(i,t^*,x^{(t^*)(0)}_i)\,|\,i \in S\rangle
+    \end{equation*}
+    and
+    \begin{equation*}
+        \langle(i,t^*,x^{(t^*)(1)}_i)\,|\, i \in S\rangle\,,
+    \end{equation*}
+    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
+    \begin{equation*}
+        \sum_{i\in S} x^{(t^*)(0)}_i = \sum_{i \in S} x^{(t^*)(1)}_i\,.
+    \end{equation*}
+    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
+    \begin{equation*}
+        \langle\mathcal{E}_{sk_i}(x^{(t^*)(b)}_i)\,|\,i\in S\rangle\,.
+    \end{equation*}
+    \item[More Queries] The attacker can now submit more queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
+    \begin{equation*}
+        \mathsf{Adv}^{AO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
+    \end{equation*} 
+\end{description}
 

### 2020-08-28 main.tex
Appendix comment
Encoding started but ran into problem - code used Farohki encoding, but when writing up the generalised version realised that this is simply an overcomplication of straightforward quantisation mod N - will update code to use simpler quantisation method, and update here when that and the new plots work More big comments

@@
 
+% 
+% 8888888          888                    
+%   888            888                    
+%   888            888                    
+%   888   88888b.  888888 888d888 .d88b.  
+%   888   888 "88b 888    888P"  d88""88b 
+%   888   888  888 888    888    888  888 
+%   888   888  888 Y88b.  888    Y88..88P 
+% 8888888 888  888  "Y888 888     "Y88P"  
+%                                         
+%                                         
+%                                         
+%
+
 \section{Introduction}
@@
 
+% 
+% ##       #### ######## 
+% ##        ##     ##    
+% ##        ##     ##    
+% ##        ##     ##    
+% ##        ##     ##    
+% ##        ##     ##    
+% ######## ####    ##    
+%
+
 \subsection{Relevant Literature on Encrypted Localisation and Estimation}
@@
 
+% 
+% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
+% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
+% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
+% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
+% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
+% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
+% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
+%
+
 \subsection{Notation}
-Notation
+Notation. Reminder to include rounding symbol
+
+% 
+% 8888888b.                  888      
+% 888   Y88b                 888      
+% 888    888                 888      
+% 888   d88P 888d888 .d88b.  88888b.  
+% 8888888P"  888P"  d88""88b 888 "88b 
+% 888        888    888  888 888  888 
+% 888        888    Y88..88P 888 d88P 
+% 888        888     "Y88P"  88888P"  
+%                                     
+%                                     
+%                                     
+%
 
@@
 \section{Private Localisation Preliminaries}
+The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model.
+We make use of an existing real-number encoding scheme which supports the homomorphic operations we'll require and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to only use these operations.
+
+% 
+% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
+% ##       ###   ## ##    ## ##     ## ##     ##  ##  ###   ## ##    ##  
+% ##       ####  ## ##       ##     ## ##     ##  ##  ####  ## ##        
+% ######   ## ## ## ##       ##     ## ##     ##  ##  ## ## ## ##   #### 
+% ##       ##  #### ##       ##     ## ##     ##  ##  ##  #### ##    ##  
+% ##       ##   ### ##    ## ##     ## ##     ##  ##  ##   ### ##    ##  
+% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
+%
 
 \subsection{Integer Encoding for Real Numbers}
-Point out the integer range limit introduced by our scheme, $x<N$, for both the weights and the values.
+
+% TODO remove when not needed - for its simlicity, and applicability to our multiplication and bound requirements, is described in \cite{farokhiSecurePrivateControl2017}.
+It provides any number of homomorphic additions, and a predefined number of homomorphic multiplications.
+
+In the encryption scheme introduced, weights and values are limited to integer values, and operations computed $\pmod{N}$ bound meaningful inputs to $x \in \mathbb{Z}_N$ for any weight or value $x$.
+The encoding scheme we have used
+
+The encoding scheme is defined by the quantisation parameter $f$, representing the number of bits used to quantise the fractional part of a real number, and $N$ the modulus to use for handling negative numbers.
+
+Encoding of a real number $a \in \mathbb{R}$ to an integer $e \in \mathbb{Z}$ is computed by
+\begin{equation}
+    e = \left\lfloor 2^{(m+1)f} a \right\rceil \pmod{N}\,,
+\end{equation}
+and decoding after $m$ homomorphic multiplications is computed by
+\begin{equation}
+    a = 
+    \begin{dcases}
+        \frac{e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
+        -\frac{N - e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} > \left\lfloor\frac{N}{2}\right\rfloor \\
+    \end{dcases}\,.
+\end{equation}
+
+Note that adding encoding number to already encoded number requires the number of multiplications to be matched
+
+that for the largest number of multiplications $m$, parameters for the encoding scheme when used with our ecncryption scheme should be defined such that
+\begin{equation*}
+    something \leq something\,else
+\end{equation*}
+
+encodings grow in size exponentially for each multilpication.
+
+% 
+% ######## #### ######## 
+% ##        ##  ##       
+% ##        ##  ##       
+% ######    ##  ######   
+% ##        ##  ##       
+% ##        ##  ##       
+% ######## #### ##       
+%
 
 \subsection{Extended Information Filter}
+
+% 
+% 8888888b.          d8b               888                       
+% 888   Y88b         Y8P               888                       
+% 888    888                           888                       
+% 888   d88P 888d888 888 888  888      888      .d88b.   .d8888b 
+% 8888888P"  888P"   888 888  888      888     d88""88b d88P"    
+% 888        888     888 Y88  88P      888     888  888 888      
+% 888        888     888  Y8bd8P       888     Y88..88P Y88b.    
+% 888        888     888   Y88P        88888888 "Y88P"   "Y8888P 
+%                                                                
+%                                                                
+%                                                                
+%
 
@@
 \subsection{Requirements for Measurement Model}
+Must be such that Jacobian consists of linear combinations of state-related variables
 
@@
 
+% 
+% 8888888b.                            888 888             
+% 888   Y88b                           888 888             
+% 888    888                           888 888             
+% 888   d88P .d88b.  .d8888b  888  888 888 888888 .d8888b  
+% 8888888P" d8P  Y8b 88K      888  888 888 888    88K      
+% 888 T88b  88888888 "Y8888b. 888  888 888 888    "Y8888b. 
+% 888  T88b Y8b.          X88 Y88b 888 888 Y88b.       X88 
+% 888   T88b "Y8888   88888P'  "Y88888 888  "Y888  88888P' 
+%                                                          
+%                                                          
+%                                                          
+%
+
 \section{Results}
@@
 A well-defined example.
+
+% 
+%  .d8888b.                             
+% d88P  Y88b                            
+% 888    888                            
+% 888         .d88b.  88888b.   .d8888b 
+% 888        d88""88b 888 "88b d88P"    
+% 888    888 888  888 888  888 888      
+% Y88b  d88P Y88..88P 888  888 Y88b.    
+%  "Y8888P"   "Y88P"  888  888  "Y8888P 
+%                                       
+%                                       
+%                                       
+%
 
@@
 \appendix
+% 
+%        d8888                                          888 d8b          
+%       d88888                                          888 Y8P          
+%      d88P888                                          888              
+%     d88P 888 88888b.  88888b.   .d88b.  88888b.   .d88888 888 888  888 
+%    d88P  888 888 "88b 888 "88b d8P  Y8b 888 "88b d88" 888 888 `Y8bd8P' 
+%   d88P   888 888  888 888  888 88888888 888  888 888  888 888   X88K   
+%  d8888888888 888 d88P 888 d88P Y8b.     888  888 Y88b 888 888 .d8""8b. 
+% d88P     888 88888P"  88888P"   "Y8888  888  888  "Y88888 888 888  888 
+%              888      888                                              
+%              888      888                                              
+%              888      888                                              
+%
+
 \section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}

### 2020-09-01 main.tex
Added encoding section, in more detail than in the past. Changes definition and remark environments to use correct ones from the scheme Added armin and argmax definitions

@@
 
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}.
-\begin{definition}
+\begin{defn}
 An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
@@
 The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
-\end{definition}
+\end{defn}
 Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
-\begin{definition}
+\begin{defn}
 An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
@@
 The formal security game for AO has been given in Appendix \ref{app:ao}.
-\end{definition}
+\end{defn}
 
@@
 
-\begin{remark}
+\begin{rem}
     The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
@@
 We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
-\end{remark}
+\end{rem}
 
@@
 
-\begin{definition}
+\begin{defn}
     An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game.
 Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
-\end{definition}
+\end{defn}
 
@@
     \begin{equation}
-        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
+        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
     \end{equation}
@@
 The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model.
-We make use of an existing real-number encoding scheme which supports the homomorphic operations we'll require and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to only use these operations.
+We make use of a real-number encoding scheme which supports the required homomorphic operations and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to use only these operations.
 
@@
 
-In the encryption scheme introduced, weights and values are limited to integer values, and operations computed $\pmod{N}$ bound meaningful inputs to $x \in \mathbb{Z}_N$ for any weight or value $x$.
-The encoding scheme we have used
-
-The encoding scheme is defined by the quantisation parameter $f$, representing the number of bits used to quantise the fractional part of a real number, and $N$ the modulus to use for handling negative numbers.
-
-Encoding of a real number $a \in \mathbb{R}$ to an integer $e \in \mathbb{Z}$ is computed by
-\begin{equation}
-    e = \left\lfloor 2^{(m+1)f} a \right\rceil \pmod{N}\,,
-\end{equation}
-and decoding after $m$ homomorphic multiplications is computed by
-\begin{equation}
-    a = 
+In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$.
+For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing.
+We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
+
+We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$.
+This contrasts with the common definition given in terms of total bits $a$ and fractional bits $b$ \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
+Rational subset $\mathbb{Q}_{r,f}$ is given by
+\begin{equation*}
+    \mathbb{Q}_{r,f} = \left\{q : f^{-1} | q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
+\end{equation*}
+and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$.
+That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$.
+In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic.
+In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
+This is captured by a third parameter $m$; the number of \textit{additional} multiplication factors to add or remove from encodings.
+
+The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
+\begin{equation}
+    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
+\end{equation}
+Decoding of integer $e \in \mathbb{Z}_N$, is given by
+\begin{equation}
+    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
     \begin{dcases}
-        \frac{e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
-        -\frac{N - e\hspace{-7pt}\pmod{N}}{2^{(m+1)f}}, &e\hspace{-7pt}\pmod{N} > \left\lfloor\frac{N}{2}\right\rfloor \\
-    \end{dcases}\,.
-\end{equation}
-
-Note that adding encoding number to already encoded number requires the number of multiplications to be matched
-
-that for the largest number of multiplications $m$, parameters for the encoding scheme when used with our ecncryption scheme should be defined such that
-\begin{equation*}
-    something \leq something\,else
-\end{equation*}
-
-encodings grow in size exponentially for each multilpication.
+        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
+        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
+    \end{dcases}.
+\end{equation}
+
+This encoding scheme provides the following homomorphic operations,
+\begin{equation}
+    \begin{split}
+        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
+        &\mathsf{E}_{N,f,m}(a_1+a_2)
+    \end{split}
+\end{equation}
+and
+\begin{equation}
+    \begin{split}
+        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
+        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
+    \end{split}
+\end{equation}
+noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.
+
+The choice of a high fractional precision $f$ may reduce quantisation erros introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
+Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
+\begin{equation*}
+    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{N}{2} \right\rfloor\,.
+\end{equation*}
+In practice, $N$ is typicaly very large ($N>2^{1024}$) and this condition can be ignored.
 

### 2020-09-02 main.tex
Added a tonne of more detailed dot points on the rest of the paper - still very informal, and inconsistent notation - measurement modification section may need to be split into two (one for new noise, and one for application to encryption scheme) Have a better idea how the paper will go now. Next step is to do the same for the problem formulation section

@@
 \subsection{Notation}
-Notation. Reminder to include rounding symbol
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides''
 
@@
 \subsection{Integer Encoding for Real Numbers}
-
-% TODO remove when not needed - for its simlicity, and applicability to our multiplication and bound requirements, is described in \cite{farokhiSecurePrivateControl2017}.
-It provides any number of homomorphic additions, and a predefined number of homomorphic multiplications.
-
 In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$.
@@
 \end{equation}
-Decoding of integer $e \in \mathbb{Z}_N$, is given by
+Decoding of an integer $e \in \mathbb{Z}_N$, is given by
 \begin{equation}
@@
 
-The choice of a high fractional precision $f$ may reduce quantisation erros introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
+The choice of a high fractional precision $f$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
 Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
@@
 \end{equation*}
-In practice, $N$ is typicaly very large ($N>2^{1024}$) and this condition can be ignored.
+In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored.
 
@@
 \subsection{Extended Information Filter}
+EIF is a reformulation of the EKF where the update step is reduced to sums. Makes it especially easier for processing multiple measurements.
+
+Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed and the prediction computed normally
+
+% The Extended Information Filter (EIF) is an algebraic reformulation of the Extended Kalman Filter (EKF) such that the update step is reduced to a simple summation.
+Given process and measurement models \eqref{} and \eqref{}, the EIF update equation is given by
+% \begin{equation}
+%     a
+% \end{equation}
 
@@
 \section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
-Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
-
-Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator.
+% Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
+
+% Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator.
 This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.
 
+Using the EIF and distance sensors, we see that the required computation of measurement vector and matrices is reduced to computing $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, for one-dimensional $R$ and jacobian $H$, at each sensor.
+As this is requires current state information $x$, relevant attributes need to be sent to the sensors.
+
+We wish to encrypt current state information and use the encryption scheme defined to compute measurement information $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ as a linear combination of state information, and encrypt it for aggregation.
+Thus allowing the navigator to only learn sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$ and update its position.
+
 \subsection{Requirements for Measurement Model}
-Must be such that Jacobian consists of linear combinations of state-related variables
+% Must be such that Jacobian consists of linear combinations of state-related variables
+
+The requirement introduced above, is that $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ can be computed as linear combinations of state-derived variables.
+Here $H$ is a Jacobian and includes current state information as well.
+
+State-derived variables refer to state vector elements, as well as non-linear functions of these elements, which do not require sensor position or measurement information to be computed.
+As our encryption scheme described above, only supports linear combinations of weights, in this case state-derived variables, all non-linear functions required for measurements information to be computed, need to be treated as individual weights to be combined.
+
+From the definition of matrix multiplication, we see that any $KxL$ matrix $D=ABC$, where $B$ has dimensions $MxN$, has element $d_{i,j}$ defined by
+\begin{equation*}
+    d_{i,j} = \sum^{N}_{n=1}\sum^{M}_{m=1}a_{i,m}b_{m,n}c_{n,j}\,,
+\end{equation*}
+and can therefore be considered as a linear combination of all elements $a_{i,m}c_{n,j}$.
+Applying this to the measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, we require that all values of $h(x)$, and all elements in Jacobian $H$ be linear combinations of state-derived variables
+
+Next, we show how this can be achieved for the specific case of 2-dimensional localisation, with range-only sensors.
 
 \subsection{Localisation Measurement Modification}
-Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
-
-Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
+% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
+
+% Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
 Give flight navigation as an applicable example with typically high distances.
 
-Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
-
-\subsection{Expanding Aggregation for Multi-dimensional Inputs}
-Give 1D example that's intuitive (with $a^2b$) and then reduce the equivalent ND case ($A^\top BA$) to a set of weighted sums.
-
-Ensure that timestamps are concatenated with the position so that no aggregation values are blinded by the same noise.
+% Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
+
+From our problem statements in Section $\cdot$, we specify the goal of private localisation in the 2-dimensional case, using range-only sensors.
+Given the current location estimate $x_{loc} = (x,y)$, which may comprise only part of the filter state estimate, and sensor location $s_{loc} = (s_x, s_y)$, the measurement equation is given by
+\begin{equation*}
+    \begin{split}
+        h(x) &= \|x_{loc} - s_{loc}\| \\
+        &= \sqrt{(x - s_x)^2 + (y - s_y)^2}\,.
+    \end{split}
+\end{equation*}
+The Jacobian $H$ for the measurement function above at $x_{loc,0}=(x_0, y_0)$ is then given by
+\begin{equation*}
+    H = 
+    \begin{bmatrix}
+        a & b \\
+        c & d
+    \end{bmatrix}\,.
+\end{equation*}
+The problem with the above function $h$ and Jacobian $H$ is that they cannot be reformulated as a linear combination of weights, where weights are defined by functions of $x$ and $y$, and do not include $s_x$ and $s_y$.
+
+Our proposed solution to this problem, is squaring sensor measurements used for the filter.
+\begin{equation*}
+    \begin{split}
+        z^2 &= (h(x) + n)^2 \\
+        &= h(x)^2 + 2nh(x) + n^2
+    \end{split}\,,
+\end{equation*}
+where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
+We account for the non-zero mean by offsetting the the squared measurement and taking this as the adjust measurement model $h'(x) = h(x)^2$, and
+\begin{equation*}
+    \begin{split}
+        z' &= h'(x) + 2nh(x) + n^2 - \sigma^2 \\
+        &= h'(x) + n'
+    \end{split}\,,
+\end{equation*}
+with variance approximated as $2(2z^2\sigma^2 + \sigma^4)$, which uses the original measurement $z$ as an unbiased estimate for $h(x)$.
+
+While the above transformation provides a measurement model that no longer has Gaussian noise, it allows for the linear formulation required for the encryption scheme, and privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
+The adjusted measurement function is now given by
+\begin{equation*}
+    \begin{split}
+        h'(x) &= \left(\|x_{loc} - s_{loc}\|\right)^2 \\
+        &= (x - s_x)^2 + (y - s_y)^2 \\
+        &= x^2 + y^2 -2s_xx -2s_yy +s_x^2 +s_y^2
+    \end{split}\,,
+\end{equation*}
+and Jacobian $H'$ by
+\begin{equation*}
+    H' = 
+    \begin{bmatrix}
+        a & b \\
+        c & d
+    \end{bmatrix}\,.
+\end{equation*}
+The above function and jacobian elements are linear combinations of state-derived functions $x$, $x^2$, $y$, $xy$ and $y^2$.
+From our equation $\cdot$ in the previous section, we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of state-derived functions $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
+\begin{equation*}
+    H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = 
+    \begin{bmatrix}
+        a \\
+        b
+    \end{bmatrix}
+\end{equation*}
+and
+\begin{equation*}
+    H^{\prime\top} R^{\prime -1}H' = 
+    \begin{bmatrix}
+        a & b \\
+        c & d
+    \end{bmatrix}\,.
+\end{equation*}
+
+The above formulation allows the use of our encryption scheme given to privately aggregate measurement matrix and vector above.
+Scheme encrypted weights $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$ are computed at each time step at the navigator, and each element of the measurement matrix and vector above is computed as a linear combination and prepared for aggregation at the navigator.
+
+Lastly, since we aggregate multiple linear combinations at each time step (each element in the result matrix and vector comes from a seperate aggregation), we require unique hash values for each aggregation.
+This is handled by hashing $t \| i \| j$ rather than $t$ for each element $x_{i,j}$ when computing combined aggregation encryption in \eqref{eqn:our_scheme_lin_comb}.
 
@@
 Piece together the whole algorithm here.
-Give the algorithm as pseudocode (including encoding and encryption)
+Give the algorithm as pseudocode (including encoding and encryption, possible as separate procedures)
 
@@
 % \end{algorithm}
+\subsection{Leakage}
+We recall the assumptions made in problem formulation and our encryption scheme, and the allowed leakage of the encryption scheme.
+Sensors are honest but curious, meaning sensor values cannot be modified from what is measured, and the protocol is followed exactly, and that the navigator sends the same state information to all sensors at each time step.
+This is justified to an extent with wireless broadcasting being received by all sensors in a typical localisation setting.
+
+From the above restrictions, sensors learn only their measurements $x_i$, and the navigator learns only the sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$.
+
+For malicious subsets not including the navigator, it is clear that they learn nothing more about the navigator location than what they can deduce given only their own measurements.
+
+The navigator, which may maliciously choose weights at every time step, is always restricted to learning at most the sum $\sum^n_{i=1} a_i$ for some values $a_i$ derived from sensor $i$ location and measurement.
+It is therefore intuitive to say that at most the navigator can learn the average of values kept private, that is, the navigator can at most learn the average position and location of sensors.
+The same can be said for any corrupted subset of honest but curious sensors and malicious navigator.
 
@@
 Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
-All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense).
+All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense):
 
@@
 
-A well-defined example.
+Discuss the meaning of the small changes in accuracy, and runtimes when using the same encryption size, that is, point out it is a generally robust method.
 
@@
 \section{Conclusion}
-Possible future work to consider writing here:
-Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors.
+Possible future work to consider: Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors or a way to confirm they are the same.
 

### 2020-09-02 main.tex
Reordered measurement section and split into two subsections More big comments for the remaining subsections

@@
 
+% 
+% ##     ##   ###    ##     ##    ###      ########  ########  #######   ######  
+% ##     ##  ##       ##   ##       ##     ##     ## ##       ##     ## ##    ## 
+% ##     ## ##         ## ##         ##    ##     ## ##       ##     ## ##       
+% ######### ##          ###          ##    ########  ######   ##     ##  ######  
+% ##     ## ##         ## ##         ##    ##   ##   ##       ##  ## ##       ## 
+% ##     ##  ##       ##   ##       ##     ##    ##  ##       ##    ##  ##    ## 
+% ##     ##   ###    ##     ##    ###      ##     ## ########  ##### ##  ######  
+%
+
 \subsection{Requirements for Measurement Model}
@@
 
-\subsection{Localisation Measurement Modification}
+% 
+%  #######  ########   ######     ##     ##  #######  ########  ######## ##       
+% ##     ## ##     ## ##    ##    ###   ### ##     ## ##     ## ##       ##       
+% ##     ## ##     ## ##          #### #### ##     ## ##     ## ##       ##       
+% ##     ## ########   ######     ## ### ## ##     ## ##     ## ######   ##       
+% ##     ## ##     ##       ##    ##     ## ##     ## ##     ## ##       ##       
+% ##     ## ##     ## ##    ##    ##     ## ##     ## ##     ## ##       ##       
+%  #######  ########   ######     ##     ##  #######  ########  ######## ######## 
+%
+
+\subsection{Localisation Measurement Model}
 % Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
@@
 
-Our proposed solution to this problem, is squaring sensor measurements used for the filter.
-\begin{equation*}
-    \begin{split}
-        z^2 &= (h(x) + n)^2 \\
-        &= h(x)^2 + 2nh(x) + n^2
-    \end{split}\,,
-\end{equation*}
-where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
-We account for the non-zero mean by offsetting the the squared measurement and taking this as the adjust measurement model $h'(x) = h(x)^2$, and
-\begin{equation*}
-    \begin{split}
-        z' &= h'(x) + 2nh(x) + n^2 - \sigma^2 \\
-        &= h'(x) + n'
-    \end{split}\,,
-\end{equation*}
-with variance approximated as $2(2z^2\sigma^2 + \sigma^4)$, which uses the original measurement $z$ as an unbiased estimate for $h(x)$.
-
-While the above transformation provides a measurement model that no longer has Gaussian noise, it allows for the linear formulation required for the encryption scheme, and privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
+Our proposed solution to this problem, is working with the adjust measurement function $h'(x) = h(x)^2$.
+The method for modifying a normal range-sensor measurment in this way and handling the no-longer Gaussian, distance-dependant variance of the measurement noise, will be discussed in Section \ref{subsec:range_measurement_mod}.
+While this transformation complicated the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
 The adjusted measurement function is now given by
@@
 
-The above formulation allows the use of our encryption scheme given to privately aggregate measurement matrix and vector above.
-Scheme encrypted weights $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$ are computed at each time step at the navigator, and each element of the measurement matrix and vector above is computed as a linear combination and prepared for aggregation at the navigator.
+The above formulation allows the application of our encryption scheme to the private aggregation of the measurement matrix and vector above.
+The scheme's encrypted weights $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$ are computed at each time step by the navigator, and each element of the measurement matrix and vector above is computed as a linear combination and prepared for aggregation by the sensors.
 
@@
 
+% 
+%  ######   #######  ##     ##    ###    ########  ######## ########     ######## 
+% ##    ## ##     ## ##     ##   ## ##   ##     ## ##       ##     ##         ##  
+% ##       ##     ## ##     ##  ##   ##  ##     ## ##       ##     ##        ##   
+%  ######  ##     ## ##     ## ##     ## ########  ######   ##     ##       ##    
+%       ## ##  ## ## ##     ## ######### ##   ##   ##       ##     ##      ##     
+% ##    ## ##    ##  ##     ## ##     ## ##    ##  ##       ##     ##     ##      
+%  ######   ##### ##  #######  ##     ## ##     ## ######## ########     ######## 
+%
+
+\subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
+The conversion of measurement function $h'(x) = h(x)^2$ is in practice complicated by gausian nature of the range sensor measurement noise.
+As we only know $z = h(x) + n$, where $n~\mathcal{N}(0,\sigma)$, we can estimate the new measurement $z'= z^2$.
+This results in the new measurement
+\begin{equation*}
+    \begin{split}
+        z^2 &= (h(x) + n)^2 \\
+        &= h(x)^2 + 2nh(x) + n^2 \\
+        &= h'(x) + 2nh(x) + n^2
+    \end{split}\,,
+\end{equation*}
+where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
+We account for the non-zero mean by offsetting the the squared measurement and taking this as the adjusted measurement model
+\begin{equation*}
+    \begin{split}
+        z' &= h'(x) + 2nh(x) + n^2 - \sigma^2 \\
+        &= h'(x) + n'
+    \end{split}\,,
+\end{equation*}
+with variance of $n'$ approximated as $2(2z^2\sigma^2 + \sigma^4)$, by using the original measurement $z$ as an unbiased estimate for $h(x)$.
+
+% 
+%    ###    ##        ######    #######  ########  #### ######## ##     ## ##     ## 
+%   ## ##   ##       ##    ##  ##     ## ##     ##  ##     ##    ##     ## ###   ### 
+%  ##   ##  ##       ##        ##     ## ##     ##  ##     ##    ##     ## #### #### 
+% ##     ## ##       ##   #### ##     ## ########   ##     ##    ######### ## ### ## 
+% ######### ##       ##    ##  ##     ## ##   ##    ##     ##    ##     ## ##     ## 
+% ##     ## ##       ##    ##  ##     ## ##    ##   ##     ##    ##     ## ##     ## 
+% ##     ## ########  ######    #######  ##     ## ####    ##    ##     ## ##     ## 
+%
+
+\subsection{Algorithm}
 % Maybe name the scheme? That would be in the heading here
-\subsection{Algorithm}
 Piece together the whole algorithm here.
@@
 % \end{algorithm}
+
+% 
+% ##       ########    ###    ##    ##    ###     ######   ######## 
+% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
+% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
+% ##       ######   ##     ## #####    ##     ## ##   #### ######   
+% ##       ##       ######### ##  ##   ######### ##    ##  ##       
+% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
+% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
+%
+
 \subsection{Leakage}

### 2020-09-03 main.tex
Wrote up more detailed dot points for problem formulation Added missing equations for measurement matrix and vector in linear combination form - notation consistency still ignored in the dot point sections - todo when writing it up

@@
 \subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides''
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm
 
@@
 \section{Problem Statement} \label{sec:problem_statement}
-
-Restate the scenario but more formally. Give a concrete example - plane and signal towers.
-
-Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
+% Restate the scenario but more formally. Give a concrete example - plane and signal towers.
+
+% Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
 Note that learning only the sum in aggregation (as is normal in AO) would, in this case, tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
 
-Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear).
+% Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear).
 Any largely incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.).
@@
 
-Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
+% Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
 In a wireless setting, all sensors would receive all broadcast weights anyway.
@@
 
-Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known
-
-Rough computational capabilities expected by parties
-
-Fixed sensor subsets of which only whole subsets can be used at once.
+% Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known
+
+% Rough computational capabilities expected by parties
+
+% Fixed sensor subsets of which only whole subsets can be used at once.
 Maybe a picture of what this might look like in a high level distributed localisation diagram.
@@
 This should be considered when choosing sensor subsets and locations.
+
+The problem we will consider is a model-based localisation estimation problem in the presence of $n$ range-only sensors. This is defined by the typical process model
+\begin{equation}
+    x_k = f(x_{k-1})+w_k
+\end{equation}
+and measurement model
+\begin{equation}
+    z_k = h(x_k)+v_k\,,
+\end{equation}
+at time $k$, with zero-mean Gaussian noises $w_k \sim \mathcal{N}(0, Q)$ and $v_k \sim \mathcal{N}(0, R)$.
+The measurement function $h(\cdot)$ for range-sensors is dependant on state location vector $x_{k,loc}$ and sensor location $s_{i,loc},\,1\leq i \leq n$.
+It is given by
+\begin{equation}
+    h(x_k) = \|x_{k,loc} - s_{i,loc}\|\,.
+\end{equation}
+We are interested in running the above estimation filter in which the estimator (in this case navigator) does not disclose state information $x_k$ to sensors, while sensors do not disclose their individual measurements $z_k$, and locations $s_{i,loc}$, to the navigator.
+
+We motivate this scenario with the example of aircraft navigation, when in the presence of privately-owned range-measuring towers.
+It is reasonable to assume that the current state of an aircraft may wish to be kept private from unknown tower-owning parties, while sensor tower locations may not wish to be disclosed to any navigating aircraft.
+
+In addition to the broad security desires above, we set some restrictions on the capabilities of participants in the navigation scenario, under which we will prove the security of our proposed scheme.
+\begin{description}
+    \item[Navigator] Due to the desire to keep sensor measurements and locations private from the navigator, and the non-linear nature of the measurement model considered, our protocol will require bi-directional communication between sensors and navigator.
+We will assume that information broadcast by the navigator is received by \textit{all} sensors, and their received information is always equal.
+In the context of wireless communication, such as aircraft locations, commonly used non-directional antennas are such that this assumption is reasonable.
+While hardware-specific methods may exist for broadcasting different information to individual sensors, we will consider this beyond the scope of our work.
+    \item[Sensors] We will adopt the honest-but-curious attacker model for sensors in our localisation method.
+That is, sensors will be assumed to follow the derived procedure correctly, but may use any gained sensitive information for other purposes.
+This is an inherent problem in estimation theory, often requiring inconsistency or outlier detection by the estimator.
+When keeping individual sensor measurements private, it can complicate this detection.
+For this reason, we exclude the possibility of Byzantine-failing sensors to simplify our construction and leave this for future work.
+\end{description}
+
+Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, where leakage formalised in the developed linear-combination aggregation scheme is considered in our localisation problem context.
+Accepted leakage of private information will be bound by the average of private sensor values.
+That is, the average location and average measurement of all honest sensors are at most what can be leaked to the navigator, while no information about the navigator state will be leaked to sensors.
+
+The computational requirements of the navigator and sensors are predominantly defined by encryption, decryption and homomorphic operations.
+We make the implicit assumption that all involved parties are computationally capable of computing the described encryption scheme and filter.
+
+A problem that arises in some navigation environments when constrained by the requirement that all sensors receive navigator broadcast information, is when some sensors are not within measurement range at all times.
+We note that this can be handled by considering subsets of sensors for which overlapping measurement ranges can be used as separate areas within which our localisation method can be performed using only the relevant subset of sensors.
+As a navigator moves from one such area to another, it will perform the protocol with the new set of sensors whose signal it is in range of.
 
@@
     \begin{bmatrix}
-        a & b \\
-        c & d
+        \frac{x_0 - s_x}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} \\
+        \frac{y_0 - s_y}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} 
     \end{bmatrix}\,.
@@
 Our proposed solution to this problem, is working with the adjust measurement function $h'(x) = h(x)^2$.
-The method for modifying a normal range-sensor measurment in this way and handling the no-longer Gaussian, distance-dependant variance of the measurement noise, will be discussed in Section \ref{subsec:range_measurement_mod}.
+The method for modifying a normal range-sensor measurement in this way and handling the no-longer Gaussian measurement noise with variance dependant on distance, will be discussed in Section \ref{subsec:range_measurement_mod}.
 While this transformation complicated the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
@@
     \begin{bmatrix}
-        a & b \\
-        c & d
+        2x_0 - 2s_x \\
+        2y_0 - 2s_y
     \end{bmatrix}\,.
@@
 \begin{equation*}
-    H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = 
-    \begin{bmatrix}
-        a \\
-        b
+    \begin{split}
+        H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
+        &\begin{bmatrix}
+            \begin{split}
+                &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
+                &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
+                &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
+                &\quad+ (-2R^{\prime -1}s_x)y^2
+            \end{split}
+            \vspace{5pt}\\
+            \begin{split}
+                &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
+                &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
+                &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
+                &\quad+ (-2R^{\prime -1}s_y)y^2
+            \end{split}
         \end{bmatrix}
+    \end{split}
 \end{equation*}
@@
     \begin{bmatrix}
-        a & b \\
-        c & d
-    \end{bmatrix}\,.
-\end{equation*}
+        \alpha_{11} & \alpha_{12} \\
+        \alpha_{21} & \alpha_{22}
+    \end{bmatrix}\,,
+\end{equation*}
+with
+\begin{align*}
+    \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
+    \begin{split}
+        \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
+        &\qquad+ (4R^{\prime -1}s_xs_y)
+    \end{split}\\
+    \alpha_{21} &= \alpha_{12} \\
+    \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
+\end{align*}
 
@@
 
-Lastly, since we aggregate multiple linear combinations at each time step (each element in the result matrix and vector comes from a seperate aggregation), we require unique hash values for each aggregation.
-This is handled by hashing $t \| i \| j$ rather than $t$ for each element $x_{i,j}$ when computing combined aggregation encryption in \eqref{eqn:our_scheme_lin_comb}.
+Lastly, since we aggregate multiple linear combinations at each time step $k$ (each element in the result matrix and vector comes from a separate aggregation), we require unique hash values for each aggregation.
+This is handled by hashing by using setting time variable $t$ as concatenation $k \| i \| j$ for each element $x_{i,j}$.
+Aggregation of each element is now performed under a different encryption scheme ``time'', when computing \eqref{eqn:our_scheme_lin_comb}.
 
@@
 where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
-We account for the non-zero mean by offsetting the the squared measurement and taking this as the adjusted measurement model
+We account for the non-zero mean by offsetting the squared measurement and taking this as the adjusted measurement model
 \begin{equation*}
@@
 
-\subsection{Leakage}
+\subsection{Leakage} \label{subsec:leakage}
 We recall the assumptions made in problem formulation and our encryption scheme, and the allowed leakage of the encryption scheme.
@@
 
-\begin{ack}                               % Place acknowledgements
-Partially supported by the Roman Senate.  % here.
+% Place acknowledgements
+% here.
+\begin{ack}                               
+Partially supported by zim
 \end{ack}
 
-\bibliographystyle{plain}        % Include this if you use bibtex 
+% Include this if you use bibtex 
 % and a bib file to produce the 
@@
 % Elsevier at the time of printing.
+\bibliographystyle{plain}
 \bibliography{BibTeX/PrivateEIFLocalisation}

### 2020-09-03 main.tex
Fixed some things in problem formulation notes and from filter description yesterday - also added the fact that we only consider 2 dimensional localisation

@@
 
-The problem we will consider is a model-based localisation estimation problem in the presence of $n$ range-only sensors. This is defined by the typical process model
+The problem we will consider is a two-dimensional model-based localisation estimation problem in the presence of $n$ range-only sensors. This is defined by the typical process model
 \begin{equation}
@@
 It is reasonable to assume that the current state of an aircraft may wish to be kept private from unknown tower-owning parties, while sensor tower locations may not wish to be disclosed to any navigating aircraft.
+Although we will consider the two-dimensional case for simplicity, the extension to three dimensions is trivial at the cost of communication complexity, as will be made clear in Section \ref{subsec:observation_model}.
 
@@
 
-Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed and the prediction computed normally
+Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
 
@@
 Using the EIF and distance sensors, we see that the required computation of measurement vector and matrices is reduced to computing $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, for one-dimensional $R$ and jacobian $H$, at each sensor.
-As this is requires current state information $x$, relevant attributes need to be sent to the sensors.
-
-We wish to encrypt current state information and use the encryption scheme defined to compute measurement information $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ as a linear combination of state information, and encrypt it for aggregation.
-Thus allowing the navigator to only learn sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$ and update its position.
+As this requires current state information $x$, relevant attributes need to be sent to the sensors.
+
+We wish to encrypt current state information and use the encryption scheme defined to compute measurement information $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ as a linear combination of said state information, and encrypt it for aggregation.
+This then allows the navigator to learn only the sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$, which is sufficient to update its position.
 
@@
 
-The requirement introduced above, is that $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ can be computed as linear combinations of state-derived variables.
-Here $H$ is a Jacobian and includes current state information as well.
-
-State-derived variables refer to state vector elements, as well as non-linear functions of these elements, which do not require sensor position or measurement information to be computed.
-As our encryption scheme described above, only supports linear combinations of weights, in this case state-derived variables, all non-linear functions required for measurements information to be computed, need to be treated as individual weights to be combined.
-
+The requirement introduced above, is that measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ can be computed as linear combinations of functions involving only state vector elements.
+In particular, a linear combination of functions which depend only on information available to the navigator.
+In the measurement matrix and vector above, $H$ is the measurement function Jacobian, and includes current state information as well.
+
+As our encryption scheme only supports linear combinations of weights, the weights need to capture all non-linear computations involving state vector elements.
 From the definition of matrix multiplication, we see that any $KxL$ matrix $D=ABC$, where $B$ has dimensions $MxN$, has element $d_{i,j}$ defined by
@@
 and can therefore be considered as a linear combination of all elements $a_{i,m}c_{n,j}$.
-Applying this to the measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, we require that all values of $h(x)$, and all elements in Jacobian $H$ be linear combinations of state-derived variables
-
-Next, we show how this can be achieved for the specific case of 2-dimensional localisation, with range-only sensors.
+Applying this to the measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, we require that all values of $h(x)$, and all elements in Jacobian $H$ be linear combinations of functions dependant on state vector elements and nothing else.
+
+We will show how this can be achieved for the specific case of 2-dimensional localisation, with range-only sensors.
 
@@
 
-\subsection{Localisation Measurement Model}
+\subsection{Localisation Measurement Model} \label{subsec:observation_model}
 % Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
@@
 
-From our problem statements in Section $\cdot$, we specify the goal of private localisation in the 2-dimensional case, using range-only sensors.
+From our problem statement in Section \ref{sec:problem_statement}, we specify the goal of private localisation in the 2-dimensional case, using range-only sensors.
 Given the current location estimate $x_{loc} = (x,y)$, which may comprise only part of the filter state estimate, and sensor location $s_{loc} = (s_x, s_y)$, the measurement equation is given by
@@
 \end{equation*}
-The problem with the above function $h$ and Jacobian $H$ is that they cannot be reformulated as a linear combination of weights, where weights are defined by functions of $x$ and $y$, and do not include $s_x$ and $s_y$.
-
-Our proposed solution to this problem, is working with the adjust measurement function $h'(x) = h(x)^2$.
+The problem with the above function $h$ and Jacobian $H$ is that they cannot be reformulated as a linear combination of weights, where weights do not depend on $s_x$ and $s_y$.
+
+Our proposed solution to this problem, is working with the adjusted measurement function $h'(x) = h(x)^2$.
 The method for modifying a normal range-sensor measurement in this way and handling the no-longer Gaussian measurement noise with variance dependant on distance, will be discussed in Section \ref{subsec:range_measurement_mod}.
-While this transformation complicated the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
+While this transformation complicates the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
 The adjusted measurement function is now given by
@@
 \end{equation*}
-The above function and jacobian elements are linear combinations of state-derived functions $x$, $x^2$, $y$, $xy$ and $y^2$.
-From our equation $\cdot$ in the previous section, we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of state-derived functions $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
+The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$.
+From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
 \begin{equation*}
@@
 Lastly, since we aggregate multiple linear combinations at each time step $k$ (each element in the result matrix and vector comes from a separate aggregation), we require unique hash values for each aggregation.
-This is handled by hashing by using setting time variable $t$ as concatenation $k \| i \| j$ for each element $x_{i,j}$.
-Aggregation of each element is now performed under a different encryption scheme ``time'', when computing \eqref{eqn:our_scheme_lin_comb}.
+This is handled by setting time variable $t$ as concatenation $k \| i \| j$ for each element $x_{i,j}$.
+Aggregation of each element is now performed under a different encryption scheme ``time'' step, when computing \eqref{eqn:our_scheme_lin_comb}.
+
+The solution above has been derived for the two-dimensional localisation case but it is easy to see that a similar solution would work in three-dimensional space.
+The cost of increasing localisation dimension however, is the increased number of state vector element functions required for broadcast by the navigator, and length of linear combination computed by sensors.
 
@@
 \subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-The conversion of measurement function $h'(x) = h(x)^2$ is in practice complicated by gausian nature of the range sensor measurement noise.
-As we only know $z = h(x) + n$, where $n~\mathcal{N}(0,\sigma)$, we can estimate the new measurement $z'= z^2$.
+The conversion of measurement function $h'(x) = h(x)^2$ is in practice complicated by measurement noise manipulation.
+As we only know $z = h(x) + n$, where $n~\mathcal{N}(0,\sigma)$, we can estimate the new measurement as $z^2$.
 This results in the new measurement
@@
 \subsection{Leakage} \label{subsec:leakage}
-We recall the assumptions made in problem formulation and our encryption scheme, and the allowed leakage of the encryption scheme.
+We recall the assumptions made in the problem formulation and our encryption scheme, and the allowed leakage of the encryption scheme.
 Sensors are honest but curious, meaning sensor values cannot be modified from what is measured, and the protocol is followed exactly, and that the navigator sends the same state information to all sensors at each time step.
@@
 
-The navigator, which may maliciously choose weights at every time step, is always restricted to learning at most the sum $\sum^n_{i=1} a_i$ for some values $a_i$ derived from sensor $i$ location and measurement.
+The navigator, which may maliciously choose weights at every time step, is always restricted to learning at most the sum $\sum^n_{i=1} a_i$ for some values $a_i$ derived from sensor $i$'s location and measurement.
 It is therefore intuitive to say that at most the navigator can learn the average of values kept private, that is, the navigator can at most learn the average position and location of sensors.

### 2020-09-04 main.tex
Added tikz picture of sensor subsets

@@
 
+% Added operators
 \DeclareMathOperator*{\argmax}{arg\,max}
 \DeclareMathOperator*{\argmin}{arg\,min}
+
+% Tikz settings
+\usetikzlibrary{math}
 
@@
 As a navigator moves from one such area to another, it will perform the protocol with the new set of sensors whose signal it is in range of.
+
+\begin{figure}[htbp]
+\centering
+\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+    % Sizes
+    \tikzmath{\srange = 3.54; \sradius = 0.04;}
+    % Sensor locations (sensor 3 is shared)
+    \coordinate (s1) at (1.132,-4.4338);
+    \coordinate (s2) at (4.0633,-5.9948);
+    \coordinate (s3) at (3.1235,-3.2054);
+    \coordinate (s4) at (4.5563,-1.6861);
+    \coordinate (s5) at (5.9909,-3.5635);
+    % Navigator location
+    \coordinate (nav_loc) at (4,-4);
+    % Bounding rectangle
+    \coordinate (brect_start) at (0,0);
+    \coordinate (brect_end) at (8.0, -8.0);
+
+    % Gray range circles
+    \begin{scope}
+        \clip (brect_start) rectangle (brect_end);
+        \draw[gray!50] (s1) circle (\srange);
+        \draw[gray!50] (s2) circle (\srange);
+        \draw[gray!50] (s3) circle (\srange);
+        \draw[gray!50] (s4) circle (\srange);
+        \draw[gray!50] (s5) circle (\srange);
+    \end{scope}
+    % Red subgroup overlap
+    \begin{scope}
+        \clip (brect_start) rectangle (brect_end);
+        \clip (s3) circle (\srange);
+        \clip (s4) circle (\srange);
+        \clip (s5) circle (\srange);
+        \fill[red!40] (brect_start) rectangle (brect_end);
+    \end{scope}
+    % Blue subgroup overlap
+    \begin{scope}
+        \clip (brect_start) rectangle (brect_end);
+        \clip (s1) circle (\srange);
+        \clip (s2) circle (\srange);
+        \clip (s3) circle (\srange);
+        \fill[blue!40] (brect_start) rectangle (brect_end);
+    \end{scope}
+    % Magenta double overlap
+    \begin{scope}
+        \clip (brect_start) rectangle (brect_end);
+        \clip (s1) circle (\srange);
+        \clip (s2) circle (\srange);
+        \clip (s3) circle (\srange);
+        \clip (s4) circle (\srange);
+        \clip (s5) circle (\srange);
+        \fill[magenta!40] (brect_start) rectangle (brect_end);
+    \end{scope}
+    % Sensors
+    \fill[black] (s1) circle (\sradius);
+    \fill[black] (s2) circle (\sradius);
+    \fill[black] (s3) circle (\sradius);
+    \fill[black] (s4) circle (\sradius);
+    \fill[black] (s5) circle (\sradius);
+    % Bounding box
+    \draw[gray] (brect_start) rectangle (brect_end);
+    % Navigator
+    \clip (brect_start) rectangle (brect_end);
+    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
+        % Plane
+        \draw[fill]  plot[smooth, tension=.6] coordinates {
+        (-0.65,-0.9) 
+        (-0.6,-0.85) 
+        (-0.4,-0.75) 
+        (-0.25,-0.65) 
+        (-0.15,-0.5) 
+        (-0.12,-0.3) 
+        (-0.10,-0.1) 
+        (0.0,0.0) 
+        (0.10,-0.1) 
+        (0.12,-0.3) 
+        (0.15,-0.5) 
+        (0.25,-0.65) 
+        (0.4,-0.75) 
+        (0.6,-0.85) 
+        (0.65,-0.9)
+        } -- plot[smooth, tension=.6] coordinates {
+        (0.65,-0.9) 
+        (0.15,-0.91)
+        (0.35,-1.1) 
+        (0.37,-1.15)
+        } -- plot[smooth, tension=.6] coordinates {
+        (0.37,-1.15)
+        (0.0,-1.12) 
+        (-0.37,-1.15) 
+        } -- plot[smooth, tension=.6] coordinates {
+        (-0.37,-1.15)
+        (-0.35,-1.1) 
+        (-0.15,-0.91) 
+        (-0.65,-0.9) 
+        } -- cycle;
+        % Trail
+        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
+    \end{scope}
+    \node[label=1] at (s1) {};
+    \node[label=2] at (s2) {};
+    \node[label=3] at (s3) {};
+    \node[label=4] at (s4) {};
+    \node[label=5] at (s5) {};
+\end{tikzpicture}
+\caption{Sensor subsets $\{1,2,3\}$ and $\{3,4,5\}$, and the areas within which the navigator is in range of all sensors within a subset.}
+\label{fig:sensor_subsets}
+\end{figure}
 

### 2020-09-08 main.tex
Fixed caption
Writing up problem formulation properly - separated into subsections - Added models and measurement function - started on assumptions/capabilities - moved leakage to end

@@
 
-% Added operators
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
+% User local packages
+\usepackage{ISASmacros/isasmathmacros}
 
@@
 \subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, vector indexing (also note starts at 0)
 
@@
 
-The problem we will consider is a two-dimensional model-based localisation estimation problem in the presence of $n$ range-only sensors. This is defined by the typical process model
-\begin{equation}
-    x_k = f(x_{k-1})+w_k
-\end{equation}
-and measurement model
-\begin{equation}
-    z_k = h(x_k)+v_k\,,
-\end{equation}
-at time $k$, with zero-mean Gaussian noises $w_k \sim \mathcal{N}(0, Q)$ and $v_k \sim \mathcal{N}(0, R)$.
-The measurement function $h(\cdot)$ for range-sensors is dependant on state location vector $x_{k,loc}$ and sensor location $s_{i,loc},\,1\leq i \leq n$.
-It is given by
-\begin{equation}
-    h(x_k) = \|x_{k,loc} - s_{i,loc}\|\,.
-\end{equation}
-We are interested in running the above estimation filter in which the estimator (in this case navigator) does not disclose state information $x_k$ to sensors, while sensors do not disclose their individual measurements $z_k$, and locations $s_{i,loc}$, to the navigator.
-
-We motivate this scenario with the example of aircraft navigation, when in the presence of privately-owned range-measuring towers.
-It is reasonable to assume that the current state of an aircraft may wish to be kept private from unknown tower-owning parties, while sensor tower locations may not wish to be disclosed to any navigating aircraft.
-Although we will consider the two-dimensional case for simplicity, the extension to three dimensions is trivial at the cost of communication complexity, as will be made clear in Section \ref{subsec:observation_model}.
-
-In addition to the broad security desires above, we set some restrictions on the capabilities of participants in the navigation scenario, under which we will prove the security of our proposed scheme.
+The localisation scenario we consider in this work is that of model-based self-navigation using range-only sensors.
+We consider localisation in the two-dimensional case for simplicty, but will derive methods suitable for an extension to the three-dimensional equivalent.
+
+The navigator state is defined as 
+\begin{equation}
+    \vec{x} = 
+    \begin{bmatrix}
+        x & dx & y & dy
+    \end{bmatrix}^\top\,.
+\end{equation}
+A known process model is followed, which at time $k$ is given by
+\begin{equation}
+    \mean{x}_k = f(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
+\end{equation}
+with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
+\begin{equation}
+    z_k = h_i(\mean{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
+\end{equation}
+with noise $\rv{v}_k \sim \mathcal{N}(\vec{0},\mat{R})$, while the measurement function $h_i$, for sensor $i$ at location
+\begin{equation}
+    \vec{s}_i = 
+    \begin{bmatrix}
+        x_{i} & y_{i}
+    \end{bmatrix}^\top\,,
+\end{equation} 
+is defined as
+\begin{equation}
+    \begin{split}
+        h_i(\mean{x}_k) &= \left\|
+        \begin{bmatrix}
+            \mean{x}_{k[0]} \\
+            \mean{x}_{k[2]}
+        \end{bmatrix}
+        - \vec{s}_{i}\right\| \\
+        &= \sqrt{(\mean{x}_{k[0]}-x_{i})^2 + (\mean{x}_{k[2]}-y_{i})^2}\,.
+    \end{split}
+\end{equation}
+We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\mean{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $z_k$ at any time $k$.
+
+We motivate these goals with an example.
+When considering aircraft navigation in the presence of privately-owned range-measuring towers, it is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown tower-owning parties.
+Similarly, tower locations may wish to be kept private from unidentified navigating aircraft.
+However, the additional safety to passengers, provided by accurate aircraft localisation, may be a goal of all those involved.
+
+% 
+%  ######     ###    ########     ###    ########  #### ##       #### ######## #### ########  ######  
+% ##    ##   ## ##   ##     ##   ## ##   ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
+% ##        ##   ##  ##     ##  ##   ##  ##     ##  ##  ##        ##     ##     ##  ##       ##       
+% ##       ##     ## ########  ##     ## ########   ##  ##        ##     ##     ##  ######    ######  
+% ##       ######### ##        ######### ##     ##  ##  ##        ##     ##     ##  ##             ## 
+% ##    ## ##     ## ##        ##     ## ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
+%  ######  ##     ## ##        ##     ## ########  #### ######## ####    ##    #### ########  ######  
+%
+
+\subsection{Participant Capabilities} 
+Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
+
 \begin{description}
-    \item[Navigator] Due to the desire to keep sensor measurements and locations private from the navigator, and the non-linear nature of the measurement model considered, our protocol will require bi-directional communication between sensors and navigator.
-We will assume that information broadcast by the navigator is received by \textit{all} sensors, and their received information is always equal.
-In the context of wireless communication, such as aircraft locations, commonly used non-directional antennas are such that this assumption is reasonable.
+    \item[Global navigator broadcast] Due to sensor location privacy and model non-linearity, bi-directional communication between navigator and sensors is required.
+We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
+
+    \item[Consistent navigator broadcast] Received information is always equal. 
+    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for sensors in our localisation method.
+That is, sensors will be assumed to follow the derived procedure correctly, but may use any gained sensitive information for other purposes.
+    \item[Computational capabilities] The computational requirements of the navigator and sensors are predominantly defined by encryption, decryption and homomorphic operations.
+We make the implicit assumption that all involved parties are computationally capable of computing the described encryption scheme and filter.
+\end{description}
+% In the context of wireless communication, such as aircraft locations, commonly used non-directional antennas are such that this assumption is reasonable.
 While hardware-specific methods may exist for broadcasting different information to individual sensors, we will consider this beyond the scope of our work.
-    \item[Sensors] We will adopt the honest-but-curious attacker model for sensors in our localisation method.
-That is, sensors will be assumed to follow the derived procedure correctly, but may use any gained sensitive information for other purposes.
-This is an inherent problem in estimation theory, often requiring inconsistency or outlier detection by the estimator.
+
+% This is an inherent problem in estimation theory, often requiring inconsistency or outlier detection by the estimator.
 When keeping individual sensor measurements private, it can complicate this detection.
 For this reason, we exclude the possibility of Byzantine-failing sensors to simplify our construction and leave this for future work.
-\end{description}
-
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, where leakage formalised in the developed linear-combination aggregation scheme is considered in our localisation problem context.
-Accepted leakage of private information will be bound by the average of private sensor values.
-That is, the average location and average measurement of all honest sensors are at most what can be leaked to the navigator, while no information about the navigator state will be leaked to sensors.
-
-The computational requirements of the navigator and sensors are predominantly defined by encryption, decryption and homomorphic operations.
-We make the implicit assumption that all involved parties are computationally capable of computing the described encryption scheme and filter.
 
@@
     % Sensor locations (sensor 3 is shared)
-    \coordinate (s1) at (1.132,-4.4338);
+    \coordinate (s1) at (1.4086,-4.5869);
     \coordinate (s2) at (4.0633,-5.9948);
@@
     \end{scope}
+    % Sensor labels
     \node[label=1] at (s1) {};
@@
 \end{tikzpicture}
-\caption{Sensor subsets $\{1,2,3\}$ and $\{3,4,5\}$, and the areas within which the navigator is in range of all sensors within a subset.}
+\caption{An example of sensor subsets; $\{1,2,3\}$ and $\{3,4,5\}$, and the areas where the navigator is in range of all sensors within a subset.}
 \label{fig:sensor_subsets}
 \end{figure}
+
+% 
+% ##       ########    ###    ##    ##    ###     ######   ######## 
+% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
+% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
+% ##       ######   ##     ## #####    ##     ## ##   #### ######   
+% ##       ##       ######### ##  ##   ######### ##    ##  ##       
+% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
+% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
+%
+
+\subsection{Inherent Leakage}
+Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, where leakage formalised in the developed linear-combination aggregation scheme is considered in our localisation problem context.
+Accepted leakage of private information will be bound by the average of private sensor values.
+That is, the average location and average measurement of all honest sensors are at most what can be leaked to the navigator, while no information about the navigator state will be leaked to sensors.
 

### 2020-09-09 main.tex
Problem formulation done Section summary done as well Added labels to all top-level sections

@@
 
-Section Summary
-%In Section \ref{sec:private_localisation} we will show how this scheme can be used to compute the measurement covariance and measurement vector homomorphically at each sensor, and allow the navigator to update their
+--
+
+%Section Summary
+% \ref{sec:problem_statement}
+% \ref{sec:crypto_prelim}
+% \ref{sec:lcao_definition}
+% \ref{sec:our_scheme}
+% \ref{sec:loc_prelim}
+% \ref{sec:private_localisation}
+% \ref{sec:results}
+% \ref{sec:conclusion}
+In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
+Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it.
+Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
+In Section \ref{sec:results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
 
@@
 Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
-
 \begin{description}
@@
 
-    \item[Consistent navigator broadcast] Received information is always equal. 
-    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for sensors in our localisation method.
-That is, sensors will be assumed to follow the derived procedure correctly, but may use any gained sensitive information for other purposes.
-    \item[Computational capabilities] The computational requirements of the navigator and sensors are predominantly defined by encryption, decryption and homomorphic operations.
-We make the implicit assumption that all involved parties are computationally capable of computing the described encryption scheme and filter.
+    A problem caused by this requirement is apparent in the context of aircraft navigation.
+It may be the case that some sensors are not within range of a navigator broadcast.
+We loosely propose that this scenario can be handled by pre-defined sensor subsets during an initial step by a trusted party.
+This has been captured in Figure \ref{fig:sensor_subsets}.
+    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is recieved equal by all sensors.
+This means the navigator may not send different information to individual sensors during a single timestep.
+
+    In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
+    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localisation procedure correctly but may store or use any gained sensitive information.
+
+    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms.
+As privacy-preserving implementations of such mechanisms require additional complications, we do not consider the scenario in this work.
+    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
+We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
 \end{description}
-% In the context of wireless communication, such as aircraft locations, commonly used non-directional antennas are such that this assumption is reasonable.
-While hardware-specific methods may exist for broadcasting different information to individual sensors, we will consider this beyond the scope of our work.
-
-% This is an inherent problem in estimation theory, often requiring inconsistency or outlier detection by the estimator.
-When keeping individual sensor measurements private, it can complicate this detection.
-For this reason, we exclude the possibility of Byzantine-failing sensors to simplify our construction and leave this for future work.
-
-A problem that arises in some navigation environments when constrained by the requirement that all sensors receive navigator broadcast information, is when some sensors are not within measurement range at all times.
-We note that this can be handled by considering subsets of sensors for which overlapping measurement ranges can be used as separate areas within which our localisation method can be performed using only the relevant subset of sensors.
-As a navigator moves from one such area to another, it will perform the protocol with the new set of sensors whose signal it is in range of.
-
 \begin{figure}[htbp]
@@
 \subsection{Inherent Leakage}
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, where leakage formalised in the developed linear-combination aggregation scheme is considered in our localisation problem context.
-Accepted leakage of private information will be bound by the average of private sensor values.
-That is, the average location and average measurement of all honest sensors are at most what can be leaked to the navigator, while no information about the navigator state will be leaked to sensors.
+Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates naturally leads to the leakage of some measurement information.
+For this reason, we accept that average information about sensors may be leaked at each time step and instead show that individual sensor information remains private.
 
@@
 
-\section{Private Linear-Combination Aggregation}
+\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
 For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation.
@@
 
-\section{Private Localisation Preliminaries}
+\section{Private Localisation Preliminaries} \label{sec:loc_prelim}
 The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model.
@@
 
-\section{Results}
+\section{Results} \label{sec:results}
 Time results can be captured in one graph.
@@
 
-\section{Conclusion}
+\section{Conclusion} \label{sec:conclusion}
 Possible future work to consider: Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors or a way to confirm they are the same.

### 2020-09-10 main.tex
EIF section just about done, last sentence missing

@@
 \begin{equation}
-    \mean{x}_k = f(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
+    \mean{x}_k = \vec{f}(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
 \end{equation}
@@
 \subsection{Extended Information Filter}
-EIF is a reformulation of the EKF where the update step is reduced to sums. Makes it especially easier for processing multiple measurements.
-
-Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
-
-% The Extended Information Filter (EIF) is an algebraic reformulation of the Extended Kalman Filter (EKF) such that the update step is reduced to a simple summation.
-Given process and measurement models \eqref{} and \eqref{}, the EIF update equation is given by
-% \begin{equation}
-%     a
-% \end{equation}
+Given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, the Extended Information Filter (EIF) is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simpified to sums of measurement information from each sensor.
+This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix forms
+\begin{equation}
+    \mean{y}_k = \mat{P}_k^{-1}\mean{x}_k
+\end{equation}
+and
+\begin{equation}
+    \mat{Y}_k = \mat{P}_k^{-1}\,.
+\end{equation}
+In this form, the update equations for $n$ measurements at time $k$ are given by
+\begin{equation}
+    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}
+\end{equation}
+and
+\begin{equation}
+    \mean{y}_k = \mean{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k)\,,
+\end{equation}
+with Jacobian
+\begin{equation}
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\mean{x}_k}
+\end{equation}
+for each sensor $1 \leq i \leq n$.
+
+Computing the prediction step of the filter can be done by converting the information vector and matrix back to state estimate and covariance with
+\begin{equation}
+    \mat{P}_k = \mat{Y}_k^{-1}
+\end{equation}
+and
+\begin{equation}
+    \mean{x}_k = \mat{P}_k\mean{y}_k\,,
+\end{equation}
+and using the normal EKF prediction equations
+
+%Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
 

### 2020-09-11 main.tex
Small change, done with EIF section

@@
 \subsection{Extended Information Filter}
-Given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, the Extended Information Filter (EIF) is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simpified to sums of measurement information from each sensor.
+Given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, the Extended Information Filter (EIF) is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
 This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix forms
@@
 for each sensor $1 \leq i \leq n$.
-
-Computing the prediction step of the filter can be done by converting the information vector and matrix back to state estimate and covariance with
-\begin{equation}
-    \mat{P}_k = \mat{Y}_k^{-1}
-\end{equation}
-and
-\begin{equation}
-    \mean{x}_k = \mat{P}_k\mean{y}_k\,,
-\end{equation}
-and using the normal EKF prediction equations
-
-%Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
+Computing the filter's prediction step can be either computed in the information filter form, or by first converting the information vector and matrix back to the state estimate and covariance, and using the normal EKF prediction equations.
 

### 2020-09-11 main.tex
EIF section made better, added a reference for it as well Started on private filter description

--- 2020-09-09 main.tex
@@
 The localisation scenario we consider in this work is that of model-based self-navigation using range-only sensors.
-We consider localisation in the two-dimensional case for simplicty, but will derive methods suitable for an extension to the three-dimensional equivalent.
+We consider localisation in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
 
@@
     A problem caused by this requirement is apparent in the context of aircraft navigation.
-It may be the case that some sensors are not within range of a navigator broadcast.
+It may be the case that some sensors are not within the range of a navigator broadcast.
 We loosely propose that this scenario can be handled by pre-defined sensor subsets during an initial step by a trusted party.
 This has been captured in Figure \ref{fig:sensor_subsets}.
-    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is recieved equal by all sensors.
+    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
 This means the navigator may not send different information to individual sensors during a single timestep.
@@
 \subsection{Extended Information Filter}
-EIF is a reformulation of the EKF where the update step is reduced to sums. Makes it especially easier for processing multiple measurements.
-
-Prediction step can be computed in either the EIF form or the equivalent EKF state and covariance can be computed before performing the prediction step in EKF form and converting the result back.
-
-% The Extended Information Filter (EIF) is an algebraic reformulation of the Extended Kalman Filter (EKF) such that the update step is reduced to a simple summation.
-Given process and measurement models \eqref{} and \eqref{}, the EIF update equation is given by
-% \begin{equation}
-%     a
-% \end{equation}
+The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
+This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
+\begin{equation}
+    \mean{y}_k = \mat{P}_k^{-1}\mean{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
+\end{equation}
+respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
+\begin{equation}
+    \mean{y}_k = \mean{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
+\end{equation}
+and
+\begin{equation}
+    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
+\end{equation}
+with Jacobian
+\begin{equation}
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\mean{x}_k} \label{eqn:measurement_jacobian}
+\end{equation}
+for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\mean{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
+\begin{equation}
+    \mean{x}_k = \mat{Y}_k^{-1}\mean{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
+\end{equation}
+before using the normal EKF prediction equations
+\begin{equation}
+    \mean{x}_k = \vec{f}(\mean{x}_{k-1})
+\end{equation}
+and
+\begin{equation}
+    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
+\end{equation}
+with Jacobian
+\begin{equation}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\mean{x}_k}\,.
+\end{equation}
 
@@
 \section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
+Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}.
+We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
+Received information from each sensor $i$ consists of the measurement vector
+\begin{equation}
+    \vec{i}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k)
+\end{equation}
+and the measurement matrix
+\begin{equation}
+    \mat{I}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,,
+\end{equation}
+at each time step $k$.
+All sensitive sensor information is captured exclusively in the filter by the Products $\vec{i}_i$ and $\mat{I}_i$, namely their measurements $z_{k,i}$, measurement variances $\mat{R}_i$ and locations, captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
+Encryption of $\vec{i}_i$ and $\mat{I}_i$ at the sensors would, however, disclose the location information of $\mean{x}_k$, required for computing Jacobians $\mat{H}_{k,i}$ in \eqref{eqn:measurement_jacobian}.
+
+--
+
 % Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
@@
 This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.
-
-Using the EIF and distance sensors, we see that the required computation of measurement vector and matrices is reduced to computing $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, for one-dimensional $R$ and jacobian $H$, at each sensor.
-As this requires current state information $x$, relevant attributes need to be sent to the sensors.
 

### 2020-09-15 main.tex
Made a lot of changes to notation Started on writing the filter section properly - intro bit done - measurement function requirements done (and merged into intro bit - started on the observation model modification section - redid the big equations with new notation

@@
 \begin{equation}
-    \vec{x} = 
+    \rvec{x} = 
     \begin{bmatrix}
-        x & dx & y & dy
-    \end{bmatrix}^\top\,.
+        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
+    \end{bmatrix}^\top\,. \label{eqn:state_def}
 \end{equation}
@@
 \begin{equation}
-    \mean{x}_k = \vec{f}(\mean{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
+    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
 \end{equation}
@@
 \begin{equation}
-    z_k = h_i(\mean{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
-\end{equation}
-with noise $\rv{v}_k \sim \mathcal{N}(\vec{0},\mat{R})$, while the measurement function $h_i$, for sensor $i$ at location
+    \rv{z}_k = h_i(\rvec{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
+\end{equation}
+with noise $\rv{v}_k \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
 \begin{equation}
@@
     \begin{bmatrix}
-        x_{i} & y_{i}
+        s_{x,i} & s_{y,i}
     \end{bmatrix}^\top\,,
@@
     \begin{split}
-        h_i(\mean{x}_k) &= \left\|
+        h_i(\rvec{x}_k) &= \left\|
         \begin{bmatrix}
-            \mean{x}_{k[0]} \\
-            \mean{x}_{k[2]}
-        \end{bmatrix}
+            \rv{x}_k & \rv{y}_k
+        \end{bmatrix}^\top
         - \vec{s}_{i}\right\| \\
-        &= \sqrt{(\mean{x}_{k[0]}-x_{i})^2 + (\mean{x}_{k[2]}-y_{i})^2}\,.
+        &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
     \end{split}
 \end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\mean{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $z_k$ at any time $k$.
+We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $\rv{z}_k$ at any time $k$.
 
@@
 The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
-This requires the conversion of state estimate $\mean{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
-\begin{equation}
-    \mean{y}_k = \mat{P}_k^{-1}\mean{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
+This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
+\begin{equation}
+    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
 \end{equation}
@@
 \begin{equation}
-    \mean{y}_k = \mean{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
+    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
 \end{equation}
@@
 \begin{equation}
-    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
+    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
 \end{equation}
@@
 \begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\mean{x}_k} \label{eqn:measurement_jacobian}
-\end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\mean{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
-\begin{equation}
-    \mean{x}_k = \mat{Y}_k^{-1}\mean{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
+\end{equation}
+for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
+\begin{equation}
+    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
 \end{equation}
@@
 \begin{equation}
-    \mean{x}_k = \vec{f}(\mean{x}_{k-1})
+    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
 \end{equation}
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\mean{x}_k}\,.
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_k}\,.
 \end{equation}
@@
 \begin{equation}
-    \vec{i}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k)
+    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
 \end{equation}
@@
 \begin{equation}
-    \mat{I}_i = \mat{H}^\top_{k,i} \mat{R}^{-1}_i \mat{H}_{k,i}\,,
+    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
 \end{equation}
 at each time step $k$.
-All sensitive sensor information is captured exclusively in the filter by the Products $\vec{i}_i$ and $\mat{I}_i$, namely their measurements $z_{k,i}$, measurement variances $\mat{R}_i$ and locations, captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-Encryption of $\vec{i}_i$ and $\mat{I}_i$ at the sensors would, however, disclose the location information of $\mean{x}_k$, required for computing Jacobians $\mat{H}_{k,i}$ in \eqref{eqn:measurement_jacobian}.
-
---
-
-% Explain it in as an overview. How is the aggregation scheme used, what does this require from the measurement model, why can this be a problem for normal distance sensors?
-
-% Explain how leakage of the final aggregation sum to the navigator means leakage of the average sensor location and measurement to the navigator.
-This is the reason for the acceptance of this leakage, as we pointed out in the problem statement section.
-
-We wish to encrypt current state information and use the encryption scheme defined to compute measurement information $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ as a linear combination of said state information, and encrypt it for aggregation.
-This then allows the navigator to learn only the sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$, which is sufficient to update its position.
-
-% 
-% ##     ##   ###    ##     ##    ###      ########  ########  #######   ######  
-% ##     ##  ##       ##   ##       ##     ##     ## ##       ##     ## ##    ## 
-% ##     ## ##         ## ##         ##    ##     ## ##       ##     ## ##       
-% ######### ##          ###          ##    ########  ######   ##     ##  ######  
-% ##     ## ##         ## ##         ##    ##   ##   ##       ##  ## ##       ## 
-% ##     ##  ##       ##   ##       ##     ##    ##  ##       ##    ##  ##    ## 
-% ##     ##   ###    ##     ##    ###      ##     ## ########  ##### ##  ######  
-%
-
-\subsection{Requirements for Measurement Model}
-% Must be such that Jacobian consists of linear combinations of state-related variables
-
-The requirement introduced above, is that measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$ can be computed as linear combinations of functions involving only state vector elements.
-In particular, a linear combination of functions which depend only on information available to the navigator.
-In the measurement matrix and vector above, $H$ is the measurement function Jacobian, and includes current state information as well.
-
-As our encryption scheme only supports linear combinations of weights, the weights need to capture all non-linear computations involving state vector elements.
-From the definition of matrix multiplication, we see that any $KxL$ matrix $D=ABC$, where $B$ has dimensions $MxN$, has element $d_{i,j}$ defined by
-\begin{equation*}
-    d_{i,j} = \sum^{N}_{n=1}\sum^{M}_{m=1}a_{i,m}b_{m,n}c_{n,j}\,,
-\end{equation*}
-and can therefore be considered as a linear combination of all elements $a_{i,m}c_{n,j}$.
-Applying this to the measurement matrix and vector $H^\top R^{-1}(z - h(x) + Hx)$ and $H^\top R^{-1}H$, we require that all values of $h(x)$, and all elements in Jacobian $H$ be linear combinations of functions dependant on state vector elements and nothing else.
-
-We will show how this can be achieved for the specific case of 2-dimensional localisation, with range-only sensors.
+In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
+
+Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$.
+Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
+As was shown in Section \ref{sec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.
+As matrix multiplication and scalar multiplication both preserve linearity, it is sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
+Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.
 
@@
 \subsection{Localisation Measurement Model} \label{subsec:observation_model}
-% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
-
-% Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
-Give flight navigation as an applicable example with typically high distances.
-
-% Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
-
-From our problem statement in Section \ref{sec:problem_statement}, we specify the goal of private localisation in the 2-dimensional case, using range-only sensors.
-Given the current location estimate $x_{loc} = (x,y)$, which may comprise only part of the filter state estimate, and sensor location $s_{loc} = (s_x, s_y)$, the measurement equation is given by
-\begin{equation*}
+Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we see that $h_i$ cannot be rearranged to a linear combination of elements private to the navigator.
+In addition, the Jacobian of $h_i$,
+\begin{equation}
+    \mat{H}_{k,i} = 
+    \begin{bmatrix}
+        \frac{\rv{x}_k - s_x}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} \\
+        \frac{\rv{y}_k - s_y}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} 
+    \end{bmatrix}\,,
+\end{equation}
+cannot be either. Instead, we consider the adjusted measurement functions
+\begin{equation}
+    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:adjusted_measurement_funcs}
+\end{equation}
+Measurement functions in this form allow rearrangement of the corresponding adjusted measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ into linear combinations of navigator information.The modified measurement functions $h'_i$ can be written as
+\begin{equation}
     \begin{split}
-        h(x) &= \|x_{loc} - s_{loc}\| \\
-        &= \sqrt{(x - s_x)^2 + (y - s_y)^2}\,.
-    \end{split}
-\end{equation*}
-The Jacobian $H$ for the measurement function above at $x_{loc,0}=(x_0, y_0)$ is then given by
-\begin{equation*}
-    H = 
+        h'_i(\rvec{x}_k) &= \left\|
         \begin{bmatrix}
-        \frac{x_0 - s_x}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} \\
-        \frac{y_0 - s_y}{\sqrt{(x_0 - s_x)^2 + (y_0 - s_y)^2}} 
+            \rv{x}_k & \rv{y}_k
+        \end{bmatrix}^\top - \vec{s}_i\right\|^2 \\
+        &= (\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2 \\
+        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_x\rv{x}_k -2s_y\rv{y}_k +s_x^2 +s_y^2
+    \end{split}\,,
+\end{equation}
+and the corresponding Jacobians $\mat{H}'_{k,i}$ as
+\begin{equation}
+    \mat{H}'_{k,i} = 
+    \begin{bmatrix}
+        2\rv{x}_k - 2s_x \\
+        2\rv{y}_k - 2s_y
     \end{bmatrix}\,.
-\end{equation*}
-The problem with the above function $h$ and Jacobian $H$ is that they cannot be reformulated as a linear combination of weights, where weights do not depend on $s_x$ and $s_y$.
-
-Our proposed solution to this problem, is working with the adjusted measurement function $h'(x) = h(x)^2$.
-The method for modifying a normal range-sensor measurement in this way and handling the no-longer Gaussian measurement noise with variance dependant on distance, will be discussed in Section \ref{subsec:range_measurement_mod}.
-While this transformation complicates the measurement model noise, it allows for the linear formulation required for the encryption scheme, and the privacy of $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$.
-The adjusted measurement function is now given by
-\begin{equation*}
+\end{equation}
+The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.
+
+As stated previously, computing $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ will preserve this ability, albeit increasing the number of weights to include combinations of their products.
+$\rvec{i}'_{k,i}$ can now be written as
+\begin{equation}
     \begin{split}
-        h'(x) &= \left(\|x_{loc} - s_{loc}\|\right)^2 \\
-        &= (x - s_x)^2 + (y - s_y)^2 \\
-        &= x^2 + y^2 -2s_xx -2s_yy +s_x^2 +s_y^2
-    \end{split}\,,
-\end{equation*}
-and Jacobian $H'$ by
-\begin{equation*}
-    H' = 
+        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
+        &= \\
+        &\hspace{-1em}
         \begin{bmatrix}
-        2x_0 - 2s_x \\
-        2y_0 - 2s_y
-    \end{bmatrix}\,.
-\end{equation*}
-The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$.
-From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
-\begin{equation*}
             \begin{split}
-        H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
-        &\begin{bmatrix}
-            \begin{split}
-                &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
-                &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
-                &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
-                &\quad+ (-2R^{\prime -1}s_x)y^2
+                &(2\mean{r}_{k,i}^{-1})\rv{x}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\mean{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{x}_k \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{x}_k + (2\mean{r}_{k,i}^{-1}s_x^3) + (2\mean{r}_{k,i}^{-1}s_xs_y^2) \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
-                &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
-                &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
-                &\quad+ (-2R^{\prime -1}s_y)y^2
+                &(2\mean{r}_{k,i}^{-1})\rv{y}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{y}_k \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{y}_k + (2\mean{r}_{k,i}^{-1}s_ys_x^2) + (2\mean{r}_{k,i}^{-1}s_y^3) \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
             \end{split}
@@
     \end{split}
-\end{equation*}
-and
-\begin{equation*}
-    H^{\prime\top} R^{\prime -1}H' = 
+\end{equation}
+
+\begin{equation}
+    \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}\mat{H}'_{k,i} = 
     \begin{bmatrix}
@@
     \end{bmatrix}\,,
-\end{equation*}
+\end{equation}
 with
-\begin{align*}
-    \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
+\begin{align}
+    \alpha_{11} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\mean{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\mean{r}_{k,i}^{-1}s_x^2) \\
     \begin{split}
-        \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
-        &\qquad+ (4R^{\prime -1}s_xs_y)
+        \alpha_{12} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\mean{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\mean{r}_{k,i}^{-1}s_x)\rv{y}_k \\
+        &\qquad+ (4\mean{r}_{k,i}^{-1}s_xs_y)
     \end{split}\\
     \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
-\end{align*}
+    \alpha_{22} &= (4\mean{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\mean{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\mean{r}_{k,i}^{-1}s_y^2)\,.
+\end{align}
+
+Modification of measurements $z_{k,i}$ to suit the adjusted measurement functions will not preserve the Gaussian nature of the true measurement noise, and will additionally require estimation of the sensor measurement variance $r_i$.
+We will denote the modified measurement from sensor $i$ at time $k$ as $\rv{z}'_{k,i}$, and the estimated, now time-dependant, sensor variance as $\mean{r}_{k,i}$.
+The computations of these values will be discussed in Section \ref{subsec:range_measurement_mod}.
+
+--
+
+% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
+
+% Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
+Give flight navigation as an applicable example with typically high distances.
+
+% Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
+
+% The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$.
+From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
+% \begin{equation*}
+%     \begin{split}
+%         H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
+%         &\begin{bmatrix}
+%             \begin{split}
+%                 &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
+%                 &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
+%                 &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
+%                 &\quad+ (-2R^{\prime -1}s_x)y^2
+%             \end{split}
+%             \vspace{5pt}\\
+%             \begin{split}
+%                 &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
+%                 &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
+%                 &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
+%                 &\quad+ (-2R^{\prime -1}s_y)y^2
+%             \end{split}
+%         \end{bmatrix}
+%     \end{split}
+% \end{equation*}
+% and
+% \begin{equation*}
+%     H^{\prime\top} R^{\prime -1}H' = 
+%     \begin{bmatrix}
+%         \alpha_{11} & \alpha_{12} \\
+%         \alpha_{21} & \alpha_{22}
+%     \end{bmatrix}\,,
+% \end{equation*}
+% with
+% \begin{align*}
+%     \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
+%     \begin{split}
+%         \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
+%         &\qquad+ (4R^{\prime -1}s_xs_y)
+%     \end{split}\\
+%     \alpha_{21} &= \alpha_{12} \\
+%     \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
+% \end{align*}
 

### 2020-09-16 main.tex
Explained the requirements of the measurement model better and added it back to it's own section - also added how the encryption time (instance) stamp is created from the filter time step - put meaning of extension to 3D as a remark Filled out the section on how an adjusted measurement function can provide the desired requirements Started on explaining how the measurement can be modified to achieved the adjusted measurement function with now non-Gaussian noise Consistently named the "adjusted" measurement function/model/vector/etc to "modified"

@@
     \begin{split}
-        h_i(\rvec{x}_k) &= \left\|
+        h_i(\rvec{x}_k) &= \left\lVert
         \begin{bmatrix}
@@
         \end{bmatrix}^\top
-        - \vec{s}_{i}\right\| \\
+        - \vec{s}_{i}\right\rVert \\
         &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
@@
 From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.
-As matrix multiplication and scalar multiplication both preserve linearity, it is sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
+
+% 
+% ##     ##   ### ##     ## ###      ########  ########  #######   ######  
+% ##     ##  ##    ##   ##    ##     ##     ## ##       ##     ## ##    ## 
+% ##     ## ##      ## ##      ##    ##     ## ##       ##     ## ##       
+% ######### ##       ###       ##    ########  ######   ##     ##  ######  
+% ##     ## ##      ## ##      ##    ##   ##   ##       ##  ## ##       ## 
+% ##     ##  ##    ##   ##    ##     ##    ##  ##       ##    ##  ##    ## 
+% ##     ##   ### ##     ## ###      ##     ## ########  ##### ##  ######  
+%
+
+\subsection{Requirements for the Measurement Model}
+From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with weights dependant only on those from the original matrices.
+For example, consider dimension $N\times N$ matrices $\mat{A}$ and $\mat{B}$, where element $(i,j)$ in matrix $\mat{A}$ is of the form $\sum_{l=0}^M w_{l,i,j}a_{l,i,j}$ and similarly for matrix $\mat{B}$, form $\sum_{l=0}^M v_{l,i,j}b_{l,i,j}$.
+If we consider $w_{l,i,j}$ and $v_{l,i,j}$ as the weight terms, we can write element $(i,j)$ of a product matrix $\mat{A}\mat{B}$, with weights dependant only on these, as
+\begin{equation}
+    \begin{split}
+        \sum_{l=0}^N&\left(\left(\sum_{m=0}^M w_{m,i,j}a_{m,i,l}\right)\left(\sum_{m=0}^Mv_{m,i,j}b_{m,l,j}\right)\right) \\
+        &=\sum_{l=0}^N\left(\sum_{m=0}^M\sum_{n=0}^M w_{m,i,l}a_{m,i,l}v_{n,l,j}b_{n,l,j}\right) \\
+        &=\sum_{l=0}^N\sum_{m=0}^M\sum_{n=0}^M (w_{m,i,l}v_{n,l,j})a_{m,i,l}b_{n,l,j}\,.
+    \end{split} \label{eqn:matrix_mult_weights}
+\end{equation}
+Similarly, scalar multiplication also holds this property.
+It is therefore sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
 Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.
@@
 \subsection{Localisation Measurement Model} \label{subsec:observation_model}
-Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we see that $h_i$ cannot be rearranged to a linear combination of elements private to the navigator.
+Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
 In addition, the Jacobian of $h_i$,
@@
 \end{equation}
-cannot be either. Instead, we consider the adjusted measurement functions
-\begin{equation}
-    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:adjusted_measurement_funcs}
-\end{equation}
-Measurement functions in this form allow rearrangement of the corresponding adjusted measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ into linear combinations of navigator information.The modified measurement functions $h'_i$ can be written as
-\begin{equation}
-    \begin{split}
-        h'_i(\rvec{x}_k) &= \left\|
+cannot be either. Instead, we consider the modified measurement functions
+\begin{equation}
+    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
+\end{equation}
+A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well.The modified measurement functions $h'_i$ can be written as
+\begin{equation}
+    \begin{split}
+        h'_i(\rvec{x}_k) &= \left\lVert
         \begin{bmatrix}
             \rv{x}_k & \rv{y}_k
-        \end{bmatrix}^\top - \vec{s}_i\right\|^2 \\
+        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
         &= (\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2 \\
@@
 
-As stated previously, computing $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ will preserve this ability, albeit increasing the number of weights to include combinations of their products.
-$\rvec{i}'_{k,i}$ can now be written as
+To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using \eqref{eqn:matrix_mult_weights}, we denote the modified measurements as $\rv{z}'_{k,i}$, and modified measurement variances as $\mean{r}_{k,i}$.
+The derivation of these from the normal measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be derived in Section \ref{subsec:range_measurement_mod}.
+The resulting linear combinations are given by
 \begin{equation}
@@
         \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
-        &= \\
-        &\hspace{-1em}
+        &= 
         \begin{bmatrix}
@@
                 &(2\mean{r}_{k,i}^{-1})\rv{x}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\mean{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{x}_k \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{x}_k + (2\mean{r}_{k,i}^{-1}s_x^3) + (2\mean{r}_{k,i}^{-1}s_xs_y^2) \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
+                &\quad+ (2\mean{r}_{k,i}^{-1}s_x^3) + (2\mean{r}_{k,i}^{-1}s_xs_y^2) \\
                 &\quad+ (-2\mean{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
@@
                 &(2\mean{r}_{k,i}^{-1})\rv{y}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{y}_k \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{y}_k + (2\mean{r}_{k,i}^{-1}s_ys_x^2) + (2\mean{r}_{k,i}^{-1}s_y^3) \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
+                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
+                &\quad+ (2\mean{r}_{k,i}^{-1}s_ys_x^2) + (2\mean{r}_{k,i}^{-1}s_y^3) \\
                 &\quad+ (-2\mean{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
@@
         \end{bmatrix}
-    \end{split}
-\end{equation}
-
-\begin{equation}
-    \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}\mat{H}'_{k,i} = 
+    \end{split} \label{eqn:hrz_linear_comb}
+\end{equation}
+and
+\begin{equation}
+    \begin{split}
+        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
+        &=
         \begin{bmatrix}
@@
         \end{bmatrix}\,,
+    \end{split} \label{eqn:hrh_linear_comb}
 \end{equation}
 with
-\begin{align}
+\begin{align*}
     \alpha_{11} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\mean{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\mean{r}_{k,i}^{-1}s_x^2) \\
@@
     \alpha_{22} &= (4\mean{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\mean{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\mean{r}_{k,i}^{-1}s_y^2)\,.
-\end{align}
-
-Modification of measurements $z_{k,i}$ to suit the adjusted measurement functions will not preserve the Gaussian nature of the true measurement noise, and will additionally require estimation of the sensor measurement variance $r_i$.
-We will denote the modified measurement from sensor $i$ at time $k$ as $\rv{z}'_{k,i}$, and the estimated, now time-dependant, sensor variance as $\mean{r}_{k,i}$.
-The computations of these values will be discussed in Section \ref{subsec:range_measurement_mod}.
-
---
-
-% Show here the weighted integrals that give mean and variance of the new noise. If wanting to show more working, do this in the appendix section, but probably not needed.
-
-% Point out here that the further away the sensor is when it makes its distance measurement (the larger the measurement) the more Gaussian the noise and the better the filter.
-Give flight navigation as an applicable example with typically high distances.
-
-% Additionally increased range accuracy may be possible when sensors know the process model of the navigator, allowing them to run their own filter (more accurate than only measurements but not as accurate as the navigator's estimate from multiple sensors) and use their filtered estimated distance as the scaling factor when computing the modified measurement variance.
-
-% The above function and jacobian elements are linear combinations of functions $x$, $x^2$, $y$, $xy$ and $y^2$.
-From the previous section, we know we can now define $H^{\prime\top} R^{\prime -1}(z' - h(x) + Hx)$ and $H^{\prime\top} R^{\prime -1}H'$ in terms of more state vector dependant functions, in this case, $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$.
-% \begin{equation*}
-%     \begin{split}
-%         H&^{\prime\top} R^{\prime -1}(z' - h(x) + Hx) = \\
-%         &\begin{bmatrix}
-%             \begin{split}
-%                 &(2R^{\prime -1}z')x + (-2R^{\prime -1}s_xz) + (-2R^{\prime -1}s_x^2)x \\
-%                 &\quad+ (2R^{\prime -1}s_x^3) + (-2R^{\prime -1}s_y^2)x + (2R^{\prime -1}s_xs_y^2) \\
-%                 &\quad+ (2R^{\prime -1})x^3 + (-R^{\prime -1}s_x)x^2 + (2R^{\prime -1})xy^2 \\
-%                 &\quad+ (-2R^{\prime -1}s_x)y^2
-%             \end{split}
-%             \vspace{5pt}\\
-%             \begin{split}
-%                 &(2R^{\prime -1}z)y + (-2R^{\prime -1}s_yz) + (-2R^{\prime -1}s_x^2)y \\
-%                 &\quad+ (2R^{\prime -1}s_ys_x^2) + (-2R^{\prime -1}s_y^2)y + (2R^{\prime -1}s_y^3) \\
-%                 &\quad+ (2R^{\prime -1})x^2y + (-2R^{\prime -1}s_y)x^2 + (2R^{\prime -1})y^3 \\
-%                 &\quad+ (-2R^{\prime -1}s_y)y^2
-%             \end{split}
-%         \end{bmatrix}
-%     \end{split}
-% \end{equation*}
-% and
-% \begin{equation*}
-%     H^{\prime\top} R^{\prime -1}H' = 
-%     \begin{bmatrix}
-%         \alpha_{11} & \alpha_{12} \\
-%         \alpha_{21} & \alpha_{22}
-%     \end{bmatrix}\,,
-% \end{equation*}
-% with
-% \begin{align*}
-%     \alpha_{11} &= (4R^{\prime -1})x^2 + (-8R^{\prime -1}s_x)x + (4R^{\prime -1}s_x^2) \\
-%     \begin{split}
-%         \alpha_{12} &= (4R^{\prime -1})xy + (-4R^{\prime -1}s_y)x + (-4R^{\prime -1}s_x)y \\
-%         &\qquad+ (4R^{\prime -1}s_xs_y)
-%     \end{split}\\
-%     \alpha_{21} &= \alpha_{12} \\
-%     \alpha_{22} &= (4R^{\prime -1})y^2 + (-8R^{\prime -1}s_y)y + (4R^{\prime -1}s_y^2)\,.
-% \end{align*}
-
-The above formulation allows the application of our encryption scheme to the private aggregation of the measurement matrix and vector above.
-The scheme's encrypted weights $x$, $x^2$, $x^3$, $y$, $xy$, $x^2y$, $y^2$, $xy^2$ and $y^3$ are computed at each time step by the navigator, and each element of the measurement matrix and vector above is computed as a linear combination and prepared for aggregation by the sensors.
-
-Lastly, since we aggregate multiple linear combinations at each time step $k$ (each element in the result matrix and vector comes from a separate aggregation), we require unique hash values for each aggregation.
-This is handled by setting time variable $t$ as concatenation $k \| i \| j$ for each element $x_{i,j}$.
-Aggregation of each element is now performed under a different encryption scheme ``time'' step, when computing \eqref{eqn:our_scheme_lin_comb}.
-
-The solution above has been derived for the two-dimensional localisation case but it is easy to see that a similar solution would work in three-dimensional space.
-The cost of increasing localisation dimension however, is the increased number of state vector element functions required for broadcast by the navigator, and length of linear combination computed by sensors.
+\end{align*}
+The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.
+
+The final step required for the application of our LCAO-secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance-stamp variable $t$, in \eqref{eqn:our_scheme_lin_comb}.
+As six linear-combination aggregations occur at each time step $k$ (four element in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
+This is handled by setting $t$ to the concatenation
+\begin{equation}
+    t=k\mathbin\|i\mathbin\|j\mathbin\|b
+\end{equation}
+for aggregation in row $i$ and column $j$, with $b=0$ for aggregations in $\rvec{i}'_{k,i}$ and $b=1$ otherwise.
+\begin{rem}
+    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived specifically for two-dimensional localisation, but can be similarly computed for the three-dimensional case.
+It is worth noting however, the additional cost required for increasing localisation dimension.
+The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by \eqref{eqn:matrix_mult_weights}.
+This in turn results in a combinatorial increase in required weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
+\end{rem}
 
@@
 \subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
+In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ and measurement variances $\mean{r}_{k,i}$ such that we used a measurement model of the same form as \eqref{eqn:measurement_model} given the modified measurement function in \eqref{eqn:modified_measurement_func}.
+
+--
+
+% Modification of measurements $z_{k,i}$ to suit the modified measurement functions will not preserve the Gaussian nature of the true measurement noise, and will additionally require estimation of the sensor measurement variance $r_i$.
+We will denote the modified measurement from sensor $i$ at time $k$ as $\rv{z}'_{k,i}$, and the estimated, now time-dependant, sensor variance as $\mean{r}_{k,i}$.
+The computations of these values will be discussed in Section \ref{subsec:range_measurement_mod}.
+
 The conversion of measurement function $h'(x) = h(x)^2$ is in practice complicated by measurement noise manipulation.
@@
 where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
-We account for the non-zero mean by offsetting the squared measurement and taking this as the adjusted measurement model
+We account for the non-zero mean by offsetting the squared measurement and taking this as the modified measurement model
 \begin{equation*}

### 2020-09-18 main.tex
Filled out the range measurement modification section - concluded section with a clear assumption which the section makes to use the approximations in the modified measurement model - changed modified measurement variance estimate to be an rv in notation and not the mean (it is an estimate but not the mean as it is conservative by intention)

@@
 \subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, vector indexing (also note starts at 0)
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance
 
@@
 \begin{equation}
-    \rv{z}_k = h_i(\rvec{x}_k)+\rv{v}_k\,, \label{eqn:measurement_model}
-\end{equation}
-with noise $\rv{v}_k \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
+    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
+\end{equation}
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
 \begin{equation}
@@
 \end{equation}
-A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well.The modified measurement functions $h'_i$ can be written as
+A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well.
+The modified measurement functions $h'_i$ can be written as
 \begin{equation}
@@
 
-To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using \eqref{eqn:matrix_mult_weights}, we denote the modified measurements as $\rv{z}'_{k,i}$, and modified measurement variances as $\mean{r}_{k,i}$.
-The derivation of these from the normal measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be derived in Section \ref{subsec:range_measurement_mod}.
-The resulting linear combinations are given by
-\begin{equation}
-    \begin{split}
-        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
+To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using \eqref{eqn:matrix_mult_weights}, we require the existance of a modified measurement model of the form
+\begin{equation}
+    \rv{z}'_{k,i} = h'_i(\rvec{x}_k)+\rv{v}'_{k,i}\,, \label{eqn:modified_measurement_model}
+\end{equation}
+where $\rv{z}'_{k,i}$ is the modified measurement, and noise $\rv{v}'_{k,i}$ is white and Gaussian.
+The approximation of $\rv{z}'_{k,i}$ and $\rv{r}_{k,i}$ from original measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be shown in Section \ref{subsec:range_measurement_mod}.
+
+With the existance of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
+\begin{equation}
+    \begin{split}
+        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
         &= 
@@
             \begin{split}
-                &(2\mean{r}_{k,i}^{-1})\rv{x}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\mean{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
-                &\quad+ (2\mean{r}_{k,i}^{-1}s_x^3) + (2\mean{r}_{k,i}^{-1}s_xs_y^2) \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_x^3) + (2\rv{r}_{k,i}^{-1}s_xs_y^2) \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2\mean{r}_{k,i}^{-1})\rv{y}_k^3 + (2\mean{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\mean{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\mean{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
-                &\quad+ (2\mean{r}_{k,i}^{-1}s_ys_x^2) + (2\mean{r}_{k,i}^{-1}s_y^3) \\
-                &\quad+ (-2\mean{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_ys_x^2) + (2\rv{r}_{k,i}^{-1}s_y^3) \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
             \end{split}
@@
     \begin{split}
-        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \mean{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
+        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
         &=
@@
 \begin{align*}
-    \alpha_{11} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\mean{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\mean{r}_{k,i}^{-1}s_x^2) \\
-    \begin{split}
-        \alpha_{12} &= (4\mean{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\mean{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\mean{r}_{k,i}^{-1}s_x)\rv{y}_k \\
-        &\qquad+ (4\mean{r}_{k,i}^{-1}s_xs_y)
+    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_x^2) \\
+    \begin{split}
+        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_x)\rv{y}_k \\
+        &\qquad+ (4\rv{r}_{k,i}^{-1}s_xs_y)
     \end{split}\\
     \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4\mean{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\mean{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\mean{r}_{k,i}^{-1}s_y^2)\,.
+    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_y^2)\,.
 \end{align*}
@@
 \begin{rem}
-    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived specifically for two-dimensional localisation, but can be similarly computed for the three-dimensional case.
-It is worth noting however, the additional cost required for increasing localisation dimension.
+    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localisation, but can be similarly extended to the three-dimensional case.
+We note however, the additional cost with increasing dimension.
 The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by \eqref{eqn:matrix_mult_weights}.
-This in turn results in a combinatorial increase in required weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
+This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
 \end{rem}
@@
 \subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ and measurement variances $\mean{r}_{k,i}$ such that we used a measurement model of the same form as \eqref{eqn:measurement_model} given the modified measurement function in \eqref{eqn:modified_measurement_func}.
-
---
-
-% Modification of measurements $z_{k,i}$ to suit the modified measurement functions will not preserve the Gaussian nature of the true measurement noise, and will additionally require estimation of the sensor measurement variance $r_i$.
-We will denote the modified measurement from sensor $i$ at time $k$ as $\rv{z}'_{k,i}$, and the estimated, now time-dependant, sensor variance as $\mean{r}_{k,i}$.
-The computations of these values will be discussed in Section \ref{subsec:range_measurement_mod}.
-
-The conversion of measurement function $h'(x) = h(x)^2$ is in practice complicated by measurement noise manipulation.
-As we only know $z = h(x) + n$, where $n~\mathcal{N}(0,\sigma)$, we can estimate the new measurement as $z^2$.
-This results in the new measurement
-\begin{equation*}
-    \begin{split}
-        z^2 &= (h(x) + n)^2 \\
-        &= h(x)^2 + 2nh(x) + n^2 \\
-        &= h'(x) + 2nh(x) + n^2
-    \end{split}\,,
-\end{equation*}
-where noise term $2nh(x) + n^2$ has mean $\sigma^2$ and standard deviation $2(2h(x)^2\sigma^2 + \sigma^4)$.
-We account for the non-zero mean by offsetting the squared measurement and taking this as the modified measurement model
-\begin{equation*}
-    \begin{split}
-        z' &= h'(x) + 2nh(x) + n^2 - \sigma^2 \\
-        &= h'(x) + n'
-    \end{split}\,,
-\end{equation*}
-with variance of $n'$ approximated as $2(2z^2\sigma^2 + \sigma^4)$, by using the original measurement $z$ as an unbiased estimate for $h(x)$.
+In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ with Gaussian noise and variances $\rv{r}_{k,i}$ in the modified measurement model \eqref{eqn:modified_measurement_model}.
+In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
+Squaring the range measurement produces
+\begin{equation}
+    \begin{split}
+        \rv{z}_{k,i}^2 &= (h_i(\rvec{x}_k) + \rv{v}_{k,i})^2 \\
+        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 \\
+        &= h'_i(\rvec{x}_k) + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2\,,
+    \end{split}
+\end{equation}
+with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependant on the measurement function $h_i$ and no longer white or Gaussian.
+We can compute the mean of the new noise term (a function of white Gaussian term $\rv{v}_{k,i}$) as
+\begin{equation}
+    \E{2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2} = r_i\, \label{eqn:modified_noise_mean}
+\end{equation}
+and define modified measurements as
+\begin{equation} \label{eqn:modified_measurement}
+    \begin{split}
+        \rv{z}'_{k,i} &= \rv{z}_{k,i}^2 - r_i \\
+        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \\
+        &= h'_i(\rvec{x}_k) + \rv{v}'_{k,i}\,,
+    \end{split}
+\end{equation}
+with now zero-mean noise $\rv{v}'_{k,i} = 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i$. The noise in this case (again a function of white Gaussian term $\rv{v}_{k,i}$) has variance 
+\begin{equation}
+    \Var{\rv{v}'_{k,i}} = 4h_i(\rvec{x}_k)^2r_i + 2r_i^2
+\end{equation}
+and is dependant on $h_i(\rvec{x}_k)$.
+We also wish to approximate this noise using values available to the sensor, $\rv{z}_{k,i}$ and $r_i$, while providing a conservative estimate of the true variance so as not to affect the convergence of the EIF.
+While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate in the case
+\begin{equation}
+    \begin{split}
+        \rv{z}_{k,i} &> h_i(\rvec{x}_k) \\
+        \rv{z}_{k,i} - h_i(\rvec{x}_k) &> 0 \\
+        \rv{v}_{k,i} &> 0\,,
+    \end{split}
+\end{equation}
+which cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
+Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
+\begin{equation}
+    \rv{r}_{k, i} = 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2\,. \label{eqn:modified_meaasurement_variance_estimate}
+\end{equation}
+
+In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variance, as
+\begin{equation}
+    \begin{split}
+        &r_i << h_i(\rvec{x}_k) \\
+        \implies &2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i} \\
+        \implies &\rv{v}'_{k,i} \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i}\,,
+    \end{split} \label{eqn:modified_noise_approaches_gaussian}
+\end{equation}
+and conclude with the following assumption.
+\begin{assum}
+    Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
+\end{assum}
 

### 2020-09-18 main.tex
Typo, commit for the day

@@
 
-In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variance, as
+In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variances, as shown by
 \begin{equation}

### 2020-09-28 main.tex
Started writing the algorithms for the whole navigation method

@@
 \usetikzlibrary{math}
+
+% Algorithm settings
+\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}
 
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_k}\,.
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
 \end{equation}
@@
 
-With the existance of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
+With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
 \begin{equation}
@@
 
-% \begin{algorithm}
-%     \caption{Paillier Key Generation}\label{paillier_key_gen}
-%     \begin{algorithmic}[1]
-%         \Procedure{PaillierKeyGen}{$security\_param$}
-%         \State $p,q \gets$ \Call{GeneratePrimes}{$security\_param$}
-%         \State $\lambda \gets$ \Call{lcm}{p,q}
-%         \State $pk \gets (n, n+1)$
-%         \State $sk \gets \lambda$
-%         \State \Return $(pk, sk)$
-%         \EndProcedure
-%     \end{algorithmic}
-% \end{algorithm}
+\begin{algorithm}
+    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
+    \begin{algorithmic}[1]
+        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$, $f$}
+        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
+        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
+        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
+        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
+            \State Compute $\rv{\omega}' = \mathsf{E}_{N,f,0}(\rv{\omega})$ by \eqref{eqn:encode}
+            \State $r \gets$ \Call{RandInt}{$1,N$}
+            \State $\mathcal{E}_{pk}(\rv{\omega}') \gets (N+1)^{\rv{\omega}'}r^N \pmod{N^2}$
+            \State Broadcast $\mathcal{E}_{pk}(\rv{\omega}')$ to sensors
+        \EndFor
+        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+    \caption{Sensor Measurement at Sensor $i$}\label{alg:measurement_info}
+    \begin{algorithmic}[1]
+        \Procedure{Measurement}{$i$, $s_x$, $s_y$, $r_i$, $N$, $H$, $f$}
+        \State Measure $\rv{z}_{k,i}$
+        \While{Navigator broadcasting}
+        \State Recieve $\mathcal{E}_{pk}((\rv{x}^3_k)') = \mathcal{E}_{pk}(\mathsf{E}_{N,f,0}(\rv{x}^3_k))$
+        \State Recieve remaining weights in the above form
+        \EndWhile
+        \For{$i = 1$ to $2$} 
+            \State $\beta_i \gets $
+            \State Send $\beta_i$ to navigator
+        \EndFor
+        \For{$i = 1$ to $2$}
+            \For{$j = 1$ to $2$} 
+                \State Compute $\omega' = \mathsf{E}_{N,f,0}(\omega)$ by \eqref{eqn:encode}
+                \State $r \gets$ \Call{RandIntInRange}{1,N}
+                \State $\mathcal{E}_{pk}(\omega') \gets (N+1)^{\omega'}r^N \pmod{N^2}$
+                \State Send $\mathcal{E}_{pk}(\omega')$ to sensors
+            \EndFor
+        \EndFor
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
 

### 2020-09-29 main.tex
Continued on algorithms. Added sensor part of algorithm

@@
 \subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list
 
@@
 
+% assume f known to all, and public/private keys already distributed
+% Note the abbreviation for encoding E (no N and f)
+% Note the different m using in Encoding when computing alphas and betas
+
 \begin{algorithm}
@@
     \begin{algorithmic}[1]
-        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$, $f$}
+        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
         \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
@@
         \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
-            \State Compute $\rv{\omega}' = \mathsf{E}_{N,f,0}(\rv{\omega})$ by \eqref{eqn:encode}
+            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
             \State $r \gets$ \Call{RandInt}{$1,N$}
-            \State $\mathcal{E}_{pk}(\rv{\omega}') \gets (N+1)^{\rv{\omega}'}r^N \pmod{N^2}$
-            \State Broadcast $\mathcal{E}_{pk}(\rv{\omega}')$ to sensors
+            \State $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega})) \gets (N+1)^{\mathsf{E}_{0}(\rv{\omega})}r^N \pmod{N^2}$
+            \State Broadcast $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
         \EndFor
@@
 \begin{algorithm}
-    \caption{Sensor Measurement at Sensor $i$}\label{alg:measurement_info}
+    \caption{Measurement at Sensor $i$}\label{alg:measurement_info}
     \begin{algorithmic}[1]
-        \Procedure{Measurement}{$i$, $s_x$, $s_y$, $r_i$, $N$, $H$, $f$}
+        \Procedure{Measurement}{$i$, $s_x$, $s_y$, $r_i$, $N$, $H$}
         \State Measure $\rv{z}_{k,i}$
+        \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
+        \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_meaasurement_variance_estimate}
         \While{Navigator broadcasting}
-        \State Recieve $\mathcal{E}_{pk}((\rv{x}^3_k)') = \mathcal{E}_{pk}(\mathsf{E}_{N,f,0}(\rv{x}^3_k))$
-        \State Recieve remaining weights in the above form
+        \State Recieve $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^3_k))$
+        \State Recieve remaining weights in the form above
         \EndWhile
-        \For{$i = 1$ to $2$} 
-            \State $\beta_i \gets $
-            \State Send $\beta_i$ to navigator
+        \State Let $\beta_{ij}$ represent element $(i,j)$ of $\rvec{i}'_{k,i}$ in \eqref{eqn:hrz_linear_comb}
+        \State $\beta_{11} \!\gets\! \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
+        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
+        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_x)}
+        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_x)}$\par
+        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}
+        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_x^2)}$\par
+        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_y^2)}
+        (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_x^3)}$\par
+        \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_xs_y^2)}
+        (N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_x\rv{z}_{k,i}')}$\par
+        \ $H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
+        \State Compute $\beta_{21}$ by \eqref{eqn:hrz_linear_comb} in the form above
+        \For{$i \gets 1$ to $2$}
+            \State Send $\beta_{i1}$ to the navigator
         \EndFor
-        \For{$i = 1$ to $2$}
-            \For{$j = 1$ to $2$} 
-                \State Compute $\omega' = \mathsf{E}_{N,f,0}(\omega)$ by \eqref{eqn:encode}
-                \State $r \gets$ \Call{RandIntInRange}{1,N}
-                \State $\mathcal{E}_{pk}(\omega') \gets (N+1)^{\omega'}r^N \pmod{N^2}$
-                \State Send $\mathcal{E}_{pk}(\omega')$ to sensors
+        \State Let $\alpha_{ij}$ represent element $(i,j)$ of $\mat{I}'_{k,i}$ in \eqref{eqn:hrh_linear_comb}
+        \State $\alpha_{11} \gets \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
+        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_x)}
+        (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_x^2)}$\par
+        \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
+        \State Compute remaining $\alpha_{ij}$ by \eqref{eqn:hrh_linear_comb} in the form above
+        \For{$i \gets 1$ to $2$}
+            \For{$j \gets 1$ to $2$} 
+                \State Send $\alpha_{ij}$ to the navigator
             \EndFor
         \EndFor
+        \EndProcedure
+    \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+    \caption{Navigator Update Step}\label{alg:nav_update}
+    \begin{algorithmic}[1]
+        \Procedure{Update}{$\rvec{x}_{k}$, $\mat{P}_{k}$, $N$, $\lambda$}
+
+        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
+        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
+        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
+        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
+            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
+            \State $r \gets$ \Call{RandInt}{$1,N$}
+            \State $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega})) \gets (N+1)^{\mathsf{E}_{0}(\rv{\omega})}r^N \pmod{N^2}$
+            \State Broadcast $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
+        \EndFor
+        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
         \EndProcedure

### 2020-09-29 main.tex
Completed the algorithm text for the whole protocol Added missing labels to all encoding and our scheme equations (used these in the protocol instead of giving equations) Added missing index i for sensor locations (obviously these are dependent on the sensor Added missing index 0 to public key of our scheme (this is how the notation is when we define it) Fixed EIF update equations which were using the wrong index (k-1 just used in the prediction step) - this should still be done in a nicer way, currently x_k updated from x_k which is not really true in an equation Fixed error when defining pri

@@
 Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$.
-The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}$.
+The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
 
@@
     \begin{equation}
-        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,,
+        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
     \end{equation}
@@
             &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
-        \end{split}
+        \end{split} \label{eqn:our_scheme_decrypt}
     \end{equation}
@@
         -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
-    \end{dcases}.
+    \end{dcases}.\label{eqn:decode}
 \end{equation}
@@
 \begin{equation}
-    \rvec{y}_k = \rvec{y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
+    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
 \end{equation}
@@
 \begin{equation}
-    \mat{Y}_k = \mat{Y}_{k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
+    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
 \end{equation}
@@
     \begin{bmatrix}
-        \frac{\rv{x}_k - s_x}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} \\
-        \frac{\rv{y}_k - s_y}{\sqrt{(\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2}} 
+        \frac{\rv{x}_k - s_{x,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} \\
+        \frac{\rv{y}_k - s_{y,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} 
     \end{bmatrix}\,,
@@
         \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
-        &= (\rv{x}_k - s_x)^2 + (\rv{y}_k - s_y)^2 \\
-        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_x\rv{x}_k -2s_y\rv{y}_k +s_x^2 +s_y^2
+        &= (\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2 \\
+        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_{x,i}\rv{x}_k -2s_{y,i}\rv{y}_k +s_{x,i}^2 +s_{y,i}^2
     \end{split}\,,
@@
     \begin{bmatrix}
-        2\rv{x}_k - 2s_x \\
-        2\rv{y}_k - 2s_y
+        2\rv{x}_k - 2s_{x,i} \\
+        2\rv{y}_k - 2s_{y,i}
     \end{bmatrix}\,.
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_x)\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{x}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_x^3) + (2\rv{r}_{k,i}^{-1}s_xs_y^2) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x \rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y)\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y)\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_x^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_y^2)\rv{y}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_ys_x^2) + (2\rv{r}_{k,i}^{-1}s_y^3) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_y\rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
             \end{split}
@@
 \begin{align*}
-    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_x)\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_x^2) \\
-    \begin{split}
-        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_y)\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_x)\rv{y}_k \\
-        &\qquad+ (4\rv{r}_{k,i}^{-1}s_xs_y)
+    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
+    \begin{split}
+        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
+        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
     \end{split}\\
     \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_y)\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_y^2)\,.
+    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
 \end{align*}
@@
         \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
+
         \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
@@
         \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
+
         \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
             \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
-            \State $r \gets$ \Call{RandInt}{$1,N$}
-            \State $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega})) \gets (N+1)^{\mathsf{E}_{0}(\rv{\omega})}r^N \pmod{N^2}$
-            \State Broadcast $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
+            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
+            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
         \EndFor
+
         \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
@@
     \begin{algorithmic}[1]
-        \Procedure{Measurement}{$i$, $s_x$, $s_y$, $r_i$, $N$, $H$}
+        \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}
+
         \State Measure $\rv{z}_{k,i}$
@@
         \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_meaasurement_variance_estimate}
+
         \While{Navigator broadcasting}
-        \State Recieve $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^3_k))$
+        \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))$
         \State Recieve remaining weights in the form above
         \EndWhile
-        \State Let $\beta_{ij}$ represent element $(i,j)$ of $\rvec{i}'_{k,i}$ in \eqref{eqn:hrz_linear_comb}
-        \State $\beta_{11} \!\gets\! \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
-        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
-        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_x)}
-        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_x)}$\par
-        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}
-        \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_x^2)}$\par
-        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_y^2)}
-        (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_x^3)}$\par
-        \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_xs_y^2)}
-        (N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_x\rv{z}_{k,i}')}$\par
-        \ $H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-        \State Compute $\beta_{21}$ by \eqref{eqn:hrz_linear_comb} in the form above
-        \For{$i \gets 1$ to $2$}
-            \State Send $\beta_{i1}$ to the navigator
+
+        \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
+        \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
+        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
+        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}$\par
+        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}
+        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}$\par
+        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}
+        \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}$\par
+        \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
+        (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}$\par
+        \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
+        H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
+        \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
+        \For{$v \gets 1$ to $2$}
+            \State Send $\beta_{v1}$ to the navigator
         \EndFor
-        \State Let $\alpha_{ij}$ represent element $(i,j)$ of $\mat{I}'_{k,i}$ in \eqref{eqn:hrh_linear_comb}
-        \State $\alpha_{11} \gets \mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
-        \ $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_x)}
-        (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_x^2)}$\par
+
+        \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
+        \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
+        \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}
+        (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}$\par
         \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-        \State Compute remaining $\alpha_{ij}$ by \eqref{eqn:hrh_linear_comb} in the form above
-        \For{$i \gets 1$ to $2$}
-            \For{$j \gets 1$ to $2$} 
-                \State Send $\alpha_{ij}$ to the navigator
+        \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
+        \For{$v \gets 1$ to $2$}
+            \For{$w \gets 1$ to $2$} 
+                \State Send $\alpha_{vw}^{(i)}$ to the navigator
             \EndFor
@@
 
-        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
-        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
-        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
-        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
-            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
-            \State $r \gets$ \Call{RandInt}{$1,N$}
-            \State $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega})) \gets (N+1)^{\mathsf{E}_{0}(\rv{\omega})}r^N \pmod{N^2}$
-            \State Broadcast $\mathcal{E}_{pk}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
+        \For{$v \gets 1$ to $2$}
+            \State Receive $\beta_{v1}^{(i)}$ from each sensor $1\leq i \leq n$
         \EndFor
+
+        \For{$v \gets 1$ to $2$}
+            \For{$w \gets 1$ to $2$}
+            \State Receive $\alpha_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
+            \EndFor
+        \EndFor
+
+        \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
+        \For{$v \gets 1$ to $2$}
+            \State $\beta_{v1} \gets \prod_{i=1}^n\beta_{v1}^{(i)}$
+            \State Compute $\mathcal{D}_{sk_0}(\beta_{v1})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{v1}))$ by \eqref{eqn:decode}
+        \EndFor
+        \State Construct $\sum_{i=1}^n\rvec{i}'_{k,i}$ from decoded decryptions above
+
+        \State Let $\alpha_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
+        \For{$v \gets 1$ to $2$}
+            \For{$w \gets 1$ to $2$}
+                \State $\alpha_{vw} \gets \prod_{i=1}^n\alpha_{vw}^{(i)}$
+                \State Compute $\mathcal{D}_{sk_0}(\alpha_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+                \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{vw}))$ by \eqref{eqn:decode}
+            \EndFor
+        \EndFor
+        \State Construct $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above
+
+        \State $\rvec{y}_k \gets \mat{P}_{k}^{-1}\rvec{x}_{k} + \sum_{i=1}^n\rvec{i}'_{k,i}$
+        \State $\mat{Y}_k \gets \mat{P}_{k}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
+        \State $\rvec{x}_{k} \gets \mat{Y}_k^{-1}\rvec{y}_k$
+        \State $\mat{P}_{k} \gets \mat{Y}_k^{-1}$
         \State \Return $\rvec{x}_{k}, \mat{P}_{k}$

### 2020-09-29 main.tex
Started on algorithm tikz picture, that captures the 3 algorithm steps Fixed missing weights x_ky_k in a few places in the paper

@@
 \end{align*}
-The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.
+The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k\rv{y}_k$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.
 
@@
 
-        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k,\rv{y}_k\rangle$} 
+        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k\rv{y}_k,\rv{x}_k,\rv{y}_k\rangle$} 
             \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}

### 2020-09-30 main.tex
Added tikz picture for the whole algorithms steps as requested - basically a summary of the three algorithms given in the same section - still need to write the text for the algorithm section, and specify the assumptions/shorthand notation in the algorithms and picture Added synctex file to gitignore

@@
 \usepackage{tikz}
-%\usepackage{microtype}
-
-% User local packages
+
+% Local packages
 \usepackage{ISASmacros/isasmathmacros}
+
+% Algorithm settings
+\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}
 
@@
 
-% Algorithm settings
-\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}
+% Tikz reused pics
+\tikzset{
+   plane/.pic = {
+    \draw[fill]  plot[smooth, tension=0.6] coordinates {
+        (-0.65,-0.9) 
+        (-0.6,-0.85) 
+        (-0.4,-0.75) 
+        (-0.25,-0.65) 
+        (-0.15,-0.5) 
+        (-0.12,-0.3) 
+        (-0.1,-0.1) 
+        (0,0) 
+        (0.1,-0.1) 
+        (0.12,-0.3) 
+        (0.15,-0.5) 
+        (0.25,-0.65) 
+        (0.4,-0.75) 
+        (0.6,-0.85) 
+        (0.65,-0.9)
+        } -- plot[smooth, tension=0.6] coordinates {
+        (0.65,-0.9) 
+        (0.15,-0.91)
+        (0.35,-1.1) 
+        (0.37,-1.15)
+        } -- plot[smooth, tension=0.6] coordinates {
+        (0.37,-1.15)
+        (0,-1.12) 
+        (-0.37,-1.15) 
+        } -- plot[smooth, tension=0.6] coordinates {
+        (-0.37,-1.15)
+        (-0.35,-1.1) 
+        (-0.15,-0.91) 
+        (-0.65,-0.9) 
+        } -- cycle;
+   }
+}
 
@@
     \clip (brect_start) rectangle (brect_end);
+    \pic[rotate=-40,xscale=0.22,yscale=0.3] at (nav_loc) {plane};
     \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
-        % Plane
-        \draw[fill]  plot[smooth, tension=.6] coordinates {
-        (-0.65,-0.9) 
-        (-0.6,-0.85) 
-        (-0.4,-0.75) 
-        (-0.25,-0.65) 
-        (-0.15,-0.5) 
-        (-0.12,-0.3) 
-        (-0.10,-0.1) 
-        (0.0,0.0) 
-        (0.10,-0.1) 
-        (0.12,-0.3) 
-        (0.15,-0.5) 
-        (0.25,-0.65) 
-        (0.4,-0.75) 
-        (0.6,-0.85) 
-        (0.65,-0.9)
-        } -- plot[smooth, tension=.6] coordinates {
-        (0.65,-0.9) 
-        (0.15,-0.91)
-        (0.35,-1.1) 
-        (0.37,-1.15)
-        } -- plot[smooth, tension=.6] coordinates {
-        (0.37,-1.15)
-        (0.0,-1.12) 
-        (-0.37,-1.15) 
-        } -- plot[smooth, tension=.6] coordinates {
-        (-0.37,-1.15)
-        (-0.35,-1.1) 
-        (-0.15,-0.91) 
-        (-0.65,-0.9) 
-        } -- cycle;
         % Trail
@@
 \end{algorithm}
+
+\begin{figure}[htbp]
+\centering
+\vspace{\baselineskip}
+\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+    % Prediction
+    \draw  (0,1.75) rectangle (8,8);
+    \node at (4,7.5) {\small 1. Prediction};
+
+    % Navigator
+    \fill  [blue!40] (3.25,7) rectangle (4.75,5.5);
+    \pic[xscale=0.22,yscale=0.3] at (4,6.6725) {plane};
+    \node at (4,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
+
+    % Sensors
+    \fill  (1.5,3) [red!40] ellipse (0.5 and 0.5);
+    \node at (1.5,2.25) {Sensor $1$};
+    \fill  (6.5,3) [red!40] ellipse (0.5 and 0.5);
+    \node at (6.5,2.25) {Sensor $n$};
+
+    \fill [black] (3.5,3) circle (0.05);
+    \fill [black] (4,3) circle (0.05);
+    \fill [black] (4.5,3) circle (0.05);
+
+    % Arrows
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.75,5.25) (1.75,3.5)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(4.25,5.25) (6.25,3.5)};
+
+    \fill [lightgray]  (0.25,4.75) rectangle (7.75,3.75);
+    \node at (4,4.25) {$\langle\mathcal{E}_{pk_0}(\rv{\omega}): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k\rv{y}_k, \rv{x}_k, \rv{y}_k\}\rangle$};
+
+    % Measurement
+    \draw  (0,-4.75) rectangle (8,1.5);
+    \node at (4,1) {\small 2. Measurement};
+
+    % Navigator
+    \fill  (4,0) [blue!40] ellipse (0.5 and 0.5);
+    \pic[xscale=0.22,yscale=0.3] at (4,0.1725) {plane};
+
+    % Sensors
+    \fill  [red!40] (7.5,-3.75)  rectangle (5.5,-2.75);
+    \node at (1.5,-4.25) {Sensor $1$};
+    \fill  [red!40] (2.5,-3.75)  rectangle (0.5,-2.75);
+    \node at (6.5,-4.25) {Sensor $n$};
+
+    \node at (1.5,-3.25) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
+    \node at (6.5,-3.25) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};
+
+    \fill [black] (3.5,-3.25) circle (0.05);
+    \fill [black] (4,-3.25) circle (0.05);
+    \fill [black] (4.5,-3.25) circle (0.05);
+
+    % Arrows
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,-2.5) (3.75,-0.75)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(6.25,-2.5) (4.25,-0.75)};
+
+    \fill [lightgray]  (0.25,-1.25) rectangle (3.75,-2.25);
+    \node at (2,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,1})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,1})$};
+    \fill [lightgray]  (4.25,-1.25) rectangle (7.75,-2.25);
+    \node at (6,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,n})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,n})$};
+
+    % Update
+    \draw  (0,-10.25) rectangle (8,-5);
+    \node at (4,-5.5) {\small 3. Update};
+
+    % Navigator
+    \fill  [blue!40] (2.25,-6) rectangle (5.75,-8);
+    \pic[xscale=0.22,yscale=0.3] at (4,-6.3275) {plane};
+    \node at (4,-7.125) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
+    \node at (4,-7.625) {$\rvec{x}_k$, $\mat{P}_k$};
+
+    % Sensors
+    \fill  (6.5,-9) [red!40] ellipse (0.5 and 0.5);
+    \node at (1.5,-9.75) {Sensor $1$};
+    \fill  (1.5,-9) [red!40] ellipse (0.5 and 0.5);
+    \node at (6.5,-9.75) {Sensor $n$};
+
+    \fill [black] (3.5,-9) circle (0.05);
+    \fill [black] (4,-9) circle (0.05);
+    \fill [black] (4.5,-9) circle (0.05);
+
+\end{tikzpicture}
+\vspace{\baselineskip}
+\caption{Alg summary}
+\label{fig:agg_steps}
+\end{figure}
 

### 2020-09-30 main.tex
Completed Algorithm section - explanation of steps and references to the algorithms - summary picture after algorithms Update tikz picture to be correct (forgot encoding and some other notation)

@@
 \vspace{\baselineskip}
-\caption{Required linear-combination aggregation steps at time $t$}
+\caption{Required linear-combination aggregation steps at time $t$.}
 \label{fig:agg_steps}
@@
 
-\subsection{Integer Encoding for Real Numbers}
+\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
 In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$.
@@
         &\mathsf{E}_{N,f,m}(a_1+a_2)
-    \end{split}
+    \end{split}\label{eqn:encoding_homomorphic_add}
 \end{equation}
@@
 
-\subsection{Algorithm}
-% Maybe name the scheme? That would be in the heading here
-Piece together the whole algorithm here.
-Give the algorithm as pseudocode (including encoding and encryption, possible as separate procedures)
-
-% assume f known to all, and public/private keys already distributed
-% Note the abbreviation for encoding E (no N and f)
-% Note the different m using in Encoding when computing alphas and betas
-
-\begin{algorithm}
-    \caption{Navigator Prediction Step}\label{alg:nav_prediction}
+\subsection{Algorithm} \label{subsec:algorithm}
+In this section, we piece together our LCAO secure encryption scheme in Section \ref{sec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.
+
+The privacy-preserving localisation filter can be described by the following steps.
+\begin{description}
+    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{sec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
+Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
+We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.
+
+    \item[Prediction] The navigator computes the typical EKF prediction equations before encrypting state variables and broadcasting to sensors. This is given by Algorithm \ref{alg:nav_prediction}.
+
+    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,1}$ and $\mat{I}'_{k,1}$, encrypting them for aggregation, and sending them back to the navigator.
+Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}.
+This has been described by Algorithm \ref{alg:measurement_info}.
+
+    \item[Update] The navigator aggregates measurement vectors and matrices before decrypting them.
+The typical EIF update equations can then be computed.
+This is shown in Algorithm \ref{alg:nav_update}.
+\end{description}
+
+\begin{algorithm}[htbp]
+    \caption{Navigator Prediction}\label{alg:nav_prediction}
     \begin{algorithmic}[1]
@@
 
-\begin{algorithm}
+\begin{algorithm}[htbp]
 \caption{Measurement at Sensor $i$}\label{alg:measurement_info}
@@
 
-\begin{algorithm}
-    \caption{Navigator Update Step}\label{alg:nav_update}
+\begin{algorithm}[htbp]
+\caption{Navigator Update}\label{alg:nav_update}
 \begin{algorithmic}[1]
@@
 
+Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_m(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
+
 \begin{figure}[htbp]
@@
 
-    \fill [lightgray]  (0.25,4.75) rectangle (7.75,3.75);
-    \node at (4,4.25) {$\langle\mathcal{E}_{pk_0}(\rv{\omega}): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k\rv{y}_k, \rv{x}_k, \rv{y}_k\}\rangle$};
+    \fill [lightgray]  (0.25,5) rectangle (7.75,4);
+    \node at (4,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k, \rv{y}_k\}\rangle$};
 
@@
 
-    \fill [lightgray]  (0.25,-1.25) rectangle (3.75,-2.25);
-    \node at (2,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,1})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,1})$};
-    \fill [lightgray]  (4.25,-1.25) rectangle (7.75,-2.25);
-    \node at (6,-1.75) {$\mathcal{E}_{pk_0}(\rvec{i}'_{k,n})$, $\mathcal{E}_{pk_0}(\mat{I}'_{k,n})$};
+    \fill [lightgray]  (0.5,-1.25) rectangle (3.5,-2.25);
+    \node[align=center] at (2,-1.75) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
+    \fill [lightgray]  (4.5,-1.25) rectangle (7.5,-2.25);
+    \node[align=center] at (6,-1.75) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
 
@@
 \vspace{\baselineskip}
-\caption{Alg summary}
-\label{fig:agg_steps}
+\caption{The summary of steps involved in our proposed privacy-preserving EIF.}
+\label{fig:alg_steps}
 \end{figure}

### 2020-10-01 main.tex
Wrote up leakage section - included quick recap/reasoning behind participant capability assumptions - summarised in a remark what the leakage is - TODO: could still give the sums in terms of original measurement (and variance if I add this as sensor private information)

@@
 
-\subsection{Participant Capabilities} 
+\subsection{Participant Capabilities} \label{subsec:capabilities}
 Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
@@
 
-\begin{rem}
+\begin{rem} \label{rem:lcao_leakage}
     The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
@@
 \subsection{Leakage} \label{subsec:leakage}
-We recall the assumptions made in the problem formulation and our encryption scheme, and the allowed leakage of the encryption scheme.
-Sensors are honest but curious, meaning sensor values cannot be modified from what is measured, and the protocol is followed exactly, and that the navigator sends the same state information to all sensors at each time step.
-This is justified to an extent with wireless broadcasting being received by all sensors in a typical localisation setting.
-
-From the above restrictions, sensors learn only their measurements $x_i$, and the navigator learns only the sums $\sum^n_{i=1}H^\top R^{-1}_i(z_i - h(x) + Hx)$ and $\sum^n_{i=1}H^\top R_i^{-1}H$.
-
-For malicious subsets not including the navigator, it is clear that they learn nothing more about the navigator location than what they can deduce given only their own measurements.
-
-The navigator, which may maliciously choose weights at every time step, is always restricted to learning at most the sum $\sum^n_{i=1} a_i$ for some values $a_i$ derived from sensor $i$'s location and measurement.
-It is therefore intuitive to say that at most the navigator can learn the average of values kept private, that is, the navigator can at most learn the average position and location of sensors.
-The same can be said for any corrupted subset of honest but curious sensors and malicious navigator.
+With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account.
+We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}.
+Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
+Honest-but-curious sensors are not required for scheme security, but avoid malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achieved by detecting changes in real measurements after reporting false measurements to the navigator.
+As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicate homomorphic operations and active malicious sensors are beyond the scope of this work.
+
+The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$.
+However, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
+That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.} $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
+
+From the leaked coefficient sums, we see that all information private to the sensors, namely their measurements $\rv{z}'_{k,i}$ and locations $\vec{s}_i$, are present only in sums
+\begin{equation}
+    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localisation_leakage}
+\end{equation}
+Therefore, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor measurements and locations.
+\begin{rem}
+    In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor measurements and locations, given by the sums in \eqref{eqn:localisation_leakage}.
+\end{rem}
 

### 2020-10-01 main.tex
Started on Results section - described implementation - referenced software libraries Started on getting the graphs included properly - total pain in the ass, still in progress

@@
 Honest-but-curious sensors are not required for scheme security, but avoid malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achieved by detecting changes in real measurements after reporting false measurements to the navigator.
-As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicate homomorphic operations and active malicious sensors are beyond the scope of this work.
+As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicates homomorphic operations and active malicious sensors are not considered in the scope of this work.
 
@@
 \section{Results} \label{sec:results}
-Time results can be captured in one graph.
+To demonstrate our proposed approach, we have implemented the algorithm in Section \ref{subsec:algorithm} and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.
+
+Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to run simultaneous processes for each sensor and navigator.
+The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required encryption scheme hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme.
+Additionally, GNU libraries GSL \cite{GSLGNUScientific2019} and GMP \cite{GMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
+Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.
+
+\begin{figure}[htbp]
+    \begin{center}
+       \includegraphics{images/timing.pdf}
+    \end{center}
+    \caption{Timing}
+    \label{fig:sim_timing}
+ \end{figure}
+
+ \begin{figure}[htbp]
+    \begin{center}
+       \includegraphics{images/layout_errors.pdf}
+    \end{center}
+    \caption{Layout errors}
+    \label{fig:sim_layout_errors}
+ \end{figure}
+
+ \begin{figure}[htbp]
+    \begin{center}
+       \includegraphics{images/layouts.pdf}
+    \end{center}
+    \caption{Layouts}
+    \label{fig:sim_layouts}
+ \end{figure}
+
+% Time results can be captured in one graph.
 Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048).
@@
 
-Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
+% Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
 All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense):
 
-Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
-
-Plot 2 will plot the RMSE as the average distance of sensors changes.
+% Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
+
+% Plot 2 will plot the RMSE as the average distance of sensors changes.
 Fixed encoding and Paillier bit size.
@@
 
-Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).
-
-Discuss the meaning of the small changes in accuracy, and runtimes when using the same encryption size, that is, point out it is a generally robust method.
+% Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).
+
+% Discuss the meaning of the small changes in accuracy, and runtimes when using the same encryption size, that is, point out it is a generally robust method.
 

### 2020-10-02 main.tex
Added cryptography proof summary tikz diagram - changed text a tiny bit to reference it nicely Moved tikz image files to their own folder - nicer to keep the imported pdfs and the itkz picture (which aren't imported) seperate

@@
     % Step 1
-    \node at (5,22.5) {\small 1. Broadcast and linear combinations step};
+    \node at (5,22.5) {1. Broadcast and linear combinations step};
     % Navigator
@@
     % Step 2
-    \node at (5,13.25) {\small 2. Aggregation step};
+    \node at (5,13.25) {2. Aggregation step};
     % Navigator
@@
 
-To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger using the \textit{Joye-Libert scheme}, such that
+To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the \textit{Joye-Libert scheme}, such that
 \begin{equation*}
@@
 for some negligible functions $\eta_1$ and $\eta_2$.
-(\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.
-The function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
+(\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof.
+The proof overview has been given in Figure \ref{fig:proof_summary}.
+Additionally, the function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
+
+\begin{figure}[htbp]
+\centering
+\vspace{\baselineskip}
+\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+    % Bounding box
+    \draw [gray] (0,-0.25) rectangle (8,7.5);
+
+    % Outer adversary rectangle
+    \draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
+    % Inner adversary rectangle
+    \draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);
+
+    % Adversaries and challenger
+    \node at (4,3.5) {\LARGE$\mathcal{A}'$};
+    \node at (4,6) {\LARGE$\mathcal{A}$};
+    \node at (4,0.5) {\LARGE$\mathcal{C}$};
+
+    % Arrows
+    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
+    \draw [-latex] (2,1.75) -- (2,2.75);
+
+    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
+    \draw [-latex] (2,4.5) --(2,5.5);
+
+    \node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
+    \draw [-latex] (6,5.5) -- (6,4.5);
+
+    \node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
+    \draw [-latex] (6,2.75) -- (6,1.75);
+\end{tikzpicture}
+\vspace{\baselineskip}
+\caption{High-level overview of our scheme's LCAO security proof.}
+\label{fig:proof_summary}
+\end{figure}
+
 \begin{pf}
@@
     % Prediction
-    \draw  (0,1.75) rectangle (8,8);
-    \node at (4,7.5) {\small 1. Prediction};
+    \draw [gray] (0,1.75) rectangle (8,8);
+    \node at (4,7.5) {1. Prediction};
 
@@
     % Measurement
-    \draw  (0,-4.75) rectangle (8,1.5);
-    \node at (4,1) {\small 2. Measurement};
+    \draw [gray] (0,-4.75) rectangle (8,1.5);
+    \node at (4,1) {2. Measurement};
 
@@
     % Update
-    \draw  (0,-10.25) rectangle (8,-5);
-    \node at (4,-5.5) {\small 3. Update};
+    \draw [gray] (0,-10.25) rectangle (8,-5);
+    \node at (4,-5.5) {3. Update};
 
@@
 
-Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to run simultaneous processes for each sensor and navigator.
-The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required encryption scheme hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme.
+Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to support simultaneous computations by sensors and navigator via different processes.
+The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme.
 Additionally, GNU libraries GSL \cite{GSLGNUScientific2019} and GMP \cite{GMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
 Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.
+
+Figure \ref{fig:sim_timing} shows
 
@@
     \end{center}
-    \caption{Layouts}
+    \caption{Layouts Normal Big}
     \label{fig:sim_layouts}

### 2020-10-02 tikz_images/proof.tex
Added cryptography proof summary tikz diagram - changed text a tiny bit to reference it nicely Moved tikz image files to their own folder - nicer to keep the imported pdfs and the itkz picture (which aren't imported) seperate

--- 2020-10-01 main.tex
@@
-% autosam.tex
-% Annotated sample file for the preparation of LaTeX files
-% for the final versions of papers submitted to or accepted for 
-% publication in AUTOMATICA.
+\begin{tikzpicture}[font=\footnotesize]
+% Bounding box
+\draw [gray] (0,-0.25) rectangle (8,7.5);
 
-% See also the Information for Authors.
+% Outer adversary rectangle
+\draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
+% Inner adversary rectangle
+\draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);
 
-% Make sure that the zip file that you send contains all the 
-% files, including the files for the figures and the bib file.
-
-% Output produced with the elsart style file does not imitate the
-% AUTOMATICA style. The style file is generic for all Elsevier
-% journals and the output is laid out for easy copy editing. The
-% final document is produced from the source file in the
-% AUTOMATICA style at Elsevier.
-
-% You may use the style file autart.cls to obtain a two-column 
-% document (see below) that more or less imitates the printed 
-% Automatica style. This may helpful to improve the formatting 
-% of the equations, tables and figures, and also serves to check 
-% whether the paper satisfies the length requirements.
-
-% Please note: Authors must not create their own macros.
-
-% For further information regarding the preparation of LaTeX files 
-% for Elsevier, please refer to the "Full Instructions to Authors" 
-% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
-% directory pub/styles, or from the internet (CTAN sites) on
-% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
-% tex-archive/macros/latex/contrib/supported/elsevier.
-
-% The use of LaTeX2e is preferred.
-%\documentclass{elsart}
-
-% Enable this line and disable the 
-% preceding line to obtain a two-column 
-% document whose style resembles the
-% printed Automatica style.
-\documentclass[twocolumn]{autart}
-
-% Include this line if your 
-% document contains figures,
-\usepackage{graphicx}
-% or this line, depending on which
-% you prefer.
-%\usepackage[dvips]{epsfig}
-
-% User imported packages
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{mathtools}
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{tikz}
-
-% Local packages
-\usepackage{ISASmacros/isasmathmacros}
-
-% Algorithm settings
-\algnewcommand{\LineComment}[1]{\State \(\triangleright\) #1}
-
-% Tikz settings
-\usetikzlibrary{math}
-
-% Tikz reused pics
-\tikzset{
-   plane/.pic = {
-    \draw[fill]  plot[smooth, tension=0.6] coordinates {
-        (-0.65,-0.9) 
-        (-0.6,-0.85) 
-        (-0.4,-0.75) 
-        (-0.25,-0.65) 
-        (-0.15,-0.5) 
-        (-0.12,-0.3) 
-        (-0.1,-0.1) 
-        (0,0) 
-        (0.1,-0.1) 
-        (0.12,-0.3) 
-        (0.15,-0.5) 
-        (0.25,-0.65) 
-        (0.4,-0.75) 
-        (0.6,-0.85) 
-        (0.65,-0.9)
-        } -- plot[smooth, tension=0.6] coordinates {
-        (0.65,-0.9) 
-        (0.15,-0.91)
-        (0.35,-1.1) 
-        (0.37,-1.15)
-        } -- plot[smooth, tension=0.6] coordinates {
-        (0.37,-1.15)
-        (0,-1.12) 
-        (-0.37,-1.15) 
-        } -- plot[smooth, tension=0.6] coordinates {
-        (-0.37,-1.15)
-        (-0.35,-1.1) 
-        (-0.15,-0.91) 
-        (-0.65,-0.9) 
-        } -- cycle;
-   }
-}
-
-\begin{document}
-
-\begin{frontmatter}
-% Running title for regular 
-% papers but only if the title  
-% is over 5 words. Running title 
-% is not shown in output.
-%\runtitle{Insert a suggested running title}
-
-% Title, preferably not more than 10 words.
-\title{Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}}
-
-\thanks[footnoteinfo]{This paper was not presented at any IFAC 
-meeting. Corresponding author Uwe~D.~Hanebeck. Tel. +49--721--608--43909.}
-
-% Add the 
-% e-mail address 
-% (ead) as shown
-\author[ISAS]{Marko Ristic}\ead{marko.ristic@kit.edu},
-\author[ISAS]{Benjamin Noack}\ead{noack@kit.edu},
-\author[ISAS]{Uwe D. Hanebeck}\ead{uwe.hanebeck@kit.edu}
-
-% Please supply
-\address[ISAS]{Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
-
-% Five to ten keywords,  
-% chosen from the IFAC 
-% keyword list or with the 
-% help of the Automatica 
-% keyword wizard
-\begin{keyword}
-System state estimation; Data privacy; Sensor fusion; Kalman filters.
-\end{keyword}
-
-% Abstract of not more than 200 words.
-\begin{abstract}
-Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
-Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
-Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common, model-based, non-linear measurement, localisation methods and forfeit broad applicability.
-We define a cryptographically secure linear-combination aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
-The security requirements, leakage, and cryptographic proof are given for the private filter and aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
-Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
-\end{abstract}
-
-\end{frontmatter}
-
-% 
-% 8888888          888                    
-%   888            888                    
-%   888            888                    
-%   888   88888b.  888888 888d888 .d88b.  
-%   888   888 "88b 888    888P"  d88""88b 
-%   888   888  888 888    888    888  888 
-%   888   888  888 Y88b.  888    Y88..88P 
-% 8888888 888  888  "Y888 888     "Y88P"  
-%                                         
-%                                         
-%                                         
-%
-
-\section{Introduction}
-
---
-
-Introduce localisation, filtering and the need for privacy.
-
-Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs
-
-Methods for introducing security and privacy include differential privacy methods and encryption methods.
-
-Differential privacy involves using statistical noise as security to make individual users' information cannot be deduced.
-Often requires a trusted aggregator, although secure aggregation methods exist.
-always requires noising result such that the outcome is not exact (a problem in localisation).
-
-Encryption schemes involve formal indistinguishability proofs typically over bits or integers.
-They rely on computationally hard problems involving security parameters of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
-Continuing, explain public-key cryptography applicability to distributed systems; difference to symmetric schemes.
-Homomorphic encryption power and use case.
-Why FHE isn't used often, why additive partially homomorphic encryption is.
-
-Advancements in function providing encryption schemes such as homomorphic encryption have also led to several other types of schemes which have found uses in signal processing.
-Private aggregation schemes allow the secure computation of the sum of encrypted values originating from different parties, leaking only the final result.
-When considering such multi-party encryption protocols, formal security definitions must now also incorporate the added dangers of colluding malicious parties, and lead to new notions of security.
-For example Aggregator Obliviousness (AO) is typically proven for private aggregation schemes, while alternatives such as Private Weighted Secure Aggregator Obliviousness (pWSAO) exist for other specific use-cases.
-
-Another example of function providing encryption, and a generalisation of private aggregation, is called functional encryption (FE) and its distributed extension, multi-client functional encryption (MCFE), which allow the unencrypted result of an arbitrary function to be computed from encrypted inputs.
-General FE and MCFE are known to be quite computationally expensive (from meeting with ITI and student Johannes - need ref.) but alternatives providing only a subset of possibly computable function exist; for example, inner product encryption.
-
-Several of the aforementioned encryption schemes have found uses in secure localisation, estimation, and control.
-
-% 
-% ##       #### ######## 
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ######## ####    ##    
-%
-
-\subsection{Relevant Literature on Encrypted Localisation and Estimation}
-
-Model-free localisation using homomorphic encryption examples include polygon thing, WSN examples which protect against adversaries but in the case of the WSN paper.
-don't preserve anchor privacy.
-Importantly, model-based filtering and localisation provide more accurate estimates and these are not applicable there.
-
-Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only the cloud-as-a-service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)
-
-pWSAO achieved in Alexandru weighted aggregation, but requires redistributing keys at every timestep resulting in a costly operation, and a complicated communication protocol.
-
-In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format.
-As is the case with our proposed localisation method, real number sensor output does not trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent.
-Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist.
-Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).
-
-Briefly describe navigator scenario and our contributions
-
---
-
-%Section Summary
-% \ref{sec:problem_statement}
-% \ref{sec:crypto_prelim}
-% \ref{sec:lcao_definition}
-% \ref{sec:our_scheme}
-% \ref{sec:loc_prelim}
-% \ref{sec:private_localisation}
-% \ref{sec:results}
-% \ref{sec:conclusion}
-In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
-Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it.
-Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
-In Section \ref{sec:results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
-
-% 
-% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
-% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
-% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
-% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
-% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
-% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
-% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
-%
-
-\subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list
-
-% 
-% 8888888b.                  888      
-% 888   Y88b                 888      
-% 888    888                 888      
-% 888   d88P 888d888 .d88b.  88888b.  
-% 8888888P"  888P"  d88""88b 888 "88b 
-% 888        888    888  888 888  888 
-% 888        888    Y88..88P 888 d88P 
-% 888        888     "Y88P"  88888P"  
-%                                     
-%                                     
-%                                     
-%
-
-\section{Problem Statement} \label{sec:problem_statement}
-% Restate the scenario but more formally. Give a concrete example - plane and signal towers.
-
-% Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
-Note that learning only the sum in aggregation (as is normal in AO) would, in this case, tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
-
-% Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear).
-Any largely incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.).
-Justify by saying sensors need to behave for localisation to work in the first place.
-
-% Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
-In a wireless setting, all sensors would receive all broadcast weights anyway.
-While special hardware, which may support directional broadcasting or receiving, could be used to locate sensors individually this is beyond the scope of what is considered in our problem.
-
-% Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known
-
-% Rough computational capabilities expected by parties
-
-% Fixed sensor subsets of which only whole subsets can be used at once.
-Maybe a picture of what this might look like in a high level distributed localisation diagram.
-Should consider that this sub-grouping would also mean the leakage of the average sensor/measurement of each subset not all sensors at once.
-This should be considered when choosing sensor subsets and locations.
-
-The localisation scenario we consider in this work is that of model-based self-navigation using range-only sensors.
-We consider localisation in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
-
-The navigator state is defined as 
-\begin{equation}
-    \rvec{x} = 
-    \begin{bmatrix}
-        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
-    \end{bmatrix}^\top\,. \label{eqn:state_def}
-\end{equation}
-A known process model is followed, which at time $k$ is given by
-\begin{equation}
-    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
-\end{equation}
-with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
-\begin{equation}
-    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
-\end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
-\begin{equation}
-    \vec{s}_i = 
-    \begin{bmatrix}
-        s_{x,i} & s_{y,i}
-    \end{bmatrix}^\top\,,
-\end{equation} 
-is defined as
-\begin{equation}
-    \begin{split}
-        h_i(\rvec{x}_k) &= \left\lVert
-        \begin{bmatrix}
-            \rv{x}_k & \rv{y}_k
-        \end{bmatrix}^\top
-        - \vec{s}_{i}\right\rVert \\
-        &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
-    \end{split}
-\end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $\rv{z}_k$ at any time $k$.
-
-We motivate these goals with an example.
-When considering aircraft navigation in the presence of privately-owned range-measuring towers, it is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown tower-owning parties.
-Similarly, tower locations may wish to be kept private from unidentified navigating aircraft.
-However, the additional safety to passengers, provided by accurate aircraft localisation, may be a goal of all those involved.
-
-% 
-%  ######     ###    ########     ###    ########  #### ##       #### ######## #### ########  ######  
-% ##    ##   ## ##   ##     ##   ## ##   ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
-% ##        ##   ##  ##     ##  ##   ##  ##     ##  ##  ##        ##     ##     ##  ##       ##       
-% ##       ##     ## ########  ##     ## ########   ##  ##        ##     ##     ##  ######    ######  
-% ##       ######### ##        ######### ##     ##  ##  ##        ##     ##     ##  ##             ## 
-% ##    ## ##     ## ##        ##     ## ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
-%  ######  ##     ## ##        ##     ## ########  #### ######## ####    ##    #### ########  ######  
-%
-
-\subsection{Participant Capabilities} \label{subsec:capabilities}
-Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
-\begin{description}
-    \item[Global navigator broadcast] Due to sensor location privacy and model non-linearity, bi-directional communication between navigator and sensors is required.
-We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
-
-    A problem caused by this requirement is apparent in the context of aircraft navigation.
-It may be the case that some sensors are not within the range of a navigator broadcast.
-We loosely propose that this scenario can be handled by pre-defined sensor subsets during an initial step by a trusted party.
-This has been captured in Figure \ref{fig:sensor_subsets}.
-    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
-This means the navigator may not send different information to individual sensors during a single timestep.
-
-    In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
-    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localisation procedure correctly but may store or use any gained sensitive information.
-
-    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms.
-As privacy-preserving implementations of such mechanisms require additional complications, we do not consider the scenario in this work.
-    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
-We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
-\end{description}
-\begin{figure}[htbp]
-\centering
-\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
-    % Sizes
-    \tikzmath{\srange = 3.54; \sradius = 0.04;}
-    % Sensor locations (sensor 3 is shared)
-    \coordinate (s1) at (1.4086,-4.5869);
-    \coordinate (s2) at (4.0633,-5.9948);
-    \coordinate (s3) at (3.1235,-3.2054);
-    \coordinate (s4) at (4.5563,-1.6861);
-    \coordinate (s5) at (5.9909,-3.5635);
-    % Navigator location
-    \coordinate (nav_loc) at (4,-4);
-    % Bounding rectangle
-    \coordinate (brect_start) at (0,0);
-    \coordinate (brect_end) at (8.0, -8.0);
-
-    % Gray range circles
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \draw[gray!50] (s1) circle (\srange);
-        \draw[gray!50] (s2) circle (\srange);
-        \draw[gray!50] (s3) circle (\srange);
-        \draw[gray!50] (s4) circle (\srange);
-        \draw[gray!50] (s5) circle (\srange);
-    \end{scope}
-    % Red subgroup overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s3) circle (\srange);
-        \clip (s4) circle (\srange);
-        \clip (s5) circle (\srange);
-        \fill[red!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Blue subgroup overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s1) circle (\srange);
-        \clip (s2) circle (\srange);
-        \clip (s3) circle (\srange);
-        \fill[blue!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Magenta double overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s1) circle (\srange);
-        \clip (s2) circle (\srange);
-        \clip (s3) circle (\srange);
-        \clip (s4) circle (\srange);
-        \clip (s5) circle (\srange);
-        \fill[magenta!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Sensors
-    \fill[black] (s1) circle (\sradius);
-    \fill[black] (s2) circle (\sradius);
-    \fill[black] (s3) circle (\sradius);
-    \fill[black] (s4) circle (\sradius);
-    \fill[black] (s5) circle (\sradius);
-    % Bounding box
-    \draw[gray] (brect_start) rectangle (brect_end);
-    % Navigator
-    \clip (brect_start) rectangle (brect_end);
-    \pic[rotate=-40,xscale=0.22,yscale=0.3] at (nav_loc) {plane};
-    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
-        % Trail
-        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
-    \end{scope}
-    % Sensor labels
-    \node[label=1] at (s1) {};
-    \node[label=2] at (s2) {};
-    \node[label=3] at (s3) {};
-    \node[label=4] at (s4) {};
-    \node[label=5] at (s5) {};
-\end{tikzpicture}
-\caption{An example of sensor subsets; $\{1,2,3\}$ and $\{3,4,5\}$, and the areas where the navigator is in range of all sensors within a subset.}
-\label{fig:sensor_subsets}
-\end{figure}
-
-% 
-% ##       ########    ###    ##    ##    ###     ######   ######## 
-% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
-% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
-% ##       ######   ##     ## #####    ##     ## ##   #### ######   
-% ##       ##       ######### ##  ##   ######### ##    ##  ##       
-% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
-% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
-%
-
-\subsection{Inherent Leakage}
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates naturally leads to the leakage of some measurement information.
-For this reason, we accept that average information about sensors may be leaked at each time step and instead show that individual sensor information remains private.
-
-% 
-%  .d8888b.                            888                 8888888b.                  888 d8b               
-% d88P  Y88b                           888                 888   Y88b                 888 Y8P               
-% 888    888                           888                 888    888                 888                   
-% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
-% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
-% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888 
-% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888 
-%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888 
-%                         888 888                                                                           
-%                    Y8b d88P 888                                                                           
-%                     "Y88P"  888                                                                           
-%
-
-\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
-
-% 
-%  ######  ########  ######  ##     ## ########  #### ######## ##    ## 
-% ##    ## ##       ##    ## ##     ## ##     ##  ##     ##     ##  ##  
-% ##       ##       ##       ##     ## ##     ##  ##     ##      ####   
-%  ######  ######   ##       ##     ## ########   ##     ##       ##    
-%       ## ##       ##       ##     ## ##   ##    ##     ##       ##    
-% ##    ## ##       ##    ## ##     ## ##    ##   ##     ##       ##    
-%  ######  ########  ######   #######  ##     ## ####    ##       ##    
-%
-
-\subsection{Security Notions}
-The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}.
-\begin{defn}
-An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
-
-The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
-\end{defn}
-Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
-\begin{defn}
-An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
-
-The formal security game for AO has been given in Appendix \ref{app:ao}.
-\end{defn}
-
-% 
-% ########     ###    #### ##       ##       #### ######## ########  
-% ##     ##   ## ##    ##  ##       ##        ##  ##       ##     ## 
-% ##     ##  ##   ##   ##  ##       ##        ##  ##       ##     ## 
-% ########  ##     ##  ##  ##       ##        ##  ######   ########  
-% ##        #########  ##  ##       ##        ##  ##       ##   ##   
-% ##        ##     ##  ##  ##       ##        ##  ##       ##    ##  
-% ##        ##     ## #### ######## ######## #### ######## ##     ## 
-%
-
-\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
-The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
-Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
-A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}.
-The public key is defined by $(N, g)$ and secret key by $(p, q)$.
-
-Encryption of a plaintext message $m \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
-\begin{equation}
-    c = g^m r^N \pmod{N^2}
-\end{equation}
-for a randomly chosen $r \in \mathbb{Z}_{N}$.
-$r^N$ can be considered the noise term which hides the value $g^m \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
-The decryption of a ciphertext is computed by
-\begin{equation}
-    m = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
-\end{equation}
-where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.
-
-In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
-\begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
-\end{align}
-
-% 
-%       ##         ##    ## 
-%       ##          ##  ##  
-%       ##           ####   
-%       ## #######    ##    
-% ##    ##            ##    
-% ##    ##            ##    
-%  ######             ##    
-%
-
-\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
-The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO.
-Similarly to the Paillier scheme, it bases its security on the DCRA.
-A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.
-
-Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
-Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
-\begin{equation*}
-    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
-\end{equation*}
-and sent to the aggregator.
-
-Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at time $t$ is computed by user $i$ as
-\begin{equation}
-    c^{(t)}_{i} = (N+1)^{m^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
-\end{equation}
-where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{m^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
-
-When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, private summation and decryption are computed by the functions
-\begin{equation}
-    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
-\end{equation}
-and
-\begin{equation}
-    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
-\end{equation}
-Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
-\begin{equation*}
-    \begin{split}
-        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
-        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
-        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
-        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
-    \end{split}
-\end{equation*}
-removing all noise terms.
-
-% 
-%  .d8888b.                            888                 8888888b.                  888      
-% d88P  Y88b                           888                 888   Y88b                 888      
-% 888    888                           888                 888    888                 888      
-% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  88888b.  
-% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d88""88b 888 "88b 
-% 888    888 888     888  888 888  888 888   888  888      888        888    888  888 888  888 
-% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y88..88P 888 d88P 
-%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y88P"  88888P"  
-%                         888 888                                                              
-%                    Y8b d88P 888                                                              
-%                     "Y88P"  888                                                              
-%
-
-\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
-For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation.
-In the context of navigation, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$.
-This has been summarized in Figure \ref{fig:agg_steps}.
-In Section \ref{sec:private_localisation} we will show how this protocol can be sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.
-
-\begin{figure}[htbp]
-\centering
-\vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.75]
-    % Step 1
-    \node at (5,22.5) {\small 1. Broadcast and linear combinations step};
-    % Navigator
-    \node at (1.25,19.25) {Navigator};
-    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
-    % Sensors
-    \node at (7.5,21.75) {Sensor $1$};
-    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
-    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
-    \node at (7.5,14.75) {Sensor $n$};
-    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
-    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
-    \fill [black] (7.5,18.75) circle (0.05);
-    \fill [black] (7.5,17.75) circle (0.05);
-    \fill [black] (7.5,18.25) circle (0.05);
-    % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
-    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
-    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
-
-    % Step 2
-    \node at (5,13.25) {\small 2. Aggregation step};
-    % Navigator
-    \node at (3.25,10.75) {Navigator};
-    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
-    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
-    % Sensors
-    \node at (8.75,12.5) {Sensor $1$};
-    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
-    \node at (8.75,6.5) {Sensor $n$};
-    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
-    \fill [black] (8.75,10) circle (0.05);
-    \fill [black] (8.75,9) circle (0.05);
-    \fill [black] (8.75,9.5) circle (0.05);
-    % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
-    \node at (6.75,11.5) {$y_1^{(t)}$};
-    \node at (6.75,7.5) {$y_n^{(t)}$};
-
-    % Bounding rectangles
-    \draw [gray] (0,23.25) rectangle (10,14.25);
-    \draw [gray] (0,14) rectangle (10,5.5);
-\end{tikzpicture}
-\vspace{\baselineskip}
-\caption{Required linear-combination aggregation steps at time $t$.}
-\label{fig:agg_steps}
-\end{figure}
-
-To perform the protocol from Figure \ref{fig:agg_steps} in a secure manner, we must first describe the security properties we aim to achieve.
-Broadly speaking, we want a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme.
-That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations.
-This can be summarised by the two informal security notions:
-\begin{description}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous timesteps, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous timesteps.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
-\end{description}
-
-\begin{rem} \label{rem:lcao_leakage}
-    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
-Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
-\end{rem}
-
-From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
-To formalise the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
-
-% 
-% ##        ######     ###     #######  
-% ##       ##    ##   ## ##   ##     ## 
-% ##       ##        ##   ##  ##     ## 
-% ##       ##       ##     ## ##     ## 
-% ##       ##       ######### ##     ## 
-% ##       ##    ## ##     ## ##     ## 
-% ########  ######  ##     ##  #######  
-%
-
-\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
-We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$, defined as
-
-\begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
-    \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
-\end{description}
-
-Next, we formalise the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
-
-\begin{description}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
-    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
-    \begin{enumerate}
-        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
-        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
-        \end{equation*}
-        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
-        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{enumerate} 
-    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
-The attacker then chooses two series of tuples
-    \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
-    \end{equation*}
-    and
-    \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
-    \end{equation*}
-    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
-    \begin{equation*}
-        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
-    \end{equation*}
-    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
-    \begin{equation*}
-        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
-    \end{equation*}
-    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
-    \begin{equation*}
-        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
-    \end{equation*} 
-\end{description}
-
-\begin{defn}
-    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game.
-Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
-\end{defn}
-
-In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
-
-% 
-%  .d88888b.                         .d8888b.           888                                      
-% d88P" "Y88b                       d88P  Y88b          888                                      
-% 888     888                       Y88b.               888                                      
-% 888     888 888  888 888d888       "Y888b.    .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.  
-% 888     888 888  888 888P"            "Y88b. d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b 
-% 888     888 888  888 888                "888 888      888  888 88888888 888  888  888 88888888 
-% Y88b. .d88P Y88b 888 888          Y88b  d88P Y88b.    888  888 Y8b.     888  888  888 Y8b.     
-%  "Y88888P"   "Y88888 888           "Y8888P"   "Y8888P 888  888  "Y8888  888  888  888  "Y8888  
-%                                                                                                
-%                                                                                                
-%                                                                                                
-%
-
-\section{Our Scheme} \label{sec:our_scheme}
-Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
-As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys.
-Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.
-
-\begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
-Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$.
-The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
-
-    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
-    \begin{equation}
-        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
-    \end{equation}
-    for a randomly chosen $r \in \mathbb{Z}_N$.
-
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as
-    \begin{equation}
-        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
-    \end{equation}
-    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
-    \begin{equation*}
-        \begin{split}
-             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
-            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
-        \end{split}
-    \end{equation*}
-    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
-Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
-
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
-    \begin{equation}
-        \begin{split}
-            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
-            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
-        \end{split} \label{eqn:our_scheme_decrypt}
-    \end{equation}
-    The correctness of aggregation can be seen from
-    \begin{align*}
-        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
-        \begin{split}
-            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
-        \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
-    \end{align*}
-    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
-\end{description}
-
-Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $x^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.
-
-% 
-% ########  ########   #######   #######  ######## 
-% ##     ## ##     ## ##     ## ##     ## ##       
-% ##     ## ##     ## ##     ## ##     ## ##       
-% ########  ########  ##     ## ##     ## ######   
-% ##        ##   ##   ##     ## ##     ## ##       
-% ##        ##    ##  ##     ## ##     ## ##       
-% ##        ##     ##  #######   #######  ##       
-%
-
-\subsection{Security Proof}
-To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
-From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA.
-We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.
-
-To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger using the \textit{Joye-Libert scheme}, such that
-\begin{equation*}
-    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
-\end{equation*}
-for some negligible functions $\eta_1$ and $\eta_2$.
-(\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.
-The function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
-\begin{pf}
-    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}.
-The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
-    \begin{description}
-        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
-        \item[Queries] Handle queries from $\mathcal{A}$:
-        \begin{description}
-            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
-            \begin{equation*}
-                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
-            \end{equation*}
-            to $\mathcal{A}$.
-            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
-The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
-            \begin{equation*}
-                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
-            \end{equation*}
-            to $\mathcal{A}$.
-            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
-        \end{description}
-        \item[Challenge] When $\mathcal{A}$ submits challenge series
-        \begin{equation*}
-            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
-        \end{equation*}
-        and
-        \begin{equation*}
-            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
-        \end{equation*}
-        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
-        \begin{equation*}
-            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
-        \end{equation*}
-        and
-        \begin{equation*}
-            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
-        \end{equation*}
-        to $\mathcal{C}$. The received response if of the form 
-        \begin{equation*}
-            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
-        \end{equation*}
-        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
-        \begin{equation*}
-            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
-        \end{equation*}
-        to $\mathcal{A}$.
-        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
-    \end{description}
-
-    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{sec:our_scheme}.
-Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
-That is, there exists a negligible function $\eta$, such that
-    \begin{equation*}
-        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
-    \end{equation*}
-    for security parameter $\kappa$. \qed
-\end{pf}
-
-% 
-% 888                            8888888b.                  888 d8b               
-% 888                            888   Y88b                 888 Y8P               
-% 888                            888    888                 888                   
-% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
-% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
-% 888     888  888 888           888        888    88888888 888 888 888  888  888 
-% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888 
-% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888 
-%                                                                                 
-%                                                                                 
-%                                                                                 
-%
-
-\section{Private Localisation Preliminaries} \label{sec:loc_prelim}
-The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model.
-We make use of a real-number encoding scheme which supports the required homomorphic operations and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to use only these operations.
-
-% 
-% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
-% ##       ###   ## ##    ## ##     ## ##     ##  ##  ###   ## ##    ##  
-% ##       ####  ## ##       ##     ## ##     ##  ##  ####  ## ##        
-% ######   ## ## ## ##       ##     ## ##     ##  ##  ## ## ## ##   #### 
-% ##       ##  #### ##       ##     ## ##     ##  ##  ##  #### ##    ##  
-% ##       ##   ### ##    ## ##     ## ##     ##  ##  ##   ### ##    ##  
-% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
-%
-
-\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
-In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$.
-For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing.
-We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
-
-We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$.
-This contrasts with the common definition given in terms of total bits $a$ and fractional bits $b$ \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
-Rational subset $\mathbb{Q}_{r,f}$ is given by
-\begin{equation*}
-    \mathbb{Q}_{r,f} = \left\{q : f^{-1} | q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
-\end{equation*}
-and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$.
-That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$.
-In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic.
-In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
-This is captured by a third parameter $m$; the number of \textit{additional} multiplication factors to add or remove from encodings.
-
-The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
-\begin{equation}
-    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
-\end{equation}
-Decoding of an integer $e \in \mathbb{Z}_N$, is given by
-\begin{equation}
-    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
-    \begin{dcases}
-        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
-        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
-    \end{dcases}.\label{eqn:decode}
-\end{equation}
-
-This encoding scheme provides the following homomorphic operations,
-\begin{equation}
-    \begin{split}
-        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
-        &\mathsf{E}_{N,f,m}(a_1+a_2)
-    \end{split}\label{eqn:encoding_homomorphic_add}
-\end{equation}
-and
-\begin{equation}
-    \begin{split}
-        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
-        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
-    \end{split}
-\end{equation}
-noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.
-
-The choice of a high fractional precision $f$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
-Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
-\begin{equation*}
-    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{N}{2} \right\rfloor\,.
-\end{equation*}
-In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored.
-
-% 
-% ######## #### ######## 
-% ##        ##  ##       
-% ##        ##  ##       
-% ######    ##  ######   
-% ##        ##  ##       
-% ##        ##  ##       
-% ######## #### ##       
-%
-
-\subsection{Extended Information Filter}
-The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
-This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
-\begin{equation}
-    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
-\end{equation}
-respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
-\begin{equation}
-    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
-\end{equation}
-and
-\begin{equation}
-    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
-\end{equation}
-with Jacobian
-\begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
-\end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
-\begin{equation}
-    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
-\end{equation}
-before using the normal EKF prediction equations
-\begin{equation}
-    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
-\end{equation}
-and
-\begin{equation}
-    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
-\end{equation}
-with Jacobian
-\begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
-\end{equation}
-
-% 
-% 8888888b.          d8b               888                       
-% 888   Y88b         Y8P               888                       
-% 888    888                           888                       
-% 888   d88P 888d888 888 888  888      888      .d88b.   .d8888b 
-% 8888888P"  888P"   888 888  888      888     d88""88b d88P"    
-% 888        888     888 Y88  88P      888     888  888 888      
-% 888        888     888  Y8bd8P       888     Y88..88P Y88b.    
-% 888        888     888   Y88P        88888888 "Y88P"   "Y8888P 
-%                                                                
-%                                                                
-%                                                                
-%
-
-\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
-Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}.
-We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
-Received information from each sensor $i$ consists of the measurement vector
-\begin{equation}
-    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
-\end{equation}
-and the measurement matrix
-\begin{equation}
-    \mat{I}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:measurement_mat}
-\end{equation}
-at each time step $k$.
-In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
-Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-
-Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$.
-Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
-As was shown in Section \ref{sec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
-From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.
-
-% 
-% ##     ##   ### ##     ## ###      ########  ########  #######   ######  
-% ##     ##  ##    ##   ##    ##     ##     ## ##       ##     ## ##    ## 
-% ##     ## ##      ## ##      ##    ##     ## ##       ##     ## ##       
-% ######### ##       ###       ##    ########  ######   ##     ##  ######  
-% ##     ## ##      ## ##      ##    ##   ##   ##       ##  ## ##       ## 
-% ##     ##  ##    ##   ##    ##     ##    ##  ##       ##    ##  ##    ## 
-% ##     ##   ### ##     ## ###      ##     ## ########  ##### ##  ######  
-%
-
-\subsection{Requirements for the Measurement Model}
-From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with weights dependant only on those from the original matrices.
-For example, consider dimension $N\times N$ matrices $\mat{A}$ and $\mat{B}$, where element $(i,j)$ in matrix $\mat{A}$ is of the form $\sum_{l=0}^M w_{l,i,j}a_{l,i,j}$ and similarly for matrix $\mat{B}$, form $\sum_{l=0}^M v_{l,i,j}b_{l,i,j}$.
-If we consider $w_{l,i,j}$ and $v_{l,i,j}$ as the weight terms, we can write element $(i,j)$ of a product matrix $\mat{A}\mat{B}$, with weights dependant only on these, as
-\begin{equation}
-    \begin{split}
-        \sum_{l=0}^N&\left(\left(\sum_{m=0}^M w_{m,i,j}a_{m,i,l}\right)\left(\sum_{m=0}^Mv_{m,i,j}b_{m,l,j}\right)\right) \\
-        &=\sum_{l=0}^N\left(\sum_{m=0}^M\sum_{n=0}^M w_{m,i,l}a_{m,i,l}v_{n,l,j}b_{n,l,j}\right) \\
-        &=\sum_{l=0}^N\sum_{m=0}^M\sum_{n=0}^M (w_{m,i,l}v_{n,l,j})a_{m,i,l}b_{n,l,j}\,.
-    \end{split} \label{eqn:matrix_mult_weights}
-\end{equation}
-Similarly, scalar multiplication also holds this property.
-It is therefore sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
-Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.
-
-% 
-%  #######  ########   ######     ##     ##  #######  ########  ######## ##       
-% ##     ## ##     ## ##    ##    ###   ### ##     ## ##     ## ##       ##       
-% ##     ## ##     ## ##          #### #### ##     ## ##     ## ##       ##       
-% ##     ## ########   ######     ## ### ## ##     ## ##     ## ######   ##       
-% ##     ## ##     ##       ##    ##     ## ##     ## ##     ## ##       ##       
-% ##     ## ##     ## ##    ##    ##     ## ##     ## ##     ## ##       ##       
-%  #######  ########   ######     ##     ##  #######  ########  ######## ######## 
-%
-
-\subsection{Localisation Measurement Model} \label{subsec:observation_model}
-Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
-In addition, the Jacobian of $h_i$,
-\begin{equation}
-    \mat{H}_{k,i} = 
-    \begin{bmatrix}
-        \frac{\rv{x}_k - s_{x,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} \\
-        \frac{\rv{y}_k - s_{y,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} 
-    \end{bmatrix}\,,
-\end{equation}
-cannot be either. Instead, we consider the modified measurement functions
-\begin{equation}
-    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
-\end{equation}
-A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well.
-The modified measurement functions $h'_i$ can be written as
-\begin{equation}
-    \begin{split}
-        h'_i(\rvec{x}_k) &= \left\lVert
-        \begin{bmatrix}
-            \rv{x}_k & \rv{y}_k
-        \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
-        &= (\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2 \\
-        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_{x,i}\rv{x}_k -2s_{y,i}\rv{y}_k +s_{x,i}^2 +s_{y,i}^2
-    \end{split}\,,
-\end{equation}
-and the corresponding Jacobians $\mat{H}'_{k,i}$ as
-\begin{equation}
-    \mat{H}'_{k,i} = 
-    \begin{bmatrix}
-        2\rv{x}_k - 2s_{x,i} \\
-        2\rv{y}_k - 2s_{y,i}
-    \end{bmatrix}\,.
-\end{equation}
-The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.
-
-To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using \eqref{eqn:matrix_mult_weights}, we require the existance of a modified measurement model of the form
-\begin{equation}
-    \rv{z}'_{k,i} = h'_i(\rvec{x}_k)+\rv{v}'_{k,i}\,, \label{eqn:modified_measurement_model}
-\end{equation}
-where $\rv{z}'_{k,i}$ is the modified measurement, and noise $\rv{v}'_{k,i}$ is white and Gaussian.
-The approximation of $\rv{z}'_{k,i}$ and $\rv{r}_{k,i}$ from original measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be shown in Section \ref{subsec:range_measurement_mod}.
-
-With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
-\begin{equation}
-    \begin{split}
-        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
-        &= 
-        \begin{bmatrix}
-            \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
-            \end{split}
-            \vspace{5pt}\\
-            \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
-            \end{split}
-        \end{bmatrix}
-    \end{split} \label{eqn:hrz_linear_comb}
-\end{equation}
-and
-\begin{equation}
-    \begin{split}
-        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
-        &=
-        \begin{bmatrix}
-            \alpha_{11} & \alpha_{12} \\
-            \alpha_{21} & \alpha_{22}
-        \end{bmatrix}\,,
-    \end{split} \label{eqn:hrh_linear_comb}
-\end{equation}
-with
-\begin{align*}
-    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
-    \begin{split}
-        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
-        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
-    \end{split}\\
-    \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
-\end{align*}
-The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k\rv{y}_k$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.
-
-The final step required for the application of our LCAO-secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance-stamp variable $t$, in \eqref{eqn:our_scheme_lin_comb}.
-As six linear-combination aggregations occur at each time step $k$ (four element in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
-This is handled by setting $t$ to the concatenation
-\begin{equation}
-    t=k\mathbin\|i\mathbin\|j\mathbin\|b
-\end{equation}
-for aggregation in row $i$ and column $j$, with $b=0$ for aggregations in $\rvec{i}'_{k,i}$ and $b=1$ otherwise.
-\begin{rem}
-    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localisation, but can be similarly extended to the three-dimensional case.
-We note however, the additional cost with increasing dimension.
-The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by \eqref{eqn:matrix_mult_weights}.
-This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
-\end{rem}
-
-% 
-%  ######   #######  ##     ##    ###    ########  ######## ########     ######## 
-% ##    ## ##     ## ##     ##   ## ##   ##     ## ##       ##     ##         ##  
-% ##       ##     ## ##     ##  ##   ##  ##     ## ##       ##     ##        ##   
-%  ######  ##     ## ##     ## ##     ## ########  ######   ##     ##       ##    
-%       ## ##  ## ## ##     ## ######### ##   ##   ##       ##     ##      ##     
-% ##    ## ##    ##  ##     ## ##     ## ##    ##  ##       ##     ##     ##      
-%  ######   ##### ##  #######  ##     ## ##     ## ######## ########     ######## 
-%
-
-\subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ with Gaussian noise and variances $\rv{r}_{k,i}$ in the modified measurement model \eqref{eqn:modified_measurement_model}.
-In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
-Squaring the range measurement produces
-\begin{equation}
-    \begin{split}
-        \rv{z}_{k,i}^2 &= (h_i(\rvec{x}_k) + \rv{v}_{k,i})^2 \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 \\
-        &= h'_i(\rvec{x}_k) + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2\,,
-    \end{split}
-\end{equation}
-with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependant on the measurement function $h_i$ and no longer white or Gaussian.
-We can compute the mean of the new noise term (a function of white Gaussian term $\rv{v}_{k,i}$) as
-\begin{equation}
-    \E{2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2} = r_i\, \label{eqn:modified_noise_mean}
-\end{equation}
-and define modified measurements as
-\begin{equation} \label{eqn:modified_measurement}
-    \begin{split}
-        \rv{z}'_{k,i} &= \rv{z}_{k,i}^2 - r_i \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \\
-        &= h'_i(\rvec{x}_k) + \rv{v}'_{k,i}\,,
-    \end{split}
-\end{equation}
-with now zero-mean noise $\rv{v}'_{k,i} = 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i$. The noise in this case (again a function of white Gaussian term $\rv{v}_{k,i}$) has variance 
-\begin{equation}
-    \Var{\rv{v}'_{k,i}} = 4h_i(\rvec{x}_k)^2r_i + 2r_i^2
-\end{equation}
-and is dependant on $h_i(\rvec{x}_k)$.
-We also wish to approximate this noise using values available to the sensor, $\rv{z}_{k,i}$ and $r_i$, while providing a conservative estimate of the true variance so as not to affect the convergence of the EIF.
-While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate in the case
-\begin{equation}
-    \begin{split}
-        \rv{z}_{k,i} &> h_i(\rvec{x}_k) \\
-        \rv{z}_{k,i} - h_i(\rvec{x}_k) &> 0 \\
-        \rv{v}_{k,i} &> 0\,,
-    \end{split}
-\end{equation}
-which cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
-Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
-\begin{equation}
-    \rv{r}_{k, i} = 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2\,. \label{eqn:modified_meaasurement_variance_estimate}
-\end{equation}
-
-In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variances, as shown by
-\begin{equation}
-    \begin{split}
-        &r_i << h_i(\rvec{x}_k) \\
-        \implies &2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i} \\
-        \implies &\rv{v}'_{k,i} \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i}\,,
-    \end{split} \label{eqn:modified_noise_approaches_gaussian}
-\end{equation}
-and conclude with the following assumption.
-\begin{assum}
-    Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
-\end{assum}
-
-% 
-%    ###    ##        ######    #######  ########  #### ######## ##     ## ##     ## 
-%   ## ##   ##       ##    ##  ##     ## ##     ##  ##     ##    ##     ## ###   ### 
-%  ##   ##  ##       ##        ##     ## ##     ##  ##     ##    ##     ## #### #### 
-% ##     ## ##       ##   #### ##     ## ########   ##     ##    ######### ## ### ## 
-% ######### ##       ##    ##  ##     ## ##   ##    ##     ##    ##     ## ##     ## 
-% ##     ## ##       ##    ##  ##     ## ##    ##   ##     ##    ##     ## ##     ## 
-% ##     ## ########  ######    #######  ##     ## ####    ##    ##     ## ##     ## 
-%
-
-\subsection{Algorithm} \label{subsec:algorithm}
-In this section, we piece together our LCAO secure encryption scheme in Section \ref{sec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.
-
-The privacy-preserving localisation filter can be described by the following steps.
-\begin{description}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{sec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
-Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
-We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.
-
-    \item[Prediction] The navigator computes the typical EKF prediction equations before encrypting state variables and broadcasting to sensors. This is given by Algorithm \ref{alg:nav_prediction}.
-
-    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,1}$ and $\mat{I}'_{k,1}$, encrypting them for aggregation, and sending them back to the navigator.
-Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}.
-This has been described by Algorithm \ref{alg:measurement_info}.
-
-    \item[Update] The navigator aggregates measurement vectors and matrices before decrypting them.
-The typical EIF update equations can then be computed.
-This is shown in Algorithm \ref{alg:nav_update}.
-\end{description}
-
-\begin{algorithm}[htbp]
-    \caption{Navigator Prediction}\label{alg:nav_prediction}
-    \begin{algorithmic}[1]
-        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
-
-        \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
-        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
-        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
-
-        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k\rv{y}_k,\rv{x}_k,\rv{y}_k\rangle$} 
-            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
-            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
-            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
-        \EndFor
-
-        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
-        \EndProcedure
-    \end{algorithmic}
-    \end{algorithm}
-
-\begin{algorithm}[htbp]
-\caption{Measurement at Sensor $i$}\label{alg:measurement_info}
-\begin{algorithmic}[1]
-    \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}
-
-    \State Measure $\rv{z}_{k,i}$
-    \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
-    \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_meaasurement_variance_estimate}
-
-    \While{Navigator broadcasting}
-    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))$
-    \State Recieve remaining weights in the form above
-    \EndWhile
-
-    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}$\par
-    \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
-    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}$\par
-    \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
-    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
-    \For{$v \gets 1$ to $2$}
-        \State Send $\beta_{v1}$ to the navigator
-    \EndFor
-
-    \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}
-    (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}$\par
-    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
-    \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$} 
-            \State Send $\alpha_{vw}^{(i)}$ to the navigator
-        \EndFor
-    \EndFor
-    \EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}[htbp]
-\caption{Navigator Update}\label{alg:nav_update}
-\begin{algorithmic}[1]
-    \Procedure{Update}{$\rvec{x}_{k}$, $\mat{P}_{k}$, $N$, $\lambda$}
-
-    \For{$v \gets 1$ to $2$}
-        \State Receive $\beta_{v1}^{(i)}$ from each sensor $1\leq i \leq n$
-    \EndFor
-
-    \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$}
-        \State Receive $\alpha_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
-        \EndFor
-    \EndFor
-
-    \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
-    \For{$v \gets 1$ to $2$}
-        \State $\beta_{v1} \gets \prod_{i=1}^n\beta_{v1}^{(i)}$
-        \State Compute $\mathcal{D}_{sk_0}(\beta_{v1})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{v1}))$ by \eqref{eqn:decode}
-    \EndFor
-    \State Construct $\sum_{i=1}^n\rvec{i}'_{k,i}$ from decoded decryptions above
-
-    \State Let $\alpha_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
-    \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$}
-            \State $\alpha_{vw} \gets \prod_{i=1}^n\alpha_{vw}^{(i)}$
-            \State Compute $\mathcal{D}_{sk_0}(\alpha_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{vw}))$ by \eqref{eqn:decode}
-        \EndFor
-    \EndFor
-    \State Construct $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above
-
-    \State $\rvec{y}_k \gets \mat{P}_{k}^{-1}\rvec{x}_{k} + \sum_{i=1}^n\rvec{i}'_{k,i}$
-    \State $\mat{Y}_k \gets \mat{P}_{k}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
-    \State $\rvec{x}_{k} \gets \mat{Y}_k^{-1}\rvec{y}_k$
-    \State $\mat{P}_{k} \gets \mat{Y}_k^{-1}$
-    \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
-    \EndProcedure
-\end{algorithmic}
-\end{algorithm}
-
-Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_m(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
-
-\begin{figure}[htbp]
-\centering
-\vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
-    % Prediction
-    \draw  (0,1.75) rectangle (8,8);
-    \node at (4,7.5) {\small 1. Prediction};
-
-    % Navigator
-    \fill  [blue!40] (3.25,7) rectangle (4.75,5.5);
-    \pic[xscale=0.22,yscale=0.3] at (4,6.6725) {plane};
-    \node at (4,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
-
-    % Sensors
-    \fill  (1.5,3) [red!40] ellipse (0.5 and 0.5);
-    \node at (1.5,2.25) {Sensor $1$};
-    \fill  (6.5,3) [red!40] ellipse (0.5 and 0.5);
-    \node at (6.5,2.25) {Sensor $n$};
-
-    \fill [black] (3.5,3) circle (0.05);
-    \fill [black] (4,3) circle (0.05);
-    \fill [black] (4.5,3) circle (0.05);
+% Adversaries and challenger
+\node at (4,3.5) {\LARGE$\mathcal{A}'$};
+\node at (4,6) {\LARGE$\mathcal{A}$};
+\node at (4,0.5) {\LARGE$\mathcal{C}$};
 
 % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.75,5.25) (1.75,3.5)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(4.25,5.25) (6.25,3.5)};
+\node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
+\draw [-latex] (2,1.75) -- (2,2.75);
 
-    \fill [lightgray]  (0.25,5) rectangle (7.75,4);
-    \node at (4,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k, \rv{y}_k\}\rangle$};
+\node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
+\draw [-latex] (2,4.5) --(2,5.5);
 
-    % Measurement
-    \draw  (0,-4.75) rectangle (8,1.5);
-    \node at (4,1) {\small 2. Measurement};
+\node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
+\draw [-latex] (6,5.5) -- (6,4.5);
 
-    % Navigator
-    \fill  (4,0) [blue!40] ellipse (0.5 and 0.5);
-    \pic[xscale=0.22,yscale=0.3] at (4,0.1725) {plane};
-
-    % Sensors
-    \fill  [red!40] (7.5,-3.75)  rectangle (5.5,-2.75);
-    \node at (1.5,-4.25) {Sensor $1$};
-    \fill  [red!40] (2.5,-3.75)  rectangle (0.5,-2.75);
-    \node at (6.5,-4.25) {Sensor $n$};
-
-    \node at (1.5,-3.25) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
-    \node at (6.5,-3.25) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};
-
-    \fill [black] (3.5,-3.25) circle (0.05);
-    \fill [black] (4,-3.25) circle (0.05);
-    \fill [black] (4.5,-3.25) circle (0.05);
-
-    % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,-2.5) (3.75,-0.75)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(6.25,-2.5) (4.25,-0.75)};
-
-    \fill [lightgray]  (0.5,-1.25) rectangle (3.5,-2.25);
-    \node[align=center] at (2,-1.75) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
-    \fill [lightgray]  (4.5,-1.25) rectangle (7.5,-2.25);
-    \node[align=center] at (6,-1.75) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
-
-    % Update
-    \draw  (0,-10.25) rectangle (8,-5);
-    \node at (4,-5.5) {\small 3. Update};
-
-    % Navigator
-    \fill  [blue!40] (2.25,-6) rectangle (5.75,-8);
-    \pic[xscale=0.22,yscale=0.3] at (4,-6.3275) {plane};
-    \node at (4,-7.125) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (4,-7.625) {$\rvec{x}_k$, $\mat{P}_k$};
-
-    % Sensors
-    \fill  (6.5,-9) [red!40] ellipse (0.5 and 0.5);
-    \node at (1.5,-9.75) {Sensor $1$};
-    \fill  (1.5,-9) [red!40] ellipse (0.5 and 0.5);
-    \node at (6.5,-9.75) {Sensor $n$};
-
-    \fill [black] (3.5,-9) circle (0.05);
-    \fill [black] (4,-9) circle (0.05);
-    \fill [black] (4.5,-9) circle (0.05);
+\node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
+\draw [-latex] (6,2.75) -- (6,1.75);
 
 \end{tikzpicture}
-\vspace{\baselineskip}
-\caption{The summary of steps involved in our proposed privacy-preserving EIF.}
-\label{fig:alg_steps}
-\end{figure}
-
-% 
-% ##       ########    ###    ##    ##    ###     ######   ######## 
-% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
-% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
-% ##       ######   ##     ## #####    ##     ## ##   #### ######   
-% ##       ##       ######### ##  ##   ######### ##    ##  ##       
-% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
-% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
-%
-
-\subsection{Leakage} \label{subsec:leakage}
-With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account.
-We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}.
-Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme security, but avoid malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achieved by detecting changes in real measurements after reporting false measurements to the navigator.
-As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicate homomorphic operations and active malicious sensors are beyond the scope of this work.
-
-The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$.
-However, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
-That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.} $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
-
-From the leaked coefficient sums, we see that all information private to the sensors, namely their measurements $\rv{z}'_{k,i}$ and locations $\vec{s}_i$, are present only in sums
-\begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localisation_leakage}
-\end{equation}
-Therefore, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor measurements and locations.
-\begin{rem}
-    In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor measurements and locations, given by the sums in \eqref{eqn:localisation_leakage}.
-\end{rem}
-
-% 
-% 8888888b.                            888 888             
-% 888   Y88b                           888 888             
-% 888    888                           888 888             
-% 888   d88P .d88b.  .d8888b  888  888 888 888888 .d8888b  
-% 8888888P" d8P  Y8b 88K      888  888 888 888    88K      
-% 888 T88b  88888888 "Y8888b. 888  888 888 888    "Y8888b. 
-% 888  T88b Y8b.          X88 Y88b 888 888 Y88b.       X88 
-% 888   T88b "Y8888   88888P'  "Y88888 888  "Y888  88888P' 
-%                                                          
-%                                                          
-%                                                          
-%
-
-\section{Results} \label{sec:results}
-Time results can be captured in one graph.
-Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048).
-Every data point should be the average over some X number of simulations.
-
-Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
-All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense):
-
-Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
-
-Plot 2 will plot the RMSE as the average distance of sensors changes.
-Fixed encoding and Paillier bit size.
-Vary between 4 layouts where 4 sensors are either very close to the centre (and ground truth, and progressively further out)
-
-Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).
-
-Discuss the meaning of the small changes in accuracy, and runtimes when using the same encryption size, that is, point out it is a generally robust method.
-
-% 
-%  .d8888b.                             
-% d88P  Y88b                            
-% 888    888                            
-% 888         .d88b.  88888b.   .d8888b 
-% 888        d88""88b 888 "88b d88P"    
-% 888    888 888  888 888  888 888      
-% Y88b  d88P Y88..88P 888  888 Y88b.    
-%  "Y8888P"   "Y88P"  888  888  "Y8888P 
-%                                       
-%                                       
-%                                       
-%
-
-\section{Conclusion} \label{sec:conclusion}
-Possible future work to consider: Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors or a way to confirm they are the same.
-
-%---Rest is template---
-
-% \section{Introduction}
-% Video, patres conscripti, in me omnium vestrum ora atque oculos esse 
-% conversos, video vos non solunn de vestro ac rei publicae, verum 
-% etiam, si id depulsum sit, de meo periculo esse sollicitos. Est mihi 
-% iucunda in malis et grata in dolore vestra erga me voluntas, sed eam, 
-% per deos inmortales, deponite atque obliti salutis meae de vobis ac 
-% de vestris liberis cogitate. Mihi si haec condicio consulatus data 
-% est, ut omnis acerbitates, onunis dolores cruciatusque perferrem, 
-% feram non solum fortiter, verum etiam lubenter, dum modo meis 
-% laboribus vobis populoque Romano dignitas salusque pariatur.
-
-% \begin{figure}
-% \begin{center}
-% \includegraphics[height=4cm]{jcaesar.eps}    % The printed column  
-% \caption{Gaius Julius Caesar, 100--44 B.C.}  % width is 8.4 cm.
-% \label{fig1}                                 % Size the figures 
-% \end{center}                                 % accordingly.
-% \end{figure}
-
-% % OR
-
-% %\begin{figure}
-% %\begin{center}
-% %\epsfig{file=jcaesar,width=7cm}
-% %\caption{Gaius Julius Caesar, 100--44 B.C.}
-% %\label{fig1}
-% %\end{center}
-% %\end{figure}
-
-% \subsection{A subsection}
-% Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
-% and philosopher.  A major figure in the last years of the Republic, 
-% he is best known for his orations against Catiline\footnote{
-% This footnote should be very brief.}
-% and for his mastery of Latin prose \cite{Heritage:92}. He was a 
-% contemporary of Julius Caesar (Fig.~\ref{fig1}).
-
-% \section{The argument}
-% Some words might be appropriate describing equation~(\ref{e1}), if 
-% we had but time and space enough.
-% \begin{equation} \label{e1}
-% {{\partial F}\over {\partial t}} =
-% D{{\partial^2 F}\over {\partial x^2}}.
-% \end{equation}
-% See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and 
-% \cite{Pow:85}.
-% This equation goes far beyond the celebrated theorem ascribed to the great
-% Pythagoras by his followers.
-% \begin{thm}
-% The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
-% of the lengths of the other two sides.
-% \end{thm}
-% \section{Epilogue}
-% A word or two to conclude, and this even includes some inline 
-% maths:  $R(x,t)\sim t^{-\beta}g(x/t^\alpha)\exp(-|x|/t^\alpha)$.
-
-% Place acknowledgements
-% here.
-\begin{ack}                               
-Partially supported by zim
-\end{ack}
-
-% Include this if you use bibtex 
-% and a bib file to produce the 
-% bibliography (preferred). The
-% correct style is generated by
-% Elsevier at the time of printing.
-\bibliographystyle{plain}
-\bibliography{BibTeX/PrivateEIFLocalisation}
-
-%\begin{thebibliography}{99}     % Otherwise use the  
-                                 % thebibliography environment.
-                                 % Insert the full references here.
-                                 % See a recent issue of Automatica 
-                                 % for the style.
-%  \bibitem[Heritage, 1992]{Heritage:92}
-%     (1992) {\it The American Heritage. 
-%     Dictionary of the American Language.}
-%     Houghton Mifflin Company.
-%  \bibitem[Able, 1956]{Abl:56}
-%     B.~C.~Able (1956). Nucleic acid content of macroscope. 
-%     {\it Nature 2}, 7--9. 
-%  \bibitem[Able {\em et al.}, 1954]{AbTaRu:54}   
-%     B.~C. Able, R.~A. Tagg, and M.~Rush (1954).
-%     Enzyme-catalyzed cellular transanimations.
-%     In A.~F.~Round, editor, 
-%     {\it Advances in Enzymology Vol. 2} (125--247). 
-%     New York, Academic Press.
-%  \bibitem[R.~Keohane, 1958]{Keo:58}
-%     R.~Keohane (1958).
-%     {\it Power and Interdependence: 
-%     World Politics in Transition.}
-%     Boston, Little, Brown \& Co.
-%  \bibitem[Powers, 1985]{Pow:85}
-%     T.~Powers (1985).
-%     Is there a way out?
-%     {\it Harpers, June 1985}, 35--47.
-
-%\end{thebibliography}
-
-% Each appendix must have a short title.
-% Sections and subsections are supported
-% in the appendices.
-\appendix
-% 
-%        d8888                                          888 d8b          
-%       d88888                                          888 Y8P          
-%      d88P888                                          888              
-%     d88P 888 88888b.  88888b.   .d88b.  88888b.   .d88888 888 888  888 
-%    d88P  888 888 "88b 888 "88b d8P  Y8b 888 "88b d88" 888 888 `Y8bd8P' 
-%   d88P   888 888  888 888  888 88888888 888  888 888  888 888   X88K   
-%  d8888888888 888 d88P 888 d88P Y8b.     888  888 Y88b 888 888 .d8""8b. 
-% d88P     888 88888P"  88888P"   "Y8888  888  888  "Y88888 888 888  888 
-%              888      888                                              
-%              888      888                                              
-%              888      888                                              
-%
-
-\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
-A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
-\begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
-    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
-    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
-\end{description}
-
-The security game between attacker and challenger for IND-CPA is given by
-\begin{description}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public key $pk$ to the attacker
-    \item[Encryptions] The attacker may compute encryptions using the public key $pk$.
-    \item[Challenge] Next, the attacker chooses two values
-    \begin{equation*}
-        x^{(0)} \text{ and } x^{(1)}
-    \end{equation*}
-    and gives them to the challenger. The challenger then chooses a random bit $b \in \{1,0\}$ and returns the encryption
-    \begin{equation*}
-        \mathcal{E}_{pk}(x^{(b)}).
-    \end{equation*}
-    \item[More Encryptions] The attacker can now compute more encryptions with the public key $pk$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
-    \begin{equation*}
-        \mathsf{Adv}^{IND-CPA}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
-    \end{equation*} 
-\end{description}
-
-\section{Aggregator Obliviousness (AO)} \label{app:ao}
-An aggregator oblivious encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{AggDec})$, defined as
-\begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
-    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At time $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
-\end{description}
-
-The security game between attacker and challenger for AO is given by
-\begin{description}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
-    \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
-    \begin{enumerate}
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_i)$ and $(i',t',x^{\prime(t')}_{i'}$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies x^{(t)}_{i} = x^{\prime(t')}_{i'}\,.
-        \end{equation*}
-        They are given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
-        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{enumerate} 
-    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
-The attacker then chooses two series of tuples
-    \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(0)}_i)\,|\,i \in S\rangle
-    \end{equation*}
-    and
-    \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(1)}_i)\,|\, i \in S\rangle\,,
-    \end{equation*}
-    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
-    \begin{equation*}
-        \sum_{i\in S} x^{(t^*)(0)}_i = \sum_{i \in S} x^{(t^*)(1)}_i\,.
-    \end{equation*}
-    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
-    \begin{equation*}
-        \langle\mathcal{E}_{sk_i}(x^{(t^*)(b)}_i)\,|\,i\in S\rangle\,.
-    \end{equation*}
-    \item[More Queries] The attacker can now submit more queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
-    \begin{equation*}
-        \mathsf{Adv}^{AO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
-    \end{equation*} 
-\end{description}
-
-\end{document}

### 2020-10-02 tikz_images/proof.tex.preview.tex
Added cryptography proof summary tikz diagram - changed text a tiny bit to reference it nicely Moved tikz image files to their own folder - nicer to keep the imported pdfs and the itkz picture (which aren't imported) seperate

--- 2020-10-02 tikz_images/proof.tex
@@
+%& C:\Users\tn5093\AppData\Roaming\TikzEdt\TikzEdt\023~1.0\TEMP_H~1
+\begin{document}
+
 \begin{tikzpicture}[font=\footnotesize]
@@
 
+\usetikzlibrary{calc}
+\pgftransformreset
+\node[inner sep=0pt,outer sep=0pt,minimum size=0pt,line width=0pt,text width=0pt,text height=0pt] at (current bounding box) {};
+%add border to avoid cropping by pdflibnet
+\foreach \border in {0.1}
+  \useasboundingbox (current bounding box.south west)+(-\border,-\border) rectangle (current bounding box.north east)+(\border,\border);
+\newwrite\metadatafile
+\immediate\openout\metadatafile=\jobname_BB.txt
+\path
+  let
+    \p1=(current bounding box.south west),
+    \p2=(current bounding box.north east)
+  in
+  node[inner sep=0pt,outer sep=0pt,minimum size=0pt,line width=0pt,text width=0pt,text height=0pt,draw=white] at (current bounding box) {
+\immediate\write\metadatafile{\p1,\p2}
+};
+\immediate\closeout\metadatafile
 \end{tikzpicture}
+
+\end{document}
+
+gbox (current bounding box.south west)+(-\border,-\border) rectangle (current bounding box.north east)+(\border,\border);
+\newwrite\metadatafile
+\immediate\openout\metadatafile=\jobname_BB.txt
+\path
+  let
+    \p1=(current bounding box.south west),
+    \p2=(current bounding box.north east)
+  in
+  node[inner sep=0pt,outer sep=0pt,minimum size=0pt,line width=0pt,text width=0pt,text height=0pt,draw=white] at (current bounding box) {
+\immediate\write\metadatafile{\p1,\p2}
+};
+\immediate\closeout\metadatafile
+\end{tikzpicture}
+
+\end{document}
+kzpicture}
+
+\end{document}
+
+ocument}
+
+ment}
+t}

### 2020-10-05 main.tex
Finished Results section - updated pictures a little bit - renamed section to simulation and results - included sensor variance and encoding details and justifications - moved timing discussion to after the accuracy discussions

@@
 and conclude with the following assumption.
-\begin{assum}
+\begin{assum} \label{assum:measurement_size}
     Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
@@
 
-\section{Results} \label{sec:results}
+\section{Simulation and Results} \label{sec:sim_and_results}
 To demonstrate our proposed approach, we have implemented the algorithm in Section \ref{subsec:algorithm} and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.
 
-Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to support simultaneous computations by sensors and navigator via different processes.
+Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to support simultaneous computations by sensors and navigator as different processes.
 The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme.
@@
 
-Figure \ref{fig:sim_timing} shows
-
+Recalling Assumption \ref{assum:measurement_size}, modified measurement noise resembles a Gaussian distribution when measurements are sufficiently large.
+We considered $4$ layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
+The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
+\begin{figure}[htbp]
+\begin{center}
+    \includegraphics{images/layouts.pdf}
+\end{center}
+\caption{Layouts Normal Big}
+\label{fig:sim_layouts}
+\end{figure}
+To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurment variances $r_i=5$ metres.
+Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
+The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
+\begin{figure}[htbp]
+\begin{center}
+    \includegraphics{images/layout_errors.pdf}
+\end{center}
+\caption{Layout errors}
+\label{fig:sim_layout_errors}
+\end{figure}
+From the results it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when comparied to a normal EIF filter.
+The robustness of the privacy-preserving method is likely due to the rationality of Assumption \ref{assum:measurement_size}, the relative size of measurements to the sensor variances in our simulations, and the sufficiently large fractional precision.
+
+In addition to accuracy, computational requirements are an important factor in the adoption of novel cryptographic methods.
+Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.} bit lengths of $N$) and the number of sensors are varied.
+Every plotted time is again the average of $100$ simulations, each running for $50$ filter iterations.
 \begin{figure}[htbp]
@@
 \end{figure}
-
- \begin{figure}[htbp]
-    \begin{center}
-       \includegraphics{images/layout_errors.pdf}
-    \end{center}
-    \caption{Layout errors}
-    \label{fig:sim_layout_errors}
- \end{figure}
-
- \begin{figure}[htbp]
-    \begin{center}
-       \includegraphics{images/layouts.pdf}
-    \end{center}
-    \caption{Layouts Normal Big}
-    \label{fig:sim_layouts}
- \end{figure}
-
-% Time results can be captured in one graph.
-Y-axis is time, X-axis is the number of sensors, each line (different colour) will show how the runtime changes as sensors are increased for different Paillier bit-sizes (at least 3: 512, 1024, 2048).
-Every data point should be the average over some X number of simulations.
-
-% Accuracy plots will describe error due to encoding and the average distance of the sensors to the navigator.
-All plots will use the same ground truth and initial state and covariance estimates (this way average error at each timestep from multiple runs makes sense):
-
-% Plot 1 will plot the RMSE of the average of X runs at each encoding size. A fixed layout of 4 mediumly spaced sensor will be used, and a fixed Paillier bit size.
-
-% Plot 2 will plot the RMSE as the average distance of sensors changes.
-Fixed encoding and Paillier bit size.
-Vary between 4 layouts where 4 sensors are either very close to the centre (and ground truth, and progressively further out)
-
-% Plot 3 will accompany plot 3 and display the 4 layouts (arrow for ground truth and points for the sensors).
-
-% Discuss the meaning of the small changes in accuracy, and runtimes when using the same encryption size, that is, point out it is a generally robust method.
+As sensor and navigator computations run in parallel, increases in runtime from additional sensors are primarily due to the longer aggregation operation at the navigator.
+The predominant computational cost is dependant on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme.
+The current recommendation for a secure implementation of the Paillier encryption scheme is to use $1024$ bit-long keys.
 

### 2020-10-05 main.tex
Added conclusion Removed template commented out code at the bottom

@@
 \section{Conclusion} \label{sec:conclusion}
-Possible future work to consider: Hardware implementations, measurement handling which preservers Gaussian noise, or non-Gaussian noise methods, ways of sending less information form the navigator to the sensors at each time step, active sensor attacker model, different state encryptions received at sensors or a way to confirm they are the same.
-
-%---Rest is template---
-
-% \section{Introduction}
-% Video, patres conscripti, in me omnium vestrum ora atque oculos esse 
-% conversos, video vos non solunn de vestro ac rei publicae, verum 
-% etiam, si id depulsum sit, de meo periculo esse sollicitos. Est mihi 
-% iucunda in malis et grata in dolore vestra erga me voluntas, sed eam, 
-% per deos inmortales, deponite atque obliti salutis meae de vobis ac 
-% de vestris liberis cogitate. Mihi si haec condicio consulatus data 
-% est, ut omnis acerbitates, onunis dolores cruciatusque perferrem, 
-% feram non solum fortiter, verum etiam lubenter, dum modo meis 
-% laboribus vobis populoque Romano dignitas salusque pariatur.
-
-% \begin{figure}
-% \begin{center}
-% \includegraphics[height=4cm]{jcaesar.eps}    % The printed column  
-% \caption{Gaius Julius Caesar, 100--44 B.C.}  % width is 8.4 cm.
-% \label{fig1}                                 % Size the figures 
-% \end{center}                                 % accordingly.
-% \end{figure}
-
-% % OR
-
-% %\begin{figure}
-% %\begin{center}
-% %\epsfig{file=jcaesar,width=7cm}
-% %\caption{Gaius Julius Caesar, 100--44 B.C.}
-% %\label{fig1}
-% %\end{center}
-% %\end{figure}
-
-% \subsection{A subsection}
-% Marcus Tullius Cicero, 106--43 B.C. was a Roman statesman, orator, 
-% and philosopher.  A major figure in the last years of the Republic, 
-% he is best known for his orations against Catiline\footnote{
-% This footnote should be very brief.}
-% and for his mastery of Latin prose \cite{Heritage:92}. He was a 
-% contemporary of Julius Caesar (Fig.~\ref{fig1}).
-
-% \section{The argument}
-% Some words might be appropriate describing equation~(\ref{e1}), if 
-% we had but time and space enough.
-% \begin{equation} \label{e1}
-% {{\partial F}\over {\partial t}} =
-% D{{\partial^2 F}\over {\partial x^2}}.
-% \end{equation}
-% See \cite{Abl:56}, \cite{AbTaRu:54}, \cite{Keo:58} and 
-% \cite{Pow:85}.
-% This equation goes far beyond the celebrated theorem ascribed to the great
-% Pythagoras by his followers.
-% \begin{thm}
-% The square of the length of the hypotenuse of a right triangle equals the sum of the squares 
-% of the lengths of the other two sides.
-% \end{thm}
-% \section{Epilogue}
-% A word or two to conclude, and this even includes some inline 
-% maths:  $R(x,t)\sim t^{-\beta}g(x/t^\alpha)\exp(-|x|/t^\alpha)$.
+To develop a model-based localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Joye-Libert aggregation scheme.
+This scheme was then used in our proposed private EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
+Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearlity requirements can be applied.
+Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.
 
@@
 \bibliography{BibTeX/PrivateEIFLocalisation}
-
-%\begin{thebibliography}{99}     % Otherwise use the  
-                                 % thebibliography environment.
-                                 % Insert the full references here.
-                                 % See a recent issue of Automatica 
-                                 % for the style.
-%  \bibitem[Heritage, 1992]{Heritage:92}
-%     (1992) {\it The American Heritage. 
-%     Dictionary of the American Language.}
-%     Houghton Mifflin Company.
-%  \bibitem[Able, 1956]{Abl:56}
-%     B.~C.~Able (1956). Nucleic acid content of macroscope. 
-%     {\it Nature 2}, 7--9. 
-%  \bibitem[Able {\em et al.}, 1954]{AbTaRu:54}   
-%     B.~C. Able, R.~A. Tagg, and M.~Rush (1954).
-%     Enzyme-catalyzed cellular transanimations.
-%     In A.~F.~Round, editor, 
-%     {\it Advances in Enzymology Vol. 2} (125--247). 
-%     New York, Academic Press.
-%  \bibitem[R.~Keohane, 1958]{Keo:58}
-%     R.~Keohane (1958).
-%     {\it Power and Interdependence: 
-%     World Politics in Transition.}
-%     Boston, Little, Brown \& Co.
-%  \bibitem[Powers, 1985]{Pow:85}
-%     T.~Powers (1985).
-%     Is there a way out?
-%     {\it Harpers, June 1985}, 35--47.
-
-%\end{thebibliography}
 

### 2020-10-05 main.tex
Added reference for the recommended keysize for our scheme

@@
 The predominant computational cost is dependant on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme.
-The current recommendation for a secure implementation of the Paillier encryption scheme is to use $1024$ bit-long keys.
+The current recommendation for a secure implementation relying on prime factorisation (difficulty of factorising $N$) is to use $2048$ bit-long keys \cite{barkerRecommendationPairwiseKey2019}.
 

### 2020-10-05 main.tex
Couple of typos (Grammarly plugin ran finally)

@@
 \end{figure}
-To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurment variances $r_i=5$ metres.
+To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurement variances $r_i=5$ metres.
 Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
@@
 \end{figure}
-From the results it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when comparied to a normal EIF filter.
+From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when compared to a normal EIF filter.
 The robustness of the privacy-preserving method is likely due to the rationality of Assumption \ref{assum:measurement_size}, the relative size of measurements to the sensor variances in our simulations, and the sufficiently large fractional precision.
@@
 This scheme was then used in our proposed private EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
-Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearlity requirements can be applied.
+Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
 Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.

### 2020-10-06 main.tex
Horrible tedious start to introduction

@@
 \section{Introduction}
-
---
-
-Introduce localisation, filtering and the need for privacy.
-
-Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs
-
-Methods for introducing security and privacy include differential privacy methods and encryption methods.
-
-Differential privacy involves using statistical noise as security to make individual users' information cannot be deduced.
+Localisation methods in distributed sensor environments have long been an active topic of research [].
+Ongoing advancements in portable computing power and sensor capabilities have led to various forms of distributed sensor localisation methods being actively researched [], of which range-based localisation methods have found a particularly large application.
+Signal strength measurements, radar measurements, GPS and multilateration are among the use-cases where distance measurements or estimates are used to produce location estimates of an involved party.
+Typically, localisation in this setting is computed by first gathering sensor details such as measurement noise, geographical location and observations centrally, before calculating a location estimate based on this information and making it available to the interested parties [].
+
+Such centrally computed algorithms, therefore, require sharing sensor or navigator information to other parties involved in the algorithm.
+
+with the advancements in cloud and ubiquitous computing, possible use-cases
+
+such as airspace localisation in the presence of private sensors or autonomous vehicle estimation without disclosing underlying hardware or methods,
+
+have made the requirements of information security and user privacy more apparent than before [14,15]
+
+For example, consider aircraft localisation in the presence of privately operated radar stations, where measurements and locations of stations may wish to be kept private from vehicles
+
+The requirement of sensing sensor or navigator information within a network 
+Centrally computing localisation algorithms typically require information that could be considered sensitive to either sensors (or those to whom they belong) or navigators be sent to
+
+Methods which have been used to handle these requirements, often by solving the problem of secure data aggregation can be grouped into two broad catagories.
+
+Differential privacy and Indistinguishable encryption.
+
+These new requirements for distributed signal processing have led to new definitions of security and methods which satisfy them, such as formalised encryption schemes [], differential privacy [] and homomorphic encryption []
+
+Differential privacy [] involves using statistical noise as security to make individual users' information cannot be deduced.
 Often requires a trusted aggregator, although secure aggregation methods exist.
@@
 
-Encryption schemes involve formal indistinguishability proofs typically over bits or integers.
+% --
+
+% Introduce localisation, filtering and the need for privacy.
+
+% Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs
+
+% Methods for introducing security and privacy include differential privacy methods and encryption methods.
+
+% Differential privacy involves using statistical noise as security to make individual users' information cannot be deduced.
+Often requires a trusted aggregator, although secure aggregation methods exist.
+always requires noising result such that the outcome is not exact (a problem in localisation).
+
+% Encryption schemes involve formal indistinguishability proofs typically over bits or integers.
 They rely on computationally hard problems involving security parameters of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
@@
 
-Advancements in function providing encryption schemes such as homomorphic encryption have also led to several other types of schemes which have found uses in signal processing.
+% Advancements in function providing encryption schemes such as homomorphic encryption have also led to several other types of schemes which have found uses in signal processing.
 Private aggregation schemes allow the secure computation of the sum of encrypted values originating from different parties, leaking only the final result.
@@
 
-Another example of function providing encryption, and a generalisation of private aggregation, is called functional encryption (FE) and its distributed extension, multi-client functional encryption (MCFE), which allow the unencrypted result of an arbitrary function to be computed from encrypted inputs.
+% Another example of function providing encryption, and a generalisation of private aggregation, is called functional encryption (FE) and its distributed extension, multi-client functional encryption (MCFE), which allow the unencrypted result of an arbitrary function to be computed from encrypted inputs.
 General FE and MCFE are known to be quite computationally expensive (from meeting with ITI and student Johannes - need ref.) but alternatives providing only a subset of possibly computable function exist; for example, inner product encryption.
 
-Several of the aforementioned encryption schemes have found uses in secure localisation, estimation, and control.
+% Several of the aforementioned encryption schemes have found uses in secure localisation, estimation, and control.
 
@@
 
---
-
 %Section Summary
-% \ref{sec:problem_statement}
-% \ref{sec:crypto_prelim}
-% \ref{sec:lcao_definition}
-% \ref{sec:our_scheme}
-% \ref{sec:loc_prelim}
-% \ref{sec:private_localisation}
-% \ref{sec:results}
-% \ref{sec:conclusion}
 In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
@@
 Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
-In Section \ref{sec:results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
+In Section \ref{sec:sim_and_results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
 
@@
 \section{Problem Statement} \label{sec:problem_statement}
-% Restate the scenario but more formally. Give a concrete example - plane and signal towers.
-
-% Exact security guarantees we aim for, as well as the definitions for these guarantees (pWSAO and indistinguishability but in context of localisation as well).
-Note that learning only the sum in aggregation (as is normal in AO) would, in this case, tell the navigator the average location and measurements of all sensors, which is fine as it does not disclose any exact sensor.
-
-% Passive attacks only from sensors to learn navigator position (Otherwise one could do some kind of attack that would send a fake measurement and note the change in its own measurements - possible this would give away the average of other sensors' measurements but unclear).
-Any largely incorrect inputs from sensors may also be detectable by comparison to alternative navigator onboard sensors (GPS etc.).
-Justify by saying sensors need to behave for localisation to work in the first place.
-
-% Active attacks from navigator to find sensor location allowed, but assume that weights sent to all sensors are the same.
-In a wireless setting, all sensors would receive all broadcast weights anyway.
-While special hardware, which may support directional broadcasting or receiving, could be used to locate sensors individually this is beyond the scope of what is considered in our problem.
-
-% Point out that learning the aggregation of sensor outputs, which contains measurement and location information also means that the average location and measurement of the sensors may be leaked, and is accepted as a part of the leakage as it is inferrable from the aggregation scheme and any functioning model-based localisation where measurements are not known
-
-% Rough computational capabilities expected by parties
-
-% Fixed sensor subsets of which only whole subsets can be used at once.
-Maybe a picture of what this might look like in a high level distributed localisation diagram.
-Should consider that this sub-grouping would also mean the leakage of the average sensor/measurement of each subset not all sensors at once.
-This should be considered when choosing sensor subsets and locations.
-
 The localisation scenario we consider in this work is that of model-based self-navigation using range-only sensors.

### 2020-10-07 main.tex
Intro going well, almost done - still missing all references, just added [] and sometimes [<comments>] where they're needed - still want to add quick description of MCFE

@@
 Localisation methods in distributed sensor environments have long been an active topic of research [].
-Ongoing advancements in portable computing power and sensor capabilities have led to various forms of distributed sensor localisation methods being actively researched [], of which range-based localisation methods have found a particularly large application.
-Signal strength measurements, radar measurements, GPS and multilateration are among the use-cases where distance measurements or estimates are used to produce location estimates of an involved party.
-Typically, localisation in this setting is computed by first gathering sensor details such as measurement noise, geographical location and observations centrally, before calculating a location estimate based on this information and making it available to the interested parties [].
-
-Such centrally computed algorithms, therefore, require sharing sensor or navigator information to other parties involved in the algorithm.
-
-with the advancements in cloud and ubiquitous computing, possible use-cases
-
-such as airspace localisation in the presence of private sensors or autonomous vehicle estimation without disclosing underlying hardware or methods,
-
-have made the requirements of information security and user privacy more apparent than before [14,15]
-
-For example, consider aircraft localisation in the presence of privately operated radar stations, where measurements and locations of stations may wish to be kept private from vehicles
-
-The requirement of sensing sensor or navigator information within a network 
-Centrally computing localisation algorithms typically require information that could be considered sensitive to either sensors (or those to whom they belong) or navigators be sent to
-
-Methods which have been used to handle these requirements, often by solving the problem of secure data aggregation can be grouped into two broad catagories.
-
-Differential privacy and Indistinguishable encryption.
-
-These new requirements for distributed signal processing have led to new definitions of security and methods which satisfy them, such as formalised encryption schemes [], differential privacy [] and homomorphic encryption []
-
-Differential privacy [] involves using statistical noise as security to make individual users' information cannot be deduced.
-Often requires a trusted aggregator, although secure aggregation methods exist.
-always requires noising result such that the outcome is not exact (a problem in localisation).
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements [], echo-based range estimates [] and magnetic field measurements [] to the TDOA and TOA pseudorange multilateration methods [].
+Range-based localisation methods, including the use of radar measurments, GPS clocks and signal strength measurmeents, have found particularly large application due to their robustness and accuracy [].
+These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally [].
+Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicous gain.
+With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made these requirements of information security and user privacy more apparent than before [14,15].
+For example, a scenario of aircraft localisation in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
+Alternatively, autonomous vehicle state estimation may benefit from neighbouring vehicles' information while no participant wishes to share information about their hardware.
+In addition, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
+All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
+
+Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
+(For example, computing the mean value of sensor meausurements.) The most common methods for ensuring privacy during aggregation have been described below.
+\begin{description}
+    \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation [].
+In the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs [norm,phe ones].
+Although differential privacy has strong computational benefits due to its implementational simplicity, it provides relatively weak security guarantees for multi-party networks, with no guarantees in the presence of multiple colluding corrupted parties.
+In addition, noisy aggregation results hinder it use in scenarios where high precision is a desired property such as aircraft localisation.
+    \item[Aggregator Oblivious Encryption] This method of encryption formalises the privacy of \textit{all} aggregation data from honest parties [].
+Encryptions of aggregation data are proven to be computationally indistingishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
+The originally proposed method [] is restiricted to a small input domain which has been expandad and computationally simplified in later works [joye-lib,student-one].
+The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicabilty to simple processing tasks such as smart-meter mean calculation [].
+\end{description}
+In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
+These methods have been broadly grouped into two domains and described below
+\begin{description}
+    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results [].
+Although theoretically ideal for many privacy-preserving tasks, current implementations are still computationally impractical for real-time or large scale tasks [].
+    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes, these schemes provide only a subset, typically one, of algebraic operations on encrypted data [].
+The reduced computational requirements and implementation simplicty have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multilpication [], set intersection computation [] and control input aggregation [].
+However, these works are relatively restricted in application due to the limited operations provided.
+\end{description}
+
+% TODO Never talked about FE and it's distributed extensio MCFE. General solutions still too computationally infeasible, while very specific functions do exists - dot product
+% "several novel methods for privacy preserving computations ...
+% which have as of yet found little application in estimation and localisation tasks
+
+Several of the aforementioned encryption schemes have found uses in privacy-preserving localisation, estimation, and control.
 
@@
 
+% TODO add overview section here - leads into crypto
+% can use the first part of the current crypto problem in here - then go straight into the scheme there
+
 % 

### 2020-10-08 main.tex
First draft for whole introduction and literature review is there - rearranged a bit, section summary and notation now come before lit review - lit review is its own section

@@
 Localisation methods in distributed sensor environments have long been an active topic of research [].
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements [], echo-based range estimates [] and magnetic field measurements [] to the TDOA and TOA pseudorange multilateration methods [].
-Range-based localisation methods, including the use of radar measurments, GPS clocks and signal strength measurmeents, have found particularly large application due to their robustness and accuracy [].
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements [], echo-based range estimates [] and magnetic field measurements [] to the TDOA and TOA pseudo-range multilateration methods [].
+Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy [].
 These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally [].
-Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicous gain.
+Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain.
 With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made these requirements of information security and user privacy more apparent than before [14,15].
@@
 Alternatively, autonomous vehicle state estimation may benefit from neighbouring vehicles' information while no participant wishes to share information about their hardware.
-In addition, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
+Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
 All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
-
-Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
-(For example, computing the mean value of sensor meausurements.) The most common methods for ensuring privacy during aggregation have been described below.
+Our contributions in this work will be presented in two parts.
+We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localisation filter using this scheme such that sensor and navigator privacy is preserved.
+
+% TODO update the below
+In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
+Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it.
+Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
+In Section \ref{sec:sim_and_results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
+
+\subsection{Notation}
+Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list
+
+\section{Literature Overview}
+In this section we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.
+
+\subsection{Encryption Schemes in Signal Processing}
+Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data [].
+The most common methods for ensuring privacy during aggregation have been described below.
 \begin{description}
     \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation [].
-In the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs [norm,phe ones].
+In the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs [norm, PHE ones].
 Although differential privacy has strong computational benefits due to its implementational simplicity, it provides relatively weak security guarantees for multi-party networks, with no guarantees in the presence of multiple colluding corrupted parties.
-In addition, noisy aggregation results hinder it use in scenarios where high precision is a desired property such as aircraft localisation.
+Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localisation.
     \item[Aggregator Oblivious Encryption] This method of encryption formalises the privacy of \textit{all} aggregation data from honest parties [].
-Encryptions of aggregation data are proven to be computationally indistingishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
-The originally proposed method [] is restiricted to a small input domain which has been expandad and computationally simplified in later works [joye-lib,student-one].
-The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicabilty to simple processing tasks such as smart-meter mean calculation [].
+Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
+The originally proposed method [] is restricted to a small input domain which has been expanded and computationally simplified in later works [joye-lib,student-one].
+The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter mean calculation [].
 \end{description}
 In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
-These methods have been broadly grouped into two domains and described below
+These methods have been broadly grouped into two domains and described below.
 \begin{description}
@@
     \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes, these schemes provide only a subset, typically one, of algebraic operations on encrypted data [].
-The reduced computational requirements and implementation simplicty have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multilpication [], set intersection computation [] and control input aggregation [].
+The reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication [], set intersection computation [] and control input aggregation [].
 However, these works are relatively restricted in application due to the limited operations provided.
 \end{description}
-
-% TODO Never talked about FE and it's distributed extensio MCFE. General solutions still too computationally infeasible, while very specific functions do exists - dot product
-% "several novel methods for privacy preserving computations ...
-% which have as of yet found little application in estimation and localisation tasks
-
-Several of the aforementioned encryption schemes have found uses in privacy-preserving localisation, estimation, and control.
-
-% --
-
-% Introduce localisation, filtering and the need for privacy.
-
-% Examples of environments where privacy is relevant and concrete examples where lack of privacy could have large costs
-
-% Methods for introducing security and privacy include differential privacy methods and encryption methods.
-
-% Differential privacy involves using statistical noise as security to make individual users' information cannot be deduced.
-Often requires a trusted aggregator, although secure aggregation methods exist.
-always requires noising result such that the outcome is not exact (a problem in localisation).
-
-% Encryption schemes involve formal indistinguishability proofs typically over bits or integers.
-They rely on computationally hard problems involving security parameters of a sufficiently large size; therefore the additional computational requirements of using encryption schemes should be pointed out and what this means in a real-time distributed sensor system.
-Continuing, explain public-key cryptography applicability to distributed systems; difference to symmetric schemes.
-Homomorphic encryption power and use case.
-Why FHE isn't used often, why additive partially homomorphic encryption is.
-
-% Advancements in function providing encryption schemes such as homomorphic encryption have also led to several other types of schemes which have found uses in signal processing.
-Private aggregation schemes allow the secure computation of the sum of encrypted values originating from different parties, leaking only the final result.
-When considering such multi-party encryption protocols, formal security definitions must now also incorporate the added dangers of colluding malicious parties, and lead to new notions of security.
-For example Aggregator Obliviousness (AO) is typically proven for private aggregation schemes, while alternatives such as Private Weighted Secure Aggregator Obliviousness (pWSAO) exist for other specific use-cases.
-
-% Another example of function providing encryption, and a generalisation of private aggregation, is called functional encryption (FE) and its distributed extension, multi-client functional encryption (MCFE), which allow the unencrypted result of an arbitrary function to be computed from encrypted inputs.
-General FE and MCFE are known to be quite computationally expensive (from meeting with ITI and student Johannes - need ref.) but alternatives providing only a subset of possibly computable function exist; for example, inner product encryption.
-
-% Several of the aforementioned encryption schemes have found uses in secure localisation, estimation, and control.
-
-% 
-% ##       #### ######## 
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ##        ##     ##    
-% ######## ####    ##    
-%
-
-\subsection{Relevant Literature on Encrypted Localisation and Estimation}
-
-Model-free localisation using homomorphic encryption examples include polygon thing, WSN examples which protect against adversaries but in the case of the WSN paper.
-don't preserve anchor privacy.
-Importantly, model-based filtering and localisation provide more accurate estimates and these are not applicable there.
-
-Model-based estimation examples include Aristov paper (which requires a linear model, and a hierarchy of sensors), Farokhi paper (which requires the controller compute entirely in encrypted space and send input back to actuator - supporting only the cloud-as-a-service type architectures) and Alexandru paper (which implements a distributed control environment but requires a constant gain matrix K)
-
-pWSAO achieved in Alexandru weighted aggregation, but requires redistributing keys at every timestep resulting in a costly operation, and a complicated communication protocol.
-
-In addition to applying suitable encryption schemes to signal processing tasks, care must be taken when converting sensor output into an encryptable homomorphic format.
-As is the case with our proposed localisation method, real number sensor output does not trivially encode to integers such that the homomorphic properties provided by an additive encryption scheme over integers keep the underlying real numbers consistent.
-Methods for handling the encoding of real numbers such that they can be used in homomorphic encryption exist.
-Google bignum adds power but risks overflow and leaks exponents, Farokhi leaks no information but allows only a single multiplication (extendable to more but each further multiplication limits the real number size and increases the risk of overflow).
-
-Briefly describe navigator scenario and our contributions
-
-%Section Summary
-In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
-Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it.
-Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
-In Section \ref{sec:sim_and_results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
-
-% 
-% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
-% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
-% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
-% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
-% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
-% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
-% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
-%
-
-\subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list
+Lastly, recent developments in encryption schemes have provided some novel methods also suitable for privacy-preserving computation in distributed environments.
+\begin{description}
+    \item[Multi-Client Function Encryption] This type of encryption allows the computing of a specific function given encrypted inputs [].
+It is suitable for privacy-preserving distributed data as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
+While such schemes that can compute arbitrary functions are still too computationally expensive for practical use [], partial schemes supporting only some functions, such as computing vector dot products [], exist, but have yet to find applications in more complicated signal processing tasks.
+\end{description}
+Of the aforementioned encryption schemes, some have found uses in privacy-preserving localisation and estimation tasks and we summarise these in the next section.
+
+\subsection{Encrypted Localisation and Estimation}
+Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors [].
+We aim to provide an accurate localisation filter in the presence of range-only sensors.
+
+Relevant estimation methods include both model-based Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter [], and model-free methods where location estimates are made independently of each other [proloc,serloc].
+The work in [proloc] uses partially homomorphic encryption to compute model-free location estimates while preserving the privacy of sensor measurements and locations.
+The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols.
+Neither method considers measurement uncertainty, and no estimate errors are provided.
+
+Model-based approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
+In [aristov], partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator.
+While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.
+Model-based encrypted control [farohki summary] also introduces some privacy-preserving methods relevant to estimation.
+[alexandru] proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires repeated key distribution among all involved parties.
+In [farohki], a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures.
+
+While we primarily focus on applying encryption schemes to localisation algorithms, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
+As is the case with localisation sensors, real number measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
+The Google BigNum library [google bignum] provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
+It, however, leaks the exponent information of encrypted numbers.
+In [farohki], a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
 

### 2020-10-08 main.tex
Section restructure and start on problem decomposition section - section not confirmed complete, might add top level section too all crypto and all localisation stuff later - problem decomposition is being added to the Problem formulation section and will include the graphic originally at the start of the crypto section. It will explain how aggregation will be the basis of the security of the scheme and justify the cryptography section that follow

@@
 
+% 
+%        d8888 888888b.    .d8888b. 88888888888 8888888b.         d8888  .d8888b. 88888888888 
+%       d88888 888  "88b  d88P  Y88b    888     888   Y88b       d88888 d88P  Y88b    888     
+%      d88P888 888  .88P  Y88b.         888     888    888      d88P888 888    888    888     
+%     d88P 888 8888888K.   "Y888b.      888     888   d88P     d88P 888 888           888     
+%    d88P  888 888  "Y88b     "Y88b.    888     8888888P"     d88P  888 888           888     
+%   d88P   888 888    888       "888    888     888 T88b     d88P   888 888    888    888     
+%  d8888888888 888   d88P Y88b  d88P    888     888  T88b   d8888888888 Y88b  d88P    888     
+% d88P     888 8888888P"   "Y8888P"     888     888   T88b d88P     888  "Y8888P"     888     
+%                                                                                             
+%                                                                                             
+%                                                                                             
+%
+
 % Abstract of not more than 200 words.
@@
 % 
-% 8888888          888                    
-%   888            888                    
-%   888            888                    
-%   888   88888b.  888888 888d888 .d88b.  
-%   888   888 "88b 888    888P"  d88""88b 
-%   888   888  888 888    888    888  888 
-%   888   888  888 Y88b.  888    Y88..88P 
-% 8888888 888  888  "Y888 888     "Y88P"  
+% 8888888 888b    888 88888888888 8888888b.   .d88888b.  
+%   888   8888b   888     888     888   Y88b d88P" "Y88b 
+%   888   88888b  888     888     888    888 888     888 
+%   888   888Y88b 888     888     888   d88P 888     888 
+%   888   888 Y88b888     888     8888888P"  888     888 
+%   888   888  Y88888     888     888 T88b   888     888 
+%   888   888   Y8888     888     888  T88b  Y88b. .d88P 
+% 8888888 888    Y888     888     888   T88b  "Y88888P"  
 %                                                        
@@
 
+% 
+% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
+% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
+% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
+% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
+% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
+% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
+% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
+%
+
 \subsection{Notation}
@@
 
+% 
+% 888      8888888 88888888888 
+% 888        888       888     
+% 888        888       888     
+% 888        888       888     
+% 888        888       888     
+% 888        888       888     
+% 888        888       888     
+% 88888888 8888888     888     
+%                              
+%                              
+%                              
+%
+
 \section{Literature Overview}
 In this section we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.
+
+% 
+% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
+% ##       ###   ## ##    ##    ##    ## ##    ## ##     ## ##       ###   ### ##       ##    ## 
+% ##       ####  ## ##          ##       ##       ##     ## ##       #### #### ##       ##       
+% ######   ## ## ## ##           ######  ##       ######### ######   ## ### ## ######    ######  
+% ##       ##  #### ##                ## ##       ##     ## ##       ##     ## ##             ## 
+% ##       ##   ### ##    ##    ##    ## ##    ## ##     ## ##       ##     ## ##       ##    ## 
+% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
+%
 
@@
 
+% 
+% ######## ##    ##  ######     ##        #######   ######  
+% ##       ###   ## ##    ##    ##       ##     ## ##    ## 
+% ##       ####  ## ##          ##       ##     ## ##       
+% ######   ## ## ## ##          ##       ##     ## ##       
+% ##       ##  #### ##          ##       ##     ## ##       
+% ##       ##   ### ##    ##    ##       ##     ## ##    ## 
+% ######## ##    ##  ######     ########  #######   ######  
+%
+
 \subsection{Encrypted Localisation and Estimation}
@@
 % 
-% 8888888b.                  888      
-% 888   Y88b                 888      
-% 888    888                 888      
-% 888   d88P 888d888 .d88b.  88888b.  
-% 8888888P"  888P"  d88""88b 888 "88b 
-% 888        888    888  888 888  888 
-% 888        888    Y88..88P 888 d88P 
-% 888        888     "Y88P"  88888P"  
+% 8888888b.  8888888b.   .d88888b.  888888b.   888      8888888888 888b     d888 
+% 888   Y88b 888   Y88b d88P" "Y88b 888  "88b  888      888        8888b   d8888 
+% 888    888 888    888 888     888 888  .88P  888      888        88888b.d88888 
+% 888   d88P 888   d88P 888     888 8888888K.  888      8888888    888Y88888P888 
+% 8888888P"  8888888P"  888     888 888  "Y88b 888      888        888 Y888P 888 
+% 888        888 T88b   888     888 888    888 888      888        888  Y8P  888 
+% 888        888  T88b  Y88b. .d88P 888   d88P 888      888        888   "   888 
+% 888        888   T88b  "Y88888P"  8888888P"  88888888 8888888888 888       888 
 %                                                                                
@@
 We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $\rv{z}_k$ at any time $k$.
-
 We motivate these goals with an example.
@@
 However, the additional safety to passengers, provided by accurate aircraft localisation, may be a goal of all those involved.
+
+% 
+% ########  ########  ######   #######  ##     ## ########  
+% ##     ## ##       ##    ## ##     ## ###   ### ##     ## 
+% ##     ## ##       ##       ##     ## #### #### ##     ## 
+% ##     ## ######   ##       ##     ## ## ### ## ########  
+% ##     ## ##       ##       ##     ## ##     ## ##        
+% ##     ## ##       ##    ## ##     ## ##     ## ##        
+% ########  ########  ######   #######  ##     ## ##        
+%
+
+\subsection{Problem Decomposition}
+The recursive nature of the problem definition above complicated the definition and proof of security requirements.
+
+We will instead decompose the communication part of the problem into a form of aggregation, which we can reason and prove more easily.
+
+Due to the non-linearity of the measurement model \eqref{eqn:measurement_model}, we will use a linearisation
+
+This type of linearisation will depend on the current state estimate and therefore requires communication between measurement producers and state estimators, in our case communication between the sensors and navigator
+
+The basic idea of our aggregation decomposition is to formulate the computing of model linearisation with the ability to compute weighted sums of state-related information at sensors, and again summing
+
+% note also the reason for not computing sums at the navigator (will require j sums to be sent rather than n)
+% Possible as a remarkat the end? "We note that y= ... = ... and argue the benefit of this method depends on j >> n reducing communication costs
 
@@
 
-% TODO add overview section here - leads into crypto
-% can use the first part of the current crypto problem in here - then go straight into the scheme there
-
-% 
-%  .d8888b.                            888                 8888888b.                  888 d8b               
-% d88P  Y88b                           888                 888   Y88b                 888 Y8P               
-% 888    888                           888                 888    888                 888                   
-% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
-% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
-% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888 
-% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888 
-%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888 
-%                         888 888                                                                           
-%                    Y8b d88P 888                                                                           
-%                     "Y88P"  888                                                                           
+% 
+% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.  8888888888 888      8888888 888b     d888 
+% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b 888        888        888   8888b   d8888 
+% 888        88888b  888 888    888      888    888 888    888 888        888        888   88888b.d88888 
+% 8888888    888Y88b 888 888             888   d88P 888   d88P 8888888    888        888   888Y88888P888 
+% 888        888 Y88b888 888             8888888P"  8888888P"  888        888        888   888 Y888P 888 
+% 888        888  Y88888 888    888      888        888 T88b   888        888        888   888  Y8P  888 
+% 888        888   Y8888 Y88b  d88P      888        888  T88b  888        888        888   888   "   888 
+% 8888888888 888    Y888  "Y8888P"       888        888   T88b 8888888888 88888888 8888888 888       888 
+%                                                                                                        
+%                                                                                                        
+%                                                                                                        
 %
@@
 % 
-%  .d8888b.                            888                 8888888b.                  888      
-% d88P  Y88b                           888                 888   Y88b                 888      
-% 888    888                           888                 888    888                 888      
-% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  88888b.  
-% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d88""88b 888 "88b 
-% 888    888 888     888  888 888  888 888   888  888      888        888    888  888 888  888 
-% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y88..88P 888 d88P 
-%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y88P"  88888P"  
-%                         888 888                                                              
-%                    Y8b d88P 888                                                              
-%                     "Y88P"  888                                                              
+% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.   .d88888b.  888888b.   
+% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b d88P" "Y88b 888  "88b  
+% 888        88888b  888 888    888      888    888 888    888 888     888 888  .88P  
+% 8888888    888Y88b 888 888             888   d88P 888   d88P 888     888 8888888K.  
+% 888        888 Y88b888 888             8888888P"  8888888P"  888     888 888  "Y88b 
+% 888        888  Y88888 888    888      888        888 T88b   888     888 888    888 
+% 888        888   Y8888 Y88b  d88P      888        888  T88b  Y88b. .d88P 888   d88P 
+% 8888888888 888    Y888  "Y8888P"       888        888   T88b  "Y88888P"  8888888P"  
+%                                                                                     
+%                                                                                     
+%                                                                                     
 %
@@
 % 
-%  .d88888b.                         .d8888b.           888                                      
-% d88P" "Y88b                       d88P  Y88b          888                                      
-% 888     888                       Y88b.               888                                      
-% 888     888 888  888 888d888       "Y888b.    .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.  
-% 888     888 888  888 888P"            "Y88b. d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b 
-% 888     888 888  888 888                "888 888      888  888 88888888 888  888  888 88888888 
-% Y88b. .d88P Y88b 888 888          Y88b  d88P Y88b.    888  888 Y8b.     888  888  888 Y8b.     
-%  "Y88888P"   "Y88888 888           "Y8888P"   "Y8888P 888  888  "Y8888  888  888  888  "Y8888  
-%                                                                                                
-%                                                                                                
-%                                                                                                
-%
-
-\section{Our Scheme} \label{sec:our_scheme}
+%  #######  ##     ## ########      ######   ######  ##     ## ######## ##     ## ######## 
+% ##     ## ##     ## ##     ##    ##    ## ##    ## ##     ## ##       ###   ### ##       
+% ##     ## ##     ## ##     ##    ##       ##       ##     ## ##       #### #### ##       
+% ##     ## ##     ## ########      ######  ##       ######### ######   ## ### ## ######   
+% ##     ## ##     ## ##   ##            ## ##       ##     ## ##       ##     ## ##       
+% ##     ## ##     ## ##    ##     ##    ## ##    ## ##     ## ##       ##     ## ##       
+%  #######   #######  ##     ##     ######   ######  ##     ## ######## ##     ## ######## 
+%
+
+\subsection{Our Scheme} \label{sec:our_scheme}
 Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
@@
 % 
-% 888                            8888888b.                  888 d8b               
-% 888                            888   Y88b                 888 Y8P               
-% 888                            888    888                 888                   
-% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
-% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
-% 888     888  888 888           888        888    88888888 888 888 888  888  888 
-% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888 
-% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888 
+% 888      .d88888b.   .d8888b.       8888888b.  8888888b.  8888888888 888      8888888 888b     d888 
+% 888     d88P" "Y88b d88P  Y88b      888   Y88b 888   Y88b 888        888        888   8888b   d8888 
+% 888     888     888 888    888      888    888 888    888 888        888        888   88888b.d88888 
+% 888     888     888 888             888   d88P 888   d88P 8888888    888        888   888Y88888P888 
+% 888     888     888 888             8888888P"  8888888P"  888        888        888   888 Y888P 888 
+% 888     888     888 888    888      888        888 T88b   888        888        888   888  Y8P  888 
+% 888     Y88b. .d88P Y88b  d88P      888        888  T88b  888        888        888   888   "   888 
+% 88888888 "Y88888P"   "Y8888P"       888        888   T88b 8888888888 88888888 8888888 888       888 
 %                                                                                                     
@@
 % 
-% 8888888b.          d8b               888                       
-% 888   Y88b         Y8P               888                       
-% 888    888                           888                       
-% 888   d88P 888d888 888 888  888      888      .d88b.   .d8888b 
-% 8888888P"  888P"   888 888  888      888     d88""88b d88P"    
-% 888        888     888 Y88  88P      888     888  888 888      
-% 888        888     888  Y8bd8P       888     Y88..88P Y88b.    
-% 888        888     888   Y88P        88888888 "Y88P"   "Y8888P 
+% 888      .d88888b.   .d8888b.  
+% 888     d88P" "Y88b d88P  Y88b 
+% 888     888     888 888    888 
+% 888     888     888 888        
+% 888     888     888 888        
+% 888     888     888 888    888 
+% 888     Y88b. .d88P Y88b  d88P 
+% 88888888 "Y88888P"   "Y8888P"  
 %                                
@@
 % 
-% 8888888b.                            888 888             
-% 888   Y88b                           888 888             
-% 888    888                           888 888             
-% 888   d88P .d88b.  .d8888b  888  888 888 888888 .d8888b  
-% 8888888P" d8P  Y8b 88K      888  888 888 888    88K      
-% 888 T88b  88888888 "Y8888b. 888  888 888 888    "Y8888b. 
-% 888  T88b Y8b.          X88 Y88b 888 888 Y88b.       X88 
-% 888   T88b "Y8888   88888P'  "Y88888 888  "Y888  88888P' 
+% 8888888b.  8888888888 .d8888b.  888     888 888    88888888888 .d8888b.  
+% 888   Y88b 888       d88P  Y88b 888     888 888        888    d88P  Y88b 
+% 888    888 888       Y88b.      888     888 888        888    Y88b.      
+% 888   d88P 8888888    "Y888b.   888     888 888        888     "Y888b.   
+% 8888888P"  888           "Y88b. 888     888 888        888        "Y88b. 
+% 888 T88b   888             "888 888     888 888        888          "888 
+% 888  T88b  888       Y88b  d88P Y88b. .d88P 888        888    Y88b  d88P 
+% 888   T88b 8888888888 "Y8888P"   "Y88888P"  88888888   888     "Y8888P"  
 %                                                                          
@@
 % 
-%  .d8888b.                             
-% d88P  Y88b                            
-% 888    888                            
-% 888         .d88b.  88888b.   .d8888b 
-% 888        d88""88b 888 "88b d88P"    
-% 888    888 888  888 888  888 888      
-% Y88b  d88P Y88..88P 888  888 Y88b.    
-%  "Y8888P"   "Y88P"  888  888  "Y8888P 
+%  .d8888b.   .d88888b.  888b    888  .d8888b.  
+% d88P  Y88b d88P" "Y88b 8888b   888 d88P  Y88b 
+% 888    888 888     888 88888b  888 888    888 
+% 888        888     888 888Y88b 888 888        
+% 888        888     888 888 Y88b888 888        
+% 888    888 888     888 888  Y88888 888    888 
+% Y88b  d88P Y88b. .d88P 888   Y8888 Y88b  d88P 
+%  "Y8888P"   "Y88888P"  888    Y888  "Y8888P"  
 %                                               
@@
 % 
-%        d8888                                          888 d8b          
-%       d88888                                          888 Y8P          
-%      d88P888                                          888              
-%     d88P 888 88888b.  88888b.   .d88b.  88888b.   .d88888 888 888  888 
-%    d88P  888 888 "88b 888 "88b d8P  Y8b 888 "88b d88" 888 888 `Y8bd8P' 
-%   d88P   888 888  888 888  888 88888888 888  888 888  888 888   X88K   
-%  d8888888888 888 d88P 888 d88P Y8b.     888  888 Y88b 888 888 .d8""8b. 
-% d88P     888 88888P"  88888P"   "Y8888  888  888  "Y88888 888 888  888 
-%              888      888                                              
-%              888      888                                              
-%              888      888                                              
+%        d8888 8888888b.  8888888b.  8888888888 888b    888 8888888b. 8888888 Y88b   d88P 
+%       d88888 888   Y88b 888   Y88b 888        8888b   888 888  "Y88b  888    Y88b d88P  
+%      d88P888 888    888 888    888 888        88888b  888 888    888  888     Y88o88P   
+%     d88P 888 888   d88P 888   d88P 8888888    888Y88b 888 888    888  888      Y888P    
+%    d88P  888 8888888P"  8888888P"  888        888 Y88b888 888    888  888      d888b    
+%   d88P   888 888        888        888        888  Y88888 888    888  888     d88888b   
+%  d8888888888 888        888        888        888   Y8888 888  .d88P  888    d88P Y88b  
+% d88P     888 888        888        8888888888 888    Y888 8888888P" 8888888 d88P   Y88b 
+%                                                                                         
+%                                                                                         
+%                                                                                         
 %

### 2020-10-09 main.tex
Finished problem decomposition section - updated the start of the crypto section to suit the now moved decomposition discussion Updated the section summary to correctly summarise the new sections Added the notation paragraph Updated all Tikz images to be narrower as it looks nicer - also updated all the tikzimage .tex's to include preamble code so they look the same when opened in TikzEdt

@@
 
-% TODO update the below
-In Section \ref{sec:problem_statement} we introduce the localisation problem and the restrictions on involved parties.
-Section \ref{sec:crypto_prelim} summarises cryptographic preliminaries and Sections \ref{sec:lcao_definition} and \ref{sec:our_scheme} introduce a novel security notion of linear-combination aggregation obliviousness and an encryption scheme which satisfies it.
-Section \ref{sec:loc_prelim} summarises localisation preliminaries, before we introduce our private localisation method in Section \ref{sec:private_localisation}, using the introduced encryption scheme.
-In Section \ref{sec:sim_and_results} we give and analyse simulation results, before concluding our work in Section \ref{sec:conclusion}.
+The remainder of the paper is structured as follows.
+In Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties.
+Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
+Sections \ref{sec:loc_prelim} and \ref{sec:private_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the secure aggregation scheme.
+We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.
 
@@
 \subsection{Notation}
-Notation. Reminder to include symbols for: rounding, concatenation, ``divides'', vector norm, expected value and variance, ordered list
+Throughout this work, we will use the following notation.
+Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$.
+Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
+$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal.
+$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively.
+Encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$, respectively.
+$\lfloor\cdot\rceil$ rounds to the nearest integer, $a | b$ stands for ``$a$ divides $b$'', and $a\|b$ for a bitwise concatenation of $a$ and $b$.
+Sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
 
@@
 \section{Literature Overview}
-In this section we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.
+In this section, we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.
 
@@
 
-\subsection{Problem Decomposition}
-The recursive nature of the problem definition above complicated the definition and proof of security requirements.
-
-We will instead decompose the communication part of the problem into a form of aggregation, which we can reason and prove more easily.
-
-Due to the non-linearity of the measurement model \eqref{eqn:measurement_model}, we will use a linearisation
-
-This type of linearisation will depend on the current state estimate and therefore requires communication between measurement producers and state estimators, in our case communication between the sensors and navigator
-
-The basic idea of our aggregation decomposition is to formulate the computing of model linearisation with the ability to compute weighted sums of state-related information at sensors, and again summing
-
-% note also the reason for not computing sums at the navigator (will require j sums to be sent rather than n)
-% Possible as a remarkat the end? "We note that y= ... = ... and argue the benefit of this method depends on j >> n reducing communication costs
+\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
+The recursive nature of the problem definition above complicates defining and proving of security requirements for the localisation scenario.
+As with existing estimation methods [] we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
+To support multiple aggregations at each time step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$.
+The bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
+That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
+This has been summarised in Figure \ref{fig:agg_steps}.
+\begin{figure}[htbp]
+\centering
+\vspace{\baselineskip}
+\begin{tikzpicture}[font=\footnotesize]
+    % Step 1
+    \node at (3.25,5.5) {1. Broadcast and combination step};
+    % Navigator
+    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
+    % Sensors
+    \node at (1.5,0.375) {Sensor $1$};
+    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
+    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
+    \node at (5,0.375) {Sensor $n$};
+    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
+    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
+    \fill [black] (3.5,1.125) circle (0.05);
+    \fill [black] (3,1.125) circle (0.05);
+    \fill [black] (3.25,1.125) circle (0.05);
+    % Lines
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
+    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
+    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
+    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
+    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
+
+    % Step 2
+    \node at (3.25,-0.75) {2. Aggregation step};
+    % Navigator
+    \fill [blue!40] (1.375,-3) rectangle (5.125,-1.25);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
+    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
+    % Sensors
+    \node at (1.25,-5.875) {Sensor $1$};
+    \fill  (5.25,-5.25) [red!40] ellipse (0.4 and 0.4);
+    \node at (5.25,-5.875) {Sensor $n$};
+    \fill  (1.25,-5.25) [red!40] ellipse (0.4 and 0.4);
+    \fill [black] (2.75,-5.25) circle (0.05);
+    \fill [black] (3.75,-5.25) circle (0.05);
+    \fill [black] (3.25,-5.25) circle (0.05);
+    % Lines
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
+    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
+    \node at (2,-4) {$y_1^{(t)}$};
+    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
+    \node at (4.625,-4) {$y_n^{(t)}$};
+
+    % Bounding rectangles
+    \draw [gray] (0,6) rectangle (6.5,0);
+    \draw [gray] (0,-0.25) rectangle (6.5,-6.25);
+\end{tikzpicture}
+\vspace{\baselineskip}
+\caption{Required linear-combination aggregation steps at instance $t$.}
+\label{fig:agg_steps}
+\end{figure}
+
+In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.
+
+\begin{rem}
+    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement is computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
+We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
+\end{rem}
 
@@
 \centering
-\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+\begin{tikzpicture}[font=\footnotesize]
     % Sizes
@@
     % Sensor locations (sensor 3 is shared)
-    \coordinate (s1) at (1.4086,-4.5869);
-    \coordinate (s2) at (4.0633,-5.9948);
-    \coordinate (s3) at (3.1235,-3.2054);
-    \coordinate (s4) at (4.5563,-1.6861);
-    \coordinate (s5) at (5.9909,-3.5635);
+    \coordinate (s1) at (0.8523,-4.1508) {};
+    \coordinate (s2) at (3.507,-5.5587) {};
+    \coordinate (s3) at (2.5,-2.75) {} {};
+    \coordinate (s4) at (4,-1.25) {};
+    \coordinate (s5) at (5.4346,-3.1274) {};
     % Navigator location
-    \coordinate (nav_loc) at (4,-4);
+    \coordinate (nav_loc) at (3.5,-3.25) {};
     % Bounding rectangle
     \coordinate (brect_start) at (0,0);
-    \coordinate (brect_end) at (8.0, -8.0);
+    \coordinate (brect_end) at (6.5, -6.5);
 
@@
 \section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
+When defining our aggregation security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
 
@@
 \section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
-For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation.
-In the context of navigation, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$.
-This has been summarized in Figure \ref{fig:agg_steps}.
-In Section \ref{sec:private_localisation} we will show how this protocol can be sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.
-
-\begin{figure}[htbp]
-\centering
-\vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.75]
-    % Step 1
-    \node at (5,22.5) {1. Broadcast and linear combinations step};
-    % Navigator
-    \node at (1.25,19.25) {Navigator};
-    \fill (1.25,18.25) [blue!40] ellipse (0.5 and 0.5);
-    % Sensors
-    \node at (7.5,21.75) {Sensor $1$};
-    \fill [red!40] (5.875,19.75) rectangle (9.5,21.25);
-    \node at (7.75,20.5) {$\displaystyle y_1^{(t)} = \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
-    \node at (7.5,14.75) {Sensor $n$};
-    \fill [red!40] (5.875,15.25) rectangle (9.5,16.75);
-    \node at (7.75,16) {$\displaystyle y_n^{(t)} = \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
-    \fill [black] (7.5,18.75) circle (0.05);
-    \fill [black] (7.5,17.75) circle (0.05);
-    \fill [black] (7.5,18.25) circle (0.05);
-    % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18.5) (5.75,20.25)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,18) (5.75,16.25)};
-    \node at (3.5,20.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
-    \node at (3.5,16.25) {$(\omega_1^{(t)},\dots ,\omega_m^{(t)})$};
-
-    % Step 2
-    \node at (5,13.25) {2. Aggregation step};
-    % Navigator
-    \node at (3.25,10.75) {Navigator};
-    \fill [blue!40] (0.5,8.75) rectangle (5.625,10.25);
-    \node at (3,9.5) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
-    % Sensors
-    \node at (8.75,12.5) {Sensor $1$};
-    \fill  (8.75,7.5) [red!40] ellipse (0.5 and 0.5);
-    \node at (8.75,6.5) {Sensor $n$};
-    \fill  (8.75,11.5) [red!40] ellipse (0.5 and 0.5);
-    \fill [black] (8.75,10) circle (0.05);
-    \fill [black] (8.75,9) circle (0.05);
-    \fill [black] (8.75,9.5) circle (0.05);
-    % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,11.25) (5.75,10)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(8.25,7.75) (5.75,9)};
-    \node at (6.75,11.5) {$y_1^{(t)}$};
-    \node at (6.75,7.5) {$y_n^{(t)}$};
-
-    % Bounding rectangles
-    \draw [gray] (0,23.25) rectangle (10,14.25);
-    \draw [gray] (0,14) rectangle (10,5.5);
-\end{tikzpicture}
-\vspace{\baselineskip}
-\caption{Required linear-combination aggregation steps at time $t$.}
-\label{fig:agg_steps}
-\end{figure}
-
-To perform the protocol from Figure \ref{fig:agg_steps} in a secure manner, we must first describe the security properties we aim to achieve.
-Broadly speaking, we want a cryptographic scheme which allows a time-series of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme.
+As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
+To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation.
+Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme.
 That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations.
@@
 \begin{description}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous timesteps, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous timesteps.
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
+    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
 Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
@@
 
-\subsection{Our Scheme} \label{sec:our_scheme}
+\subsection{Our Scheme} \label{subsec:our_scheme}
 Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+\begin{tikzpicture}[font=\footnotesize]
     % Bounding box
-    \draw [gray] (0,-0.25) rectangle (8,7.5);
+    \draw [gray] (0,0) rectangle (6.5,6.5);
 
     % Outer adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
+    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
     % Inner adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);
+    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);
 
     % Adversaries and challenger
-    \node at (4,3.5) {\LARGE$\mathcal{A}'$};
-    \node at (4,6) {\LARGE$\mathcal{A}$};
-    \node at (4,0.5) {\LARGE$\mathcal{C}$};
+    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
+    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
+    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};
 
@@
     \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
-    \draw [-latex] (2,4.5) --(2,5.5);
-
-    \node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
-    \draw [-latex] (6,5.5) -- (6,4.5);
-
-    \node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
-    \draw [-latex] (6,2.75) -- (6,1.75);
+    \draw [-latex] (2,4.5) --(2,5);
+
+    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
+    \draw [-latex] (4.5,5) -- (4.5,4.5);
+
+    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
+    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
 \end{tikzpicture}
@@
 
-    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{sec:our_scheme}.
+    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{subsec:our_scheme}.
 Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
@@
 \begin{equation}
-    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\mean{x}_k) + \mat{H}_{k,i}\mean{x}_k) \label{eqn:eif_info_vec_update}
+    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:eif_info_vec_update}
 \end{equation}
@@
 \section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
-Given our definitions for the aggregation scheme in Section \ref{sec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}.
+Given our definitions for the aggregation scheme in Section \ref{subsec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}.
 We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
@@
 Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
-As was shown in Section \ref{sec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
 From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.
@@
 \subsection{Algorithm} \label{subsec:algorithm}
-In this section, we piece together our LCAO secure encryption scheme in Section \ref{sec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.
+In this section, we piece together our LCAO secure encryption scheme in Section \ref{subsec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.
 
@@
 \begin{description}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{sec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
 Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.9375]
+\begin{tikzpicture}[font=\footnotesize]
     % Prediction
-    \draw [gray] (0,1.75) rectangle (8,8);
-    \node at (4,7.5) {1. Prediction};
+    \draw [gray] (0,2) rectangle (6.5,8);
+    \node at (3.25,7.5) {\small 1. Prediction};
 
     % Navigator
-    \fill  [blue!40] (3.25,7) rectangle (4.75,5.5);
-    \pic[xscale=0.22,yscale=0.3] at (4,6.6725) {plane};
-    \node at (4,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
+    \fill  [blue!40] (2.5,7) rectangle (4,5.5);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
+    \node at (3.25,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
 
     % Sensors
-    \fill  (1.5,3) [red!40] ellipse (0.5 and 0.5);
-    \node at (1.5,2.25) {Sensor $1$};
-    \fill  (6.5,3) [red!40] ellipse (0.5 and 0.5);
-    \node at (6.5,2.25) {Sensor $n$};
-
-    \fill [black] (3.5,3) circle (0.05);
-    \fill [black] (4,3) circle (0.05);
-    \fill [black] (4.5,3) circle (0.05);
+    \fill  (1.25,3) [red!40] ellipse (0.4 and 0.4);
+    \node at (1.25,2.375) {Sensor $1$};
+    \fill  (5.25,3) [red!40] ellipse (0.4 and 0.4);
+    \node at (5.25,2.375) {Sensor $n$};
+
+    \fill [black] (2.75,3) circle (0.05);
+    \fill [black] (3.25,3) circle (0.05);
+    \fill [black] (3.75,3) circle (0.05);
 
     % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.75,5.25) (1.75,3.5)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(4.25,5.25) (6.25,3.5)};
-
-    \fill [lightgray]  (0.25,5) rectangle (7.75,4);
-    \node at (4,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})): \rv{\omega} \in \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{x}_k, \rv{y}_k\}\rangle$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,5.25) (1.5,3.5)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,5.25) (5,3.5)};
+
+    \fill [lightgray]  (0.25,5) rectangle (6.25,4);
+    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \!:\! \rv{\omega} \!\in\! \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{y}_k\}\rangle$};
 
     % Measurement
-    \draw [gray] (0,-4.75) rectangle (8,1.5);
-    \node at (4,1) {2. Measurement};
+    \draw [gray] (0,-4.25) rectangle (6.5,1.75);
+    \node at (3.25,1.25) {\small 2. Measurement};
 
     % Navigator
-    \fill  (4,0) [blue!40] ellipse (0.5 and 0.5);
-    \pic[xscale=0.22,yscale=0.3] at (4,0.1725) {plane};
+    \fill  (3.25,0.25) [blue!40] ellipse (0.4 and 0.4);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,0.4225) {plane};
 
     % Sensors
-    \fill  [red!40] (7.5,-3.75)  rectangle (5.5,-2.75);
-    \node at (1.5,-4.25) {Sensor $1$};
-    \fill  [red!40] (2.5,-3.75)  rectangle (0.5,-2.75);
-    \node at (6.5,-4.25) {Sensor $n$};
-
-    \node at (1.5,-3.25) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
-    \node at (6.5,-3.25) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};
-
-    \fill [black] (3.5,-3.25) circle (0.05);
-    \fill [black] (4,-3.25) circle (0.05);
-    \fill [black] (4.5,-3.25) circle (0.05);
+    \fill  [red!40] (6.25,-3.625)  rectangle (4.25,-2.625);
+    \node at (1.25,-3.875) {Sensor $1$};
+    \fill  [red!40] (2.25,-3.625)  rectangle (0.25,-2.625);
+    \node at (5.25,-3.875) {Sensor $n$};
+
+    \node at (1.25,-3.125) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
+    \node at (5.25,-3.125) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};
+
+    \fill [black] (2.75,-3.125) circle (0.05);
+    \fill [black] (3.25,-3.125) circle (0.05);
+    \fill [black] (3.75,-3.125) circle (0.05);
 
     % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.75,-2.5) (3.75,-0.75)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(6.25,-2.5) (4.25,-0.75)};
-
-    \fill [lightgray]  (0.5,-1.25) rectangle (3.5,-2.25);
-    \node[align=center] at (2,-1.75) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
-    \fill [lightgray]  (4.5,-1.25) rectangle (7.5,-2.25);
-    \node[align=center] at (6,-1.75) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.25,-2.5) (3,-0.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(5.25,-2.5) (3.5,-0.25)};
+
+    \fill [lightgray]  (0.375,-0.875) rectangle (3.125,-1.875);
+    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
+    \fill [lightgray]  (3.375,-0.875) rectangle (6.125,-1.875);
+    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
 
     % Update
-    \draw [gray] (0,-10.25) rectangle (8,-5);
-    \node at (4,-5.5) {3. Update};
+    \draw [gray] (0,-8.5) rectangle (6.5,-4.5);
+    \node at (3.25,-5) {\small 3. Update};
 
     % Navigator
-    \fill  [blue!40] (2.25,-6) rectangle (5.75,-8);
-    \pic[xscale=0.22,yscale=0.3] at (4,-6.3275) {plane};
-    \node at (4,-7.125) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (4,-7.625) {$\rvec{x}_k$, $\mat{P}_k$};
-
-    % Sensors
-    \fill  (6.5,-9) [red!40] ellipse (0.5 and 0.5);
-    \node at (1.5,-9.75) {Sensor $1$};
-    \fill  (1.5,-9) [red!40] ellipse (0.5 and 0.5);
-    \node at (6.5,-9.75) {Sensor $n$};
-
-    \fill [black] (3.5,-9) circle (0.05);
-    \fill [black] (4,-9) circle (0.05);
-    \fill [black] (4.5,-9) circle (0.05);
-
+    \fill  [blue!40] (1.5,-5.5) rectangle (5,-7.5);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
+    \node at (3.25,-6.625) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
+    \node at (3.25,-7.125) {$\rvec{x}_k$, $\mat{P}_k$};
 \end{tikzpicture}
@@
 \begin{ack}                               
-Partially supported by zim
+Partially supported by ZIM
 \end{ack}

### 2020-10-09 tikz_images/proof.tex
Finished problem decomposition section - updated the start of the crypto section to suit the now moved decomposition discussion Updated the section summary to correctly summarise the new sections Added the notation paragraph Updated all Tikz images to be narrower as it looks nicer - also updated all the tikzimage .tex's to include preamble code so they look the same when opened in TikzEdt

@@
-\begin{tikzpicture}[font=\footnotesize]
+\begin{tikzpicture}[font=\small]
     % Bounding box
-\draw [gray] (0,-0.25) rectangle (8,7.5);
+    \draw [gray] (0,0) rectangle (6.5,6.5);
 
     % Outer adversary rectangle
-\draw[rounded corners=15pt, fill=gray!30] (0.5,7) rectangle (7.5,2.75);
+    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
     % Inner adversary rectangle
-\draw[rounded corners=15pt, fill=gray!60] (1,6.5) rectangle (7,5.5);
+    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);
 
     % Adversaries and challenger
-\node at (4,3.5) {\LARGE$\mathcal{A}'$};
-\node at (4,6) {\LARGE$\mathcal{A}$};
-\node at (4,0.5) {\LARGE$\mathcal{C}$};
+    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
+    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
+    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};
 
@@
     \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
-\draw [-latex] (2,4.5) --(2,5.5);
+    \draw [-latex] (2,4.5) --(2,5);
 
-\node[text width=3cm, align=center] at (6,4) {``Break''\\Our scheme};
-\draw [-latex] (6,5.5) -- (6,4.5);
+    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
+    \draw [-latex] (4.5,5) -- (4.5,4.5);
 
-\node[text width=3cm, align=center] at (6,1) {``Break''\\Joye-Libert\\scheme};
-\draw [-latex] (6,2.75) -- (6,1.75);
-
+    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
+    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
 \end{tikzpicture}

### 2020-10-12 main.tex
Added references for the placeholder citations - removed a couple as well

@@
 \section{Introduction}
-Localisation methods in distributed sensor environments have long been an active topic of research [].
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements [], echo-based range estimates [] and magnetic field measurements [] to the TDOA and TOA pseudo-range multilateration methods [].
-Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy [].
-These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally [].
+Localisation methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
+Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy.
+These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally.
 Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain.
-With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made these requirements of information security and user privacy more apparent than before [14,15].
+With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made these requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
 For example, a scenario of aircraft localisation in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
@@
 \subsection{Encryption Schemes in Signal Processing}
-Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data [].
-The most common methods for ensuring privacy during aggregation have been described below.
+Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
+The most common methods for ensuring privacy during aggregation required for signal processing tasks have been described below.
 \begin{description}
-    \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation [].
-In the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs [norm, PHE ones].
+    \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
+To handle the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs \cite{hanPrivacyControlDynamical2018,dworkDifferentialPrivacySurvey2008,andresGeoindistinguishabilityDifferentialPrivacy2013}.
 Although differential privacy has strong computational benefits due to its implementational simplicity, it provides relatively weak security guarantees for multi-party networks, with no guarantees in the presence of multiple colluding corrupted parties.
 Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localisation.
-    \item[Aggregator Oblivious Encryption] This method of encryption formalises the privacy of \textit{all} aggregation data from honest parties [].
+    \item[Aggregator Oblivious Encryption] This method of encryption formalises the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
 Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
-The originally proposed method [] is restricted to a small input domain which has been expanded and computationally simplified in later works [joye-lib,student-one].
-The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter mean calculation [].
+The originally proposed method \cite{shiPrivacyPreservingAggregationTimeSeries2011} is restricted to a small input domain which has been expanded and computationally simplified in later works \cite{joyeScalableSchemePrivacyPreserving2013,benhamoudaNewFrameworkPrivacyPreserving2016}.
+The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter mean calculation \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
 \end{description}
@@
 \begin{description}
-    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results [].
-Although theoretically ideal for many privacy-preserving tasks, current implementations are still computationally impractical for real-time or large scale tasks [].
-    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes, these schemes provide only a subset, typically one, of algebraic operations on encrypted data [].
-The reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication [], set intersection computation [] and control input aggregation [].
+    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
+Although theoretically ideal for many privacy-preserving tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
+    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset, typically one, of algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
+Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}.
 However, these works are relatively restricted in application due to the limited operations provided.
@@
 \begin{description}
-    \item[Multi-Client Function Encryption] This type of encryption allows the computing of a specific function given encrypted inputs [].
+    \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
 It is suitable for privacy-preserving distributed data as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
-While such schemes that can compute arbitrary functions are still too computationally expensive for practical use [], partial schemes supporting only some functions, such as computing vector dot products [], exist, but have yet to find applications in more complicated signal processing tasks.
+While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
 \end{description}
@@
 \subsection{Encrypted Localisation and Estimation}
-Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors [].
+Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
 We aim to provide an accurate localisation filter in the presence of range-only sensors.
 
-Relevant estimation methods include both model-based Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter [], and model-free methods where location estimates are made independently of each other [proloc,serloc].
-The work in [proloc] uses partially homomorphic encryption to compute model-free location estimates while preserving the privacy of sensor measurements and locations.
+Relevant estimation methods include both model-based Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and model-free methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
+The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute model-free location estimates while preserving the privacy of sensor measurements and locations.
 The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols.
@@
 Model-based approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
-In [aristov], partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator.
+In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator.
 While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.
-Model-based encrypted control [farohki summary] also introduces some privacy-preserving methods relevant to estimation.
-[alexandru] proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires repeated key distribution among all involved parties.
-In [farohki], a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures.
-
-While we primarily focus on applying encryption schemes to localisation algorithms, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
+Model-based encrypted control \cite{farokhiPrivacyDynamicalSystems2020} also introduces some privacy-preserving methods relevant to estimation.
+\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires repeated key distribution among all involved parties.
+In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures.
+
+While we have focused on the application of encryption schemes to localisation algorithms, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
 As is the case with localisation sensors, real number measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
-The Google BigNum library [google bignum] provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
+The Google BigNum library \cite{Encryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
 It, however, leaks the exponent information of encrypted numbers.
-In [farohki], a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
+In \cite{farokhiSecurePrivateControl2017}, a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
 
@@
 
-    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms.
-As privacy-preserving implementations of such mechanisms require additional complications, we do not consider the scenario in this work.
+    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}.
+As privacy-preserving implementations of such mechanisms require additional complications, we will not consider the scenario in this work.
     \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
@@
 % Elsevier at the time of printing.
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{BibTeX/PrivateEIFLocalisation}

### 2020-10-12 main.tex
Update to the abstract

@@
 Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
-Traditional distributed sensor navigation methods involve the leakage of sensor information or navigator location during localisation protocols and fail to preserve participants’ data privacy.
-Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common, model-based, non-linear measurement, localisation methods and forfeit broad applicability.
-We define a cryptographically secure linear-combination aggregation scheme which we apply to the Extended Kalman Filter with range-sensor measurements, and show that navigator location, sensor locations and sensor measurements can remain private during navigation.
-The security requirements, leakage, and cryptographic proof are given for the private filter and aggregation scheme, and simulations of the filter are used to evaluate the accuracy and performance of the method.
-Our approach defines a novel, computationally plausible and cryptographically private, model-based localisation filter with direct application to environments where nodes may not be fully trusted and data is considered sensitive.
+Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localisation protocols, thus not preserving participants’ data privacy.
+Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability.
+We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements.
+Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and is implemented and run on simulations to evaluate its accuracy and performance.
+The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where nodes are not trusted or data is considered sensitive.
 \end{abstract}

### 2020-10-13 main.tex
Started on making all the small changes listed in written notes Also fixing up English where its needed in first complete readthrough Making the changes suggested by Benjamin as they are reached - Currently up to LOC section, continuing from there tomorrow

@@
 Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain.
-With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made these requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
-For example, a scenario of aircraft localisation in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
-Alternatively, autonomous vehicle state estimation may benefit from neighbouring vehicles' information while no participant wishes to share information about their hardware.
+With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
+For example, an aircraft localisation scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
+Or in autonomous vehicle state estimation, benefit from neighbouring vehicles' information may be desired while no participant wishes to share information about their hardware.
 Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
@@
 $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal.
-$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively.
-Encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$, respectively.
+$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
+Additionally, key $k$ may be ommited when inferrable from context.
 $\lfloor\cdot\rceil$ rounds to the nearest integer, $a | b$ stands for ``$a$ divides $b$'', and $a\|b$ for a bitwise concatenation of $a$ and $b$.
@@
 \section{Literature Overview}
-In this section, we will discuss methods for providing security guarantees in signal processing tasks, and some applications to localisation and estimation problems.
+In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localisation and estimation problems.
 
@@
 The originally proposed method \cite{shiPrivacyPreservingAggregationTimeSeries2011} is restricted to a small input domain which has been expanded and computationally simplified in later works \cite{joyeScalableSchemePrivacyPreserving2013,benhamoudaNewFrameworkPrivacyPreserving2016}.
-The aggregation operation in aggregator obliviousness is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter mean calculation \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
+The aggregation operation in these schemes is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sum or mean calculation \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
 \end{description}
@@
 \end{description}
-Lastly, recent developments in encryption schemes have provided some novel methods also suitable for privacy-preserving computation in distributed environments.
+Lastly, recent developments in encryption schemes have presented some novel methods also suitable for privacy-preserving computation in distributed environments.
 \begin{description}
@@
 
-Relevant estimation methods include both model-based Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and model-free methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
-The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute model-free location estimates while preserving the privacy of sensor measurements and locations.
+Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
+The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute time-independent location estimates while preserving the privacy of sensor measurements and locations.
 The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols.
@@
 
-Model-based approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
+Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
 In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator.
 While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.
-Model-based encrypted control \cite{farokhiPrivacyDynamicalSystems2020} also introduces some privacy-preserving methods relevant to estimation.
+Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
 \cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires repeated key distribution among all involved parties.
@@
 As is the case with localisation sensors, real number measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
-The Google BigNum library \cite{Encryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
+Google's Encrypted BigQuery Client \cite{Encryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
 It, however, leaks the exponent information of encrypted numbers.
 In \cite{farokhiSecurePrivateControl2017}, a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
+We will discuss and justify our choice of encoding scheme when introducing the localisation filter.
 
@@
 \end{equation}
-with zero-mean Gaussian process noise $w_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
+with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
 \begin{equation}
@@
 \end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, while the measurement function $h_i$, for sensor $i$ at location
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, with measurement function $h_i$, for sensor $i$ at location
 \begin{equation}
@@
 \end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$ or their measurements $\rv{z}_k$ at any time $k$.
-We motivate these goals with an example.
-When considering aircraft navigation in the presence of privately-owned range-measuring towers, it is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown tower-owning parties.
-Similarly, tower locations may wish to be kept private from unidentified navigating aircraft.
-However, the additional safety to passengers, provided by accurate aircraft localisation, may be a goal of all those involved.
+We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
+We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
+It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
+However, the additional safety to passengers provided by accurate aircraft localisation, may be a goal of all those involved justifying their cooperation.
 
@@
 The recursive nature of the problem definition above complicates defining and proving of security requirements for the localisation scenario.
-As with existing estimation methods [] we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
+As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
+
 To support multiple aggregations at each time step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$.
-The bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
+The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
 That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
@@
 \begin{rem}
-    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement is computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
+    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
@@
 \begin{description}
-    \item[Global navigator broadcast] Due to sensor location privacy and model non-linearity, bi-directional communication between navigator and sensors is required.
+    \item[Global navigator broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required.
 We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
@@
 It may be the case that some sensors are not within the range of a navigator broadcast.
-We loosely propose that this scenario can be handled by pre-defined sensor subsets during an initial step by a trusted party.
-This has been captured in Figure \ref{fig:sensor_subsets}.
+We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party.
+An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localisation instances with global broadcasts.
     \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
@@
 \end{tikzpicture}
-\caption{An example of sensor subsets; $\{1,2,3\}$ and $\{3,4,5\}$, and the areas where the navigator is in range of all sensors within a subset.}
+\caption{An example of sensor subsets. Subsets $\{1,2,3\}$ and $\{3,4,5\}$ can be used independently for localisation when the navigator is within their ranges.}
 \label{fig:sensor_subsets}
@@
 \subsection{Inherent Leakage}
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates naturally leads to the leakage of some measurement information.
-For this reason, we accept that average information about sensors may be leaked at each time step and instead show that individual sensor information remains private.
+Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information.
+For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
+We will Instead show that individual sensor information remains private to sensors and that the most precise localisation estimate, requiring all measurements, remains private to the navigator.
 
@@
 \section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our aggregation security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
+When defining our aggregation security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme and the Joye-Libert private aggregation scheme.
 
@@
     \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \\
+    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
     \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
@@
 \subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
-The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of AO.
+The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data, that we refer to as instances for consistency, and meets the security notion of AO.
 Similarly to the Paillier scheme, it bases its security on the DCRA.
@@
 Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all users, while the last key is set as
+$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
 \begin{equation*}
@@
 
-Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at time $t$ is computed by user $i$ as
+Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
 \begin{equation}
@@
     \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,0\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
+    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=1}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{description}
@@
 Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{1,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
 \end{rem}
@@
 \subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
-We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$, defined as
+We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
+These are used by a trusted third party, an aggregator and value producing users $i\,1\leq i \leq n$.
+They are defined as follows
 
 \begin{description}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the remaining user private keys $sk_i,\,1\leq i \leq n$.
-    \item[$\mathsf{Enc}(pk_0, \omega)$] The aggregator and users can encrypt a weight $\omega$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(\omega)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At time $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
+    \item[$\mathsf{Enc}(pk_0, a)$] The aggregator and users can encrypt any value $a$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(a)$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{description}
 
-Next, we formalise the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
+We formalise the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
 
@@
     \begin{enumerate}
-        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
-        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
+        \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
+        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
         \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
@@
         \end{equation*}
-        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
+        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
     \end{enumerate} 
-    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
+    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game.
 The attacker then chooses two series of tuples
@@
     \end{equation*}
-    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
+    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
     \begin{equation*}
@@
 \subsection{Our Scheme} \label{subsec:our_scheme}
-Our scheme is based on the Paillier and Joye-Libert schemes introduced in Section \ref{sec:crypto_prelim}, and similarly bases its security on the DCRA.
+Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA.
 As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys.
@@
 
-    \item[$\mathsf{Enc}(pk_0, \omega)$] Encryption of weights is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
-    \begin{equation}
-        \mathcal{E}_{pk_0}(\omega) = (N+1)^{\omega}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
+    \item[$\mathsf{Enc}(pk_0, a)$] Encryption of values is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
+    \begin{equation}
+        \mathcal{E}_{pk_0}(a) = (N+1)^{a}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
     \end{equation}
@@
 
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
     \begin{equation}
@@
             to $\mathcal{A}$.
-            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for time $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
+            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
 The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
@@
         \end{equation*}
-        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for time $t^*$ and submit AO challenge series
+        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
         \begin{equation*}
@@
 
-    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ behaves identically to our scheme described in Section \ref{subsec:our_scheme}.
+    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ follows our scheme in Section \ref{subsec:our_scheme} exactly.
 Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
@@
 \section{Private Localisation Preliminaries} \label{sec:loc_prelim}
-The localisation filter we introduce requires real-valued inputs and functions, and relies on a non-linear measurement model.
-We make use of a real-number encoding scheme which supports the required homomorphic operations and an algebraic reformulation of the Extended Kalman Filter which reduces the filter update step to use only these operations.
+Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localisation filter.
+The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
+We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
 
@@
 We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$.
-This contrasts with the common definition given in terms of total bits $a$ and fractional bits $b$ \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
+This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
 Rational subset $\mathbb{Q}_{r,f}$ is given by
@@
 In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
-This is captured by a third parameter $m$; the number of \textit{additional} multiplication factors to add or remove from encodings.
-
-The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_N$, and the desired scaling for $m$ prior encoded multiplications, is given by
-\begin{equation}
-    \mathsf{E}_{N,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{N}\,. \label{eqn:encode}
-\end{equation}
-Decoding of an integer $e \in \mathbb{Z}_N$, is given by
-\begin{equation}
-    \mathsf{E}^{-1}_{N,f,m}(e) \!=\! 
+This is captured by a third parameter $m$; the number of multiplication factors to add or remove from encodings.
+
+The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
+\begin{equation}
+    \mathsf{E}_{r,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{r}\,. \label{eqn:encode}
+\end{equation}
+Decoding of an integer $e \in \mathbb{Z}_r$, is given by
+\begin{equation}
+    \mathsf{E}^{-1}_{r,f,m}(e) \!=\! 
     \begin{dcases}
-        \frac{e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &e\hspace{-8pt}\pmod{N} \leq \left\lfloor\frac{N}{2}\right\rfloor \\
-        -\frac{N - e\hspace{-8pt}\pmod{N}}{f^{m+1}}, &\text{otherwise} \\
+        \frac{e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &e\hspace{-8pt}\pmod{r} \leq \left\lfloor\frac{r}{2}\right\rfloor \\
+        -\frac{r - e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &\text{otherwise} \\
     \end{dcases}.\label{eqn:decode}
@@
     \begin{split}
-        \mathsf{E}_{N,f,m}(a_1) + \mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
-        &\mathsf{E}_{N,f,m}(a_1+a_2)
+        \mathsf{E}_{r,f,m}(a_1) + \mathsf{E}_{r,f,m}(a_2)& \pmod{r} =\\
+        &\mathsf{E}_{r,f,m}(a_1+a_2)
     \end{split}\label{eqn:encoding_homomorphic_add}
@@
     \begin{split}
-        \mathsf{E}_{N,f,m}(a_1)\mathsf{E}_{N,f,m}(a_2)& \pmod{N} =\\
-        &\mathsf{E}_{N,f,m+1}(a_1a_2)\,,
+        \mathsf{E}_{r,f,m}(a_1)\mathsf{E}_{r,f,m}(a_2)& \pmod{r} =\\
+        &\mathsf{E}_{r,f,m+1}(a_1a_2)\,,
     \end{split}
 \end{equation}
-noting that the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:our_scheme_lin_comb}.
+noting that when $r=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
 
@@
 \begin{equation*}
-    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{N}{2} \right\rfloor\,.
-\end{equation*}
-In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored.
+    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{r}{2} \right\rfloor\,.
+\end{equation*}
+In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $r=N$.
 
@@
 \end{equation}
-with Jacobian
+with Jacobians
 \begin{equation}

### 2020-10-14 main.tex
Completed a lot more changes - many wording consistencies - many equation numbering consistencies - many notation consistencies - some figures updated a little bit as well - etc... - 2 additions remain

@@
 % Title, preferably not more than 10 words.
-\title{Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}}
+\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}}
 
@@
 Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
-Sections \ref{sec:loc_prelim} and \ref{sec:private_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the secure aggregation scheme.
+Sections \ref{sec:loc_prelim} and \ref{sec:priv_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the private aggregation scheme.
 We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.
@@
 Additionally, key $k$ may be ommited when inferrable from context.
-$\lfloor\cdot\rceil$ rounds to the nearest integer, $a | b$ stands for ``$a$ divides $b$'', and $a\|b$ for a bitwise concatenation of $a$ and $b$.
-Sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
+$\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
 
@@
     \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
-Although theoretically ideal for many privacy-preserving tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
+Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
     \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset, typically one, of algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
@@
     \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
-It is suitable for privacy-preserving distributed data as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
+It is suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
 While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
@@
 
-To support multiple aggregations at each time step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$.
+To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$.
 The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
@@
 
-In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.
+In Section \ref{sec:priv_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.
 
@@
     \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
-This means the navigator may not send different information to individual sensors during a single timestep.
+This means the navigator may not send different information to individual sensors during a single time-step.
 
@@
 $n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
-\begin{equation*}
+\begin{equation}
     sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
-\end{equation*}
+\end{equation}
 and sent to the aggregator.
@@
 
-When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, private summation and decryption are computed by the functions
+When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
 \begin{equation}
@@
     \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^n_{i=1}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$.
+    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{description}
@@
     \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
     \begin{equation*}
@@
     % Adversaries and challenger
-    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
-    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
-    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};
+    \node at (3.25,3.25) {\Large$\mathcal{A}'$};
+    \node at (3.25,5.5) {\Large$\mathcal{A}$};
+    \node at (3.25,0.5) {\Large$\mathcal{C}$};
 
     % Arrows
-    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
+    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO secure\\scheme};
     \draw [-latex] (2,1.75) -- (2,2.75);
 
-    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
+    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO secure\\scheme};
     \draw [-latex] (2,4.5) --(2,5);
@@
 
-\section{Private Localisation Preliminaries} \label{sec:loc_prelim}
+\section{Encrypted Localisation Preliminaries} \label{sec:loc_prelim}
 Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localisation filter.
@@
 \subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
-In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x : x \in \mathbb{Z}_N\}$.
+In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x \,|\, x \in \mathbb{Z}_N\}$.
 For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing.
@@
 Rational subset $\mathbb{Q}_{r,f}$ is given by
-\begin{equation*}
-    \mathbb{Q}_{r,f} = \left\{q : f^{-1} | q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
-\end{equation*}
+\begin{equation}
+    \mathbb{Q}_{r,f} = \left\{q \,|\, f^{-1}\ \textsf{divides}\ q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
+\end{equation}
 and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$.
@@
 Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
-\begin{equation*}
+\begin{equation}
     \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{r}{2} \right\rfloor\,.
-\end{equation*}
+\end{equation}
 In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $r=N$.
@@
 
-\section{Private Localisation with Privacy-Preserving Sensors} \label{sec:private_localisation}
-Given our definitions for the aggregation scheme in Section \ref{subsec:our_scheme} and preliminaries in Section \ref{sec:loc_prelim}, we can now construct a localisation method meeting our problem formulation in Section \ref{sec:problem_statement}.
-We consider a navigator in the presence of $n$ range sensors, running a local filter with update steps computed by equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
-Received information from each sensor $i$ consists of the measurement vector
+\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
+With the relevant preliminaries, we now apply the LCAO secure scheme to our original localisation problem.
+Recall we are considering a navigator in the presence of $n$ range sensors.
+The navigator runs a local filter, computing its update step with equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}, where received information from each sensor $i$ consists of the measurement vector
 \begin{equation}
@@
 \end{equation}
-at each time step $k$.
+at each time-step $k$.
 In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
@@
 
-Normal privacy-preserving aggregation encryption of $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors would require the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$.
-Instead, we want to formulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use an LCAO secure encryption scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
-As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and the navigator cannot learn individual sensor values $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
-From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a reformulation sets requirements on the possible measurement functions $h_i$.
+The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$.
+Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
+As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.
 
@@
 
-\subsection{Requirements for the Measurement Model}
-From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with weights dependant only on those from the original matrices.
-For example, consider dimension $N\times N$ matrices $\mat{A}$ and $\mat{B}$, where element $(i,j)$ in matrix $\mat{A}$ is of the form $\sum_{l=0}^M w_{l,i,j}a_{l,i,j}$ and similarly for matrix $\mat{B}$, form $\sum_{l=0}^M v_{l,i,j}b_{l,i,j}$.
-If we consider $w_{l,i,j}$ and $v_{l,i,j}$ as the weight terms, we can write element $(i,j)$ of a product matrix $\mat{A}\mat{B}$, with weights dependant only on these, as
+\subsection{Measurement Model Requirements}
+From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependant only on weights from the original matrices.
+For example, consider dimension $N\times N$ matrices $\mat{A}$ and $\mat{B}$, where element $(i,j)$ in matrix $\mat{A}$ is of the form $\sum_{l=0}^M w_{l,i,j}a_{l,i,j}$ and similarly for matrix $\mat{B}$, the form $\sum_{l=0}^M v_{l,i,j}b_{l,i,j}$.
+If we consider $w_{l,i,j}$ and $v_{l,i,j}$ as the weight terms, we can write element $(i,j)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependant only on these weights, as
 \begin{equation}
@@
 
-The final step required for the application of our LCAO-secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance-stamp variable $t$, in \eqref{eqn:our_scheme_lin_comb}.
-As six linear-combination aggregations occur at each time step $k$ (four element in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
+The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$, in \eqref{eqn:our_scheme_lin_comb}.
+As six linear-combination aggregations occur at each time-step $k$ (four element in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
 This is handled by setting $t$ to the concatenation
@@
 \subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ with Gaussian noise and variances $\rv{r}_{k,i}$ in the modified measurement model \eqref{eqn:modified_measurement_model}.
+In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ with white Gaussian noise and variances $\rv{r}_{k,i}$ in the modified measurement model \eqref{eqn:modified_measurement_model}.
 In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
@@
     \begin{split}
-        \rv{z}_{k,i} &> h_i(\rvec{x}_k) \\
-        \rv{z}_{k,i} - h_i(\rvec{x}_k) &> 0 \\
-        \rv{v}_{k,i} &> 0\,,
+        &\rv{z}_{k,i} > h_i(\rvec{x}_k) \\
+        \implies &\rv{z}_{k,i} - h_i(\rvec{x}_k) > 0 \\
+        \implies &\rv{v}_{k,i} > 0\,,
     \end{split}
@@
 \begin{description}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
 Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
@@
 
-    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,1}$ and $\mat{I}'_{k,1}$, encrypting them for aggregation, and sending them back to the navigator.
+    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator.
 Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}.
-This has been described by Algorithm \ref{alg:measurement_info}.
+This is described by Algorithm \ref{alg:measurement_info}.
 
@@
 
-    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
+    \State Let $\beta_{v1}^{(i)}$ represent an encryption of element $(v,1)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
     \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
@@
     \fill [lightgray]  (0.25,5) rectangle (6.25,4);
-    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \!:\! \rv{\omega} \!\in\! \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{y}_k\}\rangle$};
+    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{y}_k\}\rangle$};
 
@@
 Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme security, but avoid malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achieved by detecting changes in real measurements after reporting false measurements to the navigator.
+Honest-but-curious sensors are not required for scheme security, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements.
+This is possibly achieved by detecting changes in real measurements after reporting false measurements to the navigator.
 As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicates homomorphic operations and active malicious sensors are not considered in the scope of this work.
@@
 
-From the leaked coefficient sums, we see that all information private to the sensors, namely their measurements $\rv{z}'_{k,i}$ and locations $\vec{s}_i$, are present only in sums
-\begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localisation_leakage}
-\end{equation}
-Therefore, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor measurements and locations.
-\begin{rem}
-    In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor measurements and locations, given by the sums in \eqref{eqn:localisation_leakage}.
-\end{rem}
+From the leaked coefficient sums, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
+\begin{equation}
+    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localisation_leakage}
+\end{equation}
+From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_meaasurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
+\begin{thm}
+    In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localisation_leakage}.
+\end{thm}
 
@@
 \end{center}
-\caption{Layouts Normal Big}
+\caption{The considered layouts.}
 \label{fig:sim_layouts}
 \end{figure}
-To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with unmodified sensor measurement variances $r_i=5$ metres.
+To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances $r_i=5$ metres.
 Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
@@
 \end{center}
-\caption{Layout errors}
+\caption{Filter error for different layouts.}
 \label{fig:sim_layout_errors}
@@
 \end{center}
-\caption{Timing}
+\caption{Runtimes for varying key sizes and numbers of sensors.}
 \label{fig:sim_timing}
@@
 To develop a model-based localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Joye-Libert aggregation scheme.
-This scheme was then used in our proposed private EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
+This scheme was then used in our proposed privacy-preserving EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
 Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
@@
 \begin{ack}                               
-Partially supported by ZIM
+Partially supported by ZIM \dots
 \end{ack}
@@
 
-The security game between attacker and challenger for IND-CPA is given by
+The security game between attacker and challenger for IND-CPA security is given by
 \begin{description}
@@
     \item[More Encryptions] The attacker can now compute more encryptions with the public key $pk$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
     \begin{equation*}
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
-    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At time $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At time $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
+    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
 \end{description}
 
-The security game between attacker and challenger for AO is given by
+The security game between attacker and challenger for AO security is given by
 \begin{description}
@@
         \end{equation*}
-        They are given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
+        The attacker is then given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
     \end{enumerate} 
-    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game.
+    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game.
 The attacker then chooses two series of tuples
@@
     \item[More Queries] The attacker can now submit more queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
+    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
     \begin{equation*}

### 2020-10-15 main.tex
Updated notations to denote filter estimates as x_{k|k} allowing the identification of prediction and update steps in the filter - also added it in notation paragraph - still need to do whole read-through but looks like it was done properly from first look

@@
 $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal.
+Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
 $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
@@
 \end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, with measurement function $h_i$, for sensor $i$ at location
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, and measurement function $h_i$ for sensor $i$ at location
 \begin{equation}
@@
 \end{equation} 
-is defined as
-\begin{equation}
-    \begin{split}
-        h_i(\rvec{x}_k) &= \left\lVert
+defined as
+\begin{equation}
+    \begin{split}
+        h_i(\rvec{x}) &= \left\lVert
         \begin{bmatrix}
-            \rv{x}_k & \rv{y}_k
+            \rv{x} & \rv{y}
         \end{bmatrix}^\top
         - \vec{s}_{i}\right\rVert \\
-        &= \sqrt{(\rv{x}_k-s_{x,i})^2 + (\rv{y}_k-s_{y,i})^2}\,.
+        &= \sqrt{(\rv{x}-s_{x,i})^2 + (\rv{y}-s_{y,i})^2}\,.
     \end{split}
 \end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn the estimated state $\rvec{x}_k$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
+We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn state estimates of $\rvec{x}_{k}$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
 We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
@@
             \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
-The received response is of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
+The received response will be of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
             \begin{equation*}
@@
         \end{equation*}
-        to $\mathcal{C}$. The received response if of the form 
+        to $\mathcal{C}$. The received response will be of the form 
         \begin{equation*}
@@
 
-The combined quantisation and encoding function $\mathsf{E}_{r,f,m}(x)$ of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
+The function for combined quantisation and encoding $\mathsf{E}_{r,f,m}(x)$, of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
 \begin{equation}
@@
 The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
-This requires the conversion of state estimate $\rvec{x}_k$ and estimate covariance $\mat{P}_k$ to the information vector and matrix
-\begin{equation}
-    \rvec{y}_k = \mat{P}_k^{-1}\rvec{x}_k \quad\textrm{and}\quad \mat{Y}_k = \mat{P}_k^{-1}\,,
+This requires the conversion of predicted state estimate $\rvec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ to the information vector and matrix
+\begin{equation}
+    \rvec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
 \end{equation}
@@
 \begin{equation}
-    \rvec{y}_k = \rvec{y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:eif_info_vec_update}
+    \begin{split}
+        &\rvec{y}_{k|k} = \rvec{y}_{k|k-1} + \\
+        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1})
+    \end{split} \label{eqn:eif_info_vec_update}
 \end{equation}
@@
 \begin{equation}
-    \mat{Y}_k = \mat{Y}_{k} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
+    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
 \end{equation}
@@
 \begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_k} \label{eqn:measurement_jacobian}
-\end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_k$ and matrix $\mat{Y}_k$ back to state estimate and covariance 
-\begin{equation}
-    \rvec{x}_k = \mat{Y}_k^{-1}\rvec{y}_k \quad\textrm{and}\quad \mat{P}_k = \mat{Y}_k^{-1}\,,
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
+\end{equation}
+for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
+\begin{equation}
+    \rvec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
 \end{equation}
@@
 \begin{equation}
-    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})
+    \rvec{x}_{k+1|k} = \vec{f}(\rvec{x}_{k|k})
 \end{equation}
@@
 \begin{equation}
-    \mat{P}_k = \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top\,,
+    \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top\,,
 \end{equation}
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k-1}}\,. \label{eqn:jacobian_f}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
 \end{equation}
@@
 \begin{equation}
-    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_k) + \mat{H}_{k,i}\rvec{x}_k) \label{eqn:measurement_vec}
+    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1}) \label{eqn:measurement_vec}
 \end{equation}
@@
 
-The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_k$, for the computing of Jacobians $\mat{H}_{k,i}$.
-Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_k$ as weights from the navigator.
-As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_k$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_{k|k-1}$, for the computing of Jacobians $\mat{H}_{k,i}$.
+Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as weights from the navigator.
+As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
 From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.
@@
 Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
-In addition, the Jacobian of $h_i$,
+In addition, the Jacobian of $h_i$ at $\rvec{x}_{k|k-1}$,
 \begin{equation}
@@
     \begin{bmatrix}
-        \frac{\rv{x}_k - s_{x,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} \\
-        \frac{\rv{y}_k - s_{y,i}}{\sqrt{(\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2}} 
+        \frac{\rv{x}_{k|k-1} - s_{x,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} \\
+        \frac{\rv{y}_{k|k-1} - s_{y,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} 
     \end{bmatrix}\,,
@@
 \begin{equation}
-    h'_i(\rvec{x}_k) = h_i(\rvec{x}_k)^2\,. \label{eqn:modified_measurement_func}
+    h'_i(\rvec{x}) = h_i(\rvec{x})^2\,. \label{eqn:modified_measurement_func}
 \end{equation}
@@
     \begin{split}
-        h'_i(\rvec{x}_k) &= \left\lVert
+        h'_i(\rvec{x}) &= \left\lVert
         \begin{bmatrix}
-            \rv{x}_k & \rv{y}_k
+            \rv{x} & \rv{y}
         \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
-        &= (\rv{x}_k - s_{x,i})^2 + (\rv{y}_k - s_{y,i})^2 \\
-        &= \rv{x}_k^2 + \rv{y}_k^2 -2s_{x,i}\rv{x}_k -2s_{y,i}\rv{y}_k +s_{x,i}^2 +s_{y,i}^2
+        &= (\rv{x} - s_{x,i})^2 + (\rv{y} - s_{y,i})^2 \\
+        &= \rv{x}^2 + \rv{y}^2 -2s_{x,i}\rv{x} -2s_{y,i}\rv{y} +s_{x,i}^2 +s_{y,i}^2
     \end{split}\,,
@@
     \begin{bmatrix}
-        2\rv{x}_k - 2s_{x,i} \\
-        2\rv{y}_k - 2s_{y,i}
-    \end{bmatrix}\,.
-\end{equation}
-The above have been rearranged as linear combinations of the weights $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k$ and $\rv{y}_k$, which capture all the required information that is private to the navigator.
+        2\rv{x}_{k|k-1} - 2s_{x,i} \\
+        2\rv{y}_{k|k-1} - 2s_{y,i}
+    \end{bmatrix}\,. \label{eqn:modified_jacobian}
+\end{equation}
+From the above we see that $h'_i(\rvec{x}_{k|k-1})$ and $\mat{H}'_{k,i}$ can be rearranged as linear combinations of the weights $\rv{x}_{k|k-1}^2$, $\rv{y}_{k|k-1}^2$, $\rv{x}_{k|k-1}$ and $\rv{y}_{k|k-1}$, which capture all the required information that is private to the navigator.
 
@@
     \begin{split}
-        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_k) + \mat{H}'_{k,i}\rvec{x}_k) \\
+        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_{k|k-1}) + \mat{H}'_{k,i}\rvec{x}_{k|k-1}) \\
         &= 
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{x}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k^2 + (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}^3) + (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1}^2 \\
+                &\quad+ (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1}^2 \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_{k|k-1}\\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{x,i}^3) \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{y}_k^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_k^2\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k^2 \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k^2 + (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_k \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_k + (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_k \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) + (2\rv{r}_{k,i}^{-1}s_{y,i}^3) \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
+                &(2\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2\rv{y}_{k|k-1} \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1}^2 \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_{k|k-1} \\
+                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
+                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}^3) + (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
             \end{split}
@@
 \begin{align*}
-    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_k + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
-    \begin{split}
-        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_k\rv{y}_k + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_k + (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_k \\
-        &\qquad+ (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
+    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
+    \begin{split}
+        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
+        &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
     \end{split}\\
     \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_k^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_k + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
+    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
 \end{align*}
-The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights $\rv{x}_k^3$, $\rv{y}_k^3$, $\rv{x}_k^2\rv{y}_k$, $\rv{x}_k\rv{y}_k^2$, $\rv{x}_k^2$, $\rv{y}_k^2$, $\rv{x}_k\rv{y}_k$, $\rv{x}_k$ and $\rv{y}_k$, which again capture all the required information private to the navigator.
-
-The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$, in \eqref{eqn:our_scheme_lin_comb}.
-As six linear-combination aggregations occur at each time-step $k$ (four element in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
+The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights 
+\begin{equation}
+    \begin{split}
+        &\langle \rv{x}_{k|k-1}^3,\ \rv{y}_{k|k-1}^3,\ \rv{x}_{k|k-1}^2\rv{y}_{k|k-1},\ \rv{x}_{k|k-1}\rv{y}_{k|k-1}^2,\\
+        &\quad \rv{x}_{k|k-1}^2,\ \rv{y}_{k|k-1}^2,\ \rv{x}_{k|k-1}\rv{y}_{k|k-1},\ \rv{x}_{k|k-1},\ \rv{y}_{k|k-1}\rangle\,,
+    \end{split} \label{eqn:weights_to_broadcast}
+\end{equation}
+which again capture all the required information private to the navigator.
+
+The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$ in \eqref{eqn:our_scheme_lin_comb}.
+As six linear-combination aggregations occur at each time-step $k$ (four elements in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
 This is handled by setting $t$ to the concatenation
@@
     \begin{algorithmic}[1]
-        \Procedure{Prediction}{$\rvec{x}_{k-1}$, $\mat{P}_{k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
+        \Procedure{Prediction}{$\rvec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
 
         \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
-        \State $\rvec{x}_{k} \gets \vec{f}(\rvec{x}_{k-1})$
-        \State $\mat{P}_{k} \gets \mat{F}_k\mat{P}_{k-1}\mat{F}_k^\top + \mat{Q}$
-
-        \For{$\rv{\omega}$ in $\langle\rv{x}_k^3,\rv{y}_k^3,\rv{x}_k^2\rv{y}_k,\rv{x}_k\rv{y}_k^2,\rv{x}_k^2,\rv{y}_k^2,\rv{x}_k\rv{y}_k,\rv{x}_k,\rv{y}_k\rangle$} 
+        \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
+        \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$
+
+        \For{$\rv{\omega}$ in \eqref{eqn:weights_to_broadcast}} 
             \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
@@
 
-        \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
+        \State \Return $\rvec{x}_{k|k-1}, \mat{P}_{k|k-1}$
         \EndProcedure
@@
     \While{Navigator broadcasting}
-    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))$
+    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$
     \State Recieve remaining weights in the form above
@@
     \State Let $\beta_{v1}^{(i)}$ represent an encryption of element $(v,1)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k\rv{y}^2_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}
-    \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}$\par
+    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}\cdot$\par
     \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
-    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}$\par
+    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
     \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
@@
     \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_k))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_k))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}
-    (N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}$\par
+    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
@@
 \begin{algorithmic}[1]
-    \Procedure{Update}{$\rvec{x}_{k}$, $\mat{P}_{k}$, $N$, $\lambda$}
+    \Procedure{Update}{$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}
 
@@
 
-    \State $\rvec{y}_k \gets \mat{P}_{k}^{-1}\rvec{x}_{k} + \sum_{i=1}^n\rvec{i}'_{k,i}$
-    \State $\mat{Y}_k \gets \mat{P}_{k}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
-    \State $\rvec{x}_{k} \gets \mat{Y}_k^{-1}\rvec{y}_k$
-    \State $\mat{P}_{k} \gets \mat{Y}_k^{-1}$
-    \State \Return $\rvec{x}_{k}, \mat{P}_{k}$
+    \State $\rvec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} + \sum_{i=1}^n\rvec{i}'_{k,i}$
+    \State $\mat{Y}_{k|k} \gets \mat{P}_{k|k-1}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
+    \State $\rvec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k}$
+    \State $\mat{P}_{k|k} \gets \mat{Y}_{k|k}^{-1}$
+    \State \Return $\rvec{x}_{k|k}, \mat{P}_{k|k}$
     \EndProcedure
@@
     % Navigator
-    \fill  [blue!40] (2.5,7) rectangle (4,5.5);
+    \fill  [blue!40] (2,7) rectangle (4.5,5.5);
     \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
-    \node at (3.25,5.875) {$\rvec{x}_k$, $\mat{P}_k$};
+    \node at (3.25,5.875) {$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};
 
@@
     \fill [lightgray]  (0.25,5) rectangle (6.25,4);
-    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_k, \rv{y}^3_k, \rv{x}^2_k\rv{y}_k, \dots , \rv{y}_k\}\rangle$};
+    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\rangle$};
 
@@
     \node at (3.25,-6.625) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (3.25,-7.125) {$\rvec{x}_k$, $\mat{P}_k$};
+    \node at (3.25,-7.125) {$\rvec{x}_{k|k}$, $\mat{P}_{k|k}$};
 \end{tikzpicture}
@@
 \end{figure}
-To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances $r_i=5$ metres.
+To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances set to $r_i=5$ simulation distance units.
 Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.

### 2020-10-15 main.tex
Added remark about implicit weight w=1 - also referenced the remark in the algorithm

@@
 
+\begin{rem} \label{rem:lcao_implicit_weight}
+    The construction of this scheme additionally supports the linear combination of the implicit weight, $\omega^{(t)}_j = 1$, by replacing
+    \begin{equation}
+        \mathcal{E}_{pk_0}(1)^{x^{(t)}_{i,j}} = (N+1)^{1}r_j^N \pmod{N^2}
+    \end{equation}
+    in \eqref{eqn:our_scheme_lin_comb} by
+    \begin{equation}
+        (N+1)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
+    \end{equation}
+    due to the removal of $r_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
+\end{rem}
+
 % 
@@
     \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator.
-Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}.
+Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}.
 This is described by Algorithm \ref{alg:measurement_info}.
@@
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
+    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
@@
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb} and \eqref{eqn:our_scheme_lin_comb} in the form above
+    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
@@
 Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme security, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements.
 This is possibly achieved by detecting changes in real measurements after reporting false measurements to the navigator.

### 2020-11-03 main.tex
Fixed tikz picture as per request

@@
     \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
-    \fill [lightgray] (3.375,3.375) rectangle (5.625,2.625);
-    \node at (4.5,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
-    \fill [lightgray] (0.875,3.375) rectangle (3.125,2.625);
-    \node at (2,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
+    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
+    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
 
@@
     % Outer adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.75);
+    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
     % Inner adversary rectangle
@@
     % Adversaries and challenger
-    \node at (3.25,3.25) {\Large$\mathcal{A}'$};
+    \node at (3.25,3) {\Large$\mathcal{A}'$};
     \node at (3.25,5.5) {\Large$\mathcal{A}$};
@@
     % Arrows
-    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO secure\\scheme};
-    \draw [-latex] (2,1.75) -- (2,2.75);
-
-    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO secure\\scheme};
+    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
+    \draw [-latex] (2,1.75) -- (2,2.5);
+
+    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
     \draw [-latex] (2,4.5) --(2,5);
 
-    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
+    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
     \draw [-latex] (4.5,5) -- (4.5,4.5);
@@
     \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
-    \draw [-latex] (4.5,2.75) -- (4.5,1.75);
+    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
 \end{tikzpicture}

### 2020-11-03 tikz_images/proof.tex
Completed a lot more changes - many wording consistencies - many equation numbering consistencies - many notation consistencies - some figures updated a little bit as well - etc... - 2 additions remain
Fixed tikz picture as per request

@@
     % Adversaries and challenger
-    \node at (3.25,3.25) {\LARGE$\mathcal{A}'$};
-    \node at (3.25,5.5) {\LARGE$\mathcal{A}$};
-    \node at (3.25,0.5) {\LARGE$\mathcal{C}$};
+    \node at (3.25,3) {\Large$\mathcal{A}'$};
+    \node at (3.25,5.5) {\Large$\mathcal{A}$};
+    \node at (3.25,0.5) {\Large$\mathcal{C}$};
 
     % Arrows
-    \node[text width=3cm, align=center] at (2,1.25) {Joye-Libert\\AO scheme};
-    \draw [-latex] (2,1.75) -- (2,2.75);
+    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
+    \draw [-latex] (2,1.75) -- (2,2.5);
 
-    \node[text width=3cm, align=center] at (2,4) {Our\\LCAO scheme};
+    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
     \draw [-latex] (2,4.5) --(2,5);
 
-    \node[text width=3cm, align=center] at (4.5,4) {``Break''\\Our scheme};
+    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
     \draw [-latex] (4.5,5) -- (4.5,4.5);

### 2020-11-04 main_automatica.tex
Initial switch to IEEE template (for Transactions on dependable and secure computing)

--- 2020-11-03 main.tex
@@
 \end{equation}
-where $\rv{z}'_{k,i}$ is the modified measurement, and noise $\rv{v}'_{k,i}$ is white and Gaussian.
-The approximation of $\rv{z}'_{k,i}$ and $\rv{r}_{k,i}$ from original measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be shown in Section \ref{subsec:range_measurement_mod}.
+where $\rv{z}'_{k,i}$ is the modified measurement, and noise $\rv{v}'_{k,i}$ is zero-mean with known variance.
+The approximation of $\rv{z}'_{k,i}$ and its noise variance $\rv{r}_{k,i}$ from original measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be shown in Section \ref{subsec:range_measurement_mod}.
 
@@
 \subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-In Section \ref{subsec:observation_model}, we assumed the existance of modified sensor measurements $\rv{z}'_{k,i}$ with white Gaussian noise and variances $\rv{r}_{k,i}$ in the modified measurement model \eqref{eqn:modified_measurement_model}.
+In Section \ref{subsec:observation_model}, we assumed the existance of a measurement model \eqref{eqn:modified_measurement_model} where modified sensor measurements $\rv{z}'_{k,i}$ had zero-mean noises with variances $\rv{r}_{k,i}$.
 In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
@@
 \end{equation}
-with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependant on the measurement function $h_i$ and no longer white or Gaussian.
-We can compute the mean of the new noise term (a function of white Gaussian term $\rv{v}_{k,i}$) as
+with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependant on the measurement function $h_i$ and no longer zero-mean or Gaussian.
+We can compute the mean of the new noise term (a function of the Gaussian term $\rv{v}_{k,i}$) as
 \begin{equation}
@@
 and is dependant on $h_i(\rvec{x}_k)$.
-We also wish to approximate this noise using values available to the sensor, $\rv{z}_{k,i}$ and $r_i$, while providing a conservative estimate of the true variance so as not to affect the convergence of the EIF.
-While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate in the case
+To use the modified measurement function \eqref{eqn:modified_measurement} with an EIF, we require an estimate of its noise variance using only the values available to the sensor, $\rv{z}_{k,i}$ and $r_i$.
+A conservative estimate of the variance (\textit{i.e.} a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
+While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate when
 \begin{equation}
@@
 \end{equation}
-which cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
+and cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
 Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
 \begin{equation}
-    \rv{r}_{k, i} = 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2\,. \label{eqn:modified_meaasurement_variance_estimate}
-\end{equation}
-
-In addition, we note that the distribution of noise in \eqref{eqn:modified_measurement} approaches a Gaussian when true ranges are sufficiently larger than measurement variances, as shown by
-\begin{equation}
-    \begin{split}
-        &r_i << h_i(\rvec{x}_k) \\
-        \implies &2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i} \\
-        \implies &\rv{v}'_{k,i} \approx 2h_i(\rvec{x}_k)\rv{v}_{k,i}\,,
-    \end{split} \label{eqn:modified_noise_approaches_gaussian}
-\end{equation}
-and conclude with the following assumption.
-\begin{assum} \label{assum:measurement_size}
-    Given property \eqref{eqn:modified_noise_approaches_gaussian}, and our $95\%$ confindence in the conservativness of variance estimates \eqref{eqn:modified_meaasurement_variance_estimate}, we assume that range measurements $\rv{z}_i$ are in general large enough to produce sufficiently Gaussian modified measurement noise $\rv{v}'_{k,i}$ and its variance estimated sufficiently conservative to be used in the EIF and measurement model \eqref{eqn:modified_measurement_model}.
-\end{assum}
+    \rv{r}_{k, i} = 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2\,. \label{eqn:modified_measurement_variance_estimate}
+\end{equation}
+Together, the model and variance, \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, provide a suitable substitute for the required measurement model \eqref{eqn:modified_measurement_model} and can be used to achieve the desired linear properties using only the available range sensors.
 
@@
     \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
-    \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_meaasurement_variance_estimate}
+    \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_measurement_variance_estimate}
 
@@
 \end{equation}
-From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_meaasurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
+From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
 \begin{thm}
@@
 
-Recalling Assumption \ref{assum:measurement_size}, modified measurement noise resembles a Gaussian distribution when measurements are sufficiently large.
-We considered $4$ layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
+Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements.
+We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
 The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
@@
 \end{figure}
-From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification in Section \ref{subsec:range_measurement_mod} has almost no effect on the performance when compared to a normal EIF filter.
-The robustness of the privacy-preserving method is likely due to the rationality of Assumption \ref{assum:measurement_size}, the relative size of measurements to the sensor variances in our simulations, and the sufficiently large fractional precision.
+From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter.
+The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter.
 
@@
 Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
-Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.
+Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the application of LCAO secure schemes to alternative measurement models and the exploring of implications behind an active sensor attacker model.
 

### 2020-11-05 main.tex
Continued with template matching Cleaned text from template comments and many grammarly errors

@@
-% autosam.tex
-% Annotated sample file for the preparation of LaTeX files
-% for the final versions of papers submitted to or accepted for 
-% publication in AUTOMATICA.
-
-% See also the Information for Authors.
-
-% Make sure that the zip file that you send contains all the 
-% files, including the files for the figures and the bib file.
-
-% Output produced with the elsart style file does not imitate the
-% AUTOMATICA style. The style file is generic for all Elsevier
-% journals and the output is laid out for easy copy editing. The
-% final document is produced from the source file in the
-% AUTOMATICA style at Elsevier.
-
-% You may use the style file autart.cls to obtain a two-column 
-% document (see below) that more or less imitates the printed 
-% Automatica style. This may helpful to improve the formatting 
-% of the equations, tables and figures, and also serves to check 
-% whether the paper satisfies the length requirements.
-
-% Please note: Authors must not create their own macros.
-
-% For further information regarding the preparation of LaTeX files 
-% for Elsevier, please refer to the "Full Instructions to Authors" 
-% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
-% directory pub/styles, or from the internet (CTAN sites) on
-% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
-% tex-archive/macros/latex/contrib/supported/elsevier.
-
-% The use of LaTeX2e is preferred.
-%\documentclass{elsart}
-
-% Enable this line and disable the 
-% preceding line to obtain a two-column 
-% document whose style resembles the
-% printed Automatica style.
-\documentclass[twocolumn]{autart}
-
-% Include this line if your 
-% document contains figures,
-\usepackage{graphicx}
-% or this line, depending on which
-% you prefer.
-%\usepackage[dvips]{epsfig}
-
-% User imported packages
+%% bare_jrnl_compsoc.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% Computer Society journal paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+\else
+  \usepackage[dvips]{graphicx}
+\fi
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% 
+% 8888888 888b     d888 8888888b.   .d88888b.  8888888b. 88888888888 .d8888b.  
+%   888   8888b   d8888 888   Y88b d88P" "Y88b 888   Y88b    888    d88P  Y88b 
+%   888   88888b.d88888 888    888 888     888 888    888    888    Y88b.      
+%   888   888Y88888P888 888   d88P 888     888 888   d88P    888     "Y888b.   
+%   888   888 Y888P 888 8888888P"  888     888 8888888P"     888        "Y88b. 
+%   888   888  Y8P  888 888        888     888 888 T88b      888          "888 
+%   888   888   "   888 888        Y88b. .d88P 888  T88b     888    Y88b  d88P 
+% 8888888 888       888 888         "Y88888P"  888   T88b    888     "Y8888P"  
+%                                                                              
+%                                                                              
+%                                                                              
+%
+
+% Graphics
+\usepackage{tikz}
+% Maths
 \usepackage{amsmath}
 \usepackage{amsfonts}
+\usepackage{amsthm}
 \usepackage{mathtools}
+% Algorithms
 \usepackage{algorithm}
 \usepackage{algpseudocode}
-\usepackage{tikz}
-
-% Local packages
+% Local
 \usepackage{ISASmacros/isasmathmacros}
+% Equal last columns
+\usepackage{flushend}
+
+% Environments
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+
+\theoremstyle{definition}
+\newtheorem{theorem}{Theorem}[section]
+
+\theoremstyle{remark}
+\newtheorem*{remark}{Remark}
 
@@
 
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
 \begin{document}
-
-\begin{frontmatter}
-% Running title for regular 
-% papers but only if the title  
-% is over 5 words. Running title 
-% is not shown in output.
-%\runtitle{Insert a suggested running title}
-
-% Title, preferably not more than 10 words.
-\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation\thanksref{footnoteinfo}}
-
-\thanks[footnoteinfo]{This paper was not presented at any IFAC 
-meeting. Corresponding author Uwe~D.~Hanebeck. Tel. +49--721--608--43909.}
-
-% Add the 
-% e-mail address 
-% (ead) as shown
-\author[ISAS]{Marko Ristic}\ead{marko.ristic@kit.edu},
-\author[ISAS]{Benjamin Noack}\ead{noack@kit.edu},
-\author[ISAS]{Uwe D. Hanebeck}\ead{uwe.hanebeck@kit.edu}
-
-% Please supply
-\address[ISAS]{Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany}
-
-% Five to ten keywords,  
-% chosen from the IFAC 
-% keyword list or with the 
-% help of the Automatica 
-% keyword wizard
-\begin{keyword}
-System state estimation; Data privacy; Sensor fusion; Kalman filters.
-\end{keyword}
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation}
+%
+%
+% author names and IEEE memberships
+% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
+% a structure at a ~ so this keeps an author's name from being broken across
+% two lines.
+% use \thanks{} to gain access to the first footnote area
+% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
+% was not built to handle multiple paragraphs
+
+\author{Marko~Ristic,
+        Benjamin~Noack,~\IEEEmembership{Member,~IEEE,}
+        and~Uwe~D.~Hanebeck,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
+\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M.
+Ristic, B.
+Noack and U.
+D.
+Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany.\protect\\
+% note need leading \protect in front of \\ to get a newline within \thanks as
+% \\ is fragile and will error, could use \hfil\break instead.
+E-mail: marko.ristic@kit.edu}% <-this % stops an unwanted space
+}
 
@@
 
-% Abstract of not more than 200 words.
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+\IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 
-\end{frontmatter}
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+State Estimation, Data Privacy, Sensor Fusion, Kalman Filters.
+\end{IEEEkeywords}}
+
+% make the title area
+\maketitle
+
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
+\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
@@
 
-\section{Introduction}
-Localisation methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
+\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+% Computer Society journal (but not conference!) papers do something unusual
+% with the very first section heading (almost always called "Introduction").
+% They place it ABOVE the main text! IEEEtran.cls does not automatically do
+% this for you, but you can achieve this effect with the provided
+% \IEEEraisesectionheading{} command. Note the need to keep any \label that
+% is to refer to the section immediately after \section in the above as
+% \IEEEraisesectionheading puts \section within a raised box.
+
+\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
 Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
@@
 The most common methods for ensuring privacy during aggregation required for signal processing tasks have been described below.
-\begin{description}
+\begin{LaTeXdescription}
     \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
@@
 The aggregation operation in these schemes is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sum or mean calculation \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
-\end{description}
+\end{LaTeXdescription}
 In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
 These methods have been broadly grouped into two domains and described below.
-\begin{description}
+\begin{LaTeXdescription}
     \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
@@
 However, these works are relatively restricted in application due to the limited operations provided.
-\end{description}
+\end{LaTeXdescription}
 Lastly, recent developments in encryption schemes have presented some novel methods also suitable for privacy-preserving computation in distributed environments.
-\begin{description}
+\begin{LaTeXdescription}
     \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
@@
 While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
-\end{description}
+\end{LaTeXdescription}
 Of the aforementioned encryption schemes, some have found uses in privacy-preserving localisation and estimation tasks and we summarise these in the next section.
@@
 
-\begin{rem}
+\begin{remark}
     From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
-\end{rem}
+\end{remark}
 
@@
 Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
-\begin{description}
+\begin{LaTeXdescription}
     \item[Global navigator broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required.
@@
 We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
-\end{description}
+\end{LaTeXdescription}
 \begin{figure}[htbp]
@@
 The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}.
-\begin{defn}
+\begin{definition}
 An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
@@
 The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
-\end{defn}
+\end{definition}
 Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
-\begin{defn}
+\begin{definition}
 An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
@@
 The formal security game for AO has been given in Appendix \ref{app:ao}.
-\end{defn}
+\end{definition}
 
@@
 This can be summarised by the two informal security notions:
-\begin{description}
+\begin{LaTeXdescription}
     \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
@@
 Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$.
-\end{description}
-
-\begin{rem} \label{rem:lcao_leakage}
+\end{LaTeXdescription}
+
+\begin{remark} \label{rem:lcao_leakage}
     The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
@@
 We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
-\end{rem}
+\end{remark}
 
@@
 
-\begin{description}
+\begin{LaTeXdescription}
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
@@
     \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
-\end{description}
+\end{LaTeXdescription}
 
@@
 
-\begin{description}
+\begin{LaTeXdescription}
     \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
     \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
-    \begin{enumerate}
+    \begin{LaTeXenumerate}
         \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
@@
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{enumerate} 
+    \end{LaTeXenumerate} 
     \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game.
@@
     \end{equation*} 
-\end{description}
-
-\begin{defn}
+\end{LaTeXdescription}
+
+\begin{definition}
     An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game.
 Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
-\end{defn}
+\end{definition}
 
@@
 
-\begin{description}
+\begin{LaTeXdescription}
     \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
@@
     for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
-\end{description}
+\end{LaTeXdescription}
 
@@
 
-\begin{rem} \label{rem:lcao_implicit_weight}
+\begin{remark} \label{rem:lcao_implicit_weight}
     The construction of this scheme additionally supports the linear combination of the implicit weight, $\omega^{(t)}_j = 1$, by replacing
@@
     due to the removal of $r_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
-\end{rem}
+\end{remark}
 
@@
 
-\begin{pf}
+\begin{proof}
     Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}.
 The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
-    \begin{description}
+    \begin{LaTeXdescription}
         \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
         \item[Queries] Handle queries from $\mathcal{A}$:
-        \begin{description}
+        \begin{LaTeXdescription}
             \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
@@
             \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
-        \end{description}
+        \end{LaTeXdescription}
         \item[Challenge] When $\mathcal{A}$ submits challenge series
@@
         \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
-    \end{description}
+    \end{LaTeXdescription}
 
@@
     \end{equation*}
-    for security parameter $\kappa$. \qed
-\end{pf}
+    for security parameter $\kappa$.
+\end{proof}
 
@@
 for aggregation in row $i$ and column $j$, with $b=0$ for aggregations in $\rvec{i}'_{k,i}$ and $b=1$ otherwise.
-\begin{rem}
+\begin{remark}
     The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localisation, but can be similarly extended to the three-dimensional case.
@@
 This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
-\end{rem}
+\end{remark}
 
@@
 The privacy-preserving localisation filter can be described by the following steps.
-\begin{description}
+\begin{LaTeXdescription}
     \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
@@
 This is shown in Algorithm \ref{alg:nav_update}.
-\end{description}
+\end{LaTeXdescription}
 
@@
 \end{equation}
-From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_meaasurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
-\begin{thm}
+From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
+\begin{theorem}
     In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localisation_leakage}.
-\end{thm}
+\end{theorem}
 
@@
 
-Recalling Assumption \ref{assum:measurement_size}, modified measurement noise resembles a Gaussian distribution when measurements are sufficiently large.
-We considered $4$ layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
+Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements.
+We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
 The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
 \begin{figure}[htbp]
-\begin{center}
+\centering
 \includegraphics{images/layouts.pdf}
-\end{center}
 \caption{The considered layouts.}
@@
 \begin{figure}[htbp]
-\begin{center}
+\centering
 \includegraphics{images/layout_errors.pdf}
-\end{center}
 \caption{Filter error for different layouts.}
@@
 \begin{figure}[htbp]
-\begin{center}
+\centering
 \includegraphics{images/timing.pdf}
-\end{center}
 \caption{Runtimes for varying key sizes and numbers of sensors.}
@@
 Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
-Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the relaxing of the Gaussian modified noise assumption and the exploring of implications behind an active sensor attacker model.
-
-% Place acknowledgements
-% here.
-\begin{ack}                               
-Partially supported by ZIM \dots
-\end{ack}
-
-% Include this if you use bibtex 
-% and a bib file to produce the 
-% bibliography (preferred). The
-% correct style is generated by
-% Elsevier at the time of printing.
-\bibliographystyle{unsrt}
-\bibliography{BibTeX/PrivateEIFLocalisation}
-
-% Each appendix must have a short title.
-% Sections and subsections are supported
-% in the appendices.
-\appendix
+Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the application of LCAO secure schemes to alternative measurement models and the exploring of implications behind an active sensor attacker model.
+
+% if have a single appendix:
+%\appendix[Proof of the Zonklar Equations]
+% or
+%\appendix  % for no appendix heading
+% do not use \section anymore after \appendix, only \section*
+% is possibly needed
+
+% use appendices with more than one appendix
+% then use \section to start each appendix
+% you must declare a \section before using any
+% \subsection or using \label (\appendices by itself
+% starts a section numbered zero.)
+%
+
+\appendices
 % 
@@
 A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
-\begin{description}
+\begin{LaTeXdescription}
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
@@
     \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
-\end{description}
+\end{LaTeXdescription}
 
 The security game between attacker and challenger for IND-CPA security is given by
-\begin{description}
+\begin{LaTeXdescription}
     \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public key $pk$ to the attacker
@@
     \end{equation*} 
-\end{description}
+\end{LaTeXdescription}
 
@@
 An aggregator oblivious encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{AggDec})$, defined as
-\begin{description}
+\begin{LaTeXdescription}
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
@@
     \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
-\end{description}
+\end{LaTeXdescription}
 
 The security game between attacker and challenger for AO security is given by
-\begin{description}
+\begin{LaTeXdescription}
     \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
     \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
-    \begin{enumerate}
+    \begin{LaTeXenumerate}
         \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_i)$ and $(i',t',x^{\prime(t')}_{i'}$, the following condition holds:
@@
     \end{equation*} 
-\end{description}
-
+\end{LaTeXdescription}
+
+% use section* for acknowledgement
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+Partially supported by ZIM \dots
+
+% Can use something like this to put references on a page
+% by themselves when using endfloat and the captionsoff option.
+\ifCLASSOPTIONcaptionsoff
+  \newpage
+\fi
+
+\bibliographystyle{IEEEtran}
+\bibliography{BibTeX/PrivateEIFLocalisation}
+
+% that's all folks
 \end{document}

### 2020-11-06 main.tex
Another change of template ... not for the Transactions on Automatic Control (template not found so very default IEEEtran used) Updated template folder with the latest IEEEtran files

@@
-%% bare_jrnl_compsoc.tex
+%% bare_jrnl.tex
 %% V1.4b
@@
 %% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
+%% see http://www.michaelshell.org/
 %% for current contact information.
@@
 %% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% Computer Society journal paper.
+%% journal paper.
 %%
@@
 
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
-  \usepackage{cite}
-\fi
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-\else
-  \usepackage[dvips]{graphicx}
-\fi
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+\documentclass[10pt,letterpaper,oneside,twocolumn,journal]{IEEEtran}
 
@@
 % paper title
-% Titles are generally capitalized except for words such as a, an, and, as,
-% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
-% not capitalized unless they are the first or last word of the title.
-% Linebreaks \\ can be used within to get better formatting as desired.
-% Do not put math or special symbols in the title.
 \title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation}
@@
 % author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-
 \author{Marko~Ristic,
@@
         and~Uwe~D.~Hanebeck,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
-\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem M.
+\thanks{M.
 Ristic, B.
@@
 D.
-Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany.\protect\\
-% note need leading \protect in front of \\ to get a newline within \thanks as
-% \\ is fragile and will error, could use \hfil\break instead.
-E-mail: marko.ristic@kit.edu}% <-this % stops an unwanted space
-}
+Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany.
+e-mail: marko.ristic@kit.edu}}% <-this % stops a space
+% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
+
+% The paper headers
+% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
+
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark.
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
+\maketitle
 
@@
 
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
 % As a general rule, do not put math, special symbols or citations
 % in the abstract or keywords.
-\IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 State Estimation, Data Privacy, Sensor Fusion, Kalman Filters.
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
+\end{IEEEkeywords}
+
 % For peerreview papers, this IEEEtran command inserts a page break and
@@
 
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-% Computer Society journal (but not conference!) papers do something unusual
-% with the very first section heading (almost always called "Introduction").
-% They place it ABOVE the main text! IEEEtran.cls does not automatically do
-% this for you, but you can achieve this effect with the provided
-% \IEEEraisesectionheading{} command. Note the need to keep any \label that
-% is to refer to the section immediately after \section in the above as
-% \IEEEraisesectionheading puts \section within a raised box.
-
+\section{Introduction}
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
@@
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-\appendices
 % 
@@
 
+\appendices
 \section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
@@
 
-% use section* for acknowledgement
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
-  \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
+% use section* for acknowledgment
 \section*{Acknowledgment}
-\fi
 

### 2020-11-09 main.tex
Small typo in equation
First pass-through for new symbols (making characters more unique across the work as requested) Also added some re-definitions for lambda and kappa as these were not clear Made a bunch of brackets and vertical bars use left/right/middle to be sized properly Fixed up the text in the Algorithms a tiny bit Changed rational definitions equations a little (equivalent but easier to read)

@@
 
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
+% If you want to put a publisher's ID mark on the page you can do it like this:
 %\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
@@
 Throughout this work, we will use the following notation.
-Lowercase characters are scalars, $a$, vectors are underlined, $\vec{a}$, and random variables are bold, $\rv{a}$.
+Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$.
 Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
@@
 The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
-That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
+That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
 This has been summarised in Figure \ref{fig:agg_steps}.
@@
     \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
-    \node at (1.625,1.125) {$\displaystyle y_1^{(t)} \!=\! \sum^m_{j=1}x_{1,j}^{(t)}\omega_j^{(t)}$};
+    \node at (1.625,1.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
     \node at (5,0.375) {Sensor $n$};
     \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
-    \node at (5,1.125) {$\displaystyle y_n^{(t)} \!=\! \sum^m_{j=1}x_{n,j}^{(t)}\omega_j^{(t)}$};
+    \node at (5,1.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
     \fill [black] (3.5,1.125) circle (0.05);
@@
     \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
-    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} x_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}y^{(t)}_{i}$};
+    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
     % Sensors
@@
     \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
-    \node at (2,-4) {$y_1^{(t)}$};
+    \node at (2,-4) {$l_1^{(t)}$};
     \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
-    \node at (4.625,-4) {$y_n^{(t)}$};
+    \node at (4.625,-4) {$l_n^{(t)}$};
 
@@
 \begin{remark}
-    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} x_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $x_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
+    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
@@
 
-Encryption of a plaintext message $m \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
-\begin{equation}
-    c = g^m r^N \pmod{N^2}
-\end{equation}
-for a randomly chosen $r \in \mathbb{Z}_{N}$.
-$r^N$ can be considered the noise term which hides the value $g^m \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
+Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
+\begin{equation}
+    c = g^a \rho^N \pmod{N^2}
+\end{equation}
+for a randomly chosen $\rho \in \mathbb{Z}_{N}$.
+$\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
 The decryption of a ciphertext is computed by
 \begin{equation}
-    m = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
+    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
 \end{equation}
@@
 
-In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall m_1,m_2 \in \mathbb{Z}_N$,
+In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
 \begin{align}
-    \mathcal{D}(\mathcal{E}(m_1)\mathcal{E}(m_2) \hspace{-7pt} \pmod{N^2}) &= m_1+m_2 \hspace{-7pt} \pmod{N} \\
-    \mathcal{D}(\mathcal{E}(m_1)g^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1+m_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
-    \mathcal{D}(\mathcal{E}(m_1)^{m_2} \hspace{-7pt} \pmod{N^2}) &= m_1m_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
+    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N} \\
+    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
+    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
 \end{align}
@@
 
-Encryption of plaintext $m^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
-\begin{equation}
-    c^{(t)}_{i} = (N+1)^{m^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
-\end{equation}
-where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{m^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
+Encryption of plaintext $a^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
+\begin{equation}
+    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
+\end{equation}
+where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
 
@@
 \begin{equation}
-    \sum^{n}_{i=1}m^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
+    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
 \end{equation}
@@
         &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
-        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{m_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
-        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{m_{i,t}} \pmod{N^2} \\
-        \equiv &(N+1)^{\sum^n_{i=1}m_{i,t}} \pmod{N^2}
+        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
+        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
+        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}
     \end{split}
@@
     \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $x^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $y_i$ from the current and previous instances.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$.
+    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
+Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{LaTeXdescription}
@@
 Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}x^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $x^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
 \end{remark}
@@
 We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-These are used by a trusted third party, an aggregator and value producing users $i\,1\leq i \leq n$.
+These are used by a trusted third party, an aggregator and value producing users $i,\,1\leq i \leq n$.
 They are defined as follows
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
-    \item[$\mathsf{Enc}(pk_0, a)$] The aggregator and users can encrypt any value $a$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(a)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $y^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}y_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} x^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value $x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{LaTeXdescription}
@@
 \begin{LaTeXdescription}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
+    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
     \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
     \begin{LaTeXenumerate}
-        \item \textit{Encryption:} The attacker chooses a value $a$ and computes an encryption of $a$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(a)$.
+        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
         \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
-        \end{equation*}
-        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
+        \begin{equation*}
+            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
+        \end{equation*}
+        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
@@
     \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
+        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
     \end{equation*}
@@
     \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
+        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
     \end{equation*}
@@
     \begin{equation*}
-        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
+        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
     \end{equation*}
@@
     \begin{equation*}
-        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in S\rangle\,.
+        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
     \end{equation*}
@@
 \begin{definition}
-    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter, has more than a negligible advantage in winning the above security game.
+    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
 Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
@@
 
-    \item[$\mathsf{Enc}(pk_0, a)$] Encryption of values is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
-    \begin{equation}
-        \mathcal{E}_{pk_0}(a) = (N+1)^{a}r^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
-    \end{equation}
-    for a randomly chosen $r \in \mathbb{Z}_N$.
-
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
-    \begin{equation}
-        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
+    \item[$\mathsf{Enc}(pk_0, x)$] Encryption of values is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
+    \begin{equation}
+        \mathcal{E}_{pk_0}(a) = (N+1)^{x}\rho^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
+    \end{equation}
+    for a randomly chosen $\rho \in \mathbb{Z}_N$.
+
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
+    \begin{equation}
+        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
     \end{equation}
@@
         \begin{split}
-             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
-            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
+             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
+            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
+            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
+            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
         \end{split}
     \end{equation*}
-    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
-Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
-
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] Aggregation is computed as $y^{(t)} = \prod^n_{i=1}y^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
+    for some values $\rho_i,\rho_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
+Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
+
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
     \begin{equation}
         \begin{split}
-            \sum^{n}_{i=1}\sum^{m}_{j=1}&x^{(t)}_{i,j}\omega^{(t)}_j =\\
-            &\frac{L((y^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,.
+            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(t)}_{i,j}\omega^{(t)}_j =\\
+            &\frac{L((l^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
         \end{split} \label{eqn:our_scheme_decrypt}
     \end{equation}
-    The correctness of aggregation can be seen from
+    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of aggregation can be seen from
     \begin{align*}
-        y^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x_{i,j}\omega_j}r_i^N \pmod{N^2} \\
+        l^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a_{i,j}\omega_j}\rho_i^N \pmod{N^2} \\
         \begin{split}
             &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r_i^N \pmod{N^2}
+            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho_i^N \pmod{N^2}
         \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r'^N \pmod{N^2}\,,
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho'^N \pmod{N^2}\,,
     \end{align*}
-    for some values $r_i,r' \in \mathbb{Z}_N,\,1\leq i \leq n$.
+    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,1\leq i \leq n$.
 \end{LaTeXdescription}
 
-Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $x^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.
+Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.
 
@@
     \begin{equation}
-        \mathcal{E}_{pk_0}(1)^{x^{(t)}_{i,j}} = (N+1)^{1}r_j^N \pmod{N^2}
+        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
     \end{equation}
@@
     \begin{equation}
-        (N+1)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
-    \end{equation}
-    due to the removal of $r_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
+        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,,
+    \end{equation}
+    due to the removal of $\rho_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
 \end{remark}
@@
 To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
-From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA.
+From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme and therefore meet security notion IND-CPA.
 We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.
@@
 \end{equation*}
-for some negligible functions $\eta_1$ and $\eta_2$.
+for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
 (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof.
@@
         \begin{LaTeXdescription}
-            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $r_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
-            \begin{equation*}
-                (N+1)^{\omega^{(t)}_{j}}r_j^N\pmod{N^2},\,1\leq j\leq m
+            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
+            \begin{equation*}
+                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
             \end{equation*}
             to $\mathcal{A}$.
-            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
-The received response will be of the form $(N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $r^N$ for a random $r \in \mathbb{Z}_N$ and return
-            \begin{equation*}
-                (N+1)^{\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j}r^N H(t)^{sk_i} \pmod{N^2}
+            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
+The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return
+            \begin{equation*}
+                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
             \end{equation*}
@@
         \begin{equation*}
-            \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
+            \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
         \end{equation*}
@@
         \begin{equation*}
-            \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
+            \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
         \end{equation*}
@@
         \begin{equation*}
-            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle
+            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle
         \end{equation*}
@@
         \begin{equation*}
-            \langle(i,t^*,\sum^m_{j=1}x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j)\,|\,i \in S\rangle\,,
+            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle\,,
         \end{equation*}
@@
         \begin{equation*}
-            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,|\,i\in U\rangle\,,
-        \end{equation*}
-        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return
-        \begin{equation*}
-            \langle(N+1)^{\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}r_i^N H(t^*)^{sk_i}\,|\,i\in U\rangle
+            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle\,,
+        \end{equation*}
+        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
+        \begin{equation*}
+            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
         \end{equation*}
@@
 \subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
-In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{x \,|\, x \in \mathbb{Z}_N\}$.
+In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$.
 For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing.
@@
 
-We define a subset of rational numbers in terms of a range $r \in \mathbb{N}$ and fractional precision $f \in \mathbb{N}$.
+We define a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$.
 This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
-Rational subset $\mathbb{Q}_{r,f}$ is given by
-\begin{equation}
-    \mathbb{Q}_{r,f} = \left\{q \,|\, f^{-1}\ \textsf{divides}\ q \wedge -\left\lfloor\frac{r}{2}\right\rfloor \leq q < \left\lfloor\frac{r}{2}\right\rfloor \right\}\,,
-\end{equation}
-and we quantise any real number $x$ by taking the nearest rational $q \in \mathbb{Q}_{r,f}$.
-That is, $\argmin_{q\in\mathbb{Q}_{r,f}} |x-q|$.
-In this form, mapping rationals $\mathbb{Q}_{r,f}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $r=N$, and handling negatives with modulo arithmetic.
-In addition, we note that the Q number format requires a precision factor $f$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
-This is captured by a third parameter $m$; the number of multiplication factors to add or remove from encodings.
-
-The function for combined quantisation and encoding $\mathsf{E}_{r,f,m}(x)$, of a given a real number $x \in \mathbb{R}$, integer range $\mathbb{Z}_r$, and the desired scaling for $m$ prior encoded multiplications, is given by
-\begin{equation}
-    \mathsf{E}_{r,f,m}(x) = \left\lfloor f^{m+1} x \right\rceil \pmod{r}\,. \label{eqn:encode}
-\end{equation}
-Decoding of an integer $e \in \mathbb{Z}_r$, is given by
-\begin{equation}
-    \mathsf{E}^{-1}_{r,f,m}(e) \!=\! 
+Rational subset $\mathbb{Q}_{M,\phi}$ is given by
+\begin{equation}
+    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
+\end{equation}
+and we quantise any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
+That is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
+In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $M=N$, and handling negatives with modulo arithmetic.
+In addition, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
+This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.
+
+The function for combined quantisation and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given a real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+\begin{equation}
+    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
+\end{equation}
+Decoding of an integer $u \in \mathbb{Z}_M$, is given by
+\begin{equation}
+    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
     \begin{dcases}
-        \frac{e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &e\hspace{-8pt}\pmod{r} \leq \left\lfloor\frac{r}{2}\right\rfloor \\
-        -\frac{r - e\hspace{-8pt}\pmod{r}}{f^{m+1}}, &\text{otherwise} \\
+        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
+        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
     \end{dcases}.\label{eqn:decode}
@@
     \begin{split}
-        \mathsf{E}_{r,f,m}(a_1) + \mathsf{E}_{r,f,m}(a_2)& \pmod{r} =\\
-        &\mathsf{E}_{r,f,m}(a_1+a_2)
+        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
+        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
     \end{split}\label{eqn:encoding_homomorphic_add}
@@
     \begin{split}
-        \mathsf{E}_{r,f,m}(a_1)\mathsf{E}_{r,f,m}(a_2)& \pmod{r} =\\
-        &\mathsf{E}_{r,f,m+1}(a_1a_2)\,,
+        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
+        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
     \end{split}
 \end{equation}
-noting that when $r=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
-
-The choice of a high fractional precision $f$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
-Given the largest number of expected multiplications $m_{max}$, and the largest expected decoded value $x$, the parameter should be chosen such that the following condition holds
-\begin{equation}
-    \left|f^{m_{max}+1}x\right| < \left\lfloor \frac{r}{2} \right\rfloor\,.
-\end{equation}
-In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $r=N$.
+noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
+
+The choice of a high fractional precision $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
+Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a$, the parameter should be chosen such that the following condition holds
+\begin{equation}
+    \left|\phi^{d_{max}+1}a\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
+\end{equation}
+In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.
 
@@
 From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependant only on weights from the original matrices.
-For example, consider dimension $N\times N$ matrices $\mat{A}$ and $\mat{B}$, where element $(i,j)$ in matrix $\mat{A}$ is of the form $\sum_{l=0}^M w_{l,i,j}a_{l,i,j}$ and similarly for matrix $\mat{B}$, the form $\sum_{l=0}^M v_{l,i,j}b_{l,i,j}$.
-If we consider $w_{l,i,j}$ and $v_{l,i,j}$ as the weight terms, we can write element $(i,j)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependant only on these weights, as
+For example, consider dimension $D\times D$ matrices $\mat{A}$ and $\mat{B}$, where element $(v,w)$ in matrix $\mat{A}$ is of the form $\sum_{i=0}^W a_{i,v,w}x_{i,v,w}$ and similarly for matrix $\mat{B}$, the form $\sum_{i=0}^W b_{i,v,w}y_{i,v,w}$.
+If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependant only on these weights, as
 \begin{equation}
     \begin{split}
-        \sum_{l=0}^N&\left(\left(\sum_{m=0}^M w_{m,i,j}a_{m,i,l}\right)\left(\sum_{m=0}^Mv_{m,i,j}b_{m,l,j}\right)\right) \\
-        &=\sum_{l=0}^N\left(\sum_{m=0}^M\sum_{n=0}^M w_{m,i,l}a_{m,i,l}v_{n,l,j}b_{n,l,j}\right) \\
-        &=\sum_{l=0}^N\sum_{m=0}^M\sum_{n=0}^M (w_{m,i,l}v_{n,l,j})a_{m,i,l}b_{n,l,j}\,.
+        \sum_{d=0}^D&\left(\left(\sum_{i=0}^W a_{i,v,d}x_{i,v,d}\right)\left(\sum_{i=0}^W b_{i,d,w}y_{i,d,w}\right)\right) \\
+        &=\sum_{d=0}^N\left(\sum_{i=0}^W\sum_{j=0}^W a_{i,v,d}x_{i,v,d}b_{j,d,w}y_{j,d,w}\right) \\
+        &=\sum_{d=0}^N\sum_{i=0}^W\sum_{j=0}^W (a_{i,v,d}b_{j,d,w})x_{i,v,d}y_{j,d,w}\,.
     \end{split} \label{eqn:matrix_mult_weights}
@@
 Similarly, scalar multiplication also holds this property.
-It is therefore sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
+It is, therefore, sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
 Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.
@@
         \begin{bmatrix}
-            \alpha_{11} & \alpha_{12} \\
-            \alpha_{21} & \alpha_{22}
+            \beta_{11} & \beta_{12} \\
+            \beta_{21} & \beta_{22}
         \end{bmatrix}\,,
@@
 \begin{align*}
-    \alpha_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
+    \beta_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
     \begin{split}
-        \alpha_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
+        \beta_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
         &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
     \end{split}\\
-    \alpha_{21} &= \alpha_{12} \\
-    \alpha_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
+    \beta_{21} &= \beta_{12} \\
+    \beta_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
 \end{align*}
@@
 \begin{equation}
-    t=k\mathbin\|i\mathbin\|j\mathbin\|b
-\end{equation}
-for aggregation in row $i$ and column $j$, with $b=0$ for aggregations in $\rvec{i}'_{k,i}$ and $b=1$ otherwise.
+    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau
+\end{equation}
+for aggregation in row $v$ and column $w$, with $\tau=0$ for aggregations in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.
 \begin{remark}
@@
 \begin{LaTeXdescription}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
-Additionally, we assume that fractional precision $f$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
-We will thus simplify the encoding notation $\mathsf{E}_{N,f,m}(\cdot)$ to $\mathsf{E}_{m}(\cdot)$.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
+Additionally, we assume that fractional precision $\phi$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
+We will thus simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
 
@@
     \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator.
-Care must be taken when encoding during homomorphic operations to ensure fractional factor $m$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}.
+Care must be taken when encoding during homomorphic operations to ensure fractional factor $d$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}.
 This is described by Algorithm \ref{alg:measurement_info}.
@@
 
-        \For{$\rv{\omega}$ in \eqref{eqn:weights_to_broadcast}} 
-            \State Compute $\mathsf{E}_{0}(\rv{\omega})$ by \eqref{eqn:encode}
-            \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ by \eqref{eqn:our_scheme_encrypt}
-            \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{\omega}))$ to sensors
+    \State Compute $\mathsf{E}_{0}(\rv{x}^3_{k|k-1})$ by \eqref{eqn:encode}
+    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
+    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ to sensors
+    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}} 
+        \State Broadcast weight in the form above
     \EndFor
@@
 
-    \While{Navigator broadcasting}
     \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$
-    \State Recieve remaining weights in the form above
-    \EndWhile
-
-    \State Let $\beta_{v1}^{(i)}$ represent an encryption of element $(v,1)$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
+    \For{Remaining weights in \eqref{eqn:weights_to_broadcast}}
+        \State Recieve weight in the form above
+    \EndFor
+
+    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
+    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
@@
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\beta_{21}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
-        \State Send $\beta_{v1}$ to the navigator
+        \State Send $\alpha_{v}$ to the navigator
     \EndFor
 
-    \State Let $\alpha_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\alpha_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
+    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
+    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
@@
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\alpha_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
         \For{$w \gets 1$ to $2$} 
-            \State Send $\alpha_{vw}^{(i)}$ to the navigator
+            \State Send $\beta_{vw}^{(i)}$ to the navigator
         \EndFor
@@
     \For{$v \gets 1$ to $2$}
-        \State Receive $\beta_{v1}^{(i)}$ from each sensor $1\leq i \leq n$
+        \State Receive $\alpha_{v}^{(i)}$ from each sensor $1\leq i \leq n$
     \EndFor
@@
         \For{$w \gets 1$ to $2$}
-        \State Receive $\alpha_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
+        \State Receive $\beta_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
         \EndFor
@@
 
-    \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
+    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
     \For{$v \gets 1$ to $2$}
-        \State $\beta_{v1} \gets \prod_{i=1}^n\beta_{v1}^{(i)}$
-        \State Compute $\mathcal{D}_{sk_0}(\beta_{v1})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{v1}))$ by \eqref{eqn:decode}
+        \State $\alpha_{v} \gets \prod_{i=1}^n\alpha_{v}^{(i)}$
+        \State Compute $\mathcal{D}_{sk_0}(\alpha_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{v}))$ by \eqref{eqn:decode}
     \EndFor
@@
 
-    \State Let $\alpha_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
+    \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
     \For{$v \gets 1$ to $2$}
         \For{$w \gets 1$ to $2$}
-            \State $\alpha_{vw} \gets \prod_{i=1}^n\alpha_{vw}^{(i)}$
-            \State Compute $\mathcal{D}_{sk_0}(\alpha_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{vw}))$ by \eqref{eqn:decode}
+            \State $\beta_{vw} \gets \prod_{i=1}^n\beta_{vw}^{(i)}$
+            \State Compute $\mathcal{D}_{sk_0}(\beta_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{vw}))$ by \eqref{eqn:decode}
         \EndFor
@@
 To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances set to $r_i=5$ simulation distance units.
-Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $f$, thus, $f=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
+Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
 The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
-    \item[$\mathsf{Enc}(pk, x)$] Encryption of value $x$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(x)$.
-    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(x))$] Decryption of value $x$ is computable using the secret key $sk$.
+    \item[$\mathsf{Enc}(pk, a)$] Encryption of value $a$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(a)$.
+    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(a))$] Decryption of value $a$ is computable using the secret key $sk$.
 \end{LaTeXdescription}
@@
 \begin{LaTeXdescription}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public key $pk$ to the attacker
+    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives public key $pk$ to the attacker
     \item[Encryptions] The attacker may compute encryptions using the public key $pk$.
@@
     \begin{equation*}
-        x^{(0)} \text{ and } x^{(1)}
+        a^{(0)} \text{ and } a^{(1)}
     \end{equation*}
@@
     \begin{equation*}
-        \mathcal{E}_{pk}(x^{(b)}).
+        \mathcal{E}_{pk}(a^{(b)}).
     \end{equation*}
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
-    \item[$\mathsf{Enc}(t, sk_i, x^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $y^{(t)}_i = \mathcal{E}_{sk_i}(x^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, y^{(t)}_1,\dots,y^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} x^{(t)}_i$ using its private key $sk_0$.
+    \item[$\mathsf{Enc}(t, sk_i, a^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $l^{(t)}_i = \mathcal{E}_{sk_i}(a^{(t)}_i)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
 \end{LaTeXdescription}
@@
 \begin{LaTeXdescription}
-    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
+    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
     \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
     \begin{LaTeXenumerate}
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_i)$ and $(i',t',x^{\prime(t')}_{i'}$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies x^{(t)}_{i} = x^{\prime(t')}_{i'}\,.
-        \end{equation*}
-        The attacker is then given back the encryption of the value $\mathcal{E}_{sk_i}(x^{(t)}_i)$ encrypted under the secret key $sk_i$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_i)$ and $(i',t',a^{\prime(t')}_{i'}$, the following condition holds:
+        \begin{equation*}
+            i = i' \wedge t = t' \implies a^{(t)}_{i} = a^{\prime(t')}_{i'}\,.
+        \end{equation*}
+        The attacker is then given back the encryption of the value $\mathcal{E}_{sk_i}(a^{(t)}_i)$ encrypted under the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
@@
     \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(0)}_i)\,|\,i \in S\rangle
+        \left\langle(i,t^*,a^{(t^*)(0)}_i)\,\middle|\,i \in S\right\rangle
     \end{equation*}
@@
     \begin{equation*}
-        \langle(i,t^*,x^{(t^*)(1)}_i)\,|\, i \in S\rangle\,,
+        \left\langle(i,t^*,a^{(t^*)(1)}_i)\,\middle|\, i \in S\right\rangle\,,
     \end{equation*}
@@
     \begin{equation*}
-        \sum_{i\in S} x^{(t^*)(0)}_i = \sum_{i \in S} x^{(t^*)(1)}_i\,.
+        \sum_{i\in S} a^{(t^*)(0)}_i = \sum_{i \in S} a^{(t^*)(1)}_i\,.
     \end{equation*}
@@
     \begin{equation*}
-        \langle\mathcal{E}_{sk_i}(x^{(t^*)(b)}_i)\,|\,i\in S\rangle\,.
+        \left\langle\mathcal{E}_{sk_i}(a^{(t^*)(b)}_i)\,\middle|\,i\in S\right\rangle\,.
     \end{equation*}

### 2020-11-10 main.tex
Fixed up all the references Fixed only overfull /hbox warnings (left underfull ones as-is)

@@
 
+% Used to make a few encryption functions fit in one line
+\newcommand\shrtdots{\!...}
+
 % correct bad hyphenation here
@@
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
 Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy.
@@
 As is the case with localisation sensors, real number measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
-Google's Encrypted BigQuery Client \cite{Encryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
+Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
 It, however, leaks the exponent information of encrypted numbers.
@@
     \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value $x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{LaTeXdescription}
@@
 
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
     \begin{equation}
@@
 
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
     \begin{equation}
@@
 
-Code was written in the C programming language, using the MPI library \cite{OpenMPI2020} to support simultaneous computations by sensors and navigator as different processes.
-The OpenSSL library's \cite{OpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{Libpaillier2010} was used for the implementation of the Paillier encryption scheme.
-Additionally, GNU libraries GSL \cite{GSLGNUScientific2019} and GMP \cite{GMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
+Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support simultaneous computations by sensors and navigator as different processes.
+The OpenSSL library's \cite{theopensslprojectOpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the implementation of the Paillier encryption scheme.
+Additionally, GNU libraries GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
 Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.
@@
     \item[$\mathsf{Enc}(t, sk_i, a^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $l^{(t)}_i = \mathcal{E}_{sk_i}(a^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
+    \item[$\mathsf{AggDec}(t, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
 \end{LaTeXdescription}

### 2020-11-10 main.tex
Full read-through with fixes updates and some missing notational consistency

@@
 We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements.
-Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and is implemented and run on simulations to evaluate its accuracy and performance.
-The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where nodes are not trusted or data is considered sensitive.
+Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and has been implemented to evaluate its accuracy and performance.
+The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where participants are not trusted or data is considered sensitive.
 \end{abstract}
@@
 The remainder of the paper is structured as follows.
-In Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties.
+In Section \ref{sec:lit_overview} we give an overview of the relevant literature to the topic and in Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties.
 Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
@@
 
-\section{Literature Overview}
+\section{Literature Overview} \label{sec:lit_overview}
 In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localisation and estimation problems.
@@
 The originally proposed method \cite{shiPrivacyPreservingAggregationTimeSeries2011} is restricted to a small input domain which has been expanded and computationally simplified in later works \cite{joyeScalableSchemePrivacyPreserving2013,benhamoudaNewFrameworkPrivacyPreserving2016}.
-The aggregation operation in these schemes is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sum or mean calculation \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
+The aggregation operation in these schemes is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sums or mean calculations \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
 \end{LaTeXdescription}
@@
 Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
-    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset, typically one, of algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
+    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of, typically one, algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
 Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}.
-However, these works are relatively restricted in application due to the limited operations provided.
+However, as with Aggregator Oblivious Encryption, these works are relatively restricted in application due to the limited operations provided.
 \end{LaTeXdescription}
@@
     \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
-It is suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
+They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
 While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
 \end{LaTeXdescription}
-Of the aforementioned encryption schemes, some have found uses in privacy-preserving localisation and estimation tasks and we summarise these in the next section.
+In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications. These have been summarised in the next section.
 
@@
 Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
-We aim to provide an accurate localisation filter in the presence of range-only sensors.
+We aim to provide a computationally plausible and accurate localisation filter in the presence of range-only sensors while providing uncertainties associated with estimates.
 
@@
 The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols.
-Neither method considers measurement uncertainty, and no estimate errors are provided.
+Neither method considers measurement uncertainty, and no estimate errors are provided, making them unsuitable for our desired solution.
 
@@
 Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
-\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires repeated key distribution among all involved parties.
-In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures.
-
-While we have focused on the application of encryption schemes to localisation algorithms, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
-As is the case with localisation sensors, real number measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
+\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution among all involved parties.
+In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.
+
+Above we have focused on the application of encryption schemes to localisation-relevant algorithms, however, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
+As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
 Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
@@
 We will discuss and justify our choice of encoding scheme when introducing the localisation filter.
+
+From the descriptions above, we can see that no existing methods provide a general-purpose privacy-preserving localisation method supporting range-only sensors.
+In the next section, we will formalise our problem and its accompanying security requirements.
 
@@
 \section{Problem Statement} \label{sec:problem_statement}
-The localisation scenario we consider in this work is that of model-based self-navigation using range-only sensors.
+The localisation scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
 We consider localisation in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
@@
 \end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$, and measurement function $h_i$ for sensor $i$ at location
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$ at location
 \begin{equation}
@@
 It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
-However, the additional safety to passengers provided by accurate aircraft localisation, may be a goal of all those involved justifying their cooperation.
+The additional safety to passengers provided by accurate aircraft localisation, however, may be a goal of all those involved, justifying their cooperation.
 
@@
 
-To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by $t$.
+To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by a different \textit{instance} variable $t$.
 The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
@@
 
-In Section \ref{sec:priv_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors required to update the navigator's estimation filter.
+In Section \ref{sec:priv_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
 
 \begin{remark}
-    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)}$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
+    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
@@
 \subsection{Participant Capabilities} \label{subsec:capabilities}
-Before we can define concrete security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
+Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
 \begin{LaTeXdescription}
@@
 \section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our aggregation security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme and the Joye-Libert private aggregation scheme.
+When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme and the Joye-Libert private aggregation scheme.
 
@@
 \end{equation}
-where the $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
+where $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
 
@@
     \begin{equation}
-        \mathcal{E}_{pk_0}(a) = (N+1)^{x}\rho^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
+        \mathcal{E}_{pk_0}(x) = (N+1)^{x}\rho^N \pmod{N^2}\,, \label{eqn:our_scheme_encrypt}
     \end{equation}
@@
 \begin{equation}
-    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
+    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
 \end{equation}
@@
 
-The function for combined quantisation and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given a real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+The function for combined quantisation and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
 \begin{equation}
@@
 The choice of a high fractional precision $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
-Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a$, the parameter should be chosen such that the following condition holds
-\begin{equation}
-    \left|\phi^{d_{max}+1}a\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
+Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
+\begin{equation}
+    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
 \end{equation}
@@
 
-The reason for using a linear-combination aggregation scheme in this scenario is due to computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors requiring the navigator to disclose some location information in $\rvec{x}_{k|k-1}$, for the computing of Jacobians $\mat{H}_{k,i}$.
-Instead, we want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as weights from the navigator.
-As was shown in Section \ref{subsec:our_scheme}, this guarantees that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+The reason for using a linear-combination aggregation scheme in this scenario is due to wanting to compute $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors, which would require the navigator to disclose some information in $\rvec{x}_{k|k-1}$ for the computing of Jacobians $\mat{H}_{k,i}$.
+We want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as the weights from the navigator.
+As was shown in Section \ref{subsec:our_scheme}, this will guarantee that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
 From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.
@@
 The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$ in \eqref{eqn:our_scheme_lin_comb}.
-As six linear-combination aggregations occur at each time-step $k$ (four elements in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$), it is required for the security of the scheme that $t$ be unique for each aggregation at each time.
-This is handled by setting $t$ to the concatenation
+As six linear-combination aggregations occur at each time-step $k$ (four elements in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$) and it is required for the security of the scheme that $t$ be unique for each aggregation at each time, this is handled by setting $t$ to the concatenation
 \begin{equation}
@@
     \For{$v \gets 1$ to $2$}
-        \State Send $\alpha_{v}$ to the navigator
+        \State Send $\alpha_{v}^{(i)}$ to the navigator
     \EndFor
@@
 
-Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_m(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
+Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
 
@@
 We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}.
-Consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements.
-This is possibly achieved by detecting changes in real measurements after reporting false measurements to the navigator.
-As stated in Section \ref{subsec:capabilities}, misbehaving sensors are a known problem which complicates homomorphic operations and active malicious sensors are not considered in the scope of this work.
-
-The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$.
-However, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
+Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achievable by detecting changes in real measurements after reporting false ones.
+As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
+
+The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
 That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.} $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
 
-From the leaked coefficient sums, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
+From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
 \begin{equation}
@@
 Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support simultaneous computations by sensors and navigator as different processes.
-The OpenSSL library's \cite{theopensslprojectOpenSSL2020} mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the implementation of the Paillier encryption scheme.
+The OpenSSL library's, \cite{theopensslprojectOpenSSL2020}, mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the implementation of the Paillier encryption scheme.
 Additionally, GNU libraries GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
@@
 From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter.
-The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter.
+The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.
 
@@
 \section{Conclusion} \label{sec:conclusion}
-To develop a model-based localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Joye-Libert aggregation scheme.
+To develop a Bayesian localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Paillier and Joye-Libert encryption and aggregation schemes, respectively.
 This scheme was then used in our proposed privacy-preserving EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
-    \item[$\mathsf{Enc}(t, sk_i, a^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $l^{(t)}_i = \mathcal{E}_{sk_i}(a^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
+    \item[$\mathsf{Enc}(t, sk_i, a^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $\mathcal{E}_{sk_i}(a^{(t)}_i)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, sk_0, \mathcal{E}_{sk_1}(a^{(t)}_1),\shrtdots,\mathcal{E}_{sk_n}(a^{(t)}_n))$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
 \end{LaTeXdescription}
@@
     \begin{LaTeXenumerate}
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_i$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_i)$ and $(i',t',a^{\prime(t')}_{i'}$, the following condition holds:
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_i)$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_i)$ and $(i',t',a^{\prime(t')}_{i'})$, the following condition holds:
         \begin{equation*}

### 2020-11-11 main.tex
One more read-through of intro with couple small changes Also update to leakage honest-but-curious section specifying example of why its used

@@
 $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal.
-Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
+Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
 $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
@@
 Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
-\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution among all involved parties.
+\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution step among all involved parties.
 In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.
@@
 Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achievable by detecting changes in real measurements after reporting false ones.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements, when navigator behaviour is dependant on its estimate.
+This may be achievable by detecting changes in measurements after reporting false ones.
 As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.

### 2020-11-13 main.tex
Removed acknowledgement section as it's not required
Grammarly comma removed

@@
 Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements, when navigator behaviour is dependant on its estimate.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behaviour is dependant on its estimate.
 This may be achievable by detecting changes in measurements after reporting false ones.
@@
 
-% use section* for acknowledgment
-\section*{Acknowledgment}
-
-Partially supported by ZIM \dots
-
 % Can use something like this to put references on a page

### 2020-11-23 main.tex
Added reference to private weighted sum aggregation  archive paper dealing with very similar encryption schemes, and clearly stated the differences. Also fixed up the encrypted localisation subsection as this was always the weak point. It's a bit better now

@@
 \end{LaTeXdescription}
-In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications. These have been summarised in the next section.
+In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications and some specialised encryption methods have been proposed.
+These have been summarised in the next section.
 
@@
 
-\subsection{Encrypted Localisation and Estimation}
+\subsection{Applications to Localisation and Estimation}
 Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
@@
 Neither method considers measurement uncertainty, and no estimate errors are provided, making them unsuitable for our desired solution.
-
 Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
@@
 While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.
-Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
-\cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution step among all involved parties.
-In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.
-
-Above we have focused on the application of encryption schemes to localisation-relevant algorithms, however, homomorphic encryption schemes also require suitable number encoding when used with real numbers.
+
+Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
+In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are proposed.
+The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work.
+The requirements of our aggregation operation differ however, in that weights are generalised to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
+We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.
+
+Along with encryption schemes and their application to localisation-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
 As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
@@
 It, however, leaks the exponent information of encrypted numbers.
-In \cite{farokhiSecurePrivateControl2017}, a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
-We will discuss and justify our choice of encoding scheme when introducing the localisation filter.
-
-From the descriptions above, we can see that no existing methods provide a general-purpose privacy-preserving localisation method supporting range-only sensors.
+In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
+We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section \ref{sec:loc_prelim}.
+
+While some aspects of privacy-preserving localisation are solved in the above methods and encryption schemes, they fail to provide a localisation solution in our context.
 In the next section, we will formalise our problem and its accompanying security requirements.

### 2020-11-23 main.tex
AMEERICAAAAAAAA(N) - ugly but as requested - didn't add the last comma in lists, meh - didn't treat the word 'proof' as only a verb as US Grammarly says (still used as a noun since that makes more sense in the context)

@@
 % paper title
-\title{Privacy-Preserving Localisation Using Private Linear-Combination Aggregation}
+\title{Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
 %
@@
 \begin{abstract}
-Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
-Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localisation protocols, thus not preserving participants’ data privacy.
+Distributed state estimation and localization methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
+Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localization protocols, thus not preserving participants’ data privacy.
 Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability.
@@
 Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and has been implemented to evaluate its accuracy and performance.
-The novel computationally plausible and provably secure range-based localisation filter has direct applications to environments where participants are not trusted or data is considered sensitive.
+The novel computationally plausible and provably secure range-based localization filter has direct applications to environments where participants are not trusted or data is considered sensitive.
 \end{abstract}
@@
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localisation methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
-Range-based localisation methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large application due to their robustness and accuracy.
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
+Range-based localization methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large applications due to their robustness and accuracy.
 These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally.
@@
 With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
-For example, an aircraft localisation scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
-Or in autonomous vehicle state estimation, benefit from neighbouring vehicles' information may be desired while no participant wishes to share information about their hardware.
+For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
+Or in autonomous vehicle state estimation, benefit from neighboring vehicles' information may be desired while no participant wishes to share information about their hardware.
 Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
@@
 Our contributions in this work will be presented in two parts.
-We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localisation filter using this scheme such that sensor and navigator privacy is preserved.
+We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localization filter using this scheme such that sensor and navigator privacy is preserved.
 
 The remainder of the paper is structured as follows.
-In Section \ref{sec:lit_overview} we give an overview of the relevant literature to the topic and in Section \ref{sec:problem_statement} we introduce the localisation problem, the relevant aggregation opertation for its solution and the restrictions on involved parties.
-Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarise cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
-Sections \ref{sec:loc_prelim} and \ref{sec:priv_localisation} introduce localisation preliminaries and our privacy-preserving localisation method using the private aggregation scheme.
+In Section \ref{sec:lit_overview} we give an overview of the relevant literature to the topic and in Section \ref{sec:problem_statement} we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties.
+Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
+Sections \ref{sec:loc_prelim} and \ref{sec:priv_localization} introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme.
 We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.
@@
 \section{Literature Overview} \label{sec:lit_overview}
-In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localisation and estimation problems.
+In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.
 
@@
 \begin{LaTeXdescription}
-    \item[Differential Privacy] These techniques formalise preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
+    \item[Differential Privacy] These techniques formalize preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
 To handle the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs \cite{hanPrivacyControlDynamical2018,dworkDifferentialPrivacySurvey2008,andresGeoindistinguishabilityDifferentialPrivacy2013}.
 Although differential privacy has strong computational benefits due to its implementational simplicity, it provides relatively weak security guarantees for multi-party networks, with no guarantees in the presence of multiple colluding corrupted parties.
-Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localisation.
-    \item[Aggregator Oblivious Encryption] This method of encryption formalises the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
+Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localization.
+    \item[Aggregator Oblivious Encryption] This method of encryption formalizes the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
 Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
@@
     \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
-They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalisation of the aggregation schemes described earlier.
+They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier.
 While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
 \end{LaTeXdescription}
-In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications and some specialised encryption methods have been proposed.
-These have been summarised in the next section.
+In the context of privacy-preserving localization and state estimation, some of the aforementioned schemes have found applications and some specialized encryption methods have been proposed.
+These have been summarized in the next section.
 
@@
 
-\subsection{Applications to Localisation and Estimation}
-Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
-We aim to provide a computationally plausible and accurate localisation filter in the presence of range-only sensors while providing uncertainties associated with estimates.
+\subsection{Applications to Localization and Estimation}
+Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
+We aim to provide a computationally plausible and accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.
 
@@
 Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
-In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are proposed.
+In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralized or hidden weights (pWSAc and pWSAh, respectively) are proposed.
 The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work.
-The requirements of our aggregation operation differ however, in that weights are generalised to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
+The requirements of our aggregation operation differ however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
 We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.
 
-Along with encryption schemes and their application to localisation-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
+Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
 As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
@@
 
-While some aspects of privacy-preserving localisation are solved in the above methods and encryption schemes, they fail to provide a localisation solution in our context.
-In the next section, we will formalise our problem and its accompanying security requirements.
+While some aspects of privacy-preserving localization are solved in the above methods and encryption schemes, they fail to provide a localization solution in our context.
+In the next section, we will formalize our problem and its accompanying security requirements.
 
@@
 \section{Problem Statement} \label{sec:problem_statement}
-The localisation scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
-We consider localisation in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
+The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
+We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
 
@@
 It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
-The additional safety to passengers provided by accurate aircraft localisation, however, may be a goal of all those involved, justifying their cooperation.
+The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
 
@@
 \subsection{Problem Decomposition} \label{subsec:problem_decomposition}
-The recursive nature of the problem definition above complicates defining and proving of security requirements for the localisation scenario.
+The recursive nature of the problem definition above complicates defining and proving of security requirements for the localization scenario.
 As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
@@
 That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
-This has been summarised in Figure \ref{fig:agg_steps}.
+This has been summarized in Figure \ref{fig:agg_steps}.
 \begin{figure}[htbp]
@@
 
-In Section \ref{sec:priv_localisation} we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
+In Section \ref{sec:priv_localization} we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
 
@@
 We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party.
-An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localisation instances with global broadcasts.
+An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localization instances with global broadcasts.
     \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
@@
     In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
-    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localisation procedure correctly but may store or use any gained sensitive information.
+    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.
 
@@
 \end{tikzpicture}
-\caption{An example of sensor subsets. Subsets $\{1,2,3\}$ and $\{3,4,5\}$ can be used independently for localisation when the navigator is within their ranges.}
+\caption{An example of sensor subsets. Subsets $\{1,2,3\}$ and $\{3,4,5\}$ can be used independently for localization when the navigator is within their ranges.}
 \label{fig:sensor_subsets}
@@
 For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
-We will Instead show that individual sensor information remains private to sensors and that the most precise localisation estimate, requiring all measurements, remains private to the navigator.
+We will Instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
 
@@
 A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}.
-The public key is defined by $(N, g)$ and secret key by $(p, q)$.
+The public key is defined by $(N, g)$ and the secret key by $(p, q)$.
 
@@
 \section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
-As stated in Section \ref{subsec:problem_decomposition}, we decompose the localisation method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
+As stated in Section \ref{subsec:problem_decomposition}, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
 To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation.
@@
 That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations.
-This can be summarised by the two informal security notions:
+This can be summarized by the two informal security notions:
 \begin{LaTeXdescription}
@@
 From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
-To formalise the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
+To formalize the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
 
@@
 
-We formalise the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
+We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
 
@@
 
-\section{Encrypted Localisation Preliminaries} \label{sec:loc_prelim}
-Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localisation filter.
+\section{Encrypted Localization Preliminaries} \label{sec:loc_prelim}
+Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
 The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
@@
 In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$.
-For this reason, a quantisation and integer mapping method for real numbers is required for their encryption and homomorphic processing.
-We quantise with a generalised Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
+For this reason, a quantization and integer mapping method for real numbers is required for their encryption and homomorphic processing.
+We quantize with a generalized Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
 
@@
 \end{equation}
-and we quantise any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
+and we quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
 That is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
@@
 
-The function for combined quantisation and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+The function for combined quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
 \begin{equation}
@@
 
-The choice of a high fractional precision $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
+The choice of a high fractional precision $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
 Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
@@
 
-\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
-With the relevant preliminaries, we now apply the LCAO secure scheme to our original localisation problem.
+\section{Privacy-Preserving Localization} \label{sec:priv_localization}
+With the relevant preliminaries, we now apply the LCAO secure scheme to our original localization problem.
 Recall we are considering a navigator in the presence of $n$ range sensors.
@@
 It is, therefore, sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
-Next, we will show how this can be achieved for the specific case of two-dimensional range-only localisation.
+Next, we will show how this can be achieved for the specific case of two-dimensional range-only localization.
 
@@
 
-\subsection{Localisation Measurement Model} \label{subsec:observation_model}
+\subsection{Localization Measurement Model} \label{subsec:observation_model}
 Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
@@
 \begin{remark}
-    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localisation, but can be similarly extended to the three-dimensional case.
+    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localization, but can be similarly extended to the three-dimensional case.
 We note however, the additional cost with increasing dimension.
@@
 \subsection{Algorithm} \label{subsec:algorithm}
-In this section, we piece together our LCAO secure encryption scheme in Section \ref{subsec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localisation algorithm.
-
-The privacy-preserving localisation filter can be described by the following steps.
+In this section, we piece together our LCAO secure encryption scheme in Section \ref{subsec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localization algorithm.
+
+The privacy-preserving localization filter can be described by the following steps.
 \begin{LaTeXdescription}
@@
 
-Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarised graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
+Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarized graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
 
@@
 \subsection{Leakage} \label{subsec:leakage}
-With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account.
+With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
 We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}.
 Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behaviour is dependant on its estimate.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependant on its estimate.
 This may be achievable by detecting changes in measurements after reporting false ones.
@@
 \begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localisation_leakage}
+    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
 \end{equation}
@@
 \begin{theorem}
-    In the context of our localisation scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localisation_leakage}.
+    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
 \end{theorem}
@@
 \section{Conclusion} \label{sec:conclusion}
-To develop a Bayesian localisation algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Paillier and Joye-Libert encryption and aggregation schemes, respectively.
+To develop a Bayesian localization algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Paillier and Joye-Libert encryption and aggregation schemes, respectively.
 This scheme was then used in our proposed privacy-preserving EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
-Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localisation environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
+Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localization environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
 Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the application of LCAO secure schemes to alternative measurement models and the exploring of implications behind an active sensor attacker model.

### 2020-11-27 main.tex
Disappeared brackets from Zotero auto-export re-added and auto-export disabled (outside of this repo)
All of Benjamin's final change suggestions added

@@
 Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localization protocols, thus not preserving participants’ data privacy.
-Existing approaches which provide such guarantees fail to address sensor and navigator privacy in some common non-linear measurement model applications and forfeit broad applicability.
-We define the novel notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Information Filter with range-sensor measurements.
-Our method keeps navigator location, sensor locations and sensor measurements private during navigation, and has been implemented to evaluate its accuracy and performance.
+Existing approaches that do provide such guarantees fail to address sensor and navigator privacy in common non-linear measurement model applications and therefore forfeit broad applicability.
+We define a suitable notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Kalman Filter with range-sensor measurements.
+Our method keeps navigator location, sensors' locations, and sensors' measurements private during navigation, and has been implemented to evaluate its accuracy and performance.
 The novel computationally plausible and provably secure range-based localization filter has direct applications to environments where participants are not trusted or data is considered sensitive.
@@
 \begin{IEEEkeywords}
-State Estimation, Data Privacy, Sensor Fusion, Kalman Filters.
+State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filters.
 \end{IEEEkeywords}
@@
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004} and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
-Range-based localization methods, including the use of radar measurements, GPS clocks and signal strength measurements, have found particularly large applications due to their robustness and accuracy.
-These methods use distance measurements, or computed estimates, to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location and observations centrally.
+Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004}, and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
+Range-based localization methods, including the use of radar measurements, GPS clocks, and signal strength measurements, have found particularly large applications due to their robustness and accuracy.
+These methods use distance measurements to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location, and observations centrally.
 Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain.
@@
 Our contributions in this work will be presented in two parts.
-We first propose a novel aggregation-based encryption scheme which allows private aggregation of weighted sums, before we develop a localization filter using this scheme such that sensor and navigator privacy is preserved.
+We first propose a novel aggregation-based encryption scheme which allows the private aggregation of weighted sums, before developing a computationally plausible localization filter in the presence of range-only sensors using this scheme, such that sensor and navigator privacy is preserved.
 
@@
 Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
-$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal.
+$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector norm.
 Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
@@
     \item[Aggregator Oblivious Encryption] This method of encryption formalizes the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
-Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their sum can be learned by an aggregator, whether or not they are trusted.
+Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their aggregation (typically sum) can be learned by an aggregator, whether or not they are trusted.
 The originally proposed method \cite{shiPrivacyPreservingAggregationTimeSeries2011} is restricted to a small input domain which has been expanded and computationally simplified in later works \cite{joyeScalableSchemePrivacyPreserving2013,benhamoudaNewFrameworkPrivacyPreserving2016}.
-The aggregation operation in these schemes is, however, strictly limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sums or mean calculations \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
+The aggregation operation in these schemes is, however, limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sums or mean calculations \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
 \end{LaTeXdescription}
@@
 In the context of privacy-preserving localization and state estimation, some of the aforementioned schemes have found applications and some specialized encryption methods have been proposed.
-These have been summarized in the next section.
+These are summarized in the next section.
 
@@
 Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
-We aim to provide a computationally plausible and accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.
+We aim to provide an accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.
 
@@
 The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work.
-The requirements of our aggregation operation differ however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
+The requirements of our aggregation operation differ, however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
 We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.
+We define our alternative security notion in Section \ref{sec:lcao_definition}.
 
@@
 
-The navigator state is defined as 
+The navigator state captures the position, and change in position ($\Delta$), and is defined as 
 \begin{equation}
@@
     \begin{bmatrix}
-        \rv{x} & \rv{dx} & \rv{y} & \rv{dy}
+        \rv{x} & \Delta\rv{x} & \rv{y} & \Delta\rv{y}
     \end{bmatrix}^\top\,. \label{eqn:state_def}
@@
 \end{equation}
-with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependant on sensor $i$ and given by
+with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependent on sensor $i$ and given by
 \begin{equation}
@@
 
-To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by a different \textit{instance} variable $t$.
-The desired bi-direction communication protocol at instance $t$ consists of of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
+To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by a different \textit{instance} variable, $t$.
+The desired bi-directional communication protocol at instance $t$ consists of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
 That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
@@
 
-In Section \ref{sec:priv_localization} we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
+In Section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
 
@@
 For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
-We will Instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
+We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
 
@@
 \section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme and the Joye-Libert private aggregation scheme.
+When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
 
@@
 The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}.
+The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
 \begin{definition}
 An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
-
-The formal security game for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
+The formal security game and definition for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
 \end{definition}
-Private aggregation schemes aim for the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}. 
 \begin{definition}
 An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
-
-The formal security game for AO has been given in Appendix \ref{app:ao}.
+The formal security game and definition for AO has been given in Appendix \ref{app:ao}.
 \end{definition}
+
+The Paillier encryption scheme and Joye-Libert private aggregation scheme meet the above security notions, respectively, and have been given below.
 
@@
     \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the aggregator gains additional information about the remaining sensor values to be weighted $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
-Any colluding subset \textit{including} the aggregator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
+    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
+Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{LaTeXdescription}
@@
 \begin{remark} \label{rem:lcao_leakage}
-    The notion of a leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
-Since an attacker may compromise the aggregator, they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.} $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+    The notion of an aggregator leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
+Since an attacker may compromise the navigator (in our case the aggregator), they have control over the choice of these parameters, and therefore over the leakage function.
+We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
 \end{remark}
@@
 We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-These are used by a trusted third party, an aggregator and value producing users $i,\,1\leq i \leq n$.
+These are used by a trusted third party, an aggregator, and value producing users $i,\,1\leq i \leq n$.
 They are defined as follows
@@
     \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
-    \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value $x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
+    \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value~$x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
     \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
@@
     \end{equation*}
-    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
+    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.}, the aggregator is compromised) and $S = U$, it is additionally required that
     \begin{equation*}
@@
 
-\subsection{Our Scheme} \label{subsec:our_scheme}
+\subsection{Our Scheme Meeting LCAO Security} \label{subsec:our_scheme}
 Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA.
@@
 for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
-(\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof.
+(\textit{i.e.}, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof.
 The proof overview has been given in Figure \ref{fig:proof_summary}.
@@
         to $\mathcal{A}$.
-        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to $\mathcal{C}$.
+        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
     \end{LaTeXdescription}
@@
 
-The function for combined quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+The function for \textit{combined} quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
 \begin{equation}
@@
 \begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \rvec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
 \end{equation}
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \rvec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
 \end{equation}
@@
 \subsection{Measurement Model Requirements}
-From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependant only on weights from the original matrices.
+From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependent only on weights from the original matrices.
 For example, consider dimension $D\times D$ matrices $\mat{A}$ and $\mat{B}$, where element $(v,w)$ in matrix $\mat{A}$ is of the form $\sum_{i=0}^W a_{i,v,w}x_{i,v,w}$ and similarly for matrix $\mat{B}$, the form $\sum_{i=0}^W b_{i,v,w}y_{i,v,w}$.
-If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependant only on these weights, as
+If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependent only on these weights, as
 \begin{equation}
@@
 \end{equation}
-cannot be either. Instead, we consider the modified measurement functions
+cannot be either. Therefore, we consider the modified measurement functions
 \begin{equation}
@@
 
-With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given by
+With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in the same form as \eqref{eqn:matrix_mult_weights}, by
 \begin{equation}
@@
 \begin{align*}
-    \beta_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2) \\
+    \beta_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2)\,, \\
     \begin{split}
         \beta_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
-        &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})
+        &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})\,,
     \end{split}\\
-    \beta_{21} &= \beta_{12} \\
+    \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
     \beta_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
@@
     The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localization, but can be similarly extended to the three-dimensional case.
-We note however, the additional cost with increasing dimension.
+We note, however, the additional cost with increasing dimension.
 The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by \eqref{eqn:matrix_mult_weights}.
@@
 \end{equation}
-with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependant on the measurement function $h_i$ and no longer zero-mean or Gaussian.
+with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependent on the measurement function $h_i$ and no longer zero-mean or Gaussian.
 We can compute the mean of the new noise term (a function of the Gaussian term $\rv{v}_{k,i}$) as
@@
 \end{equation}
-and is dependant on $h_i(\rvec{x}_k)$.
+and is dependent on $h_i(\rvec{x}_k)$.
 To use the modified measurement function \eqref{eqn:modified_measurement} with an EIF, we require an estimate of its noise variance using only the values available to the sensor, $\rv{z}_{k,i}$ and $r_i$.
-A conservative estimate of the variance (\textit{i.e.} a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
+A conservative estimate of the variance (\textit{i.e.}, a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
 While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate when
@@
 \begin{equation}
-    \rv{r}_{k, i} = 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2\,. \label{eqn:modified_measurement_variance_estimate}
+    \begin{split}
+        \rv{r}_{k, i} &= 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
+        &\gtrapprox \Var{\rv{v}'_{k,i}}
+    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
 \end{equation}
@@
 Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependant on its estimate.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
 This may be achievable by detecting changes in measurements after reporting false ones.
@@
 The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
-That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.} $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
+That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
 
@@
 We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
-The considered layouts have been plotted and named in Figure \ref{fig:sim_layouts}.
+The considered layouts have been plotted and named in Figure~\ref{fig:sim_layouts}.
 \begin{figure}[htbp]
@@
 \includegraphics{images/layouts.pdf}
-\caption{The considered layouts.}
+\caption{The considered layouts, with varying average distances between navigator and sensors.}
 \label{fig:sim_layouts}
@@
 \includegraphics{images/layout_errors.pdf}
-\caption{Filter error for different layouts.}
+\caption{Filter error for different layouts, where solid lines show the results for our privacy-preserving filter and dashed lines for an unmodified EIF.}
 \label{fig:sim_layout_errors}
@@
 In addition to accuracy, computational requirements are an important factor in the adoption of novel cryptographic methods.
-Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.} bit lengths of $N$) and the number of sensors are varied.
+Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.}, bit lengths of $N$) and the number of sensors are varied.
 Every plotted time is again the average of $100$ simulations, each running for $50$ filter iterations.
@@
 As sensor and navigator computations run in parallel, increases in runtime from additional sensors are primarily due to the longer aggregation operation at the navigator.
-The predominant computational cost is dependant on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme.
+The predominant computational cost is dependent on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme.
 The current recommendation for a secure implementation relying on prime factorisation (difficulty of factorising $N$) is to use $2048$ bit-long keys \cite{barkerRecommendationPairwiseKey2019}.
@@
 
+\begin{definition}
+    An encryption scheme meets IND-CPA security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
+Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$ and $\mathsf{Enc}$.
+\end{definition}
+
 \section{Aggregator Obliviousness (AO)} \label{app:ao}
@@
 \end{LaTeXdescription}
+
+\begin{definition}
+    An encryption scheme meets AO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
+Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$ and $\mathsf{Enc}$.
+\end{definition}
 

### 2020-11-27 main.tex
Fixed up notation that was technically incorrect. "randomness" removed from function inputs when referring to function inputs. Similarly for the definition of the state vector.

@@
 
-The navigator state captures the position, and change in position ($\Delta$), and is defined as 
-\begin{equation}
-    \rvec{x} = 
+The navigator state captures the position and change in position ($\Delta$), and is of the form 
+\begin{equation}
+    \vec{x} = 
     \begin{bmatrix}
-        \rv{x} & \Delta\rv{x} & \rv{y} & \Delta\rv{y}
+        x & \Delta x & y & \Delta y
     \end{bmatrix}^\top\,. \label{eqn:state_def}
 \end{equation}
-A known process model is followed, which at time $k$ is given by
+A known process model is followed, in which the state at time $k$, $\rvec{x}_k$, is given by
 \begin{equation}
@@
 \end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$ at location
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$. The measurement function $h_i$, for sensor $i$ at location
 \begin{equation}
@@
 \end{equation} 
-defined as
-\begin{equation}
-    \begin{split}
-        h_i(\rvec{x}) &= \left\lVert
+is defined as
+\begin{equation}
+    \begin{split}
+        h_i(\vec{x}) &= \left\lVert
         \begin{bmatrix}
-            \rv{x} & \rv{y}
+            x & y
         \end{bmatrix}^\top
         - \vec{s}_{i}\right\rVert \\
-        &= \sqrt{(\rv{x}-s_{x,i})^2 + (\rv{y}-s_{y,i})^2}\,.
+        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
     \end{split}
@@
 \begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \rvec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
 \end{equation}
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \rvec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
 \end{equation}
@@
 \begin{equation}
-    h'_i(\rvec{x}) = h_i(\rvec{x})^2\,. \label{eqn:modified_measurement_func}
+    h'_i(\vec{x}) = h_i(\vec{x})^2\,. \label{eqn:modified_measurement_func}
 \end{equation}
@@
     \begin{split}
-        h'_i(\rvec{x}) &= \left\lVert
+        h'_i(\vec{x}) &= \left\lVert
         \begin{bmatrix}
-            \rv{x} & \rv{y}
+            x & y
         \end{bmatrix}^\top - \vec{s}_i\right\rVert^2 \\
-        &= (\rv{x} - s_{x,i})^2 + (\rv{y} - s_{y,i})^2 \\
-        &= \rv{x}^2 + \rv{y}^2 -2s_{x,i}\rv{x} -2s_{y,i}\rv{y} +s_{x,i}^2 +s_{y,i}^2
+        &= (x - s_{x,i})^2 + (y - s_{y,i})^2 \\
+        &= x^2 + y^2 -2s_{x,i}x -2s_{y,i}y +s_{x,i}^2 +s_{y,i}^2
     \end{split}\,,

### 2020-11-27 main.tex
Missing change from notation update
Couple of english changes, from the changes added in Benjamin's last feedback

@@
 \end{equation}
-A known process model is followed, in which the state at time $k$, $\rvec{x}_k$, is given by
+A known process model is followed, in which the state at time $k$ is given by
 \begin{equation}
@@
 
-The Paillier encryption scheme and Joye-Libert private aggregation scheme meet the above security notions, respectively, and have been given below.
+The Paillier encryption scheme and the Joye-Libert private aggregation scheme meet the IND-CPA and AO security notions respectively, and are given below.
 
@@
 \includegraphics{images/layout_errors.pdf}
-\caption{Filter error for different layouts, where solid lines show the results for our privacy-preserving filter and dashed lines for an unmodified EIF.}
+\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
 \label{fig:sim_layout_errors}

### 2020-12-03 main.tex
One more read-through before submission, made a few more small missed changes

@@
 Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
-    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of, typically one, algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
+    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of (typically one) algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
 Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}.
@@
 \begin{LaTeXdescription}
-    \item[Multi-Client Function Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
+    \item[Multi-Client Functional Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
 They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier.
@@
 \subsection{Problem Decomposition} \label{subsec:problem_decomposition}
-The recursive nature of the problem definition above complicates defining and proving of security requirements for the localization scenario.
+The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario.
 As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
@@
 \begin{LaTeXdescription}
-    \item[Global navigator broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required.
+    \item[Global Navigator Broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required.
 We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
@@
 An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localization instances with global broadcasts.
-    \item[Consistent navigator broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
+    \item[Consistent Navigator Broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
 This means the navigator may not send different information to individual sensors during a single time-step.
@@
     In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
-    \item[Honest-but-curious sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.
+    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.
 
@@
 As privacy-preserving implementations of such mechanisms require additional complications, we will not consider the scenario in this work.
-    \item[Computational capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
+    \item[Computational Capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
 We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
@@
 \begin{align}
-    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N} \\
-    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N} \label{eqn:paillier_hom_plain_add}\\
+    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
+    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
     \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
@@
 Since an attacker may compromise the navigator (in our case the aggregator), they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=n}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^m_{j=1}a^{(t)}_{i,j}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
 \end{remark}
@@
 \end{figure}
-To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensors layouts with sensor measurement variances set to $r_i=5$ simulation distance units.
+To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units.
 Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.

### 2020-12-09 main.tex
Added line apparently needed for submission to TAC
Added biographies and pictures

@@
 \usepackage{tikz}
+\usepackage{graphicx}
 % Maths
@@
 % Equal last columns
-\usepackage{flushend}
+%\usepackage{flushend} - doesn't really work with bios
 
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+% Apparently requested for submission
+\pdfminorversion=4
 
@@
 
+% biography section
+% 
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
+received his diploma in Software Engineering in 2018 at the University of Melbourne, Australia.
+Since 2019, he is pursuing a Ph.D.
+at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
+His research interests are in encrypted and privacy-preserving signal processing, including state estimation, sensor fusion, and distributed filtering.
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
+received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009.
+Afterwards, he obtained his Ph.D.
+in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
+Since 2013 he is a senior researcher at the Karlsruhe Institute of Technology (KIT), Germany.
+His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
+\end{IEEEbiography}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}
+is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor–Actuator-Systems Laboratory (ISAS).
+He obtained his Ph.D.
+degree in 1997 and his habilitation degree in 2003, both in Electrical Engineering from the Technical University in Munich, Germany.
+His research interests are in the areas of information fusion, nonlinear state estimation, stochastic modeling, system identification, and control with a strong emphasis on theory-driven approaches based on stochastic system theory and uncertainty models.
+He is author and coauthor of more than 400 publications in various high-ranking journals and conferences and an IEEE Fellow.
+\end{IEEEbiography}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
 % that's all folks

### 2020-12-09 main.tex
Made biographies fit within the 16 page limit - Scaled all Tiks images to 0.95 size - added a -baselineskip after all tikz image captions - added a -baselineskip before all matplotlib picture captions - added a -baselineskip after matplotlib picture captions where caption is on one line Re-added flushend - not that it makes a difference but it's nice for completeness Added bios banner comment Removed template stuff around the bios
Fixed up my bio a bit - better English and consistent capitalisation with the other bios

@@
 % Equal last columns
-%\usepackage{flushend} - doesn't really work with bios
+\usepackage{flushend}
 
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize]
+\begin{tikzpicture}[font=\footnotesize,scale=0.95]
     % Step 1
@@
 \end{tikzpicture}
-\vspace{\baselineskip}
 \caption{Required linear-combination aggregation steps at instance $t$.}
+\vspace{-\baselineskip}
 \label{fig:agg_steps}
@@
 \centering
-\begin{tikzpicture}[font=\footnotesize]
+\begin{tikzpicture}[font=\footnotesize,scale=0.95]
     % Sizes
@@
 \caption{An example of sensor subsets. Subsets $\{1,2,3\}$ and $\{3,4,5\}$ can be used independently for localization when the navigator is within their ranges.}
+\vspace{-\baselineskip}
 \label{fig:sensor_subsets}
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize]
+\begin{tikzpicture}[font=\footnotesize,scale=0.95]
     % Bounding box
@@
 \end{tikzpicture}
-\vspace{\baselineskip}
 \caption{High-level overview of our scheme's LCAO security proof.}
+\vspace{-\baselineskip}
 \label{fig:proof_summary}
@@
 \vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize]
+\begin{tikzpicture}[font=\footnotesize,scale=0.95]
     % Prediction
@@
 \end{tikzpicture}
-\vspace{\baselineskip}
 \caption{The summary of steps involved in our proposed privacy-preserving EIF.}
+\vspace{-\baselineskip}
 \label{fig:alg_steps}
@@
 \includegraphics{images/layouts.pdf}
+\vspace{-\baselineskip}
 \caption{The considered layouts, with varying average distances between navigator and sensors.}
@@
 \includegraphics{images/layout_errors.pdf}
+\vspace{-\baselineskip}
 \caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
@@
 \includegraphics{images/timing.pdf}
+\vspace{-\baselineskip}
 \caption{Runtimes for varying key sizes and numbers of sensors.}
+\vspace{-\baselineskip}
 \label{fig:sim_timing}
@@
 
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
+% 
+% 888888b.  8888888 .d88888b.   .d8888b.  
+% 888  "88b   888  d88P" "Y88b d88P  Y88b 
+% 888  .88P   888  888     888 Y88b.      
+% 8888888K.   888  888     888  "Y888b.   
+% 888  "Y88b  888  888     888     "Y88b. 
+% 888    888  888  888     888       "888 
+% 888   d88P  888  Y88b. .d88P Y88b  d88P 
+% 8888888P" 8888888 "Y88888P"   "Y8888P"  
+%                                         
+%                                         
+%                                         
+% 
+\vspace{-\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
-received his diploma in Software Engineering in 2018 at the University of Melbourne, Australia.
-Since 2019, he is pursuing a Ph.D.
+received his diploma in software engineering in 2018 at the University of Melbourne, Australia.
+Since 2019, he has been pursuing a Ph.D.
 at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
-His research interests are in encrypted and privacy-preserving signal processing, including state estimation, sensor fusion, and distributed filtering.
+His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed filtering.
 \end{IEEEbiography}
 
-% if you will not have a photo at all:
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
@@
 
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}

### 2021-05-17 main.tex
Biography update
Started with huge overhaul New section structure created Correct labels added for sections Simply removed references to previous section (means many paragraphs now read wrong) Copied relevant parts of paper into their new sections (still need lots of work to make them read fluid) Removed sections will no longer be included (but references to them are still present - need to be removed)

@@
 
-\section{Introduction}
+\section{Introduction} \label{sec:introduction}
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
@@
 The remainder of the paper is structured as follows.
-In Section \ref{sec:lit_overview} we give an overview of the relevant literature to the topic and in Section \ref{sec:problem_statement} we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties.
-Sections \ref{sec:crypto_prelim} and \ref{sec:lcao_definition} will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
-Sections \ref{sec:loc_prelim} and \ref{sec:priv_localization} introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme.
-We show and discuss simulation results in Section \ref{sec:sim_and_results} and conclude our work in Section \ref{sec:conclusion}.
-
-% 
-% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
-% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
-% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
-% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
-% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
-% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
-% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
-%
-
-\subsection{Notation}
-Throughout this work, we will use the following notation.
-Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$.
-Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
-$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector norm.
-Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
-$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
-Additionally, key $k$ may be ommited when inferrable from context.
-$\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
-
-% 
-% 888      8888888 88888888888 
-% 888        888       888     
-% 888        888       888     
-% 888        888       888     
-% 888        888       888     
-% 888        888       888     
-% 888        888       888     
-% 88888888 8888888     888     
-%                              
-%                              
-%                              
-%
-
-\section{Literature Overview} \label{sec:lit_overview}
+In Section  we give an overview of the relevant literature to the topic and in Section  we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties.
+Sections  and  will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
+Sections  and  introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme.
+We show and discuss simulation results in Section  and conclude our work in Section .
+
+% LITERATURE OVERVIEW
+
+\label{sec:lit_overview}
 In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.
 
-% 
-% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
-% ##       ###   ## ##    ##    ##    ## ##    ## ##     ## ##       ###   ### ##       ##    ## 
-% ##       ####  ## ##          ##       ##       ##     ## ##       #### #### ##       ##       
-% ######   ## ## ## ##           ######  ##       ######### ######   ## ### ## ######    ######  
-% ##       ##  #### ##                ## ##       ##     ## ##       ##     ## ##             ## 
-% ##       ##   ### ##    ##    ##    ## ##    ## ##     ## ##       ##     ## ##       ##    ## 
-% ######## ##    ##  ######      ######   ######  ##     ## ######## ##     ## ########  ######  
-%
-
-\subsection{Encryption Schemes in Signal Processing}
+% ENCRYPTION SCHEMES IN SIGNAL PROCESSING
+
 Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
@@
 
-% 
-% ######## ##    ##  ######     ##        #######   ######  
-% ##       ###   ## ##    ##    ##       ##     ## ##    ## 
-% ##       ####  ## ##          ##       ##     ## ##       
-% ######   ## ## ## ##          ##       ##     ## ##       
-% ##       ##  #### ##          ##       ##     ## ##       
-% ##       ##   ### ##    ##    ##       ##     ## ##    ## 
-% ######## ##    ##  ######     ########  #######   ######  
-%
-
-\subsection{Applications to Localization and Estimation}
+% APPLICATIONS TO LOCALIZATION AND ESTIMATION
+
 Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
@@
 We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.
-We define our alternative security notion in Section \ref{sec:lcao_definition}.
+We define our alternative security notion in Section .
 
@@
 In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
-We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section \ref{sec:loc_prelim}.
+We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section .
 
@@
 In the next section, we will formalize our problem and its accompanying security requirements.
+
+% 
+% ##    ##  #######  ########    ###    ######## ####  #######  ##    ## 
+% ###   ## ##     ##    ##      ## ##      ##     ##  ##     ## ###   ## 
+% ####  ## ##     ##    ##     ##   ##     ##     ##  ##     ## ####  ## 
+% ## ## ## ##     ##    ##    ##     ##    ##     ##  ##     ## ## ## ## 
+% ##  #### ##     ##    ##    #########    ##     ##  ##     ## ##  #### 
+% ##   ### ##     ##    ##    ##     ##    ##     ##  ##     ## ##   ### 
+% ##    ##  #######     ##    ##     ##    ##    ####  #######  ##    ## 
+%
+
+\subsection{Notation}
+Throughout this work, we will use the following notation.
+Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$.
+Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
+$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector norm.
+Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
+$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
+Additionally, key $k$ may be ommited when inferrable from context.
+$\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
 
@@
 \section{Problem Statement} \label{sec:problem_statement}
-The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
-We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
-
-The navigator state captures the position and change in position ($\Delta$), and is of the form 
-\begin{equation}
-    \vec{x} = 
-    \begin{bmatrix}
-        x & \Delta x & y & \Delta y
-    \end{bmatrix}^\top\,. \label{eqn:state_def}
-\end{equation}
-A known process model is followed, in which the state at time $k$ is given by
-\begin{equation}
-    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
-\end{equation}
-with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependent on sensor $i$ and given by
-\begin{equation}
-    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
-\end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$. The measurement function $h_i$, for sensor $i$ at location
-\begin{equation}
-    \vec{s}_i = 
-    \begin{bmatrix}
-        s_{x,i} & s_{y,i}
-    \end{bmatrix}^\top\,,
-\end{equation} 
-is defined as
-\begin{equation}
-    \begin{split}
-        h_i(\vec{x}) &= \left\lVert
-        \begin{bmatrix}
-            x & y
-        \end{bmatrix}^\top
-        - \vec{s}_{i}\right\rVert \\
-        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
-    \end{split}
-\end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn state estimates of $\rvec{x}_{k}$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
-We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
-It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
-The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
-
-% 
-% ########  ########  ######   #######  ##     ## ########  
-% ##     ## ##       ##    ## ##     ## ###   ### ##     ## 
-% ##     ## ##       ##       ##     ## #### #### ##     ## 
-% ##     ## ######   ##       ##     ## ## ### ## ########  
-% ##     ## ##       ##       ##     ## ##     ## ##        
-% ##     ## ##       ##    ## ##     ## ##     ## ##        
-% ########  ########  ######   #######  ##     ## ##        
-%
-
-\subsection{Problem Decomposition} \label{subsec:problem_decomposition}
+
+% DECOMPOSITION
+
 The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario.
@@
 
-In Section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
+In Section , we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
 
@@
     From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
-We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section \ref{subsec:algorithm}.
+We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section .
 \end{remark}
@@
 % 
-%  ######     ###    ########     ###    ########  #### ##       #### ######## #### ########  ######  
-% ##    ##   ## ##   ##     ##   ## ##   ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
+%  ######  ########  ##    ## ########  ########  #######     ########  ########   #######  ########  
+% ##    ## ##     ##  ##  ##  ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
+% ##       ##     ##   ####   ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
+% ##       ########     ##    ########     ##    ##     ##    ########  ########  ##     ## ########  
+% ##       ##   ##      ##    ##           ##    ##     ##    ##        ##   ##   ##     ## ##     ## 
 % ##    ## ##    ##     ##    ##           ##    ##     ##    ##        ##    ##  ##     ## ##     ## 
-% ##       ##     ## ########  ##     ## ########   ##  ##        ##     ##     ##  ######    ######  
-% ##       ######### ##        ######### ##     ##  ##  ##        ##     ##     ##  ##             ## 
-% ##    ## ##     ## ##        ##     ## ##     ##  ##  ##        ##     ##     ##  ##       ##    ## 
-%  ######  ##     ## ##        ##     ## ########  #### ######## ####    ##    #### ########  ######  
-%
-
-\subsection{Participant Capabilities} \label{subsec:capabilities}
+%  ######  ##     ##    ##    ##           ##     #######     ##        ##     ##  #######  ########  
+%
+
+\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}
+
+% CAPABILITIES
+
 Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
@@
 
-% 
-% ##       ########    ###    ##    ##    ###     ######   ######## 
-% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
-% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
-% ##       ######   ##     ## #####    ##     ## ##   #### ######   
-% ##       ##       ######### ##  ##   ######### ##    ##  ##       
-% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
-% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
-%
-
-\subsection{Inherent Leakage}
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information.
-For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
-We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
-
-% 
-% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.  8888888888 888      8888888 888b     d888 
-% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b 888        888        888   8888b   d8888 
-% 888        88888b  888 888    888      888    888 888    888 888        888        888   88888b.d88888 
-% 8888888    888Y88b 888 888             888   d88P 888   d88P 8888888    888        888   888Y88888P888 
-% 888        888 Y88b888 888             8888888P"  8888888P"  888        888        888   888 Y888P 888 
-% 888        888  Y88888 888    888      888        888 T88b   888        888        888   888  Y8P  888 
-% 888        888   Y8888 Y88b  d88P      888        888  T88b  888        888        888   888   "   888 
-% 8888888888 888    Y888  "Y8888P"       888        888   T88b 8888888888 88888888 8888888 888       888 
-%                                                                                                        
-%                                                                                                        
-%                                                                                                        
-%
-
-\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
-When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
-
-% 
-%  ######  ########  ######  ##     ## ########  #### ######## ##    ## 
-% ##    ## ##       ##    ## ##     ## ##     ##  ##     ##     ##  ##  
-% ##       ##       ##       ##     ## ##     ##  ##     ##      ####   
-%  ######  ######   ##       ##     ## ########   ##     ##       ##    
-%       ## ##       ##       ##     ## ##   ##    ##     ##       ##    
-% ##    ## ##       ##    ## ##     ## ##    ##   ##     ##       ##    
-%  ######  ########  ######   #######  ##     ## ####    ##       ##    
-%
-
-\subsection{Security Notions}
-The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
-\begin{definition}
-An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
-The formal security game and definition for IND-CPA has been given in Appendix \ref{app:ind_cpa}.
-\end{definition}
-\begin{definition}
-An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
-The formal security game and definition for AO has been given in Appendix \ref{app:ao}.
-\end{definition}
-
-The Paillier encryption scheme and the Joye-Libert private aggregation scheme meet the IND-CPA and AO security notions respectively, and are given below.
-
-% 
-% ########     ###    #### ##       ##       #### ######## ########  
-% ##     ##   ## ##    ##  ##       ##        ##  ##       ##     ## 
-% ##     ##  ##   ##   ##  ##       ##        ##  ##       ##     ## 
-% ########  ##     ##  ##  ##       ##        ##  ######   ########  
-% ##        #########  ##  ##       ##        ##  ##       ##   ##   
-% ##        ##     ##  ##  ##       ##        ##  ##       ##    ##  
-% ##        ##     ## #### ######## ######## #### ######## ##     ## 
-%
-
-\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
-The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
-Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
-A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}.
-The public key is defined by $(N, g)$ and the secret key by $(p, q)$.
-
-Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
-\begin{equation}
-    c = g^a \rho^N \pmod{N^2}
-\end{equation}
-for a randomly chosen $\rho \in \mathbb{Z}_{N}$.
-$\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
-The decryption of a ciphertext is computed by
-\begin{equation}
-    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
-\end{equation}
-where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.
-
-In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
-\begin{align}
-    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
-    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
-    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
-\end{align}
-
-% 
-%       ##         ##    ## 
-%       ##          ##  ##  
-%       ##           ####   
-%       ## #######    ##    
-% ##    ##            ##    
-% ##    ##            ##    
-%  ######             ##    
-%
-
-\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
-The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data, that we refer to as instances for consistency, and meets the security notion of AO.
-Similarly to the Paillier scheme, it bases its security on the DCRA.
-A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.
-
-Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
-Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
-\begin{equation}
-    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
-\end{equation}
-and sent to the aggregator.
-
-Encryption of plaintext $a^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
-\begin{equation}
-    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
-\end{equation}
-where $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
-
-When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
-\begin{equation}
-    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
-\end{equation}
-and
-\begin{equation}
-    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
-\end{equation}
-Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
-\begin{equation*}
-    \begin{split}
-        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
-        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
-        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
-        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}
-    \end{split}
-\end{equation*}
-removing all noise terms.
-
-% 
-% 8888888888 888b    888  .d8888b.       8888888b.  8888888b.   .d88888b.  888888b.   
-% 888        8888b   888 d88P  Y88b      888   Y88b 888   Y88b d88P" "Y88b 888  "88b  
-% 888        88888b  888 888    888      888    888 888    888 888     888 888  .88P  
-% 8888888    888Y88b 888 888             888   d88P 888   d88P 888     888 8888888K.  
-% 888        888 Y88b888 888             8888888P"  8888888P"  888     888 888  "Y88b 
-% 888        888  Y88888 888    888      888        888 T88b   888     888 888    888 
-% 888        888   Y8888 Y88b  d88P      888        888  T88b  Y88b. .d88P 888   d88P 
-% 8888888888 888    Y888  "Y8888P"       888        888   T88b  "Y88888P"  8888888P"  
-%                                                                                     
-%                                                                                     
-%                                                                                     
-%
-
-\section{Private Linear-Combination Aggregation} \label{sec:lcao_definition}
-As stated in Section \ref{subsec:problem_decomposition}, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
+% LCAO OVERVIEW
+
+As stated in Section, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
 To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation.
@@
 
-% 
-% ##        ######     ###     #######  
-% ##       ##    ##   ## ##   ##     ## 
-% ##       ##        ##   ##  ##     ## 
-% ##       ##       ##     ## ##     ## 
-% ##       ##       ######### ##     ## 
-% ##       ##    ## ##     ## ##     ## 
-% ########  ######  ##     ##  #######  
-%
-
-\subsection{Linear-Combination Aggregator Oblivious Encryption} \label{subsec:lcao}
+% LINEAR-COMBINATION AGGREGATOR OBLIVIOUS ENCRYPTION
+
+\label{subsec:lcao}
 We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
@@
 
-We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger:
-
-\begin{LaTeXdescription}
-    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
-    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
-    \begin{LaTeXenumerate}
-        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
-        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
-        \end{equation*}
-        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
-        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{LaTeXenumerate} 
-    \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game.
-The attacker then chooses two series of tuples
-    \begin{equation*}
-        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
-    \end{equation*}
+We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger: %see appendix
+
+In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
+
+% 
+% ########  ######  ########    ########  ########   #######  ########  
+% ##       ##    ##    ##       ##     ## ##     ## ##     ## ##     ## 
+% ##       ##          ##       ##     ## ##     ## ##     ## ##     ## 
+% ######    ######     ##       ########  ########  ##     ## ########  
+% ##             ##    ##       ##        ##   ##   ##     ## ##     ## 
+% ##       ##    ##    ##       ##        ##    ##  ##     ## ##     ## 
+% ########  ######     ##       ##        ##     ##  #######  ########  
+%
+
+\subsection{Estimation problem} \label{subsec:est_problem}
+The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
+We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
+
+The navigator state captures the position and change in position ($\Delta$), and is of the form 
+\begin{equation}
+    \vec{x} = 
+    \begin{bmatrix}
+        x & \Delta x & y & \Delta y
+    \end{bmatrix}^\top\,. \label{eqn:state_def}
+\end{equation}
+A known process model is followed, in which the state at time $k$ is given by
+\begin{equation}
+    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
+\end{equation}
+with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependent on sensor $i$ and given by
+\begin{equation}
+    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
+\end{equation}
+with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$. The measurement function $h_i$, for sensor $i$ at location
+\begin{equation}
+    \vec{s}_i = 
+    \begin{bmatrix}
+        s_{x,i} & s_{y,i}
+    \end{bmatrix}^\top\,,
+\end{equation} 
+is defined as
+\begin{equation}
+    \begin{split}
+        h_i(\vec{x}) &= \left\lVert
+        \begin{bmatrix}
+            x & y
+        \end{bmatrix}^\top
+        - \vec{s}_{i}\right\rVert \\
+        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
+    \end{split}
+\end{equation}
+We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn state estimates of $\rvec{x}_{k}$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
+We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
+It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
+The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
+
+% LEAKAGE
+
+Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information.
+For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
+We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
+
+% 
+% 8888888b.  8888888b.  8888888888 888      8888888 888b     d888  .d8888b.  
+% 888   Y88b 888   Y88b 888        888        888   8888b   d8888 d88P  Y88b 
+% 888    888 888    888 888        888        888   88888b.d88888 Y88b.      
+% 888   d88P 888   d88P 8888888    888        888   888Y88888P888  "Y888b.   
+% 8888888P"  8888888P"  888        888        888   888 Y888P 888     "Y88b. 
+% 888        888 T88b   888        888        888   888  Y8P  888       "888 
+% 888        888  T88b  888        888        888   888   "   888 Y88b  d88P 
+% 888        888   T88b 8888888888 88888888 8888888 888       888  "Y8888P"  
+%                                                                            
+%                                                                            
+%                                                                            
+%
+
+\section{Preliminaries} \label{sec:preliminaries}
+When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
+
+% SECURITY NOTIONS
+
+The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
+The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
+\begin{definition}
+An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
+The formal security game and definition for IND-CPA has been given in Appendix .
+\end{definition}
+\begin{definition}
+An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
+The formal security game and definition for AO has been given in Appendix .
+\end{definition}
+
+The Paillier encryption scheme and the Joye-Libert private aggregation scheme meet the IND-CPA and AO security notions respectively, and are given below.
+
+% 
+% ########     ###    #### ##       ##       #### ######## ########  
+% ##     ##   ## ##    ##  ##       ##        ##  ##       ##     ## 
+% ##     ##  ##   ##   ##  ##       ##        ##  ##       ##     ## 
+% ########  ##     ##  ##  ##       ##        ##  ######   ########  
+% ##        #########  ##  ##       ##        ##  ##       ##   ##   
+% ##        ##     ##  ##  ##       ##        ##  ##       ##    ##  
+% ##        ##     ## #### ######## ######## #### ######## ##     ## 
+%
+
+\subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
+The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
+Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
+A generator $g$ is also required for encryption, which is often set to $g=N+1$ when $p$ and $q$ are of equal bit length \cite{katzIntroductionModernCryptography2008}.
+The public key is defined by $(N, g)$ and the secret key by $(p, q)$.
+
+Encryption of a plaintext message $a \in \mathbb{Z}_N$, producing ciphertext $c \in \mathbb{Z}^{*}_{N^2}$, is computed by
+\begin{equation}
+    c = g^a \rho^N \pmod{N^2}
+\end{equation}
+for a randomly chosen $\rho \in \mathbb{Z}_{N}$.
+$\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
+The decryption of a ciphertext is computed by
+\begin{equation}
+    a = \frac{L(c^\lambda\pmod{N^2})}{L(g^\lambda\pmod{N^2})} \pmod{N}
+\end{equation}
+where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.
+
+In addition to encryption and decryption, the following homomorphic functions are provided by the Paillier scheme. $\forall a_1,a_2 \in \mathbb{Z}_N$,
+\begin{align}
+    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
+    \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
+    \mathcal{D}(\mathcal{E}(a_1)^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1a_2 \hspace{-7pt} \pmod{N}\,. \label{eqn:paillier_hom_mult}
+\end{align}
+
+% 
+%       ##         ##    ## 
+%       ##          ##  ##  
+%       ##           ####   
+%       ## #######    ##    
+% ##    ##            ##    
+% ##    ##            ##    
+%  ######             ##    
+%
+
+\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
+The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data, that we refer to as instances for consistency, and meets the security notion of AO.
+Similarly to the Paillier scheme, it bases its security on the DCRA.
+A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.
+
+Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
+Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
+$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
+\begin{equation}
+    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
+\end{equation}
+and sent to the aggregator.
+
+Encryption of plaintext $a^{(t)}_{i} \in \mathbb{Z}_N$ to ciphertext $c^{(t)}_{i} \in \mathbb{Z}_{N^2}$ at instance $t$ is computed by user $i$ as
+\begin{equation}
+    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
+\end{equation}
+where $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
+
+When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
+\begin{equation}
+    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
+\end{equation}
 and
-    \begin{equation*}
-        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
-    \end{equation*}
-    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.}, the aggregator is compromised) and $S = U$, it is additionally required that
-    \begin{equation*}
-        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
-    \end{equation*}
-    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
-    \begin{equation*}
-        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
-    \end{equation*}
-    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
-    \begin{equation*}
-        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
-    \end{equation*} 
-\end{LaTeXdescription}
-
-\begin{definition}
-    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
-Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
-\end{definition}
-
-In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
-
-% 
-%  #######  ##     ## ########      ######   ######  ##     ## ######## ##     ## ######## 
-% ##     ## ##     ## ##     ##    ##    ## ##    ## ##     ## ##       ###   ### ##       
-% ##     ## ##     ## ##     ##    ##       ##       ##     ## ##       #### #### ##       
-% ##     ## ##     ## ########      ######  ##       ######### ######   ## ### ## ######   
-% ##     ## ##     ## ##   ##            ## ##       ##     ## ##       ##     ## ##       
-% ##     ## ##     ## ##    ##     ##    ## ##    ## ##     ## ##       ##     ## ##       
-%  #######   #######  ##     ##     ######   ######  ##     ## ######## ##     ## ######## 
-%
-
-\subsection{Our Scheme Meeting LCAO Security} \label{subsec:our_scheme}
+\begin{equation}
+    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
+\end{equation}
+Correctness follows from $\sum^{n}_{i=0}sk_i = 0$, and thus
+\begin{equation*}
+    \begin{split}
+        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
+        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
+        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
+        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}
+    \end{split}
+\end{equation*}
+removing all noise terms.
+
+% 
+% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
+% ##       ###   ## ##    ## ##     ## ##     ##  ##  ###   ## ##    ##  
+% ##       ####  ## ##       ##     ## ##     ##  ##  ####  ## ##        
+% ######   ## ## ## ##       ##     ## ##     ##  ##  ## ## ## ##   #### 
+% ##       ##  #### ##       ##     ## ##     ##  ##  ##  #### ##    ##  
+% ##       ##   ### ##    ## ##     ## ##     ##  ##  ##   ### ##    ##  
+% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
+%
+
+\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
+
+% INTRO
+
+Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
+The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
+We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
+
+% ENCODING
+
+In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$.
+For this reason, a quantization and integer mapping method for real numbers is required for their encryption and homomorphic processing.
+We quantize with a generalized Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
+
+We define a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$.
+This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
+Rational subset $\mathbb{Q}_{M,\phi}$ is given by
+\begin{equation}
+    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
+\end{equation}
+and we quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
+That is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
+In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $M=N$, and handling negatives with modulo arithmetic.
+In addition, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
+This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.
+
+The function for \textit{combined} quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+\begin{equation}
+    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
+\end{equation}
+Decoding of an integer $u \in \mathbb{Z}_M$, is given by
+\begin{equation}
+    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
+    \begin{dcases}
+        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
+        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
+    \end{dcases}.\label{eqn:decode}
+\end{equation}
+
+This encoding scheme provides the following homomorphic operations,
+\begin{equation}
+    \begin{split}
+        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
+        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
+    \end{split}\label{eqn:encoding_homomorphic_add}
+\end{equation}
+and
+\begin{equation}
+    \begin{split}
+        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
+        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
+    \end{split}
+\end{equation}
+noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
+
+The choice of a high fractional precision $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
+Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
+\begin{equation}
+    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
+\end{equation}
+In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.
+
+% 
+% 888      .d8888b.        d8888  .d88888b.  
+% 888     d88P  Y88b      d88888 d88P" "Y88b 
+% 888     888    888     d88P888 888     888 
+% 888     888           d88P 888 888     888 
+% 888     888          d88P  888 888     888 
+% 888     888    888  d88P   888 888     888 
+% 888     Y88b  d88P d8888888888 Y88b. .d88P 
+% 88888888 "Y8888P" d88P     888  "Y88888P"  
+%                                            
+%                                            
+%                                            
+%
+
+\section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}
+
+% OUR SCHEME MEETING LCAO SECURITY
+
+\label{subsec:our_scheme}
 Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA.
@@
 
-% 
-% ########  ########   #######   #######  ######## 
-% ##     ## ##     ## ##     ## ##     ## ##       
-% ##     ## ##     ## ##     ## ##     ## ##       
-% ########  ########  ##     ## ##     ## ######   
-% ##        ##   ##   ##     ## ##     ## ##       
-% ##        ##    ##  ##     ## ##     ## ##       
-% ##        ##     ##  #######   #######  ##       
-%
-
-\subsection{Security Proof}
+% PROOF
+
 To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
@@
 
-\begin{proof}
-    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section \ref{subsec:lcao}.
-The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix \ref{app:ao} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
-    \begin{LaTeXdescription}
-        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
-        \item[Queries] Handle queries from $\mathcal{A}$:
-        \begin{LaTeXdescription}
-            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
-            \begin{equation*}
-                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
-            \end{equation*}
-            to $\mathcal{A}$.
-            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
-The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return
-            \begin{equation*}
-                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
-            \end{equation*}
-            to $\mathcal{A}$.
-            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
-        \end{LaTeXdescription}
-        \item[Challenge] When $\mathcal{A}$ submits challenge series
-        \begin{equation*}
-            \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
-        \end{equation*}
-        and
-        \begin{equation*}
-            \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
-        \end{equation*}
-        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
-        \begin{equation*}
-            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle
-        \end{equation*}
-        and
-        \begin{equation*}
-            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle\,,
-        \end{equation*}
-        to $\mathcal{C}$. The received response will be of the form 
-        \begin{equation*}
-            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle\,,
-        \end{equation*}
-        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
-        \begin{equation*}
-            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
-        \end{equation*}
-        to $\mathcal{A}$.
-        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
-    \end{LaTeXdescription}
-
-    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ follows our scheme in Section \ref{subsec:our_scheme} exactly.
-Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
-That is, there exists a negligible function $\eta$, such that
-    \begin{equation*}
-        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
-    \end{equation*}
-    for security parameter $\kappa$.
-\end{proof}
-
-% 
-% 888      .d88888b.   .d8888b.       8888888b.  8888888b.  8888888888 888      8888888 888b     d888 
-% 888     d88P" "Y88b d88P  Y88b      888   Y88b 888   Y88b 888        888        888   8888b   d8888 
-% 888     888     888 888    888      888    888 888    888 888        888        888   88888b.d88888 
-% 888     888     888 888             888   d88P 888   d88P 8888888    888        888   888Y88888P888 
-% 888     888     888 888             8888888P"  8888888P"  888        888        888   888 Y888P 888 
-% 888     888     888 888    888      888        888 T88b   888        888        888   888  Y8P  888 
-% 888     Y88b. .d88P Y88b  d88P      888        888  T88b  888        888        888   888   "   888 
-% 88888888 "Y88888P"   "Y8888P"       888        888   T88b 8888888888 88888888 8888888 888       888 
-%                                                                                                     
-%                                                                                                     
-%                                                                                                     
-%
-
-\section{Encrypted Localization Preliminaries} \label{sec:loc_prelim}
-Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
-The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
-We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
-
-% 
-% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
-% ##       ###   ## ##    ## ##     ## ##     ##  ##  ###   ## ##    ##  
-% ##       ####  ## ##       ##     ## ##     ##  ##  ####  ## ##        
-% ######   ## ## ## ##       ##     ## ##     ##  ##  ## ## ## ##   #### 
-% ##       ##  #### ##       ##     ## ##     ##  ##  ##  #### ##    ##  
-% ##       ##   ### ##    ## ##     ## ##     ##  ##  ##   ### ##    ##  
-% ######## ##    ##  ######   #######  ########  #### ##    ##  ######   
-%
-
-\subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
-In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$.
-For this reason, a quantization and integer mapping method for real numbers is required for their encryption and homomorphic processing.
-We quantize with a generalized Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
-
-We define a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$.
-This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
-Rational subset $\mathbb{Q}_{M,\phi}$ is given by
-\begin{equation}
-    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
-\end{equation}
-and we quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
-That is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
-In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $M=N$, and handling negatives with modulo arithmetic.
-In addition, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
-This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.
-
-The function for \textit{combined} quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
-\begin{equation}
-    \mathsf{E}_{M,\phi,d}(a) = \left\lfloor \phi^{d+1} a \right\rceil \pmod{M}\,. \label{eqn:encode}
-\end{equation}
-Decoding of an integer $u \in \mathbb{Z}_M$, is given by
-\begin{equation}
-    \mathsf{E}^{-1}_{M,\phi,d}(u) \!=\! 
-    \begin{dcases}
-        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
-        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
-    \end{dcases}.\label{eqn:decode}
-\end{equation}
-
-This encoding scheme provides the following homomorphic operations,
-\begin{equation}
-    \begin{split}
-        \mathsf{E}_{M,\phi,d}(a_1) + \mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
-        &\mathsf{E}_{M,\phi,d}(a_1+a_2)
-    \end{split}\label{eqn:encoding_homomorphic_add}
-\end{equation}
-and
-\begin{equation}
-    \begin{split}
-        \mathsf{E}_{M,\phi,d}(a_1)\mathsf{E}_{M,\phi,d}(a_2)& \pmod{M} =\\
-        &\mathsf{E}_{M,\phi,d+1}(a_1a_2)\,,
-    \end{split}
-\end{equation}
-noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
-
-The choice of a high fractional precision $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
-Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
-\begin{equation}
-    \left|\phi^{d_{max}+1}a_{max}\right| < \left\lfloor \frac{M}{2} \right\rfloor\,.
-\end{equation}
-In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.
-
-% 
-% ######## #### ######## 
-% ##        ##  ##       
-% ##        ##  ##       
-% ######    ##  ######   
-% ##        ##  ##       
-% ##        ##  ##       
-% ######## #### ##       
-%
-
-\subsection{Extended Information Filter}
-The Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982} is a reformulation of the Extended Kalman Filter (EKF), such that the update equations are simplified to sums of measurement information from each sensor.
-This requires the conversion of predicted state estimate $\rvec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ to the information vector and matrix
-\begin{equation}
-    \rvec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
-\end{equation}
-respectively. In this form, the update equations for $n$ measurements at time $k$, given process and measurement models \eqref{eqn:process_model} and \eqref{eqn:measurement_model}, are given by
-\begin{equation}
-    \begin{split}
-        &\rvec{y}_{k|k} = \rvec{y}_{k|k-1} + \\
-        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1})
-    \end{split} \label{eqn:eif_info_vec_update}
-\end{equation}
-and
-\begin{equation}
-    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
-\end{equation}
-with Jacobians
-\begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
-\end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\rvec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
-\begin{equation}
-    \rvec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
-\end{equation}
-before using the normal EKF prediction equations
-\begin{equation}
-    \rvec{x}_{k+1|k} = \vec{f}(\rvec{x}_{k|k})
-\end{equation}
-and
-\begin{equation}
-    \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top\,,
-\end{equation}
-with Jacobian
-\begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\rvec{x}_{k|k}}\,. \label{eqn:jacobian_f}
-\end{equation}
-
-% 
-% 888      .d88888b.   .d8888b.  
-% 888     d88P" "Y88b d88P  Y88b 
-% 888     888     888 888    888 
-% 888     888     888 888        
-% 888     888     888 888        
-% 888     888     888 888    888 
-% 888     Y88b. .d88P Y88b  d88P 
-% 88888888 "Y88888P"   "Y8888P"  
+% 
+% 8888888b.  8888888b.  8888888 888     888      888      .d88888b.   .d8888b.  
+% 888   Y88b 888   Y88b   888   888     888      888     d88P" "Y88b d88P  Y88b 
+% 888    888 888    888   888   888     888      888     888     888 888    888 
+% 888   d88P 888   d88P   888   Y88b   d88P      888     888     888 888        
+% 8888888P"  8888888P"    888    Y88b d88P       888     888     888 888        
+% 888        888 T88b     888     Y88o88P        888     888     888 888    888 
+% 888        888  T88b    888      Y888P         888     Y88b. .d88P Y88b  d88P 
+% 888        888   T88b 8888888     Y8P          88888888 "Y88888P"   "Y8888P"  
 %                                                                               
@@
 Recall we are considering a navigator in the presence of $n$ range sensors.
-The navigator runs a local filter, computing its update step with equations \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}, where received information from each sensor $i$ consists of the measurement vector
+The navigator runs a local filter, computing its update step with equations  and , where received information from each sensor $i$ consists of the measurement vector
 \begin{equation}
@@
 We want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as the weights from the navigator.
-As was shown in Section \ref{subsec:our_scheme}, this will guarantee that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
+As was shown in Section , this will guarantee that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
 From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.
@@
 % 
-% ##     ##   ### ##     ## ###      ########  ########  #######   ######  
-% ##     ##  ##    ##   ##    ##     ##     ## ##       ##     ## ##    ## 
-% ##     ## ##      ## ##      ##    ##     ## ##       ##     ## ##       
-% ######### ##       ###       ##    ########  ######   ##     ##  ######  
-% ##     ## ##      ## ##      ##    ##   ##   ##       ##  ## ##       ## 
-% ##     ##  ##    ##   ##    ##     ##    ##  ##       ##    ##  ##    ## 
-% ##     ##   ### ##     ## ###      ##     ## ########  ##### ##  ######  
-%
-
-\subsection{Measurement Model Requirements}
-From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependent only on weights from the original matrices.
-For example, consider dimension $D\times D$ matrices $\mat{A}$ and $\mat{B}$, where element $(v,w)$ in matrix $\mat{A}$ is of the form $\sum_{i=0}^W a_{i,v,w}x_{i,v,w}$ and similarly for matrix $\mat{B}$, the form $\sum_{i=0}^W b_{i,v,w}y_{i,v,w}$.
-If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependent only on these weights, as
-\begin{equation}
-    \begin{split}
-        \sum_{d=0}^D&\left(\left(\sum_{i=0}^W a_{i,v,d}x_{i,v,d}\right)\left(\sum_{i=0}^W b_{i,d,w}y_{i,d,w}\right)\right) \\
-        &=\sum_{d=0}^N\left(\sum_{i=0}^W\sum_{j=0}^W a_{i,v,d}x_{i,v,d}b_{j,d,w}y_{j,d,w}\right) \\
-        &=\sum_{d=0}^N\sum_{i=0}^W\sum_{j=0}^W (a_{i,v,d}b_{j,d,w})x_{i,v,d}y_{j,d,w}\,.
-    \end{split} \label{eqn:matrix_mult_weights}
-\end{equation}
-Similarly, scalar multiplication also holds this property.
-It is, therefore, sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
-Next, we will show how this can be achieved for the specific case of two-dimensional range-only localization.
-
-% 
-%  #######  ########   ######     ##     ##  #######  ########  ######## ##       
-% ##     ## ##     ## ##    ##    ###   ### ##     ## ##     ## ##       ##       
-% ##     ## ##     ## ##          #### #### ##     ## ##     ## ##       ##       
-% ##     ## ########   ######     ## ### ## ##     ## ##     ## ######   ##       
-% ##     ## ##     ##       ##    ##     ## ##     ## ##     ## ##       ##       
-% ##     ## ##     ## ##    ##    ##     ## ##     ## ##     ## ##       ##       
-%  #######  ########   ######     ##     ##  #######  ########  ######## ######## 
-%
-
-\subsection{Localization Measurement Model} \label{subsec:observation_model}
+% ########     ###    ##    ##  ######   ########    ##     ##  #######  ########  
+% ##     ##   ## ##   ###   ## ##    ##  ##          ###   ### ##     ## ##     ## 
+% ##     ##  ##   ##  ####  ## ##        ##          #### #### ##     ## ##     ## 
+% ########  ##     ## ## ## ## ##   #### ######      ## ### ## ##     ## ##     ## 
+% ##   ##   ######### ##  #### ##    ##  ##          ##     ## ##     ## ##     ## 
+% ##    ##  ##     ## ##   ### ##    ##  ##          ##     ## ##     ## ##     ## 
+% ##     ## ##     ## ##    ##  ######   ########    ##     ##  #######  ########  
+%
+
+\subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
+
+% INTRO
+
 Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
@@
 
-To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using \eqref{eqn:matrix_mult_weights}, we require the existance of a modified measurement model of the form
+To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using , we require the existance of a modified measurement model of the form
 \begin{equation}
@@
 
-With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in the same form as \eqref{eqn:matrix_mult_weights}, by
+% REST
+
+In Section , we assumed the existance of a measurement model \eqref{eqn:modified_measurement_model} where modified sensor measurements $\rv{z}'_{k,i}$ had zero-mean noises with variances $\rv{r}_{k,i}$.
+In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
+Squaring the range measurement produces
+\begin{equation}
+    \begin{split}
+        \rv{z}_{k,i}^2 &= (h_i(\rvec{x}_k) + \rv{v}_{k,i})^2 \\
+        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 \\
+        &= h'_i(\rvec{x}_k) + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2\,,
+    \end{split}
+\end{equation}
+with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependent on the measurement function $h_i$ and no longer zero-mean or Gaussian.
+We can compute the mean of the new noise term (a function of the Gaussian term $\rv{v}_{k,i}$) as
+\begin{equation}
+    \E{2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2} = r_i\, \label{eqn:modified_noise_mean}
+\end{equation}
+and define modified measurements as
+\begin{equation} \label{eqn:modified_measurement}
+    \begin{split}
+        \rv{z}'_{k,i} &= \rv{z}_{k,i}^2 - r_i \\
+        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \\
+        &= h'_i(\rvec{x}_k) + \rv{v}'_{k,i}\,,
+    \end{split}
+\end{equation}
+with now zero-mean noise $\rv{v}'_{k,i} = 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i$. The noise in this case (again a function of white Gaussian term $\rv{v}_{k,i}$) has variance 
+\begin{equation}
+    \Var{\rv{v}'_{k,i}} = 4h_i(\rvec{x}_k)^2r_i + 2r_i^2
+\end{equation}
+and is dependent on $h_i(\rvec{x}_k)$.
+To use the modified measurement function \eqref{eqn:modified_measurement} with an EIF, we require an estimate of its noise variance using only the values available to the sensor, $\rv{z}_{k,i}$ and $r_i$.
+A conservative estimate of the variance (\textit{i.e.}, a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
+While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate when
+\begin{equation}
+    \begin{split}
+        &\rv{z}_{k,i} > h_i(\rvec{x}_k) \\
+        \implies &\rv{z}_{k,i} - h_i(\rvec{x}_k) > 0 \\
+        \implies &\rv{v}_{k,i} > 0\,,
+    \end{split}
+\end{equation}
+and cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
+Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
+\begin{equation}
+    \begin{split}
+        \rv{r}_{k, i} &= 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
+        &\gtrapprox \Var{\rv{v}'_{k,i}}
+    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
+\end{equation}
+Together, the model and variance, \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, provide a suitable substitute for the required measurement model \eqref{eqn:modified_measurement_model} and can be used to achieve the desired linear properties using only the available range sensors.
+
+% % 
+% % ##     ##   ### ##     ## ###      ########  ########  #######   ######  
+% % ##     ##  ##    ##   ##    ##     ##     ## ##       ##     ## ##    ## 
+% % ##     ## ##      ## ##      ##    ##     ## ##       ##     ## ##       
+% % ######### ##       ###       ##    ########  ######   ##     ##  ######  
+% % ##     ## ##      ## ##      ##    ##   ##   ##       ##  ## ##       ## 
+% % ##     ##  ##    ##   ##    ##     ##    ##  ##       ##    ##  ##    ## 
+% % ##     ##   ### ##     ## ###      ##     ## ########  ##### ##  ######  
+% %
+
+% \subsection{Measurement Model Requirements}
+% From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependent only on weights from the original matrices.
+For example, consider dimension $D\times D$ matrices $\mat{A}$ and $\mat{B}$, where element $(v,w)$ in matrix $\mat{A}$ is of the form $\sum_{i=0}^W a_{i,v,w}x_{i,v,w}$ and similarly for matrix $\mat{B}$, the form $\sum_{i=0}^W b_{i,v,w}y_{i,v,w}$.
+If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependent only on these weights, as
+% \begin{equation}
+%     \begin{split}
+%         \sum_{d=0}^D&\left(\left(\sum_{i=0}^W a_{i,v,d}x_{i,v,d}\right)\left(\sum_{i=0}^W b_{i,d,w}y_{i,d,w}\right)\right) \\
+%         &=\sum_{d=0}^N\left(\sum_{i=0}^W\sum_{j=0}^W a_{i,v,d}x_{i,v,d}b_{j,d,w}y_{j,d,w}\right) \\
+%         &=\sum_{d=0}^N\sum_{i=0}^W\sum_{j=0}^W (a_{i,v,d}b_{j,d,w})x_{i,v,d}y_{j,d,w}\,.
+%     \end{split} \label{eqn:matrix_mult_weights}
+% \end{equation}
+% Similarly, scalar multiplication also holds this property.
+It is, therefore, sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
+Next, we will show how this can be achieved for the specific case of two-dimensional range-only localization.
+
+% 
+% ##        #######   ######  
+% ##       ##     ## ##    ## 
+% ##       ##     ## ##       
+% ##       ##     ## ##       
+% ##       ##     ## ##       
+% ##       ##     ## ##    ## 
+% ########  #######   ######  
+%
+
+\subsection{Localization} \label{subsec:localization}
+With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in the same form as , by
 \begin{equation}
@@
 We note, however, the additional cost with increasing dimension.
-The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by \eqref{eqn:matrix_mult_weights}.
+The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by .
 This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
@@
 % 
-%  ######   #######  ##     ##    ###    ########  ######## ########     ######## 
-% ##    ## ##     ## ##     ##   ## ##   ##     ## ##       ##     ##         ##  
-% ##       ##     ## ##     ##  ##   ##  ##     ## ##       ##     ##        ##   
-%  ######  ##     ## ##     ## ##     ## ########  ######   ##     ##       ##    
-%       ## ##  ## ## ##     ## ######### ##   ##   ##       ##     ##      ##     
-% ##    ## ##    ##  ##     ## ##     ## ##    ##  ##       ##     ##     ##      
-%  ######   ##### ##  #######  ##     ## ##     ## ######## ########     ######## 
-%
-
-\subsection{Range Measurement Modification} \label{subsec:range_measurement_mod}
-In Section \ref{subsec:observation_model}, we assumed the existance of a measurement model \eqref{eqn:modified_measurement_model} where modified sensor measurements $\rv{z}'_{k,i}$ had zero-mean noises with variances $\rv{r}_{k,i}$.
-In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
-Squaring the range measurement produces
-\begin{equation}
-    \begin{split}
-        \rv{z}_{k,i}^2 &= (h_i(\rvec{x}_k) + \rv{v}_{k,i})^2 \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 \\
-        &= h'_i(\rvec{x}_k) + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2\,,
-    \end{split}
-\end{equation}
-with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependent on the measurement function $h_i$ and no longer zero-mean or Gaussian.
-We can compute the mean of the new noise term (a function of the Gaussian term $\rv{v}_{k,i}$) as
-\begin{equation}
-    \E{2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2} = r_i\, \label{eqn:modified_noise_mean}
-\end{equation}
-and define modified measurements as
-\begin{equation} \label{eqn:modified_measurement}
-    \begin{split}
-        \rv{z}'_{k,i} &= \rv{z}_{k,i}^2 - r_i \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \\
-        &= h'_i(\rvec{x}_k) + \rv{v}'_{k,i}\,,
-    \end{split}
-\end{equation}
-with now zero-mean noise $\rv{v}'_{k,i} = 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i$. The noise in this case (again a function of white Gaussian term $\rv{v}_{k,i}$) has variance 
-\begin{equation}
-    \Var{\rv{v}'_{k,i}} = 4h_i(\rvec{x}_k)^2r_i + 2r_i^2
-\end{equation}
-and is dependent on $h_i(\rvec{x}_k)$.
-To use the modified measurement function \eqref{eqn:modified_measurement} with an EIF, we require an estimate of its noise variance using only the values available to the sensor, $\rv{z}_{k,i}$ and $r_i$.
-A conservative estimate of the variance (\textit{i.e.}, a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
-While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate when
-\begin{equation}
-    \begin{split}
-        &\rv{z}_{k,i} > h_i(\rvec{x}_k) \\
-        \implies &\rv{z}_{k,i} - h_i(\rvec{x}_k) > 0 \\
-        \implies &\rv{v}_{k,i} > 0\,,
-    \end{split}
-\end{equation}
-and cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
-Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
-\begin{equation}
-    \begin{split}
-        \rv{r}_{k, i} &= 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
-        &\gtrapprox \Var{\rv{v}'_{k,i}}
-    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
-\end{equation}
-Together, the model and variance, \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, provide a suitable substitute for the required measurement model \eqref{eqn:modified_measurement_model} and can be used to achieve the desired linear properties using only the available range sensors.
-
-% 
-%    ###    ##        ######    #######  ########  #### ######## ##     ## ##     ## 
-%   ## ##   ##       ##    ##  ##     ## ##     ##  ##     ##    ##     ## ###   ### 
-%  ##   ##  ##       ##        ##     ## ##     ##  ##     ##    ##     ## #### #### 
-% ##     ## ##       ##   #### ##     ## ########   ##     ##    ######### ## ### ## 
-% ######### ##       ##    ##  ##     ## ##   ##    ##     ##    ##     ## ##     ## 
-% ##     ## ##       ##    ##  ##     ## ##    ##   ##     ##    ##     ## ##     ## 
-% ##     ## ########  ######    #######  ##     ## ####    ##    ##     ## ##     ## 
-%
-
-\subsection{Algorithm} \label{subsec:algorithm}
-In this section, we piece together our LCAO secure encryption scheme in Section \ref{subsec:our_scheme} with the modified measurement model in Sections \ref{subsec:observation_model} and \ref{subsec:range_measurement_mod} and define our privacy-preserving localization algorithm.
+% ##       ########    ###    ##    ##    ###     ######   ######## 
+% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
+% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
+% ##       ######   ##     ## #####    ##     ## ##   #### ######   
+% ##       ##       ######### ##  ##   ######### ##    ##  ##       
+% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
+% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
+%
+
+\subsection{Leakage} \label{subsec:leakage}
+With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
+We recall the assumptions on participant capabilities made in Section .
+Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
+This may be achievable by detecting changes in measurements after reporting false ones.
+As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
+
+The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
+That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
+
+From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
+\begin{equation}
+    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
+\end{equation}
+From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
+\begin{theorem}
+    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
+\end{theorem}
+
+% 
+%    ###    ##        ######   
+%   ## ##   ##       ##    ##  
+%  ##   ##  ##       ##        
+% ##     ## ##       ##   #### 
+% ######### ##       ##    ##  
+% ##     ## ##       ##    ##  
+% ##     ## ########  ######   
+%
+
+\subsection{Pseudocode} \label{subsec:pseudocode}
+In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.
 
@@
 \begin{LaTeXdescription}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section \ref{subsec:our_scheme} is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from Section  is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
 Additionally, we assume that fractional precision $\phi$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
@@
 
-    \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
+    \State Compute $\mat{F}_k$ by 
     \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
@@
 % 
-% ##       ########    ###    ##    ##    ###     ######   ######## 
-% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
-% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
-% ##       ######   ##     ## #####    ##     ## ##   #### ######   
-% ##       ##       ######### ##  ##   ######### ##    ##  ##       
-% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
-% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
-%
-
-\subsection{Leakage} \label{subsec:leakage}
-With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
-We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}.
-Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
-This may be achievable by detecting changes in measurements after reporting false ones.
-As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
-
-The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
-That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
-
-From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
-\begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
-\end{equation}
-From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
-\begin{theorem}
-    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
-\end{theorem}
-
-% 
-% 8888888b.  8888888888 .d8888b.  888     888 888    88888888888 .d8888b.  
-% 888   Y88b 888       d88P  Y88b 888     888 888        888    d88P  Y88b 
-% 888    888 888       Y88b.      888     888 888        888    Y88b.      
-% 888   d88P 8888888    "Y888b.   888     888 888        888     "Y888b.   
-% 8888888P"  888           "Y88b. 888     888 888        888        "Y88b. 
-% 888 T88b   888             "888 888     888 888        888          "888 
-% 888  T88b  888       Y88b  d88P Y88b. .d88P 888        888    Y88b  d88P 
-% 888   T88b 8888888888 "Y8888P"   "Y88888P"  88888888   888     "Y8888P"  
+%  .d8888b. 8888888 888b     d888 
+% d88P  Y88b  888   8888b   d8888 
+% Y88b.       888   88888b.d88888 
+%  "Y888b.    888   888Y88888P888 
+%     "Y88b.  888   888 Y888P 888 
+%       "888  888   888  Y8P  888 
+% Y88b  d88P  888   888   "   888 
+%  "Y8888P" 8888888 888       888 
 %                                 
@@
 \section{Simulation and Results} \label{sec:sim_and_results}
-To demonstrate our proposed approach, we have implemented the algorithm in Section \ref{subsec:algorithm} and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.
+To demonstrate our proposed approach, we have implemented the algorithm in Section  and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.
 
@@
 \appendices
-\section{Indistinguishability under Chosen Plaintext Attack (IND-CPA)} \label{app:ind_cpa}
-A public-key encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{Dec})$, defined as
+\section{Linear-Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
 \begin{LaTeXdescription}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public key $pk$ and secret key $sk$
-    \item[$\mathsf{Enc}(pk, a)$] Encryption of value $a$ is computable using the public key $pk$, obtaining $\mathcal{E}_{pk}(a)$.
-    \item[$\mathsf{Dec}(sk, \mathcal{E}_{pk}(a))$] Decryption of value $a$ is computable using the secret key $sk$.
-\end{LaTeXdescription}
-
-The security game between attacker and challenger for IND-CPA security is given by
-\begin{LaTeXdescription}
-    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives public key $pk$ to the attacker
-    \item[Encryptions] The attacker may compute encryptions using the public key $pk$.
-    \item[Challenge] Next, the attacker chooses two values
-    \begin{equation*}
-        a^{(0)} \text{ and } a^{(1)}
-    \end{equation*}
-    and gives them to the challenger. The challenger then chooses a random bit $b \in \{1,0\}$ and returns the encryption
-    \begin{equation*}
-        \mathcal{E}_{pk}(a^{(b)}).
-    \end{equation*}
-    \item[More Encryptions] The attacker can now compute more encryptions with the public key $pk$.
-    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
-    \begin{equation*}
-        \mathsf{Adv}^{IND-CPA}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
-    \end{equation*} 
-\end{LaTeXdescription}
-
-\begin{definition}
-    An encryption scheme meets IND-CPA security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
-Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$ and $\mathsf{Enc}$.
-\end{definition}
-
-\section{Aggregator Obliviousness (AO)} \label{app:ao}
-An aggregator oblivious encryption scheme is defined by the tuple of algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{AggDec})$, defined as
-\begin{LaTeXdescription}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the user private keys $sk_i,\,1\leq i \leq n$, and the aggregator's private key $sk_0=-\sum^n_{i=1}sk_i$.
-    \item[$\mathsf{Enc}(t, sk_i, a^{(t)}_i)$] At instance $t$, user $i$ computes and obtains the encrypted value $\mathcal{E}_{sk_i}(a^{(t)}_i)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, sk_0, \mathcal{E}_{sk_1}(a^{(t)}_1),\shrtdots,\mathcal{E}_{sk_n}(a^{(t)}_n))$] At instance $t$, the aggregator computes the aggregation of values $\sum^{n}_{i=1} a^{(t)}_i$ using its private key $sk_0$.
-\end{LaTeXdescription}
-
-The security game between attacker and challenger for AO security is given by
-\begin{LaTeXdescription}
-    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives public parameters $\mathsf{pub}$ to the attacker
-    \item[Queries] The attacker can now submit queries that are answered by the challenger. The types of queries are:
+    \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
+    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
     \begin{LaTeXenumerate}
-        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_i)$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_i)$ and $(i',t',a^{\prime(t')}_{i'})$, the following condition holds:
-        \begin{equation*}
-            i = i' \wedge t = t' \implies a^{(t)}_{i} = a^{\prime(t')}_{i'}\,.
-        \end{equation*}
-        The attacker is then given back the encryption of the value $\mathcal{E}_{sk_i}(a^{(t)}_i)$ encrypted under the secret key $sk_i$.
+        \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
+        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
+        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
+        \begin{equation*}
+            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
+        \end{equation*}
+        The attacker is then given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
@@
     \begin{equation*}
-        \left\langle(i,t^*,a^{(t^*)(0)}_i)\,\middle|\,i \in S\right\rangle
+        \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
     \end{equation*}
@@
     \begin{equation*}
-        \left\langle(i,t^*,a^{(t^*)(1)}_i)\,\middle|\, i \in S\right\rangle\,,
+        \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
     \end{equation*}
@@
     \begin{equation*}
-        \sum_{i\in S} a^{(t^*)(0)}_i = \sum_{i \in S} a^{(t^*)(1)}_i\,.
-    \end{equation*}
-    The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
-    \begin{equation*}
-        \left\langle\mathcal{E}_{sk_i}(a^{(t^*)(b)}_i)\,\middle|\,i\in S\right\rangle\,.
-    \end{equation*}
-    \item[More Queries] The attacker can now submit more queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
+        \sum_{i\in S}\sum^{m}_{j=1} a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
+    \end{equation*}
+    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
+    \begin{equation*}
+        \left\langle\mathcal{E}_{pk_0,sk_i}\left(\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i\in S\right\rangle\,.
+    \end{equation*}
+    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
     \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game if and only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
     \begin{equation*}
-        \mathsf{Adv}^{AO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
     \end{equation*} 
@@
 \begin{definition}
-    An encryption scheme meets AO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
-Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$ and $\mathsf{Enc}$.
+    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
+Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
 \end{definition}
+
+\section{Proof of our scheme security} \label{app:proof}
+\begin{proof}
+    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section .
+The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix  against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
+    \begin{LaTeXdescription}
+        \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
+        \item[Queries] Handle queries from $\mathcal{A}$:
+        \begin{LaTeXdescription}
+            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
+            \begin{equation*}
+                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
+            \end{equation*}
+            to $\mathcal{A}$.
+            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
+The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return
+            \begin{equation*}
+                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
+            \end{equation*}
+            to $\mathcal{A}$.
+            \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
+        \end{LaTeXdescription}
+        \item[Challenge] When $\mathcal{A}$ submits challenge series
+        \begin{equation*}
+            \left\langle\left(i,t^*,a^{(t^*)(0)}_{i,1},\dots,a^{(t^*)(0)}_{i,m}\right)\,\middle|\,i \in S\right\rangle
+        \end{equation*}
+        and
+        \begin{equation*}
+            \left\langle\left(i,t^*,a^{(t^*)(1)}_{i,1},\dots,a^{(t^*)(1)}_{i,m}\right)\,\middle|\, i \in S\right\rangle\,,
+        \end{equation*}
+        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
+        \begin{equation*}
+            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle
+        \end{equation*}
+        and
+        \begin{equation*}
+            \left\langle\left(i,t^*,\sum^m_{j=1}a^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\right)\,\middle|\,i \in S\right\rangle\,,
+        \end{equation*}
+        to $\mathcal{C}$. The received response will be of the form 
+        \begin{equation*}
+            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle\,,
+        \end{equation*}
+        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
+        \begin{equation*}
+            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
+        \end{equation*}
+        to $\mathcal{A}$.
+        \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
+    \end{LaTeXdescription}
+
+    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ follows our scheme in Section  exactly.
+Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
+That is, there exists a negligible function $\eta$, such that
+    \begin{equation*}
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)
+    \end{equation*}
+    for security parameter $\kappa$.
+\end{proof}
 
@@
 His research interests are in the areas of information fusion, nonlinear state estimation, stochastic modeling, system identification, and control with a strong emphasis on theory-driven approaches based on stochastic system theory and uncertainty models.
-He is author and coauthor of more than 400 publications in various high-ranking journals and conferences and an IEEE Fellow.
+He is author and coauthor of more than 500 publications in various high-ranking journals and conferences and an IEEE Fellow.
 \end{IEEEbiography}

### 2021-05-19 main.tex
Started on problem formulation section. Formal cryptographic problem section draft finished

@@
 
+% Used to be in problem formulation but better point out the differences in our contribution to pWSAc here and not mention it again
+Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
+
 Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
@@
 \section{Problem Statement} \label{sec:problem_statement}
-
-% DECOMPOSITION
-
-The recursive nature of the problem definition above complicates the defining and proving of security requirements for the localization scenario.
-As with existing estimation methods \cite{benhamoudaNewFrameworkPrivacyPreserving2016,alexandruEncryptedCooperativeControl2019} we will reduce the communication requirements, of sensors and the navigator in our case, to an aggregation operation which will make security more easily definable.
-
-To support multiple aggregations at each time-step $k$, as is required for the aggregation of multi-dimensional data, aggregation instances have been denoted by a different \textit{instance} variable, $t$.
-The desired bi-directional communication protocol at instance $t$ consists of the computation of linear combinations of navigator weights by sensors, before their privacy-preserving aggregation by the navigator.
-That is, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are broadcast by the navigator, linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator.
-This has been summarized in Figure \ref{fig:agg_steps}.
+In this work, we consider the context of privacy-presering range-sensor navigation, in which we wish for no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
+The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-sensor navigation.
+
+To give a formal cryptographic requirement in a distributed setting, we must first consider the communication requirements of our context, and define the attacker capabilities and the desired security of a suitable encryption scheme.
+In this section, we will define a communication protocol and the relevant formal definition of security we aim to achieve, followed by the estimation problem to which we will apply it.
+
+% 
+%  ######  ########  ##    ## ########  ########  #######     ########  ########   #######  ########  
+% ##    ## ##     ##  ##  ##  ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
+% ##       ##     ##   ####   ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
+% ##       ########     ##    ########     ##    ##     ##    ########  ########  ##     ## ########  
+% ##       ##   ##      ##    ##           ##    ##     ##    ##        ##   ##   ##     ## ##     ## 
+% ##    ## ##    ##     ##    ##           ##    ##     ##    ##        ##    ##  ##     ## ##     ## 
+%  ######  ##     ##    ##    ##           ##     #######     ##        ##     ##  #######  ########  
+%
+
+\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}
+The communication between the navigator and sensors in our estimation problem will be decomposed into a simple two-step bi-directional protocol that will simplify defining formal security.
+In section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals.
+
+At every \textit{instance} $t$ (used to distinguish from an estimation timestep $k$), the navigator first broadcasts a number of weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who compute individual linear-combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
+Linear-combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
+This two-step linear-combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
 \begin{figure}[htbp]
 \centering
-\vspace{\baselineskip}
 \begin{tikzpicture}[font=\footnotesize,scale=0.95]
     % Step 1
-    \node at (3.25,5.5) {1. Broadcast and combination step};
+    \node at (3.25,5.5) {1. Broadcast and Combination Step};
     % Navigator
@@
     % Step 2
-    \node at (3.25,-0.75) {2. Aggregation step};
+    \node at (3.25,-0.75) {2. Aggregation Step};
     % Navigator
@@
 \caption{Required linear-combination aggregation steps at instance $t$.}
-\vspace{-\baselineskip}
 \label{fig:agg_steps}
 \end{figure}
-
-In Section , we will show how this protocol is sufficient to compute the required estimation information at the sensors needed to update the navigator's estimation filter.
-
-\begin{remark}
-    From the aggregation definition above and the distributive property of real numbers, it is clear that an alternative method to the bi-directional communication requirement would be computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ by the navigator, requiring only uni-directional communication by sending values $a_{i,j}^{(t)}, 1 \leq j \leq m$ from each sensor $i$.
-We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in Section .
-\end{remark}
-
-% 
-%  ######  ########  ##    ## ########  ########  #######     ########  ########   #######  ########  
-% ##    ## ##     ##  ##  ##  ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
-% ##       ##     ##   ####   ##     ##    ##    ##     ##    ##     ## ##     ## ##     ## ##     ## 
-% ##       ########     ##    ########     ##    ##     ##    ########  ########  ##     ## ########  
-% ##       ##   ##      ##    ##           ##    ##     ##    ##        ##   ##   ##     ## ##     ## 
-% ##    ## ##    ##     ##    ##           ##    ##     ##    ##        ##    ##  ##     ## ##     ## 
-%  ######  ##     ##    ##    ##           ##     #######     ##        ##     ##  #######  ########  
-%
-
-\subsection{Formal Cryptographic Problem} \label{subsec:crypto_problem}
-
-% CAPABILITIES
-
-Before we can define formal security requirements and a filtering protocol, we require some assumptions on the capabilities of the navigator and sensors in our problem scenario.
+In addition, we remark that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$.
+We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.
+
+Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the navigator and sensors.
 \begin{LaTeXdescription}
-    \item[Global Navigator Broadcast] From the decomposition defined above, we know that bi-directional communication between navigator and sensors is required.
-We make the assumption that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
-
-    A problem caused by this requirement is apparent in the context of aircraft navigation.
-It may be the case that some sensors are not within the range of a navigator broadcast.
-We loosely propose that this scenario can be handled with pre-defined sensor subsets during an initial step by a trusted party.
-An example has been shown in Figure \ref{fig:sensor_subsets}, which reduces to two separate localization instances with global broadcasts.
-    \item[Consistent Navigator Broadcast] Further, we make the assumption that broadcast information from the navigator is received equal by all sensors.
-This means the navigator may not send different information to individual sensors during a single time-step.
-
-    In the context of wireless communication, the wide-spread use of cheap non-directional antennas make this assumption reasonable.
+    \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
+    \item[Consistent Navigator Broadcast] We assume that broadcast information from the navigator is received equally by all sensors.
+This means the navigator may not send different weights to individual sensors during a single instance $t$.
     \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.
-
-    Misbehaving sensors are a known problem in estimation theory, often requiring inconsistency or outlier detection mechanisms \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}.
-As privacy-preserving implementations of such mechanisms require additional complications, we will not consider the scenario in this work.
-    \item[Computational Capabilities] The computational requirements for computing encryptions and homomorphic operations are typically more costly than their plaintext equivalents.
-We make the implicit assumption that all involved parties are computationally capable of computing the required encryption and filter operations.
 \end{LaTeXdescription}
-\begin{figure}[htbp]
-\centering
-\begin{tikzpicture}[font=\footnotesize,scale=0.95]
-    % Sizes
-    \tikzmath{\srange = 3.54; \sradius = 0.04;}
-    % Sensor locations (sensor 3 is shared)
-    \coordinate (s1) at (0.8523,-4.1508) {};
-    \coordinate (s2) at (3.507,-5.5587) {};
-    \coordinate (s3) at (2.5,-2.75) {} {};
-    \coordinate (s4) at (4,-1.25) {};
-    \coordinate (s5) at (5.4346,-3.1274) {};
-    % Navigator location
-    \coordinate (nav_loc) at (3.5,-3.25) {};
-    % Bounding rectangle
-    \coordinate (brect_start) at (0,0);
-    \coordinate (brect_end) at (6.5, -6.5);
-
-    % Gray range circles
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \draw[gray!50] (s1) circle (\srange);
-        \draw[gray!50] (s2) circle (\srange);
-        \draw[gray!50] (s3) circle (\srange);
-        \draw[gray!50] (s4) circle (\srange);
-        \draw[gray!50] (s5) circle (\srange);
-    \end{scope}
-    % Red subgroup overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s3) circle (\srange);
-        \clip (s4) circle (\srange);
-        \clip (s5) circle (\srange);
-        \fill[red!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Blue subgroup overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s1) circle (\srange);
-        \clip (s2) circle (\srange);
-        \clip (s3) circle (\srange);
-        \fill[blue!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Magenta double overlap
-    \begin{scope}
-        \clip (brect_start) rectangle (brect_end);
-        \clip (s1) circle (\srange);
-        \clip (s2) circle (\srange);
-        \clip (s3) circle (\srange);
-        \clip (s4) circle (\srange);
-        \clip (s5) circle (\srange);
-        \fill[magenta!40] (brect_start) rectangle (brect_end);
-    \end{scope}
-    % Sensors
-    \fill[black] (s1) circle (\sradius);
-    \fill[black] (s2) circle (\sradius);
-    \fill[black] (s3) circle (\sradius);
-    \fill[black] (s4) circle (\sradius);
-    \fill[black] (s5) circle (\sradius);
-    % Bounding box
-    \draw[gray] (brect_start) rectangle (brect_end);
-    % Navigator
-    \clip (brect_start) rectangle (brect_end);
-    \pic[rotate=-40,xscale=0.22,yscale=0.3] at (nav_loc) {plane};
-    \begin{scope}[shift={(nav_loc)},rotate=-40,xscale=0.22,yscale=0.3]
-        % Trail
-        \fill[bottom color=white, top color=gray] (-0.05, -1.5) rectangle (0.05, -50);
-    \end{scope}
-    % Sensor labels
-    \node[label=1] at (s1) {};
-    \node[label=2] at (s2) {};
-    \node[label=3] at (s3) {};
-    \node[label=4] at (s4) {};
-    \node[label=5] at (s5) {};
-\end{tikzpicture}
-\caption{An example of sensor subsets. Subsets $\{1,2,3\}$ and $\{3,4,5\}$ can be used independently for localization when the navigator is within their ranges.}
-\vspace{-\baselineskip}
-\label{fig:sensor_subsets}
-\end{figure}
-
-% LCAO OVERVIEW
-
-As stated in Section, we decompose the localization method such that the multi-party aggregation protocol, given in Figure \ref{fig:agg_steps}, captures all communication between the navigator and sensors.
-To perform this protocol in a secure manner, we must first describe the security properties we aim to achieve during aggregation.
-Broadly speaking, we want a cryptographic scheme which allows instances of homomorphically computed linear combinations of encrypted weights, to be summed by a private aggregation scheme.
-That is, we do not want sensors to learn the navigator weights, while we do not want the navigator to learn individual weighted linear combinations.
-This can be summarized by the two informal security notions:
+We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a complete group and treated as the global set for estimation purposes, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts.
+The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work for the sake of simplicity.
+
+We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide.
+We let a linear-combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
+These will be used by a trusted setup party, the navigator and sensors $i,\,1\leq i \leq n$.
+They are defined as follows
 \begin{LaTeXdescription}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ from receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
-    \item[Private Linear-Combination Aggregation] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
+    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,1\leq i \leq n$.
+    \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear-combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+\end{LaTeXdescription}
+The security notions we want the above algorithms to meet reflect the previously stated estimation privacy goals.
+The navigator should learn no information from individual sensors while sensors should learning no information from the navigator or any other sensors.
+In the context of the introduced communication protocol, this can be summarised as the following notions.
+\begin{LaTeXdescription}
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
+    \item[Linear-Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
 Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{LaTeXdescription}
-
+While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear-Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
+Lastly, we conclude the cryptographic problem definition with the following important remark.
 \begin{remark} \label{rem:lcao_leakage}
-    The notion of an aggregator leakage function including parameters from the aggregator requires extra care to be taken when giving its definition.
-Since an attacker may compromise the navigator (in our case the aggregator), they have control over the choice of these parameters, and therefore over the leakage function.
-We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by the colluding subset, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the requirement that all sensors receive the same weights.
+    A leakage function including weights from the navigator requires extra care to be taken when giving its definition.
+If an attacker compromises the navigator (which need not follow the estimation protocol), they have control over the weights, and therefore the leakage function.
+We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
 \end{remark}
-
-From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
-To formalize the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
-
-% LINEAR-COMBINATION AGGREGATOR OBLIVIOUS ENCRYPTION
-
-\label{subsec:lcao}
-We let a linear-combination aggregator oblivious encryption scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-These are used by a trusted third party, an aggregator, and value producing users $i,\,1\leq i \leq n$.
-They are defined as follows
-
-\begin{LaTeXdescription}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the aggregator's public and private keys $pk_0$ and $sk_0$, and the user private keys $sk_i,\,1\leq i \leq n$.
-    \item[$\mathsf{Enc}(pk_0, x)$] The aggregator and users can encrypt any value~$x$ with the aggregator public key $pk_0$, and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, user $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the aggregator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
-\end{LaTeXdescription}
-
-We formalize the security notion of Linear-Combination Aggregator Obliviousness (LCAO) as the following game between attacker and challenger: %see appendix
-
-In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
 
@@
 \subsection{Estimation problem} \label{subsec:est_problem}
+
 The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
@@
 We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
+
+This has been captured in the associated secruity notions i nthe communication protocol
 
@@
 \section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}
+
+% From the crypto problem statement section - better suited here somewhere as IND-CPA and AO have not been introduced there yet
+From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
+To formalize the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
+
+In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
 

### 2021-05-20 main.tex
Draft for estimation part of the problem formulation complete

@@
 
+% Was in problem formulation but all motivations should be in the introduction instead
+We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
+It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
+The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
+
 Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
@@
 \section{Problem Statement} \label{sec:problem_statement}
-In this work, we consider the context of privacy-presering range-sensor navigation, in which we wish for no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
+In this work, we consider the context of privacy-preserving range-sensor navigation, in which we wish for no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
 The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-sensor navigation.
@@
 \subsection{Estimation problem} \label{subsec:est_problem}
-
-The localization scenario we consider in this work is that of Bayesian self-navigation using range-only sensors.
-We consider localization in the two-dimensional case for simplicity but will derive methods suitable for an extension to the three-dimensional equivalent.
-
-The navigator state captures the position and change in position ($\Delta$), and is of the form 
+The estimation problem we consider, for which we will reduce communication to the protocol required for the introduced cryptographic problem, is localisation with range-only sensors.
+In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent.
+The state that we wish to estimate captures the navigator position and the change in position ($\Delta$), and is given by
 \begin{equation}
@@
         x & \Delta x & y & \Delta y
-    \end{bmatrix}^\top\,. \label{eqn:state_def}
-\end{equation}
-A known process model is followed, in which the state at time $k$ is given by
-\begin{equation}
-    \rvec{x}_k = \vec{f}(\rvec{x}_{k-1})+\rvec{w}_k\,, \label{eqn:process_model}
-\end{equation}
-with zero-mean Gaussian process noise $\rvec{w}_k \sim \mathcal{N}(\vec{0},\mat{Q})$. The measurement model is dependent on sensor $i$ and given by
-\begin{equation}
-    \rv{z}_{k,i} = h_i(\rvec{x}_k)+\rv{v}_{k,i}\,, \label{eqn:measurement_model}
-\end{equation}
-with noise $\rv{v}_{k,i} \sim \mathcal{N}(0,r_i)$. The measurement function $h_i$, for sensor $i$ at location
+    \end{bmatrix}^\top\,. \label{eqn:state_definition}
+\end{equation}
+The state evolves following a known system model, which at timestep $k$ is given by
+\begin{equation}
+    \vec{x}_k = \vec{f}(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
+\end{equation}
+with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. The measurement model is dependent on sensor $i$'s location,
 \begin{equation}
@@
 \end{equation} 
-is defined as
+and is given by
+\begin{equation}
+    z_{k,i} = h_i(\vec{x}_k)+v_{k,i}\,, \label{eqn:measurement_model}
+\end{equation}
+with measurement noise variance $\mathsf{Var}[v_{k,i}] = r_i$ and measurement function $h_i$, for sensor $i$, as
 \begin{equation}
@@
 \end{equation}
-We wish to run a state estimation filter with models \eqref{eqn:process_model} and \eqref{eqn:measurement_model} such that all involved sensors $1 \leq i \leq n$ do not learn state estimates of $\rvec{x}_{k}$ and the navigator does not learn sensor locations $\vec{s}_i,\,1 \leq i \leq n$, measurement variances $r_i$ or their measurements $\rv{z}_{k,i}$ at any time $k$.
-We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
-It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
-The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
-
-% LEAKAGE
-
-Leakage of information will be discussed in more detail in Section \ref{subsec:leakage}, however, we stress that in any estimation problem where process and measurement models are known, knowledge of sequential state estimates as is the case at the navigator, or the knowledge of one or more measurements as is the case by one or more malicious sensors, naturally leads to the leakage of some information.
-For this reason, we accept that average sensor information may be leaked to the navigator and that less accurate estimates of location may be leaked to sensors.
-We will instead show that individual sensor information remains private to sensors and that the most precise localization estimate, requiring all measurements, remains private to the navigator.
-
-This has been captured in the associated secruity notions i nthe communication protocol
+
+Our aim is to provide a filter that estimates the navigator's state $\vec{x}_k$, at every timestep $k$, without learning sensor positions $\vec{s}_i$, measurements $z_{k,i}$ and measurement variances $r_i$ beyond information in the corresponding aggregation leakage function.
+Similarly, sensors should not learn any information about current state estimates or any other sensor information.
+Leakage will be further discussed in section \ref{subsec:leakage}, but we note that from any sequential state estimates, following known models, some sensor information leakage can be computed by the navigator.
+In the context of our leakage function, we will show that this corresponds to the global sums of private sensor information, while individual, or subsets of sensors', information remain private.
+Similarly, corrupted sensors with access to one or more measurements can produce state estimates of their own, leaking information about navigator state estimates, however, the most accurate estimates, requiring all measurements, will always remain private to the navigator.
 
@@
 When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
+
+% INTRO
+
+Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
+The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
+We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
 
@@
 
-% INTRO
-
-Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
-The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
-We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
-
 % ENCODING
@@
 
-Recalling the state definition \eqref{eqn:state_def} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
+Recalling the state definition \eqref{eqn:state_definition} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
 In addition, the Jacobian of $h_i$ at $\rvec{x}_{k|k-1}$,

### 2021-05-20 main.tex
Most of prelmiinaries section draft complete Remainder or encoding section is still to go

@@
 
-Our aim is to provide a filter that estimates the navigator's state $\vec{x}_k$, at every timestep $k$, without learning sensor positions $\vec{s}_i$, measurements $z_{k,i}$ and measurement variances $r_i$ beyond information in the corresponding aggregation leakage function.
+We aim to provide a filter that estimates the navigator's state $\vec{x}_k$, at every timestep $k$, without learning sensor positions $\vec{s}_i$, measurements $z_{k,i}$ and measurement variances $r_i$ beyond the information in the corresponding aggregation leakage function.
 Similarly, sensors should not learn any information about current state estimates or any other sensor information.
@@
 \section{Preliminaries} \label{sec:preliminaries}
-When defining our aggregation security requirements and encryption scheme we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.
-
-% INTRO
-
-Our next goal is to apply the LCAO secure encryption scheme introduced to a Bayesian localization filter.
-The filter we introduce requires the use of real-valued inputs and functions, and relies on a non-linear measurement model.
-We will make use of a real-number encoding scheme supporting our required homomorphic operations as well as a reformulated Extended Kalman Filter which reduces the filter update step to use only these operations.
-
-% SECURITY NOTIONS
-
-The security of a cryptographic scheme is typically defined by a security \textit{game}, which captures both the desired privacy guarantees, as well as the capabilities of attackers \cite{katzIntroductionModernCryptography2008}.
-The typical security notion for a homomorphic encryption scheme is Indistinguishability under Chosen Plaintext Attack (IND-CPA) \cite{chaseSecurityHomomorphicEncryption2017}, while for private aggregation schemes, the notion is Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
-\begin{definition}
-An encryption scheme meets IND-CPA security if an attacker who can choose plaintext messages to be encrypted at will, gains no additional information about an unknown plaintext message when they learn only its encryption.
-The formal security game and definition for IND-CPA has been given in Appendix .
-\end{definition}
-\begin{definition}
-An encryption scheme meets AO security if no colluding subset of participants \textit{excluding} the aggregator gains additional information about the remaining aggregation values given only their encryptions, while any colluding subset \textit{including} the aggregator learns only their sum.
-The formal security game and definition for AO has been given in Appendix .
-\end{definition}
-
-The Paillier encryption scheme and the Joye-Libert private aggregation scheme meet the IND-CPA and AO security notions respectively, and are given below.
+When proposing an encryption scheme meeting the LCAO notion, we will base our method on the additively homomorphic Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} and the Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013}.
+These schemes have been summarised below.
+Additionally, the estimation problem we consider uses real-valued inputs and functions, and will require encoding real numbers for use with the aforementioned encryption schemes.
+The method used for encoding has been summarised afterwards.
 
@@
 \subsection{Paillier Encryption Scheme} \label{subsec:paillier_scheme}
-The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme which bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
+The Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} is an additively homomorphic encryption scheme that bases its security on the decisional composite residuosity assumption (DCRA) and meets the security notion of IND-CPA.
 Key generation of the Paillier scheme is performed by choosing two sufficiently large primes $p$ and $q$, and computing $N=pq$.
@@
 for a randomly chosen $\rho \in \mathbb{Z}_{N}$.
-$\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
+Here, $\rho^N$ can be considered the noise term which hides the value $g^a \pmod{N^2}$, which due to the scheme construction, is an easily computable discrete logarithm.
 The decryption of a ciphertext is computed by
@@
 
-\subsection{Joye-Libert Private Aggregation Scheme} \label{subsec:joye_libert_scheme}
-The Joye-Libert private aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data, that we refer to as instances for consistency, and meets the security notion of AO.
+\subsection{Joye-Libert Privacy-preserving Aggregation Scheme} \label{subsec:joye_libert_scheme}
+The Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
 Similarly to the Paillier scheme, it bases its security on the DCRA.
-A notable difference to a public-key encryption scheme is the need for a trusted party to perform an initial key generation and distribution step.
-
-Key generation is computed by choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
-Additionally, hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined, and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to all $n$ users (whose values are to be aggregated), while the last key is set as
+A notable difference to a public-key encryption scheme is its need for a trusted party to perform the initial key generation and distribution.
+
+Key generation is computed by first choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
+A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$.
+$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
 \begin{equation}
@@
 \begin{equation}
-    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,,
-\end{equation}
-where $H(t)^{sk_i}$ can be considered the noise term which hides the again easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$.
+    c^{(t)}_{i} = (N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2}\,.
+\end{equation}
+Here, we can consider $H(t)^{sk_i}$ the noise term which hides the easily computable discrete logarithm $g^{a^{(t)}_{i}} \pmod{N^2}$, where $g=N+1$ (as with the Paillier scheme above).
 
@@
 \begin{equation}
-    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2}
+    c^{(t)} = H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \label{eqn:agg_summation}
 \end{equation}
@@
         \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
-        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}
+        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
     \end{split}
@@
 \subsection{Integer Encoding for Real Numbers} \label{subsec:encoding}
-
-% ENCODING
-
-In the encryption scheme introduced, weights and values are restricted to integers and all operations are computed $\pmod{N}$, thus bounding meaningful inputs to $\{a \,|\, a \in \mathbb{Z}_N\}$.
-For this reason, a quantization and integer mapping method for real numbers is required for their encryption and homomorphic processing.
-We quantize with a generalized Q number format \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
-
-We define a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$.
-This contrasts with the common definition given in terms of total bits and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not powers of two.
-Rational subset $\mathbb{Q}_{M,\phi}$ is given by
+In both the Paillier and Joye-Libert schemes, as well as the one we introduce, meaningful inputs $a$ are bounded to $a \in \mathbb{Z}_N$.
+For this reason, real-valued estimation variables require quantisation and integer mapping for encryption and aggregation.
+We will rely on a generalised Q number encoding \cite{oberstarFixedPointRepresentationFractional2007} due to implementation simplicity and applicability.
+
+We will consider a subset of rational numbers in terms of a range $M \in \mathbb{N}$ and fractional precision $\phi \in \mathbb{N}$.
+This contrasts with the common definition in terms of total and fractional bits \cite{oberstarFixedPointRepresentationFractional2007,schulzedarupEncryptedCooperativeControl2019,farokhiSecurePrivateControl2017}, but allows for a direct mapping to integer ranges which are not a power of two.
+A rational subset $\mathbb{Q}_{M,\phi}$ is then given by
 \begin{equation}
@@
 \end{equation}
-and we quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$.
-That is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
-In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to the encryption scheme range $\mathbb{Z}_N$ is achieved by choosing $M=N$, and handling negatives with modulo arithmetic.
-In addition, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication, which is not supported by our encryption scheme.
+and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
+In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and the handling negatives by modulo arithmetic.
+Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication.
 This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.
 
-The function for \textit{combined} quantization and encoding $\mathsf{E}_{M,\phi,d}(a)$, of a given real number $a \in \mathbb{R}$, integer range $\mathbb{Z}_M$, and the desired scaling for $d$ prior encoded multiplications, is given by
+The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$, for an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications, is given by
 \begin{equation}
@@
 
+% TODO up to here
+
 This encoding scheme provides the following homomorphic operations,
@@
 noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
+
+%should also reference the modulo sum in the J-L scheme (which is missing in Eq. 14!!)
 

### 2021-05-21 main.tex
Draft for section on our linear-combination aggregator oblivious scheme finished Proof has been moved to appendix and both appendix section draft finished as well

@@
 \end{equation}
-with measurement noise variance $\mathsf{Var}[v_{k,i}] = r_i$ and measurement function $h_i$, for sensor $i$, as
+with Gaussian measurement noise $v_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$, as
 \begin{equation}
@@
 \begin{equation}
-    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N}\,. \label{eqn:agg_decryption}
+    \sum^{n}_{i=1}a^{(t)}_{i} = \frac{c^{(t)}-1}{N} \pmod{N}\,. \label{eqn:agg_decryption}
 \end{equation}
@@
 and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
-In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and the handling negatives by modulo arithmetic.
+In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and handling negatives by modulo arithmetic.
 Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication.
@@
 
-% TODO up to here
-
 This encoding scheme provides the following homomorphic operations,
@@
 \end{equation}
-noting that when $M=N$, the modulus corresponds with the encrypted homomorphic operations in \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and therefore \eqref{eqn:our_scheme_lin_comb}.
-
-%should also reference the modulo sum in the J-L scheme (which is missing in Eq. 14!!)
-
-The choice of a high fractional precision $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, however, risks an overflow following too many multiplications.
-Given the largest number of expected multiplications $d_{max}$, and the largest expected decoded value $a_{max}$, the parameter should be chosen such that the following condition holds
+noting that when $M=N$, the modulus corresponds with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and the Joye-Libert sum \eqref{eqn:agg_decryption}.
+
+In general, the choice of a large precision parameter $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications.
+Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
 \begin{equation}
@@
 \section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}
-
-% From the crypto problem statement section - better suited here somewhere as IND-CPA and AO have not been introduced there yet
-From the informal definitions above, it is clear that weights encrypted by an IND-CPA secure encryption scheme are sufficient for the first requirement, while a scheme satisfying AO is not sufficient for the second.
-To formalize the second requirement, we define a novel encryption type ``Linear-Combination Aggregator Oblivious Encryption'' and an accompanying security game, which capture the additional weights and modified leakage of AO.
-
-In the next section, we will give a solution to an encryption scheme meeting LCAO security, with IND-CPA secure weight encryption, and give a cryptographic proof for its security.
-
-% OUR SCHEME MEETING LCAO SECURITY
-
-\label{subsec:our_scheme}
-Our scheme is based on the Paillier and Joye-Libert schemes introduced in Sections \ref{subsec:paillier_scheme} and \ref{subsec:joye_libert_scheme}, and similarly bases its security on the DCRA.
-As with Joye-Libert's private aggregation scheme, a trusted party is required for the initial distribution of user secret keys.
-Below, we give definitions for the four algorithms comprising the linear-combination aggregation encryption scheme.
-
+In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}.
+The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting LCAO.
+Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution.
+The four algorithms defining our scheme are given as follows.
 \begin{LaTeXdescription}
     \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
-Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose an $m>1$ as the number of weights to combine, and set public parameter $\mathsf{pub}=H$, aggregator public key $pk_0 = N$ and aggregator private key $sk_0=(p,q)$.
-The remaining user secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
-
-    \item[$\mathsf{Enc}(pk_0, x)$] Encryption of values is computed as a Paillier encryption with implicit generator $g=N+1$. This is given by
+Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine $m>1$ and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
+Sensor secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
+
+    \item[$\mathsf{Enc}(pk_0, x)$] Public-key encryption is computed by the Paillier encryption scheme with implicit generator $g=N+1$. This is given by
     \begin{equation}
@@
 
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] The linear combination encryption step at instance $t$ is computed as
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] Encrypted linear combination at instance $t$ is computed as
     \begin{equation}
@@
 
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing aggregation noise terms, and is followed by Paillier decryption
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
     \begin{equation}
@@
     \end{equation}
-    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of aggregation can be seen from
+    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of the aggregation can be seen from
     \begin{align*}
@@
 \end{LaTeXdescription}
-
-Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers, and that resulting linear combinations and summations are computed $\pmod{N}$.
-
+Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed $\pmod{N}$.
+
+The security proof of this scheme must show that both encrypted weights meet IND-CPA and encrypted aggregation meets LCAO.
+As weights are encrypted with the Paillier encryption scheme, the first requirement is already met.
+To show that aggregation meets LCAO, a reduction proof is given in appendix \ref{app:proof}.
+
+Lastly, we make the following remark about a possible implicit weight.
 \begin{remark} \label{rem:lcao_implicit_weight}
-    The construction of this scheme additionally supports the linear combination of the implicit weight, $\omega^{(t)}_j = 1$, by replacing
+    The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
     \begin{equation}
@@
     \end{equation}
-    in \eqref{eqn:our_scheme_lin_comb} by
-    \begin{equation}
-        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,,
-    \end{equation}
-    due to the removal of $\rho_j^N$ terms during decryption. This can be used to reduce the broadcast communication cost by one weight.
+    in \eqref{eqn:our_scheme_lin_comb}, by
+    \begin{equation}
+        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,.
+    \end{equation}
+    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by a single weight when it is known that $\omega^{(t)}_j=1$.
 \end{remark}
-
-% PROOF
-
-To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights.
-From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme and therefore meet security notion IND-CPA.
-We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.
-
-To show our scheme meets the security notion of LCAO, we prove by contrapositive that for an adversary $\mathcal{A}$ playing against a challenger using \textit{our scheme}, we can create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the \textit{Joye-Libert scheme}, such that
-\begin{equation*}
-    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
-\end{equation*}
-for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
-(\textit{i.e.}, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) Given the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, we know our scheme must be LCAO secure and will thus conclude our proof.
-The proof overview has been given in Figure \ref{fig:proof_summary}.
-Additionally, the function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
-
-\begin{figure}[htbp]
-\centering
-\vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.95]
-    % Bounding box
-    \draw [gray] (0,0) rectangle (6.5,6.5);
-
-    % Outer adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
-    % Inner adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);
-
-    % Adversaries and challenger
-    \node at (3.25,3) {\Large$\mathcal{A}'$};
-    \node at (3.25,5.5) {\Large$\mathcal{A}$};
-    \node at (3.25,0.5) {\Large$\mathcal{C}$};
-
-    % Arrows
-    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
-    \draw [-latex] (2,1.75) -- (2,2.5);
-
-    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
-    \draw [-latex] (2,4.5) --(2,5);
-
-    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
-    \draw [-latex] (4.5,5) -- (4.5,4.5);
-
-    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
-    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
-\end{tikzpicture}
-\caption{High-level overview of our scheme's LCAO security proof.}
-\vspace{-\baselineskip}
-\label{fig:proof_summary}
-\end{figure}
 
@@
 \section{Linear-Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
+The following game between attacker and challenger defines the security notion of LCAO.
 \begin{LaTeXdescription}
@@
 
-\section{Proof of our scheme security} \label{app:proof}
+\section{LCAO Scheme Proof} \label{app:proof}
+The scheme in section \ref{sec:lcao_scheme} will be shown to meet LCAO by contrapositive.
+We show that for an adversary $\mathcal{A}$ playing against a challenger using the scheme, we can always create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the Joye-Libert scheme, such that
+\begin{equation*}
+    \mathsf{Adv}^{LCAO}(\mathcal{A}) > \eta_1(\kappa) \implies \mathsf{Adv}^{AO}(\mathcal{A}') > \eta_2(\kappa)\,,
+\end{equation*}
+for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
+That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}).
+The reduction has been summarised visually in figure \ref{fig:proof_summary}.
+\begin{figure}[htbp]
+\centering
+\vspace{\baselineskip}
+\begin{tikzpicture}[font=\footnotesize,scale=0.95]
+    % Bounding box
+    \draw [gray] (0,0) rectangle (6.5,6.5);
+
+    % Outer adversary rectangle
+    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
+    % Inner adversary rectangle
+    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);
+
+    % Adversaries and challenger
+    \node at (3.25,3) {\Large$\mathcal{A}'$};
+    \node at (3.25,5.5) {\Large$\mathcal{A}$};
+    \node at (3.25,0.5) {\Large$\mathcal{C}$};
+
+    % Arrows
+    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
+    \draw [-latex] (2,1.75) -- (2,2.5);
+
+    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
+    \draw [-latex] (2,4.5) --(2,5);
+
+    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
+    \draw [-latex] (4.5,5) -- (4.5,4.5);
+
+    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
+    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
+\end{tikzpicture}
+\caption{Summary of our LCAO security proof.}
+\vspace{-\baselineskip}
+\label{fig:proof_summary}
+\end{figure}
 \begin{proof}
-    Consider adversary $\mathcal{A}$ playing the LCAO game defined in Section .
-The following is a construction of an adversary $\mathcal{A}'$ playing the AO game in Appendix  against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme from Section \ref{subsec:joye_libert_scheme}.
+    Consider adversary $\mathcal{A}$ playing the LCAO game.
+The following is a construction of an adversary $\mathcal{A}'$ playing the AO game \cite{shiPrivacyPreservingAggregationTimeSeries2011} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme.
     \begin{LaTeXdescription}
@@
 
-    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme from Section \ref{subsec:joye_libert_scheme} exactly, and to $\mathcal{A}$, $\mathcal{A}'$ follows our scheme in Section  exactly.
-Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-neglibile advantage adversary to $\mathcal{C}$ exists \cite{joyeScalableSchemePrivacyPreserving2013}, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
+    In the above construction, $\mathcal{C}$ follows the Joye-Libert scheme exactly, and to $\mathcal{A}$, $\mathcal{A}'$ follows the scheme in section \ref{sec:lcao_scheme} exactly.
+Since $\mathcal{A}'$ runs in polynomial-time to security parameter when $\mathcal{A}$ does, and no non-negligible advantage adversary to $\mathcal{C}$ exists, we conclude that no non-negligible advantage adversary $\mathcal{A}$ exists.
 That is, there exists a negligible function $\eta$, such that
@@
     for security parameter $\kappa$.
+Lastly, the function $H$ used by our scheme is treated as a random oracle in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
 \end{proof}

### 2021-05-21 main.tex
Removed the proof summary image as it is not so important in the appendix

@@
 That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}).
-The reduction has been summarised visually in figure \ref{fig:proof_summary}.
-\begin{figure}[htbp]
-\centering
-\vspace{\baselineskip}
-\begin{tikzpicture}[font=\footnotesize,scale=0.95]
-    % Bounding box
-    \draw [gray] (0,0) rectangle (6.5,6.5);
-
-    % Outer adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!30] (0.25,6.25) rectangle (6.25,2.5);
-    % Inner adversary rectangle
-    \draw[rounded corners=15pt, fill=gray!60] (0.5,6) rectangle (6,5);
-
-    % Adversaries and challenger
-    \node at (3.25,3) {\Large$\mathcal{A}'$};
-    \node at (3.25,5.5) {\Large$\mathcal{A}$};
-    \node at (3.25,0.5) {\Large$\mathcal{C}$};
-
-    % Arrows
-    \node[text width=3cm, align=center] at (2,1) {Joye-Libert\\AO secure\\scheme};
-    \draw [-latex] (2,1.75) -- (2,2.5);
-
-    \node[text width=3cm, align=center] at (2,3.75) {Our\\LCAO secure\\scheme};
-    \draw [-latex] (2,4.5) --(2,5);
-
-    \node[text width=3cm, align=center] at (4.5,3.75) {``Break''\\Our scheme};
-    \draw [-latex] (4.5,5) -- (4.5,4.5);
-
-    \node[text width=3cm, align=center] at (4.5,1) {``Break''\\Joye-Libert\\scheme};
-    \draw [-latex] (4.5,2.5) -- (4.5,1.75);
-\end{tikzpicture}
-\caption{Summary of our LCAO security proof.}
-\vspace{-\baselineskip}
-\label{fig:proof_summary}
-\end{figure}
 \begin{proof}

### 2021-05-26 main.tex
Draft for private localisation and measurement modification sections done Still not certain if it makes sense to give measurement modification before the linear combination rearrangement of i and I - to be discussed

@@
 Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
-$\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
+$\mathsf{E}[\cdot]$ and $\mathsf{Var}[\cdot]$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
 Additionally, key $k$ may be ommited when inferrable from context.
@@
 \section{Privacy-Preserving Localization} \label{sec:priv_localization}
-With the relevant preliminaries, we now apply the LCAO secure scheme to our original localization problem.
-Recall we are considering a navigator in the presence of $n$ range sensors.
-The navigator runs a local filter, computing its update step with equations  and , where received information from each sensor $i$ consists of the measurement vector
-\begin{equation}
-    \rvec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (\rv{z}_{k,i} - h_i(\rvec{x}_{k|k-1}) + \mat{H}_{k,i}\rvec{x}_{k|k-1}) \label{eqn:measurement_vec}
+To produce an estimate of the state $\vec{x}_k$ such that communication between $n$ range sensors and the navigator is reducible to the linear-combination aggregation protocol, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation.
+The EIF update step requires the predicted state estimate $\vec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
+\begin{equation}
+    \vec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
+\end{equation}
+respectively. In this form, the update equations for $n$ sensor measurements at time $k$, given process and measurement models \eqref{eqn:system_model} and \eqref{eqn:measurement_model}, are given by
+\begin{equation}
+    \begin{split}
+        &\vec{y}_{k|k} = \vec{y}_{k|k-1} + \\
+        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1})
+    \end{split} \label{eqn:eif_info_vec_update}
+\end{equation}
+and
+\begin{equation}
+    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \mat{H}_{k,i}\,, \label{eqn:eif_info_mat_update}
+\end{equation}
+with Jacobians
+\begin{equation}
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
+\end{equation}
+for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\vec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
+\begin{equation}
+    \vec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\vec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
+\end{equation}
+before using the normal EKF prediction equations
+\begin{equation}
+    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,,
+\end{equation}
+with Jacobian
+\begin{equation}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\vec{x}_{k|k}}\,. \label{eqn:jacobian_f}
+\end{equation}
+
+In the form above, at every timestep $k$, all sensitive sensor information required for state estimation is captured in the measurement vector
+\begin{equation}
+    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1}) \label{eqn:measurement_vec}
 \end{equation}
@@
 \end{equation}
-at each time-step $k$.
-In this form, all sensitive sensor information is exclusively found in $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
-Namely, their measurements $\rv{z}_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-
-The reason for using a linear-combination aggregation scheme in this scenario is due to wanting to compute $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ at the sensors, which would require the navigator to disclose some information in $\rvec{x}_{k|k-1}$ for the computing of Jacobians $\mat{H}_{k,i}$.
-We want to reformulate $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ such that the sensors can use the LCAO secure scheme, with location information in $\rvec{x}_{k|k-1}$ as the weights from the navigator.
-As was shown in Section , this will guarantee that sensors cannot learn navigator location information $\rvec{x}_{k|k-1}$, and that the navigator cannot learn individual sensor values required for computing $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$.
-From \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} we see that such a linear reformulation will set requirements on the possible measurement functions $h_i$.
+namely, their measurements $z_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
+$\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, also require the current predicted state estimate $\vec{x}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
+For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (weights), and subsequently aggregated at the navigator.
+Application of the linear-combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and that the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
 
@@
 
-% INTRO
-
-Recalling the state definition \eqref{eqn:state_definition} and two-dimensional measurement model \eqref{eqn:measurement_model}, we can see that $h_i$ \textit{cannot} be rearranged to a linear combination of elements private to the navigator.
-In addition, the Jacobian of $h_i$ at $\rvec{x}_{k|k-1}$,
+The first thing we note when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\vec{x}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
+Similarly, the Jacobian of $h_i$ at $\vec{x}_{k|k-1}$,
 \begin{equation}
@@
     \begin{bmatrix}
-        \frac{\rv{x}_{k|k-1} - s_{x,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} \\
-        \frac{\rv{y}_{k|k-1} - s_{y,i}}{\sqrt{(\rv{x}_{k|k-1} - s_{x,i})^2 + (\rv{y}_{k|k-1} - s_{y,i})^2}} 
+        \frac{x_{k|k-1} - s_{x,i}}{\sqrt{(x_{k|k-1} - s_{x,i})^2 + (y_{k|k-1} - s_{y,i})^2}} \\
+        \frac{y_{k|k-1} - s_{y,i}}{\sqrt{(x_{k|k-1} - s_{x,i})^2 + (y_{k|k-1} - s_{y,i})^2}} 
     \end{bmatrix}\,,
 \end{equation}
-cannot be either. Therefore, we consider the modified measurement functions
+cannot be either. We, therefore, consider the modified measurement functions
 \begin{equation}
@@
 \end{equation}
-A measurement function in this form allows rearrangement to a linear combination of navigator information, and thus of the corresponding modified measurement vector $\rvec{i}'_{k,i}$ and measurement matrix $\mat{I}'_{k,i}$ as well.
-The modified measurement functions $h'_i$ can be written as
+A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\vec{x}_{k|k-1}$, as
 \begin{equation}
@@
 \end{equation}
-and the corresponding Jacobians $\mat{H}'_{k,i}$ as
+and
 \begin{equation}
@@
     \begin{bmatrix}
-        2\rv{x}_{k|k-1} - 2s_{x,i} \\
-        2\rv{y}_{k|k-1} - 2s_{y,i}
+        2x_{k|k-1} - 2s_{x,i} \\
+        2y_{k|k-1} - 2s_{y,i}
     \end{bmatrix}\,. \label{eqn:modified_jacobian}
 \end{equation}
-From the above we see that $h'_i(\rvec{x}_{k|k-1})$ and $\mat{H}'_{k,i}$ can be rearranged as linear combinations of the weights $\rv{x}_{k|k-1}^2$, $\rv{y}_{k|k-1}^2$, $\rv{x}_{k|k-1}$ and $\rv{y}_{k|k-1}$, which capture all the required information that is private to the navigator.
-
-To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be formulated in a similar manner using , we require the existance of a modified measurement model of the form
-\begin{equation}
-    \rv{z}'_{k,i} = h'_i(\rvec{x}_k)+\rv{v}'_{k,i}\,, \label{eqn:modified_measurement_model}
-\end{equation}
-where $\rv{z}'_{k,i}$ is the modified measurement, and noise $\rv{v}'_{k,i}$ is zero-mean with known variance.
-The approximation of $\rv{z}'_{k,i}$ and its noise variance $\rv{r}_{k,i}$ from original measurements and variances $\rv{z}_{k,i}$ and $r_i$ will be shown in Section \ref{subsec:range_measurement_mod}.
-
-% REST
-
-In Section , we assumed the existance of a measurement model \eqref{eqn:modified_measurement_model} where modified sensor measurements $\rv{z}'_{k,i}$ had zero-mean noises with variances $\rv{r}_{k,i}$.
-In practice, conversion of range measurements $\rv{z}_{k,i}$ to $\rv{z}'_{k,i}$ is complicated by the noise term $\rv{v}_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
-Squaring the range measurement produces
-\begin{equation}
-    \begin{split}
-        \rv{z}_{k,i}^2 &= (h_i(\rvec{x}_k) + \rv{v}_{k,i})^2 \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 \\
-        &= h'_i(\rvec{x}_k) + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2\,,
+Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $x_{k|k-1}^2$, $y_{k|k-1}^2$, $x_{k|k-1}$ and $y_{k|k-1}$.
+To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be similarly rearranged, we also require the existence of measurements following a modified measurement model of the form
+\begin{equation}
+    z'_{k,i} = h'_i(\vec{x}_k)+v'_{k,i}\,, \label{eqn:modified_measurement_model}
+\end{equation}
+where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r_{k,i}$.
+
+The approximation of $z'_{k,i}$ and its variance $\mathsf{Var}[v'_{k,i}]$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
+Squaring the original range measurements produces
+\begin{equation}
+    \begin{split}
+        z_{k,i}^2 &= (h_i(\vec{x}_k) + v_{k,i})^2 \\
+        &= h'_i(\vec{x}_k) + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2\,,
     \end{split}
 \end{equation}
-with new noise term, $2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2$, now dependent on the measurement function $h_i$ and no longer zero-mean or Gaussian.
-We can compute the mean of the new noise term (a function of the Gaussian term $\rv{v}_{k,i}$) as
-\begin{equation}
-    \E{2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2} = r_i\, \label{eqn:modified_noise_mean}
-\end{equation}
-and define modified measurements as
+with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean or Gaussian.
+We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
+\begin{equation}
+    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
+\end{equation}
+and mean-adjust modified measurements as
 \begin{equation} \label{eqn:modified_measurement}
     \begin{split}
-        \rv{z}'_{k,i} &= \rv{z}_{k,i}^2 - r_i \\
-        &= h_i(\rvec{x}_k)^2 + 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i \\
-        &= h'_i(\rvec{x}_k) + \rv{v}'_{k,i}\,,
+        z'_{k,i} &= z_{k,i}^2 - r_i \\
+        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
+        &= h'_i(\vec{x}_k) + v'_{k,i}\,,
     \end{split}
 \end{equation}
-with now zero-mean noise $\rv{v}'_{k,i} = 2h_i(\rvec{x}_k)\rv{v}_{k,i} + \rv{v}_{k,i}^2 - r_i$. The noise in this case (again a function of white Gaussian term $\rv{v}_{k,i}$) has variance 
-\begin{equation}
-    \Var{\rv{v}'_{k,i}} = 4h_i(\rvec{x}_k)^2r_i + 2r_i^2
-\end{equation}
-and is dependent on $h_i(\rvec{x}_k)$.
-To use the modified measurement function \eqref{eqn:modified_measurement} with an EIF, we require an estimate of its noise variance using only the values available to the sensor, $\rv{z}_{k,i}$ and $r_i$.
-A conservative estimate of the variance (\textit{i.e.}, a larger estimate resulting in less confidence in measurements) is desirable to avoid increasing the likeliness of filter divergence.
-While replacing $h_i(\rvec{x}_k)$ with $\rv{z}_{k,i}$ only provides a conservative estimate when
-\begin{equation}
-    \begin{split}
-        &\rv{z}_{k,i} > h_i(\rvec{x}_k) \\
-        \implies &\rv{z}_{k,i} - h_i(\rvec{x}_k) > 0 \\
-        \implies &\rv{v}_{k,i} > 0\,,
+with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
+\begin{equation}
+    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
+\end{equation}
+and is also dependent on $h_i(\vec{x}_k)$.
+To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well.
+Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence.
+The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
+\begin{equation}
+    \begin{split}
+        &z_{k,i} > h_i(\vec{x}_k) \\
+        \implies &v_{k,i} > 0\,,
     \end{split}
 \end{equation}
-and cannot be guaranteed, we can instead provide a conservative estimate with $95\%$ confidence, by shifting measurement $\rv{z}_{k,i}$ by two standard deviations $\sqrt{r_i}$.
-Thus, the modified measurement variance for sensor $i$ at time $k$ is conservatively approximated by
-\begin{equation}
-    \begin{split}
-        \rv{r}_{k, i} &= 4(\rv{z}_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
-        &\gtrapprox \Var{\rv{v}'_{k,i}}
+which cannot be guaranteed.
+Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$.
+The modified measurement's variance at time $k$ is therefore conservatively approximated by
+\begin{equation}
+    \begin{split}
+        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
+        &\gtrapprox \Var{v'_{k,i}}
     \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
 \end{equation}
-Together, the model and variance, \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, provide a suitable substitute for the required measurement model \eqref{eqn:modified_measurement_model} and can be used to achieve the desired linear properties using only the available range sensors.
-
-% % 
-% % ##     ##   ### ##     ## ###      ########  ########  #######   ######  
-% % ##     ##  ##    ##   ##    ##     ##     ## ##       ##     ## ##    ## 
-% % ##     ## ##      ## ##      ##    ##     ## ##       ##     ## ##       
-% % ######### ##       ###       ##    ########  ######   ##     ##  ######  
-% % ##     ## ##      ## ##      ##    ##   ##   ##       ##  ## ##       ## 
-% % ##     ##  ##    ##   ##    ##     ##    ##  ##       ##    ##  ##    ## 
-% % ##     ##   ### ##     ## ###      ##     ## ########  ##### ##  ######  
-% %
-
-% \subsection{Measurement Model Requirements}
-% From the definition of matrix multiplication, we know that matrices whose elements are linear combinations of weights can be multiplied to produce elements of new linear combinations, with new weights as functions dependent only on weights from the original matrices.
-For example, consider dimension $D\times D$ matrices $\mat{A}$ and $\mat{B}$, where element $(v,w)$ in matrix $\mat{A}$ is of the form $\sum_{i=0}^W a_{i,v,w}x_{i,v,w}$ and similarly for matrix $\mat{B}$, the form $\sum_{i=0}^W b_{i,v,w}y_{i,v,w}$.
-If we consider $a_{i,v,w}$ and $b_{i,v,w}$ as the weight terms, we can write element $(v,w)$ of a product matrix $\mat{A}\mat{B}$, as a linear combination of functions dependent only on these weights, as
-% \begin{equation}
-%     \begin{split}
-%         \sum_{d=0}^D&\left(\left(\sum_{i=0}^W a_{i,v,d}x_{i,v,d}\right)\left(\sum_{i=0}^W b_{i,d,w}y_{i,d,w}\right)\right) \\
-%         &=\sum_{d=0}^N\left(\sum_{i=0}^W\sum_{j=0}^W a_{i,v,d}x_{i,v,d}b_{j,d,w}y_{j,d,w}\right) \\
-%         &=\sum_{d=0}^N\sum_{i=0}^W\sum_{j=0}^W (a_{i,v,d}b_{j,d,w})x_{i,v,d}y_{j,d,w}\,.
-%     \end{split} \label{eqn:matrix_mult_weights}
-% \end{equation}
-% Similarly, scalar multiplication also holds this property.
-It is, therefore, sufficient for $h_i$ and $\mat{H}_{k,i}$ to be linear combinations of information private to the navigator, for $\rvec{i}_{k,i}$ and $\mat{I}_{k,i}$ to be as well.
-Next, we will show how this can be achieved for the specific case of two-dimensional range-only localization.
+for each sensor $i$.
+
+The existence of modified measurements $z'_{k,i}$ and their estimated variances $r_{k, i}$ are sufficient for sensors to compute measurement vector $\vec{i}_{k,i}$ and matrix $\mat{I}_{k,i}$ in the required form for linear-combination aggregation.
 
@@
 \subsection{Localization} \label{subsec:localization}
-With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in the same form as , by
+As $h'_i$ and $\mat{H}'_{k,i}$ can be written as linear combinations of powers of location elements in $\vec{x}_{k|k-1}$, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ can too.
+
+After modifying measurements by . to produce modified measurement functions and Jacobians . and .,
+
+With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in a similar form by
 \begin{equation}

### 2021-05-27 main.tex
Rest of localisation section draft Still not happy with this and previous section - will get benjamin to look at it

@@
 \subsection{Localization} \label{subsec:localization}
-As $h'_i$ and $\mat{H}'_{k,i}$ can be written as linear combinations of powers of location elements in $\vec{x}_{k|k-1}$, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ can too.
-
-After modifying measurements by . to produce modified measurement functions and Jacobians . and .,
-
-With the existence of \eqref{eqn:modified_measurement_model}, measurement vector and measurement matrix linear combinations can be given in a similar form by
-\begin{equation}
-    \begin{split}
-        \rvec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}(\rv{z}'_{k,i} - h'_i(\rvec{x}_{k|k-1}) + \mat{H}'_{k,i}\rvec{x}_{k|k-1}) \\
+Now that range measurements can be modified by \eqref{eqn:modified_measurement}, and the modified model \eqref{eqn:modified_measurement_model} can be used, corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be computed as linear combinations of powers of location elements.
+This is given by
+\begin{equation}
+    \begin{split}
+        \vec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}(z'_{k,i} - h'_i(\vec{x}_{k|k-1}) + \mat{H}'_{k,i}\vec{x}_{k|k-1}) \\
         &= 
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1}^2 \\
-                &\quad+ (-\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1}^2 \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{x}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{x}_{k|k-1}\\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{x}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{x,i}^3) \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2\rv{r}_{k,i}^{-1}s_{x,i} \rv{z}'_{k,i})
+                &(2r_{k,i}^{-1})x_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}y_{k|k-1}^2 \\
+                &\quad+ (-r_{k,i}^{-1}s_{x,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{x,i})y_{k|k-1}^2 \\
+                &\quad+ (2r_{k,i}^{-1}z'_{k,i})x_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)x_{k|k-1}\\
+                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)x_{k|k-1} + (2r_{k,i}^{-1}s_{x,i}^3) \\
+                &\quad+ (2r_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{-1}s_{x,i} z'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^3 + (2\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2\rv{y}_{k|k-1} \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}^2 + (-2\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1}^2 \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}\rv{z}'_{k,i})\rv{y}_{k|k-1} + (-2\rv{r}_{k,i}^{-1}s_{x,i}^2)\rv{y}_{k|k-1} \\
-                &\quad+ (-2\rv{r}_{k,i}^{-1}s_{y,i}^2)\rv{y}_{k|k-1} + (2\rv{r}_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
-                &\quad+ (2\rv{r}_{k,i}^{-1}s_{y,i}^3) + (-2\rv{r}_{k,i}^{-1}s_{y,i}\rv{z}'_{k,i})
+                &(2r_{k,i}^{-1})y_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}^2y_{k|k-1} \\
+                &\quad+ (-2r_{k,i}^{-1}s_{y,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{y,i})y_{k|k-1}^2 \\
+                &\quad+ (2r_{k,i}^{-1}z'_{k,i})y_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)y_{k|k-1} \\
+                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)y_{k|k-1} + (2r_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
+                &\quad+ (2r_{k,i}^{-1}s_{y,i}^3) + (-2r_{k,i}^{-1}s_{y,i}z'_{k,i})
             \end{split}
@@
     \begin{split}
-        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} \rv{r}_{k,i}^{-1}\mat{H}'_{k,i} \\
+        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}\mat{H}'_{k,i} \\
         &=
@@
 \begin{align*}
-    \beta_{11} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{x,i})\rv{x}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}^2)\,, \\
-    \begin{split}
-        \beta_{12} &= (4\rv{r}_{k,i}^{-1})\rv{x}_{k|k-1}\rv{y}_{k|k-1} + (-4\rv{r}_{k,i}^{-1}s_{y,i})\rv{x}_{k|k-1}  \\
-        &\qquad+ (-4\rv{r}_{k,i}^{-1}s_{x,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{x,i}s_{y,i})\,,
+    \beta_{11} &= (4r_{k,i}^{-1})x_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{x,i})x_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}^2)\,, \\
+    \begin{split}
+        \beta_{12} &= (4r_{k,i}^{-1})x_{k|k-1}y_{k|k-1} + (-4r_{k,i}^{-1}s_{y,i})x_{k|k-1}  \\
+        &\qquad+ (-4r_{k,i}^{-1}s_{x,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}s_{y,i})\,,
     \end{split}\\
     \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
-    \beta_{22} &= (4\rv{r}_{k,i}^{-1})\rv{y}_{k|k-1}^2 + (-8\rv{r}_{k,i}^{-1}s_{y,i})\rv{y}_{k|k-1} + (4\rv{r}_{k,i}^{-1}s_{y,i}^2)\,.
+    \beta_{22} &= (4r_{k,i}^{-1})y_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{y,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{y,i}^2)\,.
 \end{align*}
-The above rearrangements result in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of the weights 
-\begin{equation}
-    \begin{split}
-        &\langle \rv{x}_{k|k-1}^3,\ \rv{y}_{k|k-1}^3,\ \rv{x}_{k|k-1}^2\rv{y}_{k|k-1},\ \rv{x}_{k|k-1}\rv{y}_{k|k-1}^2,\\
-        &\quad \rv{x}_{k|k-1}^2,\ \rv{y}_{k|k-1}^2,\ \rv{x}_{k|k-1}\rv{y}_{k|k-1},\ \rv{x}_{k|k-1},\ \rv{y}_{k|k-1}\rangle\,,
+The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of
+\begin{equation}
+    \begin{split}
+        &\{ x_{k|k-1}^3,\ y_{k|k-1}^3,\ x_{k|k-1}^2y_{k|k-1},\ x_{k|k-1}y_{k|k-1}^2,\\
+        &\quad x_{k|k-1}^2,\ y_{k|k-1}^2,\ x_{k|k-1}y_{k|k-1},\ x_{k|k-1},\ y_{k|k-1}\}\,,
     \end{split} \label{eqn:weights_to_broadcast}
 \end{equation}
-which again capture all the required information private to the navigator.
-
-The final step required for the application of our LCAO secure encryption scheme to the linear combinations \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} is the handling of the scheme's instance variable $t$ in \eqref{eqn:our_scheme_lin_comb}.
-As six linear-combination aggregations occur at each time-step $k$ (four elements in $\mat{I}'_{k,i}$ and two in $\rvec{i}'_{k,i}$) and it is required for the security of the scheme that $t$ be unique for each aggregation at each time, this is handled by setting $t$ to the concatenation
+which now capture all the private state information in $\vec{x}_{k|k-1}$ required at the sensors.
+The corresponding EIF update steps \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update} then become
+\begin{equation}
+    \vec{y}_{k|k} = \vec{y}_{k|k-1} + \sum^n_{i=1}\vec{i}'_{k,i} \label{eqn:eif_modified_vec_update}
+\end{equation}
+and
+\begin{equation}
+    \mat{Y}_{k|k} = \mat{Y}_{k|k-1} + \sum^n_{i=1}\mat{I}'_{k,i}\,, \label{eqn:eif_modified_mat_update}
+\end{equation}
+respectively. Additionally, we note the possible extension to the three-dimensional case.
+\begin{remark}
+    The above has been derived for two-dimensional localisation but can be similarly derived for three-dimensional case.
+However, we note that the number of weights increases combinatorially with the number of dimensions, thus affecting the cost of communication as well.
+\end{remark}
+
+The final step required for computing \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} at the sensors and \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update} at the navigator using the proposed LCAO scheme, is handling the unique instance variables $t$ in the context of estimation timesteps $k$.
+This is done by elementwise linear combination of \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} and setting $t$ to the concatenation
 \begin{equation}
@@
 \end{equation}
-for aggregation in row $v$ and column $w$, with $\tau=0$ for aggregations in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.
-\begin{remark}
-    The solutions \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} have been derived for two-dimensional localization, but can be similarly extended to the three-dimensional case.
-We note, however, the additional cost with increasing dimension.
-The number of weights is increased in the rearranged functions $h'_i$, and therefore combinatorially increased in $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ by .
-This results in a combinatorial increase in weights, and therefore communication, with respect to the number of state parameters required for computing functions $h_i$.
-\end{remark}
+for elements in row $v$ and column $w$, with $\tau=0$ for those in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.
 
@@
 \subsection{Pseudocode} \label{subsec:pseudocode}
+
+Due to the complexity
+several levels of computations
+we summarise the privacy-preserving localisation filter in this section
+
 In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.

### 2021-05-27 main.tex
Pseudocode section draft Moved leakage section back to being after the pseudocode section

@@
     \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,,
-\end{equation}
+\end{equation} \label{eqn:ekf_prediction}
 with Jacobian
@@
 and mean-adjust modified measurements as
-\begin{equation} \label{eqn:modified_measurement}
+\begin{equation}
     \begin{split}
@@
         &= h'_i(\vec{x}_k) + v'_{k,i}\,,
-    \end{split}
+    \end{split} \label{eqn:modified_measurement}
 \end{equation}
@@
 % 
-% ##       ########    ###    ##    ##    ###     ######   ######## 
-% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
-% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
-% ##       ######   ##     ## #####    ##     ## ##   #### ######   
-% ##       ##       ######### ##  ##   ######### ##    ##  ##       
-% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
-% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
-%
-
-\subsection{Leakage} \label{subsec:leakage}
-With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
-We recall the assumptions on participant capabilities made in Section .
-Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
-This may be achievable by detecting changes in measurements after reporting false ones.
-As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
-
-The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
-That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
-
-From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
-\begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
-\end{equation}
-From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
-\begin{theorem}
-    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
-\end{theorem}
-
-% 
 %    ###    ##        ######   
@@
 \subsection{Pseudocode} \label{subsec:pseudocode}
-
-Due to the complexity
-several levels of computations
-we summarise the privacy-preserving localisation filter in this section
-
-In this section, we piece together our LCAO secure encryption scheme in Section  with the modified measurement model in Sections  and  and define our privacy-preserving localization algorithm.
-
-The privacy-preserving localization filter can be described by the following steps.
+Measurement modification, real number encoding and linear combination aggregation are all required to compute the modified EIF from the previous section in a privacy-preserving manner.
+In this section, we summarise this entire localisation process and give the pseudocode for its execution.
+For brevity, we will assume $\phi$ and $M=N$ from section \ref{subsec:encoding} to be public information, and simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
+The privacy-preserving localization filter consists of the following steps.
 \begin{LaTeXdescription}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from Section  is executed by a trusted third party, $N$ and $H$ are made known to the navigator and all sensors, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$ respectively, are distributed accordingly.
-Additionally, we assume that fractional precision $\phi$ from Section \ref{subsec:encoding} is also a public parameter and made known to the navigator and sensors.
-We will thus simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
-
-    \item[Prediction] The navigator computes the typical EKF prediction equations before encrypting state variables and broadcasting to sensors. This is given by Algorithm \ref{alg:nav_prediction}.
-
-    \item[Measurement] Sensors modify their measurements before homomorphically computing measurement vectors and matrices $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$, encrypting them for aggregation, and sending them back to the navigator.
-Care must be taken when encoding during homomorphic operations to ensure fractional factor $d$ satisfies \eqref{eqn:encoding_homomorphic_add}, in particular when using the property from Remark \ref{rem:lcao_implicit_weight}.
-This is described by Algorithm \ref{alg:measurement_info}.
-
-    \item[Update] The navigator aggregates measurement vectors and matrices before decrypting them.
-The typical EIF update equations can then be computed.
-This is shown in Algorithm \ref{alg:nav_update}.
+    \item[Setup] Run only once, the $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
+
+    \item[Prediction] At each timestep $k$, the navigator computes the typical EKF prediction equations \eqref{eqn:ekf_prediction} before encrypting weights \eqref{eqn:weights_to_broadcast} with algorithm $\mathsf{Enc}$ and broadcasting them to the sensors.
+This is given by algorithm \ref{alg:nav_prediction}.
+
+    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ elementwise and sending them back to the navigator.
+This is given by algorithm \ref{alg:measurement_info}.
+
+    \item[Update] At each timestep $k$, the navigator aggregates and decrypts recieved measurement vectors and matrices with algorithm $\mathsf{AggDec}$, before computing the modified EIF update equations \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update}.
+This is given by algorithm \ref{alg:nav_update}.
 \end{LaTeXdescription}
@@
 \begin{algorithmic}[1]
-    \Procedure{Prediction}{$\rvec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
-
-    \State Compute $\mat{F}_k$ by 
-    \State $\rvec{x}_{k|k-1} \gets \vec{f}(\rvec{x}_{k-1|k-1})$
-    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}$
-
-    \State Compute $\mathsf{E}_{0}(\rv{x}^3_{k|k-1})$ by \eqref{eqn:encode}
-    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
-    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$ to sensors
+    \Procedure{Prediction}{$\vec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
+
+    \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
+    \State $\vec{x}_{k|k-1} \gets \vec{f}(\vec{x}_{k-1|k-1})$
+    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k$
+
+    \State Compute $\mathsf{E}_{0}(x^3_{k|k-1})$ by \eqref{eqn:encode}
+    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
+    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ to sensors
     \For{Remaining weights in \eqref{eqn:weights_to_broadcast}} 
@@
 
-    \State \Return $\rvec{x}_{k|k-1}, \mat{P}_{k|k-1}$
+    \State \Return $\vec{x}_{k|k-1}, \mat{P}_{k|k-1}$
     \EndProcedure
@@
 
-    \State Measure $\rv{z}_{k,i}$
-    \State Compute $\rv{z}_{k,i}'$ by \eqref{eqn:modified_measurement}
-    \State Compute $\rv{r}_{k, i}$ by \eqref{eqn:modified_measurement_variance_estimate}
-
-    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))$
+    \State Measure $z_{k,i}$
+    \State Compute $z'_{k,i}$ by \eqref{eqn:modified_measurement}
+    \State Compute $r_{k,i}$ by \eqref{eqn:modified_measurement_variance_estimate}
+
+    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$
     \For{Remaining weights in \eqref{eqn:weights_to_broadcast}}
@@
 
-    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\rvec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(2\rv{r}_{k, i}^{-1}\rv{z}_{k,i}')}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-2\rv{r}_{k, i}^{-1}s_{y,i}^2)}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}^3)}
-    (N+1)^{\mathsf{E}_{1}(2\rv{r}_{k, i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(-2\rv{r}_{k, i}^{-1}s_{x,i}\rv{z}_{k,i}')}
+    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
+    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}y^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(y^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1}z_{k,i}')}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{y,i}^2)}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}^3)}
+    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{-1}s_{x,i}z_{k,i}')}
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
@@
     \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4\rv{r}_{k, i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\rv{x}_{k|k-1}))^{\mathsf{E}_{0}(-8\rv{r}_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(4\rv{r}_{k, i}^{-1}s_{x,i}^2)}\cdot$\par
+    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{-1}s_{x,i})}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and Remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
     \For{$v \gets 1$ to $2$}
@@
 \begin{algorithmic}[1]
-    \Procedure{Update}{$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}
+    \Procedure{Update}{$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}
 
@@
 
-    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\rvec{i}'_{k,i}$
+    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\vec{i}'_{k,i}$
     \For{$v \gets 1$ to $2$}
@@
     \EndFor
-    \State Construct $\sum_{i=1}^n\rvec{i}'_{k,i}$ from decoded decryptions above
+    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ from decoded decryptions above
 
@@
 
-    \State $\rvec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\rvec{x}_{k|k-1} + \sum_{i=1}^n\rvec{i}'_{k,i}$
+    \State $\vec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} + \sum_{i=1}^n\vec{i}'_{k,i}$
     \State $\mat{Y}_{k|k} \gets \mat{P}_{k|k-1}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
-    \State $\rvec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\rvec{y}_{k|k}$
+    \State $\vec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\vec{y}_{k|k}$
     \State $\mat{P}_{k|k} \gets \mat{Y}_{k|k}^{-1}$
-    \State \Return $\rvec{x}_{k|k}, \mat{P}_{k|k}$
+    \State \Return $\vec{x}_{k|k}, \mat{P}_{k|k}$
     \EndProcedure
@@
 
-Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have been summarized graphically in Figure \ref{fig:alg_steps}, where encryptions and encodings of vectors and matrices have been denoted with $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ for brevity, and represent element-wise operations with the same parameters.
-
+Algorithms \ref{alg:nav_prediction}, \ref{alg:measurement_info} and \ref{alg:nav_update} have also been summarised graphically in figure \ref{fig:alg_steps}.
+Here, for brevity, $\mathcal{E}_{pk_0,sk_i}(\cdot)$ and $\mathsf{E}_d(\cdot)$ denote elementwise operations with the same parameters.
 \begin{figure}[htbp]
 \centering
-\vspace{\baselineskip}
 \begin{tikzpicture}[font=\footnotesize,scale=0.95]
@@
     \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
-    \node at (3.25,5.875) {$\rvec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};
+    \node at (3.25,5.875) {$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};
 
@@
     \fill [lightgray]  (0.25,5) rectangle (6.25,4);
-    \node at (3.25,4.5) {$\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\rangle$};
+    \node at (3.25,4.5) {$\left\{\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\right\}$};
 
@@
 
-    \node at (1.25,-3.125) {$\rv{z}'_{k,1}$, $\rv{r}_{k,1}$};
-    \node at (5.25,-3.125) {$\rv{z}'_{k,n}$, $\rv{r}_{k,n}$};
+    \node at (1.25,-3.125) {$z'_{k,1}$, $r_{k,1}$};
+    \node at (5.25,-3.125) {$z'_{k,n}$, $r_{k,n}$};
 
@@
     \fill [lightgray]  (0.375,-0.875) rectangle (3.125,-1.875);
-    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\rvec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
+    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
     \fill [lightgray]  (3.375,-0.875) rectangle (6.125,-1.875);
-    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\rvec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
+    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
 
@@
     \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
-    \node at (3.25,-6.625) {$\sum_{i=1}^n \rvec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (3.25,-7.125) {$\rvec{x}_{k|k}$, $\mat{P}_{k|k}$};
+    \node at (3.25,-6.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
+    \node at (3.25,-7.125) {$\vec{x}_{k|k}$, $\mat{P}_{k|k}$};
 \end{tikzpicture}
-\caption{The summary of steps involved in our proposed privacy-preserving EIF.}
-\vspace{-\baselineskip}
+\caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
 \label{fig:alg_steps}
 \end{figure}
+
+% 
+% ##       ########    ###    ##    ##    ###     ######   ######## 
+% ##       ##         ## ##   ##   ##    ## ##   ##    ##  ##       
+% ##       ##        ##   ##  ##  ##    ##   ##  ##        ##       
+% ##       ######   ##     ## #####    ##     ## ##   #### ######   
+% ##       ##       ######### ##  ##   ######### ##    ##  ##       
+% ##       ##       ##     ## ##   ##  ##     ## ##    ##  ##       
+% ######## ######## ##     ## ##    ## ##     ##  ######   ######## 
+%
+
+\subsection{Leakage} \label{subsec:leakage}
+With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
+We recall the assumptions on participant capabilities made in Section .
+Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
+Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
+This may be achievable by detecting changes in measurements after reporting false ones.
+As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
+
+The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
+That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
+
+From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
+\begin{equation}
+    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
+\end{equation}
+From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
+\begin{theorem}
+    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
+\end{theorem}
 

### 2021-05-27 main.tex
Draft of leakage section completed

@@
 Lastly, we conclude the cryptographic problem definition with the following important remark.
-\begin{remark} \label{rem:lcao_leakage}
+\begin{remark}
     A leakage function including weights from the navigator requires extra care to be taken when giving its definition.
@@
 Lastly, we make the following remark about a possible implicit weight.
-\begin{remark} \label{rem:lcao_implicit_weight}
+\begin{remark}
     The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
@@
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
     \For{$v \gets 1$ to $2$}
@@
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and remark \ref{rem:lcao_implicit_weight} in the form above
+    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
     \For{$v \gets 1$ to $2$}
@@
 \subsection{Leakage} \label{subsec:leakage}
-With the algorithm defined, we can analyze the localization leakage when the strictly defined LCAO leakage is taken into account.
-We recall the assumptions on participant capabilities made in Section .
-Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage.
-Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements when navigator behavior is dependent on its estimate.
-This may be achievable by detecting changes in measurements after reporting false ones.
-As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
-
-The aggregation operation of our encryption scheme leaks the sums of sensor measurement vectors and matrices $\sum_{i=1}^n\rvec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, however, as stated in Remark \ref{rem:lcao_leakage}, weights chosen by a corrupted navigator mean that individual sums of coefficients can be leaked as well.
-That is, sums of coefficients in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} (\textit{i.e.}, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}$, $\sum_{i=1}^n-\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n-2\rv{r}^{-1}_{k,i}s_{x,i}$, $\sum_{i=1}^n2\rv{r}^{-1}_{k,i}\rv{z}'_{k,i}$, \dots) are leaked to a corrupted navigator.
-
-From the leaked sums of coefficients, we see that all information private to the sensors and broadcast to the navigator, namely their modified measurements $\rv{z}'_{k,i}$, variance estimates $\rv{r}_{k,i}$ and locations $\vec{s}_i$, are present only in the sums
-\begin{equation}
-    \sum_{i=1}^n\rv{z}'_{k,i}\,,\ \sum_{i=1}^n\rv{r}_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,.\label{eqn:localization_leakage}
-\end{equation}
-From these sums and the definitions \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate}, we conclude that the navigator can \textit{at most} learn the sums of sensor private data, which in practice corresponds to the average sensor modified measurements, estimated variances and locations.
-\begin{theorem}
-    In the context of our localization scheme, leakage of the incorporated LCAO secure encryption scheme corresponds to the leakage of average sensor private information, given by the sums in \eqref{eqn:localization_leakage}.
-\end{theorem}
+With the privacy-preserving EIF defined in the previous section, we can now interpret the aggregation leakage of an LCAO scheme in the context of range sensor localisation.
+The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively.
+However, recalling the remark in section \ref{subsec:crypto_problem}, a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$.
+From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
+\begin{equation}
+    \sum_{i=1}^nz'_{k,i}\,,\ \sum_{i=1}^nr_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,,\label{eqn:localisation_leakage}
+\end{equation}
+which in practice may correspond to their averages.
+We can therefore say, in the context of our proposed localisation method, LCAO leakage corresponds to the averages of sensor private information, while individual sensor information remains private.
+This is in line with intuition given an aggregation leakage function.
 

### 2021-05-28 main.tex
Removed -\baselineskip spaces for until space becomes an issue again
Proofread all done draft sections so far and made small changed accordingly

@@
 \section{Problem Statement} \label{sec:problem_statement}
-In this work, we consider the context of privacy-preserving range-sensor navigation, in which we wish for no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
+In this work, we consider the context of privacy-preserving range-sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
 The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-sensor navigation.
@@
 In section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals.
-
-At every \textit{instance} $t$ (used to distinguish from an estimation timestep $k$), the navigator first broadcasts a number of weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who compute individual linear-combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
+The communication protocol is as follows.
+
+At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear-combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
 Linear-combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
@@
 \end{figure}
-In addition, we remark that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$.
+In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.
@@
 This means the navigator may not send different weights to individual sensors during a single instance $t$.
-    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localization procedure correctly but may store or use any gained sensitive information.
+    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localisation procedure correctly but may store or use any gained sensitive information.
 \end{LaTeXdescription}
 We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a complete group and treated as the global set for estimation purposes, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts.
-The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work for the sake of simplicity.
+The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.
 
@@
 These will be used by a trusted setup party, the navigator and sensors $i,\,1\leq i \leq n$.
-They are defined as follows
+They are defined as follows.
 \begin{LaTeXdescription}
@@
 \begin{LaTeXdescription}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any additional knowledge about the navigator weights $\omega_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and the ability to encrypt plaintexts of their choice.
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
     \item[Linear-Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
@@
     A leakage function including weights from the navigator requires extra care to be taken when giving its definition.
-If an attacker compromises the navigator (which need not follow the estimation protocol), they have control over the weights, and therefore the leakage function.
+If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function.
 We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
@@
 \subsection{Estimation problem} \label{subsec:est_problem}
-The estimation problem we consider, for which we will reduce communication to the protocol required for the introduced cryptographic problem, is localisation with range-only sensors.
+The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors.
 In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent.
@@
 \end{equation}
-with Gaussian measurement noise $v_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$, as
+with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$, as
 \begin{equation}
@@
     \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
-Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine $m>1$ and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
+Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
 Sensor secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
@@
 \section{Privacy-Preserving Localization} \label{sec:priv_localization}
-To produce an estimate of the state $\vec{x}_k$ such that communication between $n$ range sensors and the navigator is reducible to the linear-combination aggregation protocol, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation.
+With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that reduces to the required protocol.
+To produce an estimate of the state $\vec{x}_k$, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation.
 The EIF update step requires the predicted state estimate $\vec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
@@
 \begin{equation}
-    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,,
-\end{equation} \label{eqn:ekf_prediction}
+    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,, \label{eqn:ekf_prediction}
+\end{equation}
 with Jacobian
@@
 $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, also require the current predicted state estimate $\vec{x}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
-For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (weights), and subsequently aggregated at the navigator.
+For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator.
 Application of the linear-combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and that the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
@@
 
-The first thing we note when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\vec{x}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
+The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\vec{x}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
 Similarly, the Jacobian of $h_i$ at $\vec{x}_{k|k-1}$,
@@
 Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $x_{k|k-1}^2$, $y_{k|k-1}^2$, $x_{k|k-1}$ and $y_{k|k-1}$.
-To show how $\rvec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ can be similarly rearranged, we also require the existence of measurements following a modified measurement model of the form
+To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
 \begin{equation}
@@
 
-The approximation of $z'_{k,i}$ and its variance $\mathsf{Var}[v'_{k,i}]$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$ in \eqref{eqn:measurement_model}.
-Squaring the original range measurements produces
+Computing $z'_{k,i}$ and its variance $r_{k,i}$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$, and simply squaring the original range measurements produces
 \begin{equation}
@@
 \end{equation}
-with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean or Gaussian.
+with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean.
 We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
@@
 \end{equation}
-and is also dependent on $h_i(\vec{x}_k)$.
+and is also dependent on $h_i$.
 To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well.
@@
 Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$.
-The modified measurement's variance at time $k$ is therefore conservatively approximated by
+The modified measurement's variance at timestep $k$ is therefore conservatively approximated by
 \begin{equation}
@@
 \end{equation}
-for each sensor $i$.
-
-The existence of modified measurements $z'_{k,i}$ and their estimated variances $r_{k, i}$ are sufficient for sensors to compute measurement vector $\vec{i}_{k,i}$ and matrix $\mat{I}_{k,i}$ in the required form for linear-combination aggregation.
+at each sensor $i$.
+
+The modified measurement model \eqref{eqn:modified_measurement_model} can now be used for localisation, when measurements are modified by \eqref{eqn:modified_measurement} and their new variance estimated with \eqref{eqn:modified_measurement_variance_estimate}.
 
@@
 \subsection{Localization} \label{subsec:localization}
-Now that range measurements can be modified by \eqref{eqn:modified_measurement}, and the modified model \eqref{eqn:modified_measurement_model} can be used, corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be computed as linear combinations of powers of location elements.
-This is given by
+To complete the EIF update using a linear combination aggregation process, modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$, using the modified measurement model \eqref{eqn:modified_measurement_model}, can be rearragned as follows.
 \begin{equation}
@@
     The above has been derived for two-dimensional localisation but can be similarly derived for three-dimensional case.
-However, we note that the number of weights increases combinatorially with the number of dimensions, thus affecting the cost of communication as well.
+However, the number of weights increases combinatorially with the number of dimensions, thus affecting the cost of communication as well.
 \end{remark}
 
-The final step required for computing \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} at the sensors and \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update} at the navigator using the proposed LCAO scheme, is handling the unique instance variables $t$ in the context of estimation timesteps $k$.
-This is done by elementwise linear combination of \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} and setting $t$ to the concatenation
-\begin{equation}
-    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau
-\end{equation}
-for elements in row $v$ and column $w$, with $\tau=0$ for those in $\rvec{i}'_{k,i}$ and $\tau=1$ otherwise.
+The final step required for computing \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} at the sensors and \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update} at the navigator, using the proposed LCAO scheme, is handling the unique instance variables $t$ in the context of estimation timesteps $k$.
+We do this by performing the linear combination aggregation process of \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} for each element independently and setting $t$ to the concatenation
+\begin{equation}
+    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau\,,
+\end{equation}
+for elements in row $v$ and column $w$, and with $\tau=0$ for elements in $\vec{i}'_{k,i}$ and $\tau=1$ otherwise.
+This results in elementwise encryptions, and six aggregations at each timestep $k$ (in the two-dimensional case).
 
@@
 In this section, we summarise this entire localisation process and give the pseudocode for its execution.
-For brevity, we will assume $\phi$ and $M=N$ from section \ref{subsec:encoding} to be public information, and simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
+For brevity, we will assume $\phi$ and $M=N$ from section \ref{subsec:encoding} to be public information and thus simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
 The privacy-preserving localization filter consists of the following steps.
@@
 
-    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ elementwise and sending them back to the navigator.
+    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ for each element and sending them back to the navigator.
 This is given by algorithm \ref{alg:measurement_info}.
@@
 With the privacy-preserving EIF defined in the previous section, we can now interpret the aggregation leakage of an LCAO scheme in the context of range sensor localisation.
-The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively.
-However, recalling the remark in section \ref{subsec:crypto_problem}, a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$.
+The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums, $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively.
+However, recalling that a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$.
 From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
@@
 \end{equation}
-which in practice may correspond to their averages.
+which in practice correspond to their averages.
 We can therefore say, in the context of our proposed localisation method, LCAO leakage corresponds to the averages of sensor private information, while individual sensor information remains private.
-This is in line with intuition given an aggregation leakage function.
 
@@
 \includegraphics{images/layouts.pdf}
-\vspace{-\baselineskip}
 \caption{The considered layouts, with varying average distances between navigator and sensors.}
@@
 \includegraphics{images/layout_errors.pdf}
-\vspace{-\baselineskip}
 \caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
@@
 \includegraphics{images/timing.pdf}
-\vspace{-\baselineskip}
 \caption{Runtimes for varying key sizes and numbers of sensors.}
-\vspace{-\baselineskip}
 \label{fig:sim_timing}
@@
 %
-\vspace{-\baselineskip}
+
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}

### 2021-05-31 main.tex
Updated notation section for the updated paper Fixed typo in equation

@@
 \subsection{Notation}
-Throughout this work, we will use the following notation.
-Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$.
-Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose.
-$|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector norm.
-Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$.
-$\mathsf{E}[\cdot]$ and $\mathsf{Var}[\cdot]$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$.
-Additionally, key $k$ may be ommited when inferrable from context.
-$\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.
+Throughout this work, we make use of the following notation.
+Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices.
+$\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose.
+The expected value of a random variable is denoted $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively.
+$|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences.
+When estimating a state, notation $\vec{x}_{k|l}$ will denote an estimate at timestep $k$ given measurements from timesteps up to and including $l$.
+When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context.
+$\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator, and the term negligible function refers to the cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
 
@@
         r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
-        &\gtrapprox \Var{v'_{k,i}}
+        &\gtrapprox \mathsf{Var}[v'_{k,i}]
     \end{split}\,. \label{eqn:modified_measurement_variance_estimate}

### 2021-05-31 main.tex
Started on introduction overhaul Added section summary Updated author associations

@@
 
-% Apparently requested for submission
+% Requested for submission
 \pdfminorversion=4
@@
 % author names and IEEE memberships
-\author{Marko~Ristic,
-        Benjamin~Noack,~\IEEEmembership{Member,~IEEE,}
-        and~Uwe~D.~Hanebeck,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
-\thanks{M.
-Ristic, B.
-Noack and U.
-D.
-Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory, Institute for Anthropomatics, Karlsruhe Institute of Technology, 76131 Karlsruhe, Germany.
-e-mail: marko.ristic@kit.edu}}% <-this % stops a space
+\author{Marko~Ristic$^{1}$,
+        Benjamin~Noack$^{2}$,~\IEEEmembership{Member,~IEEE,}
+        and~Uwe~D.~Hanebeck$^{1}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
+\thanks{$^{1}$Marko Ristic and Uwe D.
+Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: \{marko.ristic, uwe.hanebeck\}@kit.edu).}% <-this % stops a space
+\thanks{$^{2}$Benjamin Noack is with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: benjamin.noack@ovgu.de).}}% <-this % stops a space
 % \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
@@
 \section{Introduction} \label{sec:introduction}
+
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
+
+Range-based localisation methods, with measurements such as signal strength \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range \cite{beutlerNewNonlinearFiltering2004} or radar, have found particularly large application due to the prevalence of suitable sensors.
+
+most rely on centralised
+
+with the rise of distributed cloud
+
+%starts to broad, skip to range-based?
+%As advancements in portable computing and sensor capabilities have developed, a wide variety of localisation methods have been proposed, including those using signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range measurements \cite{beutlerNewNonlinearFiltering2004}, magnetic field measurements \cite{sieblerLocalizationMagneticField2020} and time-difference-of-arrival multilateration methods \cite{liContributedReviewSourcelocalization2016} to localisation agents.
+
+%Due to the prevalence of suitable sensors such as radar or signal strength measurement, range-based localisation methods have found particularly large application.
+
+Localisation methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
 Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004}, and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
 Range-based localization methods, including the use of radar measurements, GPS clocks, and signal strength measurements, have found particularly large applications due to their robustness and accuracy.
+
 These methods use distance measurements to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location, and observations centrally.
@@
 With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
+
 For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
@@
 Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
+
 All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
@@
 
-The remainder of the paper is structured as follows.
-In Section  we give an overview of the relevant literature to the topic and in Section  we introduce the localization problem, the relevant aggregation operation for its solution and the restrictions on involved parties.
-Sections  and  will summarize cryptographic preliminaries and introduce a novel security notion for our required aggregation before defining and proving an encryption scheme which satisfies it.
-Sections  and  introduce localization preliminaries and our privacy-preserving localization method using the private aggregation scheme.
-We show and discuss simulation results in Section  and conclude our work in Section .
-
 % LITERATURE OVERVIEW
 
-\label{sec:lit_overview}
 In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.
@@
 
+In section \ref{sec:problem_statement} we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
+Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} the solution to the estimation problem making use of this scheme.
+Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.
+
 % 
@@
 When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context.
-$\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
-$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator, and the term negligible function refers to the cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
+$\mathbb{Z}_n$ is used for the set of integers m  odulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to the cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
 

### 2021-06-01 main.tex
Big progress on the introduction

@@
-%% bare_jrnl.tex
-%% V1.4b
-%% 2015/08/26
-%% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
-%% journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/pkg/ieeetran
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall the IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%*************************************************************************
-
 \documentclass[10pt,letterpaper,oneside,twocolumn,journal]{IEEEtran}
@@
 
+% Start
 \begin{document}
-%
+
 % paper title
 \title{Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
-%
-%
+
 % author names and IEEE memberships
@@
 \thanks{$^{2}$Benjamin Noack is with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: benjamin.noack@ovgu.de).}}% <-this % stops a space
-% \thanks{Manuscript received April 19, 2005; revised August 26, 2015.}}
-
-% The paper headers
-% \markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-% {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}
-
-% If you want to put a publisher's ID mark on the page you can do it like this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
 
@@
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
 \begin{abstract}
@@
 \section{Introduction} \label{sec:introduction}
-
-\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
-
-Range-based localisation methods, with measurements such as signal strength \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range \cite{beutlerNewNonlinearFiltering2004} or radar, have found particularly large application due to the prevalence of suitable sensors.
-
-most rely on centralised
-
-with the rise of distributed cloud
-
-%starts to broad, skip to range-based?
-%As advancements in portable computing and sensor capabilities have developed, a wide variety of localisation methods have been proposed, including those using signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range measurements \cite{beutlerNewNonlinearFiltering2004}, magnetic field measurements \cite{sieblerLocalizationMagneticField2020} and time-difference-of-arrival multilateration methods \cite{liContributedReviewSourcelocalization2016} to localisation agents.
-
-%Due to the prevalence of suitable sensors such as radar or signal strength measurement, range-based localisation methods have found particularly large application.
-
-Localisation methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,liContributedReviewSourcelocalization2016}.
-Ongoing advancements in portable computing power and sensor capabilities have led to the development of various forms of localization methods, from range-free and range-based signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic range estimates \cite{beutlerNewNonlinearFiltering2004}, and magnetic field measurements \cite{sieblerLocalizationMagneticField2020} to the TDOA and TOA pseudo-range multilateration methods for aircraft \cite{liContributedReviewSourcelocalization2016}.
-Range-based localization methods, including the use of radar measurements, GPS clocks, and signal strength measurements, have found particularly large applications due to their robustness and accuracy.
-
-These methods use distance measurements to produce location estimates and typically involve gathering sensor details such as measurement noise, geographical location, and observations centrally.
-Broadcasting or gathering information in this way, however, implies a trust between participants within a trusted communication network to ensure shared data may not be used for individual malicious gain.
-With the advancements in cloud and ubiquitous computing, changes in possible use-cases involving distributed sensors have made the requirements of information security and user privacy more apparent than before \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
-
-For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
+\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,ligginsDistributedDataFusion2012,liContributedReviewSourcelocalization2016} and have characterised many advancements of Kalman and Bayesian estimation theory \cite{mutambaraDecentralizedEstimationControl1998}.
+In particular, range-based localisation methods, including signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic ranges \cite{beutlerNewNonlinearFiltering2004} and ultra wideband ranges \cite{geziciLocalizationUltraWidebandRadios2005}, have found large application due to the prevalence of suitable sensors.
+In most cases, these localisation methods require the gathering of measurements centrally, where an estimate of location can be computed.
+With recent developments in distributed and cloud computing, uses of wireless and public communication channels for data transfer have becoming widespread, and the additional requirements of data privacy and state secrecy have become particularly relevant \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
+
+Typical cryptographic secrecy involves hiding all transferred data such that untrusted participants in the communication network learn no new information from acquired encryptions.
+This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively.
+In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in such signal processing or localisation tasks.
+In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations.
+In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, respectively, are introduced as means for computing local control inputs in a distributed environment without learning individual inputs.
+
+Our contribution in this work considers range-based localisation with formal cryptographic requirements.
+We present a novel scheme satisfying the requirements before deriving an estimation filter which uses the scheme to allow localisation without learning sensor measurements, measurement errors or locations, while sensors learn nothing other than their own measurements.
+
+based on the extended kalman filter, with no system model or sensor layout assumptions.
+
+Our contribution considers the context of range-based localisation, and consists of a formal cryptographic definition for a novel linear cmobination aggregation scheme
+
+Our contribution is in two parts
+
+Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
+
+Lastly, we motivate the scenario with some examples
+
+% old one
+
+% For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
 Or in autonomous vehicle state estimation, benefit from neighboring vehicles' information may be desired while no participant wishes to share information about their hardware.
@@
 
-All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
+% All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
 Our contributions in this work will be presented in two parts.
@@
 
-% LITERATURE OVERVIEW
-
-In this section, we will discuss methods for providing security guarantees in signal processing tasks, and their applications to localization and estimation problems.
-
-% ENCRYPTION SCHEMES IN SIGNAL PROCESSING
-
-Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
+% % ENCRYPTION SCHEMES IN SIGNAL PROCESSING
+
+% Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
 The most common methods for ensuring privacy during aggregation required for signal processing tasks have been described below.
-\begin{LaTeXdescription}
-    \item[Differential Privacy] These techniques formalize preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
+% \begin{LaTeXdescription}
+%     \item[Differential Privacy] These techniques formalize preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
 To handle the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs \cite{hanPrivacyControlDynamical2018,dworkDifferentialPrivacySurvey2008,andresGeoindistinguishabilityDifferentialPrivacy2013}.
@@
 Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localization.
-    \item[Aggregator Oblivious Encryption] This method of encryption formalizes the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
+%     \item[Aggregator Oblivious Encryption] This method of encryption formalizes the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
 Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their aggregation (typically sum) can be learned by an aggregator, whether or not they are trusted.
@@
 The aggregation operation in these schemes is, however, limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sums or mean calculations \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
-\end{LaTeXdescription}
-In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
+% \end{LaTeXdescription}
+% In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
 These methods have been broadly grouped into two domains and described below.
-\begin{LaTeXdescription}
-    \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
+% \begin{LaTeXdescription}
+%     \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
 Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
-    \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of (typically one) algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
+%     \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of (typically one) algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
 Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}.
 However, as with Aggregator Oblivious Encryption, these works are relatively restricted in application due to the limited operations provided.
-\end{LaTeXdescription}
-Lastly, recent developments in encryption schemes have presented some novel methods also suitable for privacy-preserving computation in distributed environments.
-\begin{LaTeXdescription}
-    \item[Multi-Client Functional Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
+% \end{LaTeXdescription}
+% Lastly, recent developments in encryption schemes have presented some novel methods also suitable for privacy-preserving computation in distributed environments.
+% \begin{LaTeXdescription}
+%     \item[Multi-Client Functional Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
 They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier.
 While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
-\end{LaTeXdescription}
-In the context of privacy-preserving localization and state estimation, some of the aforementioned schemes have found applications and some specialized encryption methods have been proposed.
+% \end{LaTeXdescription}
+% In the context of privacy-preserving localization and state estimation, some of the aforementioned schemes have found applications and some specialized encryption methods have been proposed.
 These are summarized in the next section.
 
-% APPLICATIONS TO LOCALIZATION AND ESTIMATION
-
-Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
+% % APPLICATIONS TO LOCALIZATION AND ESTIMATION
+
+% Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
 We aim to provide an accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.
 
-Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
+% Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
 The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute time-independent location estimates while preserving the privacy of sensor measurements and locations.
@@
 
-Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
+% Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
 In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralized or hidden weights (pWSAc and pWSAh, respectively) are proposed.
@@
 
-% Used to be in problem formulation but better point out the differences in our contribution to pWSAc here and not mention it again
-Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
-
-% Was in problem formulation but all motivations should be in the introduction instead
-We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
+% % Used to be in problem formulation but better point out the differences in our contribution to pWSAc here and not mention it again
+% Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
+
+% % Was in problem formulation but all motivations should be in the introduction instead
+% We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
 It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
@@
 
-Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
+% Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
 As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
@@
 
-While some aspects of privacy-preserving localization are solved in the above methods and encryption schemes, they fail to provide a localization solution in our context.
+% While some aspects of privacy-preserving localization are solved in the above methods and encryption schemes, they fail to provide a localization solution in our context.
 In the next section, we will formalize our problem and its accompanying security requirements.

### 2021-06-02 main.tex
Introduction draft done

@@
 
-Typical cryptographic secrecy involves hiding all transferred data such that untrusted participants in the communication network learn no new information from acquired encryptions.
+Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions.
 This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively.
@@
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
-In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, respectively, are introduced as means for computing local control inputs in a distributed environment without learning individual inputs.
-
-Our contribution in this work considers range-based localisation with formal cryptographic requirements.
-We present a novel scheme satisfying the requirements before deriving an estimation filter which uses the scheme to allow localisation without learning sensor measurements, measurement errors or locations, while sensors learn nothing other than their own measurements.
-
-based on the extended kalman filter, with no system model or sensor layout assumptions.
-
-Our contribution considers the context of range-based localisation, and consists of a formal cryptographic definition for a novel linear cmobination aggregation scheme
-
-Our contribution is in two parts
-
-Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
-
-Lastly, we motivate the scenario with some examples
-
-% old one
-
-% For example, an aircraft localization scenario in the presence of privately operated measurement stations may imply measurements and locations of stations should be kept private from navigating vehicles.
-Or in autonomous vehicle state estimation, benefit from neighboring vehicles' information may be desired while no participant wishes to share information about their hardware.
-Additionally, the dispatching of any expensive intermediate computations to service-providing cloud operators may require ensuring the privacy of information involved in the computations.
-
-% All of these scenarios, and the one we will consider, require methods for computing specific operations while ensuring the privacy of some or all of the input data.
-Our contributions in this work will be presented in two parts.
-We first propose a novel aggregation-based encryption scheme which allows the private aggregation of weighted sums, before developing a computationally plausible localization filter in the presence of range-only sensors using this scheme, such that sensor and navigator privacy is preserved.
-
-% % ENCRYPTION SCHEMES IN SIGNAL PROCESSING
-
-% Of the methods used to preserve privacy during distributed signal processing, it is common for the information exchanging portion of the algorithm to be reduced to a form of aggregation of involved parties' data.
-The most common methods for ensuring privacy during aggregation required for signal processing tasks have been described below.
-% \begin{LaTeXdescription}
-%     \item[Differential Privacy] These techniques formalize preserving the privacy of individual datum within an aggregation operation by introducing known distributions of noise to the resulting aggregation.
-To handle the cases with no trusted aggregator, local differential privacy is achieved by introducing noise to individual inputs \cite{hanPrivacyControlDynamical2018,dworkDifferentialPrivacySurvey2008,andresGeoindistinguishabilityDifferentialPrivacy2013}.
-Although differential privacy has strong computational benefits due to its implementational simplicity, it provides relatively weak security guarantees for multi-party networks, with no guarantees in the presence of multiple colluding corrupted parties.
-Additionally, noisy aggregation results hinder its use in scenarios where high precision is a desired property such as aircraft localization.
-%     \item[Aggregator Oblivious Encryption] This method of encryption formalizes the privacy of \textit{all} aggregation data from honest parties \cite{shiPrivacyPreservingAggregationTimeSeries2011,chanPrivacyPreservingStreamAggregation2012,joyeScalableSchemePrivacyPreserving2013}.
-Encryptions of aggregation data are proven to be computationally indistinguishable and guarantee that only their aggregation (typically sum) can be learned by an aggregator, whether or not they are trusted.
-The originally proposed method \cite{shiPrivacyPreservingAggregationTimeSeries2011} is restricted to a small input domain which has been expanded and computationally simplified in later works \cite{joyeScalableSchemePrivacyPreserving2013,benhamoudaNewFrameworkPrivacyPreserving2016}.
-The aggregation operation in these schemes is, however, limited to the sum operation and restricts its applicability to simple processing tasks such as smart-meter sums or mean calculations \cite{chanPrivacyPreservingStreamAggregation2012,benhamoudaNewFrameworkPrivacyPreserving2016}.
-% \end{LaTeXdescription}
-% In addition to the private aggregation of data, it may also be the case that private data needs to be modified by an external party before being returned, as with privacy-preserving cloud computing.
-These methods have been broadly grouped into two domains and described below.
-% \begin{LaTeXdescription}
-%     \item[Fully Homomorphic Encryption] These schemes allow all algebraic computations to be performed on encrypted data without the computing party learning any information about inputs, intermediate values or results \cite{gentryFullyHomomorphicEncryption2009,stehleFasterFullyHomomorphic2010}.
-Although theoretically ideal for many data-sensitive tasks, current implementations are still computationally impractical for real-time or large scale tasks \cite{acarSurveyHomomorphicEncryption2018}.
-%     \item[Partially Homomorphic Encryption] A simplification of fully homomorphic schemes; these schemes provide only a subset of (typically one) algebraic operations on encrypted data \cite{elgamalPublicKeyCryptosystem1985,paillierPublicKeyCryptosystemsBased1999,bonehEvaluating2DNFFormulas2005}.
-Reduced computational requirements and implementation simplicity have made partially homomorphic encryption schemes commonly used in privacy-preserving signal processing tasks, including private matrix multiplication \cite{kogisoCyberSecurityEnhancementNetworked2015}, set intersection computation \cite{kerschbaumOutsourcedPrivateSet2012} and control input aggregation \cite{alexandruEncryptedCooperativeControl2019}.
-However, as with Aggregator Oblivious Encryption, these works are relatively restricted in application due to the limited operations provided.
-% \end{LaTeXdescription}
-% Lastly, recent developments in encryption schemes have presented some novel methods also suitable for privacy-preserving computation in distributed environments.
-% \begin{LaTeXdescription}
-%     \item[Multi-Client Functional Encryption] These schemes allow the computing of a specific function given encrypted inputs \cite{bonehFunctionalEncryptionDefinitions2011,goldwasserMultiinputFunctionalEncryption2014}.
-They are suitable for data-sensitive distributed processing as encryptions must be combined before a result is obtained, and can be considered a generalization of the aggregation schemes described earlier.
-While general schemes that allow computing arbitrary functions are computationally expensive and complicate security definitions in distributed settings \cite{agrawalFunctionalEncryptionNew2013}, partial schemes supporting only some functions, such as vector dot products \cite{chotardDecentralizedMultiClientFunctional2018}, exist with formal security proofs, but have yet to find applications in more complicated signal processing tasks.
-% \end{LaTeXdescription}
-% In the context of privacy-preserving localization and state estimation, some of the aforementioned schemes have found applications and some specialized encryption methods have been proposed.
-These are summarized in the next section.
-
-% % APPLICATIONS TO LOCALIZATION AND ESTIMATION
-
-% Localization methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors.
-We aim to provide an accurate localization filter in the presence of range-only sensors while providing uncertainties associated with estimates.
-
-% Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}.
-The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute time-independent location estimates while preserving the privacy of sensor measurements and locations.
-The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols.
-Neither method considers measurement uncertainty, and no estimate errors are provided, making them unsuitable for our desired solution.
-Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge.
-In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator.
-While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.
-
-% Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation.
-In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralized or hidden weights (pWSAc and pWSAh, respectively) are proposed.
-The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work.
-The requirements of our aggregation operation differ, however, in that weights are generalized to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time.
-We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.
-We define our alternative security notion in Section .
-
-% % Used to be in problem formulation but better point out the differences in our contribution to pWSAc here and not mention it again
-% Although similar to the pWSAc communication protocol in \cite{alexandruPrivateWeightedSum2020}, we formalise the assumptions
-
-% % Was in problem formulation but all motivations should be in the introduction instead
-% We motivate these goals with the example of aircraft navigation in the presence of privately-operated range-measuring stations.
-It is reasonable to assume that the current state of an aircraft may not wish to be disclosed to unknown parties and, similarly, that tower locations may wish to be kept private from unidentified navigating aircraft.
-The additional safety to passengers provided by accurate aircraft localization, however, may be a goal of all those involved, justifying their cooperation.
-
-% Along with encryption schemes and their application to localization-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers.
-As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations.
-Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme.
-It, however, leaks the exponent information of encrypted numbers.
-In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings.
-We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section .
-
-% While some aspects of privacy-preserving localization are solved in the above methods and encryption schemes, they fail to provide a localization solution in our context.
-In the next section, we will formalize our problem and its accompanying security requirements.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, respectively, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
+
+Our contribution in this work considers range-only localisation with formal cryptographic requirements ensuring that sensors keep their measurements and locations private and that navigator estimates cannot be learned by sensors.
+We define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
+The linear combination aggregation scheme put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing communication assumptions and leakages is given, crucial for cryptographic security.
+
+We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations.
+While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown at other present stations and to the navigator.
+Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.
 

### 2021-06-02 main.tex
Abstract draft done (to suit updated paper Title updated as well

@@
 % paper title
-\title{Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
+\title{Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies}
 
@@
 \begin{abstract}
-Distributed state estimation and localization methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
-Traditional distributed sensor navigation methods involve the leakage of sensor or navigator information during localization protocols, thus not preserving participants’ data privacy.
-Existing approaches that do provide such guarantees fail to address sensor and navigator privacy in common non-linear measurement model applications and therefore forfeit broad applicability.
-We define a suitable notion of linear-combination aggregation encryption and provide a cryptographically secure instance that is applied to the Extended Kalman Filter with range-sensor measurements.
-Our method keeps navigator location, sensors' locations, and sensors' measurements private during navigation, and has been implemented to evaluate its accuracy and performance.
-The novel computationally plausible and provably secure range-based localization filter has direct applications to environments where participants are not trusted or data is considered sensitive.
+Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
+Traditional distributed sensor navigation methods typically involve the leakage of sensor or navigator information by communicating measurements or estimates and thus do not preserve participants’ privacy.
+The existing approaches that do provide such guarantees, fail to address sensor and navigator privacy in the common application of model-based range-only estimation, consequently forfeiting broad applicability.
+In this work, we define a notion of privacy-preserving linear combination aggregation and use it to derive a modified Extended Kalman Filter using range measurements such that navigator location, sensors' locations, and sensors' measurements are kept private during navigation.
+Additionally, a formal cryptographic backing is presented to guarantee our method's privacy as well as an implementation to evaluate its performance.
+The novel, provably secure, range-based localisation method has applications in a variety of environments where sensors may not be trusted or estimates are considered sensitive, such as autonomous vehicle localisation or air traffic navigation.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filters.
+State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filter.
 \end{IEEEkeywords}
@@
 
-In section \ref{sec:problem_statement} we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
+In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
 Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} the solution to the estimation problem making use of this scheme.

### 2021-06-02 main.tex
Started fixing up simulation section text

@@
 \section{Simulation and Results} \label{sec:sim_and_results}
-To demonstrate our proposed approach, we have implemented the algorithm in Section  and simulated the measurement and navigation of an object following a linear, time-invariant, process model in two-dimensional space.
-
-Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support simultaneous computations by sensors and navigator as different processes.
-The OpenSSL library's, \cite{theopensslprojectOpenSSL2020}, mask generation function MGF1 and hash function SHA256 were used to implement the required hash function $H$, while the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the implementation of the Paillier encryption scheme.
-Additionally, GNU libraries GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020} were used for algebraic operations and the handling of multiple-precision integers, respectively.
-Simulation execution was performed on a 3.00GHz Intel i7-9700 CPU, and run on the Windows Subsystem for Linux (WSL), where no real-time kernel was ensured but sufficiently consistent runtimes were observed for the purposes of our simulation.
-
-Recalling the dependence of the modified measurement noise on the true measurement in \eqref{eqn:modified_measurement}, the noise distribution of the model changes with varying sizes of measurements.
-We considered four layouts with varying sensor distances when running our simulations to observe differences in estimation error when measurements are of different sizes.
-The considered layouts have been plotted and named in Figure~\ref{fig:sim_layouts}.
+As well as having shown the theoretical backing for the security of our scheme, we have simulated the proposed localisation method to evaluate its performance.
+A two-dimensional linear constant velocity process model, with
+\begin{equation*}
+    \vec{f}_k(\vec{x}) =
+    \begin{bmatrix}
+        1 & 0.5 & 0 & 0\\
+        0 & 1 & 0 & 0\\
+        0 & 0 & 1 & 0.5\\
+        0 & 0 & 0 & 1
+    \end{bmatrix} \cdot \vec{x}
+\end{equation*}
+and
+\begin{equation*}
+    \mat{Q}_k = \frac{1}{10^3} \cdot
+    \begin{bmatrix}
+        0.4 & 1.3 & 0 & 0\\
+        1.3 & 5.0 & 0 & 0\\
+        0 & 0 & 0.4 & 1.3\\
+        0 & 0 & 1.3 & 5.0
+    \end{bmatrix}\,,
+\end{equation*}
+for all $k>0$, was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}.
+Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator.
+The MG1 mask generation function and the SHA256 hash function, from the OpenSSL library \cite{theopensslprojectOpenSSL2020}, were used to implement the required hash function $H$, and the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the Paillier encryption scheme.
+Additionally, GNU libraries, GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020}, were used for algebraic operations and multiple-precision encoded integers, respectively.
+All execution was performed on a 3.00GHz Intel i7-9700 CPU, running on the Windows Subsystem for Linux (WSL).
+
+We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r_{k,i}$ on the original measurements $z_{k,i}$.
+The layouts, of varying sensor distances to the navigator track, are shown in figure \ref{fig:sim_layouts}.
 \begin{figure}[htbp]
@@
 \end{figure}
+
+standard EIF, equivalent to the EKF, as the baseline we comapre to
+
 To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units.

### 2021-06-03 main.tex
Simulation section draft done

@@
 As well as having shown the theoretical backing for the security of our scheme, we have simulated the proposed localisation method to evaluate its performance.
-A two-dimensional linear constant velocity process model, with
+A two-dimensional, linear, constant velocity process model, with
 \begin{equation*}
@@
     \includegraphics{images/layouts.pdf}
-    \caption{The considered layouts, with varying average distances between navigator and sensors.}
+    \caption{Diffrent simulation layouts with varying average distances between navigator and sensors.}
     \label{fig:sim_layouts}
 \end{figure}
-
-standard EIF, equivalent to the EKF, as the baseline we comapre to
-
-To evaluate the accuracy of our method, we have run $100$ simulations, all with $50$ filter iterations, for each of the sensor layouts with sensor measurement variances set to $r_i=5$ simulation units.
-Due to the large encoding modulus $N$, no notable advantage is gained when choosing a low fractional precision factor $\phi$, thus, $\phi=2^{32}$ was chosen to ensure minimal loss of precision when compared to the floating-point computations in the unencrypted EIF.
-The plotted average RMSE of our proposed method as well as that of the unencrypted EIF filter can be seen in Figure \ref{fig:sim_layout_errors}.
+The simulation root mean square error (RMSE) of the privacy-preserving method has been compared to the RMSE of the standard EIF (algebraic equivalent of the EKF), using the unmodified measurements.
+Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times.
+Unmodified measurement variances were taken as $r_i=5$ and a large fractional precision factor, $\phi=2^{32}$, was chosen.
+The results can be seen in figure \ref{fig:sim_layout_errors}.
 \begin{figure}[htbp]
@@
     \includegraphics{images/layout_errors.pdf}
-\caption{Filter error for different layouts, where solid lines show the results from our privacy-preserving filter and dashed lines from an unmodified EIF.}
+    \caption{MSE of the privacy-preserving EIF and standard EIF for different layout simulations.}
     \label{fig:sim_layout_errors}
 \end{figure}
-From the results, it can be seen that sensor distance has little effect on the performance of the filter and that the measurement modification from Section \ref{subsec:range_measurement_mod} has a negligible effect when compared to a normal EIF filter.
-The robustness of the privacy-preserving method can be attributed to the conservativeness of variance estimates in \eqref{eqn:modified_measurement_variance_estimate} and the sufficiently large fractional precision parameter $\phi$.
-
-In addition to accuracy, computational requirements are an important factor in the adoption of novel cryptographic methods.
-Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.}, bit lengths of $N$) and the number of sensors are varied.
-Every plotted time is again the average of $100$ simulations, each running for $50$ filter iterations.
+From these results, we can see the similarity in filter performance between the privacy-preserving method and that of the traditional EIF.
+We can also see that the varying average distances between sensors and navigator have little impact to the differences in performace.
+We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
+
+In addition to filter error, computational performance is important to consider when relying on cryptographic methods.
+Figure \ref{fig:sim_timing} shows the average execution time of $50$ simulation runs with varying numbers of sensors, for different key sizes (bit lengths of $N$).
+Here, increasing the number of sensors primarily affects the number of inter-process communications and aggregation modular multiplications due to the asynchronous implementation.
 \begin{figure}[htbp]
@@
 \end{figure}
-As sensor and navigator computations run in parallel, increases in runtime from additional sensors are primarily due to the longer aggregation operation at the navigator.
-The predominant computational cost is dependent on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme.
-The current recommendation for a secure implementation relying on prime factorisation (difficulty of factorising $N$) is to use $2048$ bit-long keys \cite{barkerRecommendationPairwiseKey2019}.
+We can see from the figure that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size.
+The key size should be chosen such that sufficient security is achieved, and the current recommentation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
+This results in a complete filter update step roughly every $1.6s$, for our implementation of the filter.
 

### 2021-06-03 main.tex
Typos grammarly missed

@@
 \end{figure}
-The simulation root mean square error (RMSE) of the privacy-preserving method has been compared to the RMSE of the standard EIF (algebraic equivalent of the EKF), using the unmodified measurements.
+The simulation root mean square error (RMSE) of the privacy-preserving method has been compared to the RMSE of the standard EIF (an algebraic equivalent of the EKF), using unmodified measurements.
 Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times.
@@
 From these results, we can see the similarity in filter performance between the privacy-preserving method and that of the traditional EIF.
-We can also see that the varying average distances between sensors and navigator have little impact to the differences in performace.
+We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance.
 We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
@@
 We can see from the figure that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size.
-The key size should be chosen such that sufficient security is achieved, and the current recommentation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
+The key size should be chosen such that sufficient security is achieved, and the current recommendation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
 This results in a complete filter update step roughly every $1.6s$, for our implementation of the filter.

### 2021-06-03 main.tex
Conclusion draft done

@@
 \section{Conclusion} \label{sec:conclusion}
-To develop a Bayesian localization algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Paillier and Joye-Libert encryption and aggregation schemes, respectively.
-This scheme was then used in our proposed privacy-preserving EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator.
-Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localization environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied.
-Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the application of LCAO secure schemes to alternative measurement models and the exploring of implications behind an active sensor attacker model.
+We have presented a localisation filter in the presence of range-only sensors, which preserves both navigator and sensor privacies.
+A suitable cryptographic scheme has been introduced and a filter implementation compared and evaluated.
+Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future.
+Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to increase the filter update frequency, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.
 
@@
 for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
-That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}).
+That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case, \cite{joyeScalableSchemePrivacyPreserving2013}).
 \begin{proof}

### 2021-06-03 main.tex
Updated notation  - estimates are now with a hat  - all measurement variances are now time-dependent (also resulted in changing notation of the estimated modified measurement variance)  - made process model and process noise time-dependent as well (more general, no reason not to be)  - made the EKF prediction steps avoid k+1 notation (this led to confusion and some wrong equations that should be fixed now)  - Re-added series notation to pictures that was removed in the latest drat changes  - note that the large number of notation changes will need a thorough proof read! Picture colours updated

@@
 $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences.
-When estimating a state, notation $\vec{x}_{k|l}$ will denote an estimate at timestep $k$ given measurements from timesteps up to and including $l$.
+When estimating a state, notation $\hat{\vec{x}}_{k|l}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including $l$.
 When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context.
@@
 \section{Problem Statement} \label{sec:problem_statement}
-In this work, we consider the context of privacy-preserving range-sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
-The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-sensor navigation.
+In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
+The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-only navigation.
 
@@
 
-At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear-combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
-Linear-combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
-This two-step linear-combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
+At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
+Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
+This two-step linear combination aggregation protocol has been visually displayed in figure \ref{fig:agg_steps}.
 \begin{figure}[htbp]
@@
     % Navigator
-    \fill (3.25,4.5) [blue!40] ellipse (0.4 and 0.4);
+    \fill (3.25,4.5) [green!80!black!60] ellipse (0.4 and 0.4);
     \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
@@
     \node at (1.5,0.375) {Sensor $1$};
-    \fill [red!40] (0.25,0.625) rectangle (2.875,1.625);
+    \fill [blue!80!black!40] (0.25,0.625) rectangle (2.875,1.625);
     \node at (1.625,1.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
     \node at (5,0.375) {Sensor $n$};
-    \fill [red!40] (3.625,0.625) rectangle (6.25,1.625);
+    \fill [blue!80!black!40] (3.625,0.625) rectangle (6.25,1.625);
     \node at (5,1.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
@@
     % Navigator
-    \fill [blue!40] (1.375,-3) rectangle (5.125,-1.25);
+    \fill [green!80!black!60] (1.375,-3) rectangle (5.125,-1.25);
     \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
@@
     \node at (1.25,-5.875) {Sensor $1$};
-    \fill  (5.25,-5.25) [red!40] ellipse (0.4 and 0.4);
+    \fill  (5.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
     \node at (5.25,-5.875) {Sensor $n$};
-    \fill  (1.25,-5.25) [red!40] ellipse (0.4 and 0.4);
+    \fill  (1.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
     \fill [black] (2.75,-5.25) circle (0.05);
@@
 \end{tikzpicture}
-\caption{Required linear-combination aggregation steps at instance $t$.}
+\caption{Required linear combination aggregation steps at instance $t$.}
 \label{fig:agg_steps}
@@
 We are now ready to define the type of encryption scheme we want for the specified communication protocol and the security guarantees it should provide.
-We let a linear-combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
+We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
 These will be used by a trusted setup party, the navigator and sensors $i,\,1\leq i \leq n$.
@@
     \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear-combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{LaTeXdescription}
@@
     \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
-    \item[Linear-Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
+    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
 Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
 \end{LaTeXdescription}
-While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear-Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
+While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
 Lastly, we conclude the cryptographic problem definition with the following important remark.
@@
 \begin{equation}
-    \vec{x}_k = \vec{f}(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
-\end{equation}
-with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. The measurement model is dependent on sensor $i$'s location,
-\begin{equation}
-    \vec{s}_i = 
-    \begin{bmatrix}
-        s_{x,i} & s_{y,i}
-    \end{bmatrix}^\top\,,
-\end{equation} 
-and is given by
+    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
+\end{equation}
+with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
 \begin{equation}
@@
 \end{equation}
-with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_i)$ and measurement function $h_i$, for sensor $i$, as
+with Gaussian measurement noises $v_{k,i} \sim \mathcal{N}(0,r_{k,i})$ and measurement function
 \begin{equation}
@@
         - \vec{s}_{i}\right\rVert \\
-        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,.
+        &= \sqrt{(x-s_{x,i})^2 + (y-s_{y,i})^2}\,,
     \end{split}
 \end{equation}
-
-We aim to provide a filter that estimates the navigator's state $\vec{x}_k$, at every timestep $k$, without learning sensor positions $\vec{s}_i$, measurements $z_{k,i}$ and measurement variances $r_i$ beyond the information in the corresponding aggregation leakage function.
+where
+\begin{equation}
+    \vec{s}_i = 
+    \begin{bmatrix}
+        s_{x,i} & s_{y,i}
+    \end{bmatrix}^\top
+\end{equation} 
+is the location of sensor $i$.
+
+We aim to provide a filter that estimates the navigator's state $\vec{x}_k$, at every timestep $k$, without learning sensor positions $\vec{s}_i$, measurements $z_{k,i}$ and measurement variances $r_{k,i}$ beyond the information in the corresponding aggregation leakage function.
 Similarly, sensors should not learn any information about current state estimates or any other sensor information.
@@
 
-\section{Private Linear-Combination Aggregation Scheme} \label{sec:lcao_scheme}
+\section{Private Linear Combination Aggregation Scheme} \label{sec:lcao_scheme}
 In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}.
@@
 To produce an estimate of the state $\vec{x}_k$, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation.
-The EIF update step requires the predicted state estimate $\vec{x}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
-\begin{equation}
-    \vec{y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
+The EIF update step requires the predicted state estimate $\hat{\vec{x}}_{k|k-1}$ and estimate covariance $\mat{P}_{k|k-1}$ in the information vector and matrix forms
+\begin{equation}
+    \hat{\vec{y}}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\hat{\vec{x}}_{k|k-1} \quad\textrm{and}\quad \mat{Y}_{k|k-1} = \mat{P}_{k|k-1}^{-1}\,,
 \end{equation}
@@
     \begin{split}
-        &\vec{y}_{k|k} = \vec{y}_{k|k-1} + \\
-        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1})
+        &\hat{\vec{y}}_{k|k} = \hat{\vec{y}}_{k|k-1} + \\
+        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1})
     \end{split} \label{eqn:eif_info_vec_update}
@@
 \begin{equation}
-    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\rvec{x}_{k|k-1}} \label{eqn:measurement_jacobian}
-\end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\vec{y}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
-\begin{equation}
-    \vec{x}_{k|k} = \mat{Y}_{k|k}^{-1}\vec{y}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
+    \mat{H}_{k,i} = \left.\frac{\partial h_i}{\partial \vec{x}}\right|_{\hat{\vec{x}}_{k|k-1}} \label{eqn:measurement_jacobian}
+\end{equation}
+for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\hat{\vec{y}}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
+\begin{equation}
+    \hat{\vec{x}}_{k|k} = \mat{Y}_{k|k}^{-1}\hat{\vec{y}}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
 \end{equation}
@@
 \begin{equation}
-    \vec{x}_{k+1|k} = \vec{f}(\vec{x}_{k|k}) \quad\textrm{and}\quad \mat{P}_{k+1|k} = \mat{F}_k\mat{P}_{k|k}\mat{F}_k^\top + \mat{Q}_k\,, \label{eqn:ekf_prediction}
+    \hat{\vec{x}}_{k|k-1} \!=\! \vec{f}_k(\hat{\vec{x}}_{k-1|k-1}) \ \textrm{and}\ \mat{P}_{k|k-1} \!=\! \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k, \label{eqn:ekf_prediction}
 \end{equation}
@@
 \begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}}{\partial \vec{x}}\right|_{\vec{x}_{k|k}}\,. \label{eqn:jacobian_f}
+    \mat{F}_{k} = \left.\frac{\partial \vec{f}_k}{\partial \vec{x}}\right|_{\hat{\vec{x}}_{k-1|k-1}}\,. \label{eqn:jacobian_f}
 \end{equation}
@@
 \begin{equation}
-    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\vec{x}_{k|k-1}) + \mat{H}_{k,i}\vec{x}_{k|k-1}) \label{eqn:measurement_vec}
+    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}) \label{eqn:measurement_vec}
 \end{equation}
@@
 \end{equation}
-namely, their measurements $z_{k,i}$, measurement variances $r_i$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-$\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, also require the current predicted state estimate $\vec{x}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
+namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
+$\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
 For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator.
-Application of the linear-combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and that the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
+Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and that the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
 
@@
 
-The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\vec{x}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
-Similarly, the Jacobian of $h_i$ at $\vec{x}_{k|k-1}$,
+The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
+Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
 \begin{equation}
@@
     \begin{bmatrix}
-        \frac{x_{k|k-1} - s_{x,i}}{\sqrt{(x_{k|k-1} - s_{x,i})^2 + (y_{k|k-1} - s_{y,i})^2}} \\
-        \frac{y_{k|k-1} - s_{y,i}}{\sqrt{(x_{k|k-1} - s_{x,i})^2 + (y_{k|k-1} - s_{y,i})^2}} 
+        \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
+        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} 
     \end{bmatrix}\,,
@@
 \end{equation}
-A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\vec{x}_{k|k-1}$, as
+A measurement function in this form allows rearrangement of $h'_i$ and the corresponding Jacobian $\mat{H}'_{k,i}$ to a linear combination of powers of location elements in $\hat{\vec{x}}_{k|k-1}$, as
 \begin{equation}
@@
     \begin{bmatrix}
-        2x_{k|k-1} - 2s_{x,i} \\
-        2y_{k|k-1} - 2s_{y,i}
+        2\hat{x}_{k|k-1} - 2s_{x,i} \\
+        2\hat{y}_{k|k-1} - 2s_{y,i}
     \end{bmatrix}\,. \label{eqn:modified_jacobian}
 \end{equation}
-Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $x_{k|k-1}^2$, $y_{k|k-1}^2$, $x_{k|k-1}$ and $y_{k|k-1}$.
+Here, $h'_i$ and $\mat{H}'_{k,i}$ are linear combinations of $\hat{x}_{k|k-1}^2$, $\hat{y}_{k|k-1}^2$, $\hat{x}_{k|k-1}$ and $\hat{y}_{k|k-1}$.
 To show how the corresponding modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$ can be similarly rearranged and used for localisation, we also require the existence of measurements following a modified measurement model of the form
@@
 \end{equation}
-where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r_{k,i}$.
-
-Computing $z'_{k,i}$ and its variance $r_{k,i}$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$, and simply squaring the original range measurements produces
+where $z'_{k,i}$ is the modified measurement, and noise term $v'_{k,i}$ is zero-mean and has a known variance $r'_{k,i}$.
+
+Computing $z'_{k,i}$ and its variance $r'_{k,i}$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_{k,i})$, and simply squaring the original range measurements produces
 \begin{equation}
@@
 \begin{equation}
-    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
+    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_{k,i}\, \label{eqn:modified_noise_mean}
 \end{equation}
@@
     \begin{split}
-        z'_{k,i} &= z_{k,i}^2 - r_i \\
-        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
+        z'_{k,i} &= z_{k,i}^2 - r_{k,i} \\
+        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_{k,i} \\
         &= h'_i(\vec{x}_k) + v'_{k,i}\,,
@@
 \end{equation}
-with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
-\begin{equation}
-    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
+with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_{k,i}$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
+\begin{equation}
+    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_{k,i} + 2r_{k,i}^2
 \end{equation}
@@
 which cannot be guaranteed.
-Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$.
+Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_{k,i}}$.
 The modified measurement's variance at timestep $k$ is therefore conservatively approximated by
@@
     \begin{split}
-        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
+        r'_{k, i} &= 4(z_{k,i} + 2\sqrt{r_{k,i}})^2r_{k,i} + 2r_{k,i}^2 \\
         &\gtrapprox \mathsf{Var}[v'_{k,i}]
@@
 
-\subsection{Localization} \label{subsec:localization}
+\subsection{Localisation} \label{subsec:localisation}
 To complete the EIF update using a linear combination aggregation process, modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$, using the modified measurement model \eqref{eqn:modified_measurement_model}, can be rearragned as follows.
@@
     \begin{split}
-        \vec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}(z'_{k,i} - h'_i(\vec{x}_{k|k-1}) + \mat{H}'_{k,i}\vec{x}_{k|k-1}) \\
+        \vec{i}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{\prime-1}(z'_{k,i} - h'_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}'_{k,i}\hat{\vec{x}}_{k|k-1}) \\
         &= 
@@
             \begin{split}
-                &(2r_{k,i}^{-1})x_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}y_{k|k-1}^2 \\
-                &\quad+ (-r_{k,i}^{-1}s_{x,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{x,i})y_{k|k-1}^2 \\
-                &\quad+ (2r_{k,i}^{-1}z'_{k,i})x_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)x_{k|k-1}\\
-                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)x_{k|k-1} + (2r_{k,i}^{-1}s_{x,i}^3) \\
-                &\quad+ (2r_{k,i}^{-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{-1}s_{x,i} z'_{k,i})
+                &(2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
+                &\quad+ (-r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\
+                &\quad+ (2r_{k,i}^{\prime-1}z'_{k,i})\hat{x}_{k|k-1} + (-2r_{k,i}^{\prime-1}s_{x,i}^2)\hat{x}_{k|k-1}\\
+                &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i}^2)\hat{x}_{k|k-1} + (2r_{k,i}^{\prime-1}s_{x,i}^3) \\
+                &\quad+ (2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{\prime-1}s_{x,i} z'_{k,i})
             \end{split}
@@
             \begin{split}
-                &(2r_{k,i}^{-1})y_{k|k-1}^3 + (2r_{k,i}^{-1})x_{k|k-1}^2y_{k|k-1} \\
-                &\quad+ (-2r_{k,i}^{-1}s_{y,i})x_{k|k-1}^2 + (-2r_{k,i}^{-1}s_{y,i})y_{k|k-1}^2 \\
-                &\quad+ (2r_{k,i}^{-1}z'_{k,i})y_{k|k-1} + (-2r_{k,i}^{-1}s_{x,i}^2)y_{k|k-1} \\
-                &\quad+ (-2r_{k,i}^{-1}s_{y,i}^2)y_{k|k-1} + (2r_{k,i}^{-1}s_{y,i}s_{x,i}^2) \\
-                &\quad+ (2r_{k,i}^{-1}s_{y,i}^3) + (-2r_{k,i}^{-1}s_{y,i}z'_{k,i})
+                &(2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\
+                &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1}^2 \\
+                &\quad+ (2r_{k,i}^{\prime-1}z'_{k,i})\hat{y}_{k|k-1} + (-2r_{k,i}^{\prime-1}s_{x,i}^2)\hat{y}_{k|k-1} \\
+                &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i}^2)\hat{y}_{k|k-1} + (2r_{k,i}^{\prime-1}s_{y,i}s_{x,i}^2) \\
+                &\quad+ (2r_{k,i}^{\prime-1}s_{y,i}^3) + (-2r_{k,i}^{\prime-1}s_{y,i}z'_{k,i})
             \end{split}
@@
     \begin{split}
-        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{-1}\mat{H}'_{k,i} \\
+        \mat{I}'_{k,i} &= \mat{H}_{k,i}^{\prime\top} r_{k,i}^{\prime-1}\mat{H}'_{k,i} \\
         &=
@@
 \begin{align*}
-    \beta_{11} &= (4r_{k,i}^{-1})x_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{x,i})x_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}^2)\,, \\
-    \begin{split}
-        \beta_{12} &= (4r_{k,i}^{-1})x_{k|k-1}y_{k|k-1} + (-4r_{k,i}^{-1}s_{y,i})x_{k|k-1}  \\
-        &\qquad+ (-4r_{k,i}^{-1}s_{x,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{x,i}s_{y,i})\,,
+    \beta_{11} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
+    \begin{split}
+        \beta_{12} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\
+        &\qquad+ (-4r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}s_{y,i})\,,
     \end{split}\\
     \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
-    \beta_{22} &= (4r_{k,i}^{-1})y_{k|k-1}^2 + (-8r_{k,i}^{-1}s_{y,i})y_{k|k-1} + (4r_{k,i}^{-1}s_{y,i}^2)\,.
+    \beta_{22} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
 \end{align*}
-The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of
-\begin{equation}
-    \begin{split}
-        &\{ x_{k|k-1}^3,\ y_{k|k-1}^3,\ x_{k|k-1}^2y_{k|k-1},\ x_{k|k-1}y_{k|k-1}^2,\\
-        &\quad x_{k|k-1}^2,\ y_{k|k-1}^2,\ x_{k|k-1}y_{k|k-1},\ x_{k|k-1},\ y_{k|k-1}\}\,,
+The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of elements in
+\begin{equation}
+    \begin{split}
+        &\{ \hat{x}_{k|k-1}^3,\ \hat{y}_{k|k-1}^3,\ \hat{x}_{k|k-1}^2\hat{y}_{k|k-1},\ \hat{x}_{k|k-1}\hat{y}_{k|k-1}^2,\\
+        &\quad \hat{x}_{k|k-1}^2,\ \hat{y}_{k|k-1}^2,\ \hat{x}_{k|k-1}\hat{y}_{k|k-1},\ \hat{x}_{k|k-1},\ \hat{y}_{k|k-1}\}\,,
     \end{split} \label{eqn:weights_to_broadcast}
 \end{equation}
-which now capture all the private state information in $\vec{x}_{k|k-1}$ required at the sensors.
+which now captures all the private state information in $\hat{\vec{x}}_{k|k-1}$ required at the sensors.
 The corresponding EIF update steps \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update} then become
 \begin{equation}
-    \vec{y}_{k|k} = \vec{y}_{k|k-1} + \sum^n_{i=1}\vec{i}'_{k,i} \label{eqn:eif_modified_vec_update}
+    \hat{\vec{y}}_{k|k} = \hat{\vec{y}}_{k|k-1} + \sum^n_{i=1}\vec{i}'_{k,i} \label{eqn:eif_modified_vec_update}
 \end{equation}
@@
 \begin{algorithmic}[1]
-    \Procedure{Prediction}{$\vec{x}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}$, $\mat{Q}$, $N$}
+    \Procedure{Prediction}{$\hat{\vec{x}}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}_k$, $\mat{Q}_k$, $N$}
 
     \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
-    \State $\vec{x}_{k|k-1} \gets \vec{f}(\vec{x}_{k-1|k-1})$
+    \State $\hat{\vec{x}}_{k|k-1} \gets \vec{f}_k(\hat{\vec{x}}_{k-1|k-1})$
     \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k$
 
-    \State Compute $\mathsf{E}_{0}(x^3_{k|k-1})$ by \eqref{eqn:encode}
-    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
-    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$ to sensors
+    \State Compute $\mathsf{E}_{0}(\hat{x}^3_{k|k-1})$ by \eqref{eqn:encode}
+    \State Compute $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))$ by \eqref{eqn:our_scheme_encrypt}
+    \State Broadcast $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))$ to sensors
     \For{Remaining weights in \eqref{eqn:weights_to_broadcast}} 
@@
 
-    \State \Return $\vec{x}_{k|k-1}, \mat{P}_{k|k-1}$
+    \State \Return $\hat{\vec{x}}_{k|k-1}, \mat{P}_{k|k-1}$
     \EndProcedure
@@
 \begin{algorithmic}[1]
-    \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_i$, $N$, $H$}
+    \Procedure{Measurement}{$i$, $s_{x,i}$, $s_{y,i}$, $r_{k,i}$, $N$, $H$}
 
@@
     \State Compute $z'_{k,i}$ by \eqref{eqn:modified_measurement}
-    \State Compute $r_{k,i}$ by \eqref{eqn:modified_measurement_variance_estimate}
-
-    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))$
+    \State Compute $r'_{k,i}$ by \eqref{eqn:modified_measurement_variance_estimate}
+
+    \State Recieve $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))$
     \For{Remaining weights in \eqref{eqn:weights_to_broadcast}}
@@
     \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}y^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(y^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{-1}z_{k,i}')}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{-1}s_{y,i}^2)}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}^3)}
-    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{-1}s_{x,i}s_{y,i}^2)}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{-1}s_{x,i}z_{k,i}')}
+    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1}z_{k,i}')}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k,i}^{\prime-1}s_{y,i}^2)}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}^3)}
+    (N+1)^{\mathsf{E}_{1}(2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2)}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
@@
     \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(x^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(x_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{-1}s_{x,i})}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{-1}s_{x,i}^2)}\cdot$\par
+    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
+    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
@@
 \begin{algorithmic}[1]
-    \Procedure{Update}{$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}
+    \Procedure{Update}{$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$, $N$, $\lambda$}
 
@@
 
-    \State $\vec{y}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\vec{x}_{k|k-1} + \sum_{i=1}^n\vec{i}'_{k,i}$
+    \State $\hat{\vec{y}}_{k|k} \gets \mat{P}_{k|k-1}^{-1}\hat{\vec{x}}_{k|k-1} + \sum_{i=1}^n\vec{i}'_{k,i}$
     \State $\mat{Y}_{k|k} \gets \mat{P}_{k|k-1}^{-1} + \sum_{i=1}^n\mat{I}'_{k,i}$
-    \State $\vec{x}_{k|k} \gets \mat{Y}_{k|k}^{-1}\vec{y}_{k|k}$
+    \State $\hat{\vec{x}}_{k|k} \gets \mat{Y}_{k|k}^{-1}\hat{\vec{y}}_{k|k}$
     \State $\mat{P}_{k|k} \gets \mat{Y}_{k|k}^{-1}$
-    \State \Return $\vec{x}_{k|k}, \mat{P}_{k|k}$
+    \State \Return $\hat{\vec{x}}_{k|k}, \mat{P}_{k|k}$
     \EndProcedure
@@
     % Navigator
-    \fill  [blue!40] (2,7) rectangle (4.5,5.5);
+    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.5);
     \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
-    \node at (3.25,5.875) {$\vec{x}_{k|k-1}$, $\mat{P}_{k|k-1}$};
+    \node at (3.25,5.875) {$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$};
 
     % Sensors
-    \fill  (1.25,3) [red!40] ellipse (0.4 and 0.4);
+    \fill  (1.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
     \node at (1.25,2.375) {Sensor $1$};
-    \fill  (5.25,3) [red!40] ellipse (0.4 and 0.4);
+    \fill  (5.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
     \node at (5.25,2.375) {Sensor $n$};
@@
     \fill [lightgray]  (0.25,5) rectangle (6.25,4);
-    \node at (3.25,4.5) {$\left\{\mathcal{E}_{pk_0}(\mathsf{E}_0(\rv{\omega})) \,|\, \rv{\omega} \!\in\! \{\rv{x}^3_{k|k-1}, \rv{y}^3_{k|k-1}, \dots\}\right\}$};
+    \node at (3.25,4.5) {$\left\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\omega)) \,|\, \omega \!\in\! \{\hat{x}^3_{k|k-1}, \hat{y}^3_{k|k-1}, \dots\}\right\rangle$};
 
@@
     % Navigator
-    \fill  (3.25,0.25) [blue!40] ellipse (0.4 and 0.4);
+    \fill  (3.25,0.25) [green!80!black!60] ellipse (0.4 and 0.4);
     \pic[xscale=0.22,yscale=0.3] at (3.25,0.4225) {plane};
@@
     % Sensors
-    \fill  [red!40] (6.25,-3.625)  rectangle (4.25,-2.625);
+    \fill  [blue!80!black!40] (6.25,-3.625)  rectangle (4.25,-2.625);
     \node at (1.25,-3.875) {Sensor $1$};
-    \fill  [red!40] (2.25,-3.625)  rectangle (0.25,-2.625);
+    \fill  [blue!80!black!40] (2.25,-3.625)  rectangle (0.25,-2.625);
     \node at (5.25,-3.875) {Sensor $n$};
 
-    \node at (1.25,-3.125) {$z'_{k,1}$, $r_{k,1}$};
-    \node at (5.25,-3.125) {$z'_{k,n}$, $r_{k,n}$};
+    \node at (1.25,-3.125) {$z'_{k,1}$, $r'_{k,1}$};
+    \node at (5.25,-3.125) {$z'_{k,n}$, $r'_{k,n}$};
 
@@
     % Navigator
-    \fill  [blue!40] (1.5,-5.5) rectangle (5,-7.5);
+    \fill  [green!80!black!60] (1.5,-5.5) rectangle (5,-7.5);
     \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
     \node at (3.25,-6.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (3.25,-7.125) {$\vec{x}_{k|k}$, $\mat{P}_{k|k}$};
+    \node at (3.25,-7.125) {$\hat{\vec{x}}_{k|k}$, $\mat{P}_{k|k}$};
 \end{tikzpicture}
@@
 However, recalling that a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$.
-From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
-\begin{equation}
-    \sum_{i=1}^nz'_{k,i}\,,\ \sum_{i=1}^nr_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,,\label{eqn:localisation_leakage}
+From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r'_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
+\begin{equation}
+    \sum_{i=1}^nz'_{k,i}\,,\ \sum_{i=1}^nr'_{k,i}\,,\ \sum_{i=1}^ns_{x,i}\ \textrm{and}\ \sum_{i=1}^ns_{y,i}\,,\label{eqn:localisation_leakage}
 \end{equation}
@@
 
-We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r_{k,i}$ on the original measurements $z_{k,i}$.
+We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r'_{k,i}$ on the original measurements $z_{k,i}$.
 The layouts, of varying sensor distances to the navigator track, are shown in figure \ref{fig:sim_layouts}.
@@
 Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times.
-Unmodified measurement variances were taken as $r_i=5$ and a large fractional precision factor, $\phi=2^{32}$, was chosen.
+Unmodified measurement variances were taken as $r_{k,i}=5$ for all $k>0$ and a large fractional precision factor, $\phi=2^{32}$, was chosen.
 The results can be seen in figure \ref{fig:sim_layout_errors}.
@@
 We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance.
-We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
+We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
 
@@
 \appendices
-\section{Linear-Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
+\section{Linear Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
 The following game between attacker and challenger defines the security notion of LCAO.

### 2021-06-03 main.tex
Missed mistake and some grammarly fixes

@@
 
-% Note that keywords are not normally used for peerreview papers.
+% Key words
 \begin{IEEEkeywords}
@@
 
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
+% Creates the second title
 \IEEEpeerreviewmaketitle
@@
 In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent.
-The state that we wish to estimate captures the navigator position and the change in position ($\Delta$), and is given by
+The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
 \begin{equation}
@@
 These schemes have been summarised below.
-Additionally, the estimation problem we consider uses real-valued inputs and functions, and will require encoding real numbers for use with the aforementioned encryption schemes.
+Additionally, the estimation problem we consider uses real-valued inputs and functions and will require encoding real numbers for use with the aforementioned encryption schemes.
 The method used for encoding has been summarised afterwards.
@@
 \begin{definition}
-    An encryption scheme meets LCAO security if no adversary, running in probabilistic-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
+    An encryption scheme meets LCAO security if no probabilistic adversary, running in polynomial-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
 Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.

### 2021-06-04 main.tex
Highlighted novelty of the work more than before (as per reviewer request) Explicitly pointed out how the accuracy of the filter can be assessed form the provided figures (accuracy was said to be missing by a reviewer) Fixed problem with the reasoning behind taking a 95% confident conservative modified measurement variance estimate (error pointed out by reviewer)

@@
 
-Our contribution in this work considers range-only localisation with formal cryptographic requirements ensuring that sensors keep their measurements and locations private and that navigator estimates cannot be learned by sensors.
-We define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
-The linear combination aggregation scheme put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing communication assumptions and leakages is given, crucial for cryptographic security.
+Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private and navigator estimates cannot be learned by sensors.
+We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
+The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing communication assumptions and leakages is given, crucial for cryptographic security.
+To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.
 
 We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations.
-While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown at other present stations and to the navigator.
+While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown to the other present stations and to the navigator.
 Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.
@@
 \begin{equation}
-    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_{k,i} + 2r_{k,i}^2
+    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_{k,i} + 2r_{k,i}^2 \label{eqn:modified_measurement_variance}
 \end{equation}
@@
 Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence.
-The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
-\begin{equation}
-    \begin{split}
-        &z_{k,i} > h_i(\vec{x}_k) \\
-        \implies &v_{k,i} > 0\,,
-    \end{split}
-\end{equation}
-which cannot be guaranteed.
-Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_{k,i}}$.
-The modified measurement's variance at timestep $k$ is therefore conservatively approximated by
+While the naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$ in \eqref{eqn:modified_measurement_variance}, may not provide a conservative estimate when $z_{k,i}^2 < h_i(\vec{x}_k)^2$, the Gaussianity of $v_{k,i}$ can be exploited to provide a conservative estimate with $95\%$ confidence by shifting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_{k,i}}$.
+The modified measurement's variance at timestep $k$ can therefore be conservatively approximated by
 \begin{equation}
@@
         r'_{k, i} &= 4(z_{k,i} + 2\sqrt{r_{k,i}})^2r_{k,i} + 2r_{k,i}^2 \\
-        &\gtrapprox \mathsf{Var}[v'_{k,i}]
-    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
+        &\gtrapprox \mathsf{Var}[v'_{k,i}]\,,
+    \end{split} \label{eqn:modified_measurement_variance_estimate}
 \end{equation}
@@
 \end{figure}
-The simulation root mean square error (RMSE) of the privacy-preserving method has been compared to the RMSE of the standard EIF (an algebraic equivalent of the EKF), using unmodified measurements.
+To demonstrate the accuracy of the method, we have compared the root mean square error (RMSE) of the privacy-preserving filter to the standard EIF using unmodified measurements, that is algebraically equivalent to the EKF, typically used in industry for linearising non-linear state estimation.
 Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times.

### 2021-06-07 main.tex
Readthrough with little fixes

@@
 
-Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private and navigator estimates cannot be learned by sensors.
+Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private.
 We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
@@
 We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations.
-While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown to the other present stations and to the navigator.
+While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown to the other present stations and the navigator.
 Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.
@@
 In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
-Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} the solution to the estimation problem making use of this scheme.
+Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} gives a solution to the estimation problem making use of this scheme.
 Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.
@@
 When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context.
-$\mathbb{Z}_n$ is used for the set of integers m  odulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
-$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to the cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
+$\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
 
@@
 \end{LaTeXdescription}
-Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed $\pmod{N}$.
+Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.
 
@@
 The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums, $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively.
-However, recalling that a compromised navigator can also learn the individual sums weighted by the same weight, which in this case means the leakage of $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$.
+However, recalling that a compromised navigator can also learn the individual sums weighted by the same weight, $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$ can be leaked as well.
 From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r'_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
@@
 We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r'_{k,i}$ on the original measurements $z_{k,i}$.
-The layouts, of varying sensor distances to the navigator track, are shown in figure \ref{fig:sim_layouts}.
+These layouts of varying sensor distances to the navigator track are shown in figure \ref{fig:sim_layouts}.
 \begin{figure}[htbp]

### 2021-06-10 main.tex
Fixed error in equations where measurement vector and matrix were treated as 2 dimensional rather than 4. Small notation change has bene made to make the pseudocode handle this change accordingly

@@
 \usepackage{mathtools}
+\usepackage{bm}
 % Algorithms
@@
         \begin{bmatrix}
-            \begin{split}
-                &(2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
+            \alpha_1^{(i)} & 0 & \alpha_2^{(i)} & 0
+        \end{bmatrix}^\top\,,
+    \end{split} \label{eqn:hrz_linear_comb}
+\end{equation}
+with
+\begin{align*}
+    \begin{split}
+        \alpha_1^{(i)} &= (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
         &\quad+ (-r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\
@@
         &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i}^2)\hat{x}_{k|k-1} + (2r_{k,i}^{\prime-1}s_{x,i}^3) \\
-                &\quad+ (2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{\prime-1}s_{x,i} z'_{k,i})
-            \end{split}
-            \vspace{5pt}\\
-            \begin{split}
-                &(2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\
+        &\quad+ (2r_{k,i}^{\prime-1}s_{x,i}s_{y,i}^2) + (-2r_{k,i}^{\prime-1}s_{x,i} z'_{k,i})\ \textrm{and}
+    \end{split}\\
+    \begin{split}
+        \alpha_2^{(i)} &= (2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\
         &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1}^2 \\
@@
         &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i}^2)\hat{y}_{k|k-1} + (2r_{k,i}^{\prime-1}s_{y,i}s_{x,i}^2) \\
-                &\quad+ (2r_{k,i}^{\prime-1}s_{y,i}^3) + (-2r_{k,i}^{\prime-1}s_{y,i}z'_{k,i})
+        &\quad+ (2r_{k,i}^{\prime-1}s_{y,i}^3) + (-2r_{k,i}^{\prime-1}s_{y,i}z'_{k,i})\,,
     \end{split}
-        \end{bmatrix}
-    \end{split} \label{eqn:hrz_linear_comb}
-\end{equation}
+\end{align*}
 and
@@
         \begin{bmatrix}
-            \beta_{11} & \beta_{12} \\
-            \beta_{21} & \beta_{22}
+            \beta_1^{(i)} & 0 & \beta_2^{(i)} & 0 \\
+            0 & 0 & 0 & 0 \\
+            \beta_3^{(i)} & 0 & \beta_4^{(i)} & 0 \\
+            0 & 0 & 0 & 0
         \end{bmatrix}\,,
@@
 \begin{align*}
-    \beta_{11} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
-    \begin{split}
-        \beta_{12} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\
+    \beta_1^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
+    \begin{split}
+        \beta_2^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\
         &\qquad+ (-4r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}s_{y,i})\,,
     \end{split}\\
-    \beta_{21} &= \beta_{12}\,,\ \textrm{and} \\
-    \beta_{22} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
+    \beta_3^{(i)} &= \beta_{12}\ \textrm{and} \\
+    \beta_4^{(i)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
 \end{align*}
@@
 
-    \State Let $\alpha_{v}^{(i)}$ represent an encryption of element $v$ in $\vec{i}'_{k,i}$ from \eqref{eqn:hrz_linear_comb}
-    \State $\alpha_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
+    \State Let $\bm{\alpha}_{v}^{(i)}$ represent the encryption of $\alpha_{v}^{(i)}$ in \eqref{eqn:hrz_linear_comb}
+    \State $\bm{\alpha}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
@@
     H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\alpha_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
+    \State Compute $\bm{\alpha}_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
     \For{$v \gets 1$ to $2$}
-        \State Send $\alpha_{v}^{(i)}$ to the navigator
+        \State Send $\bm{\alpha}_{v}^{(i)}$ to the navigator
     \EndFor
 
-    \State Let $\beta_{vw}^{(i)}$ represent an encryption of element $(v,w)$ in $\mat{I}'_{k,i}$ from \eqref{eqn:hrh_linear_comb}
-    \State $\beta_{11}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
+    \State Let $\bm{\beta}_{w}^{(i)}$ represent an encryption of $\beta_{w}^{(i)}$ in \eqref{eqn:hrh_linear_comb}
+    \State $\bm{\beta}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
@@
     \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\beta_{vw}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
-    \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$} 
-            \State Send $\beta_{vw}^{(i)}$ to the navigator
-        \EndFor
+    \State Compute remaining $\bm{\beta}_{w}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
+    \For{$w \gets 1$ to $4$}
+        \State Send $\bm{\beta}_{w}^{(i)}$ to the navigator
     \EndFor
@@
     \For{$v \gets 1$ to $2$}
-        \State Receive $\alpha_{v}^{(i)}$ from each sensor $1\leq i \leq n$
+        \State Receive $\bm{\alpha}_{v}^{(i)}$ from each sensor $1\leq i \leq n$
     \EndFor
 
+    \For{$w \gets 1$ to $4$}
+        \State Receive $\bm{\beta}_{w}^{(i)}$ from each sensor $1\leq i \leq n$
+    \EndFor
+
+    \State Let $\bm{\alpha}_{v}$ represent an encryption of $\sum_{i=1}^n\alpha_{v}^{(i)}$
     \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$}
-        \State Receive $\beta_{vw}^{(i)}$ from each sensor $1\leq i \leq n$
-        \EndFor
-    \EndFor
-
-    \State Let $\alpha_{v}$ represent an encryption of element $v$ in $\sum_{i=1}^n\vec{i}'_{k,i}$
-    \For{$v \gets 1$ to $2$}
-        \State $\alpha_{v} \gets \prod_{i=1}^n\alpha_{v}^{(i)}$
-        \State Compute $\mathcal{D}_{sk_0}(\alpha_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\alpha_{v}))$ by \eqref{eqn:decode}
+        \State $\bm{\alpha}_{v} \gets \prod_{i=1}^n\bm{\alpha}_{v}^{(i)}$
+        \State Compute $\mathcal{D}_{sk_0}(\bm{\alpha}_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\alpha}_{v}))$ by \eqref{eqn:decode}
     \EndFor
@@
 
-    \State Let $\beta_{vw}$ represent an encryption of element $(v,w)$ in $\sum_{i=1}^n\mat{I}'_{k,i}$
-    \For{$v \gets 1$ to $2$}
-        \For{$w \gets 1$ to $2$}
-            \State $\beta_{vw} \gets \prod_{i=1}^n\beta_{vw}^{(i)}$
-            \State Compute $\mathcal{D}_{sk_0}(\beta_{vw})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\beta_{vw}))$ by \eqref{eqn:decode}
-        \EndFor
+    \State Let $\bm{\beta}_{w}$ represent an encryption of $\sum_{i=1}^n\beta_{w}^{(i)}$
+    \For{$w \gets 1$ to $4$}
+            \State $\bm{\beta}_{w} \gets \prod_{i=1}^n\bm{\beta}_{w}^{(i)}$
+            \State Compute $\mathcal{D}_{sk_0}(\bm{\beta}_{w})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\beta}_{w}))$ by \eqref{eqn:decode}
     \EndFor

### 2021-06-11 main.tex
Change results pictures - main result picture made much more legible (as pointed out by reviewer) - timing picture made smaller and correctly centered - layouts picture made smaller, correctly centered, and added covariance to the legend - made tikz pictures smaller (not by scaling but by moving the pics objects so that it fits in less space Still not 12 pages but very close

@@
     % Navigator
-    \fill (3.25,4.5) [green!80!black!60] ellipse (0.4 and 0.4);
-    \pic[xscale=0.22,yscale=0.3] at (3.25,4.6725) {plane};
+    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
     % Sensors
-    \node at (1.5,0.375) {Sensor $1$};
-    \fill [blue!80!black!40] (0.25,0.625) rectangle (2.875,1.625);
-    \node at (1.625,1.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
-    \node at (5,0.375) {Sensor $n$};
-    \fill [blue!80!black!40] (3.625,0.625) rectangle (6.25,1.625);
-    \node at (5,1.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
-    \fill [black] (3.5,1.125) circle (0.05);
-    \fill [black] (3,1.125) circle (0.05);
-    \fill [black] (3.25,1.125) circle (0.05);
+    \node at (1.5,1.375) {Sensor $1$};
+    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
+    \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
+    \node at (5,1.375) {Sensor $n$};
+    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
+    \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
+    \fill [black] (3.5,2.125) circle (0.05);
+    \fill [black] (3,2.125) circle (0.05);
+    \fill [black] (3.25,2.125) circle (0.05);
     % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4) (5,1.875)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4) (1.5,1.875)};
-    \fill [lightgray] (2.125,3.375) rectangle (4.375,2.625);
-    \node at (3.25,3) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,4.25) (5,2.875)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,4.25) (1.5,2.875)};
+    \fill [lightgray] (2.125,3.875) rectangle (4.375,3.125);
+    \node at (3.25,3.5) {$\langle\omega_1^{(t)},\dots ,\omega_m^{(t)}\rangle$};
 
     % Step 2
-    \node at (3.25,-0.75) {2. Aggregation Step};
+    \node at (3.25,0.25) {2. Aggregation Step};
     % Navigator
-    \fill [green!80!black!60] (1.375,-3) rectangle (5.125,-1.25);
-    \pic[xscale=0.22,yscale=0.3] at (3.25,-1.4775) {plane};
-    \node at (3.25,-2.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
+    \fill [green!80!black!60] (1.375,-2) rectangle (5.125,-0.25);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,-0.4775) {plane};
+    \node at (3.25,-1.375) {$\displaystyle \sum^{n}_{i=1}\sum^{m}_{j=1} a_{i,j}^{(t)}\omega_j^{(t)} = \sum^n_{i=1}l^{(t)}_{i}$};
     % Sensors
-    \node at (1.25,-5.875) {Sensor $1$};
-    \fill  (5.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
-    \node at (5.25,-5.875) {Sensor $n$};
-    \fill  (1.25,-5.25) [blue!80!black!40] ellipse (0.4 and 0.4);
-    \fill [black] (2.75,-5.25) circle (0.05);
-    \fill [black] (3.75,-5.25) circle (0.05);
-    \fill [black] (3.25,-5.25) circle (0.05);
+    \node at (1.25,-3.875) {Sensor $1$};
+    \fill  (5.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \node at (5.25,-3.875) {Sensor $n$};
+    \fill  (1.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \fill [black] (2.75,-3.25) circle (0.05);
+    \fill [black] (3.75,-3.25) circle (0.05);
+    \fill [black] (3.25,-3.25) circle (0.05);
     % Lines
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-4.75) (3.75,-3.25)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-4.75) (2.75,-3.25)};
-    \fill [lightgray] (1.625,-3.75) rectangle (2.25,-4.25);
-    \node at (2,-4) {$l_1^{(t)}$};
-    \fill [lightgray] (4.25,-3.75) rectangle (4.875,-4.25);
-    \node at (4.625,-4) {$l_n^{(t)}$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(5,-2.75) (4.5,-2.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.5,-2.75) (2,-2.25)};
+    \fill [lightgray] (1.625,-2.5) rectangle (2.25,-3);
+    \node at (2,-2.75) {$l_1^{(t)}$};
+    \fill [lightgray] (4.25,-2.5) rectangle (4.875,-3);
+    \node at (4.625,-2.75) {$l_n^{(t)}$};
 
     % Bounding rectangles
-    \draw [gray] (0,6) rectangle (6.5,0);
-    \draw [gray] (0,-0.25) rectangle (6.5,-6.25);
+    \draw [gray] (0,6) rectangle (6.5,1);
+    \draw [gray] (0,0.75) rectangle (6.5,-4.25);
 \end{tikzpicture}
@@
     % Prediction
-    \draw [gray] (0,2) rectangle (6.5,8);
+    \draw [gray] (0,3) rectangle (6.5,8);
     \node at (3.25,7.5) {\small 1. Prediction};
@@
     % Navigator
-    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.5);
-    \pic[xscale=0.22,yscale=0.3] at (3.25,6.6725) {plane};
-    \node at (3.25,5.875) {$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$};
+    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.75);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,6.7975) {plane};
+    \node at (3.25,6.0625) {$\hat{\vec{x}}_{k|k-1}$, $\mat{P}_{k|k-1}$};
 
     % Sensors
-    \fill  (1.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
-    \node at (1.25,2.375) {Sensor $1$};
-    \fill  (5.25,3) [blue!80!black!40] ellipse (0.4 and 0.4);
-    \node at (5.25,2.375) {Sensor $n$};
-
-    \fill [black] (2.75,3) circle (0.05);
-    \fill [black] (3.25,3) circle (0.05);
-    \fill [black] (3.75,3) circle (0.05);
+    \fill  (1.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \node at (1.25,3.375) {Sensor $1$};
+    \fill  (5.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \node at (5.25,3.375) {Sensor $n$};
+
+    \fill [black] (2.75,4) circle (0.05);
+    \fill [black] (3.25,4) circle (0.05);
+    \fill [black] (3.75,4) circle (0.05);
 
     % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,5.25) (1.5,3.5)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,5.25) (5,3.5)};
-
-    \fill [lightgray]  (0.25,5) rectangle (6.25,4);
-    \node at (3.25,4.5) {$\left\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\omega)) \,|\, \omega \!\in\! \{\hat{x}^3_{k|k-1}, \hat{y}^3_{k|k-1}, \dots\}\right\rangle$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3,5.5) (1.75,4.25)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(3.5,5.5) (4.75,4.25)};
+
+    \fill [lightgray]  (0.25,5.375) rectangle (6.25,4.625);
+    \node at (3.25,5) {$\left\langle\mathcal{E}_{pk_0}(\mathsf{E}_0(\omega)) \,|\, \omega \!\in\! \{\hat{x}^3_{k|k-1}, \hat{y}^3_{k|k-1}, \dots\}\right\rangle$};
 
     % Measurement
-    \draw [gray] (0,-4.25) rectangle (6.5,1.75);
-    \node at (3.25,1.25) {\small 2. Measurement};
+    \draw [gray] (0,-2.25) rectangle (6.5,2.75);
+    \node at (3.25,2.25) {\small 2. Measurement};
 
     % Navigator
-    \fill  (3.25,0.25) [green!80!black!60] ellipse (0.4 and 0.4);
-    \pic[xscale=0.22,yscale=0.3] at (3.25,0.4225) {plane};
+    \fill  (3.25,1.5) [green!80!black!60] ellipse (0.4 and 0.4);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,1.6725) {plane};
 
     % Sensors
-    \fill  [blue!80!black!40] (6.25,-3.625)  rectangle (4.25,-2.625);
-    \node at (1.25,-3.875) {Sensor $1$};
-    \fill  [blue!80!black!40] (2.25,-3.625)  rectangle (0.25,-2.625);
-    \node at (5.25,-3.875) {Sensor $n$};
-
-    \node at (1.25,-3.125) {$z'_{k,1}$, $r'_{k,1}$};
-    \node at (5.25,-3.125) {$z'_{k,n}$, $r'_{k,n}$};
-
-    \fill [black] (2.75,-3.125) circle (0.05);
-    \fill [black] (3.25,-3.125) circle (0.05);
-    \fill [black] (3.75,-3.125) circle (0.05);
+    \fill  [blue!80!black!40] (6.25,-1.625)  rectangle (4.25,-0.625);
+    \node at (1.25,-1.875) {Sensor $1$};
+    \fill  [blue!80!black!40] (2.25,-1.625)  rectangle (0.25,-0.625);
+    \node at (5.25,-1.875) {Sensor $n$};
+
+    \node at (1.25,-1.125) {$z'_{k,1}$, $r'_{k,1}$};
+    \node at (5.25,-1.125) {$z'_{k,n}$, $r'_{k,n}$};
+
+    \fill [black] (2.75,-1.125) circle (0.05);
+    \fill [black] (3.25,-1.125) circle (0.05);
+    \fill [black] (3.75,-1.125) circle (0.05);
 
     % Arrows
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.25,-2.5) (3,-0.25)};
-    \draw [-latex] plot[smooth, tension=.7] coordinates {(5.25,-2.5) (3.5,-0.25)};
-
-    \fill [lightgray]  (0.375,-0.875) rectangle (3.125,-1.875);
-    \node[align=center] at (1.75,-1.375) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
-    \fill [lightgray]  (3.375,-0.875) rectangle (6.125,-1.875);
-    \node[align=center] at (4.75,-1.375) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(1.25,-0.5) (3,1)};
+    \draw [-latex] plot[smooth, tension=.7] coordinates {(5.25,-0.5) (3.5,1)};
+
+    \fill [lightgray]  (0.375,0.75) rectangle (3.125,-0.25);
+    \node[align=center] at (1.75,0.25) {$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\vec{i}'_{k,1}))$,\\$\mathcal{E}_{pk_0,sk_1}(\mathsf{E}_1(\mat{I}'_{k,1}))$};
+    \fill [lightgray]  (3.375,0.75) rectangle (6.125,-0.25);
+    \node[align=center] at (4.75,0.25) {$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\vec{i}'_{k,n}))$,\\$\mathcal{E}_{pk_0,sk_n}(\mathsf{E}_1(\mat{I}'_{k,n}))$};
 
     % Update
-    \draw [gray] (0,-8.5) rectangle (6.5,-4.5);
-    \node at (3.25,-5) {\small 3. Update};
+    \draw [gray] (0,-5.75) rectangle (6.5,-2.5);
+    \node at (3.25,-3) {\small 3. Update};
 
     % Navigator
-    \fill  [green!80!black!60] (1.5,-5.5) rectangle (5,-7.5);
-    \pic[xscale=0.22,yscale=0.3] at (3.25,-5.8275) {plane};
-    \node at (3.25,-6.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
-    \node at (3.25,-7.125) {$\hat{\vec{x}}_{k|k}$, $\mat{P}_{k|k}$};
+    \fill  [green!80!black!60] (1.5,-3.5) rectangle (5,-5.5);
+    \pic[xscale=0.22,yscale=0.3] at (3.25,-3.8275) {plane};
+    \node at (3.25,-4.625) {$\sum_{i=1}^n \vec{i}'_{k,i}$, $\sum_{i=1}^n\mat{I}'_{k,i}$};
+    \node at (3.25,-5.125) {$\hat{\vec{x}}_{k|k}$, $\mat{P}_{k|k}$};
 \end{tikzpicture}
@@
     \includegraphics{images/layouts.pdf}
-    \caption{Diffrent simulation layouts with varying average distances between navigator and sensors.}
+    \caption{Different simulation layouts with varying distances between navigator and sensors.}
     \label{fig:sim_layouts}
@@
     \includegraphics{images/layout_errors.pdf}
-    \caption{MSE of the privacy-preserving EIF and standard EIF for different layout simulations.}
+    \caption{Average RMSE of our privacy-preserving filter and the standard EIF for different layouts.}
     \label{fig:sim_layout_errors}

### 2021-06-11 authors_responses/first_tac_rejection/authors_response_final.tex
Added copy of different paper author's response to use as base for creating the author's response for this one

\documentclass[a4paper]{scrartcl}

%\usepackage{showframe}
\usepackage[margin=2cm,footskip=.7cm]{geometry}
\usepackage{enumitem}
% \usepackage{fourier}
\usepackage{xcolor}
% \usepackage{abkuerzungen}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{../../ISASmacros/isasmathmacros}

\usepackage{pdfpages}

\newcommand{\sA}{\ensuremath{\mathsf{A}}}
\newcommand{\sAB}{\ensuremath{\mathsf{AB}}}
\newcommand{\sB}{\ensuremath{\mathsf{B}}}
\newcommand{\sBA}{\ensuremath{\mathsf{BA}}}
\newcommand{\sC}{\ensuremath{\mathsf{C}}}

\newcommand{\cest}{\ensuremath{\cvec{\gamma}}}
\newcommand{\cerest}{\ensuremath{\ervec{\gamma}}}
\newcommand{\cmat}{\ensuremath{\mat{\Gamma}}}
\newcommand{\tmat}{\ensuremath{\widetilde{\mat{\Gamma}}}}

\newcommand{\gainA}{\ensuremath{\mat{K}}}
\newcommand{\gainB}{\ensuremath{\mat{L}}}

% \newcommand{\fus}{\ensuremath{\op{fus}}}

% \newcommand{\CI}{\op{CI}\xspace}
% \newcommand{\EI}{\op{EI}\xspace}
% \newcommand{\ICI}{\op{ICI}\xspace}
% \newcommand{\BC}{\op{B\!/\!C}\xspace}
% \newcommand{\ind}{\op{s}\xspace}
\newcommand{\ind}{\op{in}\xspace}
\newcommand{\opt}{\cmat}

\newcommand{\excmat}{\ensuremath{\mat{\Gamma}'}}
\newcommand{\excest}{\ensuremath{\cest'}}
% \newcommand{\exoptmat}{\ensuremath{\mat{C}_{\excmat}}}
\newcommand{\exoptmat}{\ensuremath{\mat{C}'_\EI}}

%\RequirePackage[mathscr]{euscript}
%\RequirePackage{bbding}
%\RequirePackage{scalefnt}
%\RequirePackage{mathtools}
% This was enabled but makes the text look ugly
%\RequirePackage[T1]{fontenc}

%%% COLOR DEFINITIONS

% KIT Colors
\definecolor{kitgreenex}{RGB}{0,152,131}
\definecolor{kitblueex}{RGB}{52,115,186}
\definecolor{kitmaygreen}{RGB}{119,184,38}
\definecolor{kityellow}{RGB}{255,228,0}
\definecolor{kitorange}{RGB}{247,154,0}
\definecolor{kitbrown}{RGB}{182,130,28}
\definecolor{kitred}{RGB}{187,25,23}
\definecolor{kitpurple}{RGB}{190,0,126}
\definecolor{kitcyanblue}{RGB}{0,167,227}
% Own Definitions
\definecolor{grey}{RGB}{150,150,150}

\definecolor{nblue}{RGB}{54,95,145}

%%% FONTS
%\setkomafont{pageheadfoot}{\small\color{darkgray}}
%\setkomafont{pagefoot}{\normalfont\color{darkgray}}
%\setkomafont{pagenumber}{\color{darkgray}}
%\setkomafont{captionlabel}{\small\bfseries\color{darkgray}}
\setkomafont{disposition}{\bfseries}
\setkomafont{section}{\normalfont\large\bfseries}
\setkomafont{subsection}{\normalfont\bfseries}
\setkomafont{author}{\normalfont}
\setkomafont{date}{\normalfont}

%%% PARAGRAPH LAYOUT
\setlength{\parindent}{0mm}
\setlength{\parskip}{6pt}

%%% REBUTTAL COMMANDS
\newenvironment{rebuttal}{\begin{enumerate}[label={\color{grey}\thesection.\arabic{enumi}},leftmargin=0pt,ref=\thesection.\arabic{enumi}]}{\end{enumerate}}
\newcommand{\reviewtext}[1]{{\color{nblue} #1}}
\newcommand{\papertext}[1]{\emph{``#1''}}

%%% HYPERREF SETUP
\hypersetup{
        colorlinks = true,
        linkcolor = kitgreenex
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\boldmath Cryptographically Privileged State Estimation With Gaussian Keystreams}
\subtitle{Response to Reviewers' Comments - Submission L-CSS 21-0154}
\author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}

%       .d8888b.  888                     888
%      d88P  Y88b 888                     888
%      Y88b.      888                     888
%       "Y888b.   888888  8888b.  888d888 888888
%          "Y88b. 888        "88b 888P"   888
%            "888 888    .d888888 888     888
%      Y88b  d88P Y88b.  888  888 888     Y88b.
%       "Y8888P"   "Y888 "Y888888 888      "Y888

\begin{document}

\maketitle

Dear Dr. Ji-Feng Zhang,\\
Dear Reviewers,

We would like to thank you all for your responses and agreement on accepting our manuscript. As specified in the Author's Checklist, we list the changes made to the accepted manuscript here. The changes consist of switching to the final version template and minor wording and spelling changes. Throughout this response, reviewers' comments are in \reviewtext{blue}.

Sincerely,\\
Marko Ristic, Benjamin Noack, and Uwe D. Hanebeck

%      8888888888     888 d8b 888
%      888            888 Y8P 888
%      888            888     888
%      8888888    .d88888 888 888888 .d88b.  888d888
%      888       d88" 888 888 888   d88""88b 888P"
%      888       888  888 888 888   888  888 888
%      888       Y88b 888 888 Y88b. Y88..88P 888
%      8888888888 "Y88888 888  "Y888 "Y88P"  888

\section*{Response to the Editor's Report}
\def\thesection{E}
\begin{rebuttal} %\setcounter{enumi}{-1}
\item \reviewtext{All the Reviewers are fine with the revised version. Accordingly, I am glad to recommend the paper publication.

One reviewer pointed out a possible small typo in a reference. I have checked that: the reference given by the authors is correct. I guess the reviewer found the draft of the book in http://staff.ustc.edu.cn/\\\~{}mfy/moderncrypto/reading\%20materials/Introduction\_to\_Modern\_Cryptography.pdf which does not correspond exactly with the published version.}

We are happy to hear of your decision, thank you. Regarding the reference, we have left it as it was submitted in the accepted version.

\end{rebuttal}

%      8888888b.                         d888
%      888   Y88b                       d8888
%      888    888                         888
%      888   d88P .d88b.  888  888        888
%      8888888P" d8P  Y8b 888  888        888
%      888 T88b  88888888 Y88  88P        888
%      888  T88b Y8b.      Y8bd8P         888
%      888   T88b "Y8888    Y88P        8888888

\section*{Response to the Comments of Reviewer 1 (46379)}
\def\thesection{R1}
\begin{rebuttal}
\item \reviewtext{The authors have answered all my earlier concerns.}

We are glad to hear this, thank you.

\end{rebuttal}

%      8888888b.                         .d8888b.
%      888   Y88b                       d88P  Y88b
%      888    888                              888
%      888   d88P .d88b.  888  888           .d88P
%      8888888P" d8P  Y8b 888  888       .od888P"
%      888 T88b  88888888 Y88  88P      d88P"
%      888  T88b Y8b.      Y8bd8P       888"
%      888   T88b "Y8888    Y88P        888888888

\section*{Response to the Comments of Reviewer 2 (46381)}
\def\thesection{R2}
\begin{rebuttal}
\item \reviewtext{The authors have addressed my comments}

We are happy we could address them all, thank you.

\end{rebuttal}

%      8888888b.                         .d8888b.
%      888   Y88b                       d88P  Y88b
%      888    888                            .d88P
%      888   d88P .d88b.  888  888          8888"
%      8888888P" d8P  Y8b 888  888           "Y8b.
%      888 T88b  88888888 Y88  88P      888    888
%      888  T88b Y8b.      Y8bd8P       Y88b  d88P
%      888   T88b "Y8888    Y88P         "Y8888P"

\section*{Response to the Comments of Reviewer 3 (44309)}
\def\thesection{R3}
\begin{rebuttal}
\item \reviewtext{The reviewer only have the following one more suggestion.

1.Could the author explain more about the negligible function \textbackslash eta in Definition 2.3. and make a definition of this function in this paper? The reviewer cannot find the definition 3.4. in ref [8] which may be a different version.}

We're sorry to hear that the reference was not easier to find. The editor has indicated that the reference was correct and differs from the book draft that can be found online, so we have left it unchanged. We're glad we could address your remaining suggestions.

\end{rebuttal}

%\includepdf[pages=-]{diff}

\end{document}

### 2021-06-14 main.tex
Updated Benjamin's picture and biography and changed one sentence in mine

@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
-received his diploma in software engineering in 2018 at the University of Melbourne, Australia.
+received his software engineering diploma in 2018 at the University of Melbourne, Australia.
 Since 2019, he has been pursuing a Ph.D.
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
-received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009.
-Afterwards, he obtained his Ph.D.
+is a professor of Computer Science at the Otto von Guericke University Magdeburg in Germany and head of the Autonomous Multisensor Systems (AMS) group.
+He received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009.
+Afterward, he obtained his Ph.D.
 in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
-Since 2013 he is a senior researcher at the Karlsruhe Institute of Technology (KIT), Germany.
 His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Author's response skeleton tex added, all editor and reviewer comments added just need to write their responses renamed the response file from final (name was copied when file was copied)

--- 2021-06-11 authors_responses/first_tac_rejection/authors_response_final.tex
@@
 
-\title{\boldmath Cryptographically Privileged State Estimation With Gaussian Keystreams}
-\subtitle{Response to Reviewers' Comments - Submission L-CSS 21-0154}
+\title{\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
+\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
 \author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}
@@
 
-Dear Dr. Ji-Feng Zhang,\\
+Dear Dr. Zhiwei Gao,\\
 Dear Reviewers,
 
-We would like to thank you all for your responses and agreement on accepting our manuscript.
-As specified in the Author's Checklist, we list the changes made to the accepted manuscript here.
-The changes consist of switching to the final version template and minor wording and spelling changes.
+We would like to thank you all for your thorough and helpful reviews.
+In this letter, we will describe how editor and reviewer comments, questions and suggestions have been addressed.
 Throughout this response, reviewers' comments are in \reviewtext{blue}.
@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{All the Reviewers are fine with the revised version. Accordingly, I am glad to recommend the paper publication.
+\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.}
 
-One reviewer pointed out a possible small typo in a reference.
-I have checked that: the reference given by the authors is correct.
-I guess the reviewer found the draft of the book in http://staff.ustc.edu.cn/\\\~{}mfy/moderncrypto/reading\%20materials/Introduction\_to\_Modern\_Cryptography.pdf which does not correspond exactly with the published version.}
+Our response.
 
-We are happy to hear of your decision, thank you. Regarding the reference, we have left it as it was submitted in the accepted version.
+\item \reviewtext{The reviewers feel the paper interesting, which many include publishable materials.
+On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g.
+introduction etc.), and highlight the novelty and contribution.
+Also the relevance of the paper to the journal should be clarified.}
+
+Our response.
+
+\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.
+If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
+more than 8 double-column pages using IEEE template.}
+
+Our response.
+
+\item \reviewtext{In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.
+
+Please login, click on the "Author" link at the bottom of your access page, and upload your technical note under the SAME reference number.
+A new reference number will be assigned to your revised paper.}
+
+Our response.
 
@@
 
-\section*{Response to the Comments of Reviewer 1 (46379)}
+\section*{Response to the Comments of Reviewer 1 (222511)}
 \def\thesection{R1}
 \begin{rebuttal}
-\item \reviewtext{The authors have answered all my earlier concerns.}
+\item \reviewtext{This paper concerns the localization problem under privacy constraints.
+Cryptographic schemes have been devised by the authors to achieve some privacy requirements.
+The contribution is significant enough and the paper is well written but hard to understand for a usual reader of IEEE TAC due to sections with cryptographic background.}
 
-We are glad to hear this, thank you.
+Our response.
+
+\item \reviewtext{As a TAC paper, performance analysis in terms of estimation accuracy was expected but is actually missing.}
+
+Our response.
+
+\item \reviewtext{This reviewer wonders if IEEE TAC is well adapted for an efficient exposition of the authors' findings.}
+
+Our response.
+
+\item \reviewtext{In the framework of a Control theory paper, cryptographic notions would be kept as minimum as possible in the main body of the paper or moved to Appendices.}
+
+Our response.
 
@@
 
-\section*{Response to the Comments of Reviewer 2 (46381)}
+\section*{Response to the Comments of Reviewer 2 (222527)}
 \def\thesection{R2}
 \begin{rebuttal}
-\item \reviewtext{The authors have addressed my comments}
+\item \reviewtext{This paper deals with a suitable notion of linear-combination aggregation encryption and provides a cryptographically secure instance applied to a filter with range-sensor measurements.
+This approach keeps navigator location, sensor's location and sensors' measurements private during navigation.
 
-We are happy we could address them all, thank you.
+The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.}
+
+Our response.
+
+\item \reviewtext{The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}
+
+Our response.
+
+\item \reviewtext{Some additional comments are given below:
+
+-Introduction (2 pages) is too long and does not focus on the main ideas of the paper. There are too many reminders of classical notions.}
+
+Our response.
+
+\item \reviewtext{-Equation (3): i from 1 to n must be added.}
+
+Our response.
+
+\item \reviewtext{-The actual computation steps are in fact scattered all over the paper, in several sections.
+In the current version, the reader has to collect all the scattered pieces to come out with the approach.
+I would therefore, strongly recommend the authors to summarize all the steps of the approach gathered by the end of the paper, to help the reader directly use and implement the algorithm.}
+
+Our response.
+
+\item \reviewtext{-Page 10, Equation (36), Right part of Equation: d is from 0 to D}
+
+Our response.
+
+\item \reviewtext{-Inequality (50) must be clarified,}
+
+Our response.
+
+\item \reviewtext{-Algorithm 1, steps 2/3/4, it is F\_\{k-1\},}
+
+Our response.
+
+\item \reviewtext{-Section VIII-some explanations on the process model must be added. Figure 6 is too small; it is difficult to distinguish the different lines.}
+
+Our response.
 
@@
 
-\section*{Response to the Comments of Reviewer 3 (44309)}
+\section*{Response to the Comments of Reviewer 3 (229727)}
 \def\thesection{R3}
 \begin{rebuttal}
-\item \reviewtext{The reviewer only have the following one more suggestion.
+\item \reviewtext{This paper presented a theoretical framework for privacy-preserving localisation combining the encryption scheme and filtering.
+In particular, the private linear-combination aggregation has been adopted in the presented framework.
+Basically, the contribution of the paper is clearly indicated with an interesting and important topic.
+However, some technical problems need to be further clarified.
+Therefore, a major revision is necessary in my opinion.}
 
-1.Could the author explain more about the negligible function \textbackslash eta in Definition 2.3.
-and make a definition of this function in this paper?
-The reviewer cannot find the definition 3.4.
-in ref [8] which may be a different version.}
+Our response.
 
-We're sorry to hear that the reference was not easier to find.
-The editor has indicated that the reference was correct and differs from the book draft that can be found online, so we have left it unchanged.
-We're glad we could address your remaining suggestions.
+\item \reviewtext{1) Is any filtering method can be integrated into the presented framework? If so, can we replace the method via numerical approach such as particle filter.}
+
+Our response.
+
+\item \reviewtext{2) How does the linear combination reflect the dynamics of the investigated system in Eq.(2)?}
+
+Our response.
+
+\item \reviewtext{3) Why is the noise of the system Gaussian? In Eq.(2), function f() is known then what is the physical meaning of the Gaussian process noise?}
+
+Our response.
+
+\item \reviewtext{4) In the paper, the noise is depended on covariance matrix \$Q\$ which is also particularly used in Algroithm 1, however, in practice, Q is unmeasurable and unknown.
+How to estimate the value of Q in terms of performance guarantee.}
+
+Our response.
+
+\item \reviewtext{5) The experimental results are limited.
+The comparison is essential to validate the performance of the presented algorithm.
+What about using the existing filtering method to demonstrate the various encryption scheme?}
+
+Our response.
+
+\item \reviewtext{6) There are some typos in the manuscript please correct them, for example, page 1 Notation, '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ the vector norm' should be '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ is the vector norm' etc.}
+
+Our response.
 
@@
 
-%\includepdf[pages=-]{diff}
+% \includepdf[pages=-]{diff}
 

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Draft of response to the editor

@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.}
+\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.
 
-Our response.
-
-\item \reviewtext{The reviewers feel the paper interesting, which many include publishable materials.
+The reviewers feel the paper interesting, which many include publishable materials.
 On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g.
@@
 
-Our response.
+Thank you for the response.
+We have undertaken a large overhaul of the manuscript in order to accomodate for the suggested changes of the reviewers.
+The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it.
+We state the estimation problem tackled, namely, range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
+We believe that the more clarified novelty and contribution also better justifies the relevance of the paper to the TAC journal.
 
@@
 If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
-more than 8 double-column pages using IEEE template.}
+more than 8 double-column pages using IEEE template.
 
-Our response.
-
-\item \reviewtext{In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.
+In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.
 
@@
 
-Our response.
+After a large revision of our manuscript, including the suggested additions and modifications from the reviewers, we have rearranged and greatly shortened the work (in particular the introduction and cryptography sections, but all sections have been partially modified to be clearer).
+Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again.
+We hope that this decision is made clearer from the newly revised and rearranged manuscript.
+Below, we have detailed how each of the reviewer comments have been taken into account when revising the work.
 

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Draft of response to reviewer 1

@@
 The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it.
-We state the estimation problem tackled, namely, range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
-We believe that the more clarified novelty and contribution also better justifies the relevance of the paper to the TAC journal.
+We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
+We believe that the more clarified contribution and novelty also better justifies the relevance of the paper to the TAC journal.
 
@@
 
-Our response.
+We thank the reviwer for their comment on our contribution and are sorry that the work was not made easier to understand.
+We have rearranged the paper to make both the problem tackled and the solution presented easier to follow and more concise.
+Additionally we have greatly reduced the amount of cryptographic background presented, and hope that these changes make the work much easier to follow for the usual target audience of IEEE TAC.
 
@@
 
-Our response.
+We regret that the method of analysis for our approach was not made clearer.
+As the proposed method we present is ineherently a modified EKF, we directly compare the estimation accuracy of our method to the industry standrd EKF (EIF reformulation in our case).
+To make this clearer, we have rewritten the results section to portray this evaluation better, and changed the results figure to be far more legible.
+Direct comparisons beween the EIF and our method are now made for each simluation considered, and the estimation error (accuracy of the filters) can be seen much more clearly.
+We hope this makes the evaulation of the presented method easier to understand.
 
@@
 
-Our response.
+We agree that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
+For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal.
+We will additionally consider some of the heavier cryptographic computations presented for an alternative submission elsewhere.
 
@@
 
-Our response.
+As above, we regret that the quantity of presented cryptographic content was so poorly suited to the context of TAC and have greatly modified the work to make it a better fit.
+Much of the cryptographic discussion has been removed and the remaining, necessary but dense, novel notions have been put in the appendix.
+We hope this makes the work better suited in the context of TAC.
 

### 2021-06-14 authors_responses/first_tac_rejection/authors_response.tex
Half way through response to reviewer 2

@@
 
-The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.}
+The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.
 
-Our response.
+The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}
 
-\item \reviewtext{The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}
-
-Our response.
+We're happy to hear that the results were found interesing and regret that the length and organisation has made the manuscript hard to read.
+We have heavily reorganised and rewritten parts of the work to make it easier to follow, including shortening the work by four pages.
+We hope that the flow of information is now easier to follow and that the method is more concisely described.
 
@@
 
-Our response.
+We're sorry this was the case and agree with the reviewer that the introduction was too long.
+We have greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
+Our hope is that the new layout is easier to read and better suited to the target audience of the TAC journal.
 
@@
 
-Our response.
+Thank you for pointing this out, this has now been added to the manuscript.
 
@@
 
-Our response.
+Due to the number of components in the proposed method (encoding, encryption and estimation) our aim was to present the algorithm pseudocode as the summary of the method, but regret that this was not made clearer.
+We have rewritten and reorganised the localisation section and have tried to make a pseudocode summary, and its purpose, clearer.
+We hope that the updated manuscript better captures the overall summary of all presented components at the end of introduced components.
 

### 2021-06-15 authors_responses/first_tac_rejection/authors_response.tex
Draft of response to reviewer 2

@@
 
-Due to the number of components in the proposed method (encoding, encryption and estimation) our aim was to present the algorithm pseudocode as the summary of the method, but regret that this was not made clearer.
+Due to the number of components in the proposed method (encoding, encryption and estimation), our aim was to present the algorithm pseudocode as the summary of the method, and regret that this was not made clearer.
 We have rewritten and reorganised the localisation section and have tried to make a pseudocode summary, and its purpose, clearer.
-We hope that the updated manuscript better captures the overall summary of all presented components at the end of introduced components.
+We hope that the updated manuscript now presents a better overall summary after all the componenets are presented.
 
@@
 
-Our response.
+This was indeed missing. After shortening the paper, this subsection was removed and the equation is no longer there, but we thank you for pointing it out regardless.
 
@@
 
-Our response.
+We apologies for not making this clearer. The section has been modified and the reason for adding standard deviations to give a conservative estimate has been rewritten and clarified.
 
@@
 
-Our response.
+Thank you for pointing this out.
+This was due to an error in notation in a previous section which gave incorrect timestep subscripts in the EKF prediction equations.
+This has now been fixed and results in $\mat{F}_k$ being the correct notation in the pseudocode section.
 
@@
 
-Our response.
+Process model informaiton was indeed missing and the figure hard to read.
+The section has been modified to include details of the models used in the simulation and the figure modified to display comparisons between the privacy-preserving filter and the EIF seperately for each considered sensor layout.
+We hope that the comparison and the drawn conclusions are now much easier to follow.
 

### 2021-06-15 authors_responses/first_tac_rejection/authors_response.tex
Fixed a bunch of typos found by grammarly Added some of reviewer 3 response, but need confirmation on how to answer his questions about the system model

@@
 Thank you for the response.
-We have undertaken a large overhaul of the manuscript in order to accomodate for the suggested changes of the reviewers.
+We have undertaken a large overhaul of the manuscript in order to accommodate the suggested changes of the reviewers.
 The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it.
 We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
-We believe that the more clarified contribution and novelty also better justifies the relevance of the paper to the TAC journal.
+We believe that the more clarified contribution and novelty also better justify the relevance of the paper to the TAC journal.
 
@@
 
-We thank the reviwer for their comment on our contribution and are sorry that the work was not made easier to understand.
+We thank the reviewer for their comment on our contribution and are sorry that the work was not made easier to understand.
 We have rearranged the paper to make both the problem tackled and the solution presented easier to follow and more concise.
-Additionally we have greatly reduced the amount of cryptographic background presented, and hope that these changes make the work much easier to follow for the usual target audience of IEEE TAC.
+Additionally, we have greatly reduced the amount of cryptographic background presented, and hope that these changes make the work much easier to follow for the usual target audience of IEEE TAC.
 
@@
 We regret that the method of analysis for our approach was not made clearer.
-As the proposed method we present is ineherently a modified EKF, we directly compare the estimation accuracy of our method to the industry standrd EKF (EIF reformulation in our case).
-To make this clearer, we have rewritten the results section to portray this evaluation better, and changed the results figure to be far more legible.
-Direct comparisons beween the EIF and our method are now made for each simluation considered, and the estimation error (accuracy of the filters) can be seen much more clearly.
-We hope this makes the evaulation of the presented method easier to understand.
+As the proposed method we present is inherently a modified EKF, we directly compare the estimation accuracy of our method to the industry standard EKF (EIF reformulation in our case).
+To make this clearer, we have rewritten the results section to portray this evaluation better and changed the results figure to be far more legible.
+Direct comparisons between the EIF and our method are now made for each simulation considered, and the estimation error (accuracy of the filters) can be seen much more clearly.
+We hope this makes the evaluation of the presented method easier to understand.
 
@@
 
-We're happy to hear that the results were found interesing and regret that the length and organisation has made the manuscript hard to read.
+We're happy to hear that the results were found interesting and regret that the length and organisation have made the manuscript hard to read.
 We have heavily reorganised and rewritten parts of the work to make it easier to follow, including shortening the work by four pages.
@@
 
-We're sorry this was the case and agree with the reviewer that the introduction was too long.
-We have greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
-Our hope is that the new layout is easier to read and better suited to the target audience of the TAC journal.
+We're sorry that the introduction was found too long and agree that it could be made shorter.
+We have now greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
+We hope that the new layout is easier to read and better suited to the target audience of the TAC journal.
 
@@
 
-Due to the number of components in the proposed method (encoding, encryption and estimation), our aim was to present the algorithm pseudocode as the summary of the method, and regret that this was not made clearer.
+Due to the number of components in the proposed method (encoding, encryption and estimation), we aimed to present the algorithm pseudocode as the summary of the method, and regret that this was not made clearer.
 We have rewritten and reorganised the localisation section and have tried to make a pseudocode summary, and its purpose, clearer.
-We hope that the updated manuscript now presents a better overall summary after all the componenets are presented.
+We hope that the updated manuscript now presents a better overall summary after all the components are presented.
 
@@
 
-Process model informaiton was indeed missing and the figure hard to read.
-The section has been modified to include details of the models used in the simulation and the figure modified to display comparisons between the privacy-preserving filter and the EIF seperately for each considered sensor layout.
+Process model information was indeed missing and the figure hard to read.
+The section has been modified to include details of the models used in the simulation and the figure modified to display comparisons between the privacy-preserving filter and the EIF separately for each considered sensor layout.
 We hope that the comparison and the drawn conclusions are now much easier to follow.
@@
 
-Our response.
+We're glad to hear that the contribution was found interesting and important.
+We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the information easier to follow and better suited to the audience of the TAC journal.
 
@@
 
-Our response.
+% The method proposed achieves the desired security propoerties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step.
+With this method, using the EIF is cruicial for reducing the communication of distributed participants to that which can use the introduced encryption scheme, and thus meet the security properties.
+
+% While a particle filter that can reduce its communication to suit another type of encryption scheme may exist, it is beyond the scope of this work and would likely differ both in its required encryption scheme and in any filter or model modifications.
 
@@
 
-Our response.
+% TODO complete
+%The linear combination aggregation scheme is only used to encrypt communication required during computation of the EIF update step.
+Ideally, the encryption has no effect on the proposed filter, but in practice, minor descrepancies are introduced with the quantisation of floating-piont numbers used for encryption and homomorphic summation.
+The proposed filter itself requires a modified measurement function to be able to use this scheme, which is where differences in performance with a standard EIF are introduced.
+The system model given in ($2$) is, however, unaffected in our method, in that both it and the standard EIF assume the measured state to follow these dynamics exactly.
 
@@
 
-Our response.
+% TODO complete
+%Thank you for pointing this out.
+You are right to say that the Gaussianity of additive system noise is not required by either the standard EIF or our approach and has now been removed from the manuscript.
 
@@
 
-Our response.
+% TODO complete
+%As we consider a linearising state estimation filter (the EKF), system noise covariance $\mat{Q}$ is 
+%Estimating the system noise covariance $\mat{Q}$ is common practice when using linearising state estimation filters such as the EKF, and a requirement for predicting a
 
@@
 
-Our response.
+We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer.
+To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer how the proposed filter performs.
+The computational performance is more difficult to compare.
+No alternative encryption scheme suitable for our filter (i.e.
+scheme meeting LCAO) exists, beyond the one introduced in the work.
+
+%A possible comparison, as remarked earlier in the paper, is using a scheme meeting AO combined with a unidirectional communication protocol, but we consider this beyond the scope of the work due to no existing
 
@@
 
-Our response.
+We apologies for the mistake and have now corrected it, along with others throughout the work.
 

### 2021-06-16 authors_responses/first_tac_rejection/authors_response.tex
Draft of last reviewer added and reference for TAC paper about crypto added

@@
 
-We agree that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
+We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
+Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as reference during our revision.
 For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal.
@@
 We have now greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
-We hope that the new layout is easier to read and better suited to the target audience of the TAC journal.
+We hope that the new layout is easier to read and follow.
 
@@
 We're glad to hear that the contribution was found interesting and important.
-We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the information easier to follow and better suited to the audience of the TAC journal.
+We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the information easier to follow.
 
@@
 
-% The method proposed achieves the desired security propoerties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step.
-With this method, using the EIF is cruicial for reducing the communication of distributed participants to that which can use the introduced encryption scheme, and thus meet the security properties.
+The method proposed achieves the desired security properties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step.
+With this method, using the EIF is crucial for reducing participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties.
+It may be possible to rearrange a particle filter to suit some other type of encryption scheme, but to the best of our knowledge, this does not yet exist.
 
-% While a particle filter that can reduce its communication to suit another type of encryption scheme may exist, it is beyond the scope of this work and would likely differ both in its required encryption scheme and in any filter or model modifications.
+During only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter, but we have decided to use the prediction equations of the EKF for simplicity and consistency with the presented update step.
 
@@
 
-% TODO complete
-%The linear combination aggregation scheme is only used to encrypt communication required during computation of the EIF update step.
-Ideally, the encryption has no effect on the proposed filter, but in practice, minor descrepancies are introduced with the quantisation of floating-piont numbers used for encryption and homomorphic summation.
-The proposed filter itself requires a modified measurement function to be able to use this scheme, which is where differences in performance with a standard EIF are introduced.
-The system model given in ($2$) is, however, unaffected in our method, in that both it and the standard EIF assume the measured state to follow these dynamics exactly.
+The linear combination aggregation scheme is only used to encrypt the required communication during the computation of the EIF update step.
+Ideally, the encryption does not affect the proposed filter in any way, but in practice, minor discrepancies are introduced with the quantisation of floating-point numbers.
+The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF are introduced.
+The system model given in ($2$) is unaffected by both encryption and measurement model modification, in that both the proposed filter and the standard EIF assume the state follows these dynamics exactly.
 
@@
 
-% TODO complete
-%Thank you for pointing this out.
-You are right to say that the Gaussianity of additive system noise is not required by either the standard EIF or our approach and has now been removed from the manuscript.
+Thank you for pointing this out. It is correct that the Gaussianity of additive system noise is not required by either the standard EIF or our approach and has now been removed from the manuscript.
 
@@
 
-% TODO complete
-%As we consider a linearising state estimation filter (the EKF), system noise covariance $\mat{Q}$ is 
-%Estimating the system noise covariance $\mat{Q}$ is common practice when using linearising state estimation filters such as the EKF, and a requirement for predicting a
+Estimating the second moment of the system noise, $\mat{Q}$, is the standard procedure when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
+Huag), and is specific to the system being modelled.
+As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have stated above, we have presented the EKF equations for state prediction where computing it would be necassary.
 
@@
 We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer.
-To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer how the proposed filter performs.
+To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly.
 The computational performance is more difficult to compare.
-No alternative encryption scheme suitable for our filter (i.e.
-scheme meeting LCAO) exists, beyond the one introduced in the work.
-
-%A possible comparison, as remarked earlier in the paper, is using a scheme meeting AO combined with a unidirectional communication protocol, but we consider this beyond the scope of the work due to no existing
+Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript).
+Future work is being done on a similarly modified EIF which can used a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
 
@@
 
-We apologies for the mistake and have now corrected it, along with others throughout the work.
+The sentence has now been corrected, along with others throughout the work.
 

### 2021-06-17 main.tex
Updated my affiliation

@@
 \author{Marko~Ristic$^{1}$,
-        Benjamin~Noack$^{2}$,~\IEEEmembership{Member,~IEEE,}
-        and~Uwe~D.~Hanebeck$^{1}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
-\thanks{$^{1}$Marko Ristic and Uwe D.
-Hanebeck are with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: \{marko.ristic, uwe.hanebeck\}@kit.edu).}% <-this % stops a space
-\thanks{$^{2}$Benjamin Noack is with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: benjamin.noack@ovgu.de).}}% <-this % stops a space
+        Benjamin~Noack$^{1}$,~\IEEEmembership{Member,~IEEE,}
+        and~Uwe~D.~Hanebeck$^{2}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
+\thanks{$^{1}$Marko Ristic and Benjamin Noack are with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: \{marko.ristic, benjamin.noack\}@ovgu.de).}% <-this % stops a space
+\thanks{$^{2}$Uwe D.
+Hanebeck is with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: uwe.hanebeck@kit.edu).}}% <-this % stops a space
 

### 2021-06-17 authors_responses/first_tac_rejection/authors_response.tex
Went over and proof read all responses. Updated title to use the new title (and state the former title as well)

@@
 
-\title{\boldmath Privacy-Preserving Localization Using Private Linear-Combination Aggregation}
+\title{\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)}
 \subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
@@
 We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
-We believe that the more clarified contribution and novelty also better justify the relevance of the paper to the TAC journal.
+We believe that the clearer novelty and contribution also better clarify the relevance of the paper to the TAC journal.
 
@@
 If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
-more than 8 double-column pages using IEEE template.
-
-In your letter of transmittal, you should include a detailed "author's response" document describing the changes in the paper and you should refer to the present paper number.
-
-Please login, click on the "Author" link at the bottom of your access page, and upload your technical note under the SAME reference number.
-A new reference number will be assigned to your revised paper.}
+more than 8 double-column pages using IEEE template.}
 
@@
 Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again.
-We hope that this decision is made clearer from the newly revised and rearranged manuscript.
-Below, we have detailed how each of the reviewer comments have been taken into account when revising the work.
+We hope that this reasoning is made clearer in the newly revised and rearranged manuscript.
+Below, we have detailed how each of the reviewer comments has been taken into account when revising the work.
 
@@
 We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
-Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as reference during our revision.
+Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision.
 For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal.
-We will additionally consider some of the heavier cryptographic computations presented for an alternative submission elsewhere.
+We will also consider some of the denser cryptographic definitions presented for an alternative submission elsewhere.
 
@@
 
-As above, we regret that the quantity of presented cryptographic content was so poorly suited to the context of TAC and have greatly modified the work to make it a better fit.
-Much of the cryptographic discussion has been removed and the remaining, necessary but dense, novel notions have been put in the appendix.
-We hope this makes the work better suited in the context of TAC.
+As above, we regret that the quantity of presented cryptographic content was overwhelming and have greatly modified the work to make it more suitable for the journal.
+Much of the cryptographic discussion has been removed and the remaining necessary novel notions have been put in the appendix.
 
@@
 We're happy to hear that the results were found interesting and regret that the length and organisation have made the manuscript hard to read.
-We have heavily reorganised and rewritten parts of the work to make it easier to follow, including shortening the work by four pages.
+We have heavily reorganised and rewritten parts of the work to make it easier to read, including shortening the work by four pages.
 We hope that the flow of information is now easier to follow and that the method is more concisely described.
@@
 
-We're sorry that the introduction was found too long and agree that it could be made shorter.
-We have now greatly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
-We hope that the new layout is easier to read and follow.
+We agree with the reviewer that the introduction could be made shorter.
+We have now significantly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
 
@@
 We're glad to hear that the contribution was found interesting and important.
-We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the information easier to follow.
+We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the presented information easier to follow.
 
@@
 
-Estimating the second moment of the system noise, $\mat{Q}$, is the standard procedure when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
-Huag), and is specific to the system being modelled.
-As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have stated above, we have presented the EKF equations for state prediction where computing it would be necassary.
+Estimating the second moment of the system noise, $\mat{Q}$, is a standard requirement when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
+Huag).
+This can be done in various ways specific to the system being modelled and is beyond the scope of this work.
+As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have used the EKF equations for state prediction, computing it would be necessary.
 

### 2021-06-22 main.tex
Forgot to note that process noise is zero mean
Updated biography to suit new affiliation

@@
 \end{equation}
-with system noise covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
+with system noise that is zero mean and has covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
 \begin{equation}
@@
 received his software engineering diploma in 2018 at the University of Melbourne, Australia.
-Since 2019, he has been pursuing a Ph.D.
-at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
-His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed filtering.
+In 2019, he began work as a researcher at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany, and since 2021, he has been pursuing a Ph.D.
+at the Autonomous Multisensor Systems (AMS) group, Otto von Guericke University, Germany.
+His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed localisation.
 \end{IEEEbiography}

### 2021-06-24 authors_responses/first_tac_rejection/authors_response.tex
Lots of types fixed in main manuscript Removed the requirements of the system model - measurement vec/mat now have unknown dimension and have been written with 0...0 for the sections where this is the case - author's responses have been changed to reflect this Results sections updated to point out that the plotted track is only a sample track

@@
 We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
-Existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision.
+As cryptography is becoming more prevalent in the context of control and estimation literature, existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision.
 For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal.
@@
 Thank you for pointing this out.
-This was due to an error in notation in a previous section which gave incorrect timestep subscripts in the EKF prediction equations.
-This has now been fixed and results in $\mat{F}_k$ being the correct notation in the pseudocode section.
+This was due to an error in notation from a previous section which gave incorrect timestep subscripts to the EKF prediction equations.
+The revised manuscript no longer imposes using the EKF for the prediction step of the filter and these equations have been removed.
 
@@
 The method proposed achieves the desired security properties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step.
-With this method, using the EIF is crucial for reducing participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties.
+With this method, using the EIF is crucial for reformulating participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties.
 It may be possible to rearrange a particle filter to suit some other type of encryption scheme, but to the best of our knowledge, this does not yet exist.
 
-During only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter, but we have decided to use the prediction equations of the EKF for simplicity and consistency with the presented update step.
+However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter.
+We have now relaxed the requirements of the system model and no specify the prediction equations of EKF specifically.
 
@@
 
-The linear combination aggregation scheme is only used to encrypt the required communication during the computation of the EIF update step.
-Ideally, the encryption does not affect the proposed filter in any way, but in practice, minor discrepancies are introduced with the quantisation of floating-point numbers.
-The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF are introduced.
-The system model given in ($2$) is unaffected by both encryption and measurement model modification, in that both the proposed filter and the standard EIF assume the state follows these dynamics exactly.
+The linear combination aggregation scheme does not reflect or affect the dynamics of the system model given in ($2$).
+The scheme is only used to encrypt the required communication during the computation of the EIF update step.
+The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF update are introduced.
+As above, we have removed the restrictions on the system model and hope that this makes its role in the presented filter clearer.
 
@@
 
-Thank you for pointing this out. It is correct that the Gaussianity of additive system noise is not required by either the standard EIF or our approach and has now been removed from the manuscript.
+Thank you for pointing this out.
+It is correct that the Gaussianity of the system noise was not required by our approach, nor was it required for the locally computed prediction step of the filter.
+This assumption is among the restrictions on the system model which have now been removed from the manuscript.
 
@@
 
-Estimating the second moment of the system noise, $\mat{Q}$, is a standard requirement when using linearising filters such as the EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
-Huag).
+As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearlising filter for the prediction step of the algorithm.
+However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
+Huag) and has been computed when evaluating the proposed filter through simulation.
 This can be done in various ways specific to the system being modelled and is beyond the scope of this work.
-As it is possible to use a different, non-linearising, filter for the prediction step of the algorithm, it is possible to avoid having to compute $\mat{Q}$, but as we have used the EKF equations for state prediction, computing it would be necessary.
 
@@
 Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript).
-Future work is being done on a similarly modified EIF which can used a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
+Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
 

### 2021-06-24 main.tex
Lots of types fixed in main manuscript Removed the requirements of the system model - measurement vec/mat now have unknown dimension and have been written with 0...0 for the sections where this is the case - author's responses have been changed to reflect this Results sections updated to point out that the plotted track is only a sample track

@@
 We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
-The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing communication assumptions and leakages is given, crucial for cryptographic security.
+The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing different communication assumptions and leakages is given, crucial for cryptographic security.
 To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.
@@
 
-At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ to all sensors $1\leq i\leq n$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
+At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
 Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
@@
 \end{figure}
-In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, 1 \leq j \leq m$ to be sent from each sensor $i$.
+In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, j\in\{1,\dots,m\}$ to be sent from each sensor $i$.
 We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.
@@
 We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-These will be used by a trusted setup party, the navigator and sensors $i,\,1\leq i \leq n$.
+These will be used by a trusted setup party, the navigator and sensors $i\in\{1,\dots,n\}$.
 They are defined as follows.
 \begin{LaTeXdescription}
-    \item[$\mathsf{Setup}(\kappa)$] On input of security paramater $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,1\leq i \leq n$.
+    \item[$\mathsf{Setup}(\kappa)$] On input of security parameter $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,i\in\{1,\dots,n\}$.
     \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
@@
 The security notions we want the above algorithms to meet reflect the previously stated estimation privacy goals.
-The navigator should learn no information from individual sensors while sensors should learning no information from the navigator or any other sensors.
+The navigator should learn no information from individual sensors while sensors should learn no information from the navigator or any other sensors.
 In the context of the introduced communication protocol, this can be summarised as the following notions.
 \begin{LaTeXdescription}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,1\leq j \leq m$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
-    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,1\leq j\leq m$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
+    \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,j\in\{1,\dots,m\}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
 Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
@@
 \subsection{Estimation problem} \label{subsec:est_problem}
-The estimation problem we consider, for which we will reduce communication to the protocol above, is localisation with range-only sensors.
+The estimation problem we consider, for which we will reformulate communication to the protocol above, is localisation with range-only sensors.
 In this work, we will focus on the two-dimensional case for simplicity but will derive methods suitable for extension to a three-dimensional equivalent.
-The state that we wish to estimate captures the navigator position, and the change in position ($\Delta$), and is given by
+The state that we wish to estimate must capture the navigator position, $x$ and $y$, and may contain any other components relevant to the system.
+It is of the form
 \begin{equation}
@@
     \begin{bmatrix}
-        x & \Delta x & y & \Delta y
+        x & y & \cdots
     \end{bmatrix}^\top\,. \label{eqn:state_definition}
 \end{equation}
-The state evolves following a known system model, which at timestep $k$ is given by
-\begin{equation}
-    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1})+\vec{w}_k\,, \label{eqn:system_model}
-\end{equation}
-with system noise that is zero mean and has covariance $\mathsf{Cov}[\vec{w}_k]=\mat{Q}_k$. Measurements of the system follow a measurement model dependent on sensor $i$, $0\leq i \leq n$, given by 
+This state evolves following some known system model, which at timestep $k$ can be written as
+\begin{equation}
+    \vec{x}_k = \vec{f}_k(\vec{x}_{k-1}, \vec{w}_k)\,, \label{eqn:system_model}
+\end{equation}
+with noise term $\vec{w}_k$. Measurements of the system follow a measurement model dependent on sensor $i\in\{1,\dots,n\}$, given by 
 \begin{equation}
@@
 \begin{align}
-    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \\
+    \mathcal{D}(\mathcal{E}(a_1)\mathcal{E}(a_2) \hspace{-7pt} \pmod{N^2}) &= a_1+a_2 \hspace{-7pt} \pmod{N}\,, \label{eqn:paillier_hom_add}\\
     \mathcal{D}(\mathcal{E}(a_1)g^{a_2} \hspace{-7pt} \pmod{N^2}) &= a_1+a_2\hspace{-7pt}\pmod{N}\,, \label{eqn:paillier_hom_plain_add}\\
@@
 A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$.
-$n$ private keys are generated by choosing $sk_i,\,1\leq i\leq n$ uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
+$n$ private keys are generated by choosing $sk_i,\,i\in\{1,\dots,n\}$, uniformly from $\mathbb{Z}_{N^2}$ and distributing them to $n$ participants (whose values are to be aggregated), while the last key is set as
 \begin{equation}
@@
 
-When all encryptions $c^{(t)}_{i},\,1\leq i \leq n$ are sent to the aggregator, summation and decryption are computed by the functions
+When all encryptions $c^{(t)}_{i},\,i\in\{1,\dots,n\}$ are sent to the aggregator, summation and decryption of the aggregated sum are computed by the functions
 \begin{equation}
@@
         \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
-        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}g^{a_{i,t}} \pmod{N^2} \\
+        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a_{i,t}} \pmod{N^2} \\
         \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
@@
 
-The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$, for an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications, is given by
+The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
 \begin{equation}
@@
 \end{equation}
-noting that when $M=N$, the modulus corresponds with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_plain_add}, \eqref{eqn:paillier_hom_mult} and the Joye-Libert sum \eqref{eqn:agg_decryption}.
+noting that when $M=N$, the operations and modulus correspond with those in the Paillier homomorphic operations \eqref{eqn:paillier_hom_add}, \eqref{eqn:paillier_hom_plain_add} and \eqref{eqn:paillier_hom_mult}, and the Joye-Libert sum \eqref{eqn:agg_decryption}.
 
@@
 In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}.
-The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting LCAO.
+The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting the notion of LCAO defined in section \ref{subsec:crypto_problem}.
 Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution.
@@
 Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
-Sensor secret keys are generated by choosing $sk_i,\,1\leq i\leq n-1$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
+Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
 
@@
     \end{equation*}
-    for some values $\rho_i,\rho_j \in \mathbb{Z}_N\,,1\leq j \leq m$.
+    for some values $\rho_i,\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$.
 Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
@@
     \end{align*}
-    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,1\leq i \leq n$.
+    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$.
 \end{LaTeXdescription}
@@
 
-Lastly, we make the following remark about a possible implicit weight.
 \begin{remark}
-    The construction of the above scheme supports linearly combining the implicit weight $\omega^{(t)}_j = 1$, by replacing
-    \begin{equation}
-        \mathcal{E}_{pk_0}(1)^{a^{(t)}_{i,j}} = (N+1)^{1}\rho_j^N \pmod{N^2}
+    Given the construction of the scheme above, it can be seen that any weights $\omega^{(t)}_j$, whose values are known at each sensor, do not need to be broadcast by the navigator.
+In this case, sensors can replace
+    \begin{equation}
+        \mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} = (N+1)^{\omega^{(t)}_ja^{(t)}_{i,j}}\rho_j^N \pmod{N^2}
     \end{equation}
@@
     \begin{equation}
-        (N+1)^{a^{(t)}_{i,j}} \pmod{N^2}\,.
-    \end{equation}
-    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by a single weight when it is known that $\omega^{(t)}_j=1$.
+        (N+1)^{\omega^{(t)}_ja^{(t)}_{i,j}} \pmod{N^2}\,.
+    \end{equation}
+    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by the number of weights $\omega^{(t)}_j$ that do not hold any information private to the navigator and are known by the sensors in advance.
 \end{remark}
@@
 \section{Privacy-Preserving Localization} \label{sec:priv_localization}
-With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that reduces to the required protocol.
+With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that can be reformulated to the required protocol.
 To produce an estimate of the state $\vec{x}_k$, we make use of an algebraic reformulation of the Extended Kalman Filter (EKF), the Extended Information Filter (EIF) \cite{maybeckStochasticModelsEstimation1982}, which reduces the filter update step to a single summation.
@@
 \end{equation}
-respectively. In this form, the update equations for $n$ sensor measurements at time $k$, given process and measurement models \eqref{eqn:system_model} and \eqref{eqn:measurement_model}, are given by
+respectively. In this form, the update equations for $n$ sensor measurements at time $k$, with measurement models \eqref{eqn:measurement_model}, are given by
 \begin{equation}
@@
 \end{equation}
-for sensors $1 \leq i \leq n$. The filter's prediction step can be computed by converting information vector $\hat{\vec{y}}_{k|k}$ and matrix $\mat{Y}_{k|k}$ back to state estimate and covariance 
-\begin{equation}
-    \hat{\vec{x}}_{k|k} = \mat{Y}_{k|k}^{-1}\hat{\vec{y}}_{k|k} \quad\textrm{and}\quad \mat{P}_{k|k} = \mat{Y}_{k|k}^{-1}\,,
-\end{equation}
-before using the normal EKF prediction equations
-\begin{equation}
-    \hat{\vec{x}}_{k|k-1} \!=\! \vec{f}_k(\hat{\vec{x}}_{k-1|k-1}) \ \textrm{and}\ \mat{P}_{k|k-1} \!=\! \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k, \label{eqn:ekf_prediction}
-\end{equation}
-with Jacobian
-\begin{equation}
-    \mat{F}_{k} = \left.\frac{\partial \vec{f}_k}{\partial \vec{x}}\right|_{\hat{\vec{x}}_{k-1|k-1}}\,. \label{eqn:jacobian_f}
-\end{equation}
+for sensors $i\in\{1,\dots,n\}$.
+After then converting the updated information vector and matrix back to state estimate $\hat{\vec{x}}_{k|k}$ and estimate covariance $\mat{P}_{k|k}$, the filter's prediction step can be computed by the navigator locally, using any suitable filter for the known system model \eqref{eqn:system_model}.
 
@@
         \frac{\hat{x}_{k|k-1} - s_{x,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
-        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} 
+        \frac{\hat{y}_{k|k-1} - s_{y,i}}{\sqrt{(\hat{x}_{k|k-1} - s_{x,i})^2 + (\hat{y}_{k|k-1} - s_{y,i})^2}} \\
+        0 \\
+        \vdots \\
+        0
     \end{bmatrix}\,,
@@
         2\hat{x}_{k|k-1} - 2s_{x,i} \\
-        2\hat{y}_{k|k-1} - 2s_{y,i}
+        2\hat{y}_{k|k-1} - 2s_{y,i} \\
+        0 \\
+        \vdots \\
+        0
     \end{bmatrix}\,. \label{eqn:modified_jacobian}
@@
 with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean.
-We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
-\begin{equation}
-    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_{k,i}\, \label{eqn:modified_noise_mean}
-\end{equation}
-and mean-adjust modified measurements as
+We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as $\mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_{k,i}$ and mean-adjust modified measurements as
 \begin{equation}
@@
         \begin{bmatrix}
-            \alpha_1^{(i)} & 0 & \alpha_2^{(i)} & 0
+            \alpha_1^{(i)} & \alpha_2^{(i)} & 0 & \cdots & 0
         \end{bmatrix}^\top\,,
@@
         \begin{bmatrix}
-            \beta_1^{(i)} & 0 & \beta_2^{(i)} & 0 \\
-            0 & 0 & 0 & 0 \\
-            \beta_3^{(i)} & 0 & \beta_4^{(i)} & 0 \\
-            0 & 0 & 0 & 0
+            \beta_1^{(i)} & \beta_2^{(i)} & 0 & \cdots & 0 \\
+            \beta_3^{(i)} & \beta_4^{(i)} & 0 & \cdots & 0\\
+            0 & 0 & 0 & \cdots & 0 \\
+            \vdots & \vdots & \vdots & \ddots & \vdots \\
+            0 & 0 & 0 & \cdots & 0
         \end{bmatrix}\,,
@@
 \end{equation}
-respectively. Additionally, we note the possible extension to the three-dimensional case.
+respectively.
 \begin{remark}
@@
 \begin{LaTeXdescription}
-    \item[Setup] Run only once, the $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $1 \leq i \leq n$, are distributed accordingly.
-
-    \item[Prediction] At each timestep $k$, the navigator computes the typical EKF prediction equations \eqref{eqn:ekf_prediction} before encrypting weights \eqref{eqn:weights_to_broadcast} with algorithm $\mathsf{Enc}$ and broadcasting them to the sensors.
+    \item[Setup] Run only once, the $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
+
+    \item[Prediction] At each timestep $k$, the navigator computes the prediction of the current state and its covariance with a local filter before encrypting weights \eqref{eqn:weights_to_broadcast} with algorithm $\mathsf{Enc}$ and broadcasting them to the sensors.
 This is given by algorithm \ref{alg:nav_prediction}.
@@
 \begin{algorithmic}[1]
-    \Procedure{Prediction}{$\hat{\vec{x}}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $\vec{f}_k$, $\mat{Q}_k$, $N$}
-
-    \State Compute $\mat{F}_k$ by \eqref{eqn:jacobian_f}
-    \State $\hat{\vec{x}}_{k|k-1} \gets \vec{f}_k(\hat{\vec{x}}_{k-1|k-1})$
-    \State $\mat{P}_{k|k-1} \gets \mat{F}_k\mat{P}_{k-1|k-1}\mat{F}_k^\top + \mat{Q}_k$
+    \Procedure{Prediction}{$\hat{\vec{x}}_{k-1|k-1}$, $\mat{P}_{k-1|k-1}$, $N$}
+    \State Compute $\hat{\vec{x}}_{k|k-1}$ with a local filter
+    \State Compute $\mat{P}_{k|k-1}$ with a local filter
 
@@
     \For{$v \gets 1$ to $2$}
-        \State Receive $\bm{\alpha}_{v}^{(i)}$ from each sensor $1\leq i \leq n$
+        \State Receive $\bm{\alpha}_{v}^{(i)}$ from each sensor $i\in\{1,\dots,n\}$
     \EndFor
@@
     \For{$w \gets 1$ to $4$}
-        \State Receive $\bm{\beta}_{w}^{(i)}$ from each sensor $1\leq i \leq n$
+        \State Receive $\bm{\beta}_{w}^{(i)}$ from each sensor $i\in\{1,\dots,n\}$
     \EndFor
@@
 As well as having shown the theoretical backing for the security of our scheme, we have simulated the proposed localisation method to evaluate its performance.
-A two-dimensional, linear, constant velocity process model, with
-\begin{equation*}
-    \vec{f}_k(\vec{x}) =
+A two-dimensional, linear, constant velocity process model,
+\begin{equation*}
+    \vec{x}_{k} = 
     \begin{bmatrix}
@@
         0 & 0 & 0 & 1
-    \end{bmatrix} \cdot \vec{x}
-\end{equation*}
-and
-\begin{equation*}
-    \mat{Q}_k = \frac{1}{10^3} \cdot
+    \end{bmatrix} \cdot \vec{x}_{k-1} + \vec{w}_k\,,
+\end{equation*}
+where noise term $\vec{w}_k \sim \mathcal{N}(\vec{0}, \mat{Q})$ and
+\begin{equation*}
+    \mat{Q} = \frac{1}{10^3} \cdot
     \begin{bmatrix}
@@
 \end{equation*}
-for all $k>0$, was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}.
+was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}, using a linear Kalman filter for the navigator's local state prediction.
 Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator.
@@
 We have considered multiple sensor layouts, each with four sensors, to capture the dependence of estimated modified measurement variances $r'_{k,i}$ on the original measurements $z_{k,i}$.
-These layouts of varying sensor distances to the navigator track are shown in figure \ref{fig:sim_layouts}.
+These layouts of varying sensor distances are shown next to the simulation initial state and a sample track in figure \ref{fig:sim_layouts}.
 \begin{figure}[htbp]
@@
 The key size should be chosen such that sufficient security is achieved, and the current recommendation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
-This results in a complete filter update step roughly every $1.6s$, for our implementation of the filter.
+For our implementation of the filter, this results in a filter update computation duration of roughly $1.6s$.
 
@@
         \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
-        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
+        \item \textit{Weight Queries:} The attacker chooses an instance $t$ and receives the weights for that instance encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,j\in\{1,\dots,m\}$.
         \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$ and $(i',t',a^{\prime(t')}_{i',1},\dots,a^{\prime(t')}_{i',m})$, the following condition holds:
         \begin{equation*}
-            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,1\leq j\leq m\,.
+            i = i' \wedge t = t' \implies a^{(t)}_{i,j} = a^{\prime(t')}_{i',j},\,j\in\{1,\dots,m\}\,.
         \end{equation*}
@@
     \end{equation*}
-    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
+    for weights $\omega^{(t^*)}_j,\,j\in\{1,\dots,m\}$ returned by a \textit{Weight Query} with chosen instance $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
     \begin{equation*}
@@
     An encryption scheme meets LCAO security if no probabilistic adversary, running in polynomial-time with respect to security parameter $\kappa$, has more than a negligible advantage in winning the above security game.
-Probabilities are taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
+That is, for all adversaries $\mathcal{A}$, there exists a negligible function $\eta$, such that
+    \begin{equation*}
+        \mathsf{Adv}^{LCAO}(\mathcal{A}) \leq \eta(\kappa)\,,
+    \end{equation*}
+    with probabilities taken over randomness introduced by $\mathcal{A}$, and in $\mathsf{Setup}$, $\mathsf{Enc}$ and $\mathsf{CombEnc}$.
 \end{definition}
@@
 The scheme in section \ref{sec:lcao_scheme} will be shown to meet LCAO by contrapositive.
-We show that for an adversary $\mathcal{A}$ playing against a challenger using the scheme, we can always create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the Joye-Libert scheme, such that
+We show that for any adversary $\mathcal{A}$ playing against a challenger using the scheme, we can always create an adversary $\mathcal{A}'$ playing against a challenger $\mathcal{C}$ using the Joye-Libert scheme, such that
 \begin{equation*}
@@
 \end{equation*}
-for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
+for \textit{all} negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
 That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case, \cite{joyeScalableSchemePrivacyPreserving2013}).
@@
         \begin{LaTeXdescription}
-            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,1 \leq j \leq m$ and random values $\rho_j \in \mathbb{Z}_N,\,1 \leq j \leq m$, and return encryptions
-            \begin{equation*}
-                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,1\leq j\leq m
+            \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ and random values $\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$, and return encryptions
+            \begin{equation*}
+                (N+1)^{\omega^{(t)}_{j}}\rho_j^N\pmod{N^2},\,j\in\{1,\dots,m\}
             \end{equation*}
             to $\mathcal{A}$.
-            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,1 \leq j \leq m$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
+            \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,j\in\{1,\dots,m\}$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
 The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return
@@
         \end{equation*}
-        choose weights $\omega^{(t^*)}_j,1 \leq j \leq m$ for instance $t^*$ and submit AO challenge series
+        choose weights $\omega^{(t^*)}_j,j\in\{1,\dots,m\}$ for instance $t^*$ and submit AO challenge series
         \begin{equation*}
@@
         \end{equation*}
-        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,1 \leq i \leq n$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
+        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,i\in\{1,\dots,n\}$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
         \begin{equation*}

### 2021-06-25 authors_responses/first_tac_rejection/authors_response.tex
In the processes of explaining the instance-timestep relation better in the main text (not done) Fixed typos in author's response

@@
 
-As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearlising filter for the prediction step of the algorithm.
+As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearising filter for the prediction step of the algorithm.
 However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.

### 2021-06-29 main.tex
Made the matrices with zeros smaller
In the processes of explaining the instance-timestep relation better in the main text (not done) Fixed typos in author's response
Draft of notation changes done Also tried to cut down to 12 pages a bit more where possible (very close now)

@@
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
-In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, respectively, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
 
 Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private.
-We first define a novel notion for private linear combination aggregation, satisfying these cryptographic requirements, before using it to derive a filter based on the Extended Kalman Filter, with no hierarchical sensor layout assumptions.
-The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition capturing different communication assumptions and leakages is given, crucial for cryptographic security.
+We first define a novel notion for private linear combination aggregation and an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
+The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its formal security.
 To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.
@@
 \caption{Required linear combination aggregation steps at instance $t$.}
+\vspace{-\baselineskip}
 \label{fig:agg_steps}
@@
 
-Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the navigator and sensors.
+Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
 \begin{LaTeXdescription}
@@
 This means the navigator may not send different weights to individual sensors during a single instance $t$.
-    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning they are assumed to follow the localisation procedure correctly but may store or use any gained sensitive information.
+    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning that they follow the localisation procedure correctly but may store or use any gained sensitive information.
 \end{LaTeXdescription}
@@
 \end{LaTeXdescription}
-The security notions we want the above algorithms to meet reflect the previously stated estimation privacy goals.
+The security notions we want these algorithms to meet reflect the previously stated estimation privacy goals.
 The navigator should learn no information from individual sensors while sensors should learn no information from the navigator or any other sensors.
@@
 \end{equation}
-with noise term $\vec{w}_k$. Measurements of the system follow a measurement model dependent on sensor $i\in\{1,\dots,n\}$, given by 
+with noise term $\vec{w}_k$. Measurements of $\vec{x}_k$ follow a measurement model dependent on sensor $i\in\{1,\dots,n\}$, given by 
 \begin{equation}
@@
 Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication.
-This is captured by a third parameter $d$; the number of multiplication factors to add or remove from encodings.
+This is captured by a third parameter $d$; the number of precision factors present in encodings.
 
@@
 Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution.
+
+As aggregation is typically performed on scalar inputs, we extend our notation for the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$.
+To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$.
 The four algorithms defining our scheme are given as follows.
@@
 
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] Encrypted linear combination at instance $t$ is computed as
-    \begin{equation}
-        l^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
+    \item[$\mathsf{CombEnc}(t_{k,\tau}, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_j^{(k,\tau)}), a^{(k,\tau)}_{i,j}),\ j\in\{1\dots m\}$] Encrypted linear combination at instance $t_{k,\tau}$ is computed as
+    \begin{equation}
+        l^{(k,\tau)}_i = H(t_{k,\tau})^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(k,\tau)}_j)^{a^{(k,\tau)}_{i,j}} \pmod{N^2}\,,\label{eqn:our_scheme_lin_comb}
     \end{equation}
@@
         \begin{split}
-             l^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
-            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{a^{(t)}_{i,j}\omega^{(t)}_j} \rho^{N}_{j} \pmod{N^2} \\
-            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j} \rho_{i}^{N} \pmod{N^2}\,,
+            l^{(k,\tau)}_i &= H(t_{k,\tau})^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(k,\tau)}_j)^{a^{(k,\tau)}_{i,j}} \pmod{N^2} \\
+            &= H(t_{k,\tau})^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j) \pmod{N^2} \\
+            &= H(t_{k,\tau})^{sk_i}\cdot \\
+            &\qquad \prod^{m}_{j=1}(N+1)^{a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j} \rho^{N}_{j} \pmod{N^2} \\
+            &= H(t_{k,\tau})^{sk_i}\cdot \\
+            &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j} \rho_{i}^{N} \pmod{N^2}\,,
         \end{split}
@@
     for some values $\rho_i,\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$.
-Here, $\rho_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
-
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] Aggregation is computed as $l^{(t)} = \prod^n_{i=1}l^{(t)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
-    \begin{equation}
-        \begin{split}
-            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(t)}_{i,j}\omega^{(t)}_j =\\
-            &\frac{L((l^{(t)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
+Here, $\rho_i^N$ and $H(t_{k,\tau})^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
+
+    \item[$\mathsf{AggDec}(t_{k,\tau}, pk_0, sk_0, l^{(k,\tau)}_1,\shrtdots,l^{(k,\tau)}_n)$] Aggregation is computed as $l^{(k,\tau)} = \prod^n_{i=1}l^{(k,\tau)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
+    \begin{equation}
+        \begin{split}
+            \sum^{n}_{i=1}\sum^{m}_{j=1}&a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j =\\
+            &\frac{L((l^{(k,\tau)})^\lambda\pmod{N^2})}{L((N+1)^\lambda\pmod{N^2})} \pmod{N}\,,
         \end{split} \label{eqn:our_scheme_decrypt}
@@
     \begin{align*}
-        l^{(t)} &= \prod^n_{i=1}H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}a_{i,j}\omega_j}\rho_i^N \pmod{N^2} \\
-        \begin{split}
-            &= H(t)^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho_i^N \pmod{N^2}
+        \begin{split}
+        l^{(k,\tau)} &= \prod^n_{i=1}H(t_{k,\tau})^{sk_i}\cdot \\
+        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \pmod{N^2}
         \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho'^N \pmod{N^2}\,,
+        \begin{split}
+            &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
+            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \pmod{N^2}
+        \end{split}\\
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \pmod{N^2}\,,
     \end{align*}
@@
 \end{LaTeXdescription}
-Additionally, we note that in the above construction, all weights $\omega^{(t)}_j$ and values $a^{(t)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.
+Additionally, we note that in the above construction, all weights $\omega^{(k,\tau)}_j$ and values $a^{(k,\tau)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.
 
@@
 \begin{remark}
-    Given the construction of the scheme above, it can be seen that any weights $\omega^{(t)}_j$, whose values are known at each sensor, do not need to be broadcast by the navigator.
+    Given the construction of the scheme above, it can be seen that any weights $\omega^{(k,\tau)}_j$, whose values are known at each sensor, do not need to be broadcast by the navigator.
 In this case, sensors can replace
     \begin{equation}
-        \mathcal{E}_{pk_0}(\omega^{(t)}_j)^{a^{(t)}_{i,j}} = (N+1)^{\omega^{(t)}_ja^{(t)}_{i,j}}\rho_j^N \pmod{N^2}
+        \mathcal{E}_{pk_0}(\omega^{(k,\tau)}_j)^{a^{(k,\tau)}_{i,j}} = (N+1)^{\omega^{(k,\tau)}_ja^{(k,\tau)}_{i,j}}\rho_j^N \pmod{N^2}
     \end{equation}
@@
     \begin{equation}
-        (N+1)^{\omega^{(t)}_ja^{(t)}_{i,j}} \pmod{N^2}\,.
-    \end{equation}
-    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by the number of weights $\omega^{(t)}_j$ that do not hold any information private to the navigator and are known by the sensors in advance.
+        (N+1)^{\omega^{(k,\tau)}_ja^{(k,\tau)}_{i,j}} \pmod{N^2}\,.
+    \end{equation}
+    This is due to the removal of $\rho_j^N$ terms during decryption and can be used to reduce the navigator's broadcast communication cost by the number of weights $\omega^{(k,\tau)}_j$ that do not hold any information private to the navigator and are known by the sensors in advance.
 \end{remark}
@@
 For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator.
-Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and that the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
+Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
 
@@
         0 \\
-        \vdots \\
-        0
+        \vdots
     \end{bmatrix}\,,
@@
         0 \\
-        \vdots \\
-        0
+        \vdots
     \end{bmatrix}\,. \label{eqn:modified_jacobian}
@@
 \end{equation}
-with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_{k,i}$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
+with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_{k,i}$. The noise in this case (again a function of $v_{k,i}$) has variance 
 \begin{equation}
@@
         \begin{bmatrix}
-            \alpha_1^{(i)} & \alpha_2^{(i)} & 0 & \cdots & 0
+            \alpha_i^{(k,1)} & \alpha_i^{(k,2)} & 0 & \cdots
         \end{bmatrix}^\top\,,
@@
     \begin{split}
-        \alpha_1^{(i)} &= (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
+        \alpha_i^{(k,1)} &= (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
         &\quad+ (-r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\
@@
     \begin{split}
-        \alpha_2^{(i)} &= (2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\
+        \alpha_i^{(k,2)} &= (2r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2\hat{y}_{k|k-1} \\
         &\quad+ (-2r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1}^2 \\
@@
         \begin{bmatrix}
-            \beta_1^{(i)} & \beta_2^{(i)} & 0 & \cdots & 0 \\
-            \beta_3^{(i)} & \beta_4^{(i)} & 0 & \cdots & 0\\
-            0 & 0 & 0 & \cdots & 0 \\
-            \vdots & \vdots & \vdots & \ddots & \vdots \\
-            0 & 0 & 0 & \cdots & 0
+            \alpha_i^{(k,3)} & \alpha_i^{(k,4)} & 0 & \cdots \\
+            \alpha_i^{(k,5)} & \alpha_i^{(k,6)} & 0 & \cdots\\
+            0 & 0 & 0 & \cdots \\
+            \vdots & \vdots & \vdots & \ddots
         \end{bmatrix}\,,
@@
 \begin{align*}
-    \beta_1^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
-    \begin{split}
-        \beta_2^{(i)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\
+    \alpha_i^{(k,3)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
+    \begin{split}
+        \alpha_i^{(k,4)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1} + (-4r_{k,i}^{\prime-1}s_{y,i})\hat{x}_{k|k-1}  \\
         &\qquad+ (-4r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}s_{y,i})\,,
     \end{split}\\
-    \beta_3^{(i)} &= \beta_{12}\ \textrm{and} \\
-    \beta_4^{(i)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
+    \alpha_i^{(k,5)} &= \beta_{12}\ \textrm{and} \\
+    \alpha_i^{(k,6)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
 \end{align*}
@@
 \end{remark}
-
-The final step required for computing \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} at the sensors and \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update} at the navigator, using the proposed LCAO scheme, is handling the unique instance variables $t$ in the context of estimation timesteps $k$.
-We do this by performing the linear combination aggregation process of \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb} for each element independently and setting $t$ to the concatenation
-\begin{equation}
-    t=k\mathbin\|v\mathbin\|w\mathbin\|\tau\,,
-\end{equation}
-for elements in row $v$ and column $w$, and with $\tau=0$ for elements in $\vec{i}'_{k,i}$ and $\tau=1$ otherwise.
-This results in elementwise encryptions, and six aggregations at each timestep $k$ (in the two-dimensional case).
 
@@
 \begin{LaTeXdescription}
-    \item[Setup] Run only once, the $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run only once by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
 
@@
 
-    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ for each element and sending them back to the navigator.
+    \item[Measurement] At each timestep $k$, sensors modify their measurements with \eqref{eqn:modified_measurement} and \eqref{eqn:modified_measurement_variance_estimate} before computing encryptions of $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ using algorithm $\mathsf{CombEnc}$ for each element and sending them back to the navigator.
 This is given by algorithm \ref{alg:measurement_info}.
 
-    \item[Update] At each timestep $k$, the navigator aggregates and decrypts recieved measurement vectors and matrices with algorithm $\mathsf{AggDec}$, before computing the modified EIF update equations \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update}.
+    \item[Update] At each timestep $k$, the navigator aggregates and decrypts recieved measurement vectors and matrices with algorithm $\mathsf{AggDec}$, before computing the EIF update equations \eqref{eqn:eif_modified_vec_update} and \eqref{eqn:eif_modified_mat_update}.
 This is given by algorithm \ref{alg:nav_update}.
@@
 
-    \State Let $\bm{\alpha}_{v}^{(i)}$ represent the encryption of $\alpha_{v}^{(i)}$ in \eqref{eqn:hrz_linear_comb}
-    \State $\bm{\alpha}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
+    \State Let $\bm{\alpha}_{i}^{(k,\tau)}$ represent the encryption of $\alpha_{i}^{(k,\tau)}$ in \eqref{eqn:hrz_linear_comb} and \eqref{eqn:hrh_linear_comb}
+    \State $\bm{\alpha}_{i}^{(k,1)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^3_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
@@
     \ $(N+1)^{\mathsf{E}_{1}(-2r_{k, i}^{\prime-1}s_{x,i}z_{k,i}')}
-    H(k\mathbin\|1\mathbin\|1\mathbin\|0)\pmod{N^2}$
-    \State Compute $\bm{\alpha}_{2}^{(i)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
-    \For{$v \gets 1$ to $2$}
-        \State Send $\bm{\alpha}_{v}^{(i)}$ to the navigator
-    \EndFor
-
-    \State Let $\bm{\beta}_{w}^{(i)}$ represent an encryption of $\beta_{w}^{(i)}$ in \eqref{eqn:hrh_linear_comb}
-    \State $\bm{\beta}_{1}^{(i)} \gets \mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(4r_{k,i}^{\prime-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}))^{\mathsf{E}_{0}(-8r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
-    \ $(N+1)^{\mathsf{E}_{1}(4r_{k,i}^{\prime-1}s_{x,i}^2)}\cdot$\par
-    \ $H(k\mathbin\|1\mathbin\|1\mathbin\|1)\pmod{N^2}$
-    \State Compute remaining $\bm{\beta}_{w}^{(i)}$ using \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
-    \For{$w \gets 1$ to $4$}
-        \State Send $\bm{\beta}_{w}^{(i)}$ to the navigator
+    H(k\mathbin\|1)\pmod{N^2}$
+    \State Compute remaining $\bm{\alpha}_{i}^{(k,\tau)}$ using \eqref{eqn:hrz_linear_comb}, \eqref{eqn:hrh_linear_comb}, \eqref{eqn:our_scheme_lin_comb} and the remark from section \ref{sec:lcao_scheme} in the form above
+    \For{$\tau \gets 1$ to $6$}
+        \State Send $\bm{\alpha}_{i}^{(k,\tau)}$ to the navigator
     \EndFor
@@
 
-    \For{$v \gets 1$ to $2$}
-        \State Receive $\bm{\alpha}_{v}^{(i)}$ from each sensor $i\in\{1,\dots,n\}$
+    \For{$\tau \gets 1$ to $6$}
+        \State Receive $\bm{\alpha}_{i}^{(k,\tau)}$ from each sensor $i\in\{1,\dots,n\}$
     \EndFor
 
-    \For{$w \gets 1$ to $4$}
-        \State Receive $\bm{\beta}_{w}^{(i)}$ from each sensor $i\in\{1,\dots,n\}$
+    \State Let $\bm{\alpha}^{(k,\tau)}$ represent an encryption of $\sum_{i=1}^n\alpha_{i}^{(k,\tau)}$
+    \For{$\tau \gets 1$ to $6$}
+        \State $\bm{\alpha}^{(k,\tau)} \gets \prod_{i=1}^n\bm{\alpha}_{i}^{(k,\tau)}$
+        \State Compute $\mathcal{D}_{sk_0}(\bm{\alpha}^{(k,\tau)})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
+        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\alpha}^{(k,\tau)}))$ by \eqref{eqn:decode}
     \EndFor
-
-    \State Let $\bm{\alpha}_{v}$ represent an encryption of $\sum_{i=1}^n\alpha_{v}^{(i)}$
-    \For{$v \gets 1$ to $2$}
-        \State $\bm{\alpha}_{v} \gets \prod_{i=1}^n\bm{\alpha}_{v}^{(i)}$
-        \State Compute $\mathcal{D}_{sk_0}(\bm{\alpha}_{v})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-        \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\alpha}_{v}))$ by \eqref{eqn:decode}
-    \EndFor
-    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ from decoded decryptions above
-
-    \State Let $\bm{\beta}_{w}$ represent an encryption of $\sum_{i=1}^n\beta_{w}^{(i)}$
-    \For{$w \gets 1$ to $4$}
-            \State $\bm{\beta}_{w} \gets \prod_{i=1}^n\bm{\beta}_{w}^{(i)}$
-            \State Compute $\mathcal{D}_{sk_0}(\bm{\beta}_{w})$ with $\lambda$ by \eqref{eqn:our_scheme_decrypt}
-            \State Compute $\mathsf{E}^{-1}_{1}(\mathcal{D}_{sk_0}(\bm{\beta}_{w}))$ by \eqref{eqn:decode}
-    \EndFor
-    \State Construct $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above
+    \State Construct $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$ from decoded decryptions above
 
@@
 \caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
+\vspace{-\baselineskip}
 \label{fig:alg_steps}
@@
 The leakage function from the $\mathsf{AggDec}$ algorithm corresponds to the information vector and matrix sums, $\sum_{i=1}^n\vec{i}'_{k,i}$ and $\sum_{i=1}^n\mat{I}'_{k,i}$, respectively.
-However, recalling that a compromised navigator can also learn the individual sums weighted by the same weight, $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$ can be leaked as well.
-From these leaked sums, we can see that private sensor information, $z'_{k,i}$, $r'_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
+However, recalling that a compromised navigator can learn the individual sums weighted by the same weight, $\{\sum_{i=1}^n2r^{-1}_{k,i},\ \sum_{i=1}^n-r^{-1}_{k,i}s_{x,i},\ \sum_{i=1}^n-2r^{-1}_{k,i}s_{x,i},\ \dots\}$ can be leaked as well.
+From this leakage, we can see that private sensor information, $z'_{k,i}$, $r'_{k,i}$ and $\vec{s}_i$, is present only in their complete sums
 \begin{equation}
@@
 which in practice correspond to their averages.
-We can therefore say, in the context of our proposed localisation method, LCAO leakage corresponds to the averages of sensor private information, while individual sensor information remains private.
+Therefore, in the context of our proposed localisation method, LCAO leakage corresponds to the averages of sensor private information, while individual sensor information remains private.
 
@@
     \begin{bmatrix}
-        1 & 0.5 & 0 & 0\\
-        0 & 1 & 0 & 0\\
-        0 & 0 & 1 & 0.5\\
+        1 & 0 & 0.5 & 0\\
+        0 & 1 & 0 & 0.5\\
+        0 & 0 & 1 & 0\\
         0 & 0 & 0 & 1
@@
     \begin{bmatrix}
-        0.4 & 1.3 & 0 & 0\\
-        1.3 & 5.0 & 0 & 0\\
-        0 & 0 & 0.4 & 1.3\\
-        0 & 0 & 1.3 & 5.0
+        0.4 & 0 & 1.3 & 0\\
+        0 & 0.4 & 0 & 1.3\\
+        1.3 & 0 & 5.0 & 0\\
+        0 & 1.3 & 0 & 5.0
     \end{bmatrix}\,,
@@
     \caption{Average RMSE of our privacy-preserving filter and the standard EIF for different layouts.}
+    \vspace{-\baselineskip}
     \label{fig:sim_layout_errors}
@@
     \caption{Runtimes for varying key sizes and numbers of sensors.}
+    \vspace{-\baselineskip}
     \label{fig:sim_timing}
@@
 
+%\vspace{-4\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
@@
 
+%\vspace{-4\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
@@
 
+%\vspace{-4\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}

### 2021-06-30 authors_responses/first_tac_rejection/authors_response.tex
Used ieee bib settings to add et al for long references and some baselineskips to make the work fit on 12 pages Changed plot colours to match the matplotlib colours Fixed typoes throughout (response and revision) Still need to rerun simulation and update the hardware and execution parameters of new run

@@
 However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter.
-We have now relaxed the requirements of the system model and no specify the prediction equations of EKF specifically.
+We have now relaxed the requirements of the system model and no longer require prediction to be performed by an EKF specifically.
 
@@
 However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
-Huag) and has been computed when evaluating the proposed filter through simulation.
+Huag) and has been used when evaluating our proposed filter through simulation.
 This can be done in various ways specific to the system being modelled and is beyond the scope of this work.
@@
 The computational performance is more difficult to compare.
-Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript).
+Comparison with a different encryption scheme would require another scheme meeting LCAO (needed to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript).
 Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.

### 2021-06-30 main.tex
Used ieee bib settings to add et al for long references and some baselineskips to make the work fit on 12 pages Changed plot colours to match the matplotlib colours Fixed typoes throughout (response and revision) Still need to rerun simulation and update the hardware and execution parameters of new run

@@
 
-% Tikz reused pics
+% Tikz reused commands
 \tikzset{
@@
 }
+\definecolor{pyplotblue}{RGB}{31,119,180}
+\definecolor{pyplotorange}{RGB}{255,127,14}
 
@@
 In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
-Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localization} gives a solution to the estimation problem making use of this scheme.
+Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localisation} gives a solution to the estimation problem making use of this scheme.
 Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.
@@
 The communication between the navigator and sensors in our estimation problem will be decomposed into a simple two-step bi-directional protocol that will simplify defining formal security.
-In section \ref{sec:priv_localization}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals.
+In section \ref{sec:priv_localisation}, we will show how this protocol is sufficient to compute the location estimate at a navigator while meeting our desired privacy goals.
 The communication protocol is as follows.
@@
     % Navigator
-    \fill (3.25,4.75) [green!80!black!60] ellipse (0.4 and 0.4);
+    \fill (3.25,4.75) [pyplotblue!70] ellipse (0.4 and 0.4);
     \pic[xscale=0.22,yscale=0.3] at (3.25,4.9225) {plane};
@@
     \node at (1.5,1.375) {Sensor $1$};
-    \fill [blue!80!black!40] (0.25,1.625) rectangle (2.875,2.625);
+    \fill [pyplotorange!70] (0.25,1.625) rectangle (2.875,2.625);
     \node at (1.625,2.125) {$\displaystyle l_1^{(t)} \!=\! \sum^m_{j=1}a_{1,j}^{(t)}\omega_j^{(t)}$};
     \node at (5,1.375) {Sensor $n$};
-    \fill [blue!80!black!40] (3.625,1.625) rectangle (6.25,2.625);
+    \fill [pyplotorange!70] (3.625,1.625) rectangle (6.25,2.625);
     \node at (5,2.125) {$\displaystyle l_n^{(t)} \!=\! \sum^m_{j=1}a_{n,j}^{(t)}\omega_j^{(t)}$};
@@
     % Navigator
-    \fill [green!80!black!60] (1.375,-2) rectangle (5.125,-0.25);
+    \fill [pyplotblue!70] (1.375,-2) rectangle (5.125,-0.25);
     \pic[xscale=0.22,yscale=0.3] at (3.25,-0.4775) {plane};
@@
     \node at (1.25,-3.875) {Sensor $1$};
-    \fill  (5.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \fill  (5.25,-3.25) [pyplotorange!70] ellipse (0.4 and 0.4);
     \node at (5.25,-3.875) {Sensor $n$};
-    \fill  (1.25,-3.25) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \fill  (1.25,-3.25) [pyplotorange!70] ellipse (0.4 and 0.4);
     \fill [black] (2.75,-3.25) circle (0.05);
@@
 \caption{Required linear combination aggregation steps at instance $t$.}
-\vspace{-\baselineskip}
 \label{fig:agg_steps}
@@
 In addition, we note that an alternative approach to the two-step protocol is computing $\sum^{m}_{j=1}(\omega_j^{(t)}\sum^{n}_{i=1} a_{i,j}^{(t)})$ at the navigator, requiring only values $a_{i,j}^{(t)}, j\in\{1,\dots,m\}$ to be sent from each sensor $i$.
-We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localization}.
+We justify the use of bi-directional communication by reducing communication costs when the number of weights is larger than the number of sensors, $m>n$, and by sending fewer weights in the presence of repeats, as will be shown to be the case in section \ref{sec:priv_localisation}.
 
@@
 \begin{LaTeXdescription}
-    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances, and having the ability to encrypt plaintexts of their choice.
+    \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances and having the ability to encrypt plaintexts of their choice.
     \item[Linear Combination Aggregator Obliviousness] No colluding subset \textit{excluding} the navigator gains additional information about the remaining sensor values to be weighted, $a^{(t)}_{i,j},\,j\in\{1,\dots,m\}$, where sensor $i$ is not colluding, given only encryptions of their linear combinations $l_i$ from the current and previous instances.
@@
 \end{LaTeXdescription}
-While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Ciphertext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
+While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Plaintext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
 Lastly, we conclude the cryptographic problem definition with the following important remark.
@@
 
-\subsection{Joye-Libert Privacy-preserving Aggregation Scheme} \label{subsec:joye_libert_scheme}
+\subsection{Joye-Libert Privacy-Preserving Aggregation Scheme} \label{subsec:joye_libert_scheme}
 The Joye-Libert privacy-preserving aggregation scheme \cite{joyeScalableSchemePrivacyPreserving2013} is a scheme defined on time-series data and meets the security notion of Aggregator Obliviousness (AO) \cite{shiPrivacyPreservingAggregationTimeSeries2011}.
@@
 
-The function for \textit{combined} quantization and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
+The function for \textit{combined} quantisation and encoding, $\mathsf{E}_{M,\phi,d}(a)$, of a given number $a \in \mathbb{R}$ and with an integer range $\mathbb{Z}_M$, precision $\phi$ and scaling for $d$ prior encoded multiplications is given by
 \begin{equation}
@@
 
-In general, the choice of a large precision parameter $\phi$ may reduce quantization errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications.
+In general, the choice of a large precision parameter $\phi$ may reduce quantisation errors introduced in \eqref{eqn:encode}, but risks overflow after too many multiplications.
 Given the largest number of encoded multiplications, $d_{max}$, and the largest value to be encoded $a_{max}$, the parameter should be chosen such that
@@
 
-As aggregation is typically performed on scalar inputs, we extend our notation for the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$.
+As aggregation is typically performed on scalar inputs, we extend our notation to the context of multidimensional estimation data by letting an instance $t_{k,\tau}$ uniquely capture the scalar aggregation during an estimation timestep $k$ for a single element with position index $\tau$.
 To achieve this in practice, any injective function can be used, such as the concatenation $t_{k,\tau}=k\mathbin\|\tau$.
@@
 
-The security proof of this scheme must show that both encrypted weights meet IND-CPA and encrypted aggregation meets LCAO.
+The security proof of this scheme must both show that encrypted weights meet IND-CPA and that encrypted aggregation meets LCAO.
 As weights are encrypted with the Paillier encryption scheme, the first requirement is already met.
@@
 
-\section{Privacy-Preserving Localization} \label{sec:priv_localization}
+\section{Privacy-Preserving Localisation} \label{sec:priv_localisation}
 With a concrete scheme meeting the LCAO notion, we can now put forward a localisation filter with communication that can be reformulated to the required protocol.
@@
 namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-$\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
+However, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
 For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator.
@@
 \subsection{Localisation} \label{subsec:localisation}
-To complete the EIF update using a linear combination aggregation process, modified measurement vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$, using the modified measurement model \eqref{eqn:modified_measurement_model}, can be rearragned as follows.
+To complete the EIF update as a linear combination aggregation, modified vectors $\vec{i}'_{k,i}$ and matrices $\mat{I}'_{k,i}$, using the modified measurement model \eqref{eqn:modified_measurement_model}, can be rearragned as follows.
 \begin{equation}
@@
     \end{split}\\
-    \alpha_i^{(k,5)} &= \beta_{12}\ \textrm{and} \\
+    \alpha_i^{(k,5)} &= \alpha_i^{(k,4)}\ \textrm{and} \\
     \alpha_i^{(k,6)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
@@
 \begin{remark}
-    The above has been derived for two-dimensional localisation but can be similarly derived for three-dimensional case.
+    The above has been derived for two-dimensional localisation but can be similarly derived for the three-dimensional case.
 However, the number of weights increases combinatorially with the number of dimensions, thus affecting the cost of communication as well.
@@
 For brevity, we will assume $\phi$ and $M=N$ from section \ref{subsec:encoding} to be public information and thus simplify the encoding notation $\mathsf{E}_{N,\phi,d}(\cdot)$ to $\mathsf{E}_{d}(\cdot)$.
-The privacy-preserving localization filter consists of the following steps.
+The privacy-preserving localisation filter consists of the following steps.
 \begin{LaTeXdescription}
-    \item[Setup] The $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run only once by a trusted third party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
+    \item[Setup] The $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run only once by a trusted party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
 
@@
     % Navigator
-    \fill  [green!80!black!60] (2,7) rectangle (4.5,5.75);
+    \fill  [pyplotblue!70] (2,7) rectangle (4.5,5.75);
     \pic[xscale=0.22,yscale=0.3] at (3.25,6.7975) {plane};
@@
     % Sensors
-    \fill  (1.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \fill  (1.25,4) [pyplotorange!70] ellipse (0.4 and 0.4);
     \node at (1.25,3.375) {Sensor $1$};
-    \fill  (5.25,4) [blue!80!black!40] ellipse (0.4 and 0.4);
+    \fill  (5.25,4) [pyplotorange!70] ellipse (0.4 and 0.4);
     \node at (5.25,3.375) {Sensor $n$};
@@
     % Navigator
-    \fill  (3.25,1.5) [green!80!black!60] ellipse (0.4 and 0.4);
+    \fill  (3.25,1.5) [pyplotblue!70] ellipse (0.4 and 0.4);
     \pic[xscale=0.22,yscale=0.3] at (3.25,1.6725) {plane};
@@
     % Sensors
-    \fill  [blue!80!black!40] (6.25,-1.625)  rectangle (4.25,-0.625);
+    \fill  [pyplotorange!70] (6.25,-1.625)  rectangle (4.25,-0.625);
     \node at (1.25,-1.875) {Sensor $1$};
-    \fill  [blue!80!black!40] (2.25,-1.625)  rectangle (0.25,-0.625);
+    \fill  [pyplotorange!70] (2.25,-1.625)  rectangle (0.25,-0.625);
     \node at (5.25,-1.875) {Sensor $n$};
@@
     % Navigator
-    \fill  [green!80!black!60] (1.5,-3.5) rectangle (5,-5.5);
+    \fill  [pyplotblue!70] (1.5,-3.5) rectangle (5,-5.5);
     \pic[xscale=0.22,yscale=0.3] at (3.25,-3.8275) {plane};
@@
 \caption{Procedure at timestep $k$ for the proposed privacy-preserving EIF.}
-\vspace{-\baselineskip}
 \label{fig:alg_steps}
@@
 We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance.
-We can attribute the similarity in MSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
+We can attribute the similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
 
@@
     \caption{Runtimes for varying key sizes and numbers of sensors.}
-    \vspace{-\baselineskip}
     \label{fig:sim_timing}
@@
 Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future.
-Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to increase the filter update frequency, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.
+Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to decrease the filter update duration, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.
 
@@
 \end{equation*}
-for \textit{all} negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
+for \textit{any} negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$.
 That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case, \cite{joyeScalableSchemePrivacyPreserving2013}).
@@
 
-\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtranBST/IEEEtran}
 \bibliography{BibTeX/PrivateEIFLocalisation}
@@
 
-%\vspace{-4\baselineskip}
+\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
@@
 
-%\vspace{-4\baselineskip}
+\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
@@
 
-%\vspace{-4\baselineskip}
+\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}

### 2021-07-05 main.tex
Changed simulation specs in text Reran simulations and obtained new figures (1000 runs for error plots, 10 runs for timing plots) Fixed couple of spelling things

@@
 Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private.
-We first define a novel notion for private linear combination aggregation and an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
+We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
 The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its formal security.
@@
 was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}, using a linear Kalman filter for the navigator's local state prediction.
-Code was written in the C programming language, using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator.
+Code was written in the C programming language using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator.
 The MG1 mask generation function and the SHA256 hash function, from the OpenSSL library \cite{theopensslprojectOpenSSL2020}, were used to implement the required hash function $H$, and the Libpaillier library \cite{bethencourtLibpaillier2010} was used for the Paillier encryption scheme.
 Additionally, GNU libraries, GSL \cite{thegsldevelopmentteamGSLGNUScientific2019} and GMP \cite{granlundGMPGNUMultiple2020}, were used for algebraic operations and multiple-precision encoded integers, respectively.
-All execution was performed on a 3.00GHz Intel i7-9700 CPU, running on the Windows Subsystem for Linux (WSL).
+All execution was performed on a 3.33GHz Xeon W3680 CPU, running on the Windows Subsystem for Linux (WSL).
 
@@
 \end{figure}
-To demonstrate the accuracy of the method, we have compared the root mean square error (RMSE) of the privacy-preserving filter to the standard EIF using unmodified measurements, that is algebraically equivalent to the EKF, typically used in industry for linearising non-linear state estimation.
-Measurement and estimation in each layout from figure \ref{fig:sim_layouts} consists of $50$ filter iterations and was run $100$ times.
+To demonstrate the accuracy of the method, we have compared the root mean square error (RMSE) of the privacy-preserving filter to the standard EIF using unmodified measurements, which is algebraically equivalent to the EKF typically used in industry for linearising non-linear state estimation.
+Estimation in each layout from figure \ref{fig:sim_layouts} consisted of $50$ filter iterations and was run $1000$ times.
 Unmodified measurement variances were taken as $r_{k,i}=5$ for all $k>0$ and a large fractional precision factor, $\phi=2^{32}$, was chosen.
@@
 \end{figure}
-From these results, we can see the similarity in filter performance between the privacy-preserving method and that of the traditional EIF.
+From these results, we can see a strong similarity in filter performance between the privacy-preserving method and that of the traditional EIF.
 We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance.
-We can attribute the similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
+We attribute this similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
 
 In addition to filter error, computational performance is important to consider when relying on cryptographic methods.
-Figure \ref{fig:sim_timing} shows the average execution time of $50$ simulation runs with varying numbers of sensors, for different key sizes (bit lengths of $N$).
-Here, increasing the number of sensors primarily affects the number of inter-process communications and aggregation modular multiplications due to the asynchronous implementation.
+Figure \ref{fig:sim_timing} shows the averages of $10$ execution times when varying the numbers of sensors and key sizes (bit lengths of $N$).
+Here, increasing the number of sensors primarily affected the number of inter-process communications and aggregation modular multiplications due to the asynchronous implementation.
 \begin{figure}[htbp]
@@
 The key size should be chosen such that sufficient security is achieved, and the current recommendation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
-For our implementation of the filter, this results in a filter update computation duration of roughly $1.6s$.
+For our implementation of the filter, run on the aforementioned hardware, this results in a filter update computation duration of roughly $1.7s$.
 

### 2021-08-09 main.tex
New branch for switching to Automatica template Made a few equations and description items fit the larger font Fixed a few Grammarly things that were missed last time Fixed a bibtex item Now a single "overfull" error is present, but in the text is not too wide (will leave for submission if no errors triggered) Replaced template folder contents to hold new template

@@
-\documentclass[10pt,letterpaper,oneside,twocolumn,journal]{IEEEtran}
-
-% 
-% 8888888 888b     d888 8888888b.   .d88888b.  8888888b. 88888888888 .d8888b.  
-%   888   8888b   d8888 888   Y88b d88P" "Y88b 888   Y88b    888    d88P  Y88b 
-%   888   88888b.d88888 888    888 888     888 888    888    888    Y88b.      
-%   888   888Y88888P888 888   d88P 888     888 888   d88P    888     "Y888b.   
-%   888   888 Y888P 888 8888888P"  888     888 8888888P"     888        "Y88b. 
-%   888   888  Y8P  888 888        888     888 888 T88b      888          "888 
-%   888   888   "   888 888        Y88b. .d88P 888  T88b     888    Y88b  d88P 
-% 8888888 888       888 888         "Y88888P"  888   T88b    888     "Y8888P"  
-%                                                                              
-%                                                                              
-%                                                                              
-%
-
+% autosam.tex
+% Annotated sample file for the preparation of LaTeX files
+% for the final versions of papers submitted to or accepted for 
+% publication in AUTOMATICA.
+
+% See also the Information for Authors.
+
+% Make sure that the zip file that you send contains all the 
+% files, including the files for the figures and the bib file.
+
+% Output produced with the elsart style file does not imitate the
+% AUTOMATICA style. The style file is generic for all Elsevier
+% journals and the output is laid out for easy copy editing. The
+% final document is produced from the source file in the
+% AUTOMATICA style at Elsevier.
+
+% You may use the style file autart.cls to obtain a two-column 
+% document (see below) that more or less imitates the printed 
+% Automatica style. This may helpful to improve the formatting 
+% of the equations, tables and figures, and also serves to check 
+% whether the paper satisfies the length requirements.
+
+% Please note: Authors must not create their own macros.
+
+% For further information regarding the preparation of LaTeX files 
+% for Elsevier, please refer to the "Full Instructions to Authors" 
+% from Elsevier's anonymous ftp server on ftp.elsevier.nl in the
+% directory pub/styles, or from the internet (CTAN sites) on
+% ftp.shsu.edu, ftp.dante.de and ftp.tex.ac.uk in the directory
+% tex-archive/macros/latex/contrib/supported/elsevier.
+
+% The use of LaTeX2e is preferred.
+%\documentclass{elsart}
+
+% Enable this line and disable the preceding line to obtain a two-column document whose style resembles the printed Automatica style.
+\documentclass[twocolumn]{autart}
+
+% The printed column width is 8.4 cm. Size the figures accordingly.
 % Graphics
@@
 \usepackage{amsfonts}
-\usepackage{amsthm}
 \usepackage{mathtools}
@@
 \theoremstyle{remark}
-\newtheorem*{remark}{Remark}
+\newtheorem{remark}{Remark}
 
@@
 
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-% Requested for submission
-\pdfminorversion=4
-
-% Start
 \begin{document}
 
-% paper title
+\begin{frontmatter}
+% Running title for regular papers but only if the title is over 5 words. Running title is not shown in output.
+%\runtitle{Insert a suggested running title}
+
+% Title, preferably not more than 10 words.
 \title{Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies}
 
-% author names and IEEE memberships
-\author{Marko~Ristic$^{1}$,
-        Benjamin~Noack$^{1}$,~\IEEEmembership{Member,~IEEE,}
-        and~Uwe~D.~Hanebeck$^{2}$,~\IEEEmembership{Fellow,~IEEE}% <-this % stops a space
-\thanks{$^{1}$Marko Ristic and Benjamin Noack are with the Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany (e-mail: \{marko.ristic, benjamin.noack\}@ovgu.de).}% <-this % stops a space
-\thanks{$^{2}$Uwe D.
-Hanebeck is with the Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology (KIT), Germany (e-mail: uwe.hanebeck@kit.edu).}}% <-this % stops a space
-
-% make the title area
-\maketitle
-
-% 
-%        d8888 888888b.    .d8888b. 88888888888 8888888b.         d8888  .d8888b. 88888888888 
-%       d88888 888  "88b  d88P  Y88b    888     888   Y88b       d88888 d88P  Y88b    888     
-%      d88P888 888  .88P  Y88b.         888     888    888      d88P888 888    888    888     
-%     d88P 888 8888888K.   "Y888b.      888     888   d88P     d88P 888 888           888     
-%    d88P  888 888  "Y88b     "Y88b.    888     8888888P"     d88P  888 888           888     
-%   d88P   888 888    888       "888    888     888 T88b     d88P   888 888    888    888     
-%  d8888888888 888   d88P Y88b  d88P    888     888  T88b   d8888888888 Y88b  d88P    888     
-% d88P     888 8888888P"   "Y8888P"     888     888   T88b d88P     888  "Y8888P"     888     
-%                                                                                             
-%                                                                                             
-%                                                                                             
-%
-
+% Add the e-mail address (ead) as shown
+\author[ovgu]{Marko Ristic}\ead{marko.ristic@ovgu.de},
+\author[ovgu]{Benjamin Noack}\ead{benjamin.noack@ovgu.de},
+\author[kit]{Uwe D. Hanebeck}\ead{uwe.hanebeck@kit.edu}
+
+% Please supply full addresses here.
+\address[ovgu]{Autonomous Multisensor Systems Group (AMS), Institute for Intelligent Cooperating Systems (ICS), Otto von Guericke University Magdeburg (OVGU), Germany.}
+\address[kit]{Intelligent Sensor-Actuator-Systems Laboratory (ISAS), Institute for Anthropomatics, Karlsruhe Institute of Technology(KIT), Germany.}
+
+% Five to ten keywords, chosen from the IFAC keyword list or with the help of the Automatica keyword wizard
+\begin{keyword}
+State estimation; Data privacy; Sensor fusion; Extended Kalman filters.
+\end{keyword}
+
+% Abstract of not more than 200 words.
 \begin{abstract}                          
@@
 
-% Key words
-\begin{IEEEkeywords}
-State Estimation, Data Privacy, Sensor Fusion, Extended Kalman Filter.
-\end{IEEEkeywords}
-
-% Creates the second title
-\IEEEpeerreviewmaketitle
+\end{frontmatter}
 
@@
 \section{Introduction} \label{sec:introduction}
-\IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,ligginsDistributedDataFusion2012,liContributedReviewSourcelocalization2016} and have characterised many advancements of Kalman and Bayesian estimation theory \cite{mutambaraDecentralizedEstimationControl1998}.
-In particular, range-based localisation methods, including signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic ranges \cite{beutlerNewNonlinearFiltering2004} and ultra wideband ranges \cite{geziciLocalizationUltraWidebandRadios2005}, have found large application due to the prevalence of suitable sensors.
+Localisation methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,ligginsDistributedDataFusion2012,liContributedReviewSourcelocalization2016} and have characterised many advancements of Kalman and Bayesian estimation theory \cite{mutambaraDecentralizedEstimationControl1998}.
+In particular, range-based localisation methods, including signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic ranges \cite{beutlerNewNonlinearFiltering2004} and ultra-wideband ranges \cite{geziciLocalizationUltraWidebandRadios2005}, have found large application due to the prevalence of suitable sensors.
 In most cases, these localisation methods require the gathering of measurements centrally, where an estimate of location can be computed.
-With recent developments in distributed and cloud computing, uses of wireless and public communication channels for data transfer have becoming widespread, and the additional requirements of data privacy and state secrecy have become particularly relevant \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
+With recent developments in distributed and cloud computing, uses of wireless and public communication channels for data transfer have become widespread, and the additional requirements of data privacy and state secrecy have become particularly relevant \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
 
@@
 Before giving a formal definition for the construction and security of our desired encryption scheme, we make the following assumptions on the capabilities of the participants.
-\begin{LaTeXdescription}
+\begin{description}
     \item[Global Navigator Broadcast] We assume that broadcast information from the navigator is received by \textit{all} sensors involved in the protocol.
@@
     \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning that they follow the localisation procedure correctly but may store or use any gained sensitive information.
-\end{LaTeXdescription}
+\end{description}
 We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a complete group and treated as the global set for estimation purposes, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts.
@@
 They are defined as follows.
-\begin{LaTeXdescription}
+\begin{description}
     \item[$\mathsf{Setup}(\kappa)$] On input of security parameter $\kappa$, generate public parameters $\mathsf{pub}$, the number of weights $m$, the navigator's public and private keys $pk_0$ and $sk_0$ and the sensor private keys $sk_i,\,i\in\{1,\dots,n\}$.
     \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
-\end{LaTeXdescription}
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}(\omega_1^{(t)}),\dots,\mathcal{E}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination denoted $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+\end{description}
 The security notions we want these algorithms to meet reflect the previously stated estimation privacy goals.
@@
 In the context of the introduced communication protocol, this can be summarised as the following notions.
-\begin{LaTeXdescription}
+\begin{description}
     \item[Indistinguishable Weights] No colluding subset of sensors gains any new knowledge about the navigator weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ when receiving only their encryptions from the current and previous instances and having the ability to encrypt plaintexts of their choice.
@@
 Any colluding subset \textit{including} the navigator learns only the sum of all linear combinations weighted by weights of their choice, $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$.
-\end{LaTeXdescription}
+\end{description}
 While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Plaintext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
@@
 
-Key generation is computed by first choosing two equal length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
+Key generation is computed by first choosing two equal-length and sufficiently large primes $p$ and $q$, and computing $N=pq$.
 A hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$ is defined and the public key is set to $(N, H)$.
@@
     \begin{dcases}
-        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
-        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\text{otherwise} \\
-    \end{dcases}.\label{eqn:decode}
+        \frac{u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\hspace{-6pt}u\hspace{-8pt}\pmod{M} \leq \left\lfloor\frac{M}{2}\right\rfloor \\
+        -\frac{M - u\hspace{-8pt}\pmod{M}}{\phi^{d+1}}, &\hspace{-6pt}\text{otherwise} \\
+    \end{dcases}\!\!.\label{eqn:decode}
 \end{equation}
@@
 The four algorithms defining our scheme are given as follows.
-\begin{LaTeXdescription}
+\begin{description}
     \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
@@
 
-    \item[$\mathsf{CombEnc}(t_{k,\tau}, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_j^{(k,\tau)}), a^{(k,\tau)}_{i,j}),\ j\in\{1\dots m\}$] Encrypted linear combination at instance $t_{k,\tau}$ is computed as
+    \item[$\mathsf{CombEnc}(t_{k,\tau}, pk_0, sk_i, \mathcal{E}(\omega_1^{(k,\tau)})\dots , a^{(k,\tau)}_{i,1}\dots )$] At instance $t_{k,\tau}$, encrypted linear combination is computed as 
     \begin{equation}
@@
 
-    \item[$\mathsf{AggDec}(t_{k,\tau}, pk_0, sk_0, l^{(k,\tau)}_1,\shrtdots,l^{(k,\tau)}_n)$] Aggregation is computed as $l^{(k,\tau)} = \prod^n_{i=1}l^{(k,\tau)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
+    \item[$\mathsf{AggDec}(t_{k,\tau}, pk_0, sk_0, l^{(k,\tau)}_1,\dots,l^{(k,\tau)}_n)$] Aggregation is computed as $l^{(k,\tau)} = \prod^n_{i=1}l^{(k,\tau)}_i \pmod{N^2}$, removing the aggregation noise terms, and is followed by Paillier scheme decryption
     \begin{equation}
@@
         l^{(k,\tau)} &= \prod^n_{i=1}H(t_{k,\tau})^{sk_i}\cdot \\
-        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \pmod{N^2}
+        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
         \end{split}\\
@@
             &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \pmod{N^2}
+            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
         \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \pmod{N^2}\,,
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \!\!\pmod{N^2}\,,
     \end{align*}
     for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$.
-\end{LaTeXdescription}
+\end{description}
 Additionally, we note that in the above construction, all weights $\omega^{(k,\tau)}_j$ and values $a^{(k,\tau)}_{i,j}$ are integers and the resulting linear combinations and aggregation are computed modulo $N$.
@@
 \begin{align*}
-    \alpha_i^{(k,3)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{x,i}^2)\,, \\
+    \begin{split}
+        \alpha_i^{(k,3)} &= (4r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1} \\
+        &\qquad+ (4r_{k,i}^{\prime-1}s_{x,i}^2)\,,
+    \end{split}\\
     \begin{split}
@@
     \alpha_i^{(k,5)} &= \alpha_i^{(k,4)}\ \textrm{and} \\
-    \alpha_i^{(k,6)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} + (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
+    \begin{split}
+        \alpha_i^{(k,6)} &= (4r_{k,i}^{\prime-1})\hat{y}_{k|k-1}^2 + (-8r_{k,i}^{\prime-1}s_{y,i})\hat{y}_{k|k-1} \\
+        &\qquad+ (4r_{k,i}^{\prime-1}s_{y,i}^2)\,.
+    \end{split}
 \end{align*}
@@
 The privacy-preserving localisation filter consists of the following steps.
-\begin{LaTeXdescription}
+\begin{description}
     \item[Setup] The $\mathsf{Setup}$ algorithm from section \ref{sec:lcao_scheme} is run only once by a trusted party, $N$ and $H$ are made public, and the navigator and sensor secret keys, $sk_0=\lambda=\mathsf{lcm}(p-1, q-1)$ and $sk_i$, $i\in\{1,\dots,n\}$, are distributed accordingly.
@@
 This is given by algorithm \ref{alg:nav_update}.
-\end{LaTeXdescription}
+\end{description}
 
@@
 From these results, we can see a strong similarity in filter performance between the privacy-preserving method and that of the traditional EIF.
-We can also see that the varying average distances between sensors and navigator have little impact on the differences in performance.
+We can also see that the varying average distances between sensors and the navigator have little impact on the differences in performance.
 We attribute this similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
@@
 
+% Include this if you use bibtex and a bib file to produce the bibliography (preferred). The correct style is generated by Elsevier at the time of printing.
+\bibliographystyle{unsrt}
+\bibliography{BibTeX/PrivateEIFLocalisation}
+
 % 
@@
 
-\appendices
+\appendix
 \section{Linear Combination Aggregator Oblivousness (LCAO)} \label{app:lcao}
 The following game between attacker and challenger defines the security notion of LCAO.
-\begin{LaTeXdescription}
+\begin{description}
     \item[Setup] The challenger chooses security parameter $\kappa$, runs the $\mathsf{Setup}(\kappa)$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
     \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
-    \begin{LaTeXenumerate}
+    \begin{enumerate}
         \item \textit{Encryption:} The attacker chooses a value $x$ and computes an encryption of $x$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(x)$.
@@
         \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
-    \end{LaTeXenumerate} 
+    \end{enumerate} 
     \item[Challenge] Next, the attacker chooses an instance $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for the instance $t^*$, and no compromise queries, are made for the duration of the game.
@@
     \end{equation*} 
-\end{LaTeXdescription}
+\end{description}
 
@@
 That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case, \cite{joyeScalableSchemePrivacyPreserving2013}).
-\begin{proof}
+\begin{pf}
     Consider adversary $\mathcal{A}$ playing the LCAO game.
 The following is a construction of an adversary $\mathcal{A}'$ playing the AO game \cite{shiPrivacyPreservingAggregationTimeSeries2011} against a challenger $\mathcal{C}$ using the Joye-Libert aggregation scheme.
-    \begin{LaTeXdescription}
+    \begin{description}
         \item[Setup] When receiving $N$ and $H$ as public parameters from $\mathcal{C}$, choose an $m>1$ and give public parameter $H$, number of weights $m$, and $pk_0=N$ to $\mathcal{A}$.
         \item[Queries] Handle queries from $\mathcal{A}$:
-        \begin{LaTeXdescription}
+        \begin{description}
             \item[\textit{Weight Query}] When $\mathcal{A}$ submits a weight query $t$, choose weights $\omega^{(t)}_j,\,j\in\{1,\dots,m\}$ and random values $\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$, and return encryptions
@@
             \item[\textit{Compromise Query}] When $\mathcal{A}$ submits compromise query $i$, make the same compromise query $i$ to $\mathcal{C}$, and return the recieved secret key $sk_i$ to $\mathcal{A}$.
-        \end{LaTeXdescription}
+        \end{description}
         \item[Challenge] When $\mathcal{A}$ submits challenge series
@@
         \item[Guess] When $\mathcal{A}$ makes guess $b'$, make the same guess $b'$ to~$\mathcal{C}$.
-    \end{LaTeXdescription}
+    \end{description}
 
@@
 Lastly, the function $H$ used by our scheme is treated as a random oracle in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.
-\end{proof}
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-\bibliographystyle{IEEEtranBST/IEEEtran}
-\bibliography{BibTeX/PrivateEIFLocalisation}
-
-% 
-% 888888b.  8888888 .d88888b.   .d8888b.  
-% 888  "88b   888  d88P" "Y88b d88P  Y88b 
-% 888  .88P   888  888     888 Y88b.      
-% 8888888K.   888  888     888  "Y888b.   
-% 888  "Y88b  888  888     888     "Y88b. 
-% 888    888  888  888     888       "888 
-% 888   d88P  888  Y88b. .d88P Y88b  d88P 
-% 8888888P" 8888888 "Y88888P"   "Y8888P"  
-%                                         
-%                                         
-%                                         
-%
-
-\vspace{-1\baselineskip}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
-received his software engineering diploma in 2018 at the University of Melbourne, Australia.
-In 2019, he began work as a researcher at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany, and since 2021, he has been pursuing a Ph.D.
-at the Autonomous Multisensor Systems (AMS) group, Otto von Guericke University, Germany.
-His research interests include encrypted and privacy-preserving signal processing, focusing on state estimation, sensor fusion, and distributed localisation.
-\end{IEEEbiography}
-
-\vspace{-1\baselineskip}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
-is a professor of Computer Science at the Otto von Guericke University Magdeburg in Germany and head of the Autonomous Multisensor Systems (AMS) group.
-He received his diploma in computer science from the Karlsruhe Institute of Technology (KIT), Germany, in 2009.
-Afterward, he obtained his Ph.D.
-in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
-His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
-\end{IEEEbiography}
-
-\vspace{-1\baselineskip}
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}
-is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor–Actuator-Systems Laboratory (ISAS).
-He obtained his Ph.D.
-degree in 1997 and his habilitation degree in 2003, both in Electrical Engineering from the Technical University in Munich, Germany.
-His research interests are in the areas of information fusion, nonlinear state estimation, stochastic modeling, system identification, and control with a strong emphasis on theory-driven approaches based on stochastic system theory and uncertainty models.
-He is author and coauthor of more than 500 publications in various high-ranking journals and conferences and an IEEE Fellow.
-\end{IEEEbiography}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
+\end{pf}
+
 \end{document}

### 2021-08-10 main.tex
One more proof read, couple of tiny changes

@@
 This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively.
-In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in such signal processing or localisation tasks.
+In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks.
 In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations.
@@
 We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
-The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its formal security.
+The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security.
 To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.
@@
     \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
-Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose a the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
+Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
 Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
@@
 for sensors $i\in\{1,\dots,n\}$.
-After then converting the updated information vector and matrix back to state estimate $\hat{\vec{x}}_{k|k}$ and estimate covariance $\mat{P}_{k|k}$, the filter's prediction step can be computed by the navigator locally, using any suitable filter for the known system model \eqref{eqn:system_model}.
+After converting the updated information vector and matrix back to state estimate $\hat{\vec{x}}_{k|k}$ and estimate covariance $\mat{P}_{k|k}$, the filter's prediction step can be computed by the navigator locally using any suitable filter for the known system model \eqref{eqn:system_model}.
 
@@
 \end{equation}
-which now captures all the private state information in $\hat{\vec{x}}_{k|k-1}$ required at the sensors.
+which capture all of the private state information in $\hat{\vec{x}}_{k|k-1}$ required at the sensors.
 The corresponding EIF update steps \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update} then become

### 2021-08-16 main.tex
Included all text changes from the Automatica branch to this branch in prep for TAC resubmission (which is now approved)

--- 2021-07-05 main.tex
@@
 \IEEEPARstart{L}{ocalisation} methods in distributed sensor environments have long been an active topic of research \cite{pierceIntroductionLoran1946,ligginsDistributedDataFusion2012,liContributedReviewSourcelocalization2016} and have characterised many advancements of Kalman and Bayesian estimation theory \cite{mutambaraDecentralizedEstimationControl1998}.
-In particular, range-based localisation methods, including signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic ranges \cite{beutlerNewNonlinearFiltering2004} and ultra wideband ranges \cite{geziciLocalizationUltraWidebandRadios2005}, have found large application due to the prevalence of suitable sensors.
+In particular, range-based localisation methods, including signal strength measurements \cite{wangConvexCombinationSource2018,heRangeFreeLocalizationSchemes2003}, acoustic ranges \cite{beutlerNewNonlinearFiltering2004} and ultra-wideband ranges \cite{geziciLocalizationUltraWidebandRadios2005}, have found large application due to the prevalence of suitable sensors.
 In most cases, these localisation methods require the gathering of measurements centrally, where an estimate of location can be computed.
-With recent developments in distributed and cloud computing, uses of wireless and public communication channels for data transfer have becoming widespread, and the additional requirements of data privacy and state secrecy have become particularly relevant \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
+With recent developments in distributed and cloud computing, uses of wireless and public communication channels for data transfer have become widespread, and the additional requirements of data privacy and state secrecy have become particularly relevant \cite{brennerSecretProgramExecution2011,renSecurityChallengesPublic2012}.
 
@@
     \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\shrtdots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), a^{(t)}_{i,1},\shrtdots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\shrtdots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}(\omega_1^{(t)}),\dots,\mathcal{E}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination denoted $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
 \end{LaTeXdescription}
@@
             &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \pmod{N^2}
+            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
         \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \pmod{N^2}\,,
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \!\!\pmod{N^2}\,,
     \end{align*}
@@
 
-\vspace{-1\baselineskip}
+%\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
@@
 
-\vspace{-1\baselineskip}
+%\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
@@
 
-\vspace{-1\baselineskip}
+%\vspace{-1\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}

### 2022-02-01 reviews/TAC_feb_2022/COMBINED REVIEWS AND EDITOR RESPONSE.txt
TAC conditional accept received. Added reviewer comments Added new author's response document (possibly to be renamed to document of changes) Added files for creating latexdiff between accepted and final submission

COMBINED REVIEWS AND EDITOR RESPONSE

--------------------------------------------------------------------------------
EDITOR
--------------------------------------------------------------------------------

Dear Dr. Ristic:

Your paper “Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies”, Number 21-1548, that you submitted for possible publication as a Regular Paper in the IEEE Transactions on Automatic Control has now been reviewed.  Copies of the reviews are enclosed.

I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.

The reviewers would like the authors to clarify some concerns such as the assumption of the EKF design, private sensor variance information, and research motivation and challenge, and so forth.

As soon as you have completed these modifications, please submit your revised paper. Please include a detailed statement describing the changes in the manuscript. The revised paper must be received within 5 weeks of the date of this letter.

Please log-in, click on the "Author" link at the bottom of your access page, and upload your revised paper under the SAME reference number.

I look forward to receiving your revised paper.

Sincerely,

Dr. Zhiwei Gao
Associate Editor
zhiwei.gao@northumbria.ac.uk, zhiwegac@gmail.com Northumbria University

--------------------------------------------------------------------------------
REVIEWER 1
--------------------------------------------------------------------------------

Thank you for updating the manuscript and most of the concerns have
been addressed well in the response letter. However, there is one
problem still confused me. The authors claimed that the Gaussian
assumption has been removed in the revised version, however, the EKF
(EIF) was still used for prediction (Eqs. 26-27). Basically, the EKF is
based on the Gaussian assumption and the prediction is obtained in the
sense of mean value. Then, the non-Gaussian dynamics would affect the
prediction performance using EKF if the Gaussian assumption is removed.
My point is 1) if the assumption is removed, please explain the
non-Gaussian influence from the EKF or 2) if the Gaussian assumption
remains in the manuscript, please explain from the noise comes from in
physics sense.

--------------------------------------------------------------------------------
REVIEWER 2
--------------------------------------------------------------------------------

The authors have significantly improved the readability of the paper.
The contribution is significant enough for privacy preserving state
estimation. However, this reviewer still have few comments:
1- It could be interesting to comment why sensor variance is a private
information. Why is it crucial to preserve it if measurements are
already protected?

2- In the sentence 'homomorphic encryption is used to make
time-independent model-free location estimates where an estimator does
not learn sensor measurements or locations.; Shouldn't be 'cannot
learn'?

3- In problem statement 'we consider the context of privacy-preserving
range sensor navigation, where we want no sensor to learn information
about the navigator or other sensors beyond their local measurements,
and the navigator to learn no information about individual sensors
beyond its location estimate.', please specify type of information.

4- Indistinguishable weights: what would happen if the sensor learns
navigator weights?

5- Fix the following sentence: 'If an attacker compromises the
navigator, they have control over the weights,'

6- Define IND-CPA.

7- Simulation: The authors have found that 1.7 s are needed for each
computation step, is that compatible with real-time operation?

8- Can you comment why quantization noise, involved in the
encryption-decryption schemes, isn't taken into account in the filter
equations?

--------------------------------------------------------------------------------
REVIEWER 3
--------------------------------------------------------------------------------

Comments:
This paper proposes a novel distributed localisation method in the
presence of range-only sensors, which preserves both navigator and
sensor privacies. The major contribution of this paper is that a novel
private linear combination aggregation scheme is proposed, and based on
that, a modified extended Kalman filter is also derived. Some comments
are given as follows:

1.In this paper, the full names of some abbreviations are not given.
For example, in Section I, page 1, left column, “AES”and “RSA”, and in
Section I, page 1, right column, “pWSAc” and “pWSAh”.

2.The authors should elaborate the advantages and disadvantages of the
existing typical cryptographic secrecy scheme and the motivation for
proposing private linear combination aggregation scheme in this paper.

3.Some symbols are reused. For example, In Section I, Notation,
“timestep k” and “will denote encryption and decryption with key k”.

4.The authors need to present theoretical computational complexity of
the proposed method.

5.The authors should state how to measure the performance of the
private linear combination aggregation scheme proposed in this paper.

6.In practical engineering application, how to balance the relationship
between key sizes and computation.

### 2022-02-01 authors_responses/conditional_accept/authors_response.tex
TAC conditional accept received. Added reviewer comments Added new author's response document (possibly to be renamed to document of changes) Added files for creating latexdiff between accepted and final submission

--- 2021-06-25 authors_responses/first_tac_rejection/authors_response.tex
@@
 
-\title{\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies\\\normalfont(Formerly: Privacy-Preserving Localization Using Private Linear-Combination Aggregation)}
-\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 20-2108}
+\title{\boldmath Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies}
+\subtitle{Response to Reviewers' Comments - Submission IEEE-TAC 21-1548}
 \author{Marko Ristic\and Benjamin Noack\and Uwe D. Hanebeck}
@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{Based on the reviews, it is our decision that the paper cannot be accepted for publication in the Transactions in its present form.
+\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.}
 
-The reviewers feel the paper interesting, which many include publishable materials.
-On the other hand, the reviewers feel the paper should be reorganized by shortening the length (e.g.
-introduction etc.), and highlight the novelty and contribution.
-Also the relevance of the paper to the journal should be clarified.}
+My response.
 
-Thank you for the response.
-We have undertaken a large overhaul of the manuscript in order to accommodate the suggested changes of the reviewers.
-The work has been shortened by four pages, the introduction shortened to a single page and the novelty of our method clearly stated within it.
-We state the estimation problem tackled, namely, a modified EKF estimator for range-only sensor localisation with specific security requirements, and its benefits over existing and comparable approaches.
-We believe that the clearer novelty and contribution also better clarify the relevance of the paper to the TAC journal.
+\item \reviewtext{The reviewers would like the authors to clarify some concerns such as the assumption of the EKF design, private sensor variance information, and research motivation and challenge, and so forth.}
 
-\item \reviewtext{We encourage you to examine carefully the comments of the enclosed reviews and to consider making a major revision of the paper, which can be resubmitted as a Technical Note, to the Transactions on Automatic Control.
-If you do submit a revised version of the paper as a Technical Note, you should take care that the paper is reduced to no
-more than 8 double-column pages using IEEE template.}
-
-After a large revision of our manuscript, including the suggested additions and modifications from the reviewers, we have rearranged and greatly shortened the work (in particular the introduction and cryptography sections, but all sections have been partially modified to be clearer).
-Due to the novelty of the tackled problem and the cryptographically backed solution, the manuscript, albeit four pages shorter, is still too long for submission as a Technical Note, and we would like to resubmit the work as a full paper again.
-We hope that this reasoning is made clearer in the newly revised and rearranged manuscript.
-Below, we have detailed how each of the reviewer comments has been taken into account when revising the work.
+My response.
 
@@
 
-\section*{Response to the Comments of Reviewer 1 (222511)}
+\section*{Response to the Comments of Reviewer 1 (242571)}
 \def\thesection{R1}
 \begin{rebuttal}
-\item \reviewtext{This paper concerns the localization problem under privacy constraints.
-Cryptographic schemes have been devised by the authors to achieve some privacy requirements.
-The contribution is significant enough and the paper is well written but hard to understand for a usual reader of IEEE TAC due to sections with cryptographic background.}
+\item \reviewtext{Thank you for updating the manuscript and most of the concerns have been addressed well in the response letter.}
 
-We thank the reviewer for their comment on our contribution and are sorry that the work was not made easier to understand.
-We have rearranged the paper to make both the problem tackled and the solution presented easier to follow and more concise.
-Additionally, we have greatly reduced the amount of cryptographic background presented, and hope that these changes make the work much easier to follow for the usual target audience of IEEE TAC.
+My response.
 
-\item \reviewtext{As a TAC paper, performance analysis in terms of estimation accuracy was expected but is actually missing.}
+\item \reviewtext{However, there is one problem still confused me.
+The authors claimed that the Gaussian assumption has been removed in the revised version, however, the EKF (EIF) was still used for prediction (Eqs.
+26-27).
+Basically, the EKF is based on the Gaussian assumption and the prediction is obtained in the sense of mean value.
+Then, the non-Gaussian dynamics would affect the prediction performance using EKF if the Gaussian assumption is removed.
+My point is 1) if the assumption is removed, please explain the non-Gaussian influence from the EKF or 2) if the Gaussian assumption remains in the manuscript, please explain from the noise comes from in physics sense.}
 
-We regret that the method of analysis for our approach was not made clearer.
-As the proposed method we present is inherently a modified EKF, we directly compare the estimation accuracy of our method to the industry standard EKF (EIF reformulation in our case).
-To make this clearer, we have rewritten the results section to portray this evaluation better and changed the results figure to be far more legible.
-Direct comparisons between the EIF and our method are now made for each simulation considered, and the estimation error (accuracy of the filters) can be seen much more clearly.
-We hope this makes the evaluation of the presented method easier to understand.
-
-\item \reviewtext{This reviewer wonders if IEEE TAC is well adapted for an efficient exposition of the authors' findings.}
-
-We understand that the state of the initial submission was not as well suited to the TAC journal as could be desired and thank the reviewer for pointing this out.
-As cryptography is becoming more prevalent in the context of control and estimation literature, existing literature published at TAC and concerning cryptographic constructs (for example, ``Cloud-based quadratic optimization with partially homomorphic encryption'' by Andreea Alexandru et al.), has been used as a reference during our revision.
-For the resubmission, we have greatly reduced the cryptographic components of the work and stated our contribution and its novelty more clearly to clarify the suitability of the proposed estimation method to the TAC journal.
-We will also consider some of the denser cryptographic definitions presented for an alternative submission elsewhere.
-
-\item \reviewtext{In the framework of a Control theory paper, cryptographic notions would be kept as minimum as possible in the main body of the paper or moved to Appendices.}
-
-As above, we regret that the quantity of presented cryptographic content was overwhelming and have greatly modified the work to make it more suitable for the journal.
-Much of the cryptographic discussion has been removed and the remaining necessary novel notions have been put in the appendix.
+My response.
 
@@
 
-\section*{Response to the Comments of Reviewer 2 (222527)}
+\section*{Response to the Comments of Reviewer 2 (242573)}
 \def\thesection{R2}
 \begin{rebuttal}
-\item \reviewtext{This paper deals with a suitable notion of linear-combination aggregation encryption and provides a cryptographically secure instance applied to a filter with range-sensor measurements.
-This approach keeps navigator location, sensor's location and sensors' measurements private during navigation.
+\item \reviewtext{The authors have significantly improved the readability of the paper. The contribution is significant enough for privacy preserving state estimation.}
 
-The proposed approach is interesting and the results are technically sound. The literature review is OK. But the organization of paper and its length make its reading difficult.
+My response.
 
-The reviewer encourages the authors to reorganize the article by greatly shortening it and to highlight the novelty.}
+\item \reviewtext{However, this reviewer still have few comments:
 
-We're happy to hear that the results were found interesting and regret that the length and organisation have made the manuscript hard to read.
-We have heavily reorganised and rewritten parts of the work to make it easier to read, including shortening the work by four pages.
-We hope that the flow of information is now easier to follow and that the method is more concisely described.
+1- It could be interesting to comment why sensor variance is a private information. Why is it crucial to preserve it if measurements are already protected?}
 
-\item \reviewtext{Some additional comments are given below:
+My response.
 
--Introduction (2 pages) is too long and does not focus on the main ideas of the paper. There are too many reminders of classical notions.}
+\item \reviewtext{2- In the sentence 'homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations.; Shouldn't be 'cannot learn'?}
 
-We agree with the reviewer that the introduction could be made shorter.
-We have now significantly reduced the length of the introduction and removed a lot of the cryptographic reminders throughout the work.
+My response.
 
-\item \reviewtext{-Equation (3): i from 1 to n must be added.}
+\item \reviewtext{3- In problem statement 'we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.', please specify type of information.}
 
-Thank you for pointing this out, this has now been added to the manuscript.
+My response.
 
-\item \reviewtext{-The actual computation steps are in fact scattered all over the paper, in several sections.
-In the current version, the reader has to collect all the scattered pieces to come out with the approach.
-I would therefore, strongly recommend the authors to summarize all the steps of the approach gathered by the end of the paper, to help the reader directly use and implement the algorithm.}
+\item \reviewtext{4- Indistinguishable weights: what would happen if the sensor learns navigator weights?}
 
-Due to the number of components in the proposed method (encoding, encryption and estimation), we aimed to present the algorithm pseudocode as the summary of the method, and regret that this was not made clearer.
-We have rewritten and reorganised the localisation section and have tried to make a pseudocode summary, and its purpose, clearer.
-We hope that the updated manuscript now presents a better overall summary after all the components are presented.
+My response.
 
-\item \reviewtext{-Page 10, Equation (36), Right part of Equation: d is from 0 to D}
+\item \reviewtext{5- Fix the following sentence: 'If an attacker compromises the navigator, they have control over the weights,'}
 
-This was indeed missing. After shortening the paper, this subsection was removed and the equation is no longer there, but we thank you for pointing it out regardless.
+My response.
 
-\item \reviewtext{-Inequality (50) must be clarified,}
+\item \reviewtext{6- Define IND-CPA.}
 
-We apologies for not making this clearer. The section has been modified and the reason for adding standard deviations to give a conservative estimate has been rewritten and clarified.
+My response.
 
-\item \reviewtext{-Algorithm 1, steps 2/3/4, it is F\_\{k-1\},}
+\item \reviewtext{7- Simulation: The authors have found that 1.7 s are needed for each
+computation step, is that compatible with real-time operation?}
 
-Thank you for pointing this out.
-This was due to an error in notation from a previous section which gave incorrect timestep subscripts to the EKF prediction equations.
-The revised manuscript no longer imposes using the EKF for the prediction step of the filter and these equations have been removed.
+My response.
 
-\item \reviewtext{-Section VIII-some explanations on the process model must be added. Figure 6 is too small; it is difficult to distinguish the different lines.}
+\item \reviewtext{8- Can you comment why quantization noise, involved in the encryption-decryption schemes, isn't taken into account in the filter equations?}
 
-Process model information was indeed missing and the figure hard to read.
-The section has been modified to include details of the models used in the simulation and the figure modified to display comparisons between the privacy-preserving filter and the EIF separately for each considered sensor layout.
-We hope that the comparison and the drawn conclusions are now much easier to follow.
+My response.
 
@@
 
-\section*{Response to the Comments of Reviewer 3 (229727)}
+\section*{Response to the Comments of Reviewer 3 (246951)}
 \def\thesection{R3}
 \begin{rebuttal}
-\item \reviewtext{This paper presented a theoretical framework for privacy-preserving localisation combining the encryption scheme and filtering.
-In particular, the private linear-combination aggregation has been adopted in the presented framework.
-Basically, the contribution of the paper is clearly indicated with an interesting and important topic.
-However, some technical problems need to be further clarified.
-Therefore, a major revision is necessary in my opinion.}
+\item \reviewtext{Comments:
 
-We're glad to hear that the contribution was found interesting and important.
-We have made a very large revision of the work, including rewriting, reorganising and shortening the text to make the presented information easier to follow.
+This paper proposes a novel distributed localisation method in the presence of range-only sensors, which preserves both navigator and sensor privacies.
+The major contribution of this paper is that a novel private linear combination aggregation scheme is proposed, and based on that, a modified extended Kalman filter is also derived.
+Some comments are given as follows:
 
-\item \reviewtext{1) Is any filtering method can be integrated into the presented framework? If so, can we replace the method via numerical approach such as particle filter.}
+1.In this paper, the full names of some abbreviations are not given. For example, in Section I, page 1, left column, “AES”and “RSA”, and in Section I, page 1, right column, “pWSAc” and “pWSAh”.}
 
-The method proposed achieves the desired security properties by modifying the range-only measurement model and rearranging the terms in the Extended Information Filter (EIF) during the filter update step.
-With this method, using the EIF is crucial for reformulating participant communication to a protocol that can use the introduced encryption scheme, and thus meet the security properties.
-It may be possible to rearrange a particle filter to suit some other type of encryption scheme, but to the best of our knowledge, this does not yet exist.
+My response.
 
-However, during only the prediction step of the filter (performed locally by the navigator), it is possible to use any filter, including a particle filter.
-We have now relaxed the requirements of the system model and no specify the prediction equations of EKF specifically.
+\item \reviewtext{2.The authors should elaborate the advantages and disadvantages of the existing typical cryptographic secrecy scheme and the motivation for proposing private linear combination aggregation scheme in this paper.}
 
-\item \reviewtext{2) How does the linear combination reflect the dynamics of the investigated system in Eq.(2)?}
+My response.
 
-The linear combination aggregation scheme does not reflect or affect the dynamics of the system model given in ($2$).
-The scheme is only used to encrypt the required communication during the computation of the EIF update step.
-The proposed filter itself requires a modified measurement function to use linear combination aggregation, which is where differences to the standard EIF update are introduced.
-As above, we have removed the restrictions on the system model and hope that this makes its role in the presented filter clearer.
+\item \reviewtext{3.Some symbols are reused. For example, In Section I, Notation, “timestep k” and “will denote encryption and decryption with key k”.}
 
-\item \reviewtext{3) Why is the noise of the system Gaussian? In Eq.(2), function f() is known then what is the physical meaning of the Gaussian process noise?}
+My response.
 
-Thank you for pointing this out.
-It is correct that the Gaussianity of the system noise was not required by our approach, nor was it required for the locally computed prediction step of the filter.
-This assumption is among the restrictions on the system model which have now been removed from the manuscript.
+\item \reviewtext{4.The authors need to present theoretical computational complexity of the proposed method.}
 
-\item \reviewtext{4) In the paper, the noise is depended on covariance matrix \$Q\$ which is also particularly used in Algroithm 1, however, in practice, Q is unmeasurable and unknown.
-How to estimate the value of Q in terms of performance guarantee.}
+My response.
 
-As the requirements of the system model have been relaxed in the revised manuscript, the second moment of the system noise, $\mat{Q}$, may no longer be needed if using a non-linearising filter for the prediction step of the algorithm.
-However, estimating $\mat{Q}$ is a standard requirement when using filters such as the KF or EKF (see, for example, ``Bayesian Estimation and Tracking: A Practical Guide'' by Anton J.
-Huag) and has been computed when evaluating the proposed filter through simulation.
-This can be done in various ways specific to the system being modelled and is beyond the scope of this work.
+\item \reviewtext{5.The authors should state how to measure the performance of the private linear combination aggregation scheme proposed in this paper.}
 
-\item \reviewtext{5) The experimental results are limited.
-The comparison is essential to validate the performance of the presented algorithm.
-What about using the existing filtering method to demonstrate the various encryption scheme?}
+My response.
 
-We agree that the results section was lacking and have rewritten it to try and make the evaluation clearer.
-To validate the accuracy of the algorithm, it has been compared to the industry standard EKF (reformulated as the EIF) and the comparison figure changed to make it clearer that the proposed filter performs very similarly.
-The computational performance is more difficult to compare.
-Comparison with a different encryption scheme would require another scheme meeting LCAO (required to meet the security requirements), but no such scheme exists (we define the novel LCAO notion and present a scheme that meets it in the manuscript).
-Future work is being done on a similarly modified EIF which can use a scheme meeting Aggregator Oblivousness (AO) instead, and that could be used for such a comparison, but is beyond the scope of this work.
+\item \reviewtext{6.In practical engineering application, how to balance the relationship between key sizes and computation.}
 
-\item \reviewtext{6) There are some typos in the manuscript please correct them, for example, page 1 Notation, '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ the vector norm' should be '\$\textbackslash left\textbackslash\textbar\textbackslash underline a\textbackslash right\textbackslash\textbar\$ is the vector norm' etc.}
-
-The sentence has now been corrected, along with others throughout the work.
+My response.
 
@@
 
-% \includepdf[pages=-]{diff}
+\includepdf[pages=-]{../../diff.pdf}
 

### 2022-02-01 main_conditional_accept_022022.tex
TAC conditional accept received. Added reviewer comments Added new author's response document (possibly to be renamed to document of changes) Added files for creating latexdiff between accepted and final submission

--- 2021-08-16 main.tex
@@
 Distributed state estimation and localisation methods have become increasingly popular with the rise of ubiquitous computing, and have led naturally to an increased concern regarding data and estimation privacy.
-Traditional distributed sensor navigation methods typically involve the leakage of sensor or navigator information by communicating measurements or estimates and thus do not preserve participants’ privacy.
+Traditional distributed sensor navigation methods typically involve the leakage of sensor or navigator information by communicating measurements or estimates and thus do not preserve participants' privacy.
 The existing approaches that do provide such guarantees, fail to address sensor and navigator privacy in the common application of model-based range-only estimation, consequently forfeiting broad applicability.
@@
 \begin{LaTeXdescription}
-    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
+    \item[$\mathsf{Setup}(\kappa)$] On input parameter $\kappa$, generate two equal-length, sufficiently large, primes $p$ and $q$, and compute $N=pq$.
 Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.

### 2022-03-02 authors_responses/conditional_accept/authors_response.tex
Started on final author's response

@@
 
-We would like to thank you all for your thorough and helpful reviews.
-In this letter, we will describe how editor and reviewer comments, questions and suggestions have been addressed.
+Thank you all for your detailed reviews and for finding the manuscript suitable for publication.
+In this letter, we will address the remaining editor and reviewer comments and describe any changes made to the manuscript.
 Throughout this response, reviewers' comments are in \reviewtext{blue}.
@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.}
+\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.
+The reviewers would like the authors to clarify some concerns such as the assumption of the EKF design, private sensor variance information, and research motivation and challenge, and so forth.}
 
-My response.
-
-\item \reviewtext{The reviewers would like the authors to clarify some concerns such as the assumption of the EKF design, private sensor variance information, and research motivation and challenge, and so forth.}
-
-My response.
+We are glad to hear the paper is acceptable for publication and have responded to each of the reviewer comments below, hoping to clarify all remaining concerns.
 
@@
 
-My response.
+We are happy to hear this is the case, thank you.
 
@@
 
-My response.
+We regret that there was some confusion about the prediction step of the presented localisation algorithm.
+Equations $26$-$27$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$.
+The Gaussian assumption has indeed been removed from the system model, and obtaining the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$ can be computed using any local filter (linearising or otherwise) as mentioned in Section V.
+The Gaussian assumption that remains is only present in the measurement model, as is a commonly done to simplify the modelling of sensors, and the non-linear distance-measurement function $h_i$ is linearlised by an appropriate EKF filter for the localisation update step only.
+We hope this clarifies equations $26$-$27$ and the use of the EKF.
 
@@
 
-My response.
+We thank you for the comment and are glad that the contribution is found significant.
 

### 2022-03-03 authors_responses/conditional_accept/authors_response.tex
Continued on response. Few comments added for responses to reviewer two which are not yet written up nicely. Diff not yet updated

@@
 
-My response.
+This is a good question that had not been elaborated in the work.
+The key reason that any sensor-specific information (such as its measurement noise variance) is considered private is that it may hold identifying data if analysed by an adversary.
+For example, a particular model of sensor may be identified from its measurement noise variance, enabling a targeted attack (cyber or physical) against that sensor.
+We have made a change to the introduction section to clarify this reasoning.
 
@@
 
-My response.
+Thank you for pointing this out, we have added the change to the manuscript.
 
@@
 My response.
+abstraction from cryptography to capture the fact nothing is can be learnt from the encryptions
 
@@
 My response.
+Continuation from above.
+Since nothing is to be learnt, then any information from the navigator involved in the localisation must remain private.
+In practice, as is later evident from the concrete use of the scheme, the weights correspond to the navigator estimate which we want to hide from sensors
 
@@
 My response.
+Referenced on first use of the term. Was removed from appendix after previous reviews as fewer cryptographic background was requested by reviewers.
 

### 2022-03-03 main.tex
Added missing hyphen
Continued on response. Few comments added for responses to reviewer two which are not yet written up nicely. Diff not yet updated

@@
 In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks.
-In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations.
+In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations.
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
@@
 
-Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements and locations private while the navigator keeps its estimates private.
+Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private.
 We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
@@
 We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations.
-While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying location or hardware details to remain unknown to the other present stations and the navigator.
+While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other present stations and the navigator.
 Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.
@@
 In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
-The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the scheme in the context of range-only navigation.
+The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the encryption in the context of range-only navigation.
 

### 2022-03-07 authors_responses/conditional_accept/authors_response.tex
Added a few more responses to reviewer 2 (most responses required no or little changes to the the text)

@@
 
-My response.
-abstraction from cryptography to capture the fact nothing is can be learnt from the encryptions
+We regret that this was not clear to the reviewer.
+We refer to leakable content as arbitrary information to stress that \textit{nothing} can be leart.
+That is, neither the information we can predict the importance of (such as state estimates or sensor locations), nor that for which we cannot.
+This is common in cryptography, as no assumptions on the methods or intentions of adversaries can be made.
+We have updated the sentence to try and make this clearer and note that examples of information that should not be learnt (state estimates and sensor locations) have been given in the preceeding section.
 
@@
 
-My response.
-Continuation from above.
-Since nothing is to be learnt, then any information from the navigator involved in the localisation must remain private.
-In practice, as is later evident from the concrete use of the scheme, the weights correspond to the navigator estimate which we want to hide from sensors
+This relates to the abstraction from the previous response.
+Since a meaningful cryptographic definition cannot make assumptions about what leakable information might be useful, we cannot state what would happen.
+As the weights originate from the navigator and we do not want sensors to learn any information from the navigator, we can say that no new information should be leart from the weights (and therefore require cryptographic indistinguishabilty of weights).
+In the concrete scheme presented later, it can be seen that the weights correspond to elements of the navigator's state estimate vector, which is stated as an example of information that must remain private to the navigator.
+We hope this makes the meaning and reasoning of indistinguishability clearer.
 
@@
 
-My response.
+Unfortunately, we are unable to find an issue with the stated sentence and have asked additional native English speakers that have also agreed that the sentence looks correct.
+In case the use of ``they'' (rather than ``he'' or ``she'') is being referred to, it is the formal grammatical pronoun for a person when gender is not specified.
 
@@
 
-My response.
-Referenced on first use of the term. Was removed from appendix after previous reviews as fewer cryptographic background was requested by reviewers.
+We are sorry for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]).
+The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information.
+We hope this clears up why the definition is only referenced.
 
@@
 
-My response.
+We're sorry this wan't clearer.
+
+\dots quantisation noise is negligible when the quantised integer bit size is larger than the bit size of used floating-point numbers
 

### 2022-03-07 main.tex
Added a few more responses to reviewer 2 (most responses required no or little changes to the the text)

@@
 \section{Problem Statement} \label{sec:problem_statement}
-In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.
+In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn any information about the navigator or other sensors beyond their local measurements, and the navigator not to learn any information about individual sensors beyond its location estimate.
 The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the encryption in the context of range-only navigation.
@@
 If an attacker compromises the navigator, they have control over the weights, and therefore the leakage function.
-We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learned by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
+We note that in the leakage function above, $\sum^n_{i=1}\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j$, an individual sum weighted by the same weight may be learnt by an attacker, \textit{e.g.}, $\sum^n_{i=1}a^{(t)}_{i,1}$ given weights $(1,0,\dots,0)$, but that individual sensor values $a^{(t)}_{i,j}$ remain private due to the assumption of a consistent broadcast.
 \end{remark}

### 2022-03-08 authors_responses/conditional_accept/authors_response.tex
Several more responses to reviewer 2 and 3 and accompanying changes to the paper

@@
 The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information.
-We hope this clears up why the definition is only referenced.
+For this reason, we have left the definition only referenced and hope this is found satisfactory.
 
@@
 
-My response.
+It is hard to say explicitly whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet).
+In addition, a further optimised implementation executed on more powerful hardware could result in significantly faster runtimes.
+
+\textit{+changes made} time was used primarily as a comparitive measure in key sizes.
 
@@
 We're sorry this wan't clearer.
-
-\dots quantisation noise is negligible when the quantised integer bit size is larger than the bit size of used floating-point numbers
+The quantisation noise is captured by the precision parameter $\phi$, which results in less noise when the parameter is large but is upper-bounded by $(20)$.
+Here, it is noted that when $M=N$, the upper bound can be practically ignored since $\phi$ can be chosen to have a bit-length much larger than a floating-point number, making any introduced encoding noise negligible.
+When pseudocode is presented in subsection V.C, $M=N$ is chosen, and in the results section VI, $\phi=2^{32}$ leads to a negligible difference in performance between an unencrypted (and unquantised) EIF and the presented quantised and encrypted one.
+We have udpated subsection V.C to make this clearer and hope that explains why there is no need for the quantisation noise to be considered in the filter.
 
@@
 
-My response.
+We apologise for having missed these, the full names have now been added.
 
@@
 
-My response.
+Thank you for noticing this. We have updated the notation section and other places throughout the text to remove the found errors.
 
@@
 
-My response.
+In practice, chosen cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key.
+For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must not be leaked for the foreseeable future.
+Since cryptographic \textit{guarantees} are required, computation is not directly considered when choosing key sizes.
+However, in cases where computation makes desired cryptograhpic guarantees infeasible, shorter required secrecy or more frequent key exchanges can be considered to reduce key sizes and computation times.
+
+\textit{+changes made}
 

### 2022-03-08 main.tex
Several more responses to reviewer 2 and 3 and accompanying changes to the paper

@@
 Typical cryptographic secrecy involves hiding all transferred data such that external parties in the communication network learn no new information from acquired encryptions.
-This can be achieved with common symmetric and public-key encryption scheme such as AES \cite{gueronIntelAdvancedEncryption2010} and RSA \cite{rivestMethodObtainingDigital1978}, respectively.
+This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively.
 In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks.
@@
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
-In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, centralised and hidden weighted sum aggregations, pWSAc and pWSAh, are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised and hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
 
@@
 $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences.
-When estimating a state, notation $\hat{\vec{x}}_{k|l}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including $l$.
-When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context.
-$\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group.
+When estimating a state, notation $\hat{\vec{x}}_{k|e}$ will denote an estimate of $\vec{x}$ at timestep $k$ given measurements from timesteps up to and including timestep $e$.
+When discussing cryptography, $\mathcal{E}_{sk}(\cdot)$ and $\mathcal{D}_{sk}(\cdot)$ will denote encryption and decryption with key $sk$, respectively, with $sk$ ommited when inferrable from context.
+$\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group.
 $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
@@
 \end{equation}
-where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$.
+where $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(\psi) = \frac{\psi-1}{N}$.
 
@@
 \begin{equation}
-    \mathbb{Q}_{M,\phi} = \left\{q \,\middle|\, \phi q \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi q < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
-\end{equation}
-and we can quantize any real number $a$ by taking the nearest rational $q \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{q\in\mathbb{Q}_{M,\phi}} |a-q|$.
+    \mathbb{Q}_{M,\phi} = \left\{o \,\middle|\, \phi o \in \mathbb{N} \wedge -\left\lfloor\frac{M}{2}\right\rfloor \leq \phi o < \left\lfloor\frac{M}{2}\right\rfloor \right\}\,,
+\end{equation}
+and we can quantize any real number $a$ by taking the nearest rational $o \in \mathbb{Q}_{M,\phi}$, that is, $\argmin_{o\in\mathbb{Q}_{M,\phi}} |a-o|$.
 In this form, mapping rationals $\mathbb{Q}_{M,\phi}$ to an encryption range $\mathbb{Z}_N$ is achieved by choosing $M=N$ and handling negatives by modulo arithmetic.
 Additionally, we note that the Q number format requires a precision factor $\phi$ to be removed after each encoded multiplication.
-This is captured by a third parameter $d$; the number of precision factors present in encodings.
+This is captured by a third parameter $d$; the number of additional precision factors present in encodings.
 
@@
 \end{equation}
-In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$.
+In practice, $N$ is typically very large ($N>2^{1024}$) and this condition can be ignored when $M=N$, as $\phi$ can be made sufficiently large to make quantisation errors negligible.
 
@@
     \end{equation}
-    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(u) = \frac{u-1}{N}$. The correctness of the aggregation can be seen from
+    with $\lambda = \mathsf{lcm}(p-1, q-1)$ and $L(\psi) = \frac{\psi-1}{N}$. The correctness of the aggregation can be seen from
     \begin{align*}

### 2022-03-09 authors_responses/conditional_accept/authors_response.tex
Some errors in equations fixed (missing '2', notation update, etc) Reviewer 2 comments finished and more responses to reviewer 3 added. Relevant changes to main text made as well

@@
 
-It is hard to say explicitly whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet).
-In addition, a further optimised implementation executed on more powerful hardware could result in significantly faster runtimes.
-
-\textit{+changes made} time was used primarily as a comparitive measure in key sizes.
+It is hard to explicitly say whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet).
+In terms of reducing this time, a smaller key size, optimised code or more powerful hardware could be used depending on the scenario.
+We have updated the discussion on execution time and choosing key sizes in section VI to elaborate on their relation and how computation time could be reduced in hopes it makes the reasoning clearer.
 
@@
 My response.
+existing typical schemes AES and RSA
 
@@
 
-My response.
+As the proposed method presents a solution to a novel cryptographic problem
+
+due to the lack of methods to which it can be comap
+
+as the work presents a novel solution to a cryptographic problem
+in addition to keeping the work short
+the divide .. would further complicate the interpretation of complexity analysis statements due to the combination of bit terms and number terms
+Due to the divide between the cryptographic component and the localisation component
+
+We hope this reasoning 
+backs the reasoning for excluding a complexity analysis in the work
 
@@
 
-In practice, chosen cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key.
-For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must not be leaked for the foreseeable future.
-Since cryptographic \textit{guarantees} are required, computation is not directly considered when choosing key sizes.
-However, in cases where computation makes desired cryptograhpic guarantees infeasible, shorter required secrecy or more frequent key exchanges can be considered to reduce key sizes and computation times.
-
-\textit{+changes made}
+In practice, choosing a cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key.
+For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must remain private for the foreseeable future.
+Since the secrecy is required, computation is not directly considered when choosing key sizes.
+However, in cases where computation makes the desired secrecy infeasible, shorter required secrecy and more frequent key exchanges can be considered to reduce key sizes and computation times.
+To elaborate this requirement, we have added comments discussing the execution time and choosing key sizes in section VI.
 

### 2022-03-09 main.tex
Some errors in equations fixed (missing '2', notation update, etc) Reviewer 2 comments finished and more responses to reviewer 3 added. Relevant changes to main text made as well

@@
 \begin{equation}
-    sk_0 = -\sum^{n}_{i=1}sk_i \pmod{N^2}\,,
+    sk_0 = -\sum^{n}_{i=1}sk_i\,,
 \end{equation}
@@
     \begin{split}
-        &H(t)^{sk_0}\prod^{n}_{i=1}c_{i,t} \pmod{N^2} \\
-        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a_{i,t}} H(t)^{sk_i} \pmod{N^2} \\
-        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a_{i,t}} \pmod{N^2} \\
-        \equiv &(N+1)^{\sum^n_{i=1}a_{i,t}} \pmod{N^2}\,,
+        &H(t)^{sk_0}\prod^{n}_{i=1}c^{(t)}_{i} \pmod{N^2} \\
+        \equiv &H(t)^{sk_0}\prod^{n}_{i=1}(N+1)^{a^{(t)}_{i}} H(t)^{sk_i} \pmod{N^2} \\
+        \equiv &H(t)^{\sum^n_{j=0}sk_j} \prod^{n}_{i=1}(N+1)^{a^{(t)}_{i}} \pmod{N^2} \\
+        \equiv &(N+1)^{\sum^n_{i=1}a^{(t)}_{i}} \pmod{N^2}\,,
     \end{split}
@@
 Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
-Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i \pmod{N^2}$.
+Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i$.
 
@@
         \vdots
-    \end{bmatrix}\,,
+    \end{bmatrix}^\top\,,
 \end{equation}
@@
         \vdots
-    \end{bmatrix}\,. \label{eqn:modified_jacobian}
+    \end{bmatrix}^\top\,. \label{eqn:modified_jacobian}
 \end{equation}
@@
         \alpha_i^{(k,1)} &= (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}^3 + (2r_{k,i}^{\prime-1})\hat{x}_{k|k-1}\hat{y}_{k|k-1}^2 \\
-        &\quad+ (-r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\
+        &\quad+ (-2r_{k,i}^{\prime-1}s_{x,i})\hat{x}_{k|k-1}^2 + (-2r_{k,i}^{\prime-1}s_{x,i})\hat{y}_{k|k-1}^2 \\
         &\quad+ (2r_{k,i}^{\prime-1}z'_{k,i})\hat{x}_{k|k-1} + (-2r_{k,i}^{\prime-1}s_{x,i}^2)\hat{x}_{k|k-1}\\
@@
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}_{k|k-1}\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(2r_{k,i}^{\prime-1})}\cdot$\par
-    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
+    \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{x}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
     \ $\mathcal{E}_{pk_0}(\mathsf{E}_{0}(\hat{y}^2_{k|k-1}))^{\mathsf{E}_{0}(-2r_{k, i}^{\prime-1}s_{x,i})}\cdot$\par
@@
 Figure \ref{fig:sim_timing} shows the averages of $10$ execution times when varying the numbers of sensors and key sizes (bit lengths of $N$).
-Here, increasing the number of sensors primarily affected the number of inter-process communications and aggregation modular multiplications due to the asynchronous implementation.
+Here, increasing the number of sensors primarily affects the number of inter-process communications and aggregation steps due to the asynchronous implementation.
 \begin{figure}[htbp]
@@
 \end{figure}
-We can see from the figure that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size.
-The key size should be chosen such that sufficient security is achieved, and the current recommendation, when relying on the DCRA for security (difficulty of factorising $N$), is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
-For our implementation of the filter, run on the aforementioned hardware, this results in a filter update computation duration of roughly $1.7s$.
+We can see that the predominant computational costs stem from cryptographic computations and are directly dependent on the chosen key size.
+In practice, choosing a key size should take into account the duration of secrecy and the secret key lifetime.
+When relying on the DCRA for security, the current recommendation for encrypting government documents is the use of $2048$ bit length keys \cite{barkerRecommendationPairwiseKey2019}.
+For our implementation and aforementioned hardware, this results in a filter update roughly every $1.7s$.
+In a scenario where sensors are mobile and past navigations can be made public, reduced key sizes can be considered, while a further decrease in computation time could be achieved with code optimisations and more powerful hardware.
 

### 2022-03-10 authors_responses/conditional_accept/authors_response.tex
Completed reviewer response document Remaining: proof read + fit to 12 pages + update of diff document

--- 2022-03-07 authors_responses/conditional_accept/authors_response.tex
@@
 
-We are glad to hear the paper is acceptable for publication and have responded to each of the reviewer comments below, hoping to clarify all remaining concerns.
+We are glad to hear the paper is acceptable for publication and have responded to each of the reviewer comments below, hoping to clarify all the remaining concerns.
 
@@
 The key reason that any sensor-specific information (such as its measurement noise variance) is considered private is that it may hold identifying data if analysed by an adversary.
-For example, a particular model of sensor may be identified from its measurement noise variance, enabling a targeted attack (cyber or physical) against that sensor.
+For example, a particular sensor's model may be identified from its measurement noise variance, enabling a targeted attack (cyber or physical) against that sensor.
 We have made a change to the introduction section to clarify this reasoning.
@@
 We regret that this was not clear to the reviewer.
-We refer to leakable content as arbitrary information to stress that \textit{nothing} can be leart.
-That is, neither the information we can predict the importance of (such as state estimates or sensor locations), nor that for which we cannot.
+We refer to leakable content as arbitrary information to stress that \textit{nothing} can be learnt.
+That is, neither the information we can predict the importance of (such as state estimates or sensor locations) nor that for which we cannot.
 This is common in cryptography, as no assumptions on the methods or intentions of adversaries can be made.
-We have updated the sentence to try and make this clearer and note that examples of information that should not be learnt (state estimates and sensor locations) have been given in the preceeding section.
+We have updated the sentence to try and make this clearer and note that examples of information that should not be learnt (state estimates and sensor locations) have been given in the preceding section.
 
@@
 
-This relates to the abstraction from the previous response.
+This is a good question and relates to the abstraction from the previous response.
 Since a meaningful cryptographic definition cannot make assumptions about what leakable information might be useful, we cannot state what would happen.
-As the weights originate from the navigator and we do not want sensors to learn any information from the navigator, we can say that no new information should be leart from the weights (and therefore require cryptographic indistinguishabilty of weights).
+As the weights originate from the navigator and we do not want sensors to learn any information from the navigator, we can say that no new information should be learnt from the weights (and therefore require cryptographic indistinguishability of weights).
 In the concrete scheme presented later, it can be seen that the weights correspond to elements of the navigator's state estimate vector, which is stated as an example of information that must remain private to the navigator.
@@
 
-We are sorry for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]).
-The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information.
-We hope this clears up why the definition is only referenced.
+We apologise for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]).
+The full cryptographic game which defines it was originally present in the appendix of the initial submission, but removed after reviewers requested less cryptographic background.
+For this reason, we have left the definition only referenced and hope this is found satisfactory.
 
@@
 
-My response.
+We agree that a further interpretation of execution times was lacking.
+It is hard to explicitly say whether a filter update of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air balloon but would be insufficient for a fast-moving object such as a jet).
+In terms of reducing this time, a smaller key size, optimised code or more powerful hardware could be used depending on the scenario.
+We have updated the discussion on execution time and choosing key sizes in section VI to elaborate on their relationship and how computation time could be reduced hoping that this makes our reasoning clearer.
 
@@
 
-We're sorry this wan't clearer.
-
-\dots quantisation noise is negligible when the quantised integer bit size is larger than the bit size of used floating-point numbers
+We regret that this was not clearer.
+The quantisation noise is captured by the precision parameter $\phi$, which results in less noise when the parameter is large but is upper-bounded by $(20)$.
+Here, it is noted that when $M=N$, the upper bound can be practically ignored since $\phi$ can be chosen to have a bit-length much larger than a floating-point number, making any introduced encoding noise negligible.
+When pseudocode is presented in subsection V.C, $M=N$ is chosen, and in the results section VI, $\phi=2^{32}$ leads to a negligible difference in performance between an unencrypted (and non-quantised) EIF and the presented quantised and encrypted one.
+We have updated subsection V.C to make this clearer and hope that it now explains why there is no need for the quantisation noise to be considered in the filter.
 
@@
 
-My response.
+This could indeed have been stated more explicitly in the text.
+Typical symmetric and public-key encryption schemes only support the encryption and decryption of data and therefore imply a trust between encryptor and decryptor (any information from the encryptor is learnt, in whole, by the decryptor).
+This assumption can be made in some scenarios, for example, when loading a secure webpage, the decryptor wishes to see the page in its entirety while the encryptor wishes to provide it.
+However, when this trust cannot be assumed, such as in our scenario of a navigator and sensors, we want specific control over what information can be learnt from encryptions, making the typical schemes (as well as existing homomorphic schemes in our case) no longer applicable.
+The motivation for the notion of linear combination aggregator obliviousness is the potential for modifying the communications in distributed range-only navigation to a sum of locally weighted sums where the result contains only average sensor data.
+This notion is defined as part of the problem statement before a scheme that meets it and the appropriately modified navigation are presented as solutions.
+We have now updated the introduction section to better explain why the typical cryptographic schemes are not applicable to the problem we consider.
 
@@
 
-My response.
+Thank you for noticing this. We have updated the notation section and other places throughout the text to remove any found errors.
 
@@
 
-My response.
+We thank you for the reasonable suggestion.
+As the proposed method presents a solution to a novel cryptographic problem, we believe that a lack of methods to which it can be compared reduces the benefits of a complexity analysis to readers.
+While also keeping the work shorter, the combination of complexities in terms of bit lengths (required for cryptographic components) and number sizes (required for state estimation components) would further complicate the interpretation of any presented analysis.
+We hope this rationale can be understood as the reason for excluding a theoretical complexity analysis from the work.
 
@@
 
-My response.
+Thank you for the interesting suggestion.
+We found the topic relates to our reasoning in responses to your comments $2$ and $4$ above.
+The cryptographic notion of linear combination aggregator obliviousness is presented as a novel part of the problem to which the proposed scheme is a solution.
+Since the proposed scheme is proven correct (meets the novel notion), and no alternative that meets this notion is known to exist, it is difficult to measure its performance through a meaningful comparison.
+Instead, the presented use-case for the scheme, distributed range-only localisation, has its performance measured in terms of accuracy (comparison to an industry-standard algorithm without privacy guarantees) and execution time (from our local implementation, including the aggregation scheme).
+A possible measure of scheme performance would be the execution times of individual operations in the proposed scheme, but due to their implicit presence in figure 5 (predominant computation costs stem from cryptographic operations) and the desire to keep the paper short, we have decided to omit this.
+We hope this elaborates on our reasoning.
 
@@
 
-My response.
+In practice, choosing a cryptographic key size is dependent on the required duration of secrecy and the planned lifetimes of used secret keys.
+For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must remain private for the foreseeable future.
+Since secrecy is required, computation is not directly considered when choosing key sizes.
+However, in cases where computation makes the desired secrecy infeasible, shorter required secrecy and more frequent key exchanges can be considered to reduce key sizes and computation times.
+To elaborate on this requirement, we have added comments discussing the execution time and choosing key sizes in section VI.
 

### 2022-03-10 main.tex
Completed reviewer response document Remaining: proof read + fit to 12 pages + update of diff document

@@
 This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively.
-In some cases however, partial data leakage or encrypted data processing is required for achieving a desired goal which has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in signal processing or localisation tasks.
+These scenarios, however, imply a trust between the encrypting and decrypting parties in the network.
+In some cases, this assumption cannot be made and control over what can be learnt or performed with encryptions is desired.
+This has led to several homomorphic and functional encryption schemes \cite{paillierPublicKeyCryptosystemsBased1999,shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013,chotardDecentralizedMultiClientFunctional2018} finding uses in various signal processing and localisation tasks.
 In \cite{alanwarPrOLocResilientLocalization2017}, homomorphic encryption is used to make time-independent model-free location estimates where an estimator cannot learn sensor measurements or locations.
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
-In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised and hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
 

### 2022-03-10 main.tex
Small inconsistent ascii hyphen

@@
 Afterward, he obtained his Ph.D.
-in 2013 at the Intelligent Sensor–Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
+in 2013 at the Intelligent Sensor-Actuator-Systems Laboratory, Karlsruhe Institute of Technology (KIT), Germany.
 His research interests are in the areas of multi-sensor data fusion, distributed and decentralized Kalman filtering, combined stochastic and set-membership approaches to state estimation, and event-based systems.
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}
-is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor–Actuator-Systems Laboratory (ISAS).
+is a chaired professor of Computer Science at the Karlsruhe Institute of Technology (KIT) in Germany and director of the Intelligent Sensor-Actuator-Systems Laboratory (ISAS).
 He obtained his Ph.D.

### 2022-03-11 main.tex
Completed final proof read and updated diff in author's response

@@
 This can be achieved with common symmetric and public-key encryption schemes such as the Advanced Encryption Standard (AES) \cite{gueronIntelAdvancedEncryption2010} and the Rivest-Shamir-Adleman cryptosystem (RSA) \cite{rivestMethodObtainingDigital1978}, respectively.
-These scenarios, however, imply a trust between the encrypting and decrypting parties in the network.
+These scenarios, however, imply trust between the encrypting and decrypting parties in the network.
 In some cases, this assumption cannot be made and control over what can be learnt or performed with encryptions is desired.
@@
 In \cite{aristovEncryptedMultisensorInformation2018}, similar secrecy is achieved with a linear Kalman filter when a hierarchical sensor network is present.
-In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total powergrid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing local control inputs in a distributed environment without learning individual inputs.
+In \cite{shiPrivacyPreservingAggregationTimeSeries2011,joyeScalableSchemePrivacyPreserving2013}, privacy-preserving aggregation schemes are presented as a means to compute total power grid usage without disclosing individual contributions, while in \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, private Weighted Sum Aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are introduced as a means for computing control inputs in a distributed network without learning individual contributions.
 
 Our contribution in this work presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private.
-We first define a novel notion for private linear combination aggregation and present an implementation that satisfies these requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
-The linear combination aggregation scheme we put forward is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security.
+We first define a novel cryptographic notion for linear combination aggregation and present an implementation satisfying the requirements, before using it to derive a filter based on the Extended Kalman Filter with no hierarchical sensor layout assumptions.
+The linear combination aggregation scheme is in principle similar to the pWSAh scheme in \cite{alexandruPrivateWeightedSum2020}, however, a formal definition with different communication assumptions and leakages is given, crucial for its cryptographic security.
 To the best of the authors' knowledge, no existing method for Bayesian state estimation using range-only sensors and meeting the desired privacy requirements exists.
 
-We motivate this scenario with the example of vehicle localisation in the presence of privately owned measurement stations.
-While the intention of measurement stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other present stations and the navigator.
-Similarly, a navigator may not wish to disclose their most accurate location estimates to untrusted third-party measurers.
+We motivate this scenario with an example of vehicle localisation in the presence of privately owned measurement stations.
+While the intention of stations is the accurate navigation of passing vehicles, it may be reasonable to desire identifying details, such as hardware specifications or physical locations, to remain unknown to the other stations and the navigator.
+Similarly, a navigator may not wish to disclose their accurate location estimates to untrusted third-party measurers.
 
@@
 \end{LaTeXdescription}
-We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a complete group and treated as the global set for estimation purposes, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts.
+We justify the global broadcast assumption by noting that any subset of sensors within the range of the navigator can be considered a group and treated as the global set during estimation, generalising the method, while the wide-spread use of cheap non-directional antennas supports the assumption of consistent broadcasts.
 The final assumption refers to the known problem of misbehaving sensors \cite{lazosSeRLocSecureRangeindependent2004,ben-galOutlierDetection2005}, often requiring additional complicated detection mechanisms, and will not be considered in this work.
@@
 Define a hash function $H:\mathbb{Z} \rightarrow \mathbb{Z}_{N^2}^*$, choose the number of weights to combine, $m>1$, and set public parameter $\mathsf{pub}=H$, navigator public key $pk_0 = N$ and navigator private key $sk_0=(p,q)$.
-Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key as $sk_n = -\sum^{n-1}_{i=1}sk_i$.
+Sensor secret keys are generated by choosing $sk_i,\,i\in\{1,\dots,n-1\}$ uniformly from $\mathbb{Z}_{N^2}$ and setting the last key to $sk_n = -\sum^{n-1}_{i=1}sk_i$.
 
@@
 namely, their measurements $z_{k,i}$, measurement variances $r_{k,i}$ and locations $\vec{s}_i$; captured in measurement functions $h_i$ and Jacobians $\mat{H}_{k,i}$.
-However, $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ also require the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ to be computed (in $h_i$ and $\mat{H}_{k,i}$).
-For this reason, our goal is to reformulate \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} to be computable at each sensor $i$ as a linear combination of functions of the navigator state estimate (the navigator weights), to be subsequently aggregated at the navigator.
-Application of the linear combination aggregation scheme proposed would in turn guarantee that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
+To compute $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$, however, the current predicted state estimate $\hat{\vec{x}}_{k|k-1}$ is also required (in $h_i$ and $\mat{H}_{k,i}$).
+Therefore, our goal is to rearrange \eqref{eqn:measurement_vec} and \eqref{eqn:measurement_mat} as a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$ (the navigator weights) computable at each sensor $i$, to be subsequently aggregated at the navigator.
+Application of the linear combination aggregation scheme proposed in turn guarantees that sensors do not learn the navigator state, and the navigator learns only the aggregation required for updating its state estimate in \eqref{eqn:eif_info_vec_update} and \eqref{eqn:eif_info_mat_update}.
 
@@
 
-The first thing we notice when wanting to decompose $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
+The first thing we notice when wanting to rearrange $\vec{i}_{k,i}$ and $\mat{I}_{k,i}$ to a linear combination of functions of $\hat{\vec{x}}_{k|k-1}$, is that $h_i$ cannot be rearranged in this way due to the present square-root.
 Similarly, the Jacobian of $h_i$ at $\hat{\vec{x}}_{k|k-1}$,
@@
 Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future.
-Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to decrease the filter update duration, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.
+Additional future work includes exploring more computationally efficient encryption schemes, the security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to enforce the consistent broadcast assumption.
 
@@
 
-%\vspace{-1\baselineskip}
+\vspace{-2\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/marko_ristic}}]{Marko Ristic}
@@
 
-%\vspace{-1\baselineskip}
+\vspace{-2\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/benjamin_noack}}]{Benjamin Noack}
@@
 
-%\vspace{-1\baselineskip}
+\vspace{-2\baselineskip}
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/uwe_d_hanebeck}}]{Uwe D. Hanebeck}

### 2022-04-20 authors_responses/conditional_accept/authors_response.tex
Made all small changes from Benjamin's final proof read. Updated diff and response accordingly

@@
 We regret that there was some confusion about the prediction step of the presented localisation algorithm.
-Equations $26$-$27$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$.
+Equations $(26)$ -- $(27)$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$.
 The Gaussian assumption has indeed been removed from the system model, and obtaining the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$ can be computed using any local filter (linearising or otherwise) as mentioned in Section V.
 The Gaussian assumption that remains is only present in the measurement model, as is a commonly done to simplify the modelling of sensors, and the non-linear distance-measurement function $h_i$ is linearlised by an appropriate EKF filter for the localisation update step only.
-We hope this clarifies equations $26$-$27$ and the use of the EKF.
+We hope this clarifies equations $(26)$ -- $(27)$ and the use of the EKF.
 

### 2022-04-20 main.tex
Made all small changes from Benjamin's final proof read. Updated diff and response accordingly

@@
 Traditional distributed sensor navigation methods typically involve the leakage of sensor or navigator information by communicating measurements or estimates and thus do not preserve participants' privacy.
-The existing approaches that do provide such guarantees, fail to address sensor and navigator privacy in the common application of model-based range-only estimation, consequently forfeiting broad applicability.
+The existing approaches that do provide such guarantees fail to address sensor and navigator privacy in the common application of model-based range-only localisation, consequently forfeiting broad applicability.
 In this work, we define a notion of privacy-preserving linear combination aggregation and use it to derive a modified Extended Kalman Filter using range measurements such that navigator location, sensors' locations, and sensors' measurements are kept private during navigation.
@@
 In section \ref{sec:problem_statement}, we introduce both the cryptographic and estimation problems considered in this work, before giving some relevant preliminaries in section \ref{sec:preliminaries}.
-Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties and section \ref{sec:priv_localisation} gives a solution to the estimation problem making use of this scheme.
-Simulation results are discussed in section \ref{sec:sim_and_results} and concluding remarks are made in section \ref{sec:conclusion}.
+Section \ref{sec:lcao_scheme} proposes a cryptographic scheme meeting our desired security properties, and section \ref{sec:priv_localisation} gives a solution to the estimation problem making use of this scheme.
+Simulation results are discussed in section \ref{sec:sim_and_results}, and concluding remarks are made in section \ref{sec:conclusion}.
 
@@
 $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose.
-The expected value of a random variable is denoted $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively.
+The expected value of a random variable is denoted by $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively.
 $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences.
@@
 $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group.
-$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator, and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
 
@@
 In this work, we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn any information about the navigator or other sensors beyond their local measurements, and the navigator not to learn any information about individual sensors beyond its location estimate.
-The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them, as well as an estimation scheme that can use the encryption in the context of range-only navigation.
-
-To give a formal cryptographic requirement in a distributed setting, we must first consider the communication requirements of our context, and define the attacker capabilities and the desired security of a suitable encryption scheme.
+The problem is two-fold, in that we require explicit cryptographic requirements with a suitable encryption scheme meeting them as well as an estimation scheme that can use the encryption in the context of range-only navigation.
+
+To give a formal cryptographic requirement in a distributed setting, we must first consider the communication requirements of our context and define the attacker capabilities and the desired security of a suitable encryption scheme.
 In this section, we will define a communication protocol and the relevant formal definition of security we aim to achieve, followed by the estimation problem to which we will apply it.
@@
 We let a linear combination aggregation scheme be defined as a tuple of the four algorithms $(\mathsf{Setup}, \mathsf{Enc}, \mathsf{CombEnc}, \mathsf{AggDec})$.
-These will be used by a trusted setup party, the navigator and sensors $i\in\{1,\dots,n\}$.
+These will be used by a trusted setup party, the navigator, and sensors $i\in\{1,\dots,n\}$.
 They are defined as follows.
@@
 \end{LaTeXdescription}
-While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Plaintext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix \ref{app:lcao}.
+While indistinguishable weights can be achieved by encrypting weights with an encryption scheme meeting the notion of Indistinguishability under the Chosen Plaintext Attack (IND-CPA) \cite{katzIntroductionModernCryptography2008}, the novel notion of Linear Combination Aggregator Obliviousness (LCAO) has been formalised as a typical cryptographic game between attacker and challenger in appendix~\ref{app:lcao}.
 Lastly, we conclude the cryptographic problem definition with the following important remark.
@@
 In this section, we introduce an encryption scheme meeting the desired security properties in section \ref{subsec:crypto_problem}.
-The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting the notion of LCAO defined in section \ref{subsec:crypto_problem}.
+The scheme is a combination of the Paillier and Joye-Libert schemes and provides encrypted weights meeting IND-CPA and encrypted aggregation meeting the notion of LCAO defined in section~\ref{subsec:crypto_problem}.
 Similarly to its constituents, the scheme bases its security on the DCRA and, as with the Joye-Libert scheme, requires a trusted party for initial key generation and distribution.
@@
 
-    \item[$\mathsf{CombEnc}(t_{k,\tau}, pk_0, sk_i, \mathcal{E}(\omega_1^{(k,\tau)})\dots , a^{(k,\tau)}_{i,1}\dots )$] At instance $t_{k,\tau}$, encrypted linear combination is computed as 
+    \item[$\mathsf{CombEnc}(t_{k,\tau}, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(k,\tau)})\dots , a^{(k,\tau)}_{i,1}\dots )$] At the instance $t_{k,\tau}$, encrypted linear combination is given by 
     \begin{equation}
@@
             &= H(t_{k,\tau})^{sk_i}\cdot \\
-            &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j} \rho_{i}^{N} \pmod{N^2}\,,
+            &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j} \tilde{\rho}_{i}^{N} \pmod{N^2}\,,
         \end{split}
     \end{equation*}
-    for some values $\rho_i,\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$.
-Here, $\rho_i^N$ and $H(t_{k,\tau})^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
+    for some values $\rho_j \in \mathbb{Z}_N,\,j\in\{1,\dots,m\}$ and $\tilde{\rho}_i=\prod^{m}_{j=1}\rho_j$.
+Here, $\tilde{\rho}_i^N$ and $H(t_{k,\tau})^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.
 
@@
         l^{(k,\tau)} &= \prod^n_{i=1}H(t_{k,\tau})^{sk_i}\cdot \\
-        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
+        &\qquad (N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\tilde{\rho}_i^N \!\!\pmod{N^2}
         \end{split}\\
@@
             &= H(t_{k,\tau})^{\sum^n_{i=1}sk_i}\cdot \\
-            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho_i^N \!\!\pmod{N^2}
+            &\qquad \prod^n_{i=1}(N+1)^{\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\tilde{\rho}_i^N \!\!\pmod{N^2}
         \end{split}\\
-        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\rho'^N \!\!\pmod{N^2}\,,
+        &= (N+1)^{\sum^n_{i=1}\sum^{m}_{j=1}a^{(k,\tau)}_{i,j}\omega^{(k,\tau)}_j}\tilde{\rho}^N \!\!\pmod{N^2}\,,
     \end{align*}
-    for some values $\rho_i,\rho' \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$.
+    for some values $\tilde{\rho}_i \in \mathbb{Z}_N,\,i\in\{1,\dots,n\}$ and $\tilde{\rho}=\prod^{n}_{i=1}\tilde{\rho}_i$.
 \end{LaTeXdescription}
@@
         &\hat{\vec{y}}_{k|k} = \hat{\vec{y}}_{k|k-1} + \\
-        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1})
+        &\quad \sum^n_{i=1}\mat{H}^\top_{k,i} r^{-1}_i \left(z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}\right)
     \end{split} \label{eqn:eif_info_vec_update}
@@
 \begin{equation}
-    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i (z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}) \label{eqn:measurement_vec}
+    \vec{i}_{k,i} = \mat{H}^\top_{k,i} r^{-1}_i \left(z_{k,i} - h_i(\hat{\vec{x}}_{k|k-1}) + \mat{H}_{k,i}\hat{\vec{x}}_{k|k-1}\right) \label{eqn:measurement_vec}
 \end{equation}
@@
 \end{align*}
-The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear comabinations of elements in
+The above rearrangements give $\vec{i}'_{k,i}$ and $\mat{I}'_{k,i}$ as linear combinations of elements in
 \begin{equation}
@@
 \end{equation*}
-was simulated and tracked with the algorithms in section \ref{subsec:pseudocode}, using a linear Kalman filter for the navigator's local state prediction.
+was simulated and tracked with the algorithms in section~\ref{subsec:pseudocode}, using a linear Kalman filter for the navigator's local state prediction.
 Code was written in the C programming language using the MPI library \cite{theopenmpiprojectOpenMPI2020} to support asynchronous computations by the sensors and navigator.
@@
 We can also see that the varying average distances between sensors and the navigator have little impact on the differences in performance.
-We attribute this similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, resulting in few additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
+We attribute this similarity in RMSE to the conservativeness of estimated modified measurement variances $r'_{k,i}$, eliminating additional filter divergences, and to the high fractional precision factor, keeping computations consistent with the floating-point arithmetic of the EIF.
 
@@
             \item[\textit{Combine Query}] When $\mathcal{A}$ submits combine query $(i, t, a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$, choose weights $\omega^{(t)}_j,j\in\{1,\dots,m\}$ if not already chosen for the instance $t$, and make an AO encryption query $(i, t, \sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ to $\mathcal{C}$.
-The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\rho^N$ for a random $\rho \in \mathbb{Z}_N$ and return
-            \begin{equation*}
-                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\rho^N H(t)^{sk_i} \pmod{N^2}
+The received response will be of the form $(N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}H(t)^{sk_i}$; multiply it by $\tilde{\rho}^N$ for a random $\tilde{\rho} \in \mathbb{Z}_N$ and return
+            \begin{equation*}
+                (N+1)^{\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j}\tilde{\rho}^N H(t)^{sk_i} \pmod{N^2}
             \end{equation*}
@@
         \end{equation*}
-        for an unknown $b \in \{0,1\}$. Multiply series elements by $\rho_i^N,\,i\in\{1,\dots,n\}$ for randomly chosen $\rho_i \in \mathbb{Z}_N$ and return
-        \begin{equation*}
-            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\rho_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
+        for an unknown $b \in \{0,1\}$. Multiply series elements by $\tilde{\rho}_i^N,\,i\in\{1,\dots,n\}$ for randomly chosen $\tilde{\rho}_i \in \mathbb{Z}_N$ and return
+        \begin{equation*}
+            \left\langle(N+1)^{\sum^m_{j=1}a^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j}\tilde{\rho}_i^N H(t^*)^{sk_i}\,\middle|\,i\in U\right\rangle
         \end{equation*}

### 2022-10-10 authors_responses/conditional_accept_2/authors_response.tex
Responding to (hopefully) final reviewer response.

--- 2022-03-09 authors_responses/conditional_accept/authors_response.tex
@@
 
-Dear Dr. Zhiwei Gao,\\
+Dear Dr Zhiwei Gao,\\
 Dear Reviewers,
 
-Thank you all for your detailed reviews and for finding the manuscript suitable for publication.
-In this letter, we will address the remaining editor and reviewer comments and describe any changes made to the manuscript.
+Thank you all for the positive reviews, in this letter we will address the remaining comments and changes made to the manuscript.
 Throughout this response, reviewers' comments are in \reviewtext{blue}.
@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.
-The reviewers would like the authors to clarify some concerns such as the assumption of the EKF design, private sensor variance information, and research motivation and challenge, and so forth.}
+\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.}
 
-We are glad to hear the paper is acceptable for publication and have responded to each of the reviewer comments below, hoping to clarify all remaining concerns.
+We are glad to hear the positive response, thank you. Below we respond to the remaining reviewer comments.
 
@@
 
-\section*{Response to the Comments of Reviewer 1 (242571)}
+\section*{Response to the Comments of Reviewer 1 (262567)}
 \def\thesection{R1}
 \begin{rebuttal}
-\item \reviewtext{Thank you for updating the manuscript and most of the concerns have been addressed well in the response letter.}
+\item \reviewtext{Based on the revision, all my concerns have been addressed well now I recommend accepting this manuscript as it is.}
 
 We are happy to hear this is the case, thank you.
-
-\item \reviewtext{However, there is one problem still confused me.
-The authors claimed that the Gaussian assumption has been removed in the revised version, however, the EKF (EIF) was still used for prediction (Eqs.
-26-27).
-Basically, the EKF is based on the Gaussian assumption and the prediction is obtained in the sense of mean value.
-Then, the non-Gaussian dynamics would affect the prediction performance using EKF if the Gaussian assumption is removed.
-My point is 1) if the assumption is removed, please explain the non-Gaussian influence from the EKF or 2) if the Gaussian assumption remains in the manuscript, please explain from the noise comes from in physics sense.}
-
-We regret that there was some confusion about the prediction step of the presented localisation algorithm.
-Equations $26$-$27$ are the EKF (EIF) update equations (rather than the prediction equations), resulting in updated terms $\vec{y}_{k|k}$ and $\mat{Y}_{k|k}$ from the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$.
-The Gaussian assumption has indeed been removed from the system model, and obtaining the predictions $\vec{y}_{k|k-1}$ and $\mat{Y}_{k|k-1}$ can be computed using any local filter (linearising or otherwise) as mentioned in Section V.
-The Gaussian assumption that remains is only present in the measurement model, as is a commonly done to simplify the modelling of sensors, and the non-linear distance-measurement function $h_i$ is linearlised by an appropriate EKF filter for the localisation update step only.
-We hope this clarifies equations $26$-$27$ and the use of the EKF.
 
@@
 
-\section*{Response to the Comments of Reviewer 2 (242573)}
+\section*{Response to the Comments of Reviewer 2 (262571)}
 \def\thesection{R2}
 \begin{rebuttal}
-\item \reviewtext{The authors have significantly improved the readability of the paper. The contribution is significant enough for privacy preserving state estimation.}
+\item \reviewtext{This paper presents a range-only localisation method meeting formal cryptographic requirements that ensure sensors keep their measurements, sensor variances and locations private while the navigator keeps its estimates private.
+The paper is standardized and the mathematical derivation seems correct, but there are still some areas that need to be improved, please check and correct.
 
-We thank you for the comment and are glad that the contribution is found significant.
+1. In Notation, please correct the sentence ``$\|$ the binary concatination operator''.}
 
-\item \reviewtext{However, this reviewer still have few comments:
+Thank you for the supportive comments. The quoted sentence has been updated.
 
-1- It could be interesting to comment why sensor variance is a private information. Why is it crucial to preserve it if measurements are already protected?}
+\item \reviewtext{2. In section II-A, please check the correctness of the formula $l_i^{(t)}=\sum_{j=1}^m a^{(t)}_{j,i} \omega^{(t)}_i$, which is inconsistent with the description in Fig. 1.}
 
-This is a good question that had not been elaborated in the work.
-The key reason that any sensor-specific information (such as its measurement noise variance) is considered private is that it may hold identifying data if analysed by an adversary.
-For example, a particular model of sensor may be identified from its measurement noise variance, enabling a targeted attack (cyber or physical) against that sensor.
-We have made a change to the introduction section to clarify this reasoning.
+Thank you for noticing this. The error has now been corrected.
 
-\item \reviewtext{2- In the sentence 'homomorphic encryption is used to make time-independent model-free location estimates where an estimator does not learn sensor measurements or locations.; Shouldn't be 'cannot learn'?}
+\item \reviewtext{3. In section II-A, is the sensor Honest-but-Curious or is the attacker model Honest-but-Curious? How does the attack occur in the sensors?}
 
-Thank you for pointing this out, we have added the change to the manuscript.
+We regret that the intended meaning was not clearer.
+The two expressions were used interchangeably due to sensors being the only corruptible parties by an attacker.
+The section has been updated to explicitly state that attackers are honest-but-curious and that sensors can be corrupted.
+We hope this clarifies the intended meaning.
 
-\item \reviewtext{3- In problem statement 'we consider the context of privacy-preserving range sensor navigation, where we want no sensor to learn information about the navigator or other sensors beyond their local measurements, and the navigator to learn no information about individual sensors beyond its location estimate.', please specify type of information.}
+\item \reviewtext{4.
+What's the meaning of $\mathcal{E}(\cdot)$ in $\mathsf{CombEnc}(t,pk_0,sk_i,\mathcal{E}(\omega_1^{(t)}),\dots)$?
+The author does not give a paraphrase in Notation.
+And in $\mathsf{AggDec}(t,pk_0,sk_0,\dots)$, the public and private keys $pk_0,sk_0$ is not shown in the description of linear combinations $\sum_{i=1}^n l_i^{(t)} = \sum_{i=1}^n \sum_{j=1}^m a^{(t)}_{i,j} \omega^{(t)}_j$.}
 
-We regret that this was not clear to the reviewer.
-We refer to leakable content as arbitrary information to stress that \textit{nothing} can be leart.
-That is, neither the information we can predict the importance of (such as state estimates or sensor locations), nor that for which we cannot.
-This is common in cryptography, as no assumptions on the methods or intentions of adversaries can be made.
-We have updated the sentence to try and make this clearer and note that examples of information that should not be learnt (state estimates and sensor locations) have been given in the preceeding section.
+TODO respond.
 
-\item \reviewtext{4- Indistinguishable weights: what would happen if the sensor learns navigator weights?}
+\item \reviewtext{5. Please complete the references with the relevant information, for example, the year of publication of ref. 8.}
 
-This relates to the abstraction from the previous response.
-Since a meaningful cryptographic definition cannot make assumptions about what leakable information might be useful, we cannot state what would happen.
-As the weights originate from the navigator and we do not want sensors to learn any information from the navigator, we can say that no new information should be leart from the weights (and therefore require cryptographic indistinguishabilty of weights).
-In the concrete scheme presented later, it can be seen that the weights correspond to elements of the navigator's state estimate vector, which is stated as an example of information that must remain private to the navigator.
-We hope this makes the meaning and reasoning of indistinguishability clearer.
-
-\item \reviewtext{5- Fix the following sentence: 'If an attacker compromises the navigator, they have control over the weights,'}
-
-Unfortunately, we are unable to find an issue with the stated sentence and have asked additional native English speakers that have also agreed that the sentence looks correct.
-In case the use of ``they'' (rather than ``he'' or ``she'') is being referred to, it is the formal grammatical pronoun for a person when gender is not specified.
-
-\item \reviewtext{6- Define IND-CPA.}
-
-We are sorry for the confusion, the first use of the term ``Indistinguishability under the Chosen Plaintext Attack (IND-CPA)'' is in section II.A and has been referenced (reference [21]).
-The full cryptographic game which defines it was present in the appendix of the initial submission but removed due to initial reviews requesting fewer cryptographic background information.
-For this reason, we have left the definition only referenced and hope this is found satisfactory.
-
-\item \reviewtext{7- Simulation: The authors have found that 1.7 s are needed for each
-computation step, is that compatible with real-time operation?}
-
-It is hard to explicitly say whether a filter udpate of $1.7s$ is compatible with real-time computation as this is dependent on the use-case (for example, infrequent measurements may suffice for the localisation of a slow-moving object such as a hot air baloon but would be insufficient for a fast moving object such as a jet).
-In terms of reducing this time, a smaller key size, optimised code or more powerful hardware could be used depending on the scenario.
-We have updated the discussion on execution time and choosing key sizes in section VI to elaborate on their relation and how computation time could be reduced in hopes it makes the reasoning clearer.
-
-\item \reviewtext{8- Can you comment why quantization noise, involved in the encryption-decryption schemes, isn't taken into account in the filter equations?}
-
-We're sorry this wan't clearer.
-The quantisation noise is captured by the precision parameter $\phi$, which results in less noise when the parameter is large but is upper-bounded by $(20)$.
-Here, it is noted that when $M=N$, the upper bound can be practically ignored since $\phi$ can be chosen to have a bit-length much larger than a floating-point number, making any introduced encoding noise negligible.
-When pseudocode is presented in subsection V.C, $M=N$ is chosen, and in the results section VI, $\phi=2^{32}$ leads to a negligible difference in performance between an unencrypted (and unquantised) EIF and the presented quantised and encrypted one.
-We have udpated subsection V.C to make this clearer and hope that explains why there is no need for the quantisation noise to be considered in the filter.
-
-\end{rebuttal}
-
-%      8888888b.                         .d8888b.
-%      888   Y88b                       d88P  Y88b
-%      888    888                            .d88P
-%      888   d88P .d88b.  888  888          8888"
-%      8888888P" d8P  Y8b 888  888           "Y8b.
-%      888 T88b  88888888 Y88  88P      888    888
-%      888  T88b Y8b.      Y8bd8P       Y88b  d88P
-%      888   T88b "Y8888    Y88P         "Y8888P"
-
-\section*{Response to the Comments of Reviewer 3 (246951)}
-\def\thesection{R3}
-\begin{rebuttal}
-\item \reviewtext{Comments:
-
-This paper proposes a novel distributed localisation method in the presence of range-only sensors, which preserves both navigator and sensor privacies.
-The major contribution of this paper is that a novel private linear combination aggregation scheme is proposed, and based on that, a modified extended Kalman filter is also derived.
-Some comments are given as follows:
-
-1.In this paper, the full names of some abbreviations are not given. For example, in Section I, page 1, left column, “AES”and “RSA”, and in Section I, page 1, right column, “pWSAc” and “pWSAh”.}
-
-We apologise for having missed these, the full names have now been added.
-
-\item \reviewtext{2.The authors should elaborate the advantages and disadvantages of the existing typical cryptographic secrecy scheme and the motivation for proposing private linear combination aggregation scheme in this paper.}
-
-My response.
-existing typical schemes AES and RSA
-
-\item \reviewtext{3.Some symbols are reused. For example, In Section I, Notation, “timestep k” and “will denote encryption and decryption with key k”.}
-
-Thank you for noticing this. We have updated the notation section and other places throughout the text to remove the found errors.
-
-\item \reviewtext{4.The authors need to present theoretical computational complexity of the proposed method.}
-
-As the proposed method presents a solution to a novel cryptographic problem
-
-due to the lack of methods to which it can be comap
-
-as the work presents a novel solution to a cryptographic problem
-in addition to keeping the work short
-the divide .. would further complicate the interpretation of complexity analysis statements due to the combination of bit terms and number terms
-Due to the divide between the cryptographic component and the localisation component
-
-We hope this reasoning 
-backs the reasoning for excluding a complexity analysis in the work
-
-\item \reviewtext{5.The authors should state how to measure the performance of the private linear combination aggregation scheme proposed in this paper.}
-
-My response.
-
-\item \reviewtext{6.In practical engineering application, how to balance the relationship between key sizes and computation.}
-
-In practice, choosing a cryptographic key size is dependent on the required length of secrecy and the planned lifetime of the used secret key.
-For example, if the location of an object needs only be private on the day of travel and new keys are generated each day, a shorter key can be used than for an object whose past location must remain private for the foreseeable future.
-Since the secrecy is required, computation is not directly considered when choosing key sizes.
-However, in cases where computation makes the desired secrecy infeasible, shorter required secrecy and more frequent key exchanges can be considered to reduce key sizes and computation times.
-To elaborate this requirement, we have added comments discussing the execution time and choosing key sizes in section VI.
+TODO respond.
 

### 2022-10-11 authors_responses/conditional_accept_2/authors_response.tex
Added remaining changes from reviewer comments Updated authors response with information from updated TAC response (different editor now)

@@
 
-Dear Dr Zhiwei Gao,\\
+Dear Prof. David Castanon,\\
 Dear Reviewers,
@@
 \begin{rebuttal} %\setcounter{enumi}{-1}
-\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.}
+\item \reviewtext{I am pleased to inform you that the paper is acceptable for publication in the Transactions provided that you can make the modifications described below.
 
-We are glad to hear the positive response, thank you. Below we respond to the remaining reviewer comments.
+The reviewers would like the authors to double check the symbols and formulas and clarify some concerns on sensor attacks etc, which are detailed in their comments.}
+
+We are glad to hear the positive response, thank you. Below we clarify the remaining concerns from reviewer comments.
 
@@
 
-Thank you for noticing this. The error has now been corrected.
+The error has now been corrected, thank you for noticing it.
 
@@
 
-We regret that the intended meaning was not clearer.
-The two expressions were used interchangeably due to sensors being the only corruptible parties by an attacker.
-The section has been updated to explicitly state that attackers are honest-but-curious and that sensors can be corrupted.
+This was not written clearly and we are grateful that it was pointed out.
+The section has been updated to explicitly state that attackers are honest-but-curious and that the navigator or sensors can be corrupted.
 We hope this clarifies the intended meaning.
@@
 
-TODO respond.
+The reviewer is correct to notice the inconsistency with notations in this section.
+Key subscripts have been added to make it clear that the encryptions $\mathcal{E}(\cdot)$ are performed with the keys generated in the $\mathsf{Setup}(\cdot)$ algorithm and the linear combinations $l_i^{(t)}$ modified to denote the unencrypted sum.
 
@@
 
-TODO respond.
+Sorry about the mistake, the missing year has been added and the remaining references inspected for additional errors.
 

### 2022-10-11 main.tex
Added remaining changes from reviewer comments Updated authors response with information from updated TAC response (different editor now)

@@
 $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group.
-$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator, and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ is the binary concatination operator, and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
 
@@
 
-At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{j,i}^{(t)}\omega_i^{(t)}$ based on their measurement data $a_{j,i}$.
+At every \textit{instance} $t$ (used to distinguish from an estimation \textit{timestep}), the navigator first broadcasts $m$ weights $\omega_j^{(t)}, j\in\{1,\dots,m\}$ to all sensors $i\in\{1,\dots,n\}$, who individually compute linear combinations $l^{(t)}_i=\sum^m_{j=1}a_{i,j}^{(t)}\omega_j^{(t)}$ based on their measurement data $a_{j,i}$.
 Linear combinations are then sent back to the navigator, who computes their sum $\sum^n_{i=1}l^{(t)}_{i}$.
@@
 This means the navigator may not send different weights to individual sensors during a single instance $t$.
-    \item[Honest-but-Curious Sensors] We adopt the honest-but-curious attacker model for all involved sensors, meaning that they follow the localisation procedure correctly but may store or use any gained sensitive information.
+    \item[Honest-but-Curious Attackers] We adopt the honest-but-curious attacker model for all corrupted parties that an attacker controls, meaning that the navigator and sensors follow the localisation procedure correctly but attackers may store or use any gained sensitive information.
 \end{LaTeXdescription}
@@
     \item[$\mathsf{Enc}(pk_0, x)$] The navigator and sensors can encrypt any value $x$ with the navigator's public key $pk_0$ and obtain the encryption $\mathcal{E}_{pk_0}(x)$.
-    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}(\omega_1^{(t)}),\dots,\mathcal{E}(\omega_m^{(t)}), a^{(t)}_{i,1},\dots,a^{(t)}_{i,m})$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination denoted $l^{(t)}_i = \mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ using its secret key $sk_i$.
-    \item[$\mathsf{AggDec}(t, pk_0, sk_0, l^{(t)}_1,\dots,l^{(t)}_n)$] At instance $t$, the navigator computes the aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}=\sum^{n}_{i=1}\sum^{m}_{j=1} a^{(t)}_{i,j}\omega^{(t)}_j$ using its public and private keys $pk_0$, $sk_0$.
+    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\!...,\mathcal{E}_{pk_0}(\omega_m^{(t)}),a^{(t)}_{i,1},\!...,a^{(t)}_{i,m})\hspace*{1.2pt}$] At instance $t$, sensor $i$ computes and obtains the encrypted linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}a^{(t)}_{i,j}\omega^{(t)}_j)$ with secret key $sk_i$.
+    \item[$\mathsf{AggDec}(t, pk_0, sk_0, \mathcal{E}_{pk_0,sk_1}(l^{(t)}_1),\dots,\mathcal{E}_{pk_0,sk_n}(l^{(t)}_n))$] At instance $t$, the navigator computes the plaintext aggregation of linear combinations $\sum^{n}_{i=1}l_i^{(t)}$ using its public and private keys $pk_0$, $sk_0$.
 \end{LaTeXdescription}
@@
 Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future.
-Additional future work includes exploring more computationally efficient encryption schemes, the security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to enforce the consistent broadcast assumption.
+Additional future work includes exploring more computationally efficient encryption schemes, the security implications of attackers that are not only honest-but-curious and expanding the LCAO notion to enforce the consistent broadcast assumption.
 

### 2022-10-11 main.tex
Minor rewording to make the manuscript fit on 12 pages again Updated and added diff file to the response

@@
 $\mathbb{Z}_N$ is used for the set of integers modulo $N$ and $\mathbb{Z}^*_N$ for its multiplicative group.
-$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ is the binary concatination operator, and the term \textit{negligible function} refers to its cryptographic definition in \cite{katzIntroductionModernCryptography2008}.
+$\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ is the binary concatination operator, and the term \textit{negligible function} refers to its definition in \cite{katzIntroductionModernCryptography2008}.
 
@@
 This means the navigator may not send different weights to individual sensors during a single instance $t$.
-    \item[Honest-but-Curious Attackers] We adopt the honest-but-curious attacker model for all corrupted parties that an attacker controls, meaning that the navigator and sensors follow the localisation procedure correctly but attackers may store or use any gained sensitive information.
+    \item[Honest-but-Curious Attackers] We adopt the honest-but-curious attacker model.
+The navigator and sensors are corruptable but follow the localisation procedure correctly, while attackers may use any gained sensitive information.
 \end{LaTeXdescription}
